### 2020-07-17 99-admin/naming-conventions/names.Rmd
Add current version of naming conventions
May do some small edits here before pull requesting

---
title: "Naming Conventions for GRSSLCM"
subtitle: "Grande Ronde State-Space Life Cycle Model"
output: html_document
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F)

# load packages
library(knitr)
library(kableExtra)
```

# General Conventions:

*  $P$ is used for parr (first year freshwater juveniles)
*  $M$ is used for smolt (second year freshwater juveniles)
*  $O$ is used for ocean juveniles
*  $R$ is used for returning adults
*  $S$ is used for spawning adults
*  $b$ is used to denote "before migration" 
*  $a$ is used to denote "after migration"
*  $\phi$ is used to denote a survival term, subscripts used to denote the from/to states
*  $\psi$ is used to denote maturation from ocean juvenile to returning adult (no distinction between jacks and adults because they are all sexually mature)
*  $\dot{x}$ is used to denote that $x$ is an observed quantity (data)
*  $L$ (uppercase) is used to denote that the quantity has been logit-tranformed, $l$ (lowercase) is used to denote that the quantity has been log-transformed.
*  $y$ represents brood year fish were spawned; $t$ represents return year for adults

**Notes following 7/10/2020 Call**

*  May wish to consider replacing $\phi$ with $\mathrm{surv}$ and $\psi$ with $\mathrm{mat}$.
*  May wish to consider replacing $M$ with $SM$ and $S$ with $SP$
    *  If all other variables (abundance states) are one letter long, would this confuse readers making them think about multiplication?
*  Overall, we agreed this conventional structure is good for now, and we can revise if we find it too cumbersome or reviewers find it confusing
*  It has the advantage of consistency in naming logic

# Specific Conventions {.tabset .tabset-dropdown}

```{r read-manip-table}
# raw input file
tab = read.csv("names.csv", allowEscapes = T, stringsAsFactors = F)

# mark it up
tab$code = paste0("`", tab$code, "`")
tab$symbol = paste0("$", tab$symbol, "$")

colnames(tab) = c("", "In Code", "Symbol", "Description", "Notes")
```

```{r create-table-fun}
create_table = function(group) {
  kable(tab[tab[,1] == group,-1], format = "html", escape = F, row.names = F) %>%
    kable_styling(full_width = F, bootstrap_options = c("condensed", "striped"))
}
```

_NOTE_: From a hierarchical perspective, the tables below only include the lowest level of the hierarchy (where applicable), e.g., the year- and population-specific quantity. See the next section for naming conventions for higher levels in the hierarchy.

## Indices

`r create_table("Indices")`

## Adult States

`r create_table("Adult States")`

## FW Juv States

`r create_table("FW Juv States")`

## SW Juv States

`r create_table("SW Juv States")`

## Survival

`r create_table("Survival")`

## Maturation

`r create_table("Maturation")`

## Recruitment Function

`r create_table("Recruitment Function")`

## Density-Dependent Survival

`r create_table("Density-Dependent Survival")`

## Data: FW Juv Survival

`r create_table("Data: FW Juv Survival")`

## Data: FW Juv Abundance

`r create_table("Data: FW Juv Abundance")`

## Data: Adult Abundance

`r create_table("Data: Adult Abundance")`

## Data: Adult Composition

`r create_table("Data: Adult Composition")`

# Higher-Level Conventions

For the hyper-distributions controlling the between-population and within-population mean and variances, here's one proposition using survival term for spring migration to LGD as an example.

*  The **mean across populations**
    * e.g., $\mu_{L\phi_{Mb \rightarrow Ma}}$ (`MU_Lphi_Mb_Ma`)
*  The **SD across populations**
    * e.g., $\sigma_{L\phi_{Mb \rightarrow Ma}}$ (`SIG_Lphi_Mb_Ma`)
*  The **mean across years within each population**
    * e.g., $\mu_{L\phi_{Mb \rightarrow Ma, j}}$ (`mu_Lphi_Mb_Ma[j]`)
*  The **SD across years within a population**
    * e.g., $\sigma_{L\phi_{Mb \rightarrow Ma, j}}$ (`sig_Lphi_Mb_Ma[j]`)

### 2020-07-17 99-admin/naming-conventions/names.Rmd
Edit naming-convention rmd root directory
This is for consistency with the rules - all paths should be relative to the project root

Also add in some more comments and context

@@
 
-```{r setup, include = F}
-knitr::opts_chunk$set(echo = F)
+```{r directories, include = F}
+# set root directory to the project directory: two levels up from this location
+knitr::opts_knit$set(root.dir = "../../")
+```
 
+```{r pkg-and-options, include = F}
 # load packages
-library(knitr)
-library(kableExtra)
+source("00-packages.R")
+
+# set global knitting options
+opts_chunk$set(echo = F)
 ```
@@
 # raw input file
-tab = read.csv("names.csv", allowEscapes = T, stringsAsFactors = F)
+tab = read.csv("99-admin/naming-conventions/names.csv", allowEscapes = T, stringsAsFactors = F)
 
@@
 
+# edit column names
 colnames(tab) = c("", "In Code", "Symbol", "Description", "Notes")
@@
 ```{r create-table-fun}
+# function to create a table based on the type of quantity
 create_table = function(group) {
@@
 See the next section for naming conventions for higher levels in the hierarchy.
+
+_NOTE_: The "code" column specifies how the variables/parameters will be referred to in the JAGS model code and post-processing code, not necessarily the same as the raw data or preparation of raw data code.
 

### 2020-09-04 99-admin/naming-conventions/names.Rmd
Edit naming conventions: text clarifications

@@
 *  $S$ is used for spawning adults
-*  $b$ is used to denote "before migration" 
-*  $a$ is used to denote "after migration"
+*  $b$ is used to denote "before event", generally migration from one location to another or a mortality source 
+*  $a$ is used to denote "after event"
 *  $\phi$ is used to denote a survival term, subscripts used to denote the from/to states
@@
 *  $L$ (uppercase) is used to denote that the quantity has been logit-tranformed, $l$ (lowercase) is used to denote that the quantity has been log-transformed.
-*  $y$ represents brood year fish were spawned; $t$ represents return year for adults
+*  $y$ represents brood year fish were spawned for all non-adult states. For adult states, it is the brood year in which they return
 

### 2020-09-09 00-packages.R
Create a function for quickly plotting time series
* Accepts posterior summary and observed data series
* Plots posterior median and 95% intervals as a time series
* Adds points
* depends on 'scales' package for transparent colors

@@ -4,3 +4,4 @@ library(reshape2)       # for reformatting data (e.g., long to wide); install.pa
 library(abind)          # for binding together array objects; install.packages("abind")
 library(jagsUI)         # for calling JAGS from R; install.packages("jagsUI")
 library(postpack)       # for processing posterior samples; remotes::install.packages("bstaton1/postpack")
+library(scales)         # for transparent colors in plots; install.packages("scales")

### 2020-09-09 01-functions/plot-fns.R

@@ -1,0 +1,43 @@
+# :::::::::::::::::::::::::::::::::::::::::::::::::: #
+# SCRIPT TO HOUSE FUNCTIONS FOR PLOTTING INFORMATION #
+# :::::::::::::::::::::::::::::::::::::::::::::::::: #
+
+##### PLOT A TIME SERIES OF ESTIMATES, WITH DATA IF AVAILABLE #####
+
+# est: output from postpack::post_summ()
+# obs: optional vector of observed data to plot on top of estimates
+# main: plot title
+# xaxis: plot the xaxis?
+# yaxis_side: 2 or 4 or NULL, where should the y-axis be placed?
+# set_par: set some par() options internally?
+
+plot_tseries = function(est, obs = NULL, main = NULL, xaxis = T, yaxis_side = 2, set_par = T) {
+  # extract year labels
+  yrs = as.numeric(names(obs))
+  
+  # set the graphics device parameters
+  if (set_par) par(mar = c(2,2,2,1), tcl = -0.2, mgp = c(2,0.3,0))
+  
+  # create empty plot with correct dimensions/labels
+  plot(1,1, type = "n", 
+       xlim = range(yrs), ylim = range(rbind(est[c("2.5%", "97.5%"),], obs), na.rm = T),
+       xlab = "", las = 1, ylab = "", main = main, xaxt = "n", yaxt = "n")
+  
+  # draw band representing 95% credible region
+  polygon(x = c(yrs, rev(yrs)), y = c(est["2.5%",], rev(est["97.5%",])), border = NA, col = alpha("salmon", 0.5))
+  lines(est["2.5%",] ~ yrs, col = "red", lty = 2)
+  lines(est["97.5%",] ~ yrs, col = "red", lty = 2)
+  
+  # draw posterior median
+  lines(est["50%",] ~ yrs, col = "red", lwd = 2)
+  
+  # draw data if provided
+  if (!is.null(obs)) points(obs ~ yrs, pch = 21, col = "blue", bg = alpha("skyblue2", 0.5), cex = 1.2)
+  
+  # draw axes/labels
+  if (xaxis) {
+    at_yrs = c(seq(min(yrs), max(yrs), 4), max(yrs))
+    axis(side = 1, at = at_yrs, labels = paste0("", substr(at_yrs, 3, 4)))
+  } 
+  if (!is.null(yaxis_side)) axis(side = yaxis_side)
+}

### 2020-09-09 03-post-process/output-plots.Rmd
Initial an Rmd file to create output plots for a single model fit

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: html_document
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
editor_options: 
  chunk_output_type: console
---

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "../")
```

```{r setup, include = FALSE}
# set global knitting options
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")

# load packages
source("00-packages.R")

# load all necessary functions
invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))

# set the input directory
in_dir = "02-model/model-output"

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output.rds")))

# extract the two key structures from this object
post = model_info$post
jags_data = model_info$jags_data

# which years are "observable"?
observable = (jags_data$kmax+1):jags_data$ny
```

The code used to render this output relies heavily on Staton's 'postpack' package (currently under CRAN review). Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.

### 2020-09-09 03-post-process/output-plots.Rmd
Include plots for fits to data
* abundance data,
* survival data,
* composition data

@@
 Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.
+
+# Fit to Data {.tabset .tabset-pills}
+
+In the figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
+
+## Abundance Data
+
+```{r abundance-data-fits, fig.width = 3, fig.height = 5}
+par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
+plot_tseries(post_summ(post, "^Mb[.+,2]$"), jags_data$Mb_obs[observable,2], main = "Spring Trap Abundance")
+plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Abundance")
+```
+
+## Survival Data
+
+```{r survival-data-fits, fig.width = 3, fig.height = 5}
+par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
+
+plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "Summer Tagging to LGD")
+plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "Fall Trap to LGD")
+plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2]), main = "Spring Trap to LGD")
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Survival")
+```
+
+## Composition Data
+
+```{r comp-data-fits, fig.width = 6, fig.height = 5}
+# calculate observed q
+q_obs = t(apply(jags_data$x_obs, 1, function(y) y/sum(y)))
+
+par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, "^q[.+,1]$"), q_obs[observable,1], main = "Female Age 3")
+plot_tseries(post_summ(post, "^q[.+,2]$"), q_obs[observable,2], main = "Female Age 4")
+plot_tseries(post_summ(post, "^q[.+,3]$"), q_obs[observable,3], main = "Female Age 5")
+plot_tseries(post_summ(post, "^q[.+,4]$"), q_obs[observable,4], main = "Male Age 3")
+plot_tseries(post_summ(post, "^q[.+,5]$"), q_obs[observable,5], main = "Male Age 4")
+plot_tseries(post_summ(post, "^q[.+,6]$"), q_obs[observable,6], main = "Male Age 5")
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+```

### 2020-09-09 03-post-process/output-plots.Rmd
Add a plot to display BH spawner to parr relationship
* Also, draw on fit of OLS regression fitted to reconstructed data.
* To create the uncertainty in this fit, depends on 'mvtnorm' package

@@
 ```
+
+# Spawner-to-Parr Relationship
+
+All red component are posterior summaries (medians and 95% credible intervals).
+The black curve is from an `nls()` fit on reconstructed parr and spawners -- the grey region is the confidence interval around this fit (from a parametric bootstrap).
+
+```{r spawners-to-parr, fig.width = 6, fig.height = 4}
+# extract posterior samples of the BH productivity and capacity parameters
+bh_params = post_subset(post, c("alpha", "beta"), matrix = T)
+
+# extract posterior summaries of total spawners by brood year
+Sa_tot = post_summ(post, "Sa_tot")
+
+# extract posterior summaries of total parr recruits by brood year
+Pb = post_summ(post, "^Pb[")
+
+# predict parr recruits along a sequence of spawner abundances
+Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
+Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(Sa_pred, bh_params[i,1], bh_params[i,2])))
+colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
+Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
+Pb_pred = post_summ(Pb_pred, "Pb_pred")
+
+# fit ordinary least squares version
+ols_fit = fit_basic_BH(jags_data)$BH_fit
+
+# draw 1000 random parameters
+ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
+
+# calculate predicted curve at each pair/summarize
+ols_R_pred = t(sapply(1:1000, function(i) BH(Sa_pred, ols_params[i,1], ols_params[i,2])))
+ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
+
+# graphical parameters
+par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
+
+# empty plot
+plot(1, 1, type = "n", xlim = range(0, Sa_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
+     xlab = "Spawners", ylab = "Parr Recruits")
+
+# draw fitted relationship: Bayesian
+polygon(c(Sa_pred, rev(Sa_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
+lines(Pb_pred[4,] ~ Sa_pred, col = "red", lty = 2)
+lines(Pb_pred[5,] ~ Sa_pred, col = "red", lty = 2)
+
+# draw fitted relationship: OLS
+polygon(c(Sa_pred, rev(Sa_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
+lines(ols_R_pred[1,] ~ Sa_pred, lwd = 2)
+lines(ols_R_pred[2,] ~ Sa_pred, lty = 2)
+lines(ols_R_pred[3,] ~ Sa_pred, lty = 2)
+lines(Pb_pred[3,] ~ Sa_pred, col = "red", lwd = 2)
+
+# draw state pairs + uncertainty
+segments(Sa_tot[4,], Pb[3,], Sa_tot[5,], Pb[3,], col = "red")
+segments(Sa_tot[3,], Pb[4,], Sa_tot[3,], Pb[5,], col = "red")
+points(Pb[3,] ~ Sa_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+```

### 2020-09-09 00-packages.R

@@ -5,3 +5,4 @@ library(abind)          # for binding together array objects; install.packages("
 library(jagsUI)         # for calling JAGS from R; install.packages("jagsUI")
 library(postpack)       # for processing posterior samples; remotes::install.packages("bstaton1/postpack")
 library(scales)         # for transparent colors in plots; install.packages("scales")
+library(mvtnorm)        # for sampling multivariate normal random variables; install.packages("mvtnorm")

### 2020-09-09 03-post-process/output-plots.Rmd
Create boxplots showing posteriors of hyperparameters
* across year mean survival, maturity, etc. parameters
* the among year logit-normal standard deviations

@@
 ```
+
+# Parameter Estimates {.tabset .tabset-pills}
+
+**Quick refresher on parameter names**
+_In alphabetical order, as displayed in figures_
+
+* `mu_omega[1]`: mean probability of being a female at ocean entry
+* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
+* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)
+* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
+* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
+* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
+* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)
+
+`sig_L*` are the among-year logit-normal standard deviations of these quantities. `sigma_Pb` is lognormal standard deviation of parr recruitment.
+
+## Means
+
+```{r mu-boxplots, fig.width = 6, fig.height = 6}
+# parameters to display
+keep = match_params(post, "mu")
+
+# remove redundant elements
+keep = keep[-which(keep %in% c("mu_init_recruits", "mu_omega[2]", "mu_phi_Mb_Ma[2]", "mu_pi[2]"))]
+
+# extract posterior samples of these parameters: for drawing initial box plot
+post_samples = post_subset(post, keep, T)
+
+# calculate custom summaries of these parameters: for drawing actual box plot
+post_summaries = post_summ(post, keep, probs = c(0.025, 0.25, 0.5, 0.75, 0.975))[-c(1:2),]
+
+# graphical parameters
+par(mar = c(8,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
+
+# set up a box plot and replace the stats with the custom stats
+bp = boxplot(post_samples, plot = F)
+bp$stats = post_summaries
+
+# draw the box plot
+bxp(bp, ylim = c(0,1), outline = F, las = 2, boxcol = "red", medcol = "red", whiskcol = "red", staplecol = "red", boxfill = alpha("salmon", 0.5))
+```
+
+## Standard Deviations
+
+```{r sig-boxplots, fig.width = 6, fig.height = 6}
+# parameters to display
+keep = match_params(post, "sig")
+
+# remove redundant elements
+keep = keep[-which(keep %in% c("sig_init_lrecruits", "sig_Lphi_Mb_Ma[2]"))]
+
+# extract posterior samples of these parameters: for drawing initial box plot
+post_samples = post_subset(post, keep, T)
+
+# calculate custom summaries of these parameters: for drawing actual box plot
+post_summaries = post_summ(post, keep, probs = c(0.025, 0.25, 0.5, 0.75, 0.975))[-c(1:2),]
+
+# graphical parameters
+par(mar = c(8,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
+
+# set up a box plot and replace the stats with the custom stats
+bp = boxplot(post_samples, plot = F)
+bp$stats = post_summaries
+
+# draw the box plot
+bxp(bp, ylim = c(0,max(post_summaries)), outline = F, las = 2, boxcol = "red", medcol = "red", whiskcol = "red", staplecol = "red", boxfill = alpha("salmon", 0.5))
+```

### 2020-09-09 03-post-process/output-plots.Rmd

@@
 Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.
+
+# MCMC Information {.tabset .tabset-pills}
+
+## Attributes
+
+This table shows some dimensions of the MCMC run.
+
+```{r mcmc-dims}
+# query the dimensions of the posterior samples
+dims = post_dim(post)
+
+# build a data frame for printing
+df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
+
+# render the table
+kable(df, format.args = list(big.mark = ",")) %>%
+  kable_styling(full_width = F, bootstrap_options = "condensed")
+```
+
+## Diagnostic Summaries
+
+This table shows the number of parameters that fail to meet some diagnostic threshold. Lower Rhat values are good, larger Neff values are good, and lower MCMC SE/Mean values are good.
+
+The "match" column shows the kinds of parameters summarized in that row.
+E.g., `^mu_phi` covers all parameter names that start with `mu_phi` and are followed by anything else (`r paste(match_params(post, "^mu_phi"), collapse = ", ")`).
+
+This model was ran for a very short time, and I'm impressed with how well the sampling performed even considering this.
+
+```{r mcmc-diags}
+# groups of parameters to match and calculate diagnostic summaries for separately
+diag_params = list(
+  c("alpha", "beta", "sigma_Pb"),
+  "^mu_phi",
+  "^mu_psi",
+  "^mu_omega",
+  "^mu_pi",
+  "^sig_Lphi",
+  "^sig_Lpsi",
+  c("^sig_Lomega", "^sig_Lpi"),
+  "^Pb[", 
+  "init_recruits", 
+  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
+)
+
+# calculate the diagnostic statistics for each group
+diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T, mcse = T)[c("mean", "Rhat", "neff", "mcse_mean"),])
+
+# count up the number of parameters by group that fail to meet certain thresholds
+diag_summ = t(sapply(diags, function(param) {
+  mc_cv = (param["mcse_mean",]/param["mean",]) * 100
+  c(
+    n_total = ncol(param),
+    n_Rhat_1 = sum(param["Rhat",] > 1.05),
+    n_Rhat_2 = sum(param["Rhat",] > 1.1),
+    n_Rhat_3 = sum(param["Rhat",] > 1.2),
+    n_neff_1 = sum(param["neff",] < 2000),
+    n_neff_2 = sum(param["neff",] < 1000),
+    n_neff_3 = sum(param["neff",] < 500),
+    mc_cv_1 = sum(mc_cv > 1),
+    mc_cv_2 = sum(mc_cv > 5),
+    mc_cv_3 = sum(mc_cv > 10)
+  )
+}))
+
+# format to a table
+diag_summ = as.data.frame(diag_summ)
+colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500", ">1%", ">5%", ">10%")
+df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)
+
+# render the table
+kable(df, align = "lcccccccccc") %>%
+  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
+  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3, "MCMC SE/Mean * 100%" = 3)) %>%
+  column_spec(1, monospace = T) %>%
+  column_spec(c(2,5,8), border_right = T)
+
+```
 

### 2020-09-24 03-post-process/output-plots.Rmd
Add plots displaying fit to pre-spawn data

@@
 
-The code used to render this output relies heavily on Staton's 'postpack' package (currently under CRAN review).
+The code used to render this output relies heavily on Staton's 'postpack' package (now available on CRAN).
 Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.
@@
 
+## Spawn Status Data
+
+```{r spawn-status-fits, fig.width = 3.5, fig.height = 5}
+par(oma = c(1.5,1.5,0,0))
+layout(matrix(c(1,2), 2, 1), heights = c(1, 0.65))
+plot_tseries(post_summ(post, "^phi_Sb_Sa["), with(jags_data, carcs_spawned/carcs_sampled)[observable], main = "Successful Spawning")
+mtext(side = 2, "Survival Probability", line = 1.5)
+
+at_x = seq(1, length(observable), 4)
+par(mar = c(2,2,0,1), yaxs = "i")
+mp = barplot(jags_data$carcs_sampled[observable], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
+axis(side = 1, at = mp[at_x], labels = substr( names(jags_data$carcs_sampled[observable]), 3, 4)[at_x])
+box()
+mtext(side = 2, "Carcasses Sampled", line = 1.5)
+mtext(side = 1, "Brood Year", line = 1.5)
+```
+
 # Spawner-to-Parr Relationship
 
-All red component are posterior summaries (medians and 95% credible intervals).
+All red components are posterior summaries (medians and 95% credible intervals).
 The black curve is from an `nls()` fit on reconstructed parr and spawners -- the grey region is the confidence interval around this fit (from a parametric bootstrap).

### 2020-09-24 03-post-process/output-plots.Rmd
Add MCMC diagnostic plots

@@
 
+```
+
+## Diagnostic Plots {.tabset .tabset-pills}
+
+### `alpha`, `beta`
+
+```{r alpha-beta-diag-plots, fig.width = 4, fig.height = 5}
+diag_plots(post, c("alpha", "beta"), layout = "2x1")
+```
+
+### `^mu`
+
+```{r mu-diag-plots, fig.width = 7, fig.height = 7}
+diag_plots(post, "^mu", layout = "5x3")
+```
+
+### `^sig`
+
+```{r sig-diag-plots, fig.width = 7, fig.height = 7}
+diag_plots(post, "^sig", layout = "5x3")
+```
+
+### `init_recruits`
+
+```{r init-recruits-diag-plots, fig.width = 5, fig.height = 7}
+diag_plots(post, "init_recruits", layout = "4x2")
 ```

### 2020-09-25 03-post-process/output-plots.Rmd
Add plots showing density-dependent relationship

@@
 
+# Overwinter Survival Relationships
+
+```{r overwinter-survival, fig.width = 4, fig.height = 7}
+
+# extract parr, scale it to PEU, and add to posterior samples
+Pa = post_subset(post, "^Pa[", matrix = T)
+Pa_scaled = Pa/jags_data$peu
+colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
+post = post_bind(post, Pa_scaled)
+
+# summarize posterior of scaled parr
+Pa_scaled_mean = array_format(post_summ(post, "Pa_scaled")["mean",])
+Pa_scaled_lwr = array_format(post_summ(post, "Pa_scaled")["2.5%",])
+Pa_scaled_upr = array_format(post_summ(post, "Pa_scaled")["97.5%",])
+
+# create vectors to predict survival at: for credible regions and mean curve
+Pa_scaled_seq = matrix(NA, 30, 2)
+Pa_scaled_seq[,1] = seq(min(Pa_scaled_lwr[,1], na.rm = T), max(Pa_scaled_upr[,1], na.rm = T), length = 30)
+Pa_scaled_seq[,2] = seq(min(Pa_scaled_lwr[,2], na.rm = T), max(Pa_scaled_upr[,2], na.rm = T), length = 30)
+
+# extract posteriors of coefficients
+gamma0 = post_subset(post, "gamma0", matrix = T)
+gamma1 = post_subset(post, "gamma1", matrix = T)
+
+# extract/format posterior summaries of realized survivals
+phi_Pa_Mb_mean = array_format(post_summ(post, "^phi_Pa_Mb[")["mean",])
+phi_Pa_Mb_lwr = array_format(post_summ(post, "^phi_Pa_Mb[")["2.5%",])
+phi_Pa_Mb_upr = array_format(post_summ(post, "^phi_Pa_Mb[")["97.5%",])
+
+# function to create predicted survival curves for one posterior sample
+f = function(i) {
+  pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
+  pred_phi_Pa_Mb2 = plogis(gamma0[i,2] + gamma1[i,2] * Pa_scaled_seq[,2])
+
+  names(pred_phi_Pa_Mb1) = paste0("pred_phi_Pa_Mb[", 1:30, ",1]")
+  names(pred_phi_Pa_Mb2) = paste0("pred_phi_Pa_Mb[", 1:30, ",2]")
+
+  c(pred_phi_Pa_Mb1, pred_phi_Pa_Mb2)
+}
+
+# calculate predicted survivals and add to posterior samples
+pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), f))
+post = post_bind(post, pred_phi_Pa_Mb)
+
+# summarize predicted survivals
+pred_phi_Pa_Mb_mean = array_format(post_summ(post, "pred_phi_Pa_Mb")["mean",])
+pred_phi_Pa_Mb_lwr = array_format(post_summ(post, "pred_phi_Pa_Mb")["2.5%",])
+pred_phi_Pa_Mb_upr = array_format(post_summ(post, "pred_phi_Pa_Mb")["97.5%",])
+
+# function to draw plot for one LH-type
+plot_fun = function(i) {
+  # blank plot of correct dimensions
+  plot(1,1, type = "n", 
+       ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i], phi_Pa_Mb_upr[,i], na.rm = T),
+       xlim = range(0, Pa_scaled_seq), 
+       main = c("Fall Migrants", "Spring Migrants")[i]
+  )
+
+  # expected relationship
+  polygon(c(Pa_scaled_seq[,i], rev(Pa_scaled_seq[,i])), c(pred_phi_Pa_Mb_lwr[,i], rev(pred_phi_Pa_Mb_upr[,i])), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_phi_Pa_Mb_lwr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
+  lines(pred_phi_Pa_Mb_upr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
+  lines(pred_phi_Pa_Mb_mean[,i] ~ Pa_scaled_seq[,i], col = "red", lwd = 2)
+
+  # realized survivals
+  segments(Pa_scaled_lwr[,i], phi_Pa_Mb_mean[,i], Pa_scaled_upr[,i], phi_Pa_Mb_mean[,i], col = alpha("red", 0.5))
+  segments(Pa_scaled_mean[,i], phi_Pa_Mb_lwr[,i], Pa_scaled_mean[,i], phi_Pa_Mb_upr[,i], col = alpha("red", 0.5))
+  points(phi_Pa_Mb_mean[,i] ~ Pa_scaled_mean[,i], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+}
+
+# create the plot
+par(mfrow = c(2,1), mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1), oma = c(2,2,0,0))
+plot_fun(1)
+plot_fun(2)
+mtext(side = 1, line = 1, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
+mtext(side = 2, line = 1, outer = T, "Overwinter Survival", cex = 1.2)
+```
+
 # Parameter Estimates {.tabset .tabset-pills}

### 2020-09-26 03-post-process/output-plots.Rmd

@@
   c("alpha", "beta", "sigma_Pb"),
+  "gamma",
   "^mu_phi",
@@
 diag_plots(post, c("alpha", "beta"), layout = "2x1")
+```
+
+### `gamma`
+
+```{r gamma-diag-plots, fig.width = 3, fig.height = 6}
+diag_plots(post, "gamma", layout = "4x1")
 ```

### 2020-10-15 02-model/fit-model.R
Implement correction factor in fit-model.R
* create dummy variables for age/sex
* track nodes z , carc_adj, q_Ra, and q_Sa_adj

@@ -16,13 +16,13 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 # set the output directory: if it doesn't exist, a new directory will be created
 out_dir = "02-model/model-output"
 
-##### STEP 1: PREPARE DATA FOR JAGS #####
 
 # select the population to fit
 # pop = "UGR"
 # pop = "CAT"
 # pop = "MIN"  # don't do this one yet, the data prep steps (for age comp mostly) aren't correct for MIN
 pop = "LOS"
+##### STEP 1: PREPARE DATA FOR JAGS #####
 
 # build JAGS data object
 jags_data = create_jags_data_one(pop)
@@ -34,7 +34,16 @@ add_jags_data = list(
   mu_phi_O1_O2 = 0.8,   # survival from SWA1 to SWA2
   mu_phi_O2_O3 = 0.8,   # survival from SWA2 to SWA3
   mu_phi_Rb_Ra = 0.7   # survival upstream as adults in-river. mortality sources: sea lions, fishery, hydrosystem
+  mu_phi_Rb_Ra = 0.7    # survival upstream as adults in-river. mortality sources: sea lions, fishery, hydrosystem
 )
+
+# some dummy variables for performing weir vs. carcass composition correction
+add_jags_data2 = list(
+  age3 = c(1,0,0),      # is each k age 3? 1 = yes; 0 = no
+  age5 = c(0,0,1),      # is each k age 5?
+  male = c(0,1)         # is each s male?
+)
+add_jags_data = append(add_jags_data, add_jags_data2)
 
 # calculate the upper bound on initial adult recruits and add to data
 add_jags_data = append(add_jags_data, list(max_init_recruits = max(jags_data$Ra_obs/(add_jags_data$mu_phi_Rb_Ra) * 1.5, na.rm = T)))
@@ -77,6 +86,10 @@ jags_params = c(
   # states
   "Pb", "Pa", "Mb", "Ma", "M", "O", "Rb",
   "Ra", "Sb", "Sa", "q", "Sa_tot", "Ra_tot"
+  "Ra", "Sb", "Sa", "q_Ra", "q_Sa_adj", "Sa_tot", "Ra_tot",
+  
+  # carcass vs. weir correction
+  "z", "carc_adj"
 )
 
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####

### 2020-10-15 03-post-process/output-plots.Rmd
Update fit plots for composition data

@@
 
-## Composition Data
+## Composition Data {.tabset .tabset-pills .tabset-fade}
 
-```{r comp-data-fits, fig.width = 6, fig.height = 5}
+Within a single year, the values across all panels sum to one.
+
+### Weir Sampling
+
+```{r weir-comp-data-fits, fig.width = 8, fig.height = 5}
 # calculate observed q
-q_obs = t(apply(jags_data$x_obs, 1, function(y) y/sum(y)))
+q_obs = t(apply(jags_data$weir_x_obs, 1, function(y) y/sum(y)))
 
-par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^q[.+,1]$"), q_obs[observable,1], main = "Female Age 3")
-plot_tseries(post_summ(post, "^q[.+,2]$"), q_obs[observable,2], main = "Female Age 4")
-plot_tseries(post_summ(post, "^q[.+,3]$"), q_obs[observable,3], main = "Female Age 5")
-plot_tseries(post_summ(post, "^q[.+,4]$"), q_obs[observable,4], main = "Male Age 3")
-plot_tseries(post_summ(post, "^q[.+,5]$"), q_obs[observable,5], main = "Male Age 4")
-plot_tseries(post_summ(post, "^q[.+,6]$"), q_obs[observable,6], main = "Male Age 5")
+par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, "^q_Ra[.+,1]$"), q_obs[observable,1], main = "Nat. Female Age 3")
+plot_tseries(post_summ(post, "^q_Ra[.+,2]$"), q_obs[observable,2], main = "Nat. Female Age 4")
+plot_tseries(post_summ(post, "^q_Ra[.+,3]$"), q_obs[observable,3], main = "Nat. Female Age 5")
+plot_tseries(post_summ(post, "^q_Ra[.+,4]$"), q_obs[observable,4], main = "Nat. Male Age 3")
+plot_tseries(post_summ(post, "^q_Ra[.+,5]$"), q_obs[observable,5], main = "Nat. Male Age 4")
+plot_tseries(post_summ(post, "^q_Ra[.+,6]$"), q_obs[observable,6], main = "Nat. Male Age 5")
+plot_tseries(post_summ(post, "^q_Ra[.+,7]$"), q_obs[observable,7], main = "Hat. Female Age 3")
+plot_tseries(post_summ(post, "^q_Ra[.+,8]$"), q_obs[observable,8], main = "Hat. Female Age 4")
+plot_tseries(post_summ(post, "^q_Ra[.+,9]$"), q_obs[observable,9], main = "Hat. Female Age 5")
+plot_tseries(post_summ(post, "^q_Ra[.+,10]$"), q_obs[observable,10], main = "Hat. Male Age 3")
+plot_tseries(post_summ(post, "^q_Ra[.+,11]$"), q_obs[observable,11], main = "Hat. Male Age 4")
+plot_tseries(post_summ(post, "^q_Ra[.+,12]$"), q_obs[observable,12], main = "Hat. Male Age 5")
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+```
+
+### Carcass Sampling
+
+```{r carc-comp-data-fits, fig.width = 8, fig.height = 5}
+# calculate observed q
+q_obs = t(apply(jags_data$carc_x_obs, 1, function(y) y/sum(y)))
+
+par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,1]$"), q_obs[observable,1], main = "Nat. Female Age 3")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,2]$"), q_obs[observable,2], main = "Nat. Female Age 4")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,3]$"), q_obs[observable,3], main = "Nat. Female Age 5")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,4]$"), q_obs[observable,4], main = "Nat. Male Age 3")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,5]$"), q_obs[observable,5], main = "Nat. Male Age 4")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,6]$"), q_obs[observable,6], main = "Nat. Male Age 5")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,7]$"), q_obs[observable,7], main = "Hat. Female Age 3")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,8]$"), q_obs[observable,8], main = "Hat. Female Age 4")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,9]$"), q_obs[observable,9], main = "Hat. Female Age 5")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,10]$"), q_obs[observable,10], main = "Hat. Male Age 3")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,11]$"), q_obs[observable,11], main = "Hat. Male Age 4")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,12]$"), q_obs[observable,12], main = "Hat. Male Age 5")
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")

### 2020-10-20 03-post-process/output-plots.Rmd
Add new parameters to output plots

@@
   "init_recruits", 
-  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
+  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
+  "^phi_Mb_M["
 )
@@
 plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
-plot_tseries(post_summ(post, "^Mb[.+,2]$"), jags_data$Mb_obs[observable,2], main = "Spring Trap Abundance")
+plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = "Spring Trap Abundance")
 plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
@@
 * `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
+* `mu_phi_Mb_M`: mean probability of surviving from hatchery release in spring to estuary (hatchery fish)
 * `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)

### 2020-10-20 03-post-process/output-plots.Rmd
Add rmd option to turn off drawing mcmc diagnostic plots

@@
     choices: [CAT, LOS, UGR]
+  mcmc_plots:
+    label: "Make MCMC Plots"
+    input: checkbox
+    value: FALSE
 editor_options: 
@@
 
-## Diagnostic Plots {.tabset .tabset-pills}
+`r if (params$mcmc_plots) "## Diagnostic Plots {.tabset .tabset-pills}"`
 
-### `alpha`, `beta`
+`r if (params$mcmc_plots) "### $\\alpha$, $\\beta$"`
 
-```{r alpha-beta-diag-plots, fig.width = 4, fig.height = 5}
+```{r alpha-beta-diag-plots, eval = params$mcmc_plots, fig.width = 4, fig.height = 5}
 diag_plots(post, c("alpha", "beta"), layout = "2x1")
@@
 
-### `gamma`
+`r if (params$mcmc_plots) "### $\\gamma$"`
 
-```{r gamma-diag-plots, fig.width = 3, fig.height = 6}
+```{r gamma-diag-plots, eval = params$mcmc_plots, fig.width = 3, fig.height = 6}
 diag_plots(post, "gamma", layout = "4x1")
@@
 
-### `^mu`
+`r if (params$mcmc_plots) "### $\\mu$"`
 
-```{r mu-diag-plots, fig.width = 7, fig.height = 7}
+```{r mu-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
 diag_plots(post, "^mu", layout = "5x3")
@@
 
-### `^sig`
+`r if (params$mcmc_plots) "### $$\\sigma$"`
 
-```{r sig-diag-plots, fig.width = 7, fig.height = 7}
+```{r sig-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
 diag_plots(post, "^sig", layout = "5x3")
@@
 
-### `init_recruits`
+`r if (params$mcmc_plots) "### init_recruits"`
 
-```{r init-recruits-diag-plots, fig.width = 5, fig.height = 7}
+```{r init-recruits-diag-plots, eval = params$mcmc_plots, fig.width = 5, fig.height = 7}
 diag_plots(post, "init_recruits", layout = "4x2")

### 2020-10-20 02-model/fit-model.R

@@ -22,6 +22,7 @@ out_dir = "02-model/model-output"
 args = commandArgs(trailingOnly = T)
 pop = args[1]
 rmd = as.logical(args[2])
+rmd_mcmc_plots = T
 
 # if pop not supplied, set a value and warn
 if (is.na(pop)) {
@@ -196,7 +197,7 @@ if (rmd) {
   setwd("03-post-process")
   rmarkdown::render(input = "output-plots.Rmd",
                     output_file = paste0(pop, "-output-plots.html"), 
-                    params = list(pop = pop), 
+                    params = list(pop = pop, mcmc_plots = rmd_mcmc_plots), 
                     quiet = T
   )
   setwd("../")

### 2020-10-20 03-post-process/output-plots.Rmd
Add smolt-to-adult return rate plot

@@
 
+# Smolt-to-Adult Rates
+
+This is survival from $Mb$ (smolts in tributary, prior to mortality associated with movement to LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
+
+The adult part is calculated across return years, by summing the number of adults of each age (regardless of sex) that return in the appropriate years.
+For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
+The calculation is done for hatchery and natural origin fish separately.
+Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
+
+Other SARS could be calculated, but currently this is the only one that is comparable between hatchery and natural origins.
+
+```{r}
+# function to calculate posterior 
+get_SAR_post = function(post, jags_data) {
+  # extract posterior abundances
+  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
+  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring
+
+  # number of saved samples
+  ni = post_dim(post, "saved")
+
+  # first and last brood year SAR can be calculated for
+  first_SAR_y = jags_data$kmax + 1
+  last_SAR_y = jags_data$ny - jags_data$kmax
+
+  # containers
+  nat_SAR = hat_SAR = NULL
+
+  # loop over mcmc iters
+  for (i in 1:ni) {
+    # extract quantities for this iter
+    Ra = array_format(Ra_post[i,])
+    Mb = array_format(Mb_post[i,])
+
+    # give names
+    dimnames(Ra) = dimnames(jags_data$p_remove)
+    dimnames(Mb) = dimnames(jags_data$Mb_obs)
+
+    # drop sex structure from Ra
+    Ra = Ra[,,1,] + Ra[,,2,]
+
+    # loop over years
+    nat_SAR_i = hat_SAR_i = NULL
+    for (y in first_SAR_y:last_SAR_y) {
+      # sum up smolts across life history types
+      nat_smolt = sum(Mb[y,,"Nat"])
+      hat_smolt = sum(Mb[y,,"Hat"], na.rm = T)
+
+      # sum up returing adults from this brood
+      nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
+      hat_adults = Ra[y+3,1,"Hat"] + Ra[y+4,2,"Hat"] + Ra[y+5,3,"Hat"]
+
+      nat_SAR_i = c(nat_SAR_i, nat_adults/nat_smolt)
+      hat_SAR_i = c(hat_SAR_i, hat_adults/hat_smolt)
+    }
+
+    # combine with other mcmc iters
+    nat_SAR = rbind(nat_SAR, nat_SAR_i)
+    hat_SAR = rbind(hat_SAR, hat_SAR_i)
+  }
+
+  colnames(nat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",1]")
+  colnames(hat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",2]")
+
+  # drop out SAR years for hatchery fish where missing
+  hat_SAR = hat_SAR[,!is.na(colSums(hat_SAR))]
+
+  out = cbind(nat_SAR, hat_SAR)
+  return(out)
+}
+
+# apply the function
+SAR_post = get_SAR_post(post, jags_data)
+
+# combine samples with main posterior object
+post = post_bind(post, SAR_post)
+
+# calculate/format posterior summaries
+SAR_mean = array_format(post_summ(post, "SAR")["mean",]) * 100
+SAR_lwr = array_format(post_summ(post, "SAR")["2.5%",]) * 100
+SAR_upr = array_format(post_summ(post, "SAR")["97.5%",]) * 100
+
+# subset years
+all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
+SAR_yrs = all_yrs[1:nrow(SAR_mean)]
+
+# graphics device
+par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.2)
+
+# blank plot with appropriate dimensions
+plot(SAR_mean[,1] ~ SAR_yrs, ylab = "Adults/100 Smolt", xlab = "Brood Year",
+     xlim = range(all_yrs), ylim = c(0, max(SAR_upr, na.rm = T)), type = "n", las = 1)
+
+# draw posterior summary for natural origin
+polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,1], rev(SAR_upr[,1])), col = alpha("skyblue2", 0.5), border = NA)
+lines(SAR_lwr[,1] ~ SAR_yrs, col = "blue", lty = 2)
+lines(SAR_upr[,1] ~ SAR_yrs, col = "blue", lty = 2)
+lines(SAR_mean[,1] ~ SAR_yrs, col = "blue", lwd = 2)
+
+# draw posterior summary for hatchery origin
+polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,2], rev(SAR_upr[,2])), col = alpha("salmon", 0.5), border = NA)
+lines(SAR_lwr[,2] ~ SAR_yrs, col = "red", lty = 2)
+lines(SAR_upr[,2] ~ SAR_yrs, col = "red", lty = 2)
+lines(SAR_mean[,2] ~ SAR_yrs, col = "red", lwd = 2)
+
+# draw a legend
+legend("topright", legend = c("Natural", "Hatchery"), title = "Origin",
+       pch = 22, col = c("blue", "red"), pt.cex = 2, pt.bg = alpha(c("skyblue2", "salmon"), 0.5), bty = "n")
+```
+
 # Parameter Estimates {.tabset .tabset-pills}

### 2020-10-21 03-post-process/output-plots.Rmd
Add some numerical summaries to output plots

@@
 subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
-output: html_document
+output: 
+  html_document:
+    toc: true
+    toc_float: true
 params:
@@
 ```
+
+# Numerical Summaries
+
+## Recruitment Function
+
+```{r}
+# extract posterior summaries
+alpha_summ = post_summ(post, "alpha", digits = 0)
+beta_summ = post_summ(post, "beta", digits = -3)
+sigma_summ = post_summ(post, "sigma_Pb", digits = 2)
+
+# create/format the table
+tab = cbind(alpha_summ, beta_summ, sigma_summ)
+colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\sigma_{Pb}$")
+
+# produce html table
+kable(tab, format.args = list(big.mark = ","), escape = F) %>%
+  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
+  column_spec(1, bold = T)
+```
+
+## Carcass Correction Factors
+
+```{r}
+# extract posterior summaries
+carc_adj = post_summ(post, "carc_adj", digits = 1)
+
+# create/format table
+x = paste0(carc_adj["mean",], " (", carc_adj["2.5%",], " -- ", carc_adj["97.5%",], ")")
+names(x) = colnames(carc_adj)
+tab = array_format(x)
+colnames(tab) = c("Female", "Male")
+rownames(tab) = c("Age 3", "Age 4", "Age 5")
+
+# produce html table
+kable(tab) %>%
+  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
+  column_spec(1, bold = T)
+```

### 2020-10-21 01-functions/data-fns.R
Delete all references to p_HOR
Not needed any more

@@ -163,18 +163,6 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   weir_x_obs[y_names %in% sub$brood_year,] = as.matrix(cbind(nat_comp, hat_comp))
   weir_nx_obs = rowSums(weir_x_obs)
   
-  ### PERCENT OF HATCHERY ORIGIN RETURN ###
-  # used to expand natural origin adult returns to obtain
-  # done on an age/sex structured basis
-  nat_comp = as.matrix(nat_comp)
-  hat_comp = as.matrix(hat_comp)
-  p_HOR = array(NA, c(ny, nk, ns)); dimnames(p_HOR) = list(y_names, k_names, s_names)
-  p_HOR[y_names %in% sub$brood_year,,1] = hat_comp[,1:nk]/(hat_comp[,1:nk] + nat_comp[,1:nk]) 
-  p_HOR[y_names %in% sub$brood_year,,2] = hat_comp[,(nk+1):(2*nk)]/(hat_comp[,(nk+1):(2*nk)] + nat_comp[,(nk+1):(2*nk)]) 
-  p_HOR[is.na(p_HOR)] = 0
-  p_HOR[p_HOR == 0] = 0.01  # needed to explain some carcass counts of hatchery fish in early years
-  p_HOR[p_HOR == 1] = 0.95  # needed to allow some natural fish to be present even though they weren't sampled at weir
-  
   ### ADULT AGE COMP: CARCASSES ###
   # obtain names of age comp variables
   carc_comp_names = create_comp_names("carc", o_names, s_names, k_names)
@@ -292,9 +280,6 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
     carc_x_obs = carc_x_obs,
     carc_nx_obs = carc_nx_obs,   # multinomial sample size
     
-    # proportion of hatchery origin returns
-    p_HOR = p_HOR,
-    
     # number of carcasses sampled for spawn status
     carcs_sampled = carcs_sampled,
     
@@ -370,9 +355,6 @@ create_jags_data_mult = function(pops, first_y = 1991, last_y = 2019) {
     
     # broodstock removals
     p_remove = abind(lapply(main_list, function(x) x$p_remove), along = 5),
-    
-    # proportion of hatchery origin returns
-    p_HOR = abind(lapply(main_list, function(x) x$p_HOR), along = 4),
     
     # number of carcasses sampled for spawn status
[…]

### 2020-10-27 03-post-process/output-plots.Rmd

@@
 
-`r if (params$mcmc_plots) "### $$\\sigma$"`
+`r if (params$mcmc_plots) "### $\\sigma$"`
 
@@
 diag_plots(post, "init_recruits", layout = "4x2")
+```
+
+`r if (params$mcmc_plots) "### stray"`
+
+_There are some elements of both `n_stray_tot` and `stray_comp` that are exactly zero each MCMC iteration. These are omitted from the plots below._
+
+```{r stray-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
+stray = post_subset(post, "stray", T)
+non_zero_stray = apply(stray, 2, function(x) all(x != 0))
+stray_nodes = names(non_zero_stray)[non_zero_stray]
+diag_plots(post, stray_nodes, layout = "5x3")
 ```
@@
 
-```{r}
+```{r sar-plot}
 # function to calculate posterior 
@@
 
+SAR_mean[SAR_mean == "Inf"] = NA
+SAR_lwr[SAR_lwr == "Inf"] = NA
+SAR_upr[SAR_upr == "Inf"] = NA
+
 # subset years
@@
        pch = 22, col = c("blue", "red"), pt.cex = 2, pt.bg = alpha(c("skyblue2", "salmon"), 0.5), bty = "n")
+```
+
+# Number of Strays
+
+```{r stray-tot-plot}
+par(oma = c(1,1,0,0))
+plot_tseries(post_summ(post, "n_stray_tot"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
+mtext(side = 1, outer = T, line = -0.5, "Return Year")
+mtext(side = 2, outer = T, line = 0, "Number of Strays")
 ```

### 2020-11-19 03-post-process/output-plots.Rmd
Updates to output plots Rmd source
* drop deleted parameter from diagnostics: phi_Mb_M
* Add a fit plot for survival of hatchery fish to LGD
* Recalculate  SARS to be from LGD to trib

@@
   "init_recruits", 
-  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
-  "^phi_Mb_M["
+  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
 )
@@
 
-```{r survival-data-fits, fig.width = 3, fig.height = 5}
-par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
+```{r survival-data-fits, fig.width = 3, fig.height = 6}
+par(mfcol = c(4,1), oma = c(1.5,1.5,0,0))
 
-plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "Summer Tagging to LGD")
-plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "Fall Trap to LGD")
-plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2]), main = "Spring Trap to LGD")
+plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "(Nat) Summer Tagging to LGD")
+plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "(Nat) Fall Trap to LGD")
+plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = "(Nat) Spring Trap to LGD")
+plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 
-This is survival from $Mb$ (smolts in tributary, prior to mortality associated with movement to LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
+This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
 
@@
 
-Other SARS could be calculated, but currently this is the only one that is comparable between hatchery and natural origins.
-
 ```{r sar-plot}
@@
   # extract posterior abundances
-  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
-  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring
+  Ra_post = post_subset(post, "^Ra[", T) # adults returning to Columbia River mouth
+  Ma_post = post_subset(post, "^Ma[", T) # smolts at top of LGD
 
@@
     Ra = array_format(Ra_post[i,])
-    Mb = array_format(Mb_post[i,])
+    Ma = array_format(Ma_post[i,])
 
@@
     dimnames(Ra) = dimnames(jags_data$p_remove)
-    dimnames(Mb) = dimnames(jags_data$Mb_obs)
+    dimnames(Ma) = dimnames(jags_data$Mb_obs)
 
@@
       # sum up smolts across life history types
-      nat_smolt = sum(Mb[y,,"Nat"])
-      hat_smolt = sum(Mb[y,,"Hat"], na.rm = T)
+      nat_smolt = sum(Ma[y,,"Nat"])
+      hat_smolt = sum(Ma[y,,"Hat"])
 
-      # sum up returing adults from this brood
+      # sum up returning adults from this brood
       nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
@@
 * `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
-* `mu_phi_Mb_M`: mean probability of surviving from hatchery release in spring to estuary (hatchery fish)
-* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)
+* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)
 * `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)

### 2020-11-20 03-post-process/output-plots.Rmd
Output plots: create fit plots for hydro survival data

@@
 
-```{r survival-data-fits, fig.width = 3, fig.height = 6}
-par(mfcol = c(4,1), oma = c(1.5,1.5,0,0))
+```{r survival-data-fits, fig.width = 5, fig.height = 6}
+par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
 
@@
 plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
+plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = "(Nat) LGD to BON")
+plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = "(Hat) LGD to BON")
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")

### 2020-11-20 03-post-process/output-plots.Rmd
Build in structure for scenario names
This will facilitate comparing different parameterizations of ocean survival and other things down the road

@@
     choices: [CAT, LOS, UGR]
+  scenario:
+    label: "Scenario"
+    value: base
+    input: text
   mcmc_plots:
@@
 # read information from this model
-model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output.rds")))
+model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output-", params$scenario, ".rds")))
 

### 2020-11-20 02-model/fit-model.R

@@ -16,6 +16,9 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 # set the output directory: if it doesn't exist, a new directory will be created
 out_dir = "02-model/model-output"
 
+# specify a scenario name
+scenario = "base"
+
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
 # or if in interactive session, uncomment the pop you wish to fit
@@ -198,11 +201,12 @@ if (!dir.exists(out_dir)) dir.create(out_dir)
 out_obj = list(
   jags_data = jags_data,
   post = post,
-  pop = pop
+  pop = pop,
+  scenario = scenario
 )
 
 # create the output file name
-out_file = paste0(pop, "-output.rds")
+out_file = paste0(pop, "-output-", scenario, ".rds")
 
 # save the file
 cat("\nSaving rds Output")
@@ -213,8 +217,8 @@ if (rmd) {
   cat("\nRendering Rmd Output")
   setwd("03-post-process")
   rmarkdown::render(input = "output-plots.Rmd",
-                    output_file = paste0(pop, "-output-plots.html"), 
-                    params = list(pop = pop, mcmc_plots = rmd_mcmc_plots), 
+                    output_file = paste0(pop, "-output-plots-", scenario, ".html"), 
+                    params = list(pop = pop, scenario = scenario, mcmc_plots = rmd_mcmc_plots), 
                     quiet = T
   )
   setwd("../")

### 2020-11-20 03-post-process/output-plots.Rmd
Output plots: delete calculation of MCSE in diagnostics
This was causing some crashes with the error: result would be too long a vector. It is related to the mcmcse package somewhere. We are mostly concerned with Rhat and Neff anyways

@@
 # calculate the diagnostic statistics for each group
-diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T, mcse = T)[c("mean", "Rhat", "neff", "mcse_mean"),])
+diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T)[c("mean", "Rhat", "neff"),])
 
@@
 diag_summ = t(sapply(diags, function(param) {
-  mc_cv = (param["mcse_mean",]/param["mean",]) * 100
   c(
@@
     n_neff_2 = sum(param["neff",] < 1000),
-    n_neff_3 = sum(param["neff",] < 500),
-    mc_cv_1 = sum(mc_cv > 1),
-    mc_cv_2 = sum(mc_cv > 5),
-    mc_cv_3 = sum(mc_cv > 10)
+    n_neff_3 = sum(param["neff",] < 500)
   )
@@
 diag_summ = as.data.frame(diag_summ)
-colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500", ">1%", ">5%", ">10%")
+colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500")
 df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)
@@
 # render the table
-kable(df, align = "lcccccccccc") %>%
+kable(df, align = "lccccccc") %>%
   kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
-  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3, "MCMC SE/Mean * 100%" = 3)) %>%
+  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3)) %>%
   column_spec(1, monospace = T) %>%
-  column_spec(c(2,5,8), border_right = T)
+  column_spec(c(2,5), border_right = T)
 

### 2020-11-21 02-model/fit-model.R
Add placeholders for ocean survival that will be estimated in future versions

@@ -57,10 +57,10 @@ jags_data = append_no_na_indices(jags_data)
 # some parameters we are assuming known (for now)
 # [1] is natural, [2] is hatchery origin
 add_jags_data = list(
-  mu_phi_M_O1 = c(0.2, 0.2),    # survival from arrival to estuary to next spring (become SWA1)
-  mu_phi_O1_O2 = c(0.8, 0.8),   # survival from SWA1 to SWA2
-  mu_phi_O2_O3 = c(0.8, 0.8),   # survival from SWA2 to SWA3
-  mu_phi_Rb_Ra = c(0.7, 0.7)    # survival upstream as adults in-river. mortality sources: sea lions, fishery, hydrosystem
+  mu_phi_M_O1_assume = c(0.2, 0.2),    # survival from arrival to estuary to next spring (become SWA1)
+  mu_phi_O1_O2_assume = c(0.8, 0.8),   # survival from SWA1 to SWA2
+  mu_phi_O2_O3_assume = c(0.8, 0.8),   # survival from SWA2 to SWA3
+  mu_phi_Rb_Ra_assume = c(0.7, 0.7)    # survival upstream as adults in-river. mortality sources: sea lions, fishery, hydrosystem
 )
 
 # some dummy variables for performing weir vs. carcass composition correction
@@ -125,14 +125,17 @@ jags_params = c(
   # hyperparameters: central tendency
   "mu_pi", "mu_phi_Mb_Ma", "mu_phi_Ma_M",
   "mu_omega", "mu_psi_O1_Rb", "mu_psi_O2_Rb", "mu_phi_Sb_Sa",
+  "mu_phi_M_O1", "mu_phi_O1_O2", "mu_phi_O2_O3",
   
   # hyperparameters: inter-annual sd
   "sig_Lpi", "sig_Lphi_Pa_Mb", "sig_Lphi_Mb_Ma", "sig_Lphi_Ma_M",
   "sig_Lomega", "sig_Lpsi_O1_Rb", "sig_Lpsi_O2_Rb", "sig_Lphi_Sb_Sa",
+  "sig_Lphi_M_O1", "sig_Lphi_O1_O2", "sig_Lphi_O2_O3",
   
   # year-specific parameters
   "pi", "phi_Pa_Mb", "phi_Mb_Ma", "phi_Ma_M", "omega", 
   "psi_O1_Rb", "psi_O2_Rb", "phi_Sb_Sa",
[…]

### 2020-11-21 02-model/model-code.R

@@ -54,9 +54,17 @@ jags_model_code = function() {
     sig_Lomega[o] ~ dunif(0, 5)
   }
   
-  # sex/origin-specific maturation probabilities
-  for (s in 1:ns) {
-    for (o in 1:no) {
+  for (o in 1:no) {
+    # origin/age-specific ocean survival
+    mu_phi_M_O1[o] <- mu_phi_M_O1_assume[o]    # first winter at sea: to become SWA1
+    mu_phi_O1_O2[o] <- mu_phi_O1_O2_assume[o]   # second winter at sea: to become SWA2
+    mu_phi_O2_O3[o] <- mu_phi_O2_O3_assume[o]   # third winter at sea: to become SW3
+    sig_Lphi_M_O1[o] <- 0
+    sig_Lphi_O1_O2[o] <- 0
+    sig_Lphi_O2_O3[o] <- 0
+    
+    # sex/origin-specific maturation probabilities
+    for (s in 1:ns) {
       # pr(return at SWA1)
       mu_psi_O1_Rb[s,o] ~ dbeta(1, 1)     
       sig_Lpsi_O1_Rb[s,o] ~ dunif(0, 5)
@@ -129,7 +137,7 @@ jags_model_code = function() {
       phi_O2_O3[y,o] <- mu_phi_O2_O3[o]
       
       # upstream adult survival
-      phi_Rb_Ra[y,o] <- mu_phi_Rb_Ra[o]
+      phi_Rb_Ra[y,o] <- mu_phi_Rb_Ra_assume[o]
     }
     
     # pre-spawn survival

### 2020-11-21 03-post-process/output-plots.Rmd
Output plots: add time series plots for ocean survival, sex apportionment, and maturity

@@
 
+# Ocean Survival
+
+```{r ocean-surv-plots, fig.width = 4, fig.height = 6}
+par(mfrow = c(3,2), oma = c(1,1,0,0))
+plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = "BON -> O1 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = "BON -> O1 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = "O1 -> O2 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$"), main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$"), main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Survival")
+```
+
+# Sex Apportionment
+
+```{r sex-plots, fig.width = 7, fig.height = 4}
+par(mfrow = c(1,2), oma = c(1,1,0,0))
+plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Female Proportion of Esutary Smolts")
+```
+
+# Maturity
+
+```{r maturity-plots, fig.width = 4, fig.height = 7}
+par(mfrow = c(4,2), oma = c(1,1,0,0))
+plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,1]$"), main = "Age 3 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,2]$"), main = "Age 3 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,1]$"), main = "Age 3 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,2]$"), main = "Age 3 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,1]$"), main = "Age 4 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,2]$"), main = "Age 4 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,1]$"), main = "Age 4 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,2]$"), main = "Age 4 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Pr(Mature-at-Age|Alive in Ocean)")
+
+```
+
 # Parameter Estimates {.tabset .tabset-pills}

### 2020-12-16 02-model/model-code.R
Estimate scalers between hat and nat ocean survival rather than these independtly

@@ -54,14 +54,22 @@ jags_model_code = function() {
     sig_Lomega[o] ~ dunif(0, 5)
   }
   
+  # origin/age-specific ocean survival
+  surv_scaler_M_O1 ~ dt(0, 1/1.566^2, 7.763)
+  surv_scaler_O1_O2 ~ dt(0, 1/1.566^2, 7.763)
+  surv_scaler_O2_O3 ~ dt(0, 1/1.566^2, 7.763)
+  mu_phi_M_O1[o_nat] ~ dbeta(1, 1)    # first winter at sea: to become SWA1
+  mu_phi_O1_O2[o_nat] ~ dbeta(1, 1)   # second winter at sea: to become SWA2
+  mu_phi_O2_O3[o_nat] ~ dbeta(1, 1)   # third winter at sea: to become SW3
+  sig_Lphi_M_O1[o_nat] ~ dunif(0, 5)
+  sig_Lphi_O1_O2[o_nat] ~ dunif(0, 5)
+  sig_Lphi_O2_O3[o_nat] ~ dunif(0, 5)
+  
+  logit(mu_phi_M_O1[o_hat]) <- logit(mu_phi_M_O1[o_nat]) + surv_scaler_M_O1
+  logit(mu_phi_O1_O2[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + surv_scaler_O1_O2
+  logit(mu_phi_O2_O3[o_hat]) <- logit(mu_phi_O2_O3[o_nat]) + surv_scaler_O2_O3
+  
   for (o in 1:no) {
-    # origin/age-specific ocean survival
-    mu_phi_M_O1[o] ~ dbeta(1, 1)    # first winter at sea: to become SWA1
-    mu_phi_O1_O2[o] ~ dbeta(1, 1)   # second winter at sea: to become SWA2
-    mu_phi_O2_O3[o] ~ dbeta(1, 1)   # third winter at sea: to become SW3
-    sig_Lphi_M_O1[o] ~ dunif(0, 5)
-    sig_Lphi_O1_O2[o] ~ dunif(0, 5)
-    sig_Lphi_O2_O3[o] ~ dunif(0, 5)
     
     # sex/origin-specific maturation probabilities
     for (s in 1:ns) {
@@ -118,8 +126,8 @@ jags_model_code = function() {
     }
[…]

### 2020-12-16 02-model/fit-model.R
Track new parameters

@@ -148,7 +148,9 @@ jags_params = c(
   "Ra", "Sb", "Sa", "q_Ra", "q_Sa_adj", "Sa_tot", "Ra_tot",
   
   # carcass vs. weir correction
-  "z", "carc_adj", "n_stray_tot", "stray_comp"
+  "z", "carc_adj", "n_stray_tot", "stray_comp",
+  
+  "surv_scaler_M_O1", "surv_scaler_O1_O2", "surv_scaler_O2_O3"
 )
 
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####

### 2020-12-16 03-post-process/output-plots.Rmd
Add new parameters to diagnostics in output plots

@@
     label: "Scenario"
-    value: base
+    value: "relate-hat-nat"
     input: text
@@
   "init_recruits", 
-  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
+  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
+  "^phi_M_O1", "^phi_O1_O2", "^phi_O2_O3",
+  "^psi_O1_Rb", "^psi_O2_Rb", "surv_scaler"
 )
@@
 diag_plots(post, "init_recruits", layout = "4x2")
+```
+
+`r if (params$mcmc_plots) "### surv_scaler"`
+
+```{r surv-scaler-diag-plots, eval = params$mcmc_plots, fig.width = 5, fig.height = 7}
+diag_plots(post, "surv_scaler", layout = "4x1")
 ```

### 2020-12-28 03-post-process/output-plots.Rmd
Change the name of the survival scaler

--- 2020-11-21 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: base
+    value: "relate-hat-nat-age-4-5-same"
     input: text
@@
   "init_recruits", 
-  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
+  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
+  "^phi_M_O1", "^phi_O1_O2", "^phi_O2_O3",
+  "^psi_O1_Rb", "^psi_O2_Rb", "O_phi_scaler_nat_hat"
 )
@@
 # calculate the diagnostic statistics for each group
-diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T)[c("mean", "Rhat", "neff"),])
+diags = lapply(diag_params, function(param) as.matrix(post_summ(post, param, Rhat = T, neff = T)[c("mean", "Rhat", "neff"),]))
 
@@
 diag_plots(post, "init_recruits", layout = "4x2")
+```
+
+`r if (params$mcmc_plots) "### surv_scaler"`
+
+```{r surv-scaler-diag-plots, eval = params$mcmc_plots, fig.width = 6, fig.height = 4}
+diag_plots(post, "O_phi_scaler_nat_hat")
 ```

### 2020-12-28 02-model/fit-model.R

@@ -150,7 +150,8 @@ jags_params = c(
   # carcass vs. weir correction
   "z", "carc_adj", "n_stray_tot", "stray_comp",
   
-  "surv_scaler_M_O1", "surv_scaler_O1_O2", "surv_scaler_O2_O3"
+  # misc parameters
+  "O_phi_scaler_nat_hat"
 )
 
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####

### 2020-12-28 02-model/model-code.R

@@ -55,9 +55,7 @@ jags_model_code = function() {
   }
   
   # origin/age-specific ocean survival
-  surv_scaler_M_O1 ~ dt(0, 1/1.566^2, 7.763)
-  surv_scaler_O1_O2 <- surv_scaler_M_O1
-  surv_scaler_O2_O3 <- surv_scaler_O1_O2
+  O_phi_scaler_nat_hat ~ dt(0, 1/1.566^2, 7.763)
   mu_phi_M_O1[o_nat] ~ dbeta(1, 1)    # first winter at sea: to become SWA1
   mu_phi_O1_O2[o_nat] ~ dbeta(1, 1)   # second winter at sea: to become SWA2
   mu_phi_O2_O3[o_nat] <- mu_phi_O1_O2[o_nat]   # third winter at sea: to become SW3
@@ -65,9 +63,9 @@ jags_model_code = function() {
   sig_Lphi_O1_O2[o_nat] ~ dunif(0, 5)
   sig_Lphi_O2_O3[o_nat] <- sig_Lphi_O1_O2[o_nat]
   
-  logit(mu_phi_M_O1[o_hat]) <- logit(mu_phi_M_O1[o_nat]) + surv_scaler_M_O1
-  logit(mu_phi_O1_O2[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + surv_scaler_O1_O2
-  logit(mu_phi_O2_O3[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + surv_scaler_O2_O3
+  logit(mu_phi_M_O1[o_hat]) <- logit(mu_phi_M_O1[o_nat]) + O_phi_scaler_nat_hat
+  logit(mu_phi_O1_O2[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + O_phi_scaler_nat_hat
+  logit(mu_phi_O2_O3[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + O_phi_scaler_nat_hat
   
   for (o in 1:no) {
     
@@ -146,11 +144,10 @@ jags_model_code = function() {
     phi_M_O1[y,o_nat] <- ilogit(Lphi_M_O1[y,o_nat])
     Lphi_O1_O2[y,o_nat] ~ dnorm(logit(mu_phi_O1_O2[o_nat]), 1/sig_Lphi_O1_O2[o_nat]^2)
[…]

### 2021-01-05 03-post-process/output-plots.Rmd

@@
     label: "Scenario"
-    value: "relate-hat-nat-age-4-5-same"
+    value: "base"
     input: text
@@
 plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$"), main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$"), main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
 mtext(side = 1, outer = T, line = -0.5, "Brood Year")

### 2021-03-18 03-post-process/output-plots.Rmd

@@
 par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
-plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = "Spring Trap Abundance")
-plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
+plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = TeX("$Fall\\,Parr\\,Abundance\\,(At\\,Trap)$"))
+plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = TeX("$Spring\\,Smolt\\,Abundance\\,(At\\,Trap)$"))
+plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = TeX("$Adult\\,Return\\,Abundance$"))
+
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
-
-plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "(Nat) Summer Tagging to LGD")
-plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "(Nat) Fall Trap to LGD")
-plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = "(Nat) Spring Trap to LGD")
-plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
-plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = "(Nat) LGD to BON")
-plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = "(Hat) LGD to BON")
+plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = TeX("$Summer\\,Parr \\rightarrow LGR"))
+plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = TeX("$Fall\\,Parr \\rightarrow LGR"))
+plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(NOR)"))
+plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
+plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(NOR)"))
+plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(HOR)"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 
-par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^q_Ra[.+,1]$"), q_obs[observable,1], main = "Nat. Female Age 3")
-plot_tseries(post_summ(post, "^q_Ra[.+,2]$"), q_obs[observable,2], main = "Nat. Female Age 4")
-plot_tseries(post_summ(post, "^q_Ra[.+,3]$"), q_obs[observable,3], main = "Nat. Female Age 5")
-plot_tseries(post_summ(post, "^q_Ra[.+,4]$"), q_obs[observable,4], main = "Nat. Male Age 3")
-plot_tseries(post_summ(post, "^q_Ra[.+,5]$"), q_obs[observable,5], main = "Nat. Male Age 4")
-plot_tseries(post_summ(post, "^q_Ra[.+,6]$"), q_obs[observable,6], main = "Nat. Male Age 5")
-plot_tseries(post_summ(post, "^q_Ra[.+,7]$"), q_obs[observable,7], main = "Hat. Female Age 3")
-plot_tseries(post_summ(post, "^q_Ra[.+,8]$"), q_obs[observable,8], main = "Hat. Female Age 4")
-plot_tseries(post_summ(post, "^q_Ra[.+,9]$"), q_obs[observable,9], main = "Hat. Female Age 5")
-plot_tseries(post_summ(post, "^q_Ra[.+,10]$"), q_obs[observable,10], main = "Hat. Male Age 3")
-plot_tseries(post_summ(post, "^q_Ra[.+,11]$"), q_obs[observable,11], main = "Hat. Male Age 4")
-plot_tseries(post_summ(post, "^q_Ra[.+,12]$"), q_obs[observable,12], main = "Hat. Male Age 5")
+par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
+plot_tseries(post_summ(post, "^q_Ra[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Ra[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,1]$"), q_obs[observable,1], main = "Nat. Female Age 3")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,2]$"), q_obs[observable,2], main = "Nat. Female Age 4")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,3]$"), q_obs[observable,3], main = "Nat. Female Age 5")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,4]$"), q_obs[observable,4], main = "Nat. Male Age 3")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,5]$"), q_obs[observable,5], main = "Nat. Male Age 4")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,6]$"), q_obs[observable,6], main = "Nat. Male Age 5")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,7]$"), q_obs[observable,7], main = "Hat. Female Age 3")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,8]$"), q_obs[observable,8], main = "Hat. Female Age 4")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,9]$"), q_obs[observable,9], main = "Hat. Female Age 5")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,10]$"), q_obs[observable,10], main = "Hat. Male Age 3")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,11]$"), q_obs[observable,11], main = "Hat. Male Age 4")
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,12]$"), q_obs[observable,12], main = "Hat. Male Age 5")
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+plot_tseries(post_summ(post, "^q_Sa_adj[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 
-```{r ocean-surv-plots, fig.width = 4, fig.height = 6}
-par(mfrow = c(3,2), oma = c(1,1,0,0))
-plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = "BON -> O1 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = "BON -> O1 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = "O1 -> O2 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
+par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+mtext(side = 1, outer = T, line = 0.5, "Brood Year")
 mtext(side = 2, outer = T, line = 0, "Survival")

### 2021-06-21 02-model/model-code.R
Add AR(1) process to several model components
* parr recruitment
* movement out of basin to LGR (HOR & NOR)
* movement from LGR to BON (HOR & NOR)
* first year ocean survival

@@ -85,6 +85,22 @@ jags_model_code = function() {
   logit(mu_phi_O1_O2[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + O_phi_scaler_nat_hat
   logit(mu_phi_O2_O3[o_hat]) <- logit(mu_phi_O1_O2[o_nat]) + O_phi_scaler_nat_hat
   
+  ### PRIORS: AR(1) COEFFICIENTS
+  kappa_Pb ~ dunif(-0.99,0.99)                # total summer parr recruitment
+  kappa_phi_Mb_Ma[o_nat] ~ dunif(-0.99,0.99)  # movement survival in spring to LGR (natural origin)
+  kappa_phi_Mb_Ma[o_hat] ~ dunif(-0.99,0.99)  # movement survival in spring to LGR (hatchery origin)
+  kappa_phi_Ma_M[o_nat] ~ dunif(-0.99,0.99)   # movement survival from LGR thru BON (natural origin)
+  kappa_phi_Ma_M[o_hat] ~ dunif(-0.99,0.99)   # movement survival from LGR thru BON (hatchery origin)
+  kappa_phi_M_O1 ~ dunif(-0.99,0.99)          # overwinter survival for first winter at sea
+  
+  ### PRIORS: YEAR-0 RESIDUALS FOR ALL TERMS THAT USE AR(1) PROCESS
+  lPb_resid[kmax] ~ dnorm(0, (1/sigma_Pb^2) * (1 - kappa_Pb^2))
+  Lphi_Mb_Ma_resid[kmax,o_nat] ~ dnorm(0, (1/sig_Lphi_Mb_Ma[i_spring,o_nat]^2) * (1 - kappa_phi_Mb_Ma[o_nat]^2))
+  Lphi_Mb_Ma_resid[kmax,o_hat] ~ dnorm(0, (1/sig_Lphi_Mb_Ma[i_spring,o_hat]^2) * (1 - kappa_phi_Mb_Ma[o_hat]^2))
+  Lphi_Ma_M_resid[kmax,o_nat] ~ dnorm(0, (1/sig_Lphi_Ma_M[o_nat]^2) * (1 - kappa_phi_Ma_M[o_nat]^2)) 
+  Lphi_Ma_M_resid[kmax,o_hat] ~ dnorm(0, (1/sig_Lphi_Ma_M[o_hat]^2) * (1 - kappa_phi_Ma_M[o_hat]^2))   
[…]

### 2021-06-21 02-model/fit-model.R
Monitor new quantities: autoregressive coefficients

@@ -17,7 +17,7 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 out_dir = "02-model/model-output"
 
 # specify a scenario name
-scenario = "base"
+scenario = "AR1"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -176,7 +176,10 @@ jags_params = c(
   "Lpi_resid", "Lphi_Pa_Mb_resid", "Lphi_Mb_Ma_resid",
   "Lphi_Ma_M_resid", "Lomega_resid", "Lpsi_O1_Rb_resid",
   "Lpsi_O2_Rb_resid", "Lphi_M_O1_resid", "Lphi_O1_O2_resid",
-  "Lphi_Sb_Sa_resid", "lPb_resid"
+  "Lphi_Sb_Sa_resid", "lPb_resid",
+  
+  # AR(1) coefficients
+  "kappa_Pb", "kappa_phi_Mb_Ma", "kappa_phi_Ma_M", "kappa_M_O1"
 )
 
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####

### 2021-06-21 03-post-process/output-plots.Rmd
Add summaries for AR(1) coefficients to output plots

@@
     # give names
-    dimnames(Ra) = dimnames(jags_data$p_remove)
+    dimnames(Ra) = dimnames(jags_data$n_broodstock)
     dimnames(Ma) = dimnames(jags_data$Mb_obs)
@@
 ```
+
+## AR(1) Coefficients
+
+```{r}
+post_summ(post, "kappa", Rhat = TRUE, neff = TRUE, digits = 3)
+```
+
+# JAGS Model and Data {.tabset .tabset-pills}
+
+## JAGS Model Code
+
+```{r, comment = NA}
+# print the JAGS model code
+cat(model_info$jags_model_code, sep = "\n")
+```
+
+## JAGS Model Data
+
+```{r, comment = NA}
+# print the JAGS model data
+model_info$jags_data
+```

### 2021-06-23 02-model/model-code.R
Edit JAGS model to use the subtraction of broodstock

@@ -324,8 +324,8 @@ jags_model_code = function() {
           Ra[y,k,s,o] <- Rb[y,k,s,o] * phi_Rb_Ra[y,o] + n_stray_tot[y] * stray_comp[k,s,o]
           
           # remove fish for brood stock
-          Sb[y,k,s,o] <- Ra[y,k,s,o] * (1 - p_remove[y,k,s,o])
-          
+          Sb[y,k,s,o] <- max(Ra[y,k,s,o] - n_broodstock[y,k,s,o], 0)
+
           # survive pre-spawn mortality
           # currently assumed to apply equally to hatchery and wild origin returns
           # and to be age/sex non-selective

### 2021-06-23 03-post-process/output-plots.Rmd
Add a figure to output plots diagnosing issues from new broodstock removal

@@
 
-## AR(1) Coefficients
+# Misc
 
-```{r}
-post_summ(post, "kappa", Rhat = TRUE, neff = TRUE, digits = 3)
+## Brood stock Removals
+
+This figure shows the frequency that `Sb[y,k,s,o]` (spawners passed above weir, following broodstock removals) would go negative if not for the constraint `Sb[y,k,s,o] <- max(Ra[y,k,s,o] - n_broodstock[y,k,s,o], 0)`.
+
+```{r, fig.width = 8, fig.height = 5}
+Sb_post = post_subset(post, "^Sb[", matrix = TRUE)
+p0 = array_format(colMeans(Sb_post == 0))
+dimnames(p0) = dimnames(jags_data$n_broodstock)
+years = as.numeric(dimnames(p1)[[1]])
+
+par(mfcol = c(3,4), oma = c(1.5,1.5,0,0), mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+plot(p0[observable,1,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,3\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,2,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,4\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,3,1,1] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,5\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,1,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,3\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,2,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,4\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,3,2,1] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,5\\,(NOR)$"), ylim = c(0,1))
+plot(p0[observable,1,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,3\\,(HOR)$"), ylim = c(0,1))
+plot(p0[observable,2,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,4\\,(HOR)$"), ylim = c(0,1))
+plot(p0[observable,3,1,2] ~ years[observable], type = "l", main = TeX("$Female\\,Age\\,5\\,(HOR)$"), ylim = c(0,1))
+plot(p0[observable,1,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,3\\,(HOR)$"), ylim = c(0,1))
+plot(p0[observable,2,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,4\\,(HOR)$"), ylim = c(0,1))
+plot(p0[observable,3,2,2] ~ years[observable], type = "l", main = TeX("$Male\\,Age\\,5\\,(HOR)$"), ylim = c(0,1))
 ```

### 2021-07-23 03-post-process/output-plots.Rmd

--- 2021-06-21 03-post-process/output-plots.Rmd
@@
   "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
-  "^phi_M_O1", "^phi_O1_O2", "^phi_O2_O3",
+  "^phi_O0_O1", "^phi_O1_O2", "^phi_O2_O3",
   "^psi_O1_Rb", "^psi_O2_Rb", "O_phi_scaler_nat_hat"
@@
 plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
-plot_tseries(post_summ(post, "^phi_Ma_M[.+,1]$"), expit(jags_data$Lphi_obs_Ma_M[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(NOR)"))
-plot_tseries(post_summ(post, "^phi_Ma_M[.+,2]$"), expit(jags_data$Lphi_obs_Ma_M[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow BON\\,(HOR)"))
+plot_tseries(post_summ(post, "^phi_Ma_O0[.+,1]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(NOR)"))
+plot_tseries(post_summ(post, "^phi_Ma_O0[.+,2]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(HOR)"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
     # give names
-    dimnames(Ra) = dimnames(jags_data$n_broodstock)
+    dimnames(Ra) = dimnames(jags_data$n_remove)
     dimnames(Ma) = dimnames(jags_data$Mb_obs)
@@
 par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O0_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O0_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
 plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
@@
 par(mfrow = c(1,2), oma = c(1,1,0,0))
-plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames
+                                                                                           (jags_data$Pa_obs)[observable]), ylim = c(0,1))
 plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
@@
 * `mu_omega[1]`: mean probability of being a female at ocean entry
-* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
+* `mu_phi_Ma_O0`: mean probability of surviving from LGD to ocean entry
 * `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)

### 2021-07-23 03-post-process/output-plots.Rmd
Add new monitored output to the output plots

@@
 # MCMC Information {.tabset .tabset-pills}
+
+## Time Stamps
+
+```{r}
+df = data.frame(Value = model_info$jags_time)
+rownames(df) = c("Time Started", "Time Ended", "Time Elapsed")
+kable(df) %>%
+  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
+  column_spec(1, bold = TRUE)
+```
 
@@
 
-# Smolt-to-Adult Rates
+# Equivilency Rates
+
+## Smolt-to-Adult Rates
 
@@
        pch = 22, col = c("blue", "red"), pt.cex = 2, pt.bg = alpha(c("skyblue2", "salmon"), 0.5), bty = "n")
+```
+
+## Parr per Spawner
+
+"Spawner" means total spawners that survive pre-spawn mortality.
+
+```{r}
+par(oma = c(1,1,0,0))
+plot_tseries(est = post_summ(post, "Pb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Parr/Spawner")
+```
+
+## Smolt per Spawner
+
+"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
+
+```{r}
+par(oma = c(1,1,0,0))
+plot_tseries(est = post_summ(post, "Mb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Smolt/Spawner")
+```
+
+## Spawners per Spawner
+
+This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
+"Brood year" refers to the year the returning production was spawned.
+
+```{r}
+all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
+
+par(oma = c(1,1,0,0))
+plot_tseries(est = post_summ(post, "Sa_tot_per_Sa_tot["), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)])
+mtext(side = 1, outer = T, line = -0.5, "Brood Year")
+mtext(side = 2, outer = T, line = 0, "Spawners/Spawner")
+abline(h = 1, lty = 2)
 ```
@@
 alpha_summ = post_summ(post, "alpha", digits = 0)
-beta_summ = post_summ(post, "beta", digits = -3)
+beta_summ = post_summ(post, "^beta$", digits = -3)
+beta_per_peu_summ = post_summ(post, "beta_per_peu", digits = -1)
 sigma_summ = post_summ(post, "sigma_Pb", digits = 2)
@@
 # create/format the table
-tab = cbind(alpha_summ, beta_summ, sigma_summ)
-colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\sigma_{Pb}$")
+tab = cbind(alpha_summ, beta_summ, beta_per_peu_summ, sigma_summ)
+colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\beta/\\mathrm{PEU}$", "$\\sigma_{Pb}$")
 

### 2021-07-26 03-post-process/output-plots.Rmd

@@
 title: "Output Summary"
-subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
+subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'MIN' = 'Minam', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
 output: 
@@
   "init_recruits", 
-  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
+  "^phi_Ma_O0", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
   "^phi_O0_O1", "^phi_O1_O2", "^phi_O2_O3",
@@
 # extract posterior summaries of total spawners by brood year
-Sa_tot = post_summ(post, "Sa_tot")
+Sa_tot = post_summ(post, "^Sa_tot[")
 

### 2021-07-27 03-post-process/output-plots.Rmd
Update and add to output plots -- more info relative to fecundity inclusion

@@
 
-# Spawner-to-Parr Relationship
+# Spawner-to-Parr Relationship {.tabset .tabset-pills}
+
+## Beverton-Holt
 
 All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and spawners -- the grey region is the confidence interval around this fit (from a parametric bootstrap).
+The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
 
-```{r spawners-to-parr, fig.width = 6, fig.height = 4}
+```{r eggs-to-parr, fig.width = 6, fig.height = 4}
 # extract posterior samples of the BH productivity and capacity parameters
-bh_params = post_subset(post, c("alpha", "beta"), matrix = T)
+bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)
 
+# extract posterior summaries of total spawners by brood year
+Sa_tot = post_summ(post, "^Sa_tot[")
+
+# extract posterior summaries of total egg production by brood year
+f_tot = post_summ(post, "^f_tot[")
+
+# extract posterior summaries of total parr recruits by brood year
+Pb = post_summ(post, "^Pb[")
+
+# predict parr recruits along a sequence of spawner abundances
+Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
+f_pred = seq(0, max(f_tot[5,]), length = 30)
+
+Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
+colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
+Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
+Pb_pred = post_summ(Pb_pred, "Pb_pred")
+
+# fit ordinary least squares version
+ols_fit = fit_fecund_BH(jags_data)$BH_fit
+
+# draw 1000 random parameters
+ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
+
+# calculate predicted curve at each pair/summarize
+ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
+ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
+
+# graphical parameters
+par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
+
+# empty plot
+plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
+     xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")
+
+x_ticks = axisTicks(par("usr")[1:2], log = F)
+axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+# draw fitted relationship: Bayesian
+polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
+lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
+lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
+
+# draw fitted relationship: OLS
+polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
+lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
+lines(ols_R_pred[2,] ~ f_pred, lty = 2)
+lines(ols_R_pred[3,] ~ f_pred, lty = 2)
+lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
+
+# draw state pairs + uncertainty
+segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = "red")
+segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = "red")
+points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+```
+
+## Total Eggs vs. Total Spawners
+
+This figure illustrates that total spawners is a reasonable index of total egg production.
+The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
+
+```{r, fig.width = 6, fig.height = 4}
+# extract posterior summaries of total egg production by brood year
+f_tot = post_summ(post, "^f_tot[")
+
+# extract posterior summaries of total spawners by brood year
+Sa_tot = post_summ(post, "^Sa_tot[")
+
+par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+plot(f_tot["mean",] ~ Sa_tot["mean",],
+     ylim = c(0, max(f_tot["97.5%",])),
+     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
+     ylab = "Total Egg Production (Millions)", xlab = "Total Spawners", las = 1, yaxt = "n")
+y_ticks = axisTicks(par("usr")[3:4], log = F)
+axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
+
+segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
+segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
+points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+abline(c(0, 1000), lty = 1)
+abline(c(0, 1800), lty = 2)
+abline(c(0, 3600), lty = 3)
+legend("bottomright", title = "If Each Spawner Had:",
+       legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
+       lty = c(1,2,3), bty = "n")
+```
+
+## Parr per Egg
+
+This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
+The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.
+
+```{r, fig.width = 6, fig.height = 4}
+# extract posterior summaries of total egg production by brood year
+f_tot = post_summ(post, "^f_tot[")
+
+# extract posterior summaries of total parr recruits by brood year
+Pb = post_summ(post, "^Pb[")
+
+# conversion rates
+Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")
+
+# max survival
+alpha = post_summ(post, "^alpha")
+
+par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
+     ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
+     xlim = c(0, max(f_tot["97.5%",])), type = "n",
+     ylab = "Parr per Egg", xlab = "Total Egg Production (Millions)", las = 1, xaxt = "n")
+x_ticks = axisTicks(par("usr")[1:2], log = F)
+axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
+segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
+points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
+abline(h = alpha["mean",], lwd = 2, col = "red")
+box()
+```
+
+## Parr per Spawner
+
+This figure is identical to above, but shows parr production per spawner instead of per egg.
+
+```{r, fig.width = 6, fig.height = 4}
 # extract posterior summaries of total spawners by brood year
@@
 
-# predict parr recruits along a sequence of spawner abundances
-Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(Sa_pred, bh_params[i,1], bh_params[i,2])))
-colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
-Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-Pb_pred = post_summ(Pb_pred, "Pb_pred")
+# conversion rates
+Pb_per_Sa_tot = post_summ(post, "^Pb_per_Sa_tot[")
 
-# fit ordinary least squares version
-ols_fit = fit_basic_BH(jags_data)$BH_fit
-
-# draw 1000 random parameters
-ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
-
-# calculate predicted curve at each pair/summarize
-ols_R_pred = t(sapply(1:1000, function(i) BH(Sa_pred, ols_params[i,1], ols_params[i,2])))
-ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
-
-# graphical parameters
-par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
-
-# empty plot
-plot(1, 1, type = "n", xlim = range(0, Sa_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-     xlab = "Spawners", ylab = "Parr Recruits")
-
-# draw fitted relationship: Bayesian
-polygon(c(Sa_pred, rev(Sa_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-lines(Pb_pred[4,] ~ Sa_pred, col = "red", lty = 2)
-lines(Pb_pred[5,] ~ Sa_pred, col = "red", lty = 2)
-
-# draw fitted relationship: OLS
-polygon(c(Sa_pred, rev(Sa_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
-lines(ols_R_pred[1,] ~ Sa_pred, lwd = 2)
-lines(ols_R_pred[2,] ~ Sa_pred, lty = 2)
-lines(ols_R_pred[3,] ~ Sa_pred, lty = 2)
-lines(Pb_pred[3,] ~ Sa_pred, col = "red", lwd = 2)
-
-# draw state pairs + uncertainty
-segments(Sa_tot[4,], Pb[3,], Sa_tot[5,], Pb[3,], col = "red")
-segments(Sa_tot[3,], Pb[4,], Sa_tot[3,], Pb[5,], col = "red")
-points(Pb[3,] ~ Sa_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
+     ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
+     xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
+     ylab = "Parr per Spawner", xlab = "Spawners", las = 1)
+segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
+segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
+points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
 ```
@@
 
-```{r sar-plot}
+```{r sar-plot, fig.width = 6, fig.height = 4}
 # function to calculate posterior 
@@
 
-```{r}
+```{r, fig.width = 6, fig.height = 4}
 par(oma = c(1,1,0,0))
@@
 
-```{r}
+```{r, fig.width = 6, fig.height = 4}
 all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
@@
 
-```{r stray-tot-plot}
+```{r stray-tot-plot, fig.width = 6, fig.height = 4}
 par(oma = c(1,1,0,0))
@@
 # extract posterior summaries
-alpha_summ = post_summ(post, "alpha", digits = 0)
+alpha_summ = post_summ(post, "alpha", digits = 3)
 beta_summ = post_summ(post, "^beta$", digits = -3)
 beta_per_peu_summ = post_summ(post, "beta_per_peu", digits = -1)
-sigma_summ = post_summ(post, "sigma_Pb", digits = 2)
+sigma_summ = post_summ(post, "sigma_Pb", digits = 3)
 

### 2021-07-27 03-post-process/output-plots-single.Rmd
Create duplicates of key files
These will archive the single-population version and the main version files will be edited to be applicable to multiple populations.

--- 2021-07-27 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: "base"
+    value: "base-single"
     input: text

### 2021-07-27 02-model/model-code-single.R

@@ -1,0 +1,485 @@
+jags_model_code = function() {
+  
+  ### PRIORS: RECRUITMENT FUNCTION ###
+  # spawner to aggregate parr recruitment function
+  # log_alpha ~ dnorm(0, 0.001) %_% T(,9.2) # log productivity. bound to prevent nonsensically large draws
+  # alpha <- exp(log_alpha)
+  alpha ~ dbeta(1, 1)
+  log_beta ~ dnorm(0, 0.001) %_% T(,15)   # log capacity. bound to prevent nonsensically large draws
+  beta <- exp(log_beta)
+  sigma_Pb ~ dunif(0, 5)
+  beta_per_peu <- beta/peu
+  
+  ### PRIORS: FRESHWATER PARAMETERS ###
+  # aggregate parr to LH-specific parr
+  mu_pi[i_fall] ~ dbeta(1, 1)
+  sig_Lpi ~ dunif(0, 5)
+  mu_pi[i_spring] <- 1 - mu_pi[i_fall]
+  
+  # overwinter survival parameters: LH-specific
+  # uses logistic relationship to introduce density-depdendence
+  # gamma0: LH-specific intercepts
+  # gamma1: LH-common slopes
+  for (i in 1:ni) {
+    gamma0[i] ~ dnorm(0, 1e-3)
+    sig_Lphi_Pa_Mb[i] ~ dunif(0, 5)
+  }
+  gamma1[i_fall] ~ dnorm(0, 1e-3)
+  gamma1[i_spring] <- gamma1[i_fall]
+
+  # natural origin movement survival (trib to LGD): estimate for spring migrants and assume the same value for fall migrants
+  mu_phi_Mb_Ma[i_spring,o_nat] ~ dbeta(1, 1)
+  sig_Lphi_Mb_Ma[i_spring,o_nat] ~ dunif(0, 5)
+  mu_phi_Mb_Ma[i_fall,o_nat] <- mu_phi_Mb_Ma[i_spring,o_nat]
+  sig_Lphi_Mb_Ma[i_fall,o_nat] <- sig_Lphi_Mb_Ma[i_spring,o_nat]
+  
+  # hatchery origin movement survival (trib to LGD): have spring migrants only
+  mu_phi_Mb_Ma[i_spring,o_hat] ~ dbeta(1, 1)
+  sig_Lphi_Mb_Ma[i_spring,o_hat] ~ dunif(0, 5)
+  
[…]

### 2021-08-03 02-model/fit-model.R
Update fit-model.R to run multi-population model

@@ -1,6 +1,6 @@
-# ::::::::::::::::::::::::::::::::::::::::::::::: #
-# SCRIPT TO RUN THE JAGS MODEL FOR ONE POPULATION #
-# ::::::::::::::::::::::::::::::::::::::::::::::: #
+# :::::::::::::::::::::::::::::::::::::::::::::::: #
+# SCRIPT TO RUN THE JAGS MODEL FOR ALL POPULATIONS #
+# :::::::::::::::::::::::::::::::::::::::::::::::: #
 
 ##### STEP 0: SET UP WORKSPACE #####
 
@@ -23,35 +23,23 @@ scenario = "base"
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
 # or if in interactive session, uncomment the pop you wish to fit
 args = commandArgs(trailingOnly = T)
-pop = args[1]
-rmd = as.logical(args[2])
-mcmc_length = args[3]
-rmd_mcmc_plots = T
-
-# if pop not supplied, set a value and warn
-if (is.na(pop)) {
-  pop = "CAT"
-  # pop = "LOS"
-  # pop = "MIN" # don't do this one yet, the data prep steps (for age comp mostly) aren't correct for MIN
-  # pop = "UGR"
-  cat("\n\n'pop' was not supplied as a command line argument.", pop, " will be used.")
-}
+rmd = as.logical(args[1])
+mcmc_length = args[2]
 
 if (is.na(rmd)) {
-  rmd = T
-  # rmd = F
-  cat("\n\n'rmd' was not supplied as a command line argument.", rmd, " will be used.")
+  rmd = FALSE
+  cat("\n\n'rmd' was not supplied as a command line argument.", rmd, "will be used.")
 }
 
 if (is.na(mcmc_length)) {
   mcmc_length = "short"
-  cat("\n\n'mcmc_length' was not supplied as a command line argument.", mcmc_length, " will be used.")
+  cat("\n\n'mcmc_length' was not supplied as a command line argument.", mcmc_length, "will be used.")
 }
 
 ##### STEP 1: PREPARE DATA FOR JAGS #####
 
 # build JAGS data object
-jags_data = create_jags_data_one(pop)
+jags_data = create_jags_data_mult(c("CAT", "LOS", "MIN", "UGR"))
 jags_data = append_no_na_indices(jags_data)
 
 # some parameters we are assuming known (for now)
[…]

### 2021-08-03 03-post-process/output-plots.Rmd
Update front matter of output-plots for multi-population model

@@
 title: "Output Summary"
-subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'MIN' = 'Minam', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
+subtitle: "Multi-Population Model"
 output: 
@@
 params:
-  pop:
-    label: "Population"
-    value: CAT
-    input: select
-    choices: [CAT, LOS, UGR]
   scenario:
@@
     input: text
-  mcmc_plots:
-    label: "Make MCMC Plots"
-    input: checkbox
-    value: FALSE
 editor_options: 
@@
 # read information from this model
-model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output-", params$scenario, ".rds")))
+model_info = readRDS(file.path(in_dir, paste0(params$pop, "output-", params$scenario, ".rds")))
 
@@
 
-# which years are "observable"?
+# the years included by the model
+all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
+
+# which years are "observable" for at least some quantities?
 observable = (jags_data$kmax+1):jags_data$ny

### 2021-08-03 03-post-process/output-plots.Rmd
Add more information to Time Stamps section of output-plots

@@
 
-## Time Stamps
+## Time Information
 
 ```{r}
-df = data.frame(Value = model_info$jags_time)
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed")
+# Calculate hours per 10,000 iterations
+hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
+  # calculation of total iters differs if parallel or not
+  if (parallel) {
+    total_iters = n_adapt + n_post + n_burn
+  } else {
+    total_iters = (n_adapt + n_post + n_burn) * n_chains
+  }
+  ten_thousands_of_total_iters = total_iters/10000
+
+  # calculate hours elapsed
+  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
+  time_number = as.numeric(time_diff)
+  time_units = attributes(time_diff)$units
+  hour_convert = switch(time_units,
+                        "secs" = 3600,
+                        "mins" = 60,
+                        "hours" = 1,
+                        "days" = 1/24)
+  hours_diff = time_number/hour_convert
+
+  # calculate/round rate
+  round(hours_diff/ten_thousands_of_total_iters, 2)
+})
+
+# combine relevant info into a data frame
+df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
+rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
+
+# make a kable for printing in output
 kable(df) %>%
@@
 kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed")
+  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
+  column_spec(1, bold = TRUE)
 ```

### 2021-08-03 03-post-process/output-plots.Rmd
Introduce a new framework for easily accessing specific posterior summaries
The indexing in the model gets quite complex in some areas. Take returns to the estuary by year, age, sex, origin, and population: Rb[y,k,s,o,j]. If we wish to extract the posterior summary of all age 4 natural origin males for UGR, we would write: post_summ(post, "Rb[.+,2,2,1,4]"). This is confusing to read and edit when copying and pasting to summarize a similar quantity but for a different combo of age/sex/origin/population.

This commit introduces the function `sub_index()`, which makes this task much easier. Coupl

@@
 observable = (jags_data$kmax+1):jags_data$ny
+```
+
+```{r dimension-ids}
+# population names
+pops = colnames(jags_data$Ra_obs)
+
+# dimension IDs
+i_fall   = 1  # fall migrants are i = 1
+i_spring = 2  # spring migrants are i = 2,
+o_nor    = 1  # natural origin are o = 1,
+o_hor    = 2  # hatchery origin are o = 2,
+s_female = 1  # females are s = 1,
+s_male   = 2  # males are s = 2
+j_cat    = 1  # Catherine Creek is j = 1
+j_los    = 2  # Lostine River is j = 2
+j_min    = 3  # Minam River is j = 3
+j_ugr    = 4  # Upper Grande Ronde River is j = 4
+k_3      = 1  # age 3 is k = 1
+k_4      = 2  # age 4 is k = 2
+k_5      = 3  # age 5 is k = 3
 ```

### 2021-08-03 01-functions/util-fns.R

@@ -136,3 +136,41 @@ find_no_na_indices = function(x) {
 BH = function(x, alpha, beta) {
   x/((1/alpha) + (x/beta))
 }
+
+##### REPLACE PLACEHOLDER INDEX #####
+# x: a string like "psi_O1_Rb[year,sex,origin,pop]
+# other arguments: a number to replace
+# e.g., sub_index("psi_O1_Rb[year,sex,origin,pop]", year = ".+", sex = 1, origin = 2, pop = ".")
+# returns "psi_O1_Rb[.+,1,2,.]"
+# this reduces how much hardcoding is required in generating output summaries
+
+sub_index = function(x, year = NULL, LH_type = NULL, age = NULL, sex = NULL, origin = NULL, pop = NULL) {
+  # create a duplicate object
+  newx = x
+  
+  # if one of the dimensions was specified, perform replacement
+  if (!is.null(year)) newx = stringr::str_replace(newx, "year", as.character(year))
+  if (!is.null(age)) newx = stringr::str_replace(newx, "age", as.character(age))
+  if (!is.null(LH_type)) newx = stringr::str_replace(newx, "LH_type", as.character(LH_type))
+  if (!is.null(sex)) newx = stringr::str_replace(newx, "sex", as.character(sex))
+  if (!is.null(origin)) newx = stringr::str_replace(newx, "origin", as.character(origin))
+  if (!is.null(pop)) newx = stringr::str_replace(newx, "pop", as.character(pop))
+  
+  # return the version with placeholders replaced by index values
+  newx
+}
+
+##### COMBINE A LIST OF DATA FRAMES #####
+# list: a list with data frames to be rbind-ed stored as elements
+
+unlist_dfs = function(list) {
+  # empty object
+  output = NULL
+  
+  # loop through list elements, combining the data frame in each with all previous
+  for (i in 1:length(list)) output = rbind(output, list[[i]])
+  
+  # return the output
+  return(output)
+}
+

### 2021-08-03 03-post-process/output-plots.Rmd
Completely revamp MCMC diagnostics in output-plots
* All info is in a table now, no MCMC diagnostic plots. This compiles much faster and shows all information more compactly
* Information is shown (% of nodes that violate a threshold) for Rhat, ESS (mean & quantiles), and MCMC CV (mean & quantiles)
* All estimated parameters are now diagnosed, where as before some were missing
* Diagnostic summaries are calculated using the updated calculations included in the 'posterior' package
* Table is color-coded based on severity of violations

@@
 
-This table shows the number of parameters that fail to meet some diagnostic threshold. Lower Rhat values are good, larger Neff values are good, and lower MCMC SE/Mean values are good.
+```{r mcmc-diag-function}
+# a function to get MCMC diagnoses for a group of parameters
+# params: a string to match with postpack::match_params()
+# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
+# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
+# L3: a "Level-3" group label; such as NOR or females or age-3 females
 
-The "match" column shows the kinds of parameters summarized in that row.
-E.g., `^mu_phi` covers all parameter names that start with `mu_phi` and are followed by anything else (`r paste(match_params(post, "^mu_phi"), collapse = ", ")`).
+diag_fn = function(params, L1 = NA, L2 = NA, L3 = NA) {
 
-This model was ran for a very short time, and I'm impressed with how well the sampling performed even considering this.
+  # extract the posteriors of interest and format for 'posterior' package
+  post_sub = as_draws_df(post_subset(post, params))
 
-```{r mcmc-diags}
-# groups of parameters to match and calculate diagnostic summaries for separately
-diag_params = list(
-  c("alpha", "beta", "sigma_Pb"),
-  "gamma",
-  "^mu_phi",
-  "^mu_psi",
-  "^mu_omega",
-  "^mu_pi",
-  "^sig_Lphi",
-  "^sig_Lpsi",
-  c("^sig_Lomega", "^sig_Lpi"),
-  "^Pb[", 
-  "init_recruits", 
-  "^phi_Ma_O0", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
-  "^phi_O0_O1", "^phi_O1_O2", "^phi_O2_O3",
-  "^psi_O1_Rb", "^psi_O2_Rb", "O_phi_scaler_nat_hat"
+  # summarize the posteriors
+  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
+
+  # discard any parameters that were the same value every MCMC iteration
+  # (will have an NA for rhat)
+  diags = diags[!is.na(diags$rhat),]
+
+  # add "Monte Carlo CV"
+  diags$mccv_mean = diags$mcse_mean/diags$mean
+  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
+  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
+
+  # summarize the summaries
+  out = data.frame(
+    L1 = L1,
+    L2 = L2,
+    L3 = L3,
+    match = params,
+    n_params = nrow(diags),
+    Rhat_1.05 = sum(diags$rhat >= 1.05),
+    Rhat_1.1 = sum(diags$rhat >= 1.1),
+    Rhat_1.2 = sum(diags$rhat >= 1.2),
+    ess_mean_400 = sum(diags$ess_mean < 400),
+    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
+    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
+    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
+    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
+    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
   )
 
-# calculate the diagnostic statistics for each group
-diags = lapply(diag_params, function(param) as.matrix(post_summ(post, param, Rhat = T, neff = T)[c("mean", "Rhat", "neff"),]))
-
-# count up the number of parameters by group that fail to meet certain thresholds
-diag_summ = t(sapply(diags, function(param) {
-  c(
-    n_total = ncol(param),
-    n_Rhat_1 = sum(param["Rhat",] > 1.05),
-    n_Rhat_2 = sum(param["Rhat",] > 1.1),
-    n_Rhat_3 = sum(param["Rhat",] > 1.2),
-    n_neff_1 = sum(param["neff",] < 2000),
-    n_neff_2 = sum(param["neff",] < 1000),
-    n_neff_3 = sum(param["neff",] < 500)
-  )
-}))
-
-# format to a table
-diag_summ = as.data.frame(diag_summ)
-colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500")
-df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)
-
-# render the table
-kable(df, align = "lccccccc") %>%
-  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
-  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3)) %>%
-  column_spec(1, monospace = T) %>%
-  column_spec(c(2,5), border_right = T)
+  # return the summarized summaries
+  return(out)
+}
 
@@
 
-`r if (params$mcmc_plots) "## Diagnostic Plots {.tabset .tabset-pills}"`
+```{r calculate-mcmc-diagnostics}
+# parr recruitment
+L1 = "Parr Recruitment"
+L2 = c("BH Productivity", "BH Capacity", "Process SD", "Parr States")
+match = c("alpha", "^beta[", "sigma_Pb", "^Pb[")
+parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
-`r if (params$mcmc_plots) "### $\\alpha$, $\\beta$"`
+# LH apportionment
+L1 = "Life History Apportionment"
+L2 = c("Mean", "Process SD", "Realized")
+match = c("mu_pi[1,.]", "sig_Lpi", "^pi[.+,1,.]")
+pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
-```{r alpha-beta-diag-plots, eval = params$mcmc_plots, fig.width = 4, fig.height = 5}
-diag_plots(post, c("alpha", "beta"), layout = "2x1")
+# Overwinter survival
+L1 = "Overwinter Survival"
+L2 = c("Intercept", "Slope", "Process SD", "Realized")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
+match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants")))
+match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants")))
+phi_Pa_Mb_diags = rbind(tmp1, tmp2)
+
+# Migration survival: trib to LGR
+L1 = "Migration Survival (Trib to LGR)"
+L2 = c("Mean", "Process SD", "Realized")
+base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[LH_type,origin,pop]", "phi_Mb_Ma[year,LH_type,origin,pop]")
+match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+phi_Mb_Ma_diags = rbind(tmp1, tmp2)
+
+# Migration survival: LGR to BON
+L1 = "Migration Survival (LGR to Ocean)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", origin = o_hor)
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+phi_Ma_O0_diags = rbind(tmp1, tmp2)
+
+# Sex Apportionment
+L1 = "Sex Apportionment"
+L2 = c("Mean", "Process SD", "Realized")
+base = list("mu_omega[sex,origin,pop]", "sig_Lomega[origin,pop]", "omega[year,sex,origin,pop]")
+match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+omega_diags = rbind(tmp1, tmp2)
+
+# Probability of Maturing at Age-3
+L1 = "Pr(Mature at Age-3)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_psi_O1_Rb[sex,origin,pop]", "sig_Lpsi_O1_Rb[sex,origin,pop]", "psi_O1_Rb[.+,sex,origin,pop]")
+match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
+match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
+match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
+tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
+match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
+tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
+psi_O1_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)
+
+# Probability of Maturing at Age-4
+L1 = "Pr(Mature at Age-4)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_psi_O2_Rb[sex,origin,pop]", "sig_Lpsi_O2_Rb[sex,origin,pop]", "psi_O2_Rb[.+,sex,origin,pop]")
+match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
+match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
+match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
+tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
+match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
+tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
+psi_O2_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)
+
+# Year 1 ocean survival
+L1 = "Year 1 Ocean Survival"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_O0_O1[origin]", "sig_Lphi_O0_O1", "phi_O0_O1[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
+phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Year 2 ocean survival
+L1 = "Year 2 Ocean Survival"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_O1_O2[origin]", "sig_Lphi_O1_O2", "phi_O1_O2[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
+phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Misc ocean survival
+L1 = "Misc Ocean Survival"
+L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
+match = c("O_phi_scaler_nat_hat", "Lphi_O0_O1_resid[5]", "kappa_phi_O0_O1")
+misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Pre-spawn Survival
+L1 = "Pre-spawn Survival"
+L2 = c("Mean", "Process SD", "Realized")
+match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "phi_Sb_Sa[.+,.]")
+phi_Sb_Sa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Carcass Correction
+L1 = "Carcass Correction Factor"
+z_diags = diag_fn("z", L1 = L1)
+
+# Initial adult recruitment
+L1 = "Initial Adult Recruitment"
+L2 = c("Mean", "Process SD", "Realized")
+match = c("mu_init_recruits[.]", "sig_init_lrecruits[.]", "^init_recruits[.+,.]")
+init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Straying
+L1 = "Strays"
+L2 = c("Realized Number", "Age/Sex Comp")
+match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = "."))
+stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# combine diagnostic summaries into one massive table
+diags_table = rbind(
+  parr_recruit_diags,
+  pi_diags,
+  phi_Pa_Mb_diags,
+  phi_Mb_Ma_diags,
+  phi_Ma_O0_diags,
+  omega_diags,
+  psi_O1_Rb_diags,
+  psi_O2_Rb_diags,
+  phi_O0_O1_diags,
+  phi_O1_O2_diags,
+  phi_Sb_Sa_diags,
+  misc_ocean_surv_diags,
+  z_diags,
+  init_diags,
+  stray_diags
+)
 ```
 
-`r if (params$mcmc_plots) "### $\\gamma$"`
+This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
+Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
+E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had Rhat values greater than 1.05.
+Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
 
-```{r gamma-diag-plots, eval = params$mcmc_plots, fig.width = 3, fig.height = 6}
-diag_plots(post, "gamma", layout = "4x1")
+* **Rhat** measures convergence of multiple chains to a common target distribution.
+Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should not be used for inference (general rules).
+* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
+Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
+[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
+* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
+Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
+
+The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
+[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
+
+```{r mcmc-diag-table}
+# duplicate the diagnostic output
+kable_table = diags_table
+
+# order the rows
+kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
+kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]
+
+# keep only relevant columns for kable
+kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]
+
+# convert counts of offending parameters to percentages
+kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
+kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
+kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
+kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
+kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
+kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
+kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
+kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
+kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")
+
+# add basic formatting
+colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
+kable_table$Group[is.na(kable_table$Group)] = " "
+kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "
+
+assign_color = function(x, colors = c("white","red")) {
+  pal = colorRampPalette(colors)
+  cols = pal(6)
+  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
+  names(cols) = bin_names
+  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
+  cols_use = cols[as.character(bins)]
+  alpha(unname(cols_use), 0.5)
+}
+
+# produce the kable
+kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
+  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("striped", "condensed")) %>%
+  add_header_above(c(" " = 4, "Rhat" = 3, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
+  column_spec(2:3, width = "150px") %>%
+  column_spec(c(4,7,10), border_right = TRUE) %>%
+  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
+  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
+  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
+  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
+  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
+  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
+  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
+  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
+  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
+  collapse_rows(columns = 1:2)
 ```
 
-`r if (params$mcmc_plots) "### $\\mu$"`
-
-```{r mu-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
-diag_plots(post, "^mu", layout = "5x3")
 ```
 
-`r if (params$mcmc_plots) "### $\\sigma$"`
-
-```{r sig-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
-diag_plots(post, "^sig", layout = "5x3")
 ```
 
-`r if (params$mcmc_plots) "### init_recruits"`
-
-```{r init-recruits-diag-plots, eval = params$mcmc_plots, fig.width = 5, fig.height = 7}
-diag_plots(post, "init_recruits", layout = "4x2")
-```
-
-`r if (params$mcmc_plots) "### surv_scaler"`
-
-```{r surv-scaler-diag-plots, eval = params$mcmc_plots, fig.width = 6, fig.height = 4}
-diag_plots(post, "O_phi_scaler_nat_hat")
-```
-
-`r if (params$mcmc_plots) "### stray"`
-
-_There are some elements of both `n_stray_tot` and `stray_comp` that are exactly zero each MCMC iteration. These are omitted from the plots below._
-
-```{r stray-diag-plots, eval = params$mcmc_plots, fig.width = 7, fig.height = 7}
-stray = post_subset(post, "stray", T)
-non_zero_stray = apply(stray, 2, function(x) all(x != 0))
-stray_nodes = names(non_zero_stray)[non_zero_stray]
-diag_plots(post, stray_nodes, layout = "5x3")
 ```

### 2021-08-03 03-post-process/output-plots.Rmd
Update all fit diagnostic plots to show multiple populations

@@
 
-```
-
-```
-
-```
-
-# Fit to Data {.tabset .tabset-pills}
-
-In the figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data
-
-```{r abundance-data-fits, fig.width = 3, fig.height = 5}
-par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = TeX("$Fall\\,Parr\\,Abundance\\,(At\\,Trap)$"))
-plot_tseries(post_summ(post, "^Mb[.+,2,1]$"), jags_data$Mb_obs[observable,2,1], main = TeX("$Spring\\,Smolt\\,Abundance\\,(At\\,Trap)$"))
-plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = TeX("$Adult\\,Return\\,Abundance$"))
-
+# Fit to Data
+
+In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
+
+## Abundance Data {.tabset .tabset-pills}
+
+### Fall Parr Abundance
+
+```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), jags_data$Pa_obs[observable,i_fall,j], main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Abundance")
-```
-
-## Survival Data
-
-```{r survival-data-fits, fig.width = 5, fig.height = 6}
-par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = TeX("$Summer\\,Parr \\rightarrow LGR"))
-plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = TeX("$Fall\\,Parr \\rightarrow LGR"))
-plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(NOR)"))
-plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = TeX("$Spring\\,Smolt \\rightarrow LGR\\,(HOR)"))
-plot_tseries(post_summ(post, "^phi_Ma_O0[.+,1]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,1]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(NOR)"))
-plot_tseries(post_summ(post, "^phi_Ma_O0[.+,2]$"), expit(jags_data$Lphi_obs_Ma_O0[observable,2]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,(HOR)"))
+mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
+```
+
+### Spring Smolt Abundance
+
+```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), jags_data$Mb_obs[observable,i_spring,o_nor,j], main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling
-
-```{r weir-comp-data-fits, fig.width = 8, fig.height = 5}
-# calculate observed q
-q_obs = t(apply(jags_data$weir_x_obs, 1, function(y) y/sum(y)))
-
-par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-plot_tseries(post_summ(post, "^q_Ra[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Ra[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
+```
+
+### Adult Return Abundance
+
+```{r adult-N-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)), jags_data$Ra_obs[observable,j], main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Return Year")
+mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
+```
+
+## Survival Data {.tabset .tabset-pills}
+
+### Summer Parr $\rightarrow$ LGR
+
+```{r summer-surv-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)), expit(jags_data$Lphi_obs_Pb_Ma[observable,j]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-```
-
-### Carcass Sampling
-
-```{r carc-comp-data-fits, fig.width = 8, fig.height = 5}
-# calculate observed q
-q_obs = t(apply(jags_data$carc_x_obs, 1, function(y) y/sum(y)))
-
-par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,1]$"), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,2]$"), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,3]$"), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,4]$"), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,5]$"), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,6]$"), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,7]$"), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,8]$"), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,9]$"), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,10]$"), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,11]$"), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-plot_tseries(post_summ(post, "^q_Sa_adj[.+,12]$"), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
+```
+
+### Fall Parr $\rightarrow$ LGR
+
+```{r fall-surv-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), expit(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 3.5, fig.height = 5}
-par(oma = c(1.5,1.5,0,0))
-layout(matrix(c(1,2), 2, 1), heights = c(1, 0.65))
-plot_tseries(post_summ(post, "^phi_Sb_Sa["), with(jags_data, carcs_spawned/carcs_sampled)[observable], main = "Successful Spawning")
-mtext(side = 2, "Survival Probability", line = 1.5)
-
-at_x = seq(1, length(observable), 4)
-par(mar = c(2,2,0,1), yaxs = "i")
-mp = barplot(jags_data$carcs_sampled[observable], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
-axis(side = 1, at = mp[at_x], labels = substr( names(jags_data$carcs_sampled[observable]), 3, 4)[at_x])
-box()
-mtext(side = 2, "Carcasses Sampled", line = 1.5)
-mtext(side = 1, "Brood Year", line = 1.5)
+mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
+```
+
+### Spring Smolt $\rightarrow$ LGR (NOR)
+
+```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
+```
+
+### Spring Smolt $\rightarrow$ LGR (HOR)
+
+```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
 ```
@@
 bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)
+### LGR Smolt $\rightarrow O_0$ (NOR)
 
@@
 Sa_tot = post_summ(post, "^Sa_tot[")
+```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
+par(oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Survival")
+```
 
@@
 f_tot = post_summ(post, "^f_tot[")
+### LGR Smolt $\rightarrow O_0$ (HOR)
 
@@
 Pb = post_summ(post, "^Pb[")
+```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
+par(oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Survival")
+```
 
@@
 f_pred = seq(0, max(f_tot[5,]), length = 30)
+## Composition Data {.tabset .tabset-pills .tabset-fade}
 
@@
 Pb_pred = post_summ(Pb_pred, "Pb_pred")
+Within a single year, the values across all panels sum to one.
 
@@
 ols_fit = fit_fecund_BH(jags_data)$BH_fit
+### Weir Sampling {.tabset .tabset-pills}
+
+```{r weir-comp-fit-func}
+weir_comp_fit_plot = function(j) {
+  # calculate observed q
+  q_obs = t(apply(jags_data$weir_x_obs[,,j], 1, function(y) y/sum(y)))
+
+  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+
+  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+```
 
@@
 ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
+#### CAT
 
@@
 ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
+```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
+weir_comp_fit_plot(1)
+```
 
@@
 par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
+#### LOS
 
@@
      xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")
+```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
+weir_comp_fit_plot(2)
+```
 
@@
 axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+#### MIN
 
@@
 lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
+```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
+weir_comp_fit_plot(3)
+```
 
@@
 lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
+#### UGR
 
@@
 points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
+weir_comp_fit_plot(4)
 ```
@@
 ## Total Eggs vs. Total Spawners
+### Carcass Sampling {.tabset .tabset-pills}
 
@@
 The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
+```{r carc-comp-fit-func}
+carc_comp_fit_plot = function(j) {
+
+  # calculate observed q
+  q_obs = t(apply(jags_data$carc_x_obs[,,j], 1, function(y) y/sum(y)))
+
+  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
+}
+```
 
@@
 f_tot = post_summ(post, "^f_tot[")
+#### CAT
 
@@
 Sa_tot = post_summ(post, "^Sa_tot[")
+```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(1)
+```
 
@@
 axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
+#### LOS
 
@@
        lty = c(1,2,3), bty = "n")
+```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(2)
 ```
@@
 The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.
+#### MIN
 
@@
 f_tot = post_summ(post, "^f_tot[")
+```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(3)
+```
 
@@
 Pb = post_summ(post, "^Pb[")
+#### UGR
 
@@
 Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")
+```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(4)
+```
 
@@
 alpha = post_summ(post, "^alpha")
+## Spawn Status Data
 
@@
 axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+```{r spawn-status-fits, fig.width = 8, fig.height = 5}
+par(oma = c(2,2,0,0))
+layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
 
@@
 points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
+  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
+
+  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
+mp = barplot(jags_data$carcs_sampled[observable,j], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
+  at_x = seq(1, length(observable), 4)
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
+  box()
+
+  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
+}
 
@@
 box()
+junk = sapply(1:jags_data$nj, plot_f)
 ```

### 2021-08-03 03-post-process/output-plots.Rmd
Update all plots that display spawner-recruit and overwinter survival information
For multiple populations

@@
 
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 4}
-# extract posterior samples of the BH productivity and capacity parameters
-bh_params = post_subset(post, c("alpha", "^beta$"), matrix = T)
 ### LGR Smolt $\rightarrow O_0$ (NOR)
 
-# extract posterior summaries of total spawners by brood year
-Sa_tot = post_summ(post, "^Sa_tot[")
 ```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
@@
 
-# extract posterior summaries of total egg production by brood year
-f_tot = post_summ(post, "^f_tot[")
 ### LGR Smolt $\rightarrow O_0$ (HOR)
 
-# extract posterior summaries of total parr recruits by brood year
-Pb = post_summ(post, "^Pb[")
 ```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
@@
 
-# predict parr recruits along a sequence of spawner abundances
-Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-f_pred = seq(0, max(f_tot[5,]), length = 30)
 ## Composition Data {.tabset .tabset-pills .tabset-fade}
 
-Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
-colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
-Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-Pb_pred = post_summ(Pb_pred, "Pb_pred")
 Within a single year, the values across all panels sum to one.
 
-# fit ordinary least squares version
-ols_fit = fit_fecund_BH(jags_data)$BH_fit
 ### Weir Sampling {.tabset .tabset-pills}
@@
 
-# draw 1000 random parameters
-ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
 #### CAT
 
-# calculate predicted curve at each pair/summarize
-ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
-ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
 ```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
@@
 
-# graphical parameters
-par(mar = c(3,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
 #### LOS
 
-# empty plot
-plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-     xlab = "Total Egg Production (millions)", ylab = "Parr Recruits", xaxt = "n")
 ```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
@@
 
-x_ticks = axisTicks(par("usr")[1:2], log = F)
-axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
 #### MIN
 
-# draw fitted relationship: Bayesian
-polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
-lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
 ```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
@@
 
-# draw fitted relationship: OLS
-polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
-lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
-lines(ols_R_pred[2,] ~ f_pred, lty = 2)
-lines(ols_R_pred[3,] ~ f_pred, lty = 2)
-lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
 #### UGR
 
-# draw state pairs + uncertainty
-segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = "red")
-segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = "red")
-points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5))
 ```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
@@
 
-## Total Eggs vs. Total Spawners
 ### Carcass Sampling {.tabset .tabset-pills}
 
-This figure illustrates that total spawners is a reasonable index of total egg production.
-The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
 ```{r carc-comp-fit-func}
@@
 
-```{r, fig.width = 6, fig.height = 4}
-# extract posterior summaries of total egg production by brood year
-f_tot = post_summ(post, "^f_tot[")
 #### CAT
 
-# extract posterior summaries of total spawners by brood year
-Sa_tot = post_summ(post, "^Sa_tot[")
 ```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
@@
 
-par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+#### LOS
+
+```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(2)
+```
+
+#### MIN
+
+```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(3)
+```
+
+#### UGR
+
+```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(4)
+```
+
+## Spawn Status Data
+
+```{r spawn-status-fits, fig.width = 8, fig.height = 5}
+par(oma = c(2,2,0,0))
+layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
+
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
+  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
+
+  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
+mp = barplot(jags_data$carcs_sampled[observable,j], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
+  at_x = seq(1, length(observable), 4)
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
+  box()
+
+  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
+}
+
+junk = sapply(1:jags_data$nj, plot_f)
+```
+
+# Spawner-to-Parr Relationship {.tabset .tabset-pills}
+
+## Beverton-Holt
+
+All red components are posterior summaries (medians and 95% credible intervals).
+The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
+
+```{r eggs-to-parr, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # extract posterior samples of the BH productivity and capacity parameters
+  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
+
+  # extract posterior summaries of total spawners by brood year
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
+
+  # extract posterior summaries of total egg production by brood year
+  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
+
+  # extract posterior summaries of total parr recruits by brood year
+  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))
+
+  # predict parr recruits along a sequence of spawner abundances
+  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
+  f_pred = seq(0, max(f_tot[5,]), length = 30)
+
+  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
+  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
+  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
+  Pb_pred = post_summ(Pb_pred, "Pb_pred")
+
+  # fit ordinary least squares version
+  ols_fit = fit_fecund_BH(jags_data, pop = j)$BH_fit
+
+  # draw 1000 random parameters
+  ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
+
+  # calculate predicted curve at each pair/summarize
+  ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
+  ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
+
+  # graphical parameters
+  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+
+  # empty plot
+  plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
+       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
+
+  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
+  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
+
+  # draw fitted relationship: Bayesian
+  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
+  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
+  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
+
+  # draw fitted relationship: OLS
+  polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
+  lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
+  lines(ols_R_pred[2,] ~ f_pred, lty = 2)
+  lines(ols_R_pred[3,] ~ f_pred, lty = 2)
+  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
+
+  # draw state pairs + uncertainty
+  segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = alpha("red", 0.5))
+  segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = alpha("red", 0.5))
+  points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
+mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
+```
+
+## Total Eggs vs. Total Spawners
+
+This figure illustrates that total spawners is a reasonable index of total egg production.
+The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
+
+```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # extract posterior summaries of total spawners by brood year
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
+
+  # extract posterior summaries of total egg production by brood year
+  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
+
+  # graphical parameters
+  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+
+  # empty plot
   plot(f_tot["mean",] ~ Sa_tot["mean",],
@@
        xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-     ylab = "Total Egg Production (Millions)", xlab = "Total Spawners", las = 1, yaxt = "n")
+       ylab = "", xlab = "", las = 1, yaxt = "n")
+
+  # yaxis ticks
   y_ticks = axisTicks(par("usr")[3:4], log = F)
   axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-#### LOS
 
@@
   abline(c(0, 3600), lty = 3)
+
+  if (j == 1) {
     legend("bottomright", title = "If Each Spawner Had:",
            legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-       lty = c(1,2,3), bty = "n")
-```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(2)
+           lty = c(1,2,3), bty = "n", cex = 0.75)
+  }
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
+mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
 ```
@@
 This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha$) in the absence of density dependence.
-#### MIN
-
-```{r, fig.width = 6, fig.height = 4}
+The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
+
+```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
   # extract posterior summaries of total egg production by brood year
-f_tot = post_summ(post, "^f_tot[")
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(3)
-```
-
-# extract posterior summaries of total parr recruits by brood year
-Pb = post_summ(post, "^Pb[")
-#### UGR
+  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
 
   # conversion rates
-Pb_per_f_tot = post_summ(post, "^Pb_per_f_tot[")
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(4)
-```
+  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[.+,pop]", pop = j))
 
   # max survival
-alpha = post_summ(post, "^alpha")
-## Spawn Status Data
-
-par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
+
+  # graphical parameters
+  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+
+  # empty plot
   plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
-     ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
+       # ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
+       ylim = c(0, 1),
        xlim = c(0, max(f_tot["97.5%",])), type = "n",
-     ylab = "Parr per Egg", xlab = "Total Egg Production (Millions)", las = 1, xaxt = "n")
+       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
+
+  # x-axis
   x_ticks = axisTicks(par("usr")[1:2], log = F)
   axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
 
@@
   points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-mp = barplot(jags_data$carcs_sampled[observable,j], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
 
@@
   box()
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
 junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
+mtext(side = 1, outer = T, line = 0.25, "Parr per Egg")
 ```
@@
 
-```{r, fig.width = 6, fig.height = 4}
+```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
   # extract posterior summaries of total spawners by brood year
-Sa_tot = post_summ(post, "^Sa_tot[")
-
-# extract posterior summaries of total parr recruits by brood year
-Pb = post_summ(post, "^Pb[")
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
 
   # conversion rates
-Pb_per_Sa_tot = post_summ(post, "^Pb_per_Sa_tot[")
-
-par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(3,3,1,1))
+  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[.+,pop]", pop = j))
+
+  # graphical parameters
+  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+
+  # empty plot
   plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
@@
        xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-     ylab = "Parr per Spawner", xlab = "Spawners", las = 1)
+       ylab = "", xlab = "", las = 1)
+
   segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
@@
   points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
+mtext(side = 1, outer = T, line = 0.25, "Parr per Spawner")
 ```
@@
 
-```{r overwinter-survival, fig.width = 4, fig.height = 7}
-
-# extract parr, scale it to PEU, and add to posterior samples
-Pa = post_subset(post, "^Pa[", matrix = T)
-Pa_scaled = Pa/jags_data$peu
+```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
+plot_fn = function(j) {
+  # extract parr, scale it to PEU, and create new post object
+  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
+  Pa_scaled = Pa/jags_data$peu[j]
   colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
-post = post_bind(post, Pa_scaled)
+  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))
 
   # summarize posterior of scaled parr
-Pa_scaled_mean = array_format(post_summ(post, "Pa_scaled")["mean",])
-Pa_scaled_lwr = array_format(post_summ(post, "Pa_scaled")["2.5%",])
-Pa_scaled_upr = array_format(post_summ(post, "Pa_scaled")["97.5%",])
+  Pa_scaled_mean = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["mean",])
+  Pa_scaled_lwr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["2.5%",])
+  Pa_scaled_upr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["97.5%",])
 
@@
   Pa_scaled_seq = matrix(NA, 30, 2)
-Pa_scaled_seq[,1] = seq(min(Pa_scaled_lwr[,1], na.rm = T), max(Pa_scaled_upr[,1], na.rm = T), length = 30)
-Pa_scaled_seq[,2] = seq(min(Pa_scaled_lwr[,2], na.rm = T), max(Pa_scaled_upr[,2], na.rm = T), length = 30)
+  Pa_scaled_seq[,i_fall] = seq(min(Pa_scaled_lwr[,i_fall,j], na.rm = TRUE), max(Pa_scaled_upr[,i_fall,j], na.rm = T), length = 30)
+  Pa_scaled_seq[,i_spring] = seq(min(Pa_scaled_lwr[,i_spring,j], na.rm = TRUE), max(Pa_scaled_upr[,i_spring,j], na.rm = T), length = 30)
 
   # extract posteriors of coefficients
-gamma0 = post_subset(post, "gamma0", matrix = T)
-gamma1 = post_subset(post, "gamma1", matrix = T)
+  gamma0 = post_subset(post, sub_index("gamma0[.,pop]", pop = j), matrix = TRUE)
+  gamma1 = post_subset(post, sub_index("gamma1[.,pop]", pop = j), matrix = TRUE)
 
   # extract/format posterior summaries of realized survivals
-phi_Pa_Mb_mean = array_format(post_summ(post, "^phi_Pa_Mb[")["mean",])
-phi_Pa_Mb_lwr = array_format(post_summ(post, "^phi_Pa_Mb[")["2.5%",])
-phi_Pa_Mb_upr = array_format(post_summ(post, "^phi_Pa_Mb[")["97.5%",])
+  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["mean",])
+  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["2.5%",])
+  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["97.5%",])
 
   # function to create predicted survival curves for one posterior sample
-f = function(i) {
+  pred_fn = function(i) {
     pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
@@
   # calculate predicted survivals and add to posterior samples
-pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), f))
-post = post_bind(post, pred_phi_Pa_Mb)
+  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pa = post_bind(post_pa, pred_phi_Pa_Mb)
 
   # summarize predicted survivals
-pred_phi_Pa_Mb_mean = array_format(post_summ(post, "pred_phi_Pa_Mb")["mean",])
-pred_phi_Pa_Mb_lwr = array_format(post_summ(post, "pred_phi_Pa_Mb")["2.5%",])
-pred_phi_Pa_Mb_upr = array_format(post_summ(post, "pred_phi_Pa_Mb")["97.5%",])
+  pred_phi_Pa_Mb_mean = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["mean",])
+  pred_phi_Pa_Mb_lwr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["2.5%",])
+  pred_phi_Pa_Mb_upr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["97.5%",])
 
   # function to draw plot for one LH-type
-plot_fun = function(i) {
+  plot_fn2 = function(i) {
     # blank plot of correct dimensions
     plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i], phi_Pa_Mb_upr[,i], na.rm = T),
+         ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i,j], phi_Pa_Mb_upr[,i,j], na.rm = T),
          xlim = range(0, Pa_scaled_seq), 
-       main = c("Fall Migrants", "Spring Migrants")[i]
+         main = ifelse(i == 1, pops[j], "")
     )
@@
     # realized survivals
-  segments(Pa_scaled_lwr[,i], phi_Pa_Mb_mean[,i], Pa_scaled_upr[,i], phi_Pa_Mb_mean[,i], col = alpha("red", 0.5))
-  segments(Pa_scaled_mean[,i], phi_Pa_Mb_lwr[,i], Pa_scaled_mean[,i], phi_Pa_Mb_upr[,i], col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean[,i] ~ Pa_scaled_mean[,i], pch = 21, col = "red", bg = alpha("salmon", 0.5))
+    segments(Pa_scaled_lwr[,i,j], phi_Pa_Mb_mean[,i,j], Pa_scaled_upr[,i,j], phi_Pa_Mb_mean[,i,j], col = alpha("red", 0.5))
+    segments(Pa_scaled_mean[,i,j], phi_Pa_Mb_lwr[,i,j], Pa_scaled_mean[,i,j], phi_Pa_Mb_upr[,i,j], col = alpha("red", 0.5))
+    points(phi_Pa_Mb_mean[,i,j] ~ Pa_scaled_mean[,i,j], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
   }
@@
   # create the plot
-par(mfrow = c(2,1), mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1), oma = c(2,2,0,0))
-plot_fun(1)
-plot_fun(2)
-mtext(side = 1, line = 1, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
-mtext(side = 2, line = 1, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-# Equivilency Rates
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot_fn2(1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
+  plot_fn2(2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
+
+}
+
+par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
+mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
+```
+
+# Equivilency Rates {.tabset .tabset-pills}
 
@@
 
-```{r sar-plot, fig.width = 6, fig.height = 4}
-# function to calculate posterior 
-get_SAR_post = function(post, jags_data) {
-  # extract posterior abundances
-  Ra_post = post_subset(post, "^Ra[", T) # adults returning to Columbia River mouth
-  Ma_post = post_subset(post, "^Ma[", T) # smolts at top of LGD
-
-  # number of saved samples
-  ni = post_dim(post, "saved")
-
-  # first and last brood year SAR can be calculated for
-  first_SAR_y = jags_data$kmax + 1
-  last_SAR_y = jags_data$ny - jags_data$kmax
-
-  # containers
-  nat_SAR = hat_SAR = NULL
-
-  # loop over mcmc iters
-  for (i in 1:ni) {
-    # extract quantities for this iter
-    Ra = array_format(Ra_post[i,])
-    Ma = array_format(Ma_post[i,])
-
-    # give names
-    dimnames(Ra) = dimnames(jags_data$n_remove)
-    dimnames(Ma) = dimnames(jags_data$Mb_obs)
-
-    # drop sex structure from Ra
-    Ra = Ra[,,1,] + Ra[,,2,]
-
-    # loop over years
-    nat_SAR_i = hat_SAR_i = NULL
-    for (y in first_SAR_y:last_SAR_y) {
-      # sum up smolts across life history types
-      nat_smolt = sum(Ma[y,,"Nat"])
-      hat_smolt = sum(Ma[y,,"Hat"])
-
-      # sum up returning adults from this brood
-      nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
-      hat_adults = Ra[y+3,1,"Hat"] + Ra[y+4,2,"Hat"] + Ra[y+5,3,"Hat"]
-
-      nat_SAR_i = c(nat_SAR_i, nat_adults/nat_smolt)
-      hat_SAR_i = c(hat_SAR_i, hat_adults/hat_smolt)
-    }
-
-    # combine with other mcmc iters
-    nat_SAR = rbind(nat_SAR, nat_SAR_i)
-    hat_SAR = rbind(hat_SAR, hat_SAR_i)
-  }
-
-  colnames(nat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",1]")
-  colnames(hat_SAR) = paste0("SAR[", first_SAR_y:last_SAR_y, ",2]")
-
-  # drop out SAR years for hatchery fish where missing
-  hat_SAR = hat_SAR[,!is.na(colSums(hat_SAR))]
-
-  out = cbind(nat_SAR, hat_SAR)
-  return(out)
-}
-
-# apply the function
-SAR_post = get_SAR_post(post, jags_data)
-
-# combine samples with main posterior object
-post = post_bind(post, SAR_post)
-
-# calculate/format posterior summaries
-SAR_mean = array_format(post_summ(post, "SAR")["mean",]) * 100
-SAR_lwr = array_format(post_summ(post, "SAR")["2.5%",]) * 100
-SAR_upr = array_format(post_summ(post, "SAR")["97.5%",]) * 100
-
-SAR_mean[SAR_mean == "Inf"] = NA
-SAR_lwr[SAR_lwr == "Inf"] = NA
-SAR_upr[SAR_upr == "Inf"] = NA
-
-# subset years
-all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
-SAR_yrs = all_yrs[1:nrow(SAR_mean)]
-
-# graphics device
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.2)
-
-# blank plot with appropriate dimensions
-plot(SAR_mean[,1] ~ SAR_yrs, ylab = "Adults/100 Smolt", xlab = "Brood Year",
-     xlim = range(all_yrs), ylim = c(0, max(SAR_upr, na.rm = T)), type = "n", las = 1)
-
-# draw posterior summary for natural origin
-polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,1], rev(SAR_upr[,1])), col = alpha("skyblue2", 0.5), border = NA)
-lines(SAR_lwr[,1] ~ SAR_yrs, col = "blue", lty = 2)
-lines(SAR_upr[,1] ~ SAR_yrs, col = "blue", lty = 2)
-lines(SAR_mean[,1] ~ SAR_yrs, col = "blue", lwd = 2)
-
-# draw posterior summary for hatchery origin
-polygon(x = c(SAR_yrs, rev(SAR_yrs)), y = c(SAR_lwr[,2], rev(SAR_upr[,2])), col = alpha("salmon", 0.5), border = NA)
-lines(SAR_lwr[,2] ~ SAR_yrs, col = "red", lty = 2)
-lines(SAR_upr[,2] ~ SAR_yrs, col = "red", lty = 2)
-lines(SAR_mean[,2] ~ SAR_yrs, col = "red", lwd = 2)
-
-# draw a legend
-legend("topright", legend = c("Natural", "Hatchery"), title = "Origin",
-       pch = 22, col = c("blue", "red"), pt.cex = 2, pt.bg = alpha(c("skyblue2", "salmon"), 0.5), bty = "n")
+```{r adults-per-smolt, fig.width = 6, fig.height = 5}
+sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]
+
+plot_fn = function(j) {
+  # which years had zero hatchery smolt released
+  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
+
+  # summarize rates
+  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_nor, pop = j)) * 100
+  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_hor, pop = j)) * 100
+
+  # make hatchery values NA in year with no smolt
+  Ra_per_Ma_hor[,zero_hor_smolt] = NA
+
+  # plot natural origin time series
+  plot_tseries(est = Ra_per_Ma_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, 10))
+
+  # add hatchery origin time series
+  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
+  lines(Ra_per_Ma_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
+  lines(Ra_per_Ma_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
+  lines(Ra_per_Ma_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)
+
+  if (j == 1) {
+    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
+         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
+  }
+}
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
 ```
@@
 
-```{r, fig.width = 6, fig.height = 4}
-par(oma = c(1,1,0,0))
-plot_tseries(est = post_summ(post, "Pb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
-mtext(side = 2, outer = T, line = 0, "Parr/Spawner")
+```{r parr-per-spawner, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
+  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
 ```
@@
 
-```{r, fig.width = 6, fig.height = 4}
-par(oma = c(1,1,0,0))
-plot_tseries(est = post_summ(post, "Mb_per_Sa_tot["), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
-mtext(side = 2, outer = T, line = 0, "Smolt/Spawner")
+```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
+  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
 ```
@@
 
-```{r, fig.width = 6, fig.height = 4}
-all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
-
-par(oma = c(1,1,0,0))
-plot_tseries(est = post_summ(post, "Sa_tot_per_Sa_tot["), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)])
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
-mtext(side = 2, outer = T, line = 0, "Spawners/Spawner")
+```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
+  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[.+,pop]", pop = j)), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)], main = pops[j])
  abline(h = 1, lty = 2)
-```
-
-# Number of Strays
-
-```{r stray-tot-plot, fig.width = 6, fig.height = 4}
-par(oma = c(1,1,0,0))
-plot_tseries(post_summ(post, "n_stray_tot"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]))
-mtext(side = 1, outer = T, line = -0.5, "Return Year")
-mtext(side = 2, outer = T, line = 0, "Number of Strays")
+}
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
+```
+
+# Straying Dynamics {.tabset .tabset-pills}
+
+## Number of Strays
+
+```{r n-stray, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
+  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Return Year")
+mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
+```
+
+## Stray Composition
+
+```{r stray-comp, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
+  x = post_summ(post, sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = j))
+
+  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
+  mp = barplot(x["mean",], ylim = c(0, 0.6), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
+  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
+  axis(side = 1, at = mp, labels = paste0(rep(c("Female", "Male"), each = jags_data$nk), "-", rep(jags_data$kmin:jags_data$kmax, jags_data$ns)), las = 2)
+  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
+}
+
+par(mfrow = c(2,2), oma = c(0,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age/Sex")
 ```

### 2021-08-03 03-post-process/output-plots.Rmd
Update remaining features of output-plots.Rmd
* sex apportionment, ocean survival, and maturity time series
* add boxplots showing posterior summaries of key parameter estimates compared across populations, where applicable

@@
 
-```{r sex-plots, fig.width = 7, fig.height = 4}
-par(mfrow = c(1,2), oma = c(1,1,0,0))
-plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames
-                                                                                           (jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
-mtext(side = 2, outer = T, line = 0, "Female Proportion of Esutary Smolts")
-```
-
-# Maturity
-
-```{r maturity-plots, fig.width = 4, fig.height = 7}
-par(mfrow = c(4,2), oma = c(1,1,0,0))
-plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,1]$"), main = "Age 3 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,2]$"), main = "Age 3 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,1]$"), main = "Age 3 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,2]$"), main = "Age 3 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,1]$"), main = "Age 4 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,2]$"), main = "Age 4 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,1]$"), main = "Age 4 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,2]$"), main = "Age 4 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-
-mtext(side = 1, outer = T, line = -0.5, "Brood Year")
-mtext(side = 2, outer = T, line = 0, "Pr(Mature-at-Age|Alive in Ocean)")
-
-```
-
-# Parameter Estimates {.tabset .tabset-pills}
-
-**Quick refresher on parameter names**
-_In alphabetical order, as displayed in figures_
-
-* `mu_omega[1]`: mean probability of being a female at ocean entry
-* `mu_phi_Ma_O0`: mean probability of surviving from LGD to ocean entry
-* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)
-* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
-* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
-* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
-* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)
-
-`sig_L*` are the among-year logit-normal standard deviations of these quantities. `sigma_Pb` is lognormal standard deviation of parr recruitment.
-
-## Means
-
-```{r mu-boxplots, fig.width = 6, fig.height = 6}
-# parameters to display
-keep = match_params(post, "mu")
-
-# remove redundant elements
-keep = keep[-which(keep %in% c("mu_init_recruits", "mu_omega[2]", "mu_phi_Mb_Ma[2]", "mu_pi[2]"))]
-
-# extract posterior samples of these parameters: for drawing initial box plot
-post_samples = post_subset(post, keep, T)
-
-# calculate custom summaries of these parameters: for drawing actual box plot
-post_summaries = post_summ(post, keep, probs = c(0.025, 0.25, 0.5, 0.75, 0.975))[-c(1:2),]
-
-# graphical parameters
-par(mar = c(8,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
-
-# set up a box plot and replace the stats with the custom stats
-bp = boxplot(post_samples, plot = F)
-bp$stats = post_summaries
-
-# draw the box plot
-bxp(bp, ylim = c(0,1), outline = F, las = 2, boxcol = "red", medcol = "red", whiskcol = "red", staplecol = "red", boxfill = alpha("salmon", 0.5))
-```
-
-## Standard Deviations
-
-```{r sig-boxplots, fig.width = 6, fig.height = 6}
-# parameters to display
-keep = match_params(post, "sig")
-
-# remove redundant elements
-keep = keep[-which(keep %in% c("sig_init_lrecruits", "sig_Lphi_Mb_Ma[2]"))]
-
-# extract posterior samples of these parameters: for drawing initial box plot
-post_samples = post_subset(post, keep, T)
-
-# calculate custom summaries of these parameters: for drawing actual box plot
-post_summaries = post_summ(post, keep, probs = c(0.025, 0.25, 0.5, 0.75, 0.975))[-c(1:2),]
-
-# graphical parameters
-par(mar = c(8,3,1,1), mgp = c(2,0.3,0), tcl = -0.2)
-
-# set up a box plot and replace the stats with the custom stats
-bp = boxplot(post_samples, plot = F)
-bp$stats = post_summaries
-
-# draw the box plot
-bxp(bp, ylim = c(0,max(post_summaries)), outline = F, las = 2, boxcol = "red", medcol = "red", whiskcol = "red", staplecol = "red", boxfill = alpha("salmon", 0.5))
-```
-
-# Numerical Summaries
-
-## Recruitment Function
-
-```{r}
-# extract posterior summaries
-alpha_summ = post_summ(post, "alpha", digits = 3)
-beta_summ = post_summ(post, "^beta$", digits = -3)
-beta_per_peu_summ = post_summ(post, "beta_per_peu", digits = -1)
-sigma_summ = post_summ(post, "sigma_Pb", digits = 3)
-
-# create/format the table
-tab = cbind(alpha_summ, beta_summ, beta_per_peu_summ, sigma_summ)
-colnames(tab) = c("$\\alpha$", "$\\beta$", "$\\beta/\\mathrm{PEU}$", "$\\sigma_{Pb}$")
-
-# produce html table
-kable(tab, format.args = list(big.mark = ","), escape = F) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = T)
-```
-
-## Carcass Correction Factors
-
-```{r}
-# extract posterior summaries
-carc_adj = post_summ(post, "carc_adj", digits = 1)
-
-# create/format table
-x = paste0(carc_adj["mean",], " (", carc_adj["2.5%",], " -- ", carc_adj["97.5%",], ")")
-names(x) = colnames(carc_adj)
-tab = array_format(x)
-colnames(tab) = c("Female", "Male")
-rownames(tab) = c("Age 3", "Age 4", "Age 5")
-
-# produce html table
-kable(tab) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = T)
-```
-
-## AR(1) Coefficients
-
-```{r}
-post_summ(post, "kappa", Rhat = TRUE, neff = TRUE, digits = 3)
+```{r sex-plots, fig.width = 8, fig.height = 5}
+plot_fn = function(j) {
+    par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot_tseries(post_summ(post, sub_index("^omega[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = pops[j], yrs = as.numeric(rownames(jags_data$Pa_obs[observable,,j])), ylim = c(0,1)); if (j == 1) mtext(side = 2, line = 1.5, "NOR")
+
+  plot_tseries(post_summ(post, sub_index("^omega[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = NULL, yrs = as.numeric(rownames(jags_data$Pa_obs[observable,,j])), ylim = c(0,1)); if (j == 1) mtext(side = 2, line = 1.5, "HOR")
+}
+
+par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, line = 1.5, outer = T, "Brood Year", cex = 1.2)
+mtext(side = 2, line = 2, outer = T, "Proportion Female", cex = 1.2)
+```
+
+# Maturity {.tabset .tabset-pills}
+
+```{r maturity-plot-fn}
+maturity_plot = function(j) {
+  par(mfrow = c(4,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = "Age 3 Females (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = "Age 3 Females (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_nor, pop = j)), main = "Age 3 Males (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_hor, pop = j)), main = "Age 3 Males (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = "Age 4 Females (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = "Age 4 Females (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_nor, pop = j)), main = "Age 4 Males (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_hor, pop = j)), main = "Age 4 Males (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+
+  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
+}
+```
+
+## CAT
+
+```{r, fig.width = 4, fig.height = 7}
+maturity_plot(1)
+```
+
+## LOS
+
+```{r, fig.width = 4, fig.height = 7}
+maturity_plot(2)
+```
+
+## MIN
+
+```{r maturity-min, fig.width = 4, fig.height = 7}
+maturity_plot(3)
+```
+
+## UGR
+
+```{r maturity-ugr, fig.width = 4, fig.height = 7}
+maturity_plot(4)
+```
+
+# Parameter Summaries {.tabset .tabset-dropdown}
+
+```{r my-boxplot-function}
+my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), ...) {
+  # extract posterior samples and rename them
+  post_sub = post_subset(post, params, matrix = TRUE)
+
+  if (ncol(post_sub) >= 2) {
+    colnames(post_sub) = ticklabs
+  }
+
+  # initialize a boxplot object
+  bp = boxplot(post_sub, plot = FALSE)
+
+  # replace the summary stats with my preferred quantiles
+  par(mar = c(2,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
+  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
+  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
+      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
+} 
+```
+
+## Parr Recruitment
+
+```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,3))
+my_boxplot("^alpha[.]$", "Productivity")
+my_boxplot("^beta[.]$", "Capacity")
+my_boxplot("^sigma_Pb[.]$", "Process SD")
+```
+
+## Life History Apportionment
+
+```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
+my_boxplot("^sig_Lpi[.]$", "Process SD")
+```
+
+## Overwinter Survival {.tabset .tabset-pills}
+
+### Logistic Function Parameters
+
+```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,3))
+my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
+my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
+my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope")
+```
+
+### Process SD
+
+```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,3))
+my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
+my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
+```
+
+## Movement Survival to LGR {.tabset .tabset-pills}
+
+### Mean
+
+```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_nor, pop = "."), "Average Migration Survival", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
+```
+
+### Process SD
+
+```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_nor, pop = "."), "Process SD", main = "NOR")
+my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Process SD", main = "HOR")
+```
+
+## Movement Survival to Ocean
+
+```{r lgr-to-ocean-bxp}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
+```
+
+## Sex Apportionment {.tabset .tabset-pills}
+
+### Mean
+
+```{r sex-bxp1, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_omega[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "Average Proportion Female", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_omega[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "Average Proportion Female", main = "HOR", ylim = c(0,1))
+```
+
+### Process SD
+
+```{r sex-bxp2, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("sig_Lomega[origin,pop]", origin = o_nor, pop = "."), "Process SD", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("sig_Lomega[origin,pop]", origin = o_hor, pop = "."), "Process SD", main = "HOR", ylim = c(0,1))
+```
+
+## Probability of Maturing at Age-3 {.tabset .tabset-pills}
+
+### Females
+
+```{r age3-female-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```
+
+### Males
+
+```{r age3-male-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_male, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_male, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```
+
+## Probability of Maturing at Age-4 {.tabset .tabset-pills}
+
+### Females
+
+```{r age-4-female-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```
+
+### Males
+
+```{r age-4-male-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_male, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_male, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```
+
+## Ocean Survival {.tabset .tabset-pills}
+
+### Year 1
+
+```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_O0_O1[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
+my_boxplot("sig_Lphi_O0_O1", ylab = "Process SD")
+```
+
+### Year 2
+
+```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_O1_O2[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
+my_boxplot("sig_Lphi_O1_O2", ylab = "Process SD")
+```
+
+## Pre-spawn Survival
+
+```{r prespawn-surv-bxp}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
+my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
 ```
@@
 
-```{r, comment = NA}
+```{r jags-model, comment = NA}
 # print the JAGS model code
@@
 
-```{r, comment = NA}
+```{r jags-data, comment = NA}
 # print the JAGS model data

### 2021-08-04 03-post-process/output-plots.Rmd
Fix typos in axis labels in a handful of plots in output-plots

@@
 
-This figure shows the inherent density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
+This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
 The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
@@
 mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 1, outer = T, line = 0.25, "Parr per Egg")
+mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
 ```
@@
 mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 1, outer = T, line = 0.25, "Parr per Spawner")
+mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
 ```

### 2021-08-04 03-post-process/output-plots.Rmd
Add aggregated composition plots to output-plots
Can help diagnose lack of fit issues with respect to age, sex, or origin specifically

@@
 # read information from this model
-model_info = readRDS(file.path(in_dir, paste0(params$pop, "output-", params$scenario, ".rds")))
+model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
 
@@
 post = model_info$post
+# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
 jags_data = model_info$jags_data
@@
 k_5      = 3  # age 5 is k = 3
-```
-
-The code used to render this output relies heavily on Staton's 'postpack' package (now available on CRAN).
-Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.
+
+# kso represents "age/sex/origin" combo
+# e.g., kso = 1 is age 3 female NORs
+# e.g., kso = 12 is age 5 male HORs
+# these objects specify which elements of kso are for different aggregations of these
+kso_age = list(
+  kso_3 = c(1, 4, 7, 10),
+  kso_4 = c(2, 5, 8, 11),
+  kso_5 = c(3, 6, 9, 12)
+)
+
+kso_sex = list(
+  kso_female = c(1,2,3,7,8,9),
+  kso_male = c(4,5,6,10,11,12)
+)
+
+kso_origin = list(
+  kso_nor = 1:6,
+  kso_hor = 7:12
+)
+```
 
@@
 
+```{r calculate-aggregated-comps-model}
+# extract the full posteriors of the two composition sets
+q_Ra_full = post_subset(post, "q_Ra", matrix = TRUE)
+q_Sa_adj_full = post_subset(post, "q_Sa", matrix = TRUE)
+
+# primary containers: will store final recalculated output
+q_Ra_age = q_Sa_adj_age = q_Ra_sex = q_Sa_adj_sex = q_Ra_origin = q_Sa_adj_origin = NULL
+
+# number of posterior samples
+n = post_dim(post, "saved")
+
+# loop through posterior samples, calculate various aggregates of composition by type
+for (i in 1:n) {
+
+  # format the posterior draw as arrays -- easier to subset
+  q_Ra = array_format(q_Ra_full[i,])
+  q_Sa_adj = array_format(q_Sa_adj_full[i,])
+
+  ## BY AGE, AGGREGATED ACROSS SEX AND ORIGIN
+
+  # containers
+  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
+  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
+  for (j in 1:jags_data$nj) {
+    for (k in 1:jags_data$nk) {
+      # calculate aggregate proportions for each age
+      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,kso_age[[k]],j])
+      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,kso_age[[k]],j])
+
+      # build the element identifiers - for building names later
+      inds_1_age[,k,j] = 1:jags_data$ny
+      inds_2_age[,k,j] = k
+      inds_3_age[,k,j] = j
+    }
+  }
+
+  # vectorize, add names, and remove NAs
+  q_Ra_age_v = as.numeric(q_Ra_age_tmp)
+  q_Sa_adj_age_v = as.numeric(q_Sa_adj_age_tmp)
+  names(q_Ra_age_v) = paste0("q_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
+  names(q_Sa_adj_age_v) = paste0("q_Sa_adj_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
+  q_Ra_age_v = q_Ra_age_v[!is.na(q_Ra_age_v)]
+  q_Sa_adj_age_v = q_Sa_adj_age_v[!is.na(q_Sa_adj_age_v)]
+
+  ## BY SEX, AGGREGATED ACROSS AGE AND ORIGIN
+
+  # containers
+  q_Ra_sex_tmp = q_Sa_adj_sex_tmp = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
+  inds_1_sex = inds_2_sex = inds_3_sex = q_Ra_sex_tmp
+  for (j in 1:jags_data$nj) {
+    for (s in 1:jags_data$ns) {
+      # calculate aggregate proportions for each sex
+      q_Ra_sex_tmp[,s,j] = rowSums(q_Ra[,kso_sex[[s]],j])
+      q_Sa_adj_sex_tmp[,s,j] = rowSums(q_Sa_adj[,kso_sex[[s]],j])
+
+      # build the element identifiers - for building names later
+      inds_1_sex[,s,j] = 1:jags_data$ny
+      inds_2_sex[,s,j] = s
+      inds_3_sex[,s,j] = j
+    }
+  }
+
+  # vectorize, add names, and remove NAs
+  q_Ra_sex_v = as.numeric(q_Ra_sex_tmp)
+  q_Sa_adj_sex_v = as.numeric(q_Sa_adj_sex_tmp)
+  names(q_Ra_sex_v) = paste0("q_Ra_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
+  names(q_Sa_adj_sex_v) = paste0("q_Sa_adj_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
+  q_Ra_sex_v = q_Ra_sex_v[!is.na(q_Ra_sex_v)]
+  q_Sa_adj_sex_v = q_Sa_adj_sex_v[!is.na(q_Sa_adj_sex_v)]
+
+  ## BY ORIGIN, AGGREGATED ACROSS AGE AND SEX
+
+  # containers
+  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
+  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
+  for (j in 1:jags_data$nj) {
+    for (o in 1:jags_data$no) {
+      # calculate aggregate proportions for each origin
+      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,kso_origin[[o]],j])
+      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,kso_origin[[o]],j])
+
+      # build the element identifiers - for building names later
+      inds_1_origin[,o,j] = 1:jags_data$ny
+      inds_2_origin[,o,j] = o
+      inds_3_origin[,o,j] = j
+    }
+  }
+
+  # vectorize, add names, and remove NAs
+  q_Ra_origin_v = as.numeric(q_Ra_origin_tmp)
+  q_Sa_adj_origin_v = as.numeric(q_Sa_adj_origin_tmp)
+  names(q_Ra_origin_v) = paste0("q_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
+  names(q_Sa_adj_origin_v) = paste0("q_Sa_adj_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
+  q_Ra_origin_v = q_Ra_origin_v[!is.na(q_Ra_origin_v)]
+  q_Sa_adj_origin_v = q_Sa_adj_origin_v[!is.na(q_Sa_adj_origin_v)]
+
+  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
+
+  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
+  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
+  q_Ra_sex = rbind(q_Ra_sex, q_Ra_sex_v)
+  q_Sa_adj_sex = rbind(q_Sa_adj_sex, q_Sa_adj_sex_v)
+  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
+  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)
+
+}
+
+# combine new calculated quantites into a big matrix
+q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_sex, q_Sa_adj_sex, q_Ra_origin, q_Sa_adj_origin)
+
+# combine with the rest of the posterior samples
+post = post_bind(post, q_new)
+
+```
+
+```{r calculate-aggregated-comps-data}
+
+# these are the observed proportions by age (aggregated across sex and origin), sex (aggregated across age and origin), and origin (aggregated across age and sex)
+
+# containers
+q_weir_age_obs = q_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
+q_weir_sex_obs = q_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
+q_weir_origin_obs = q_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
+
+for (j in 1:jags_data$nj) {
+  # calculate aggregate proportions for each age
+  for (k in 1:jags_data$nk) {
+    q_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])/jags_data$weir_nx_obs[,j]
+    q_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])/jags_data$carc_nx_obs[,j]
+  }
+
+  # calculate aggregate proportions for each sex
+  for (s in 1:jags_data$ns) {
+    q_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])/jags_data$weir_nx_obs[,j]
+    q_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])/jags_data$carc_nx_obs[,j]
+  }
+
+  # calculate aggregate proportions for each origin
+  for (o in 1:jags_data$no) {
+    q_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])/jags_data$weir_nx_obs[,j]
+    q_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])/jags_data$carc_nx_obs[,j]
+  }
+}
+
+dimnames(q_weir_age_obs)[[1]] = dimnames(q_weir_sex_obs)[[1]] = dimnames(q_weir_origin_obs)[[1]] = dimnames(q_carc_age_obs)[[1]] = dimnames(q_carc_sex_obs)[[1]] = dimnames(q_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
+
+q_weir_new_obs = list(
+  q_weir_age_obs = q_weir_age_obs,
+  q_weir_sex_obs = q_weir_sex_obs,
+  q_weir_origin_obs = q_weir_origin_obs
+)
+
+q_carc_new_obs = list(
+  q_carc_age_obs = q_carc_age_obs,
+  q_carc_sex_obs = q_carc_sex_obs,
+  q_carc_origin_obs = q_carc_origin_obs
+)
+
+```
+
 Within a single year, the values across all panels sum to one.
@@
 
-```{r weir-comp-fit-func}
+```{r weir-comp-fit-funcs}
+
+# for completely disaggregated fits
 weir_comp_fit_plot = function(j) {
@@
 
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
   mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
 }
-```
-
-#### CAT
+
+# for fits to each age, aggregated across sexes and origins
+weir_comp_fit_plot_age = function(j) {
+  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,1,j], main = TeX("$Age\\,3$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,2,j], main = TeX("$Age\\,4$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,3,j], main = TeX("$Age\\,5$"), ylim = c(0,1))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+
+# for fits to each sex, aggregated across ages and origins
+weir_comp_fit_plot_sex = function(j) {
+  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,1,j], main = TeX("$Females$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,2,j], main = TeX("$Males$"), ylim = c(0,1))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+
+# for fits to each origin, aggregated across ages and sexes
+weir_comp_fit_plot_origin = function(j) {
+  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,1,j], main = TeX("$NOR$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,2,j], main = TeX("$HOR$"), ylim = c(0,1))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+```
+
+#### By Age/Sex/Origin {.tabset .tabset-pills}
+
+This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
+
+##### CAT
 
 ```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(1)
-```
-
-#### LOS
-
-```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(2)
-```
-
-#### MIN
+weir_comp_fit_plot(j_cat)
+```
+
+##### LOS
+
+```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
+weir_comp_fit_plot(j_los)
+```
+
+##### MIN
 
 ```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(3)
-```
-
-#### UGR
+weir_comp_fit_plot(j_min)
+```
+
+##### UGR
 
 ```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(4)
+weir_comp_fit_plot(j_ugr)
+```
+
+#### By Age {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the weir composition data by age, aggregated by sex and origin.
+
+##### CAT
+
+```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+weir_comp_fit_plot_age(j_cat)
+```
+
+##### LOS
+
+```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+weir_comp_fit_plot_age(j_los)
+```
+
+##### MIN
+
+```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+weir_comp_fit_plot_age(j_min)
+```
+
+##### UGR
+
+```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+weir_comp_fit_plot_age(j_ugr)
+```
+
+#### By Sex {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the weir composition data by sex, aggregated by age and origin.
+
+##### CAT
+
+```{r cat-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_sex(j_cat)
+```
+
+##### LOS
+
+```{r los-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_sex(j_los)
+```
+
+##### MIN
+
+```{r min-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_sex(j_min)
+```
+
+##### UGR
+
+```{r ugr-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_sex(j_ugr)
+```
+
+#### By Origin {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the weir composition data by origin, aggregated by age and sex.
+
+##### CAT
+
+```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_origin(j_cat)
+```
+
+##### LOS
+
+```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_origin(j_los)
+```
+
+##### MIN
+
+```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_origin(j_min)
+```
+
+##### UGR
+
+```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+weir_comp_fit_plot_origin(j_ugr)
 ```
@@
 
-```{r carc-comp-fit-func}
+```{r carc-comp-fit-funcs}
+
+# for completely disaggregated fits
 carc_comp_fit_plot = function(j) {
@@
   plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
   mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
 }
-```
-
-#### CAT
+
+# for fits to each age, aggregated across sexes and origins
+carc_comp_fit_plot_age = function(j) {
+  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,1,j], main = TeX("$Age\\,3$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,2,j], main = TeX("$Age\\,4$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,3,j], main = TeX("$Age\\,5$"))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+
+# for fits to each sex, aggregated across ages and origins
+carc_comp_fit_plot_sex = function(j) {
+  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,1,j], main = TeX("$Females$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,2,j], main = TeX("$Males$"))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+
+# for fits to each origin, aggregated across ages and sexes
+carc_comp_fit_plot_origin = function(j) {
+  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,1,j], main = TeX("$NOR$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,2,j], main = TeX("$HOR$"))
+  mtext(side = 1, outer = T, line = 0.25, "Return Year")
+  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+}
+
+```
+
+#### By Age/Sex/Origin {.tabset .tabset-pills}
+
+This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
+
+##### CAT
 
 ```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(1)
-```
-
-#### LOS
-
-```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(2)
-```
-
-#### MIN
+carc_comp_fit_plot(j_cat)
+```
+
+##### LOS
+
+```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
+carc_comp_fit_plot(j_los)
+```
+
+##### MIN
 
 ```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(3)
-```
-
-#### UGR
+carc_comp_fit_plot(j_min)
+```
+
+##### UGR
 
 ```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(4)
+carc_comp_fit_plot(j_ugr)
+```
+
+#### By Age {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the carcass composition data by age, aggregated by sex and origin.
+
+##### CAT
+
+```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+carc_comp_fit_plot_age(j_cat)
+```
+
+##### LOS
+
+```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+carc_comp_fit_plot_age(j_los)
+```
+
+##### MIN
+
+```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+carc_comp_fit_plot_age(j_min)
+```
+
+##### UGR
+
+```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+carc_comp_fit_plot_age(j_ugr)
+```
+
+#### By Sex {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the carcass composition data by sex, aggregated by age and origin.
+
+##### CAT
+
+```{r cat-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_sex(j_cat)
+```
+
+##### LOS
+
+```{r los-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_sex(j_los)
+```
+
+##### MIN
+
+```{r min-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_sex(j_min)
+```
+
+##### UGR
+
+```{r ugr-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_sex(j_ugr)
+```
+
+#### By Origin {.tabset .tabset-pills}
+
+These figures show the agreement of the model with the carcass composition data by origin, aggregated by age and sex.
+
+##### CAT
+
+```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_origin(j_cat)
+```
+
+##### LOS
+
+```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_origin(j_los)
+```
+
+##### MIN
+
+```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_origin(j_min)
+```
+
+##### UGR
+
+```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+carc_comp_fit_plot_origin(j_ugr)
 ```

### 2021-08-05 03-post-process/output-plots.Rmd
Add plots that show the multinomial sample sizes for weir and carcass composition sampling

@@
 
+# for multinomial sample size
+weir_sample_size = function(j) {
+  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+  mp = barplot(jags_data$weir_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
+               ylim = c(0, max(jags_data$weir_nx_obs[observable,j], na.rm = TRUE)),
+               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
+  usr = par("usr")
+  at_x = seq(1, length(observable), 4)
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$weir_nx_obs[observable,j]), 3, 4)[at_x])
+  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
+}
+
 # for completely disaggregated fits
@@
 
+#### Total Sample Size {.tabset .tabset-pills}
+
+These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
+
+##### CAT
+
+```{r cat-weir-ss, fig.width = 6, fig.height = 4}
+weir_sample_size(j_cat)
+```
+
+##### LOS
+
+```{r los-weir-ss, fig.width = 6, fig.height = 4}
+weir_sample_size(j_los)
+```
+
+##### MIN
+
+```{r min-weir-ss, fig.width = 6, fig.height = 4}
+weir_sample_size(j_min)
+```
+
+##### UGR
+
+```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
+weir_sample_size(j_ugr)
+```
+
 ### Carcass Sampling {.tabset .tabset-pills}
@@
 ```{r carc-comp-fit-funcs}
+
+# for multinomial sample size
+carc_sample_size = function(j) {
+  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+  mp = barplot(jags_data$carc_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
+               ylim = c(0, max(jags_data$carc_nx_obs[observable,j], na.rm = TRUE)),
+               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
+  usr = par("usr")
+  at_x = seq(1, length(observable), 4)
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carc_nx_obs[observable,j]), 3, 4)[at_x])
+  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
+}
 
@@
 
+#### Total Sample Size {.tabset .tabset-pills}
+
+These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
+
+##### CAT
+
+```{r cat-carc-ss, fig.width = 6, fig.height = 4}
+carc_sample_size(j_cat)
+```
+
+##### LOS
+
+```{r los-carc-ss, fig.width = 6, fig.height = 4}
+carc_sample_size(j_los)
+```
+
+##### MIN
+
+```{r min-carc-ss, fig.width = 6, fig.height = 4}
+carc_sample_size(j_min)
+```
+
+##### UGR
+
+```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
+carc_sample_size(j_ugr)
+```
+
 ## Spawn Status Data
@@
 plot_f = function(j) {
+  par(yaxs = "r")
   plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))

### 2021-08-31 01-functions/plot-fns.R
Add functions to calculate 95% CI of an estimate used by the model as data
One for multinomial, logit-normal, and log-normal

@@ -2,6 +2,56 @@
 # SCRIPT TO HOUSE FUNCTIONS FOR PLOTTING INFORMATION #
 # :::::::::::::::::::::::::::::::::::::::::::::::::: #
 
+##### FUNCTIONS TO GET UNCERTAINTY IN DATA FOR PLOTTING #####
+
+## FOR A DATASET OF MULTINOMIAL RANDOM VARIABLES
+# x is the matrix of counts (rows = years; columns = group), i is the group id
+get_obs_ests_multinomial = function(x, i) {
+  
+  # calculate the proportion point estimate
+  p_ests = t(apply(x, 1, function(y) y/sum(y)))
+  p_ests[p_ests == "NaN"] = NA
+  
+  # calculate number of trials
+  N_tot = rowSums(x)
+  
+  # calculate standard error of proportion point estimate
+  se_p_ests = apply((p_ests * (1 - p_ests)), 2, function(x) sqrt(x/N_tot))
+  
+  # calculate confidence intervals; impose boundaries
+  lwr = p_ests - 1.96 * se_p_ests; lwr[lwr < 0] = 0.001
+  upr = p_ests + 1.96 * se_p_ests; upr[upr > 1] = 0.999
+  
+  out = cbind(
+    mean = p_ests[,i],
+    lwr95 = lwr[,i],
+    upr95 = upr[,i]
+  )
+  return(out)
+}
+
+## FOR A DATASET OF LOGIT-NORMAL RANDOM VARIABLES
+# Lmean is the logit-scale point estimate; Lsig is the logit-normal standard error
+get_obs_ests_logit_normal = function(Lmean, Lsig) {
+  out = cbind(
+    mean = expit(Lmean),
+    lwr95 = expit(qnorm(0.025, Lmean, Lsig)),
+    upr95 = expit(qnorm(0.975, Lmean, Lsig))
+  )
+  return(out)
+}
+
+## FOR A DATASET OF LOGNORMAL RANDOM VARIABLES
+# lmean is the log-scale point estiamte; lsig is the log-normal standard error
+get_obs_ests_log_normal = function(lmean, lsig) {
+  out = cbind(
+    mean = exp(lmean),
+    lwr95 = qlnorm(0.025, lmean, lsig),
+    upr95 = qlnorm(0.975, lmean, lsig)
+  )
+  return(out)
+}
+
 ##### PLOT A TIME SERIES OF ESTIMATES, WITH DATA IF AVAILABLE #####
 
 # est: output from postpack::post_summ()

### 2021-08-31 01-functions/plot-fns.R
Update plot_tseries() to show uncertainty in data

@@ -65,12 +65,12 @@ plot_tseries = function(est, obs = NULL, main = NULL, xaxis = T, yaxis_side = 2,
   
   # extract year labels
   if (is.null(yrs)) {
-    yrs = as.numeric(names(obs))
+    yrs = as.numeric(rownames(obs))
   }
   
   # set y limits
   if (is.null(ylim)) {
-    ylim = range(rbind(est[c("2.5%", "97.5%"),], obs), na.rm = T)
+    ylim = range(cbind(t(est[c("2.5%", "97.5%"),]), obs), na.rm = T)
   }
   
   # set the graphics device parameters
@@ -90,7 +90,10 @@ plot_tseries = function(est, obs = NULL, main = NULL, xaxis = T, yaxis_side = 2,
   lines(est["50%",] ~ yrs, col = "red", lwd = 2)
   
   # draw data if provided
-  if (!is.null(obs)) points(obs ~ yrs, pch = 21, col = "blue", bg = alpha("skyblue2", 0.5), cex = 1.2)
+  if (!is.null(obs)) {
+    segments(yrs, obs[,"lwr95"], yrs, obs[,"upr95"], col = "blue")
+    points(obs[,"mean"] ~ yrs, pch = 21, col = "blue", bg = alpha("skyblue2", 0.5), cex = 1.2)
+  } 
   
   # draw axes/labels
   if (xaxis) {

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in abundance fit plots

@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), jags_data$Pa_obs[observable,i_fall,j], main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
+               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
+               main = pops[j])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), jags_data$Mb_obs[observable,i_spring,o_nor,j], main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), 
+               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
+               main = pops[j])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)), jags_data$Ra_obs[observable,j], main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)),
+               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
+               main = pops[j])
 }

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in survival fit plots

@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)), expit(jags_data$Lphi_obs_Pb_Ma[observable,j]), main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)),
+               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
+               main = pops[j])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), expit(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j]), main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
+               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
+               main = pops[j])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]), main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)),
+               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
+               main = pops[j])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)), expit(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]), main = pops[j])
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)),
+               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
+               main = pops[j])
 }
@@
 par(oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_nor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
+             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
+             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 par(oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)), expit(jags_data$Lphi_obs_Ma_O0[observable,o_hor]), main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
+             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
+             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in weir composition plots

@@
 # containers
-q_weir_age_obs = q_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-q_weir_sex_obs = q_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
-q_weir_origin_obs = q_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
+x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
+x_weir_sex_obs = x_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
+x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
 
@@
   for (k in 1:jags_data$nk) {
-    q_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])/jags_data$weir_nx_obs[,j]
-    q_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])/jags_data$carc_nx_obs[,j]
+    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])
+    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])
   }
@@
   for (s in 1:jags_data$ns) {
-    q_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])/jags_data$weir_nx_obs[,j]
-    q_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])/jags_data$carc_nx_obs[,j]
+    x_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])
+    x_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])
   }
@@
   for (o in 1:jags_data$no) {
-    q_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])/jags_data$weir_nx_obs[,j]
-    q_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])/jags_data$carc_nx_obs[,j]
-  }
-}
-
-dimnames(q_weir_age_obs)[[1]] = dimnames(q_weir_sex_obs)[[1]] = dimnames(q_weir_origin_obs)[[1]] = dimnames(q_carc_age_obs)[[1]] = dimnames(q_carc_sex_obs)[[1]] = dimnames(q_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
-
-q_weir_new_obs = list(
-  q_weir_age_obs = q_weir_age_obs,
-  q_weir_sex_obs = q_weir_sex_obs,
-  q_weir_origin_obs = q_weir_origin_obs
+    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])
+    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])
+  }
+}
+
+dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_sex_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_sex_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
+
+x_weir_new_obs = list(
+  x_weir_age_obs = x_weir_age_obs,
+  x_weir_sex_obs = x_weir_sex_obs,
+  x_weir_origin_obs = x_weir_origin_obs
 )
 
-q_carc_new_obs = list(
-  q_carc_age_obs = q_carc_age_obs,
-  q_carc_sex_obs = q_carc_sex_obs,
-  q_carc_origin_obs = q_carc_origin_obs
+x_carc_new_obs = list(
+  x_carc_age_obs = x_carc_age_obs,
+  x_carc_sex_obs = x_carc_sex_obs,
+  x_carc_origin_obs = x_carc_origin_obs
 )
@@
 weir_comp_fit_plot = function(j) {
-  # calculate observed q
-  q_obs = t(apply(jags_data$weir_x_obs[,,j], 1, function(y) y/sum(y)))
 
   par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 7), main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 8), main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 9), main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 10), main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 11), main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 12), main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
 
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,1,j], main = TeX("$Age\\,3$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,2,j], main = TeX("$Age\\,4$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,3,j], main = TeX("$Age\\,5$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,1,j], main = TeX("$Females$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,2,j], main = TeX("$Males$"), ylim = c(0,1))
+
+  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 1), main = TeX("$Females$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 2), main = TeX("$Males$"), ylim = c(0,1))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,1,j], main = TeX("$NOR$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,2,j], main = TeX("$HOR$"), ylim = c(0,1))
+
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in carcass composition plots

@@
 
-  # calculate observed q
-  q_obs = t(apply(jags_data$carc_x_obs[,,j], 1, function(y) y/sum(y)))
-
   par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 7), main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 8), main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 9), main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 10), main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 11), main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 12), main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,1,j], main = TeX("$Age\\,3$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,2,j], main = TeX("$Age\\,4$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,3,j], main = TeX("$Age\\,5$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,1,j], main = TeX("$Females$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,2,j], main = TeX("$Males$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_sex_obs[observable,,j], 1), main = TeX("$Females$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_sex_obs[observable,,j], 2), main = TeX("$Males$"))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,1,j], main = TeX("$NOR$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,2,j], main = TeX("$HOR$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")

### 2021-08-31 03-post-process/output-plots.Rmd

@@
   par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)),
+               get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
+               main = pops[j], ylim = c(0,1))
   par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

### 2021-09-02 02-model/fit-model.R
Track log posterior predictive density for each data set

@@ -160,7 +160,12 @@ jags_params = c(
   "Pa_obs_dev", "Pa_obs_new_dev", "Mb_obs_dev", "Mb_obs_new_dev", 
   "Ra_obs_dev", "Ra_obs_new_dev", "Lphi_obs_Pb_Ma_dev", "Lphi_obs_new_Pb_Ma_dev",
   "Lphi_obs_Pa_Ma_dev", "Lphi_obs_new_Pa_Ma_dev", "Lphi_obs_Mb_Ma_dev", "Lphi_obs_new_Mb_Ma_dev",
-  "Lphi_obs_Ma_O0_dev", "Lphi_obs_new_Ma_O0_dev", "carcs_spawned_dev", "carcs_spawned_new_dev"
+  "Lphi_obs_Ma_O0_dev", "Lphi_obs_new_Ma_O0_dev", "carcs_spawned_dev", "carcs_spawned_new_dev",
+  
+  # log posterior predictive density
+  "weir_x_obs_lppd", "carc_x_obs_lppd", "Pa_obs_lppd", "Mb_obs_lppd", "Ra_obs_lppd",
+  "Lphi_obs_Pb_Ma_lppd", "Lphi_obs_Pa_Ma_lppd", "Lphi_obs_Mb_Ma_lppd",
+  "Lphi_obs_Ma_O0_lppd", "carcs_spawned_lppd"
   
 )
 
@@ -237,20 +242,20 @@ if (rmd) {
   cat("\nRendering Rmd Output")
   # set working dir to post-processing directory
   setwd("03-post-process")
-
+  
   # file name of rendered output
   rmd_out_file = paste0("output-plots-", scenario, ".html")
-
+  
   # render the output
   render(input = "output-plots.Rmd",
          output_file = rmd_out_file,
          params = list(scenario = scenario),
          quiet = TRUE
   )
-
+  
   # open the rendered file when complete
   file.show(rmd_out_file)
-
+  
   # set the working dir back
   setwd("../")
   cat("\n\nDone.")

### 2021-09-02 02-model/model-code.R

@@ -377,6 +377,14 @@ jags_model_code = function() {
   
   ### OBSERVATION MODEL ###
   
+  # the content under the "data likelihood" header is the only portion needed to fit the model
+  # the other content is for evaluating model fit and parsimony
+  # objects labeled "new" pertain to simulated data, for evaluating model fit to the observed data compared to "perfect data"
+  # objects labeled "dev" represent measure of the deviation of the data from the model
+  # objects labeled "lppd" represent log posterior predictive density; used in calculating WAIC
+  
+  # the long form index notation enables skipping over missing data while keeping all object dimensions identical
+  
   # age/sex composition
   for (j in 1:nj) {
     for (y in (kmax+1):ny) {
@@ -394,6 +402,9 @@ jags_model_code = function() {
       weir_x_obs_dev[y,j] <- sum(((weir_x_obs[y,1:nkso,j] - expected_weir_x_obs[y,1:nkso,j])^2)/expected_weir_x_obs[y,1:nkso,j])
       weir_x_obs_new_dev[y,j] <- sum(((weir_x_obs_new[y,1:nkso,j] - expected_weir_x_obs[y,1:nkso,j])^2)/expected_weir_x_obs[y,1:nkso,j])
       
+      # calculate log posterior predictive density
+      weir_x_obs_lppd[y,j] <- logdensity.multi(weir_x_obs[y,1:nkso,j], q_Ra[y,1:nkso,j], weir_nx_obs[y,j])
+      
       # FOR CARCASSES
       # data likelihood
[…]

### 2021-09-02 03-post-process/output-plots.Rmd
Add a table summarizing posterior predictive check results

@@
 
+## Posterior Predictive Checks
+
+This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
+For each observed data point and MCMC iteration, a value was simulated from the model.
+The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
+P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
+Across years within a data set, p-values were summarized as the median and central 95% intervals.
+The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.
+
+The fit criterion differed depending on the likelihood function used to fit the model to the data set:
+
+* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
+* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, expect pre-spawn survival which used a binomial distribution.
+* **Binomial/Multinomial**: chi-squared fit statistic. This applies to all composition data and the pre-spawn survival data.
+
+```{r calculate-bayesian-pvals}
+# function to summarize bayesian p-values within a data source
+summarize_bp = function(bp) {
+  data.frame(
+    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
+    "median" = apply(bp, 2, median, na.rm = TRUE),
+    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
+    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
+    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
+    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
+  )
+}
+
+### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###
+
+# fall trap
+new = post_subset(post, "Pa_obs_new_dev", TRUE)
+obs = post_subset(post, "Pa_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
+bp = bp[,"fall-mig",]
+Pa_bp = data.frame(
+  name = rep("Juveniles", 4), pop = pops,
+  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
+  summarize_bp(bp)
+)
+rownames(Pa_bp) = NULL
+
+# spring trap
+new = post_subset(post, "Mb_obs_new_dev", TRUE)
+obs = post_subset(post, "Mb_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
+bp = bp[,"spring-mig","NOR",]
+Mb_bp = data.frame(
+  name = rep("Juveniles", 4), pop = pops,
+  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
+  summarize_bp(bp)
+)
+rownames(Mb_bp) = NULL
+
+# adult abundance
+new = post_subset(post, "Ra_obs_new_dev", TRUE)
+obs = post_subset(post, "Ra_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+Ra_bp = data.frame(
+  name = rep("Adults", 4), pop = pops,
+  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(Ra_bp) = NULL
+
+### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###
+
+# summer tagging survival
+new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
+obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+phi_Pb_Ma_bp = data.frame(
+  name = rep("Summer Tagging to LGR", 4), pop = pops,
+  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(phi_Pb_Ma_bp) = NULL
+
+# fall trap survival
+new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
+obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
+bp = bp[,"fall-mig",]
+phi_Pa_Ma_bp = data.frame(
+  name = rep("Fall Trap to LGR", 4), pop = pops,
+  origin = rep("NOR", 4),   LH_type = rep("Fall Migrants", 4),
+  summarize_bp(bp)
+)
+rownames(phi_Pa_Ma_bp) = NULL
+
+# trib to lgr survival
+new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
+obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), c("NOR", "HOR"), pops)
+bp = bp[,"spring-mig",,]
+bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
+           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
+           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
+           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
+phi_Mb_Ma_bp = data.frame(
+  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
+  origin = rep(c("NOR", "HOR"), 4), LH_type = rep("Spring Migrants", 8),
+  summarize_bp(bp)
+)
+rownames(phi_Mb_Ma_bp) = NULL
+
+# hydropower survival
+new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
+obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
+phi_Ma_O0_bp = data.frame(
+  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
+  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
+  summarize_bp(bp)
+)
+rownames(phi_Ma_O0_bp) = NULL
+
+### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
+
+# weir composition
+new = post_subset(post, "weir_x_obs_new_dev", TRUE)
+obs = post_subset(post, "weir_x_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+bp[jags_data$weir_nx_obs == 0 | is.na(jags_data$weir_nx_obs)] = NA
+weir_x_bp = data.frame(
+  name = rep("Weir", 4), pop = pops,
+  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(weir_x_bp) = NULL
+
+# carcass composition
+new = post_subset(post, "carc_x_obs_new_dev", TRUE)
+obs = post_subset(post, "carc_x_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+bp[jags_data$carc_nx_obs == 0 | is.na(jags_data$carc_nx_obs)] = NA
+carc_x_bp = data.frame(
+  name = rep("Carcasses", 4), pop = pops,
+  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(carc_x_bp) = NULL
+
+# pre-spawn survival
+new = post_subset(post, "carcs_spawned_new_dev", TRUE)
+obs = post_subset(post, "carcs_spawned_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+carcs_spawned_bp = data.frame(
+  name = rep("Prespawn", 4), pop = pops,
+  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(carcs_spawned_bp) = NULL
+
+### COMBINE INTO ONE TABLE ###
+bp_tab = rbind(
+  Pa_bp, Mb_bp, Ra_bp,
+  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
+  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp
+)
+
+# add a main data category variable
+category = rep(NA, nrow(bp_tab))
+category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
+category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
+category[is.na(category)] = "Survival"
+bp_tab = data.frame(category = category, bp_tab)
+
+# drop the several cases with no data
+# MIN HOR survival to LGR and MIN weir data
+bp_tab = bp_tab[bp_tab$N > 0,]
+
+# re-order output/misc formatting
+bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
+bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
+bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
+bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
+rownames(bp_tab) = NULL
+```
+
+```{r bayesian-pvals-table}
+# a function to color cells depending on the value
+assign_color = function(x) {
+  red_pal = colorRampPalette(c("white", "red"))
+  blue_pal = colorRampPalette(c("blue", "white"))
+  red_cols = red_pal(5)
+  blue_cols = blue_pal(5)
+  cols = c(blue_cols, red_cols)
+  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
+  names(cols) = bin_names
+  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
+  cols_use = cols[as.character(bins)]
+  alpha(unname(cols_use), 0.5)
+}
+
+# produce the kable
+bp_tab %>%
+  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
+      align = c("lllllcccccc")) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
+  column_spec(7, background = assign_color(bp_tab[,7])) %>%
+  column_spec(8, background = assign_color(bp_tab[,8])) %>%
+  column_spec(9, background = assign_color(bp_tab[,9])) %>%
+  collapse_rows(1:5) 
+```
+
 # Fit to Data

### 2021-09-02 03-post-process/output-plots.Rmd

@@
 
+## WAIC
+
+WAIC is a measure of model parsimony.
+The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
+There are two methods of calculating `pD`, both are shown below.
+As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
+
+```{r calculate-waic}
+summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
+  # calculate total lppd summed across all data sets within a given year
+  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
+
+  tmp_log = log(apply(exp(total_lppd), 2, mean))
+  tmp_sum = -2 * sum(tmp_log)
+
+  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
+  pD2 = sum(apply(total_lppd, 2, var))
+  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
+}
+
+waic_out = summarize_lppd("_lppd[year,.+]$")
+
+waic_out = as.data.frame(as.list(waic_out))
+waic_out %>%
+  kbl(format.args = list(big.mark = ",")) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
+```
+
 ## Posterior Predictive Checks

### 2021-09-03 03-post-process/output-plots.Rmd
Add new parameters to output-plots
For the quantities representing upstream survival, added content for:

* MCMC diagnostics
* Posterior predictive checks
* Fit check plots
* Parameter summary plots

@@
 
+# Migration survival: BON to LGR
+L1 = "Migration Survival (BON to LGR)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", origin = o_hor)
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+phi_Rb_Ra_diags = rbind(tmp1, tmp2)
+
 # Pre-spawn Survival
@@
   phi_O1_O2_diags,
+  phi_Rb_Ra_diags,
   phi_Sb_Sa_diags,
@@
 )
+
+# remove any summaries for nodes that don't have diagnostics
+# e.g., if that "parameter" takes on a fixed value in the model
+diags_table = diags_table[diags_table$n_params > 0,]
 ```
@@
 
+# movement survival from BON to LGR
+new = post_subset(post, "LGR_adults_new_dev", TRUE)
+obs = post_subset(post, "LGR_adults_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
+LGR_adults_bp = data.frame(
+  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
+  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
+  summarize_bp(bp)
+)
+rownames(LGR_adults_bp) = NULL
+
 ### COMBINE INTO ONE TABLE ###
@@
   phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp
+  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp, LGR_adults_bp
 )
@@
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Survival")
+```
+
+### BON Adults $\rightarrow$ LGR (NOR)
+
+```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
+par(oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
+             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
+             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
+mtext(side = 1, outer = T, line = 0.25, "Return Year")
+mtext(side = 2, outer = T, line = 0.25, "Survival")
+```
+
+### BON Adults $\rightarrow$ LGR (HOR)
+
+```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
+par(oma = c(1.5,1.5,0,0))
+plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
+             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
+             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
+mtext(side = 1, outer = T, line = 0.25, "Return Year")
 mtext(side = 2, outer = T, line = 0.25, "Survival")
@@
 
+## Movement Survival BON to LGR
+
+```{r bon-to-lgr-bxp}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
+```
+
 ## Pre-spawn Survival

### 2021-09-15 03-post-process/output-plots.Rmd
Don't summarize diagnostics for sig_inits
Fixing its value at 0.3

--- 2021-09-02 03-post-process/output-plots.Rmd
@@
 L1 = "Initial Adult Recruitment"
-L2 = c("Mean", "Process SD", "Realized")
-match = c("mu_init_recruits[.]", "sig_init_lrecruits[.]", "^init_recruits[.+,.]")
+L2 = c("Mean", "Realized")
+match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
 init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

### 2021-09-21 02-model/model-code.R
Use "Sig" instead of "sig"

@@ -126,15 +126,15 @@ jags_model_code = function() {
   for (i in 1:nj) {
     for (j in 1:nj) {
       # covariance matrix of white noise portion of yr1 ocean survival
-      Sigma_Lphi_O0_O1[i,j] <- sig_Lphi_O0_O1 * sig_Lphi_O0_O1 * ifelse(i == j, 1, rho_Lphi_O0_O1)
+      Sig_Lphi_O0_O1[i,j] <- sig_Lphi_O0_O1 * sig_Lphi_O0_O1 * ifelse(i == j, 1, rho_Lphi_O0_O1)
       
       # covariance matrix of total process noise in yr1 ocean survival
-      Sigma_Lphi_O0_O1_init[i,j] <- sig_Lphi_O0_O1_init[i] * sig_Lphi_O0_O1_init[j] * ifelse(i == j, 1, rho_Lphi_O0_O1)
+      Sig_Lphi_O0_O1_init[i,j] <- sig_Lphi_O0_O1_init[i] * sig_Lphi_O0_O1_init[j] * ifelse(i == j, 1, rho_Lphi_O0_O1)
     }
   }
   
   # year 0 residuals for yr1 ocean survival (needed for AR(1) process)
-  Lphi_O0_O1_resid[kmax,o_nat,1:nj] ~ dmnorm.vcov(rep(0, nj), Sigma_Lphi_O0_O1_init[1:nj,1:nj])
+  Lphi_O0_O1_resid[kmax,o_nat,1:nj] ~ dmnorm.vcov(rep(0, nj), Sig_Lphi_O0_O1_init[1:nj,1:nj])
 
   # migration survival adults from BON to LGR
   for (o in 1:no) {
@@ -212,7 +212,7 @@ jags_model_code = function() {
     }
     
     # yr1 ocean survival for natural origin: multivariate logit-normal error on white noise portion of AR(1) process
-    Lphi_O0_O1[y,o_nat,1:nj] ~ dmnorm.vcov(logit(mu_phi_O0_O1[o_nat,1:nj]) + Lphi_O0_O1_resid[y-1,o_nat,1:nj] * kappa_phi_O0_O1[1:nj], Sigma_Lphi_O0_O1[1:nj,1:nj])
[…]

### 2021-09-21 02-model/fit-model.R
Set up model fitting script to run new model

@@ -17,7 +17,7 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 out_dir = "02-model/model-output"
 
 # specify a scenario name
-scenario = "add-upstream-survival-data"
+scenario = "complex-ocean-survival-with-prior"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -114,7 +114,7 @@ jags_params = c(
   # hyperparameters: inter-annual sd
   "sig_Lpi", "sig_Lphi_Pa_Mb", "sig_Lphi_Mb_Ma", "sig_Lphi_Ma_O0",
   "sig_Lomega", "sig_Lpsi_O1_Rb", "sig_Lpsi_O2_Rb", "sig_Lphi_Sb_Sa",
-  "sig_Lphi_O0_O1", "sig_Lphi_O1_O2", "sig_Lphi_O2_O3", "sig_Lphi_Rb_Ra",
+  "Sig_Lphi_O0_O1", "sig_Lphi_Rb_Ra",
   
   # year-specific parameters
   "pi", "phi_Pa_Mb", "phi_Mb_Ma", "phi_Ma_O0", "omega", 
@@ -139,7 +139,7 @@ jags_params = c(
   "O_phi_scaler_nat_hat",
   
   # misc derived quantities
-  "beta_per_peu", "Pb_per_Sa_tot", "Pb_per_f_tot", "Mb_per_Sa_tot", "Sa_tot_per_Sa_tot", "Ra_per_Ma",
+  "beta_per_peu", "Pb_per_Sa_tot", "Pb_per_f_tot", "Mb_per_Sa_tot", "Sa_tot_per_Sa_tot", "Ra_per_Ma", "phi_O0_Rb_BON",
   
   # residuals
   "Lpi_resid", "Lphi_Pa_Mb_resid", "Lphi_Mb_Ma_resid",
@@ -235,7 +235,12 @@ saveRDS(out_obj, file.path(out_dir, out_file))
 
 # render the output plots if requested
 if (rmd) {
+  # start a timer, this can take a while
+  starttime = Sys.time()
+  
+  # print a progress message
   cat("\nRendering Rmd Output")
+  
   # set working dir to post-processing directory
   setwd("03-post-process")
   
@@ -251,6 +256,10 @@ if (rmd) {
   
   # open the rendered file when complete
   file.show(rmd_out_file)
+  
+  # stop the timer
[…]

### 2021-09-21 03-post-process/output-plots.Rmd
add decomposition of vcov to output plots

--- 2021-09-03 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: "base"
+    value: "complex-ocean-survival-with-prior"
     input: text
@@
 jags_data = model_info$jags_data
-
+```
+
+```{r dimension-ids}
 # the years included by the model
@@
 observable = (jags_data$kmax+1):jags_data$ny
-```
-
-```{r dimension-ids}
+
 # population names
@@
 )
+```
+
+```{r vcov-decomp, message = FALSE}
+# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
+# postpack::vcov_decomp() does this for all posterior samples
+
+Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
+
+# make the labels/indices for which elements of the vcov matrices contain unique covariances
+# no point in summarizing/displaying both off-diagonal triangles
+dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
+dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
+vcov_cols = dummy_cols[lower.tri(dummy_cols)]
+vcov_rows = dummy_rows[lower.tri(dummy_rows)]
+vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
+vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")
+
+# subset out only the unique elements
+Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))
+
+# combine these derived posterior samples with the main object
+post = post_bind(post, Sig_Lphi_O0_O1_post)
 ```

### 2021-09-21 03-post-process/output-plots.Rmd
Update diagnostics for new model

@@
 L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_O0_O1[origin]", "sig_Lphi_O0_O1", "phi_O0_O1[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
+L2 = c("Mean", "Process SD", "Among Pop. Correlation", "Realized")
+base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
 phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 L1 = "Year 2 Ocean Survival"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_O1_O2[origin]", "sig_Lphi_O1_O2", "phi_O1_O2[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
+L2 = c("Mean")
+base = c("mu_phi_O1_O2[origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
 phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# Year 3 ocean survival
+L1 = "Year 3 Ocean Survival"
+L2 = c("Mean")
+base = c("mu_phi_O2_O3[origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+phi_O2_O3_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
 L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
-match = c("O_phi_scaler_nat_hat", "Lphi_O0_O1_resid[5]", "kappa_phi_O0_O1")
+base = c("O_phi_scaler_nat_hat[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
+match = sub_index(base, pop = ".")
 misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
   phi_O1_O2_diags,
+  phi_O2_O3_diags,
   phi_Rb_Ra_diags,

### 2021-09-21 03-post-process/output-plots.Rmd
Add a BON to BON survival rate plot

@@
 
-## Smolt-to-Adult Rates
+## Smolt-to-Adult Rates {.tabset .tabset-pills}
+
+### LGR to Tributary
 
@@
 mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
+```
+
+### BON to BON
+
+```{r bon-to-bon, fig.width = 6, fig.height = 5}
+sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]
+
+plot_fn = function(j) {
+  # which years had zero hatchery smolt released
+  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
+
+  # summarize rates
+  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
+  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))
+
+  # get a max value for ylim
+  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])
+
+  # make hatchery values NA in year with no smolt
+  phi_hor[,zero_hor_smolt] = NA
+
+  # plot natural origin time series
+  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))
+
+  # add hatchery origin time series
+  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
+  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
+  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
+  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)
+
+  if (j == 1) {
+    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
+         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
+  }
+}
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
 ```

### 2021-09-21 03-post-process/output-plots.Rmd
Add population-specific ocean survival time series plots

@@
 
-# Ocean Survival
+# Ocean Survival {.tabset .tabset-pills}
 
 ```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
+ocean_surv_plot = function(j) {
   par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-plot_tseries(post_summ(post, "phi_O0_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O0_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
-plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_nor, pop = j)),
+               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_hor, pop = j)),
+               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_nor, pop = j)),
+               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_hor, pop = j)),
+               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_nor, pop = j)),
+               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_hor, pop = j)),
+               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
   mtext(side = 1, outer = T, line = 0.5, "Brood Year")
   mtext(side = 2, outer = T, line = 0, "Survival")
+}
+```
+
+## CAT
+
+```{r}
+ocean_surv_plot(j_cat)
+```
+
+## LOS
+
+```{r}
+ocean_surv_plot(j_los)
+```
+
+## MIN
+
+```{r}
+ocean_surv_plot(j_min)
+```
+
+## UGR
+
+```{r}
+ocean_surv_plot(j_ugr)
 ```

### 2021-09-21 03-post-process/output-plots.Rmd
Update boxplots showing main parameter estimates for ocean survival

@@
   # replace the summary stats with my preferred quantiles
-  par(mar = c(2,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
+  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
   bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
@@
 
-### Year 1
+### Year 1 {.tabset .tabset-pills}
+
+#### Mean
 
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
-my_boxplot("sig_Lphi_O0_O1", ylab = "Process SD")
-```
-
-### Year 2
+my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
+```
+
+#### Process SD and Correlation
+
+```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,3))
+my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
+my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
+my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among Population Correlation", ylim = c(-1,1), las = 2)
+```
+
+### Year 2 {.tabset .tabset-pills}
 
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin]", origin = "."), ticklabs = c("NOR", "HOR"), ylim = c(0,1), ylab = "Average Survival")
-my_boxplot("sig_Lphi_O1_O2", ylab = "Process SD")
+my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
+```
+
+### Year 3 {.tabset .tabset-pills}
+
+```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
+```
+
+### NOR:HOR Log Odds Ratio
+
+```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
+my_boxplot(sub_index("O_phi_scaler_nat_hat[pop]", pop = "."), ylab = "Log Odds Ratio")
 ```

### 2021-10-11 03-post-process/output-plots.Rmd
Rename model scenario to base
This is new best version of the model

@@
     label: "Scenario"
-    value: "complex-ocean-survival-with-prior"
+    value: "base"
     input: text

### 2021-10-11 02-model/fit-model.R

@@ -17,7 +17,7 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 out_dir = "02-model/model-output"
 
 # specify a scenario name
-scenario = "complex-ocean-survival-with-prior"
+scenario = "base"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE

### 2021-10-11 03-post-process/output-plots.Rmd

--- 2021-09-21 03-post-process/output-plots.Rmd
@@
 jags_data = model_info$jags_data
-```
-
-```{r dimension-ids}
+
 # the years included by the model
@@
 observable = (jags_data$kmax+1):jags_data$ny
-
+```
+
+```{r dimension-ids}
 # population names
@@
 )
-```
-
-```{r vcov-decomp, message = FALSE}
-# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
-# postpack::vcov_decomp() does this for all posterior samples
-
-Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
-
-# make the labels/indices for which elements of the vcov matrices contain unique covariances
-# no point in summarizing/displaying both off-diagonal triangles
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")
-
-# subset out only the unique elements
-Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))
-
-# combine these derived posterior samples with the main object
-post = post_bind(post, Sig_Lphi_O0_O1_post)
 ```
@@
 L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among Pop. Correlation", "Realized")
-base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_O0_O1[origin]", "sig_Lphi_O0_O1", "phi_O0_O1[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
 phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_O1_O2[origin]", "sig_Lphi_O1_O2", "phi_O1_O2[year,origin]")
+match = sub_index(base, year = ".+", origin = o_nor)
 phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
-
-# Year 3 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-phi_O2_O3_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
 L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
-base = c("O_phi_scaler_nat_hat[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
-match = sub_index(base, pop = ".")
+match = c("O_phi_scaler_nat_hat", "Lphi_O0_O1_resid[5]", "kappa_phi_O0_O1")
 misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
   phi_O1_O2_diags,
-  phi_O2_O3_diags,
   phi_Rb_Ra_diags,
@@
 
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
+## Smolt-to-Adult Rates
 
@@
 
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]
-
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
 ## Parr per Spawner
@@
 
-# Ocean Survival {.tabset .tabset-pills}
+# Ocean Survival
 
 ```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
 par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O0_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O0_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
+plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
 mtext(side = 1, outer = T, line = 0.5, "Brood Year")
 mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
 ```

### 2021-10-15 02-model/fit-model.R
Add new data objects for population-specific carcass corrections

@@ -71,7 +71,9 @@ overall_phi_Rb_Ra = with(append(jags_data, add_jags_data), mean(phi_SL, na.rm = 
 # some dummy variables for performing weir vs. carcass composition correction
 add_jags_data2 = list(
   age3 = c(1,0,0),      # is each k age 3? 1 = yes; 0 = no
-  age5 = c(0,0,1)       # is each k age 5?
+  age5 = c(0,0,1),      # is each k age 5?
+  j_z = c(1,2,4),       # which j elements will have z estimated (must have both carcass and weir composition data)?
+  nj_z = 3              # how many j elements will have z estimated?
 )
 add_jags_data = append(add_jags_data, add_jags_data2)
 

### 2021-10-15 02-model/fit-model.R
Track new parameters

@@ -142,7 +142,7 @@ jags_params = c(
   "Ra", "Sb", "Sa", "q_Ra", "q_Sa_adj", "Sa_tot", "Ra_tot", "f_tot",
   
   # carcass vs. weir correction
-  "z", "carc_adj", "n_stray_tot", "stray_comp",
+  "z", "carc_adj", "n_stray_tot", "stray_comp", "mu_z", "sig_z",
   
   # misc parameters
   "O_phi_scaler_nat_hat",

### 2021-10-15 03-post-process/output-plots.Rmd
Update MCMC diagnostics for carcass correction coefficients

--- 2021-10-11 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: "base"
+    value: "no-sex"
     input: text
@@
 o_hor    = 2  # hatchery origin are o = 2,
-s_female = 1  # females are s = 1,
-s_male   = 2  # males are s = 2
 j_cat    = 1  # Catherine Creek is j = 1
@@
 
-# kso represents "age/sex/origin" combo
-# e.g., kso = 1 is age 3 female NORs
-# e.g., kso = 12 is age 5 male HORs
-# these objects specify which elements of kso are for different aggregations of these
-kso_age = list(
-  kso_3 = c(1, 4, 7, 10),
-  kso_4 = c(2, 5, 8, 11),
-  kso_5 = c(3, 6, 9, 12)
+# ko represents "age/origin" combo
+# e.g., ko = 1 is age 3 NORs
+# e.g., ko = 5 is age 4 HORs
+# these objects specify which elements of ko are for different aggregations of these
+ko_age = list(
+  ko_3 = c(1, 4),
+  ko_4 = c(2, 5),
+  ko_5 = c(3, 6)
 )
 
-kso_sex = list(
-  kso_female = c(1,2,3,7,8,9),
-  kso_male = c(4,5,6,10,11,12)
-)
-
-kso_origin = list(
-  kso_nor = 1:6,
-  kso_hor = 7:12
+ko_origin = list(
+  ko_nor = 1:3,
+  ko_hor = 4:6
 )
@@
 
-```{r}
+```{r mcmc-time-info}
 # Calculate hours per 10,000 iterations
@@
 # L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
-# L3: a "Level-3" group label; such as NOR or females or age-3 females
+# L3: a "Level-3" group label; such as NOR or HOR
 
@@
 
-# Sex Apportionment
-L1 = "Sex Apportionment"
-L2 = c("Mean", "Process SD", "Realized")
-base = list("mu_omega[sex,origin,pop]", "sig_Lomega[origin,pop]", "omega[year,sex,origin,pop]")
-match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
-match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-omega_diags = rbind(tmp1, tmp2)
-
 # Probability of Maturing at Age-3
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_psi_O1_Rb[sex,origin,pop]", "sig_Lpsi_O1_Rb[sex,origin,pop]", "psi_O1_Rb[.+,sex,origin,pop]")
-match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
-match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
-match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
-tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
-match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
-tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
-psi_O1_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)
+base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "psi_O1_Rb[.+,origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+psi_O1_Rb_diags = rbind(tmp1, tmp2)
 
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_psi_O2_Rb[sex,origin,pop]", "sig_Lpsi_O2_Rb[sex,origin,pop]", "psi_O2_Rb[.+,sex,origin,pop]")
-match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
-match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
-match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
-tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
-match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
-tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
-psi_O2_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)
+base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "psi_O2_Rb[.+,origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
+tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
+tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+psi_O2_Rb_diags = rbind(tmp1, tmp2)
 
@@
 phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
-
-# Year 3 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-phi_O2_O3_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
 L1 = "Carcass Correction Factor"
-z_diags = diag_fn("z", L1 = L1)
+L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
+match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
+z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
 L1 = "Strays"
-L2 = c("Realized Number", "Age/Sex Comp")
-match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = "."))
+L2 = c("Realized Number", "Age Comp")
+match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
 stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
   phi_Ma_O0_diags,
-  omega_diags,
   psi_O1_Rb_diags,
@@
 # primary containers: will store final recalculated output
-q_Ra_age = q_Sa_adj_age = q_Ra_sex = q_Sa_adj_sex = q_Ra_origin = q_Sa_adj_origin = NULL
+q_Ra_age = q_Sa_adj_age = q_Ra_origin = q_Sa_adj_origin = NULL
 
@@
 
-  ## BY AGE, AGGREGATED ACROSS SEX AND ORIGIN
+  ## BY AGE, AGGREGATED ACROSS ORIGINS
 
@@
       # calculate aggregate proportions for each age
-      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,kso_age[[k]],j])
-      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,kso_age[[k]],j])
+      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,ko_age[[k]],j])
+      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,ko_age[[k]],j])
 
@@
 
-  ## BY SEX, AGGREGATED ACROSS AGE AND ORIGIN
-
-  # containers
-  q_Ra_sex_tmp = q_Sa_adj_sex_tmp = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
-  inds_1_sex = inds_2_sex = inds_3_sex = q_Ra_sex_tmp
-  for (j in 1:jags_data$nj) {
-    for (s in 1:jags_data$ns) {
-      # calculate aggregate proportions for each sex
-      q_Ra_sex_tmp[,s,j] = rowSums(q_Ra[,kso_sex[[s]],j])
-      q_Sa_adj_sex_tmp[,s,j] = rowSums(q_Sa_adj[,kso_sex[[s]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_sex[,s,j] = 1:jags_data$ny
-      inds_2_sex[,s,j] = s
-      inds_3_sex[,s,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  q_Ra_sex_v = as.numeric(q_Ra_sex_tmp)
-  q_Sa_adj_sex_v = as.numeric(q_Sa_adj_sex_tmp)
-  names(q_Ra_sex_v) = paste0("q_Ra_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
-  names(q_Sa_adj_sex_v) = paste0("q_Sa_adj_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
-  q_Ra_sex_v = q_Ra_sex_v[!is.na(q_Ra_sex_v)]
-  q_Sa_adj_sex_v = q_Sa_adj_sex_v[!is.na(q_Sa_adj_sex_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGE AND SEX
+  ## BY ORIGIN, AGGREGATED ACROSS AGES
 
@@
       # calculate aggregate proportions for each origin
-      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,kso_origin[[o]],j])
-      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,kso_origin[[o]],j])
+      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,ko_origin[[o]],j])
+      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,ko_origin[[o]],j])
 
@@
   q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
-  q_Ra_sex = rbind(q_Ra_sex, q_Ra_sex_v)
-  q_Sa_adj_sex = rbind(q_Sa_adj_sex, q_Sa_adj_sex_v)
   q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
@@
 
-# combine new calculated quantites into a big matrix
-q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_sex, q_Sa_adj_sex, q_Ra_origin, q_Sa_adj_origin)
+# combine new calculated quantities into a big matrix
+q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_origin, q_Sa_adj_origin)
 
@@
 
-# these are the observed proportions by age (aggregated across sex and origin), sex (aggregated across age and origin), and origin (aggregated across age and sex)
+# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
 
@@
 x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-x_weir_sex_obs = x_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
 x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
@@
   for (k in 1:jags_data$nk) {
-    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])
-    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each sex
-  for (s in 1:jags_data$ns) {
-    x_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])
-    x_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])
+    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,ko_age[[k]],j])
+    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,ko_age[[k]],j])
   }
@@
   for (o in 1:jags_data$no) {
-    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])
-    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])
-  }
-}
-
-dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_sex_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_sex_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
+    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,ko_origin[[o]],j])
+    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,ko_origin[[o]],j])
+  }
+}
+
+dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
 
@@
   x_weir_age_obs = x_weir_age_obs,
-  x_weir_sex_obs = x_weir_sex_obs,
   x_weir_origin_obs = x_weir_origin_obs
@@
   x_carc_age_obs = x_carc_age_obs,
-  x_carc_sex_obs = x_carc_sex_obs,
   x_carc_origin_obs = x_carc_origin_obs
@@
 
-  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 7), main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 8), main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 9), main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 10), main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 11), main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 12), main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"))
 
@@
 
-# for fits to each age, aggregated across sexes and origins
+# for fits to each age, aggregated across origins
 weir_comp_fit_plot_age = function(j) {
@@
 
-# for fits to each sex, aggregated across ages and origins
-weir_comp_fit_plot_sex = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 1), main = TeX("$Females$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 2), main = TeX("$Males$"), ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages and sexes
+# for fits to each origin, aggregated across ages
 weir_comp_fit_plot_origin = function(j) {
@@
 
-#### By Age/Sex/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
+#### By Age/Origin {.tabset .tabset-pills}
+
+This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
 
@@
 
-These figures show the agreement of the model with the weir composition data by age, aggregated by sex and origin.
+These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
 
@@
 
-#### By Sex {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by sex, aggregated by age and origin.
-
-##### CAT
-
-```{r cat-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_sex(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_sex(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_sex(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_sex(j_ugr)
-```
-
 #### By Origin {.tabset .tabset-pills}
 
-These figures show the agreement of the model with the weir composition data by origin, aggregated by age and sex.
+These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
 
@@
 
-These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
+These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
 
@@
 
-  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 7), main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 8), main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 9), main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 10), main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 11), main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 12), main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
+  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"))
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
 
-# for fits to each age, aggregated across sexes and origins
+# for fits to each age, aggregated across origins
 carc_comp_fit_plot_age = function(j) {
@@
 
-# for fits to each sex, aggregated across ages and origins
-carc_comp_fit_plot_sex = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_sex_obs[observable,,j], 1), main = TeX("$Females$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_sex_obs[observable,,j], 2), main = TeX("$Males$"))
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages and sexes
+# for fits to each origin, aggregated across ages
 carc_comp_fit_plot_origin = function(j) {
@@
 
-#### By Age/Sex/Origin {.tabset .tabset-pills}
+#### By Age/Origin {.tabset .tabset-pills}
 
@@
 
-These figures show the agreement of the model with the carcass composition data by age, aggregated by sex and origin.
+These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
 
@@
 
-#### By Sex {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by sex, aggregated by age and origin.
-
-##### CAT
-
-```{r cat-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_sex(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_sex(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_sex(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_sex(j_ugr)
-```
-
 #### By Origin {.tabset .tabset-pills}
 
-These figures show the agreement of the model with the carcass composition data by origin, aggregated by age and sex.
+These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
 
@@
 
-This figure illustrates that total spawners is a reasonable index of total egg production.
-The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.
+This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
+The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
 
@@
 
-The adult part is calculated across return years, by summing the number of adults of each age (regardless of sex) that return in the appropriate years.
+The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
 For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
@@
 plot_fn = function(j) {
-  x = post_summ(post, sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = j))
+  x = post_summ(post, sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = j))
 
   par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 0.6), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
+  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
   segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0(rep(c("Female", "Male"), each = jags_data$nk), "-", rep(jags_data$kmin:jags_data$kmax, jags_data$ns)), las = 2)
+  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
   segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age/Sex")
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
 ```
@@
 
-# Sex Apportionment
-
-```{r sex-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j) {
-    par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_tseries(post_summ(post, sub_index("^omega[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = pops[j], yrs = as.numeric(rownames(jags_data$Pa_obs[observable,,j])), ylim = c(0,1)); if (j == 1) mtext(side = 2, line = 1.5, "NOR")
-
-  plot_tseries(post_summ(post, sub_index("^omega[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = NULL, yrs = as.numeric(rownames(jags_data$Pa_obs[observable,,j])), ylim = c(0,1)); if (j == 1) mtext(side = 2, line = 1.5, "HOR")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, line = 1.5, outer = T, "Brood Year", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Proportion Female", cex = 1.2)
-```
-
 # Maturity {.tabset .tabset-pills}
@@
 maturity_plot = function(j) {
-  par(mfrow = c(4,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = "Age 3 Females (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = "Age 3 Females (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_nor, pop = j)), main = "Age 3 Males (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_hor, pop = j)), main = "Age 3 Males (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_nor, pop = j)), main = "Age 4 Females (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_female, origin = o_hor, pop = j)), main = "Age 4 Females (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_nor, pop = j)), main = "Age 4 Males (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,sex,origin,pop]$", sex = s_male, origin = o_hor, pop = j)), main = "Age 4 Males (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
 
@@
 
-```{r, fig.width = 4, fig.height = 7}
-maturity_plot(1)
+```{r maturity-cat, fig.width = 6, fig.height = 5}
+maturity_plot(j_cat)
 ```
@@
 
-```{r, fig.width = 4, fig.height = 7}
-maturity_plot(2)
+```{r maturity-los, fig.width = 6, fig.height = 5}
+maturity_plot(j_los)
 ```
@@
 
-```{r maturity-min, fig.width = 4, fig.height = 7}
-maturity_plot(3)
+```{r maturity-min, fig.width = 6, fig.height = 5}
+maturity_plot(j_min)
 ```
@@
 
-```{r maturity-ugr, fig.width = 4, fig.height = 7}
-maturity_plot(4)
+```{r maturity-ugr, fig.width = 6, fig.height = 5}
+maturity_plot(j_ugr)
 ```
@@
 
-## Sex Apportionment {.tabset .tabset-pills}
-
-### Mean
-
-```{r sex-bxp1, fig.width = 8, fig.height = 3.5}
+## Probability of Maturing at Age-3 {.tabset .tabset-pills}
+
+### Means
+
+```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_omega[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "Average Proportion Female", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_omega[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "Average Proportion Female", main = "HOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
 ```
@@
 
-```{r sex-bxp2, fig.width = 8, fig.height = 3.5}
+```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lomega[origin,pop]", origin = o_nor, pop = "."), "Process SD", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("sig_Lomega[origin,pop]", origin = o_hor, pop = "."), "Process SD", main = "HOR", ylim = c(0,1))
-```
-
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Females
-
-```{r age3-female-bxp, fig.width = 8, fig.height = 3.5}
+my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
+```
+
+## Probability of Maturing at Age-4 {.tabset .tabset-pills}
+
+### Means
+
+```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Males
-
-```{r age3-male-bxp, fig.width = 8, fig.height = 3.5}
+my_boxplot(sub_index("mu_psi_O2_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O2_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```
+
+### Process SD
+
+```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_male, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1_Rb[sex,origin,pop]", sex = s_male, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
-
-### Females
-
-```{r age-4-female-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_female, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_female, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Males
-
-```{r age-4-male-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_male, origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2_Rb[sex,origin,pop]", sex = s_male, origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
 ```
@@
 
+**NOTE:** The Year 3 parameters are the same as the Year 2 parameters.
+
 ```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}

### 2021-10-15 03-post-process/output-plots.Rmd

@@
 L1 = "Carcass Correction Factor"
-L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
-match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+z_diags = diag_fn("z", L1 = L1)
 

### 2021-10-15 03-post-process/output-plots.Rmd
Update to base scenario

--- 2021-10-15 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: "no-sex"
+    value: "base"
     input: text

### 2021-10-15 02-model/fit-model.R

@@ -17,7 +17,7 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 out_dir = "02-model/model-output"
 
 # specify a scenario name
-scenario = "no-sex"
+scenario = "base"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE

### 2021-10-19 03-post-process/output-plots.Rmd
Change sigma_Pb to sig_Pb throughout
For consistency with other SD terms

@@
 L2 = c("BH Productivity", "BH Capacity", "Process SD", "Parr States")
-match = c("alpha", "^beta[", "sigma_Pb", "^Pb[")
+match = c("alpha", "^beta[", "sig_Pb", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sigma_Pb[.]$", "Process SD")
+my_boxplot("^sig_Pb[.]$", "Process SD")
 ```

### 2021-10-19 01-functions/init-fns.R

@@ -174,7 +174,7 @@ gen_initials = function(c, jags_data) {
     alpha = sapply(BH_ests, function(ests) exp(rnorm(1, ests["log_alpha","Estimate"], ests["log_alpha","Std. Error"]))),
     log_beta = sapply(BH_ests, function(ests) rnorm(1, ests["log_beta","Estimate"], ests["log_beta","Std. Error"])),
     Pb = Pb_ests * matrix(exp(rnorm(jags_data$ny * jags_data$nj, 0, 0.1)), jags_data$ny, jags_data$nj),
-    sigma_Pb = runif(jags_data$nj, 0.3, 0.4),
+    sig_Pb = runif(jags_data$nj, 0.3, 0.4),
     n_stray_tot = n_stray_tot, 
     mu_init_recruits = mu_init_recruits
   )

### 2021-10-19 02-model/fit-model.R

@@ -110,7 +110,7 @@ jags_model_contents[1] = "model {"
 
 jags_params = c(
   # reproduction
-  "alpha", "beta", "sigma_Pb",
+  "alpha", "beta", "sig_Pb",
   
   # overwinter survival coefficients
   "gamma0", "gamma1",

### 2021-10-19 02-model/model-code.R

@@ -6,7 +6,7 @@ jags_model_code = function() {
     alpha[j] ~ dbeta(1, 1)
     log_beta[j] ~ dnorm(0, 0.001) %_% T(,15)   # log capacity. bound to prevent nonsensically large draws
     beta[j] <- exp(log_beta[j])
-    sigma_Pb[j] ~ dunif(0, 5)
+    sig_Pb[j] ~ dunif(0, 5)
     beta_per_peu[j] <- beta[j]/peu[j]
     
     ### PRIORS: FRESHWATER PARAMETERS ###
@@ -277,7 +277,7 @@ jags_model_code = function() {
     for (y in (kmax+1):ny) {
       # reproductive link: total summer parr
       Pb_pred[y,j] <- f_tot[y,j]/(1/alpha[j] + f_tot[y,j]/beta[j])
-      Pb[y,j] ~ dlnorm(log(Pb_pred[y,j]), 1/sigma_Pb[j]^2)
+      Pb[y,j] ~ dlnorm(log(Pb_pred[y,j]), 1/sig_Pb[j]^2)
       
       # natural origin tributary-to-LGD dynamics
       for (i in 1:ni) {

### 2021-10-22 01-functions/util-fns.R
Create new method for exporting JAGS model code to a text file
Not a consequential change, but allows retaining comments in JAGS code and showing the results of toggle_rho_estimation() (see next commit) when the JAGS code is shown in the RMD output

@@ -173,3 +173,30 @@ unlist_dfs = function(list) {
   return(output)
 }
 
+
+##### CREATE A JAGS MODEL FILE FROM AN R FUNCTION #####
+
+# this function does the same thing as postpack::write_model or R2OpenBUGS::write.model
+# except that it retains the comments contained in the source function
+
+# function to write function to file
+write_model_code = function(fun_file, out_file) {
+  
+  # extract the function body, including comments
+  # code = attr(fun, "srcref")
+  # code = as.character(code)
+  code = readLines(fun_file)
+  
+  # replace the first line
+  code[1] = "model {"
+  
+  # replace the last line
+  code[length(code)] = "}  # END OF MODEL"
+  
+  # remove any instances of "%_%"
+  code = stringr::str_remove(code, "%_%\\s?")
+  
+  # write the code to a file
+  writeLines(code, out_file)
+}
+

### 2021-10-22 02-model/fit-model.R

@@ -96,15 +96,11 @@ jags_data = append(jags_data, add_jags_data)
 
 ##### STEP 2: SPECIFY JAGS MODEL #####
 
-# source the jags model code and write to a text file
-source("02-model/model-code.R")
+# write the jags model source code to a text file
+jags_source = "02-model/model-code.R"
 jags_file = "02-model/model.txt"
-write_model(jags_model_code, jags_file)
+write_model_code(jags_source, jags_file)
 
-# store the model code as an object, to be saved in the output object later
-# use this version rather than 'model.txt' because this one retains the comments
-jags_model_contents = readLines("02-model/model-code.R")
-jags_model_contents[1] = "model {"
 
 ##### STEP 3: SELECT NODES TO MONITOR #####
 
@@ -216,9 +212,6 @@ stoptime = Sys.time()
 cat("\nMCMC ended:", format(stoptime))
 cat("\nMCMC elapsed:", format(round(stoptime - starttime, 2)))
 
-# delete the text file that contains the JAGS code
-unlink(jags_file)
-
 ##### STEP 7: SAVE THE OUTPUT #####
 
 # create the output directory if it doesn't already exist
@@ -226,7 +219,7 @@ if (!dir.exists(out_dir)) dir.create(out_dir)
 
 # create the output object: stores data, posterior samples, and population name
 out_obj = list(
-  jags_model_code = jags_model_contents,
+  jags_model_code = readLines(jags_file),
   jags_data = jags_data,
   jags_inits = jags_inits,
   jags_dims = jags_dims,
@@ -241,6 +234,9 @@ out_file = paste0("output-", scenario, ".rds")
 # save the file
 cat("\nSaving rds Output")
 saveRDS(out_obj, file.path(out_dir, out_file))
+
+# delete the text file that contains the JAGS code
+unlink(jags_file)
 
 # render the output plots if requested
 if (rmd) {

### 2021-10-22 03-post-process/output-plots.Rmd
Update vcov_decomp() code in RMD

@@
 ```{r vcov-decomp, message = FALSE}
-# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
+# Convert the precision/covariance matrices monitored by JAGS into the marginal SD and correlation matrix terms
 # postpack::vcov_decomp() does this for all posterior samples
-
-Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
+Sig_lPb = suppressMessages(vcov_decomp(post, "Sig_lPb", sigma_base_name = "sig_lPb", rho_base_name = "rho_lPb"))
+Sig_Lpi = suppressMessages(vcov_decomp(post, "Sig_Lpi", sigma_base_name = "sig_Lpi", rho_base_name = "rho_Lpi"))
+Sig_Lphi_Pa_Mb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,1]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
+Sig_Lphi_Pa_Mb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,2]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
+Sig_Lphi_Mb_Ma1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,1]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
+Sig_Lphi_Mb_Ma2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,2]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
+Sig_Lphi_Ma_O0 = suppressMessages(vcov_decomp(post, "Sig_Lphi_Ma_O0", sigma_base_name = "sig_Lphi_Ma_O0", rho_base_name = "rho_Lphi_Ma_O0"))
+Sig_Lphi_O0_O1 = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
+Sig_Lpsi_O1_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,1]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
+Sig_Lpsi_O1_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,2]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
+Sig_Lpsi_O2_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,1]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
+Sig_Lpsi_O2_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,2]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
+Sig_Lphi_Rb_Ra = suppressMessages(vcov_decomp(post, "Sig_Lphi_Rb_Ra", sigma_base_name = "sig_Lphi_Rb_Ra", rho_base_name = "rho_Lphi_Rb_Ra"))
+Sig_Lphi_Sb_Sa = suppressMessages(vcov_decomp(post, "Sig_Lphi_Sb_Sa", sigma_base_name = "sig_Lphi_Sb_Sa", rho_base_name = "rho_Lphi_Sb_Sa"))
+
+# update node names for quantities that have a third dimension to the covariance matrix (origin or LH type)
+Sig_Lphi_Pa_Mb1 = add_index(Sig_Lphi_Pa_Mb1, c("sig", "rho"), 1)
+Sig_Lphi_Pa_Mb2 = add_index(Sig_Lphi_Pa_Mb2, c("sig", "rho"), 2)
+Sig_Lphi_Mb_Ma1 = add_index(Sig_Lphi_Mb_Ma1, c("sig", "rho"), 1)
+Sig_Lphi_Mb_Ma2 = add_index(Sig_Lphi_Mb_Ma2, c("sig", "rho"), 2)
+Sig_Lpsi_O1_Rb1 = add_index(Sig_Lpsi_O1_Rb1, c("sig", "rho"), 1)
+Sig_Lpsi_O1_Rb2 = add_index(Sig_Lpsi_O1_Rb2, c("sig", "rho"), 2)
+Sig_Lpsi_O2_Rb1 = add_index(Sig_Lpsi_O2_Rb1, c("sig", "rho"), 1)
+Sig_Lpsi_O2_Rb2 = add_index(Sig_Lpsi_O2_Rb2, c("sig", "rho"), 2)
 
@@
 vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")
+vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "(,.)?]")
 
 # subset out only the unique elements
-Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))
+Sig_lPb = post_subset(Sig_lPb, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lpi = post_subset(Sig_Lpi, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Pa_Mb1 = post_subset(Sig_Lphi_Pa_Mb1, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Pa_Mb2 = post_subset(Sig_Lphi_Pa_Mb2, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Mb_Ma1 = post_subset(Sig_Lphi_Mb_Ma1, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Mb_Ma2 = post_subset(Sig_Lphi_Mb_Ma2, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Ma_O0 = post_subset(Sig_Lphi_Ma_O0, c("sig", "rho.+"))
+Sig_Lphi_O0_O1 = post_subset(Sig_Lphi_O0_O1, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lpsi_O1_Rb1 = post_subset(Sig_Lpsi_O1_Rb1, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lpsi_O1_Rb2 = post_subset(Sig_Lpsi_O1_Rb2, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lpsi_O2_Rb1 = post_subset(Sig_Lpsi_O2_Rb1, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lpsi_O2_Rb2 = post_subset(Sig_Lpsi_O2_Rb2, c("sig", paste0("rho.+", vcov_indices)))
+Sig_Lphi_Rb_Ra = post_subset(Sig_Lphi_Rb_Ra, c("sig", "rho.+"))
+Sig_Lphi_Sb_Sa = post_subset(Sig_Lphi_Sb_Sa, c("sig", paste0("rho.+", vcov_indices)))
 
 # combine these derived posterior samples with the main object
-post = post_bind(post, Sig_Lphi_O0_O1_post)
+post = post_bind(post, Sig_lPb)
+post = post_bind(post, Sig_Lpi)
+post = post_bind(post, Sig_Lphi_Pa_Mb1)
+post = post_bind(post, Sig_Lphi_Pa_Mb2)
+post = post_bind(post, Sig_Lphi_Mb_Ma1)
+post = post_bind(post, Sig_Lphi_Mb_Ma2)
+post = post_bind(post, Sig_Lphi_Ma_O0)
+post = post_bind(post, Sig_Lphi_O0_O1)
+post = post_bind(post, Sig_Lpsi_O1_Rb1)
+post = post_bind(post, Sig_Lpsi_O1_Rb2)
+post = post_bind(post, Sig_Lpsi_O2_Rb1)
+post = post_bind(post, Sig_Lpsi_O2_Rb2)
+post = post_bind(post, Sig_Lphi_Rb_Ra)
+post = post_bind(post, Sig_Lphi_Sb_Sa)
 ```

### 2021-10-22 03-post-process/output-plots.Rmd
Update MCMC diagnostics in RMD

@@
 L1 = "Parr Recruitment"
-L2 = c("BH Productivity", "BH Capacity", "Process SD", "Parr States")
-match = c("alpha", "^beta[", "sig_Pb", "^Pb[")
+L2 = c("BH Productivity", "BH Capacity", "Process SD", "Among-pop Correlation", "Parr States")
+match = c("alpha", "^beta[", "sig_lPb", "rho_lPb", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 L1 = "Life History Apportionment"
-L2 = c("Mean", "Process SD", "Realized")
-match = c("mu_pi[1,.]", "sig_Lpi", "^pi[.+,1,.]")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
 pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
+L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
@@
 L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[LH_type,origin,pop]", "phi_Mb_Ma[year,LH_type,origin,pop]")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
@@
 tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-phi_Ma_O0_diags = rbind(tmp1, tmp2)
+tmp3 = diag_fn("rho_Lphi_Ma_O0[2,1]", L1 = "Migration Survival (LGR to Ocean)", L2 = "Among-origin Correlation")
+phi_Ma_O0_diags = rbind(tmp1, tmp2, tmp3)
 
@@
 L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "psi_O1_Rb[.+,origin,pop]")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O1_Rb[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "psi_O2_Rb[.+,origin,pop]")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O2_Rb[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among Pop. Correlation", "Realized")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
 base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
@@
 # Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
+L1 = "Year 2&3 Ocean Survival"
 L2 = c("Mean")
@@
 tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
+tmp3 = diag_fn("rho_Lphi_Rb_Ra[2,1]", L1 = "Migration Survival (BON to LGR)", L2 = "Among-origin Correlation")
 phi_Rb_Ra_diags = rbind(tmp1, tmp2)
@@
 L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "phi_Sb_Sa[.+,.]")
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
 phi_Sb_Sa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

### 2021-10-22 03-post-process/output-plots.Rmd
Update parameter summary boxplots in RMD

@@
     label: "Scenario"
-    value: "base"
+    value: "mvn-short"
     input: text
@@
 ```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
+par(mfrow = c(1,4))
 my_boxplot("^alpha[.]$", "Productivity")
 my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Pb[.]$", "Process SD")
+my_boxplot("^sig_lPb[.]$", "Process SD")
+my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
 ```
@@
 ```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
+par(mfrow = c(1,3))
 my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
 my_boxplot("^sig_Lpi[.]$", "Process SD")
+my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
 ```
@@
 ```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[LH_type,pop]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
+par(mfrow = c(1,2))
+my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
+my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
+```
+
+### Among-pop Correlation
+
+```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_nor, pop = "."), "Process SD", main = "NOR")
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Process SD", main = "HOR")
+my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
+my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
+```
+
+### Among-pop Correlation
+
+```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
 ```
@@
 ```{r lgr-to-ocean-bxp}
-par(mfrow = c(1,2))
+par(mfrow = c(1,3))
 my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
 my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
+my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
+```
+
+### Among-pop Correlation
+
+```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR")
+my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
+```
+
+### Among-pop Correlation
+
+```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,2))
+my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
 ```
@@
 my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
-my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among Population Correlation", ylim = c(-1,1), las = 2)
+my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
 ```
@@
 ```{r bon-to-lgr-bxp}
-par(mfrow = c(1,2))
+par(mfrow = c(1,3))
 my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
 my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
 ```
@@
 ```{r prespawn-surv-bxp}
-par(mfrow = c(1,2))
+par(mfrow = c(1,3))
 my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
 my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
+my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
 ```

### 2021-10-22 03-post-process/output-plots.Rmd
Insignificant changes to RMD

@@
 ```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0))
+par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
 plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
@@
 ```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0))
+par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
 plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
@@
 ```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0))
+par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
 plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
@@
 ```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0))
+par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
 plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),

### 2021-10-22 03-post-process/output-plots.Rmd
Move vcov_decomp() code to fit-model.R script
This makes the sig and rho terms part of the posterior samples object, and discards the all Sig terms. This way, these terms can be easily compared among models without having to do this step later

@@
 )
-```
-
-```{r vcov-decomp, message = FALSE}
-# Convert the precision/covariance matrices monitored by JAGS into the marginal SD and correlation matrix terms
-# postpack::vcov_decomp() does this for all posterior samples
-Sig_lPb = suppressMessages(vcov_decomp(post, "Sig_lPb", sigma_base_name = "sig_lPb", rho_base_name = "rho_lPb"))
-Sig_Lpi = suppressMessages(vcov_decomp(post, "Sig_Lpi", sigma_base_name = "sig_Lpi", rho_base_name = "rho_Lpi"))
-Sig_Lphi_Pa_Mb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,1]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
-Sig_Lphi_Pa_Mb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,2]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
-Sig_Lphi_Mb_Ma1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,1]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
-Sig_Lphi_Mb_Ma2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,2]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
-Sig_Lphi_Ma_O0 = suppressMessages(vcov_decomp(post, "Sig_Lphi_Ma_O0", sigma_base_name = "sig_Lphi_Ma_O0", rho_base_name = "rho_Lphi_Ma_O0"))
-Sig_Lphi_O0_O1 = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
-Sig_Lpsi_O1_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,1]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
-Sig_Lpsi_O1_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,2]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
-Sig_Lpsi_O2_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,1]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
-Sig_Lpsi_O2_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,2]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
-Sig_Lphi_Rb_Ra = suppressMessages(vcov_decomp(post, "Sig_Lphi_Rb_Ra", sigma_base_name = "sig_Lphi_Rb_Ra", rho_base_name = "rho_Lphi_Rb_Ra"))
-Sig_Lphi_Sb_Sa = suppressMessages(vcov_decomp(post, "Sig_Lphi_Sb_Sa", sigma_base_name = "sig_Lphi_Sb_Sa", rho_base_name = "rho_Lphi_Sb_Sa"))
-
-# update node names for quantities that have a third dimension to the covariance matrix (origin or LH type)
-Sig_Lphi_Pa_Mb1 = add_index(Sig_Lphi_Pa_Mb1, c("sig", "rho"), 1)
-Sig_Lphi_Pa_Mb2 = add_index(Sig_Lphi_Pa_Mb2, c("sig", "rho"), 2)
-Sig_Lphi_Mb_Ma1 = add_index(Sig_Lphi_Mb_Ma1, c("sig", "rho"), 1)
-Sig_Lphi_Mb_Ma2 = add_index(Sig_Lphi_Mb_Ma2, c("sig", "rho"), 2)
-Sig_Lpsi_O1_Rb1 = add_index(Sig_Lpsi_O1_Rb1, c("sig", "rho"), 1)
-Sig_Lpsi_O1_Rb2 = add_index(Sig_Lpsi_O1_Rb2, c("sig", "rho"), 2)
-Sig_Lpsi_O2_Rb1 = add_index(Sig_Lpsi_O2_Rb1, c("sig", "rho"), 1)
-Sig_Lpsi_O2_Rb2 = add_index(Sig_Lpsi_O2_Rb2, c("sig", "rho"), 2)
-
-# make the labels/indices for which elements of the vcov matrices contain unique covariances
-# no point in summarizing/displaying both off-diagonal triangles
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "(,.)?]")
-
-# subset out only the unique elements
-Sig_lPb = post_subset(Sig_lPb, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lpi = post_subset(Sig_Lpi, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Pa_Mb1 = post_subset(Sig_Lphi_Pa_Mb1, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Pa_Mb2 = post_subset(Sig_Lphi_Pa_Mb2, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Mb_Ma1 = post_subset(Sig_Lphi_Mb_Ma1, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Mb_Ma2 = post_subset(Sig_Lphi_Mb_Ma2, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Ma_O0 = post_subset(Sig_Lphi_Ma_O0, c("sig", "rho.+"))
-Sig_Lphi_O0_O1 = post_subset(Sig_Lphi_O0_O1, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lpsi_O1_Rb1 = post_subset(Sig_Lpsi_O1_Rb1, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lpsi_O1_Rb2 = post_subset(Sig_Lpsi_O1_Rb2, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lpsi_O2_Rb1 = post_subset(Sig_Lpsi_O2_Rb1, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lpsi_O2_Rb2 = post_subset(Sig_Lpsi_O2_Rb2, c("sig", paste0("rho.+", vcov_indices)))
-Sig_Lphi_Rb_Ra = post_subset(Sig_Lphi_Rb_Ra, c("sig", "rho.+"))
-Sig_Lphi_Sb_Sa = post_subset(Sig_Lphi_Sb_Sa, c("sig", paste0("rho.+", vcov_indices)))
-
-# combine these derived posterior samples with the main object
-post = post_bind(post, Sig_lPb)
-post = post_bind(post, Sig_Lpi)
-post = post_bind(post, Sig_Lphi_Pa_Mb1)
-post = post_bind(post, Sig_Lphi_Pa_Mb2)
-post = post_bind(post, Sig_Lphi_Mb_Ma1)
-post = post_bind(post, Sig_Lphi_Mb_Ma2)
-post = post_bind(post, Sig_Lphi_Ma_O0)
-post = post_bind(post, Sig_Lphi_O0_O1)
-post = post_bind(post, Sig_Lpsi_O1_Rb1)
-post = post_bind(post, Sig_Lpsi_O1_Rb2)
-post = post_bind(post, Sig_Lpsi_O2_Rb1)
-post = post_bind(post, Sig_Lpsi_O2_Rb2)
-post = post_bind(post, Sig_Lphi_Rb_Ra)
-post = post_bind(post, Sig_Lphi_Sb_Sa)
 ```

### 2021-10-22 02-model/fit-model.R

@@ -217,7 +217,88 @@ stoptime = Sys.time()
 cat("\nMCMC ended:", format(stoptime))
 cat("\nMCMC elapsed:", format(round(stoptime - starttime, 2)))
 
-##### STEP 7: SAVE THE OUTPUT #####
+##### STEP 7: PROCESS COVARIANCE MATRICES #####
+
+# decompose all covariance matrices ("^Sig.+" nodes)
+# into an SD vector and a correlation matrix
+# postpack::vcov_decomp() does this for all posterior samples
+# do this here so these quantities can be easily compared across models
+
+cat("\nDecomposing all covariance matrices")
+
+# Convert the precision/covariance matrices monitored by JAGS into the marginal SD and correlation matrix terms
+suppressMessages({
+  Sig_lPb = vcov_decomp(post, "Sig_lPb", sigma_base_name = "sig_lPb", rho_base_name = "rho_lPb")
+  Sig_Lpi = vcov_decomp(post, "Sig_Lpi", sigma_base_name = "sig_Lpi", rho_base_name = "rho_Lpi")
+  Sig_Lphi_Pa_Mb1 = vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,1]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb")
+  Sig_Lphi_Pa_Mb2 = vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,2]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb")
+  Sig_Lphi_Mb_Ma1 = vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,1]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma")
[…]

### 2021-10-22 03-post-process/output-plots.Rmd
Move creation of vcov_labels/indices

@@
 )
+
+# make the labels for which elements of the rho matrices contain unique elements
+dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
+dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
+vcov_cols = dummy_cols[lower.tri(dummy_cols)]
+vcov_rows = dummy_rows[lower.tri(dummy_rows)]
+vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
 ```

### 2021-10-22 02-model/fit-model.R

@@ -260,7 +260,6 @@ dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags
 dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
 vcov_cols = dummy_cols[lower.tri(dummy_cols)]
 vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
 vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "(,.)?]")
 
 # subset out only the unique elements

### 2021-10-22 03-post-process/output-plots.Rmd
Make this the base scenario

@@
     label: "Scenario"
-    value: "mvn-short"
+    value: "base"
     input: text

### 2021-11-24 03-post-process/output-plots.Rmd
Update overwinter surv plotting code to use WUL instead of PEU

@@
 plot_fn = function(j) {
-  # extract parr, scale it to PEU, and create new post object
+  # extract parr, scale it to WUL, and create new post object
   Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
-  Pa_scaled = Pa/jags_data$peu[j]
+  Pa_scaled = Pa/jags_data$wul[j]
   colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
+mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/WUL", cex = 1.2)
 mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)

### 2021-11-24 03-post-process/compare-sim-to-obs.Rmd

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario:', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base-with-sim-medium"
    input: text
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4)
knitr::opts_knit$set(root.dir = "../")
```

```{r load}
# load packages
source("00-packages.R")

# load all necessary functions
invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))

# set the input directory
in_dir = "02-model/model-output"

# read information from this model
model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))

# extract the two key structures from this object
# post = model_info$post                               # full posterior takes a long time to run on this script
post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

```{r select-years}
all_yrs = as.numeric(rownames(jags_data$phi_SL))
fy_obs = which(all_yrs == 2001)

# for non sar values, which years correspond to observed and simulated years?
obs_y = with(jags_data, fy_obs:ny_obs)
sim_y = with(jags_data, (ny_obs+1):ny)

# same but for sar values. A bit different because not all adults have returned from the last brood year.
obs_sar_y = with(jags_data, fy_obs:(ny_obs-kmax))
sim_sar_y = with(jags_data, (ny_obs-kmax+1):(ny-kmax))
```

```{r add-p-hos}
# extract spawners returning to tributary
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
  out = rbind(out, as.numeric(hor/(nor + hor)))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out) = paste0("p_hor[", r_ind, ",", c_ind, "]")

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Rb-tot}
# extract spawners returning to tributary
Rb = post_subset(post, "^Rb[", matrix = TRUE)

# for each posterior sample, calculate the fraction that are hatchery origin
out = NULL
for (i in 1:nrow(Ra)) {
  Rb_i = array_format(Rb[i,])
  nor = Rb_i[,1,1,] + Rb_i[,2,1,] + Rb_i[,3,1,]
  hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
  out = rbind(out, as.numeric(nor + hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-Ma-tot}
# extract smolt at LGR
Ma = post_subset(post, "^Ma[", matrix = TRUE)

# for each posterior sample, calculate the number of NOR and HOR smolt at LGR
out_nor = NULL
out_hor = NULL
for (i in 1:nrow(Ra)) {
  Ma_i = array_format(Ma[i,])
  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
  hor = Ma_i[,1,2,] + Ma_i[,2,2,]
  out_nor = rbind(out_nor, as.numeric(nor))
  out_hor = rbind(out_hor, as.numeric(hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(nor), ncol(nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(nor), each = nrow(nor))

# make element names
colnames(out_nor) = paste0("Ma_tot[", r_ind, ",", "1", ",", c_ind, "]")
colnames(out_hor) = paste0("Ma_tot[", r_ind, ",", "2", ",", c_ind, "]")
out = cbind(out_nor, out_hor)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-age-comp}
Ra = post_subset(post, "^Ra[", matrix = TRUE)

# for each posterior sample, calculate the fraction that of each age by origin
p3_nor_out = p4_nor_out = p5_nor_out = p3_hor_out = p4_hor_out = p5_hor_out = NULL
for (i in 1:nrow(Ra)) {
  Ra_i = array_format(Ra[i,])
  nor_tot = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
  hor_tot = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]

  p3_nor = Ra_i[,1,1,]/nor_tot
  p4_nor = Ra_i[,2,1,]/nor_tot
  p5_nor = Ra_i[,3,1,]/nor_tot
  p3_hor = Ra_i[,1,2,]/hor_tot
  p4_hor = Ra_i[,2,2,]/hor_tot
  p5_hor = Ra_i[,3,2,]/hor_tot

  p3_nor_out = rbind(p3_nor_out, as.numeric(p3_nor))
  p4_nor_out = rbind(p4_nor_out, as.numeric(p4_nor))
  p5_nor_out = rbind(p5_nor_out, as.numeric(p5_nor))
  p3_hor_out = rbind(p3_hor_out, as.numeric(p3_hor))
  p4_hor_out = rbind(p4_hor_out, as.numeric(p4_hor))
  p5_hor_out = rbind(p5_hor_out, as.numeric(p5_hor))
}

# build the row indices for each element: the year
r_ind = rep(1:nrow(p3_nor), ncol(p3_nor))

# build the column indices for each element: the population
c_ind = rep(1:ncol(p3_nor), each = nrow(p3_nor))

# make element names
colnames(p3_nor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "1", ",", c_ind, "]")
colnames(p4_nor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "1", ",", c_ind, "]")
colnames(p5_nor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "1", ",", c_ind, "]")
colnames(p3_hor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "2", ",", c_ind, "]")
colnames(p4_hor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "2", ",", c_ind, "]")
colnames(p5_hor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "2", ",", c_ind, "]")

out = cbind(p3_nor_out, p4_nor_out, p5_nor_out, p3_hor_out, p4_hor_out, p5_hor_out)

# drop out those that have NA values (first k_max years)
out[out == "NaN"] = 0
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-trib-smolt-per-parr}
Mb = post_subset(post, "^Mb[", matrix = TRUE)
Pa = post_subset(post, "^Pa[", matrix = TRUE)

# for each posterior sample, calculate survival from parr to lgr smolt by LH type
out_fall = out_spring = NULL

for (i in 1:nrow(Mb)) {
  Mb_i = array_format(Mb[i,])
  Pa_i = array_format(Pa[i,])

  Mb_per_Pa = Mb_i[,,1,]/Pa_i

  out_fall = rbind(out_fall, as.numeric(Mb_per_Pa[,1,]))
  out_spring = rbind(out_spring, as.numeric(Mb_per_Pa[,2,]))
}

# build the row indices for each element: the year
r_ind = rep(1:dim(Mb_per_Pa)[1], dim(Mb_per_Pa)[3])

# build the column indices for each element: the population
c_ind = rep(1:dim(Mb_per_Pa)[3], each = dim(Mb_per_Pa)[1])

# make element names
colnames(out_fall) = paste0("Mb_per_Pa[", r_ind, ",", "1", ",", c_ind, "]")
colnames(out_spring) = paste0("Mb_per_Pa[", r_ind, ",", "2", ",", c_ind, "]")

out = cbind(out_fall, out_spring)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)
```

```{r add-lgr-smolt-per-parr}
Ma = post_subset(post, "^Ma[", matrix = TRUE)
Pa = post_subset(post, "^Pa[", matrix = TRUE)

# for each posterior sample, calculate survival from parr to lgr smolt by LH type
out_fall = out_spring = NULL

for (i in 1:nrow(Ma)) {
  Ma_i = array_format(Ma[i,])
  Pa_i = array_format(Pa[i,])

  Ma_per_Pa = Ma_i[,,1,]/Pa_i

  out_fall = rbind(out_fall, as.numeric(Ma_per_Pa[,1,]))
  out_spring = rbind(out_spring, as.numeric(Ma_per_Pa[,2,]))
}

# build the row indices for each element: the year
r_ind = rep(1:dim(Ma_per_Pa)[1], dim(Ma_per_Pa)[3])

# build the column indices for each element: the population
c_ind = rep(1:dim(Ma_per_Pa)[3], each = dim(Ma_per_Pa)[1])

# make element names
colnames(out_fall) = paste0("Ma_per_Pa[", r_ind, ",", "1", ",", c_ind, "]")
colnames(out_spring) = paste0("Ma_per_Pa[", r_ind, ",", "2", ",", c_ind, "]")

out = cbind(out_fall, out_spring)

# drop out those that have NA values (first k_max years)
na_ind = which(!is.na(out[1,]))
out = out[,na_ind]

# combine this with the rest of the posterior samples
post = post_bind(post, out)

```

```{r dim_names fn}
# function to create dimension names from numeric indicators
dim_names = function(LH_type = NULL, age = NULL, origin = NULL, pop = NULL) {

  # empty list
  out = list()

  # combine the dimention names for each type supplied
  if (!is.null(LH_type)) out = append(out, list(LH_type = c("fall", "spring")[LH_type]))
  if (!is.null(age)) out = append(out, list(age = c("age3", "age4", "age5")[age]))
  if (!is.null(origin)) out = append(out, list(origin = c("NOR", "HOR")[origin]))
  if (!is.null(pop)) out = append(out, list(pop = c("CAT", "LOS", "MIN", "UGR")[pop]))

  return(out)
}
```

```{r get_ratio fn}
# function to calculate the ratio of mean and CV between simulated and observed years
get_ratio = function(param, obs_y, sim_y, ...) {

  # get node names for the observed years
  obs_param = sub_index(param, year = obs_y, ...)

  # get node names for the simulated years
  sim_param = sub_index(param, year = sim_y, ...)

  # extract posterior samples of these
  obs_x = post_subset(post, obs_param, matrix = TRUE)
  sim_x = post_subset(post, sim_param, matrix = TRUE)

  # obtain a nicely formatted parameter identifier
  named_param = do.call(sub_index, append(list(x = param), dim_names(...)))
  named_param = stringr::str_remove(named_param, "year,")
  named_param = stringr::str_extract(named_param, "\\[.+\\]")
  named_param = stringr::str_remove(named_param, "age[:digit:],")
  named_param = stringr::str_remove(named_param, "\\[")
  named_param = stringr::str_remove(named_param, "\\]")

  # function calculate lag-1 autocorrelation coefficient
  get_1_acf = function(x) acf(x, lag.max = 1, plot = FALSE)$acf[2,1,1]

  # calculate and return the summary statistics for each posterior sample and period
  vals_out = array(NA, dim = c(nrow(obs_x), 3, 3, 1))
  dimnames(vals_out) = list(iter = 1:nrow(obs_x), period = c("obs", "sim", "sim-v-obs"), stat = c("cv", "mean", "acf"), dims = named_param)
  vals_out[,"obs","mean",] = sapply(1:nrow(obs_x), function(i) mean(obs_x[i,]))
  vals_out[,"sim","mean",] = sapply(1:nrow(sim_x), function(i) mean(sim_x[i,]))
  vals_out[,"obs","cv",] = sapply(1:nrow(obs_x), function(i) sd(obs_x[i,])/mean(obs_x[i,]))
  vals_out[,"sim","cv",] = sapply(1:nrow(sim_x), function(i) sd(sim_x[i,])/mean(sim_x[i,]))
  vals_out[,"obs","acf",] = sapply(1:nrow(obs_x), function(i) get_1_acf(obs_x[i,]))
  vals_out[,"sim","acf",] = sapply(1:nrow(sim_x), function(i) get_1_acf(sim_x[i,]))
  vals_out[,"sim-v-obs","cv",] = vals_out[,"sim","cv",]/vals_out[,"obs","cv",]
  vals_out[,"sim-v-obs","mean",] = vals_out[,"sim","mean",]/vals_out[,"obs","mean",]
  vals_out[,"sim-v-obs","acf",] = vals_out[,"sim","acf",] - vals_out[,"obs","acf",]

  return(vals_out)
}

```

```{r ratio_plot fn}
ratio_plot = function(ratios, line_y, ...) {

  # calculate summaries of the ratios
  summs = apply(ratios, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE))

  # set graphics parameters
  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")

  # make an empty plot with the right dimensions
  mp = barplot(summs["50%",], col = "white", ylab = "", border = "white", las = 2,
               ylim = c(min(0, min(summs, na.rm = TRUE)), max(summs, na.rm = TRUE)) * 1.1, ...)

  # draw tick labels
  axis(side = 1, at = mp, labels = F)

  # create an "acceptable region"
  usr = par("usr"); rect(usr[1], line_y - 0.25, usr[2], line_y + 0.25, col = "grey90", border = NA)
  abline(h = line_y, lty = 2, col = "grey")

  # draw the ratio summaries
  segments(mp, summs["2.5%",], mp, summs["97.5%",])
  segments(mp, summs["25%",], mp, summs["75%",], lwd = 6)
  points(summs["50%",] ~ mp, pch = 3, cex = 1.5)
  box()
}
```

```{r ratio_plots fn}
ratio_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2,2,0))
  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", line_y = 1)
  ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", line_y = 1)
  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", line_y = 0)
  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Ratio (Sim:Obs)")
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```

```{r vals_plot fn}
vals_plot = function(vals, ...) {
  f = function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE)

  summs = array(NA, dim = c(2,5,dim(vals)[3]))
  dimnames(summs) = list(c("obs", "sim"), names(f(rnorm(10))), dimnames(x)[[4]])

  summs["obs",,] = apply(vals[,"obs",], 2, f)
  summs["sim",,] = apply(vals[,"sim",], 2, f)

  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
  mp = barplot(summs[,"50%",], beside = TRUE, col = "white", border = "white", ylim = range(summs, na.rm = TRUE) + diff(range(summs, na.rm = TRUE)) * c(-0.05,0.05), xaxt = "n", ...)
  segments(mp, summs[,"2.5%",], mp, summs[,"97.5%",], col = c("red", "blue"))
  segments(mp, summs[,"25%",], mp, summs[,"75%",], col = c("red", "blue"), lwd = 6)
  points(y = summs[,"50%",], x = mp, col = c("red", "blue"), pch = 3, cex = 1.5)
  axis(side = 1, at = colSums(mp)/2, labels = dimnames(summs)[[3]], las = 2)
  box()
}
```

```{r vals_plots fn}
vals_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2,2,0))
  vals_plot(x[,c("obs", "sim"),"cv",], main = "CV")
  vals_plot(x[,c("obs", "sim"),"mean",], main = "Mean")
  vals_plot(x[,c("obs", "sim"),"acf",], main = "ACF")
  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Value")
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```

For us to use the state-space model as a simulation model, it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

This document is intended to identify whether simulated outcomes are similar to observed outcomes. It looks at two primary types of quantities: stochastic time series parameters (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes (e.g., total adult return abundance, BON to BON SAR rates, etc.). Because all emergent outcomes are derived from the stochastic elements, issues with emergent outcomes should be traceable to specific stochastic parents.

The JAGS model was altered to carry out the life cycle processes through brood year 2050. This means for each posterior sample we have an observed and simulated time series. The simulated time series picks up where the observed on left off, and assumes the same random processes for all components as used in the observed time series. Several quantities are supplied to the model as known without error (weir removals, hatchery smolt releases, harvest rates below BON, etc.). These time series were extended to the future years external to the model using basic averages or resampling from historical outcomes as appropriate. This exercise is purely for model validation.

Observed vs. simulated consistency is visualized in two ways: by comparing summary statistics of the inter-annual variation and central tendency and by directly comparing the historical time series with 5 random simulated futures.

# Distribution Comparison Plots

These plots show summaries of a quantity in the model:

1. **Inter-annual CV**: measures how variable the quantity is among years
2. **Inter-annual mean**: measures the central tendency of the quantity across years
3. **Lag-1 autocorrelation**: measures whether consecutive years are independent

If these summary statistics are inconsistent among the observed and simulated time periods, that indicates that the state-space model has not sufficiently captured the random processes that have generated the observed outcomes and that we may have reason to question the reliability of its ability to simulate future outcomes, at least as a direct extension of the historical population dynamics.

In all figures in this section, these time periods were used:

* **Observed**: `r paste0(all_yrs[min(obs_y)], " -- ", all_yrs[max(obs_y)])`
* **Simulated**: `r paste0(all_yrs[min(sim_y)], " -- ", all_yrs[max(sim_y)])`

The entire 1991 - 2019 period isn't used for the observed period because the early years did not have a hatchery program but the simulation has hatchery input in all years. Thus, including the non-hatchery years may throw off the inference.

For each quantity, two types of plots are shown:

* **Estimates**: this shows the CV, mean, and autocorrelation coefficient for a quantity based on the time period (red = observed, blue = simulated)
* **Ratios**: this shows a ratio between the summary statistic between simulated and observed periods. For CV and mean, this is simulated/observed, and for autocorrelation this is simulated - observed.

These summary statistics were calculated for each posterior sample. In all plots, the cross mark represents the posterior median, the thick bar represents the central 50% of posterior samples, and the thin bar represents the central 95% of posterior samples.

## Time Series Parameters {.tabset .tabset-pills}

### Freshwater Juvenile Phase {.tabset .tabset-pills}

#### Egg to Parr Survival

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb_per_f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Egg to Parr Survival: Estimates")
ratio_plots(x, "Egg to Parr Survival: Ratios")
```

#### Proportion Fall Migrants

```{r}
x = lapply(1:4, function(j) get_ratio("^pi[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Fall Migrants: Estimates")
ratio_plots(x, "Proportion Fall Migrants: Ratios")
```

#### Overwinter Survival

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Overwinter Survival: Estimates")
ratio_plots(x, "Overwinter Survival: Ratios")
```

#### Migration to LGR Survival

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Migration to LGR Survival: Estimates")
ratio_plots(x, "Migration to LGR Survival: Ratios")
```

#### LGR to Ocean Survival

```{r}
x = append(
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "LGR to Ocean Survival: Estimates")
ratio_plots(x, "LGR to Ocean Survival: Ratios")
```

### Marine Juvenile Phase {.tabset .tabset-pills}

#### Year 1 Ocean Survival

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "First Year Ocean Survival: Estimates")
ratio_plots(x, "First Year Ocean Survival: Ratios")
```

#### Age-3 Maturity

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-3 Maturity: Estimates")
ratio_plots(x, "Age-3 Maturity: Ratios")
```

#### Age-4 Maturity

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-4 Maturity: Estimates")
ratio_plots(x, "Age-4 Maturity: Ratios")
```

### Freshwater Adult Phase {.tabset .tabset-pills}

#### BON to LGR Survival

```{r}
x = append(
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "BON to LGR Survival: Estimates")
ratio_plots(x, "BON to LGR Survival: Ratios")
```

#### Pre-Spawn Survival

```{r}
x = lapply(1:4, function(j) get_ratio("^phi_Sb_Sa[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Pre-Spawn Survival: Estimates")
ratio_plots(x, "Pre-Spawn Survival: Ratios")
```

## Emergent Properties {.tabset .tabset-pills}

### Abundance Quantities {.tabset .tabset-pills}

#### Total Adult Return (To Estuary)

```{r}
x = lapply(1:4, function(j) get_ratio("^Rb_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Estuary): Estimates")
ratio_plots(x, "Total Adults (Estuary): Ratios")
```

#### Total Adult Return (To Tributary)

```{r}
x = lapply(1:4, function(j) get_ratio("^Ra_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Adults (Tributary): Estimates")
ratio_plots(x, "Total Adults (Tributary): Ratios")
```

#### Total Spawners

```{r}
x = lapply(1:4, function(j) get_ratio("^Sa_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Spawners: Estimates")
ratio_plots(x, "Total Spawners: Ratios")
```

#### Total Egg Production

```{r}
x = lapply(1:4, function(j) get_ratio("^f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Egg Production: Estimates")
ratio_plots(x, "Total Egg Production: Ratios")
```

#### Total Parr Recruitment

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Parr Recruitment: Estimates")
ratio_plots(x, "Total Parr Recruitment: Ratios")
```

#### Total LGR Smolt

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total LGR Smolt: Estimates")
ratio_plots(x, "Total LGR Smolt: Ratios")
```

### SAR Rates {.tabset .tabset-pills}

#### BON to BON SAR

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("phi_O0_Rb_BON[year,origin,pop]", obs_sar_y, sim_sar_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("phi_O0_Rb_BON[year,origin,pop]", obs_sar_y, sim_sar_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "BON to BON SAR: Estimates")
ratio_plots(x, "BON to BON SAR: Ratios")
```

#### LGR to LGR SAR

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_per_Ma[year,origin,pop]", obs_sar_y, sim_sar_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Ra_per_Ma[year,origin,pop]", obs_sar_y, sim_sar_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "LGR to LGR SAR: Estimates")
ratio_plots(x, "LGR to LGR SAR: Ratios")
```

### Production Rates {.tabset .tabset-pills}

#### Parr per Spawner

```{r}
x = lapply(1:4, function(j) get_ratio("Pb_per_Sa_tot[year,pop]", obs_sar_y, sim_sar_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Parr per Spawner: Estimates")
ratio_plots(x, "Parr per Spawner: Ratios")
```

#### Smolt per Spawner

```{r}
x = lapply(1:4, function(j) get_ratio("Mb_per_Sa_tot[year,pop]", obs_sar_y, sim_sar_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Smolt per Spawner: Estimates")
ratio_plots(x, "Smolt per Spawner: Ratios")
```

#### Smolt in Tributary per Parr

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Mb_per_Pa[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1)),
  lapply(1:4, function(j) get_ratio("Mb_per_Pa[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Smolt in Tributary per Parr: Estimates")
ratio_plots(x, "Smolt in Tributary per Parr: Ratios")
```

#### Smolt at LGR per Parr

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ma_per_Pa[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1)),
  lapply(1:4, function(j) get_ratio("Ma_per_Pa[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Smolt at LGR per Parr: Estimates")
ratio_plots(x, "Smolt at LGR per Parr: Ratios")
```

#### Spawners per Spawner

```{r}
x = lapply(1:4, function(j) get_ratio("Sa_tot_per_Sa_tot[year,pop]", obs_sar_y, sim_sar_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Spawners per Spawner: Estimates")
ratio_plots(x, "Spawners per Spawner: Ratios")
```

### Adult Composition {.tabset .tabset-pills}

#### Proportion Hatchery Return

```{r}
x = lapply(1:4, function(j) get_ratio("p_hor[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Hatchery Return: Estimates")
ratio_plots(x, "Proportion Hatchery Return: Ratios")
```

#### Proportion Age-3 Return

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 1, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Age-3 Return: Estimates")
ratio_plots(x, "Proportion Age-3 Return: Ratios")
```

#### Proportion Age-4 Return

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 2, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Age-4 Return: Estimates")
ratio_plots(x, "Proportion Age-4 Return: Ratios")
```

#### Proportion Age-5 Return

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("Ra_comp[year,age,origin,pop]", obs_y, sim_y, age = 3, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Age-5 Return: Estimates")
ratio_plots(x, "Proportion Age-5 Return: Ratios")
```

# Time Series Plots

```{r}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 8)
```

```{r ts_plot fn}
n_sim_draw = 5
isim = sample(1:post_dim(post, "saved"), n_sim_draw, replace = FALSE)
obs_y = 6:jags_data$ny_obs
obs_sar_y = 6:(jags_data$ny_obs-jags_data$kmax)
sim_sar_y = (jags_data$ny_obs-jags_data$kmax+1):(jags_data$ny-jags_data$kmax)

# param = "phi_O0_Rb_BON[year,origin,pop]"
# obs_y_use = obs_sar_y
# sim_y_use = sim_sar_y
# origin = 1
# main = "main"

ts_plot = function(param, main, obs_y_use = obs_y, sim_y_use = sim_y, ...) {

  obs_vals = post_summ(post, sub_index(param, year = obs_y_use, ...))
  sim_vals = post_subset(post, sub_index(param, year = sim_y_use, ...), matrix = TRUE)
  # obs_vals = post_summ(post, sub_index(param, year = obs_y_use, pop = 1, origin = 1))
  # sim_vals = post_subset(post, sub_index(param, year = sim_y_use, pop = 1, origin = 1), matrix = TRUE)

  par(mar = c(1,2,2,1), mgp = c(2,0.35,0), tcl = -0.15)
  plot(obs_vals["mean",] ~ obs_y_use, type = "n", xlim = range(6, sim_y_use),
       ylim = range(obs_vals[c("2.5%", "97.5%"),], sim_vals[isim,]), xaxt = "n", xlab = "", ylab = "", main = main)
  usr = par("usr"); at_x = axisTicks(usr[1:2], log = FALSE)
  at_x = c(6, at_x[!(at_x %in% c(0, 6, max(sim_y_use)))], max(sim_y_use))
  axis(side = 1, at = at_x, labels = all_yrs[at_x])

  polygon(c(obs_y_use, rev(obs_y_use)), c(obs_vals["2.5%",], rev(obs_vals["97.5%",])), border = NA, col = alpha("salmon", 0.5))
  lines(obs_vals["mean",] ~ obs_y_use, col = "red", lwd = 2)

  junk = sapply(isim, function(i) lines(sim_vals[i,] ~ sim_y_use, col = alpha("blue", 0.5)))
}

pop_ts_plots = function(param, obs_y_use = obs_y, sim_y_use = sim_y, ...) {
  par(mfrow = c(4,1), oma = c(2,2,0,0))
  ts_plot(param, main = "CAT", obs_y_use = obs_y_use, sim_y_use = sim_y_use, pop = 1, ...)
  ts_plot(param, main = "LOS", obs_y_use = obs_y_use, sim_y_use = sim_y_use, pop = 2, ...)
  ts_plot(param, main = "MIN", obs_y_use = obs_y_use, sim_y_use = sim_y_use, pop = 3, ...)
  ts_plot(param, main = "UGR", obs_y_use = obs_y_use, sim_y_use = sim_y_use, pop = 4, ...)
  mtext(side = 1, outer = TRUE, line = 0.5, "Year")
  mtext(side = 2, outer = TRUE, line = 0.5, "Value")
}
```

## Time Series Parameters {.tabset .tabset-pills}

### Freshwater Juvenile Phase {.tabset .tabset-pills}

#### Egg to Parr Survival

```{r}
pop_ts_plots("^Pb_per_f_tot[year,pop]")
```

#### Proportion Fall Migrants

```{r}
pop_ts_plots("^pi[year,LH_type,pop]", LH_type = 1)
```

#### Overwinter Survival {.tabset .tabset-pills}

##### Fall Migrants

```{r}
pop_ts_plots("^phi_Pa_Mb[year,LH_type,pop]", LH_type = 1)
```

##### Spring Migrants

```{r}
pop_ts_plots("^phi_Pa_Mb[year,LH_type,pop]", LH_type = 2)
```

#### Migration to LGR Survival {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("^phi_Mb_Ma[year,LH_type,origin,pop]", LH_type = 2, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("^phi_Mb_Ma[year,LH_type,origin,pop]", LH_type = 2, origin = 2)
```

#### LGR to Ocean Survival

```{r}
par(mfrow = c(2,1), oma = c(2,2,0,0))
ts_plot("^phi_Ma_O0[year,origin]", main = "NOR", origin = 1)
ts_plot("^phi_Ma_O0[year,origin]", main = "HOR", origin = 2)
mtext(side = 1, outer = TRUE, line = 0.5, "Year")
mtext(side = 2, outer = TRUE, line = 0.5, "Value")
```

### Marine Juvenile Phase {.tabset .tabset-pills}

#### Year 1 Ocean Survival {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("phi_O0_O1[year,origin,pop]", origin = 1)
```

##### HOR

```{r}
pop_ts_plots("phi_O0_O1[year,origin,pop]", origin = 1)
```

#### Age-3 Maturity {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("^psi_O1_Rb[year,origin,pop]", origin = 1)
```

##### HOR

```{r}
pop_ts_plots("^psi_O1_Rb[year,origin,pop]", origin = 1)
```

#### Age-4 Maturity {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("^psi_O2_Rb[year,origin,pop]", origin = 1)
```

##### HOR

```{r}
pop_ts_plots("^psi_O2_Rb[year,origin,pop]", origin = 1)
```

### Freshwater Adult Phase {.tabset .tabset-pills}

#### BON to LGR Survival

```{r}
par(mfrow = c(2,1), oma = c(2,2,0,0))
ts_plot("^phi_Rb_Ra[year,origin]", main = "NOR", origin = 1)
ts_plot("^phi_Rb_Ra[year,origin]", main = "HOR", origin = 2)
mtext(side = 1, outer = TRUE, line = 0.5, "Year")
mtext(side = 2, outer = TRUE, line = 0.5, "Value")
```

#### Pre-Spawn Survival

```{r}
pop_ts_plots("^phi_Sb_Sa[year,pop]")
```

## Emergent Properties {.tabset .tabset-pills}

### Abundance Quantities {.tabset .tabset-pills}

#### Total Adult Return (To Estuary)

```{r}
pop_ts_plots("^Rb_tot[year,pop]")
```

#### Total Adult Return (To Tributary)

```{r}
pop_ts_plots("^Ra_tot[year,pop]")
```

#### Total Spawners

```{r}
pop_ts_plots("^Sa_tot[year,pop]")
```

#### Total Egg Production

```{r}
pop_ts_plots("^f_tot[year,pop]")
```

#### Total Parr Recruitment

```{r}
pop_ts_plots("^Pb[year,pop]")
```

#### Total LGR Smolt {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("Ma_tot[year,origin,pop]", origin = 1)
```

##### HOR

```{r}
pop_ts_plots("Ma_tot[year,origin,pop]", origin = 2)
```

### SAR Rates {.tabset .tabset-pills}

#### BON to BON SAR {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("phi_O0_Rb_BON[year,origin,pop]", obs_y_use = obs_sar_y, sim_y_use = sim_sar_y, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("phi_O0_Rb_BON[year,origin,pop]", obs_y_use = obs_sar_y, sim_y_use = sim_sar_y, origin = 2)
```

#### LGR to LGR SAR {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("Ra_per_Ma[year,origin,pop]", obs_y_use = obs_sar_y, sim_y_use = sim_sar_y, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("Ra_per_Ma[year,origin,pop]", obs_y_use = obs_sar_y, sim_y_use = sim_sar_y, origin = 2)
```

### Production Rates {.tabset .tabset-pills}

#### Parr per Spawner

```{r}
pop_ts_plots("Pb_per_Sa_tot[year,pop]")
```

#### Smolt per Spawner

```{r}
pop_ts_plots("Mb_per_Sa_tot[year,pop]")
```

#### Smolt in Tributary per Parr {.tabset .tabset-pills}

##### Fall Migrants

```{r}
pop_ts_plots("Mb_per_Pa[year,LH_type,pop]", LH_type = 1)
```

##### Fall Migrants

```{r}
pop_ts_plots("Mb_per_Pa[year,LH_type,pop]", LH_type = 2)
```

#### Smolt at LGR per Parr {.tabset .tabset-pills}

##### Fall Migrants

```{r}
pop_ts_plots("Ma_per_Pa[year,LH_type,pop]", LH_type = 1)
```

##### Fall Migrants

```{r}
pop_ts_plots("Ma_per_Pa[year,LH_type,pop]", LH_type = 2)
```

#### Spawners per Spawner

```{r}
pop_ts_plots("Sa_tot_per_Sa_tot[year,pop]", obs_y_use = obs_sar_y, sim_y_use = sim_sar_y)
```

### Adult Composition {.tabset .tabset-pills}

#### Proportion Hatchery Return

```{r}
pop_ts_plots("p_hor[year,pop]")
```

#### Proportion Age-3 Return {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 1, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 1, origin = 2)
```

#### Proportion Age-4 Return {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 2, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 2, origin = 2)
```

#### Proportion Age-5 Return {.tabset .tabset-pills}

##### NOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 3, origin = 1)
```

##### HOR

```{r}
pop_ts_plots("Ra_comp[year,age,origin,pop]", age = 3, origin = 2)
```

### 2021-11-29 02-model/model-code.R
Reparameterize parr recruitment process
Have BH relationship predict egg to parr survival rather than total parr, as described in #112

@@ -8,9 +8,9 @@ jags_model_code = function() {
     ### PRIORS: RECRUITMENT FUNCTION ###
     # total egg production to aggregate parr recruitment function
     alpha[j] ~ dbeta(1, 1)
-    sig_Pb[j] ~ dunif(0, 5)
     lbeta[j] ~ dnorm(log(mu_beta_per_wul * wul[j]), 1/sig_lbeta^2) %_% T(,15) # log capacity. bound to prevent nonsensically large draws
     beta[j] <- exp(lbeta[j])
+    sig_Lphi_f_Pb[j] ~ dunif(0, 5)
     beta_per_wul[j] <- beta[j]/wul[j]
 
     ### PRIORS: FRESHWATER PARAMETERS ###
@@ -119,7 +119,7 @@ jags_model_code = function() {
   
   # correlation parameters
   # see toggle_rho_estimation() function; 01-functions/util-fns.R
-  rho_lPb <- 0
+  rho_Lphi_f_Pb <- 0
   rho_Lpi <- 0
   rho_Lphi_Pa_Mb[i_fall] <- 0
   rho_Lphi_Pa_Mb[i_spring] <- 0
@@ -138,7 +138,7 @@ jags_model_code = function() {
   for (i in 1:nj) {
     for (j in 1:nj) {
       # covariance matrix of parr recruitment
-      Sig_lPb[i,j] <- sig_Pb[i] * sig_Pb[j] * ifelse(i == j, 1, rho_lPb)
+      Sig_Lphi_f_Pb[i,j] <- sig_Lphi_f_Pb[i] * sig_Lphi_f_Pb[j] * ifelse(i == j, 1, rho_Lphi_f_Pb)
       
       # covariance matrix of LH apportionment
       Sig_Lpi[i,j] <- sig_Lpi[i] * sig_Lpi[j] * ifelse(i == j, 1, rho_Lpi)
@@ -219,8 +219,8 @@ jags_model_code = function() {
   ### PRIORS: BROOD-YEAR-SPECIFIC PARAMETERS ###
   for (y in 2:ny) {
     
-    # parr recruitment
-    lPb[y,1:nj] ~ dmnorm.vcov(log(Pb_mean[y,1:nj]), Sig_lPb[1:nj,1:nj])
+    # egg to parr survival: Beverton-Holt relationship
[…]

### 2021-11-29 02-model/fit-model.R
Update model fitting script to run new BH parameterization

@@ -21,7 +21,7 @@ out_dir = "02-model/model-output"
 last_yr = 2019
 
 # specify a scenario name
-scenario = "base"
+scenario = "new-BH"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -98,7 +98,6 @@ jags_data = append(jags_data, add_jags_data)
 ### ADD ON QUANTITIES FOR FORWARD SIMULATION ###
 
 set.seed(1234) # for reproducibility; weir removals and hatchery inputs use sample() below
-
 last_obs_yr = max(as.numeric(rownames(jags_data$Pa_obs)))
 ny_sim = last_yr - last_obs_yr
 
@@ -198,8 +197,8 @@ toggle_rho_estimation("rho_Lphi_O0_O1")    # first year ocean survival
 
 jags_params = c(
   # reproduction
-  "alpha", "beta", "Sig_lPb", "mu_beta_per_wul", "sig_lbeta",
-  
+  "alpha", "beta", "Sig_Lphi_f_Pb", "phi_f_Pb", "mu_beta_per_wul", "sig_lbeta",
+
   # overwinter survival coefficients
   "gamma0", "gamma1",
   
@@ -242,7 +241,7 @@ jags_params = c(
   "Lpi_resid", "Lphi_Pa_Mb_resid", "Lphi_Mb_Ma_resid",
   "Lphi_Ma_O0_resid", "Lpsi_O1_Rb_resid",
   "Lpsi_O2_Rb_resid", "Lphi_O0_O1_resid", "Lphi_O1_O2_resid",
-  "Lphi_Sb_Sa_resid", "lPb_resid", "Lphi_Rb_Ra_resid",
+  "Lphi_Sb_Sa_resid", "Lphi_f_Pb_resid", "Lphi_Rb_Ra_resid",
   
   # AR(1) coefficients
   "kappa_phi_O0_O1",
@@ -315,7 +314,7 @@ cat("\nDecomposing all covariance matrices")
 
 # Convert the precision/covariance matrices monitored by JAGS into the marginal SD and correlation matrix terms
 suppressMessages({
[…]

### 2021-11-29 03-post-process/output-plots.Rmd
Update output plots Rmd to reflect new BH parameterization

@@
     label: "Scenario"
-    value: "base"
+    value: "new-BH"
     input: text
+  include_sim_years:
+    label: "Include Simulated Years on Plots?"
+    value: FALSE
+    input: checkbox
 editor_options: 
@@
 # the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
+all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
 
 # which years are "observable" for at least some quantities?
-observable = (jags_data$kmax+1):jags_data$ny
+observable = 2:jags_data$ny_obs
+
+# which years are simulated for at least some quantities?
+simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
+
+# which years should be included in time series plots?
+if (params$include_sim_years) {
+  ts_yrs = c(observable, simulated)
+} else {
+  ts_yrs = observable
+}
+
+# which years can be plotted for SARs? Drop off last kmax years
+# since brood year adult returns not complete
+sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
 
@@
 
+```{r make-diag-post, message = FALSE}
+# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
+# there is no point in calculating diagnostic summaries for future years
+if (length(simulated) > 0) {
+  diag_post = post_remove(post, paste0("[", simulated), ask = FALSE)
+} else {
+  diag_post = post
+}
+```
+
 ```{r mcmc-diag-function}
@@
   # extract the posteriors of interest and format for 'posterior' package
-  post_sub = as_draws_df(post_subset(post, params))
+  post_sub = as_draws_df(post_subset(diag_post, params))
 
@@
 # parr recruitment
-L1 = "Parr Recruitment"
-L2 = c("BH Productivity", "BH Capacity", "Process SD", "Among-pop Correlation", "Parr States")
-match = c("alpha", "^beta[", "sig_lPb", "rho_lPb", "^Pb[")
+L1 = "Egg-to-Parr Survival"
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
+match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_f_Pb", "rho_Lphi_f_Pb", "^phi_f_Pb[", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+
+# parr survival from summer to winter tagging
+L1 = "Survival From Summer to Winter"
+match = c("phi_Pb_Pa[2,.]")
+phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))
 
@@
 # Initial adult recruitment
-L1 = "Initial Adult Recruitment"
-L2 = c("Mean", "Realized")
-match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
-init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+L1 = "Initial Adult Returns"
+L2 = c("Age-3", "Age-4", "Age-5")
+match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
+init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))
 
@@
   pi_diags,
+  phi_Pb_Pa_diags,
   phi_Pa_Mb_diags,
@@
 
-# fall trap survival
+# fall & winter trap survival
 new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
@@
 bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
-bp = bp[,"fall-mig",]
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
+bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
+           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
+           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
+           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
 phi_Pa_Ma_bp = data.frame(
-  name = rep("Fall Trap to LGR", 4), pop = pops,
-  origin = rep("NOR", 4),   LH_type = rep("Fall Migrants", 4),
+  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
+  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
   summarize_bp(bp)
@@
 
+## Process Noise Diagnostics
+
+The model assumes mean-zero process noise for all components.
+That is, the model has an expected value for each component in a given year, and it estimates deviations from this expected value to obtain the realized value in that year.
+Deviations from the expectation are assumed to be equally likely to be positive or negative for any given year.
+We can average the process noise components across years to check if it is close to zero.
+Large deviations from zero in the table below indicate a problem.
+
+```{r get-resids-fn}
+# a function to extract the posterior mean of all process model residuals for a single population
+get_resids = function(post, j) {
+
+  out = list(
+    egg_to_parr_surv = post_summ(post, sub_index("^lPb_resid[.+,pop]", pop = j))["mean",],
+    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
+    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
+    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
+    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
+    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
+    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
+    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
+    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
+    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
+    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
+    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
+  )
+  out = do.call(cbind, out)
+  rownames(out) = NULL
+  out
+}
+```
+
+```{r make-mean-zero-resid-table}
+# extract posterior mean residual time series for each population
+resids = lapply(1:4, get_resids, post = diag_post)
+
+# convert to array format (list elements become matrix slices)
+resids = do.call(abind, append(resids, list(along = 3)))
+dimnames(resids)[[3]] = c("CAT", "LOS", "MIN", "UGR")
+
+# calculate the mean of each time series: these should be close to 0
+resid_means = t(sapply(1:dim(resids)[2], function(p) colMeans(resids[,p,])))
+rownames(resid_means) = dimnames(resids)[[2]]
+resid_means = round(resid_means, 3)
+
+# determine the phase of each process model component
+is_fw_juvn = rownames(resid_means) %in% c("egg_to_parr_surv", "p_fall_mig", "ow_surv_fall", "ow_surv_spring", "toLGR_surv_nor", "toLGR_surv_hor", "LGR_to_BON_surv_nor", "LGR_to_BON_surv_hor")
+is_sw_juvn = stringr::str_detect(rownames(resid_means), "ocean|mat")
+
+# determine the origin of each
+is_nor = stringr::str_detect(rownames(resid_means), "nor|egg_to_parr|p_fall|ow_surv")
+is_hor = stringr::str_detect(rownames(resid_means), "hor")
+
+# determine the process type: Life History (pi & psi) or Survival (phi)
+is_surv = stringr::str_detect(rownames(resid_means), "surv")
+
+# determine the migratory strategy: fall/spring/combined
+is_fall = stringr::str_detect(rownames(resid_means), "fall")
+is_spring = stringr::str_detect(rownames(resid_means), "spring")
+
+# build ID data frame
+resid_IDs = data.frame(
+  life_phase = ifelse(is_fw_juvn, "FW Juvenile", ifelse(is_sw_juvn, "SW Juvenile", "FW Adult")),
+  type = ifelse(is_surv, "Survival", "Life History"),
+  desc = c("Egg-to-Parr", "Strategy Apportionment", "Overwinter", "Overwinter", "Trib to LGR", "Trib to LGR",
+           "LGR to BON", "LGR to BON", "Yr1 Ocean", "Age-3 Maturity", "Age-3 Maturity", "Age-4 Maturity", "Age-4 Maturity",
+           "BON to LGR", "BON to LGR", "Pre-Spawn"),
+  origin = ifelse(is_nor, "NOR", ifelse(is_hor, "HOR", "Combined")), 
+  mig_type = ifelse(is_fall, "Fall Migrants", ifelse(is_spring, "Spring Migrants", "Combined"))
+)
+
+# combine IDs with mean residual values by population
+out = cbind(resid_IDs, resid_means)
+
+# build a kable
+kable(out, "html", row.names = FALSE, col.names = c("Life Phase", "Process Type", "Description", "Origin", "Migratory Strategy", colnames(resid_means))) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+  collapse_rows(1:5)
+```
+
 # Fit to Data
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
+  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
                get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
+               yrs = all_yrs[ts_yrs],
                main = pops[j])
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), 
+  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
                get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j])
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)),
+  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
                get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j])
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[.+,pop]", pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
                get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j])
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
                get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j])
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
 }
@@
 
+### Winter Parr $\rightarrow$ LGR
+
+```{r winter-surv-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
+               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
+```
+
 ### Spring Smolt $\rightarrow$ LGR (NOR)
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$",LH_type = i_spring, origin = o_nor, pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
                get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j])
+               main = pops[j], yrs = all_yrs[ts_yrs])
 }
@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]$", LH_type = i_spring, origin = o_hor, pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
                get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j])
+               main = pops[j], yrs = all_yrs[ts_yrs])
 }
@@
 par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_nor)),
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
              get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"))
+             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
+             yrs = all_yrs[ts_yrs])
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[.+,origin]$", origin = o_hor)),
+plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
              get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"))
+             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
+             yrs = all_yrs[ts_yrs])
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
@@
 par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
+plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
              get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
+             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
+             yrs = all_yrs[ts_yrs])
 mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
 par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
+plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
              get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
+             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
+             yrs = all_yrs[ts_yrs])
 mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
 # containers
-x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
+x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
+x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
 
@@
   par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
 
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
 
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"))
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
                get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1))
+               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
   par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
@@
   # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
   # extract posterior summaries of total egg production by brood year
-  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
+  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))
 
   # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))
+  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
 
@@
 
-  # fit ordinary least squares version
-  ols_fit = fit_fecund_BH(jags_data, pop = j)$BH_fit
-
-  # draw 1000 random parameters
-  ols_params = exp(rmvnorm(1000, coef(ols_fit), vcov(ols_fit)))
-
-  # calculate predicted curve at each pair/summarize
-  ols_R_pred = t(sapply(1:1000, function(i) BH(f_pred, ols_params[i,1], ols_params[i,2])))
-  ols_R_pred = apply(ols_R_pred, 2, function(x) quantile(x, c(0.5, 0.025, 0.975)))
-
   # graphical parameters
@@
   lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
-
-  # draw fitted relationship: OLS
-  polygon(c(f_pred, rev(f_pred)), c(ols_R_pred[2,], rev(ols_R_pred[3,])), col = alpha("grey", 0.5), border = NA)
-  lines(ols_R_pred[1,] ~ f_pred, lwd = 2)
-  lines(ols_R_pred[2,] ~ f_pred, lty = 2)
-  lines(ols_R_pred[3,] ~ f_pred, lty = 2)
   lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
@@
   # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
   # extract posterior summaries of total egg production by brood year
-  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
+  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))
 
@@
   # extract posterior summaries of total egg production by brood year
-  f_tot = post_summ(post, sub_index("^f_tot[.+,pop]", pop = j))
+  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))
 
   # conversion rates
-  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[.+,pop]", pop = j))
+  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[year,pop]", pop = j, year = ts_yrs))
 
@@
   # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[.+,pop]", pop = j))
+  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
   # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[.+,pop]", pop = j))
+  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
@@
 
+# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
+
+## Scatterplot
+
+Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
+
+```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
+# extract posterior summaries of the capacity parameters
+beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
+
+# extract posterior samples of the slope parameter
+beta_per = post_subset(post, "mu_beta_per_wul", TRUE)
+
+# create a sequence of WUL values to predict capacity at
+wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
+
+# obtain the regression line for each posterior sample
+pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
+
+# select a subset of posterior samples at random to draw
+i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
+
+# empty plot with correct labeling/dimensions
+par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
+plot(1,1, type = "n", xlim = range(wul_seq),
+     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
+     xlab = "Weighted Usable Length (km)",
+     ylab = "Parr Capacity (000s)", yaxt = "n")
+at_y = axisTicks(par("usr")[3:4], log = FALSE)
+axis(side = 2, at = at_y, labels = at_y/1000)
+
+# draw the random regression lines
+junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
+
+# draw the posterior mean regression line
+lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
+
+# draw the population-specific capacity estimates w/error bars and labels
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
+text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
+```
+
+## Slope Parameter
+
+```{r beta-v-habitat-slope}
+# extract posterior summary of slope
+est = post_summ(post, "mu_beta_per_wul")
+colnames(est) = "slope"
+
+# print a table 
+kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
+```
+
+# Migratory Strategy Apportionment
+
+```{r pi-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
+```
+
 # Overwinter Survival Relationships
@@
   # extract parr, scale it to WUL, and create new post object
-  Pa = post_subset(post, sub_index("^Pa[.+,.,pop]", pop = j), matrix = TRUE)
+  Pa = post_subset(post, sub_index("^Pa[year,.,pop]", pop = j, year = ts_yrs), matrix = TRUE)
   Pa_scaled = Pa/jags_data$wul[j]
@@
   # extract/format posterior summaries of realized survivals
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["mean",])
-  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["2.5%",])
-  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[.+,.+,pop]", pop = j))["97.5%",])
+  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["mean",])
+  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["2.5%",])
+  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["97.5%",])
 
@@
 ```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]
-
 plot_fn = function(j) {
   # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
+  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
 
   # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[.+,origin,pop]", origin = o_hor, pop = j)) * 100
+  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
+  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
 
@@
   # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, 10))
+  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
 
   # add hatchery origin time series
-  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)
+  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
+  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
+  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
+  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
 
@@
 ```{r bon-to-bon, fig.width = 6, fig.height = 5}
-sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]
-
 plot_fn = function(j) {
   # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = c(6:29), LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
+  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
 
   # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))
+  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
+  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
 
   # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])
+  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
 
@@
   # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))
+  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
 
   # add hatchery origin time series
-  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)
+  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
+  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
+  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
+  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
 
@@
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
 }
@@
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
 }
@@
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
+mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
 ```
@@
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[.+,pop]", pop = j)), yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
  abline(h = 1, lty = 2)
@@
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[.+,pop]", pop = j)), yrs = as.numeric(rownames(jags_data$Pa_obs[,,j])[observable]), main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
 }
@@
   par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
+               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
+               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
+               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
+               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
+               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
+               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
   mtext(side = 1, outer = T, line = 0.5, "Brood Year")
@@
   par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[observable], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[.+,origin,pop]$", origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[observable], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
 
@@
 my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_lPb[.]$", "Process SD")
-my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
+my_boxplot("^sig_Lphi_f_Pb[.]$", "Process SD")
+my_boxplot("^rho_Lphi_f_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
 ```

### 2021-12-02 03-post-process/output-plots.Rmd

--- 2021-11-24 03-post-process/output-plots.Rmd
@@
 
+## Process Noise Diagnostics
+
+The model assumes mean-zero process noise for all components.
+That is, the model has an expected value for each component in a given year, and it estimates deviations from this expected value to obtain the realized value in that year.
+Deviations from the expectation are assumed to be equally likely to be positive or negative for any given year.
+We can average the process noise components across years to check if it is close to zero.
+Large deviations from zero in the table below indicate a problem.
+
+```{r get-resids-fn}
+# a function to extract the posterior mean of all process model residuals for a single population
+get_resids = function(post, j) {
+
+  out = list(
+    egg_to_parr_surv = post_summ(post, sub_index("^lPb_resid[.+,pop]", pop = j))["mean",],
+    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
+    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
+    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
+    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
+    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
+    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
+    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
+    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
+    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
+    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
+    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
+  )
+  out = do.call(cbind, out)
+  rownames(out) = NULL
+  out
+}
+```
+
+```{r make-mean-zero-resid-table}
+# extract posterior mean residual time series for each population
+resids = lapply(1:4, get_resids, post = post)
+
+# convert to array format (list elements become matrix slices)
+resids = do.call(abind, append(resids, list(along = 3)))
+dimnames(resids)[[3]] = c("CAT", "LOS", "MIN", "UGR")
+
+# calculate the mean of each time series: these should be close to 0
+resid_means = t(sapply(1:dim(resids)[2], function(p) colMeans(resids[,p,])))
+rownames(resid_means) = dimnames(resids)[[2]]
+resid_means = round(resid_means, 3)
+
+# determine the phase of each process model component
+is_fw_juvn = rownames(resid_means) %in% c("egg_to_parr_surv", "p_fall_mig", "ow_surv_fall", "ow_surv_spring", "toLGR_surv_nor", "toLGR_surv_hor", "LGR_to_BON_surv_nor", "LGR_to_BON_surv_hor")
+is_sw_juvn = stringr::str_detect(rownames(resid_means), "ocean|mat")
+
+# determine the origin of each
+is_nor = stringr::str_detect(rownames(resid_means), "nor|egg_to_parr|p_fall|ow_surv")
+is_hor = stringr::str_detect(rownames(resid_means), "hor")
+
+# determine the process type: Life History (pi & psi) or Survival (phi)
+is_surv = stringr::str_detect(rownames(resid_means), "surv")
+
+# determine the migratory strategy: fall/spring/combined
+is_fall = stringr::str_detect(rownames(resid_means), "fall")
+is_spring = stringr::str_detect(rownames(resid_means), "spring")
+
+# build ID data frame
+resid_IDs = data.frame(
+  life_phase = ifelse(is_fw_juvn, "FW Juvenile", ifelse(is_sw_juvn, "SW Juvenile", "FW Adult")),
+  type = ifelse(is_surv, "Survival", "Life History"),
+  desc = c("Egg-to-Parr", "Strategy Apportionment", "Overwinter", "Overwinter", "Trib to LGR", "Trib to LGR",
+           "LGR to BON", "LGR to BON", "Yr1 Ocean", "Age-3 Maturity", "Age-3 Maturity", "Age-4 Maturity", "Age-4 Maturity",
+           "BON to LGR", "BON to LGR", "Pre-Spawn"),
+  origin = ifelse(is_nor, "NOR", ifelse(is_hor, "HOR", "Combined")), 
+  mig_type = ifelse(is_fall, "Fall Migrants", ifelse(is_spring, "Spring Migrants", "Combined"))
+)
+
+# combine IDs with mean residual values by population
+out = cbind(resid_IDs, resid_means)
+
+# build a kable
+kable(out, "html", row.names = FALSE, col.names = c("Life Phase", "Process Type", "Description", "Origin", "Migratory Strategy", colnames(resid_means))) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+  collapse_rows(1:5)
+```
+
 # Fit to Data

### 2021-12-07 03-post-process/output-plots.Rmd
Add Bayesian p-value calculations for winter tagging data

--- 2021-11-29 03-post-process/output-plots.Rmd
@@
     label: "Scenario"
-    value: "new-BH"
+    value: "base"
     input: text
@@
 # which years are "observable" for at least some quantities?
-observable = 2:jags_data$ny_obs
+observable = (jags_data$kmax+1):jags_data$ny_obs
 
@@
 # parr recruitment
-L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
-match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_f_Pb", "rho_Lphi_f_Pb", "^phi_f_Pb[", "^Pb[")
+L1 = "Parr Recruitment"
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
+match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
-
-# parr survival from summer to winter tagging
-L1 = "Survival From Summer to Winter"
-match = c("phi_Pb_Pa[2,.]")
-phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))
 
@@
 # Initial adult recruitment
-L1 = "Initial Adult Returns"
-L2 = c("Age-3", "Age-4", "Age-5")
-match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))
+L1 = "Initial Adult Recruitment"
+L2 = c("Mean", "Realized")
+match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
+init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
   pi_diags,
-  phi_Pb_Pa_diags,
   phi_Pa_Mb_diags,
@@
 # extract posterior mean residual time series for each population
-resids = lapply(1:4, get_resids, post = diag_post)
+resids = lapply(1:4, get_resids, post = post)
 
@@
 
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
 ### Spring Smolt $\rightarrow$ LGR (NOR)
@@
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
 ```
@@
 my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Lphi_f_Pb[.]$", "Process SD")
-my_boxplot("^rho_Lphi_f_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
+my_boxplot("^sig_lPb[.]$", "Process SD")
+my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
 ```

### 2021-12-09 02-model/fit-model.R
Update model fit script for new model

@@ -16,6 +16,10 @@ invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names
 # set the output directory: if it doesn't exist, a new directory will be created
 out_dir = "02-model/model-output"
 
+# specify the last year of model calculations
+# make later than 2019 to include simulated outcomes
+last_yr = 2019
+
 # specify a scenario name
 scenario = "base"
 
@@ -32,7 +36,7 @@ if (is.na(rmd)) {
 }
 
 if (is.na(mcmc_length)) {
-  mcmc_length = "short"
+  mcmc_length = "very_short"
   cat("\n\n'mcmc_length' was not supplied as a command line argument.", mcmc_length, "will be used.")
 }
 
@@ -98,8 +102,6 @@ jags_data = append(jags_data, add_jags_data)
 
 set.seed(1234) # for reproducibility; weir removals and hatchery inputs use sample() below
 
-# specify the last year of model calculations
-last_yr = 2050
 last_obs_yr = max(as.numeric(rownames(jags_data$Pa_obs)))
 ny_sim = last_yr - last_obs_yr
 
@@ -199,7 +201,7 @@ toggle_rho_estimation("rho_Lphi_O0_O1")    # first year ocean survival
 
 jags_params = c(
   # reproduction
-  "alpha", "beta", "Sig_lPb",
+  "alpha", "beta", "Sig_lPb", "mu_beta_per_wul", "sig_lbeta",
   
   # overwinter survival coefficients
   "gamma0", "gamma1",

### 2021-12-09 03-post-process/output-plots.Rmd
Include new parameters in MCMC diagnostics

--- 2021-12-02 03-post-process/output-plots.Rmd
@@
 L1 = "Parr Recruitment"
-L2 = c("BH Productivity", "BH Capacity", "Process SD", "Among-pop Correlation", "Parr States")
-match = c("alpha", "^beta[", "sig_lPb", "rho_lPb", "^Pb[")
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
+match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

### 2021-12-09 03-post-process/output-plots.Rmd
Add summary output for habitat capacity relationship to RMD

@@
 
+# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
+
+## Scatterplot
+
+Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
+
+```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
+# extract posterior summaries of the capacity parameters
+beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
+
+# extract posterior samples of the slope parameter
+beta_per = post_subset(post, "mu_beta_per_wul", TRUE)
+
+# create a sequence of WUL values to predict capacity at
+wul_seq = seq(0, max(jags_data$wul) * 1.05, length = 30)
+
+# obtain the regression line for each posterior sample
+pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
+
+# select a subset of posterior samples at random to draw
+i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
+
+# empty plot with correct labeling/dimensions
+par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
+plot(1,1, type = "n", xlim = range(wul_seq),
+     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
+     xlab = "Weighted Usable Length (km)",
+     ylab = "Parr Capacity (000s)", yaxt = "n")
+at_y = axisTicks(par("usr")[3:4], log = FALSE)
+axis(side = 2, at = at_y, labels = at_y/1000)
+
+# draw the random regression lines
+junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
+
+# draw the posterior mean regression line
+lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
+
+# draw the population-specific capacity estimates w/error bars and labels
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
+text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
+```
+
+## Slope Parameter
+
+```{r}
+# extract posterior summary of slope
+est = post_summ(post, "mu_beta_per_wul")
+colnames(est) = "slope"
+
+# print a table 
+kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
+```
+
 # Overwinter Survival Relationships

### 2021-12-10 03-post-process/compare-sim-to-obs.Rmd
correct small issues in compare-sim-to-obs RMD

@@
 ```{r select-years}
+# all of the years included in the model
 all_yrs = as.numeric(rownames(jags_data$phi_SL))
+
+# which is the first year of observation period?
+# may want to use 2001 to cut off years without hatchery supplementation
 fy_obs = which(all_yrs == 2001)
@@
 out = NULL
-for (i in 1:nrow(Ra)) {
+for (i in 1:nrow(Rb)) {
   Rb_i = array_format(Rb[i,])
@@
 out_hor = NULL
-for (i in 1:nrow(Ra)) {
+for (i in 1:nrow(Ma)) {
   Ma_i = array_format(Ma[i,])
   nor = Ma_i[,1,1,] + Ma_i[,2,1,]
-  hor = Ma_i[,1,2,] + Ma_i[,2,2,]
+  hor = Ma_i[,2,2,]
   out_nor = rbind(out_nor, as.numeric(nor))

### 2021-12-11 03-post-process/output-plots.Rmd
Set up better handling of which years to plot in output RMD
An additional parameter is included that allows user to toggle on/off the inclusion of simulated years in all plots

@@
     input: text
+  include_sim_years:
+    label: "Include Simulated Years on Plots?"
+    value: FALSE
+    input: checkbox
 editor_options: 
@@
 # the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])
+all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
 
 # which years are "observable" for at least some quantities?
-observable = (jags_data$kmax+1):jags_data$ny
+observable = (jags_data$kmax+1):jags_data$ny_obs
+
+# which years are simulated for at least some quantities?
+simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
+
+# which years should be included in time series plots?
+if (params$include_sim_years) {
+  ts_yrs = c(observable, simulated)
+} else {
+  ts_yrs = observable
+}
+
+# which years can be plotted for SARs? Drop off last kmax years
+# since brood year adult returns not complete
+sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
 

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include calculation of aggregate quantities in sim vs. obs RMD

@@
 title: "Observed vs. Simulated Year Comparison"
-subtitle: "`r paste0('Model Scenario:', params$scenario)`"
+subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
 output: html_document
@@
 
+```
+
+```{r add-nor-lgr-smolt-aggregate}
+# extract smolt at LGR
+Ma = post_subset(post, "^Ma[", matrix = TRUE)
+
+# for each posterior sample, calculate the total aggregate return
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ma)) {
+  Ma_i = array_format(Ma[i,])
+  nor = Ma_i[,1,1,] + Ra_i[,2,1,]
+  hor = Ra_i[,2,2,]
+
+  out_nor = rbind(out_nor, rowSums(nor))
+  out_hor = rbind(out_hor, rowSums(hor))
+}
+
+# build the indices for each element: the year
+r_ind = 1:nrow(nor)
+
+# make element names
+colnames(out_nor) = paste0("Ma_aggregate[", r_ind, ",", "1", "]")
+colnames(out_hor) = paste0("Ma_aggregate[", r_ind, ",", "2", "]")
+out = cbind(out_nor, out_hor)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-Ra-aggregate}
+# extract spawners returning to tributary
+Ra = post_subset(post, "^Ra[", matrix = TRUE)
+
+# for each posterior sample, calculate the total aggregate return
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ra)) {
+  Ra_i = array_format(Ra[i,])
+  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
+  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
+  tot = nor + hor
+
+  out_nor = rbind(out_nor, rowSums(nor))
+  out_hor = rbind(out_hor, rowSums(hor))
+}
+
+# build the indices for each element: the year
+r_ind = 1:nrow(nor)
+
+# make element names
+colnames(out_nor) = paste0("Ra_aggregate[", r_ind, ",", "1", "]")
+colnames(out_hor) = paste0("Ra_aggregate[", r_ind, ",", "2", "]")
+out = cbind(out_nor, out_hor)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
 ```

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include plots for aggregate quantities in sim vs. obs RMD

@@
 ratio_plots(x, "Total LGR Smolt: Ratios")
+#### Aggregate Total Adult Return (To Tributary)
+
+```{r}
+x = append(
+  list(get_ratio("Ra_aggregate[year,origin]", obs_y, sim_y, origin = 1)),
+  list(get_ratio("Ra_aggregate[year,origin]", obs_y, sim_y, origin = 2))
+)
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Aggregate Total Adult Return (To Tributary): Estimates")
+ratio_plots(x, "Aggregate Total Adult Return (To Tributary): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Aggregate Total Adult Return (To Tributary)"))
+```
+
+#### Aggregate Total Smolt (At LGR)
+
+```{r}
+x = append(
+  list(get_ratio("Ma_aggregate[year,origin]", obs_y, sim_y, origin = 1)),
+  list(get_ratio("Ma_aggregate[year,origin]", obs_y, sim_y, origin = 2))
+)
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Aggregate Total Smolt (At LGR): Estimates")
+ratio_plots(x, "Aggregate Total Smolt (At LGR): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Aggregate Total Smolt (At LGR)"))
 ```
@@
 
+#### Aggregate Total Adult Return (To Tributary) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r, fig.width = 7, fig.height = 4}
+ts_plot("Ra_aggregate[year,origin]", origin = 1)
+```
+
+##### HOR
+
+```{r, fig.width = 7, fig.height = 4}
+ts_plot("Ra_aggregate[year,origin]", origin = 2)
+```
+
+#### Aggregate Total Smolt (At LGR) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r, fig.width = 7, fig.height = 4}
+ts_plot("Ma_aggregate[year,origin]", origin = 1)
+```
+
+##### HOR
+
+```{r, fig.width = 7, fig.height = 4}
+ts_plot("Ma_aggregate[year,origin]", origin = 2)
+```
+
 ### SAR Rates {.tabset .tabset-pills}

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include functions create tables summarizing sim vs. obs ratios

@@
 
+```{r summarize_ratios fn}
+summarize_ratios = function(x, Class, Type) {
+  xsumm = as.data.frame(t(apply(x[,"sim-v-obs",,], 3, colMeans)))
+  xsumm = cbind(Class = Class, Type = Type, ID = rownames(xsumm), xsumm); rownames(xsumm) = NULL
+  return(xsumm)
+}
+```
+
+```{r assign_color fns}
+# functions to assign a color based on a numeric value
+
+# values close to 1 will be closer to white; values closer to 0 will be blue; values closer to 2 will be red
+assign_color_1 = function(x) {
+  red_pal = colorRampPalette(c("white", "red"))
+  blue_pal = colorRampPalette(c("blue", "white"))
+  red_cols = red_pal(5)
+  blue_cols = blue_pal(5)
+  cols = c(blue_cols, red_cols)
+
+  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 3)
+  bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
+  names(cols) = c(bin_names[1:5], bin_names[5:9])
+  bins = cut(x, breaks = breaks, include.lowest = TRUE)
+  cols_use = cols[as.character(bins)]
+  cols_use[is.na(cols_use)] = cols[5]
+  alpha(unname(cols_use), 0.5)
+}
+
+# values close to 0 will be closer to white; values closer to -1 will be blue; values closer to 1 will be red
+assign_color_0 = function(x) {
+  red_pal = colorRampPalette(c("white", "red"))
+  blue_pal = colorRampPalette(c("blue", "white"))
+  red_cols = red_pal(5)
+  blue_cols = blue_pal(5)
+  cols = c(blue_cols, red_cols)
+
+  breaks = c(-1, -0.75, -0.5, -0.25, -0.1, 0.1, 0.25, 0.5, 0.75, 1)
+  bin_names = levels(cut(runif(1e6, -1, 1), breaks = breaks, include.lowest = TRUE))
+  names(cols) = c(bin_names[1:5], bin_names[5:9])
+  bins = cut(x, breaks = breaks, include.lowest = TRUE)
+  cols_use = cols[as.character(bins)]
+  cols_use[is.na(cols_use)] = cols[5]
+  alpha(unname(cols_use), 0.5)
+}
+```
+
+```{r prep_est_ratios fn}
+# function to prepare ratios for table-making
+prep_est_ratios = function(x, q) {
+  # add/format additional column IDs
+  x$origin = stringr::str_extract(x$ID, "NOR|HOR")
+  x$pop = stringr::str_extract(x$ID, "CAT|LOS|MIN|UGR")
+  x$LH_type = stringr::str_extract(x$ID, "fall|spring")
+  x$LH_type[x$LH_type == "spring"] = "Spring"
+  x$LH_type[x$LH_type == "fall"] = "Fall"
+  x$pop = ifelse(is.na(x$pop), "Combined", x$pop)
+  x$origin = ifelse(is.na(x$origin), "Combined", x$origin)
+  x$LH_type = ifelse(is.na(x$LH_type), "Combined", x$LH_type)
+
+  # make populations separate columns
+  x = dcast(x, Class + Type + origin + LH_type ~ pop, value.var = q)
+
+  # reorder columns
+  x = x[,c("Class", "Type", "LH_type", "origin", "CAT", "LOS", "MIN", "UGR", "Combined")]
+
+  # reorder rows
+  x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
+  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Proportion Fall Migrants", "Overwinter Survival", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
+  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
+  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
+  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]
+
+  colnames(x)[which(colnames(x) == "LH_type")] = "Mig. Type"
+  colnames(x)[which(colnames(x) == "Origin")] = "Origin"
+
+  return(x)
+}
+```
+
+```{r prep_derived_ratios fn}
+# function to prepare ratios for table-making
+prep_derived_ratios = function(x, q) {
+  # add/format additional column IDs
+  x$origin = stringr::str_extract(x$ID, "NOR|HOR")
+  x$pop = stringr::str_extract(x$ID, "CAT|LOS|MIN|UGR")
+  x$LH_type = stringr::str_extract(x$ID, "fall|spring")
+  x$LH_type[x$LH_type == "spring"] = "Spring"
+  x$LH_type[x$LH_type == "fall"] = "Fall"
+  x$pop = ifelse(is.na(x$pop), "Combined", x$pop)
+  x$origin = ifelse(is.na(x$origin), "Combined", x$origin)
+  x$LH_type = ifelse(is.na(x$LH_type), "Combined", x$LH_type)
+
+  # make populations separate columns
+  x = dcast(x, Class + Type + origin + LH_type ~ pop, value.var = q)
+
+  # reorder columns
+  x = x[,c("Class", "Type", "LH_type", "origin", "CAT", "LOS", "MIN", "UGR", "Combined")]
+
+  # reorder rows
+  x$Class = factor(x$Class, levels = c("Abundance", "Production Rates", "SAR", "Adult Composition"))
+  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
+  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
+  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
+  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]
+
+  colnames(x)[which(colnames(x) == "LH_type")] = "Mig. Type"
+  colnames(x)[which(colnames(x) == "Origin")] = "Origin"
+
+  return(x)
+}
+```
+
+```{r make_ratios_table fn}
+# function to make the table
+make_ratios_table = function(ratios, q) {
+
+  x = ratios
+  table_x = x
+  table_x[,5:9] = round(table_x[,5:9],2)
+  table_x[is.na(table_x)] = ""
+
+  # select the correct color rule
+  if (q %in% c("mean", "cv")) {
+    assign_color = assign_color_1
+  } else {
+    assign_color = assign_color_0
+  }
+
+  kable(table_x, "html", digits = 2, row.names = FALSE, align = "llllccccc") %>%
+    kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    column_spec(5, background = assign_color(x[,5])) %>%
+    column_spec(6, background = assign_color(x[,6])) %>%
+    column_spec(7, background = assign_color(x[,7])) %>%
+    column_spec(8, background = assign_color(x[,8])) %>%
+    column_spec(9, background = assign_color(x[,9])) %>%
+    collapse_rows(1:4)
+}
+```
+
 For us to use the state-space model as a simulation model, it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Store the ratio summaries for all estimated quantities

@@
 
+```{r}
+est_ratios = NULL
+```
+
 ## Time Series Parameters {.tabset .tabset-pills}
@@
 ratio_plots(x, "Egg to Parr Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Egg to Parr Survival"))
 ```
@@
 ratio_plots(x, "Proportion Fall Migrants: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Proportion Fall Migrants"))
 ```
@@
 ratio_plots(x, "Overwinter Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Overwinter Survival"))
 ```
@@
 ratio_plots(x, "Migration to LGR Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Migration to LGR Survival"))
 ```
@@
 ratio_plots(x, "LGR to Ocean Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "LGR to Ocean Survival"))
 ```
@@
 ratio_plots(x, "First Year Ocean Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "First Year Ocean Survival"))
 ```
@@
 ratio_plots(x, "Age-3 Maturity: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-3 Maturity"))
 ```
@@
 ratio_plots(x, "Age-4 Maturity: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-4 Maturity"))
 ```
@@
 ratio_plots(x, "BON to LGR Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "BON to LGR Survival"))
 ```
@@
 ratio_plots(x, "Pre-Spawn Survival: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "Pre-Spawn Survival"))
 ```

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Store the ratios for all derived quantities

@@
 This document is intended to identify whether simulated outcomes are similar to observed outcomes.
-It looks at two primary types of quantities: stochastic time series parameters (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes (e.g., total adult return abundance, BON to BON SAR rates, etc.).
+It looks at two primary types of quantities: stochastic time series parameters that are directly estimated by the model (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes calculated as derived quantities from stochastic parameters (e.g., total adult return abundance, BON to BON SAR rates, etc.).
 Because all emergent outcomes are derived from the stochastic elements, issues with emergent outcomes should be traceable to specific stochastic parents.
 
-The JAGS model was altered to carry out the life cycle processes through brood year 2050.
+The JAGS model was altered to carry out the life cycle processes through brood year `r max(all_yrs)`.
 This means for each posterior sample we have an observed and simulated time series.
-The simulated time series picks up where the observed on left off, and assumes the same random processes for all components as used in the observed time series.
-Several quantities are supplied to the model as known without error (weir removals, hatchery smolt releases, harvest rates below BON, etc.).
+The simulated time series picks up where the observed one left off, and assumes the same random processes for all components as used in the observed time series.
+
+Several quantities are supplied to the model as known without error in the observed time series (weir removals, hatchery smolt releases, harvest rates below BON, etc.).
 These time series were extended to the future years external to the model using basic averages or resampling from historical outcomes as appropriate.
@@
 
+```{r}
+derived_ratios = NULL
+```
+
 ### Abundance Quantities {.tabset .tabset-pills}
@@
 ratio_plots(x, "Total Adults (Estuary): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (Estuary)"))
 ```
@@
 ratio_plots(x, "Total Adults (Tributary): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (To Tributary)"))
 ```
@@
 ratio_plots(x, "Total Spawners: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Spawners"))
 ```
@@
 ratio_plots(x, "Total Egg Production: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
 ```
@@
 ratio_plots(x, "Total Parr Recruitment: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Parr Recruitment"))
 ```
@@
 ratio_plots(x, "Total LGR Smolt: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total LGR Smolt"))
+```
+
 #### Aggregate Total Adult Return (To Tributary)
@@
 ratio_plots(x, "BON to BON SAR: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "SAR", Type = "BON to BON"))
 ```
@@
 ratio_plots(x, "LGR to LGR SAR: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "SAR", Type = "LGR to LGR"))
 ```
@@
 ratio_plots(x, "Parr per Spawner: Ratios")
-```
-
-#### Smolt per Spawner
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Parr per Spawner"))
+```
+
+#### Smolt in Tributary per Spawner
 
@@
 ratio_plots(x, "Smolt per Spawner: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Smolt in Tributary per Spawner"))
 ```
@@
 ratio_plots(x, "Smolt in Tributary per Parr: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Smolt in Tributary per Parr"))
 ```
@@
 ratio_plots(x, "Smolt at LGR per Parr: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Smolt at LGR per Parr"))
 ```
@@
 ratio_plots(x, "Spawners per Spawner: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Spawners per Spawner"))
 ```
@@
 ratio_plots(x, "Proportion Hatchery Return: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return"))
 ```
@@
 ratio_plots(x, "Proportion Age-3 Return: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-3 Return"))
 ```
@@
 ratio_plots(x, "Proportion Age-4 Return: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-4 Return"))
 ```
@@
 ratio_plots(x, "Proportion Age-5 Return: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
+```
 ```

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include sim vs. obs ratio summary tables in RMD

@@
 ```
+
+## Summary Tables {.tabset .tabset-pills}
+
+These tables summarize the mean ratio values shown in the plots above, and are intended to be a quick visual for identifying areas where the simulated outcomes are systematically different in some way (central tendency, interannual variability, or temporal autocorrelation) from the observed outcomes.
+The number in each cell represents the posterior mean value of:
+
+* **Across Year Mean** is the ratio `mean(simulated years)/mean(observed years)`. Values greater than 1 indicate the value in simulated years is larger in magnitude than in observed years.
+* **Across Year CV** is the ratio `cv(simulated years)/cv(observed years)`. Values greater than 1 indicate the variability from one year to the next is larger larger than in observed years.
+* **Lag-1 Autocorrelation** is the difference `acf(simulated years) - acf(observed years)`.
+Values greater than 0 indicate the quantity shows more autocorrelation in the simulated years than in observed years.
+
+Values close to 1 are ideal for the mean and CV ratios and cells are color-coded based on how far they fall from 1: less than 1 are blue and greater than 1 are red; values between 0.9 and 1.1 might be considered "good enough", and have been assigned no color.
+
+Values close to 0 are ideal for the autocorrelation differences and cells are color-coded based on how far they fall from zero: less than zero are blue and greater than zero are red; values between -0.1 and 0.1 might be considered "good enough", and have been assigned no color.
+
+### Estimated Quantities {.tabset .tabset-pills}
+
+#### Across Year Mean
+
+```{r est-mean-table}
+make_ratios_table(prep_est_ratios(est_ratios, "mean"), "mean")
+```
+
+#### Across Year CV
+
+```{r est-cv-table}
+make_ratios_table(prep_est_ratios(est_ratios, "cv"), "cv")
+```
+
+#### Lag-1 Autocorrelation
+
+```{r est-acf-table}
+make_ratios_table(prep_est_ratios(est_ratios, "acf"), "acf")
+```
+
+### Derived Quantities {.tabset .tabset-pills}
+
+#### Across Year Mean
+
+```{r derived-mean-table}
+make_ratios_table(prep_derived_ratios(derived_ratios, "mean"), "mean")
+```
+
+#### Across Year CV
+
+```{r derived-cv-table}
+make_ratios_table(prep_derived_ratios(derived_ratios, "cv"), "cv")
+```
+
+#### Lag-1 Autocorrelation
+
+```{r derived-acf-table}
+make_ratios_table(prep_derived_ratios(derived_ratios, "acf"), "acf")
 ```
@@
 
-ts_plot = function(param, main, obs_y_use = obs_y, sim_y_use = sim_y, ...) {
+ts_plot = function(param, main = NULL, obs_y_use = obs_y, sim_y_use = sim_y, ...) {
 

### 2021-12-11 03-post-process/output-plots.Rmd

@@
 # create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.05, length = 30)
+wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
 
@@
 
-```{r}
+```{r beta-v-habitat-slope}
 # extract posterior summary of slope

### 2021-12-16 02-model/fit-model.R
Add phi_Pb_Pa term
Represents survival between summer tagging and winter tagging for parr that become spring migrants

@@ -236,7 +236,7 @@ jags_params = c(
   "z", "carc_adj", "n_stray_tot", "stray_comp", "mu_z", "sig_z",
   
   # misc parameters
-  "O_phi_scaler_nat_hat", "toLGR_scaler",
+  "O_phi_scaler_nat_hat", "phi_Pb_Pa", "bad_flag",
   
   # misc derived quantities
   "beta_per_wul", "Pb_per_Sa_tot", "Pb_per_f_tot", "Mb_per_Sa_tot", "Sa_tot_per_Sa_tot", "Ra_per_Ma", "phi_O0_Rb_BON",

### 2021-12-16 02-model/model-code.R

@@ -101,6 +101,14 @@ jags_model_code = function() {
     }
   }
   
+  # survival between summer tagging/LH apportionment and winter tagging for spring migrants
+  # parameter is needed to allow inclusion of winter tagging data, this is not a key pop dyn parameter
+  phi_Pb_Pa[i_fall,1:nj] <- rep(1, nj)  # doesn't apply to fall migrants, but loops over i dimension
+  phi_Pb_Pa[i_spring,1] ~ dunif(0, 1)
+  phi_Pb_Pa[i_spring,2] ~ dunif(0, 1)
+  phi_Pb_Pa[i_spring,3] <- 1            # don't estimate for MIN -- no winter tagging data
+  phi_Pb_Pa[i_spring,4] ~ dunif(0, 1)
+  
   ### PRIORS: PARAMETERS THAT ARE CONSTANT ACROSS POPULATIONS ###
   
   # juvenile movement survival (LGR to estuary [ocean-age 0]): same for both LH types, different for origin types
@@ -361,8 +369,13 @@ jags_model_code = function() {
         Ma[y,i,o_nat,j] <- Mb[y,i,o_nat,j] * phi_Mb_Ma[y,i,o_nat,j]
         
         # derived survival for fitting: fall trap to LGD
-        phi_Pa_Ma[y,i,j] <- Ma[y,i,o_nat,j]/Pa[y,i,j]
+        phi_Pa_Ma[y,i,j] <- Ma[y,i,o_nat,j]/max(Pa[y,i,j] * phi_Pb_Pa[i,j], Ma[y,i,o_nat,j])
       }
+      
+      # flag that tells us how often max constraint is violated
+      # will remove this eventually. the max constraint is needed for MCMC during early tuning (crashes w/o it)
+      # but none of the converged samples have this occur
+      bad_flag[y,j] <- ifelse(Pa[y,i_spring,j] * phi_Pb_Pa[i_spring,j] < Ma[y,i_spring,o_nat,j], 1, 0)
       
       # derived survival for fitting: summer tagging to LGD
       phi_Pb_Ma[y,j] <- sum(Ma[y,1:ni,o_nat,j])/Pb[y,j]

### 2021-12-16 03-post-process/output-plots.Rmd
Add diagnostics for new survival parameter

@@
 
+# parr survival from summer to winter tagging
+L1 = "Survival From Summer to Winter"
+match = c("phi_Pb_Pa[2,.]")
+phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))
+
 # Overwinter survival
@@
   pi_diags,
+  phi_Pb_Pa_diags
   phi_Pa_Mb_diags,

### 2021-12-16 02-model/fit-model.R
Update model scenario name: base

@@ -21,7 +21,7 @@ out_dir = "02-model/model-output"
 last_yr = 2019
 
 # specify a scenario name
-scenario = "winter-surv-data"
+scenario = "base"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE

### 2021-12-17 02-model/fit-model.R
Update model fitting script

@@ -48,8 +48,8 @@ jags_data = append_no_na_indices(jags_data)
 
 # some parameters we are assuming known (for now)
 # harvest rates Below and Above BON by year, age, origin
-Ub_45_nat = with(jags_data, c(rep(NA, kmax), rep(0.02, ny - kmax)))
-Ub_45_hat = with(jags_data, c(rep(NA, kmax), rep(0.08, ny - kmax)))
+Ub_45_nat = with(jags_data, c(NA, rep(0.02, ny - 1)))
+Ub_45_hat = with(jags_data, c(NA, rep(0.08, ny - 1)))
 Ub = abind(list(cbind(Ub_45_nat * 0.25, Ub_45_nat, Ub_45_nat), cbind(Ub_45_hat * 0.75, Ub_45_hat, Ub_45_hat)), along = 3)
 dimnames(Ub) = with(jags_data, list(rownames(Ra_obs), kmin:kmax, c("Nat", "Hat")))
 
@@ -67,10 +67,6 @@ add_jags_data = list(
   f = c(1904, 3971, 4846),  # fecundity [female age]
   p_female = p_female       # proportion of spawners by age and population that are female
 )
-
-# calculate a metric for overall survival from estuary to tributary
-# used in obtaining an upper bound for initial adult recruits
-overall_phi_Rb_Ra = with(append(jags_data, add_jags_data), mean(phi_SL, na.rm = T) * mean(LGR_adults[,"Nat"]/BON_adults[,"Nat"], na.rm = TRUE))
 
 # some dummy variables for performing weir vs. carcass composition correction
 add_jags_data2 = list(
@@ -90,10 +86,11 @@ add_jags_data3 = list(
 )
 add_jags_data = append(add_jags_data, add_jags_data3)
 
-# calculate the upper bound on initial adult recruits and add to data
-p_NOR = apply(jags_data$carc_x_obs, 3, function(y) {rowSums(t(apply(y, 1, function(z) z/sum(z)))[,1:6])})
-add_jags_data = append(add_jags_data, list(max_init_recruits = apply(((jags_data$Ra_obs * p_NOR)/overall_phi_Rb_Ra * 1.5), 2, max, na.rm = TRUE),
-                                           first_LGR_adults = min(which(!is.na(jags_data$LGR_adults[,1])))))
+# set first year adult PIT tag data exist to inform BON -> LGR survival
[…]

### 2021-12-17 02-model/model-code.R
Narrow prior on n_stray_tot

@@ -82,7 +82,7 @@ jags_model_code = function() {
     ### PRIORS: HATCHERY STRAYS RETURNING IN YEARS WITH NO ASSOCIATED SMOLT RELEASE ###
     # the number of hatchery strays: only estimate in years where no other mechanism for generating hatchery fish
     for (i in 1:n_stray_yrs[j]) {
-      n_stray_tot[stray_yrs[i,j],j] ~ dunif(0, 5000)
+      n_stray_tot[stray_yrs[i,j],j] ~ dunif(0, 500)
     }
     for (i in 1:n_not_stray_yrs[j]) {
       n_stray_tot[not_stray_yrs[i,j],j] <- 0

### 2021-12-17 03-post-process/output-plots.Rmd
Update output plots for new model

@@
 # which years are "observable" for at least some quantities?
-observable = (jags_data$kmax+1):jags_data$ny_obs
+observable = 2:jags_data$ny_obs
 
@@
   pi_diags,
-  phi_Pb_Pa_diags
+  phi_Pb_Pa_diags,
   phi_Pa_Mb_diags,
@@
 # extract posterior mean residual time series for each population
-resids = lapply(1:4, get_resids, post = post)
+resids = lapply(1:4, get_resids, post = diag_post)
 

### 2021-12-17 03-post-process/output-plots.Rmd
Add a plot showing proportion of fall migrants

@@
 
+# Migratory Strategy Apportionment
+
+```{r pi-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
+```
+
 # Overwinter Survival Relationships

### 2022-01-05 03-post-process/compare-sim-to-obs.Rmd
Change name of f to E throughout (deals with eggs)

@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^Pb_per_f_tot[year,pop]", obs_y, sim_y, pop = j))
+x = lapply(1:4, function(j) get_ratio("^Pb_per_E[year,pop]", obs_y, sim_y, pop = j))
 x = do.call(abind, append(x, list(along = 4)))
@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^f_tot[year,pop]", obs_y, sim_y, pop = j))
+x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
 x = do.call(abind, append(x, list(along = 4)))
@@
 ```{r}
-pop_ts_plots("^Pb_per_f_tot[year,pop]")
+pop_ts_plots("^Pb_per_E[year,pop]")
 ```
@@
 ```{r}
-pop_ts_plots("^f_tot[year,pop]")
+pop_ts_plots("^E[year,pop]")
 ```

### 2022-01-05 03-post-process/output-plots.Rmd
Change name of f to E throughout (deals with eggs)

@@
     label: "Scenario"
-    value: "base"
+    value: "new-BH"
     input: text
@@
 # parr recruitment
-L1 = "Parr Recruitment"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
-match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
+L1 = "Egg-to-Parr Survival"
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
+match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
   out = list(
-    egg_to_parr_surv = post_summ(post, sub_index("^lPb_resid[.+,pop]", pop = j))["mean",],
+    egg_to_parr_surv = post_summ(post, sub_index("^Lphi_E_Pb_resid[.+,pop]", pop = j))["mean",],
     p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
@@
   # extract posterior summaries of total egg production by brood year
-  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))
+  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
 
@@
   Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  f_pred = seq(0, max(f_tot[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
+  E_pred = seq(0, max(E[5,]), length = 30)
+
+  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
   colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
@@
   # empty plot
-  plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
+  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
        xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
@@
   # draw fitted relationship: Bayesian
-  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)
+  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
+  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
+  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
+  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
 
   # draw state pairs + uncertainty
-  segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
+  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
+  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
 }
@@
   # empty plot
-  plot(f_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(f_tot["97.5%",])),
+  plot(E["mean",] ~ Sa_tot["mean",],
+       ylim = c(0, max(E["97.5%",])),
        xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
@@
 
-  segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
-  points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
+  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
+  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
   abline(c(0, 1000), lty = 1)
@@
   # extract posterior summaries of total egg production by brood year
-  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))
+  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
 
   # conversion rates
-  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[year,pop]", pop = j, year = ts_yrs))
+  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
 
@@
   # empty plot
-  plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
-       # ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
+  plot(Pb_per_E["mean",] ~ E["mean",],
        ylim = c(0, 1),
-       xlim = c(0, max(f_tot["97.5%",])), type = "n",
+       xlim = c(0, max(E["97.5%",])), type = "n",
        ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
@@
 
-  segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
-  segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
+  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
+  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
 
@@
 my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_lPb[.]$", "Process SD")
-my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
+my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
+my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
 ```

### 2022-01-05 02-model/fit-model.R

@@ -197,7 +197,7 @@ toggle_rho_estimation("rho_Lphi_O0_O1")    # first year ocean survival
 
 jags_params = c(
   # reproduction
-  "alpha", "beta", "Sig_Lphi_f_Pb", "phi_f_Pb", "mu_beta_per_wul", "sig_lbeta",
+  "alpha", "beta", "Sig_Lphi_E_Pb", "phi_E_Pb", "mu_beta_per_wul", "sig_lbeta",
 
   # overwinter survival coefficients
   "gamma0", "gamma1",
@@ -226,7 +226,7 @@ jags_params = c(
   
   # states
   "Pb", "Pa", "Mb", "Ma", "O0", "O", "Rb",
-  "Ra", "Sb", "Sa", "q_Ra", "q_Sa_adj", "Sa_tot", "Ra_tot", "f_tot",
+  "Ra", "Sb", "Sa", "q_Ra", "q_Sa_adj", "Sa_tot", "Ra_tot", "E",
   
   # carcass vs. weir correction
   "z", "carc_adj", "n_stray_tot", "stray_comp", "mu_z", "sig_z",
@@ -235,13 +235,13 @@ jags_params = c(
   "O_phi_scaler_nat_hat", "phi_Pb_Pa", "bad_flag",
   
   # misc derived quantities
-  "beta_per_wul", "Pb_per_Sa_tot", "Pb_per_f_tot", "Mb_per_Sa_tot", "Sa_tot_per_Sa_tot", "Ra_per_Ma", "phi_O0_Rb_BON",
+  "beta_per_wul", "Pb_per_Sa_tot", "Pb_per_E", "Mb_per_Sa_tot", "Sa_tot_per_Sa_tot", "Ra_per_Ma", "phi_O0_Rb_BON",
   
   # residuals
   "Lpi_resid", "Lphi_Pa_Mb_resid", "Lphi_Mb_Ma_resid",
   "Lphi_Ma_O0_resid", "Lpsi_O1_Rb_resid",
   "Lpsi_O2_Rb_resid", "Lphi_O0_O1_resid", "Lphi_O1_O2_resid",
-  "Lphi_Sb_Sa_resid", "Lphi_f_Pb_resid", "Lphi_Rb_Ra_resid",
+  "Lphi_Sb_Sa_resid", "Lphi_E_Pb_resid", "Lphi_Rb_Ra_resid",
   
   # AR(1) coefficients
   "kappa_phi_O0_O1",
[…]

### 2022-01-05 02-model/model-code.R

@@ -10,7 +10,7 @@ jags_model_code = function() {
     alpha[j] ~ dbeta(1, 1)
     lbeta[j] ~ dnorm(log(mu_beta_per_wul * wul[j]), 1/sig_lbeta^2) %_% T(,15) # log capacity. bound to prevent nonsensically large draws
     beta[j] <- exp(lbeta[j])
-    sig_Lphi_f_Pb[j] ~ dunif(0, 5)
+    sig_Lphi_E_Pb[j] ~ dunif(0, 5)
     beta_per_wul[j] <- beta[j]/wul[j]
 
     ### PRIORS: FRESHWATER PARAMETERS ###
@@ -119,7 +119,7 @@ jags_model_code = function() {
   
   # correlation parameters
   # see toggle_rho_estimation() function; 01-functions/util-fns.R
-  rho_Lphi_f_Pb <- 0
+  rho_Lphi_E_Pb <- 0
   rho_Lpi <- 0
   rho_Lphi_Pa_Mb[i_fall] <- 0
   rho_Lphi_Pa_Mb[i_spring] <- 0
@@ -138,7 +138,7 @@ jags_model_code = function() {
   for (i in 1:nj) {
     for (j in 1:nj) {
       # covariance matrix of parr recruitment
-      Sig_Lphi_f_Pb[i,j] <- sig_Lphi_f_Pb[i] * sig_Lphi_f_Pb[j] * ifelse(i == j, 1, rho_Lphi_f_Pb)
+      Sig_Lphi_E_Pb[i,j] <- sig_Lphi_E_Pb[i] * sig_Lphi_E_Pb[j] * ifelse(i == j, 1, rho_Lphi_E_Pb)
       
       # covariance matrix of LH apportionment
       Sig_Lpi[i,j] <- sig_Lpi[i] * sig_Lpi[j] * ifelse(i == j, 1, rho_Lpi)
@@ -220,7 +220,7 @@ jags_model_code = function() {
   for (y in 2:ny) {
     
     # egg to parr survival: Beverton-Holt relationship
-    Lphi_f_Pb[y,1:nj] ~ dmnorm.vcov(logit(phi_f_Pb_mean[y,1:nj]), Sig_Lphi_f_Pb[1:nj,1:nj])
[…]

### 2022-01-05 03-post-process/output-plots.Rmd
Suppress messages regarding removal of nodes

@@
 
-```{r make-diag-post, message = FALSE}
+```{r make-diag-post}
 # make a reduced diagnostic posterior: drop out all quantities associated with simulated years
@@
 if (length(simulated) > 0) {
-  diag_post = post_remove(post, paste0("[", simulated), ask = FALSE)
+  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
 } else {

### 2022-01-05 03-post-process/compare-sim-to-obs.Rmd
Fix typos in compare sim to obs

@@
     label: "Scenario"
-    value: "base-with-sim-medium"
+    value: "new-BH"
     input: text
@@
 # post = model_info$post                               # full posterior takes a long time to run on this script
-post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 10% of the retained MCMC samples
+post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
 jags_data = model_info$jags_data
@@
   Ma_i = array_format(Ma[i,])
-  nor = Ma_i[,1,1,] + Ra_i[,2,1,]
-  hor = Ra_i[,2,2,]
+  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
+  hor = Ma_i[,2,2,]
 

### 2022-01-05 03-post-process/output-plots.Rmd

@@
 # extract the two key structures from this object
-post = model_info$post
-# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
+# post = model_info$post
+post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
 jags_data = model_info$jags_data
@@
 
+# Correlation Parameters
+
+```{r rho_plot, fig.width = 6, fig.height = 8}
+# get the names of all rho parameters
+# these are elements of a correlation matrix
+# but because the rho term is the same for all population pairs, it is sufficient 
+# to summarize just one element from each matrix
+rho_params = c(
+  match_params(post, "rho_.+[2,1]"),
+  match_params(post, "rho_.+[2,1,1]"),
+  match_params(post, "rho_.+[2,1,2]")
+)
+
+# calculate/format posterior summaries
+rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
+rho_summs = as.data.frame(rho_summs)
+rho_summs = cbind(param = rownames(rho_summs), rho_summs)
+rownames(rho_summs) = NULL
+
+# make prettier names for each term
+rho_names = c(
+  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
+  "rho_Lpi[2,1]" = "Mig. Stategy Apportionment",
+  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
+  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
+  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
+  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
+  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
+  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
+  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
+  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
+  "rho_Lpsi_O1_Rb[2,1,1]" = "Age-3 Maturation (NOR)",
+  "rho_Lpsi_O1_Rb[2,1,2]" = "Age-3 Maturation (HOR)",
+  "rho_Lpsi_O2_Rb[2,1,1]" = "Age-4 Maturation (NOR)",
+  "rho_Lpsi_O2_Rb[2,1,2]" = "Age-4 Maturation (HOR)"
+  )
+rho_summs$name = rho_names[rho_summs$param]
+
+# reorder by decreasing mean correlation
+rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
+at_y = nrow(rho_summs):1
+
+# use different colors for correlations that are between origins vs. between populations
+col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
+
+# make the plot
+par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
+plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
+abline(v = 0, lty = 2)
+segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
+segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
+points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
+axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
+abline(h = at_y - 0.5, col = "grey")
+legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
+box()
+```
+
 # JAGS Model and Data {.tabset .tabset-pills}

### 2022-01-10 100-math-description/GR-sslcm-math-description.Rmd
Add Rmarkdown source for math description

---
title: "\\textsc{Mathematical Description}"
subtitle: "\\textsc{State-Space Life Cycle Model for Grande Ronde Spring Chinook Salmon}"
output: 
  pdf_document:
    keep_tex: false
    toc: true
    toc_depth: 3
    number_sections: true
    citation_package: natbib
fontfamily: mathpazo
geometry: margin=1in
linkcolor: cyan
urlcolor: cyan
citecolor: black
bibliography: cites.bib
link-citations: true
biblio-style: apalike
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{microtype}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \cfoot{\thepage}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\footrulewidth}{0.5pt}
  - \lfoot{State-Space Life Cycle Model\\Mathematical Description}
  - \rfoot{Grande Ronde Spring Chinook Salmon}
  - \usepackage{titlesec}
  - \titleformat{\section}{\bfseries\LARGE\scshape}{\thesection}{1em}{}
  - \titleformat{\subsection}{\bfseries\large}{\thesubsection}{1em}{}
  - \titleformat{\subsubsection}{\itshape}{\thesubsubsection}{1em}{}
  - \renewcommand{\contentsname}{Table of Contents}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
```

\newcommand{\logit}{\mathrm{logit}}
\newcommand{\ilogit}{\mathrm{logit}^{-1}}

\pagenumbering{gobble}
\clearpage
\pagenumbering{arabic}

# Model Overview

The purpose of the state-space life cycle model for Grande Ronde spring Chinook salmon is to synthesize the abundant and diverse biological data sets that have been collected as part of routine monitoring programs into a self-contained and internally consistent population dynamics model.
Such a synthesis can provide richer insights about unobserved quantities (e.g., total parr recruitment abundance) and the relationships between them than allowed by more piecemeal analyses.
Further, because the model estimates expected values and the magnitude of inter-annual variability in a time series framework, the output will be useful for structuring simulation models of future population dynamics.
These simulation exercises will ultimately allow decision-makers to posit plausible future states of nature (e.g., climate change) or management strategies (e.g., habitat restoration or harvest policies) and to receive a distribution of possible future outcomes weighted by their probability of occurrence as suggested by historical population dynamics.
The outputs of those analyses will be useful in decision frameworks that seek to prioritize certain actions over others, while helping to set reasonable expectations for what might likely occur in the face of future challenges.
Although this is the ultimate goal and purpose of developing the state-space life cycle model described herein, we do not discuss this concept further, as it is beyond the scope of the statistical population dynamics model, which is the topic of this document.

The state-space life cycle model tracks the fates of $n_y$ cohorts of fish from egg to adulthood within a statistical population dynamics model.
The model is fundamentally statistical because it receives input data in the form of empirical observations (or externally derived estimates informed by empirical observations, with uncertainty in the external estimation propagated to this model) and estimates unknown parameters that must be internally consistent with the data and one another.
The model is considered "state-space" because it captures two discrete types of variability: (_i_) process noise, i.e., variability in the biological and environmental processes that give rise to latent (i.e., true but unobserved) population dynamics and outcomes and (_ii_) observation error, i.e., variability in the measurement processes that result in the observed data representing an imperfect (but generally unbiased) perception of the true states and transitions among them.
As such, the model is inherently a time series model: spawners in one year produce eggs, which then become parr, then smolt, ocean juveniles, and ultimately spawners in future years -- along this life cycle, it is the same pool of fish at one life stage that is decremented (via survival rate transition probabilities) to become a pool of fish at a later stage of the life cycle.

Furthermore, the model has several dimensions and the majority of processes are assumed to operate differently (i.e., have varying numerical values) along each dimension.
One dimension is age structure: anadromous Chinook salmon in the Grande Ronde basin return predominately as age-3, age-4, or age-5 adults, these outcomes are mutually exclusive but can occur for any fish from a given cohort.
This important feature of Chinook salmon life history means monitoring activities in one year of adult returns sample fish that are progeny from from 3 consecutive brood (i.e., i.e., spawning) years; due to the resulting time linkages in the data this creates, it is essential that our model account for it.
Another dimension is origin structure: adults returning in any given year may be the result of either natural spawning/rearing in the wild or via captive spawning/rearing in a hatchery setting.
Critical outputs of the model are productivity (i.e., fish produced per fish) and capacity (i.e., declining productivity with increasing density) which makes it crucial that we track the fates of naturally and hatchery produced fish separately.
Among naturally produced juveniles, an additional dimension is migratory strategy structure: some individuals rear over their first winter as free-swimming juveniles in the headwaters near where they were spawned, while others migrate to areas lower in the basin to rear overwinter; regardless, all individuals migrate out to sea the following spring as age-2 smolt.
This phenological life history complexity is important to capture because these two groups of fish are monitored separately and they may have different survival outcomes while inhabiting heterogeneous habitats. 
A final dimension is population structure: there are several tributaries within the Grande Ronde basin that support spawning Chinook salmon, and local environmental conditions and genetic adaptations may result in their population dynamics differing in terms of productivity, capacity, or overall life cycle fitness.
Four tributaries, which we consider to be distinct spawning populations, have been monitored using largely consistent methods for nearly three decades; these include Catherine Creek, Lostine River, Minam River, and Upper Grande Ronde River.
Although we model their population dynamics separately, it is also reasonable to expect that these populations should show some level of synchronicity in the conditions they face and the resulting production and survival outcomes. 
Thus, wherever possible we attempt to capture the covariability among population-specific dynamics.

The model is framed in the Bayesian mode of inference, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \ref{tab:param_table}).
A final benefit of using the Bayesian framework is the seamless propagation of uncertainty from directly estimated parameters to derived quantities (of which there are many) -- all unknown quantities, either estimated parameters or deterministic functions of estimated parameters, receive a posterior distribution in the Bayesian framework.
Due to the analytical intractability of the complexity of the model, we employ Markov Chain Monte Carlo methods (implemented via the JAGS probabilistic programming language) to sample from the joint posterior distribution of all unknown quantities in the model.

We begin our description of the mathematical structure of the life cycle model with an overview of several syntax and statistical conventions we employ.
In our mathematical representation of quantities in the model, we have striven for consistency, but this has created somewhat non-intuitive conventions which require devoted explanation.
All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \ref{tab:index_table}, \ref{tab:symbol_table}, \ref{tab:param_table}, and \ref{tab:data_table} for reference and a catalog of all equations is provided in Table \ref{tab:equation_table}.

We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \ref{fig:diagram}): freshwater juvenile, ocean juvenile, and freshwater adult.
For each life phase, we describe the process model dynamics as a set of stochastic and deterministic processes followed by how they are informed by empirical data as part of the observation model.
Although we present these phases and model components in discrete sections, note that they are all components of a single integrated population dynamics model that is statistical in the sense that unknown quantities are estimated with uncertainty from input data.

# Syntactical and Statistical Conventions

* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn -- this includes age-3 fish which are generally referred to as "jacks".
* Life stage-specific states are defined by capital letters, e.g., parr ($P$), smolt ($M$), or spawners ($S$)
* Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are denoted by Greek symbols, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
* Subscripts denote the structure of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population.
* We use the convention $b$ to indicate "before event" and $a$ to indicate "after event" for a quantity that occurs at the same life stage. E.g., $M^{b}$ represents smolt abundance _before_ out-of-basin migration and $M^{a}$ represents smolt abundance _after_ out-of-basin migration. As such, superscripts are most often used syntactically, not mathematically. E.g., $M^{b}$ is not "$M$ raised to the power $b$"; if we must raise the quantity $M^{b}$ to the power $c$, it will be written $(M^{b})^c$.
* Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \rightarrow B}_{y,j}$.
* Most terms vary annually to capture process noise in population dynamics. We denote the deterministic (i.e., expected) value in the absence of process noise with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$. We use the term "deterministic" in the sense that it is the expected value for a stochastic (i.e., with process noise) quantity; the deterministic quantity still has a posterior probability density function.
* In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array). Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax. E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for a given population.
* Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.
* In some cases, a calculation is performed differently for a subset of the possible index values. For example, to denote that $k$ should take on only the values of 1 and 3 (not 2), we would write, $k \in [1,3]$.
* $\log(x)$ represents the natural logarithm of $x$ (i.e., $\log_e(x)$) and it is implied that the constraint $x > 0$ is satisfied.
* $\logit(p)$ represents the log odds of $p$ (i.e., $\log[p/(1-p)])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \rightarrow B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \rightarrow B}_{y,j}}$, which we use as a direct estimate of observation error variability).
* Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (or mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution; generally $\theta_{1}$ is a location parameter specifying the expected value of $x_{y}$ and $\theta_{2}$ is a dispersion parameter specifying the variability of $x_{y}$ around the expected value.

Process noise is introduced by assuming year-specific values are multivariate logit-normal random variables around the deterministic value.
This is done to enable modeling covariability in process noise among populations (or origins, in the few cases where population structure is not modeled).
The covariance matrix of these random variables are denoted by $\Sigma$, and have a common structure for all model components.
Take the hypothetical survival term $\phi^{A \rightarrow B}_{y,j}$ as an example.
We denote its random variability across years and populations as:
\begin{equation}
\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
\label{eq:generic-random}
\end{equation}
where $\Sigma_{\phi^{A \rightarrow B}}$ is an $n_j \times n_j$ matrix with the structure:
\begin{equation}
\left[
\begin{array}{cccc}
\left(\sigma_{\phi^{A \rightarrow B}_{j=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}} & \dots & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}} \\
\sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \left(\sigma_{\phi^{A \rightarrow B}_{j=2}}\right)^2 & \dots & \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}} \\
\vdots & \vdots & \ddots & \vdots \\
\sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}} & \dots & \left(\sigma_{\phi^{A \rightarrow B}_{j=n_j}}\right)^2
\end{array}
\right]
\label{eq:generic-Sigma4by4}
\end{equation}
That is, all populations ($j$) have unique variance terms $(\sigma_{\phi^{A \rightarrow B}_j})^2$ but we assume the correlation component of the covariance calculation ($\rho_{\phi^{A \rightarrow B}}$) is identical for all population pairs.
In cases where a quantity varies annually and is different by origin but not by population, $\Sigma$ would have dimensions $n_o \times n_o$:
\begin{equation}
\left[
\begin{array}{cc}
\left(\sigma_{\phi^{A \rightarrow B}_{o=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{o=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{o=2}} \cdot \rho_{\phi^{A \rightarrow B}} \\
\sigma_{\phi^{A \rightarrow B}_{o=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{o=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \left(\sigma_{\phi^{A \rightarrow B}_{o=2}}\right)^2
\end{array}
\right]
\label{eq:generic-Sigma2by2}
\end{equation}
Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \ref{tab:param_table}) and the $\Sigma$ matrices were constructed using the structures defined in eqs. \ref{eq:generic-Sigma4by4} and \ref{eq:generic-Sigma2by2}.

\clearpage

# Freshwater Juvenile Phase

## Process Model

### Reproduction and Parr Recruitment

Total egg production is the sum product of age-specific spawner abundance (from eq. \ref{eq:get-Sa}, below), proportion female, and fecundity:
\begin{equation}
E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k,j} \cdot f_{k}
\label{eq:get-E}
\end{equation}
The proportion of spawners at age that are female ($\Omega_{k,j}$) was calculated from carcass survey data and averaged across years and fecundity ($f_k$) was calculated from samples taken from Grande Ronde-origin hatchery broodstock.
Both quantities were supplied to the model assuming no error or inter-annual variability.

Deterministic egg-to-parr survival is density-dependent and follows a Beverton-Holt relationship with productivity parameter $\alpha_j$ and capacity parameter $\beta_j$:
\begin{equation}
\dot{\phi}^{E \rightarrow P^{b}}_{y,j} = \frac{1}{\frac{1}{\alpha_j} + \frac{E_{y,j}}{\beta_j}}
\label{eq:get-phi-E-Pb-dot}
\end{equation}
To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\mathrm{WUL}_j$).
Derivation of $\mathrm{WUL}_j$ is too detailed to describe fully here, but briefly, the "value" of stream segments with different habitat characteristics were quantified by a complex generalized linear mixed model that treated detectability-adjusted snorkel counts as the response variable and habitat features (e.g., pool frequency, water temperature, large wood density, etc.) as predictor variables and weights were assigned to stream segments based on their relative value to the segment with the highest value; $\mathrm{WUL}_j$ was then the sum of segment-specific weight and length within the known spawning and rearing extent for each population. We modeled capacity ($\beta_j$) as a function of this $\mathrm{WUL}_j$ metric:
\begin{equation}
\log(\beta_j) \sim \mathcal{N}\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
\label{eq:beta-random}
\end{equation}
where $\lambda$ is the expected change in parr capacity per 1 km change in weighted usable habitat length, and $\sigma_{\beta}$ is the log-normal standard deviation of variability in this relationship not captured by $\mathrm{WUL}$ values.

Realized (i.e., with process noise) egg-to-parr survival was a multivariate logit-normal random variable around the deterministic value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) predicted by the Beverton-Holt function in eq. \ref{eq:get-phi-E-Pb-dot} with covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
\label{eq:phi-E-Pb-random}
\end{equation}
Parr recruitment ($P^{b}_{y,j}$) to the end of summer was then the product of total egg production and egg-to-parr survival:
\begin{equation}
P^{b}_{y,j} = \phi^{E \rightarrow P^{b}}_{y,j} \cdot E_{y,j}
\label{eq:get-Pb}
\end{equation}

### Migratory Strategy Apportionment

Not all summer parr ($P^{b}_{y,j}$) stay in the headwaters to rear overwinter -- some migrate out in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \mathrm{fall}$) and others migrate out the following spring (termed "spring migrants" and indexed by $i = \mathrm{spring}$).
Due to this difference in migratory phenology, these two groups of fish are monitored separately.
To enable building an observation model that could accommodate this feature of the populations in our model, summer parr was apportioned to these two strategies:
\begin{equation}
P^{a}_{y,i,j} = P^{b}_{y,j} \cdot \pi_{y,i,j}
\label{eq:get-Pa}
\end{equation}
where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
For fall migrants, this proportion was a multivariate logit-normal random variable around a time-constant mean ($\dot{\pi}_{i = \mathrm{fall},j}$) with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$ (constructed of $\sigma_{\pi_{i=\mathrm{fall},j}}$ and $\rho_{\pi_{i=\mathrm{fall}}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
\label{eq:pi-random}
\end{equation}
and the proportion that are spring migrants was obtained as its complement ($\pi_{y,i = \mathrm{spring},j} = 1 - \pi_{y,i = \mathrm{fall},j}$).

### Survival to Smolt Stage and Hatchery Inputs

Overwinter survival from the end of the parr year (i.e., age-1) to the start of the smolt year (i.e., age-2), denoted by $\phi^{P^{a} \rightarrow M^{b}}_{y,i,j}$, was modeled as a logit-linear function of parr density (scaled to the same metric of weighted usable habitat length [$\mathrm{WUL}_j$] used in eq. \ref{eq:beta-random}).
Deterministic overwinter survival was:
\begin{equation}
\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot \left(\frac{P^{a}_{y,i,j}}{\mathrm{WUL}_j}\right)
\label{eq:get-phi-Pa-Mb-dot}
\end{equation}
Note the migratory strategy-specific intercept ($\gamma_{0,i,j}$) but common slope terms ($\gamma_{1,j}$).
Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
\label{eq:phi-Pa-Mb-random}
\end{equation}
Natural-origin (indexed by $o=\mathrm{NOR}$) parr surviving to the beginning of the following year was then:
\begin{equation}
M^{b}_{y,i,o=\mathrm{NOR},j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \rightarrow M^{b}}_{y,i,j}
\label{eq:get-Mb-NOR}
\end{equation}
For populations with hatchery supplementation, hatchery-origin smolt releases (assumed known without error) were introduced at this point as well and stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.

### Seaward Migration

In-basin smolt ($M^{b}_{y,i,o,j}$) migrate to the ocean in the spring of the year they become age-2.
We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams encountered in the downstream migration, and (_ii_) from LGR to the ocean.
For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these parameter below), but we were able to model natural-origin survival separately from hatchery-origin.
We assume that year-specific realized survival values were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{b} \rightarrow M^{a}}_{o,j}$) with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}$ (constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{o,j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}_{o}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
\label{eq:phi-Mb-Ma-random}
\end{equation}
Thus, the abundance of smolt reaching LGR was:
\begin{equation}
M^{a}_{y,i,o,j} = M^{b}_{y,i,o,j} \cdot \phi^{M^{b} \rightarrow M^{a}}_{y,o,j}
\label{eq:get-Ma}
\end{equation}
After reaching LGR, we modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
We assumed these survival rates were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$ (constructed of $\sigma_{\phi^{M^{a} \rightarrow O^{0}}_{o}}$ and $\rho_{\phi^{M^{a} \rightarrow O^{0}}}$ following eq. \ref{eq:generic-Sigma2by2}):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
\label{eq:phi-Ma-O0-random}
\end{equation}
Thus, the abundance of fish reaching the ocean by origin was:
\begin{equation}
O^{0}_{y,o,j} = \phi^{M^{a} \rightarrow O^{0}}_{y,o} \sum_i^{n_i} M^{a}_{y,i,o,j}
\label{eq:get-O0}
\end{equation}
Note the summation across migratory strategies ($i$) in eq. \ref{eq:get-O0}, which indicates that the fates of fish with these different strategies were assumed to be the result of identical processes following arrival to LGR.

## Observation Model

The observation model components for the freshwater juvenile life stage were fitted to two primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary) in either the fall or spring and (_ii_) survival of juveniles from several PIT tagging events to LGR.
For both types, the information supplied to the model were externally compiled estimates (e.g., survival from Cormack-Jolly-Seber models) and the estimated standard error was supplied to the model as a measure of observation error variability.

### Abundance Data Sources

Fish with the fall migratory strategy pass the screw trap in the fall and fish with the spring migratory strategy pass the screw trap the following spring.
The estimated passage during these time periods were used in log-normal likelihoods by assuming:
\begin{equation}
\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
\label{eq:fall-count-data}
\end{equation}
for the fall screw trap estimate and
\begin{equation}
\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
\label{eq:spring-count-data}
\end{equation}
for the spring screw trap estimate.

### Survival Data Sources

Natural-origin juveniles have been PIT-tagged during four separate events in most years and populations: (_i_) at the end of summer prior to migratory strategy apportionment, (_ii_) as fall migrant parr pass the screw trap in the fall, (_iii_) at the start of winter in the headwaters (after fall migrants leave, so applies only to spring migrants; also not available for Minam River), and (_iv_) as spring migrant smolt pass the screw trap.
Hatchery-origin smolt released in the spring have also been PIT-tagged.
All five of these tag groups have their survival estimated from the time of tagging to their arrival at LGR.
These estimates (and their associated standard errors) were used in logit-normal likelihoods by assuming:
\begin{equation}
\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \mathcal{N}\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
\label{eq:summer-surv-data}
\end{equation}
for the summer tagging group, 
\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
\label{eq:fall-surv-data}
\end{equation}
for the fall tagging group,
\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
\label{eq:winter-surv-data}
\end{equation}
for the winter tagging group (where $\phi^{P^{b} \rightarrow P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$), 
\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
\label{eq:spring-surv-data}
\end{equation}
for the spring tagging group, and
\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
\label{eq:spring-surv-HOR-data}
\end{equation}
for hatchery-origin smolt releases ($j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$).

Much quantitative research has been devoted to studying the survival of Chinook salmon smolts migrating through the hydrosystem located on the Snake and Columbia rivers.
As a result, we thought it best to utilize the findings from some of this research as input data to our modeling effort rather than attempt to have our model freely estimate survival along this migration -- doing so would give us the flexibility to more freely estimate quantities which have received less directed research, namely ocean survival.
We used the output from the most recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{NOR}}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{HOR}}$ here).
We treated these estimates as representative of the survival for each population, which implies an assumption that the different populations we model experience similar conditions during this migration and ignores any effect of barge-transporting fish.
Similar to the other survival data sets, we assumed these estimates are made with logit-normal random error around the life cycle model estimate to build the likelihood:
\begin{equation}
\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
\label{eq:hydro-surv-data}
\end{equation}

# Ocean Juvenile Phase

## Process Model

Spring Chinook salmon in the Grande Ronde basin migrate to sea as age-2 smolts and can return as either age-3, age-4, or age-5 adults.
That is, ocean juveniles spend between 1 and 3 winters at sea and some fraction will mature and make the return migration after each winter and before the following winter at sea (which we term the "maturation rate").
Thus, we divided ocean population dynamics into two types of demographic rates: survival and maturation rates. We treated survival in the first year with the most complexity and we vastly simplified survival in the second and third years for parameter identifiability purposes.
Further, we wished to account for differences in ocean survival among natural- and hatchery-origin fish, but were limited in the level of complexity that was estimable; thus we assumed natural- and hatchery-origin survival at sea was perfectly correlated over time, but shifted by a log-odds ratio.

First year natural-origin ocean survival was assumed to be a multivariate logit-normal random variable around a time-constant and density-independent deterministic value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$ (constructed of $\sigma_{\phi^{O^{0} \rightarrow O^{1}}_{j}}$ and $\rho_{\phi^{O^{0} \rightarrow O^{1}}}$ following eq. \ref{eq:generic-Sigma4by4}), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion (all $o=\mathrm{NOR}$ in eq. \ref{eq:phi-O0-O1-random}, omitted for brevity):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
\label{eq:phi-O0-O1-random}
\end{equation}
We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same deterministic value each year (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \ref{tab:param_table}).
To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
\begin{equation}
\begin{aligned}
\logit\left(\phi^{O^{0} \rightarrow O^{1}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{0} \rightarrow O^{1}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
\logit\left(\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
\logit\left(\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
\end{aligned}
\label{eq:get-phi-O-HOR}
\end{equation}
Maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) were assumed to vary by ocean age, origin, brood year, and population and were treated as multivariate logit-normal random variables around time-constant and density-independent deterministic values ($\dot{\psi}^{O^{w}}_{o,j}$, $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}_o}$ (one matrix per origin, each constructed of $\sigma_{\psi^{O^{w}}_{o,j}}$ and $\rho_{\psi^{O^{w}}_{o}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\begin{aligned}
\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
\end{aligned}
\label{eq:psi-random}
\end{equation}
Since we assumed age-5 to be the last age of maturity, all fish alive and in the ocean after the third year at sea must mature and return that year (i.e., all $\psi^{O^{3}}_{y,o,j} = 1$).

Now that we have defined the sources of process noise in the ocean demographic rates, we can define the process equations that result in transitioning ocean juveniles through the various ocean ages.
We modeled ocean population dynamics as a sequence of survival, maturation of surviving fish, and survival of non-maturing fish:
\begin{equation}
\begin{aligned}
O^{1}_{y,o,j} &= O^{0}_{y,o,j} \cdot \phi^{O^{0} \rightarrow O^{1}}_{y,o,j} \\
O^{2}_{y,o,j} &= O^{1}_{y,o,j} \cdot (1 - \psi^{O^{1}}_{y,o,j}) \cdot \phi^{O^{1} \rightarrow O^{2}}_{y,o,j} \\
O^{3}_{y,o,j} &= O^{2}_{y,o,j} \cdot (1 - \psi^{O^{2}}_{y,o,j}) \cdot \phi^{O^{2} \rightarrow O^{3}}_{y,o,j} \\
\end{aligned}
\label{eq:get-Os}
\end{equation}
That is, fish reaching the ocean as age-2 juveniles ($O^{0}_{y,o,j}$) must survive one winter to become age-3 ocean juveniles ($O^{1}_{y,o,j}$); if they do not mature at age-3 ($1 - \psi^{O^{1}}_{y,o,j}$), then they must survive another winter to become age-4 ocean juveniles ($O^{2}_{y,o,j}$), and if they do not mature at that point ($1 - \psi^{O^{2}}_{y,o,j}$), they must survive a third winter to become age-5 ocean juveniles ($O^{3}_{y,o,j}$).

Now, we must place the maturing portion of each of $O^{1}_{y,o,j}$, $O^{2}_{y,o,j}$, and $O^{3}_{y,o,j}$ into the correct year and age of return to the mouth of the Columbia River ($R^{b}_{y,k,o,j}$).
Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age at maturity in year $y + k_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $k_{\mathrm{min}}$ = 3).
As an example, fish spawned in brood year $y$ = 2000 will return in 2003 as age-3 ($k$ = 1), in 2004 as age-4 ($k$ = 2), or in 2005 as age-5 ($k$ = 3).
Thus, the abundance of fish spawned in brood year $y$ returning as age-3, age-4, and age-5, respectively, was:
\begin{equation}
\begin{aligned}
R^{b}_{y+k_{\mathrm{min}} + 1 - 1,1,o,j} &= O^{1}_{y,o,j} \cdot \psi^{O^{1}}_{y,o,j} \\
R^{b}_{y+k_{\mathrm{min}} + 2 - 1,2,o,j} &= O^{2}_{y,o,j} \cdot \psi^{O^{2}}_{y,o,j} \\
R^{b}_{y+k_{\mathrm{min}} + 3 - 1,3,o,j} &= O^{3}_{y,o,j} \cdot \psi^{O^{3}}_{y,o,j} \\
\end{aligned}
\label{eq:get-Rbs}
\end{equation}
Note, however, that this leaves 12 age/year combinations per origin unpopulated (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns).
This is because the life cycle dynamics must start somewhere, and no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \ref{tab:param_table}) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
Initial abundance of hatchery-origin returns was handled by the "straying model", described below.

## Observation Model

No data sources were used to inform ocean juvenile population dynamics -- estimation of these quantities was enabled by (_i_) reasonably precise information about the abundance and composition of fish entering the ocean and returning to natal tributaries, (_ii_) the simplifying assumptions described above (i.e., time-constant second and third year ocean survival and perfectly correlated but offset origin-specific survival), and (_iii_) through the use of reasonably strong priors for second and third year ocean survival (Table \ref{tab:param_table}).

# Freshwater Adult Phase

## Process Model

There are several sources of mortality that occur on the upstream migration between the mouth of the Columbia River and the natal tributaries in the Grande Ronde basin.
Downstream of Bonneville Dam (BON, the first dam encountered in this upstream migration), returning adults are subject to predation mortality (survival denoted by $\phi^{SL}_{y,j}$) from sea lions and harvest mortality from fisheries (harvest rate after sea lion predation denoted by $U_{y,k,o}$).
We compiled the best available estimates of these quantities, but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error.
Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around deterministic values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$ (constructed of $\sigma_{\phi^{R^{b} \rightarrow R^{a}}_o}$ and $\rho_{\phi^{R^{b} \rightarrow R^{a}}}$ following eq. \ref{eq:generic-Sigma2by2}).
In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the deterministic expectation in these years for parameter identifiability purposes:
\begin{equation}
\logit\left(\boldsymbol{\phi}^{R^{b} \rightarrow R^{a}}_{y,1:n_o}\right)
\begin{cases}
= \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
\sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
\end{cases}
\label{eq:phi-Rb-Ra-random}
\end{equation}
Examination of the adult data indicated that hatchery-origin adults returned to Grande Ronde populations in years that could not be attributed to hatchery-origin smolt releases to these populations.
Further, the Minam River population (which has no hatchery supplementation program) has had hatchery adults return in many of the years with adult data.
Since there were non-zero observations of hatchery-origin adults in cases without a process model component to produce them, we required a process model mechanism to populate non-zero expected values for the observation model to remain valid based on the available data.
We term this part of the model the "straying model", and apply it only in years/populations in which there is no other way to explain the presence of hatchery-origin adults.
We denote the total number of strays that enter population $j$ in year $y$ as $T_{y,o,j}$; we forced all $T_{y,o=\mathrm{NOR},j} = 0$ and forced all $T_{y,o=\mathrm{HOR},j} = 0$ in years where hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
We denote the age composition of these strays by $p^{T}_{k,j}$ (where $\sum_k^{n_k} p^{T}_{k,j} = 1$) and apportioned $T_{y,o,j}$ to age-specific values by $T_{y,k,o,j}=T_{y,o,j} \cdot p^{T}_{k,j}$.

We can now define the abundance of adults arriving to their natal spawning tributaries by age and origin ($R^{a}_{y,k,o,j}$) as:
\begin{equation}
R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot \phi^{SL}_{y,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(T_{y,o,j} \cdot p^{T}_{k,j}\right)
\label{eq:get-Ra}
\end{equation}
Upon arrival in the tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \mathrm{MIN}$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
These weir removals (denoted by $B_{y,k,o,j}$) were passed to the model as perfectly known values and $B_{y,k,o,j=\mathrm{MIN}} = 0$.
Thus, the abundance of fish passed upstream of the weir and that would have a chance to spawn each year was (the maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$):
\begin{equation}
S^{b}_{y,k,o,j} = \max\left(R^{a}_{y,k,o,j} - B_{y,k,o,j}, 1\right)
\label{eq:get-Sb}
\end{equation}
As a final step before spawning, these fish on the spawning grounds must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
We term this phenomenon "pre-spawn survival", denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, which we assume are multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$) with covariance matrix $\Sigma_{\phi^{S^{b} \rightarrow S^{a}}}$ (constructed of $\sigma_{\phi^{S^{b} \rightarrow S^{a}}_j}$ and $\rho_{\phi^{S^{b} \rightarrow S^{a}}}$ following eq. \ref{eq:generic-Sigma4by4}):
\begin{equation}
\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
\label{eq:phi-Sb-Sa-random}
\end{equation}
Thus, the abundance of total successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
\begin{equation}
S^{a}_{y,k,o,j} = S^{b}_{y,k,o,j} \cdot \phi^{S^{b} \rightarrow S^{a}}_{y,j}
\label{eq:get-Sa}
\end{equation}
It is this $S^{a}_{y,k,o,j}$ value from which total egg production ($E_{y,j}$) is calculated in eq. \ref{eq:get-E} to complete the life cycle.

## Observation Model

The adult observation model relies on three primary data types: (_i_) total abundance of adult returns to the natal tributaries, (_ii_) information about survival on the upstream migration between LGR and BON as well as on the spawning grounds, and (_iii_) composition data to inform the relative abundance of adults of different ages and origins.

### Abundance Data Source

Total return abundance is estimated annually external to the model using a combination of weir counts, mark-recapture methods, and spawning ground surveys.
For each population and year, these have been compiled into a point estimate ($\hat{R}^{a}_{y,j}$; note the lack of $o$ or $k$ indices -- this indicates the estimate is aggregated across these dimensions) and an estimate of observation uncertainty ($\hat{\sigma}_{R^{a}_{y,j}}$, expressed as a log-normal standard error).
We assumed the point estimate is made with log-normal observation error around the model-predicted total returns to the tributary to build the likelihood for this component:
\begin{equation}
\log\left(\hat{R}^{a}_{y,j}\right) \sim \mathcal{N}\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
\label{eq:Ra-data}
\end{equation}

### Survival Data Sources

For the observation model component informing migration survival upstream through the hydropower system, we relied on counts of PIT tag detections of known Grande Ronde-origin fish passing BON ($\hat{x}^{\mathrm{BON}}_{y,o}$) and LGR ($\hat{x}^{\mathrm{LGR}}_{y,o}$).
We assumed the latter was a binomial random variable to build the likelihood component for this data set:
\begin{equation}
\hat{x}^{\mathrm{LGR}}_{y,o} \sim \mathcal{B}\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
\label{eq:upstream-surv-data}
\end{equation}
The other survival data set informing the freshwater adult observation model was for spawning success, i.e., pre-spawn survival.
In annual spawning ground carcass surveys, surveyors record the counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$).
Females are counted this way because it is too difficult to tell if a male has successfully spawned based on their gonads alone, thus we assumed that males and females experience the same pre-spawn survival.
We assumed these counts were gathered using binomial sampling to build the likelihood:
\begin{equation}
\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \mathcal{B}\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
\label{eq:prespawn-surv-data}
\end{equation}

### Composition Data Sources

Since the model is both age- and origin-structured, we required data to inform the relative abundance of adults returning according to these different classes.
These took the form of two sources: (_i_) those collected at the weirs located within three of the four populations we model ($\hat{x}^{R^{a}}_{y,ko,j}$) and (_ii_) those collected during carcass surveys ($\hat{x}^{S^{a^{\prime}}}_{y,ko,j}$), given the Minam River population does not have a weir.
We assumed the weir sampled fish representatively with respect to age and origin composition, however we discovered there was an age sampling bias for carcass surveys relative to the weir.
We fitted to these data assuming multinomial sampling in which there were $n_{ko} = 6$ possible outcomes: $n_k = 3$ ages of return by $n_o = 2$ origins.
Further, we chose to use the observed sample size ($\sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}$) as the multinomial sample size rather than attempting to adjust it for non-independent sampling.
The model-expected composition by age and origin ($p^{R^{a}}_{y,ko,j}$) was calculated from the return abundance by age and origin, reorganized such that age and origin fell along the same array dimension ($R^{a}_{y,ko,j}$) rather than along two dimensions as shown in the process model ($R^{a}_{y,k,o,j}$):
\begin{equation}
p^{R^{a}}_{y,ko,j} = \frac{R^{a}_{y,ko,j}}{\sum_{ko}^{n_{ko}} R^{a}_{y,ko,j}}
\label{eq:get-pRa}
\end{equation}
which we used as the multinomial expected frequency to build the likelihood:
\begin{equation}
\boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
\label{eq:weir-comp-data}
\end{equation}
Due to the age sampling bias of carcass surveys we discovered, we required a correction to ensure reliable fits to all data sets while still recovering unbiased true age composition data for the Minam River population, which had only carcass composition data (the other three populations had both weir and carcass composition data).
For the three populations with paired composition data (i.e., $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$), we estimated correction factors in a hierarchical fashion:
\begin{equation}
z_{k,j} \sim \mathcal{N}(\dot{z}_{k}, \sigma_{z_k})
\label{eq:z-random}
\end{equation}
where $k=1$ or $k=3$ ($k=2$ was treated as the baseline category), $z_{k,j}$ are age- and population-specific coefficients, $\dot{z}_{k}$ are their expectations across populations, and $\sigma_{z_k}$ are their standard deviations across populations.
These coefficients were used in the following log-linear model to derive the correction factors ($\zeta_{k,j}$):
\begin{equation}
\log(\zeta_{k,j}) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
\label{eq:get-zeta-no-minam}
\end{equation}
where $k \in [1,2,3]$, $\boldsymbol{\mathrm{age3}}_{1:n_k} = [1~0~0]$ is a dummy variable indicating whether each value of $k$ corresponds to age-3, and $\boldsymbol{\mathrm{age5}}_{1:n_k} = [0~0~1]$ is a dummy variable indicating whether each value of $k$ corresponds to age-5.
These correction factors were averaged across populations to obtain the correction factors for the Minam River population:
\begin{equation}
\zeta_{k,j=\mathrm{MIN}} = \mathrm{mean}(\zeta_{k,j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]})
\label{eq:get-zeta-minam}
\end{equation}
We used these correction factors to calculate the expected proportions by age and origin for carcass surveys ($p^{S^{a^{\prime}}}_{y,ko,j}$):
\begin{equation}
p^{S^{a^{\prime}}}_{y,ko,j} = \frac{S^{a}_{y,ko,j} \cdot \zeta_{k,j}}{\sum_{ko}^{n_{ko}} S^{a}_{y,ko,j} \cdot \zeta_{k,j}}
\label{eq:get-pSa-prime}
\end{equation}
which we used as the multinomial expected frequency to build the likelihood by assuming:
\begin{equation}
\boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
\label{eq:carcass-comp-data}
\end{equation}

\clearpage

# Figures {-}

```{r diagram_fig_cap}
diagram_fig_cap = "Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon."
```

```{r diagram, fig.cap = diagram_fig_cap, eval = FALSE}
include_graphics("GR-sslcm-diagram.pdf")
```

\rhead{\empty}
\lhead{\empty}
\renewcommand{\headrulewidth}{0pt}

\begin{figure}[H]
\centering
\caption{Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.}
\includegraphics{GR-sslcm-diagram.pdf}
\label{fig:diagram}
\end{figure}

# Tables {-}

```{r index_table_cap}
index_tab_cap = "The various indices and dimensional constants used in defining the structure and scope for the state-space life cycle model for Grande Ronde spring Chinook salmon."
```

```{r index_table}
# read in csv version of table
tab = read.csv("01-indices.csv", allowEscapes = TRUE)

# prettier labels
type_key = c(
  "index" = "Indices",
  "scope" = "Scoping Constants",
  "dimension" = "Dimensional Constants"
)
tab$Type = type_key[as.character(tab$Type)]

# specify footnote text (requires LaTeX syntax, and all instances of \ require four "\\\\")
footnote_key = c(
  "1" = "``Population'' is used to distinguish among the tributaries within the Grande Ronde basin with sufficient data to model complete life cycle population dynamics. Abbreviations are as follows: Catherine Creek (CAT), Lostine River (LOS), Minam River (MIN), and Upper Grande Ronde River (UGR).",
  "2" = "``Year'' refers to the year of spawning; for juvenile phases this is the year fish were spawned (i.e., brood year) and for adult phases this is the year of spawning (i.e., return or calendar year).",
  "3" = "``Age'' refers to the total age, i.e., the number of winters experienced post-spawning including the winter spent as an egg. For example, eggs fertilized in brood year 2000 are age-0 until they hatch in spring of 2001 (age-1), migrate to sea in spring/summer of 2002 (age-2), and return to spawn in one of 2003 (age-3), 2004 (age-4), or 2005 (age-5). $k=1$ is the first age of maturation (age-3) and $k=3$ is the last age of maturation (age-5).",
  "4" = "``Migratory strategy'' refers to the timing of migration from headwaters rearing areas -- some fish (fall migrants) migrate out in the fall at age-1 and spend the winter downstream whereas others stay and migrate out at age-2 (spring migrants). Regardless of this migratory strategy, all fish make the seaward out-of-basin migration at age-2.",
  "5" = "``Origin'' refers to the type of spawning that produced the fish in question: natural-origin (NOR) are fish that were spawned in the wild and hatchery-origin (HOR) are fish that were spawned in a hatchery setting.",
  "6" = "Most quantities treat age ($k$) and origin ($o$) as two separate dimensions of a larger array. However, for fitting to compositional data by age and origin, we collapse these two dimensions into one such that a single vector of proportions can represent the composition by age and origin. $k \\\\in [1,2,3]$ represents age-3, age-4, and age-5 for natural-origin fish, respectively, and $k \\\\in [4,5,6]$ represents these same ages for hatchery-origin fish, respectively."
)

# add footnote symbols where appropriate
tab$Description = paste0(ifelse(is.na(tab$Footnote), "", paste0("\\textsuperscript{", tab$Footnote, "}")), tab$Description)

# build the table
kable(tab[,1:3], "latex", booktabs = TRUE, linesep = "", caption = index_tab_cap, escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "332px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major") %>%
  footnote(number = footnote_key, threeparttable = TRUE, escape = FALSE)
```

\clearpage

```{r symbol_tab_cap}
symbol_tab_cap = "The symbology used to represent the key states (i.e., abundance at life stage/group) and rates (i.e., transition probabilities among states) in the presentation of the state-space life cycle model for Grande Ronde spring Chinook salmon. The majority of rates presented in this table are hierarchically structured/estimated, where the population- and/or origin-specific expected value and standard deviation are free parameters (or a function of free parameters) presented in Table \\ref{tab:param_table}. Equation numbers reference any equation that uses that quantity -- these may include the equation where the quantity is first defined, where it is used in process model, or where it is used in the observation model."
```

```{r symbol_table}
tab = read.csv("02-symbols.csv", allowEscapes = TRUE)

type_key = c(
  "state" = "States",
  "rate" = "Rates"
)

tab$Type = type_key[as.character(tab$Type)]

handle_eqs = function(x) {
  if (x == "") {
    out = ""
  } else {
    x_split = unlist(stringr::str_split(x, ","))
    x_split = stringr::str_remove_all(x_split, " ")
    x_refs = paste0("\\ref{eq:", x_split, "}")
    out = paste(x_refs, collapse = ", ")
  }
  return(out)
}

tab$Eqs. = unname(sapply(tab$Eqs., handle_eqs))

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "25px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "50px") %>%
  column_spec(4, width = "300px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

\clearpage

```{r param_tab_cap}
param_tab_cap = "All free parameters (i.e., that have a prior that is not function of other free parameters) estimated by the state-space life cycle model for Grande Ronde spring Chinook salmon."
```

```{r param_table}
tab = read.csv("03-params.csv", allowEscapes = TRUE)

tab$Eqs. = unname(sapply(tab$Eqs., handle_eqs))

footnote_key = c(
  "1" = "Beta Distribution: $b(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2)$",
  "2" = "Normal Distribution: $\\\\mathcal{N}(\\\\mathrm{mean}$, $\\\\mathrm{precision})$",
  "3" = "Uniform Distribution: $\\\\mathcal{U}(\\\\mathrm{lower}$, $\\\\mathrm{upper})$",
  "4" = "$t$-Distribution: $t$(mean, precision, degrees of freedom)",
  "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$"
)

colnames(tab)[3] = "Prior\\textsuperscript{1,2,3,4,5}"

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "65px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "290px") %>%
  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
  footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
```

\clearpage

```{r data_tab_cap}
data_tab_cap = "The symbology used to represent the data sources in the presentation of observation model components of the state-space life cycle model for Grande Ronde spring Chinook salmon. All data sources listed here have an explicit likelihood component and were thus assumed to be observed with error."
```

```{r data_table}
tab = read.csv("04-data.csv", allowEscapes = TRUE)

type_key = c(
  "abund" = "Abundance",
  "surv" = "Survival",
  "comp" = "Composition"
)

tab$Eqs. = unname(sapply(tab$Eqs., handle_eqs))

tab$Type = type_key[as.character(tab$Type)]

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "70px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "295px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

\clearpage

```{r equation_tab_cap}
equation_tab_cap = "Catalog of all equations presented, separated by life phase (freshwater juvenile, ocean juvenile, or freshwater adult) and model component (process model or observation model)."
```

```{r equation_table}
tab = read.csv("05-equations.csv", allowEscapes = TRUE)

component_key = c(
  "syntax" = "Syntax",
  "process" = "Process",
  "observation" = "Observation"
)

tab$Eq. = unname(sapply(tab$Eq., handle_eqs))

tab$Component = component_key[as.character(tab$Component)]
colnames(tab)[2] = "Model Component"

kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "55px") %>%
  column_spec(2, width = "15px") %>%
  column_spec(3, width = "365px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major")
```

\clearpage

# References {-}

### 2022-01-11 03-post-process/compare-sim-to-obs.Rmd
Update more variable names
This time, done throughout all files

@@
 x = append(
-  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
-  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
+  lapply(1:4, function(j) get_ratio("^psi_O1[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
+  lapply(1:4, function(j) get_ratio("^psi_O1[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
 )
@@
 x = append(
-  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
-  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
+  lapply(1:4, function(j) get_ratio("^psi_O2[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
+  lapply(1:4, function(j) get_ratio("^psi_O2[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
 )
@@
 ```{r}
-pop_ts_plots("^psi_O1_Rb[year,origin,pop]", origin = 1)
+pop_ts_plots("^psi_O1[year,origin,pop]", origin = 1)
 ```
@@
 ```{r}
-pop_ts_plots("^psi_O2_Rb[year,origin,pop]", origin = 1)
+pop_ts_plots("^psi_O2[year,origin,pop]", origin = 1)
 ```

### 2022-01-11 03-post-process/output-plots.Rmd
Update more variable names
This time, done throughout all files

@@
 L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
-match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
+match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
 parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O1_Rb[.+,origin,pop]")
+base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-psi_O1_Rb_diags = rbind(tmp1, tmp2)
+psi_O1_diags = rbind(tmp1, tmp2)
 
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O2_Rb[.+,origin,pop]")
+base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-psi_O2_Rb_diags = rbind(tmp1, tmp2)
+psi_O2_diags = rbind(tmp1, tmp2)
 
@@
 L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
-base = c("O_phi_scaler_nat_hat[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
+base = c("delta[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
 match = sub_index(base, pop = ".")
@@
 L1 = "Strays"
-L2 = c("Realized Number", "Age Comp")
-match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+L2 = c("Realized Total Number", "Age Comp")
+match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
+G_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
 
@@
   phi_Ma_O0_diags,
-  psi_O1_Rb_diags,
-  psi_O2_Rb_diags,
+  psi_O1_diags,
+  psi_O2_diags,
   phi_O0_O1_diags,
@@
   init_diags,
-  stray_diags
+  G_diags
 )
@@
 # weir composition
-new = post_subset(post, "weir_x_obs_new_dev", TRUE)
-obs = post_subset(post, "weir_x_obs_dev", TRUE)
+new = post_subset(post, "x_Ra_new_dev", TRUE)
+obs = post_subset(post, "x_Ra_dev", TRUE)
 bp = array_format(colMeans(obs > new))
 dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$weir_nx_obs == 0 | is.na(jags_data$weir_nx_obs)] = NA
-weir_x_bp = data.frame(
+bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
+x_Ra_bp = data.frame(
   name = rep("Weir", 4), pop = pops,
@@
 )
-rownames(weir_x_bp) = NULL
+rownames(x_Ra_bp) = NULL
 
 # carcass composition
-new = post_subset(post, "carc_x_obs_new_dev", TRUE)
-obs = post_subset(post, "carc_x_obs_dev", TRUE)
+new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
+obs = post_subset(post, "x_Sa_prime_dev", TRUE)
 bp = array_format(colMeans(obs > new))
 dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$carc_nx_obs == 0 | is.na(jags_data$carc_nx_obs)] = NA
-carc_x_bp = data.frame(
+bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
+x_Sa_prime_bp = data.frame(
   name = rep("Carcasses", 4), pop = pops,
@@
 )
-rownames(carc_x_bp) = NULL
+rownames(x_Sa_prime_bp) = NULL
 
 # pre-spawn survival
-new = post_subset(post, "carcs_spawned_new_dev", TRUE)
-obs = post_subset(post, "carcs_spawned_dev", TRUE)
+new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
+obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
 bp = array_format(colMeans(obs > new))
 dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-carcs_spawned_bp = data.frame(
+x_carcass_spawned_bp = data.frame(
   name = rep("Prespawn", 4), pop = pops,
@@
 )
-rownames(carcs_spawned_bp) = NULL
+rownames(x_carcass_spawned_bp) = NULL
 
 # movement survival from BON to LGR
-new = post_subset(post, "LGR_adults_new_dev", TRUE)
-obs = post_subset(post, "LGR_adults_dev", TRUE)
+new = post_subset(post, "x_LGR_new_dev", TRUE)
+obs = post_subset(post, "x_LGR_dev", TRUE)
 bp = array_format(colMeans(obs > new))
 dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
-LGR_adults_bp = data.frame(
+x_LGR_bp = data.frame(
   name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
@@
 )
-rownames(LGR_adults_bp) = NULL
+rownames(x_LGR_bp) = NULL
 
@@
   phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp, LGR_adults_bp
+  phi_Ma_O0_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
 )
@@
     yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
-    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
-    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
-    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
-    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
+    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
+    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
     BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
@@
 plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
+             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
              main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
@@
 plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
+             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
              main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
@@
 # extract the full posteriors of the two composition sets
-q_Ra_full = post_subset(post, "q_Ra", matrix = TRUE)
-q_Sa_adj_full = post_subset(post, "q_Sa", matrix = TRUE)
+p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
+p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
 
 # primary containers: will store final recalculated output
-q_Ra_age = q_Sa_adj_age = q_Ra_origin = q_Sa_adj_origin = NULL
+p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
 
@@
   # format the posterior draw as arrays -- easier to subset
-  q_Ra = array_format(q_Ra_full[i,])
-  q_Sa_adj = array_format(q_Sa_adj_full[i,])
+  p_Ra = array_format(p_Ra_full[i,])
+  p_Sa_prime = array_format(p_Sa_prime_full[i,])
 
@@
   # containers
-  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
+  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
+  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
   for (j in 1:jags_data$nj) {
@@
       # calculate aggregate proportions for each age
-      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,ko_age[[k]],j])
-      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,ko_age[[k]],j])
+      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
+      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
 
@@
   # vectorize, add names, and remove NAs
-  q_Ra_age_v = as.numeric(q_Ra_age_tmp)
-  q_Sa_adj_age_v = as.numeric(q_Sa_adj_age_tmp)
-  names(q_Ra_age_v) = paste0("q_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(q_Sa_adj_age_v) = paste0("q_Sa_adj_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  q_Ra_age_v = q_Ra_age_v[!is.na(q_Ra_age_v)]
-  q_Sa_adj_age_v = q_Sa_adj_age_v[!is.na(q_Sa_adj_age_v)]
+  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
+  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
+  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
+  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
+  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
+  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
 
@@
   # containers
-  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
+  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
+  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
   for (j in 1:jags_data$nj) {
@@
       # calculate aggregate proportions for each origin
-      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,ko_origin[[o]],j])
-      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,ko_origin[[o]],j])
+      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
+      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
 
@@
   # vectorize, add names, and remove NAs
-  q_Ra_origin_v = as.numeric(q_Ra_origin_tmp)
-  q_Sa_adj_origin_v = as.numeric(q_Sa_adj_origin_tmp)
-  names(q_Ra_origin_v) = paste0("q_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(q_Sa_adj_origin_v) = paste0("q_Sa_adj_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  q_Ra_origin_v = q_Ra_origin_v[!is.na(q_Ra_origin_v)]
-  q_Sa_adj_origin_v = q_Sa_adj_origin_v[!is.na(q_Sa_adj_origin_v)]
+  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
+  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
+  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
+  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
+  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
+  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
 
@@
 
-  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
-  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
-  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
-  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)
+  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
+  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
+  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
+  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
 
@@
 # combine new calculated quantities into a big matrix
-q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_origin, q_Sa_adj_origin)
+q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
 
@@
 # containers
-x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
+x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
+x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
 
@@
   for (k in 1:jags_data$nk) {
-    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,ko_age[[k]],j])
-    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,ko_age[[k]],j])
+    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
+    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
   }
@@
   for (o in 1:jags_data$no) {
-    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,ko_origin[[o]],j])
-    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]
-
-x_weir_new_obs = list(
-  x_weir_age_obs = x_weir_age_obs,
-  x_weir_origin_obs = x_weir_origin_obs
+    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
+    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
+  }
+}
+
+dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
+
+x_Ra_new_obs = list(
+  x_Ra_age_obs = x_Ra_age_obs,
+  x_Ra_origin_obs = x_Ra_origin_obs
 )
 
-x_carc_new_obs = list(
-  x_carc_age_obs = x_carc_age_obs,
-  x_carc_origin_obs = x_carc_origin_obs
+x_Sa_prime_new_obs = list(
+  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
+  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
 )
@@
   par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$weir_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$weir_nx_obs[observable,j], na.rm = TRUE)),
+  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
+               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
                xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
@@
   at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$weir_nx_obs[observable,j]), 3, 4)[at_x])
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
   segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
@@
   par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
 
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
 
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$carc_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$carc_nx_obs[observable,j], na.rm = TRUE)),
+  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
+               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
                xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
@@
   at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carc_nx_obs[observable,j]), 3, 4)[at_x])
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
   segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
@@
   par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$carc_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_carc_new_obs$x_carc_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
+               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
                main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
@@
   if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$carcs_sampled[observable,j], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
+  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
   at_x = seq(1, length(observable), 4)
@@
 # extract posterior samples of the slope parameter
-beta_per = post_subset(post, "mu_beta_per_wul", TRUE)
+beta_per = post_subset(post, "lambda", TRUE)
 
@@
 # extract posterior summary of slope
-est = post_summ(post, "mu_beta_per_wul")
+est = post_summ(post, "^lambda$")
 colnames(est) = "slope"
@@
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("n_stray_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
 }
@@
 plot_fn = function(j) {
-  x = post_summ(post, sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = j))
+  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
 
@@
   par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2_Rb[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
 
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
+my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O1_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2_Rb[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2_Rb[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2_Rb[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
+my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
+my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
 ```
@@
 par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O2_Rb[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
+my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
 ```
@@
 ```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-my_boxplot(sub_index("O_phi_scaler_nat_hat[pop]", pop = "."), ylab = "Log Odds Ratio")
+my_boxplot(sub_index("delta[pop]", pop = "."), ylab = "Log Odds Ratio")
 ```
@@
   "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1_Rb[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1_Rb[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2_Rb[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2_Rb[2,1,2]" = "Age-4 Maturation (HOR)"
+  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
+  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
+  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
+  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
   )

### 2022-01-11 01-functions/data-fns.R

@@ -168,9 +168,9 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   hat_comp[is.na(hat_comp)] = 0
   
   # age frequencies: for fitting composition of returns
-  weir_x_obs = matrix(NA, ny, no * nk); dimnames(weir_x_obs) = list(y_names, ko_names)
-  weir_x_obs[y_names %in% sub$brood_year,] = as.matrix(cbind(nat_comp, hat_comp))
-  weir_nx_obs = rowSums(weir_x_obs)
+  x_Ra = matrix(NA, ny, no * nk); dimnames(x_Ra) = list(y_names, ko_names)
+  x_Ra[y_names %in% sub$brood_year,] = as.matrix(cbind(nat_comp, hat_comp))
+  nx_Ra = rowSums(x_Ra)
   
   ### ADULT AGE COMP: CARCASSES ###
   # obtain names of age comp variables
@@ -183,9 +183,9 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   hat_comp[is.na(hat_comp)] = 0
   
   # age frequencies: for fitting composition of returns
-  carc_x_obs = matrix(NA, ny, no * nk); dimnames(carc_x_obs) = list(y_names, ko_names)
-  carc_x_obs[y_names %in% sub$brood_year,] = as.matrix(cbind(nat_comp, hat_comp))
-  carc_nx_obs = rowSums(carc_x_obs)
+  x_Sa_prime = matrix(NA, ny, no * nk); dimnames(x_Sa_prime) = list(y_names, ko_names)
+  x_Sa_prime[y_names %in% sub$brood_year,] = as.matrix(cbind(nat_comp, hat_comp))
+  nx_Sa_prime = rowSums(x_Sa_prime)
   
   ### NUMBER OF RETURNING ADULTS REMOVED AT WEIR ###
   rm_comp_names = create_comp_names("rm", o_names, k_names)
@@ -205,14 +205,14 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   phi_SL[y_names %in% sub$brood_year] = sub$surv_est_sea_lions
   
   ### COUNTS OF ADULT PIT TAG DETECTIONS AT BON ###
-  BON_adults = matrix(NA, ny, no); dimnames(BON_adults) = list(y_names, o_names)
[…]

### 2022-01-11 01-functions/util-fns.R

@@ -138,10 +138,10 @@ BH = function(x, alpha, beta) {
 }
 
 ##### REPLACE PLACEHOLDER INDEX #####
-# x: a string like "psi_O1_Rb[year,sex,origin,pop]
+# x: a string like "psi_O1[year,sex,origin,pop]
 # other arguments: a number to replace
-# e.g., sub_index("psi_O1_Rb[year,sex,origin,pop]", year = ".+", sex = 1, origin = 2, pop = ".")
-# returns "psi_O1_Rb[.+,1,2,.]"
+# e.g., sub_index("psi_O1[year,sex,origin,pop]", year = ".+", sex = 1, origin = 2, pop = ".")
+# returns "psi_O1[.+,1,2,.]"
 # this reduces how much hardcoding is required in generating output summaries
 
 sub_index = function(x, year = NULL, LH_type = NULL, age = NULL, origin = NULL, pop = NULL) {

### 2022-01-11 02-model/fit-model.R

@@ -48,24 +48,24 @@ jags_data = append_no_na_indices(jags_data)
 
 # some parameters we are assuming known (for now)
 # harvest rates Below and Above BON by year, age, origin
-Ub_45_nat = with(jags_data, c(NA, rep(0.02, ny - 1)))
-Ub_45_hat = with(jags_data, c(NA, rep(0.08, ny - 1)))
-Ub = abind(list(cbind(Ub_45_nat * 0.25, Ub_45_nat, Ub_45_nat), cbind(Ub_45_hat * 0.75, Ub_45_hat, Ub_45_hat)), along = 3)
-dimnames(Ub) = with(jags_data, list(rownames(Ra_obs), kmin:kmax, c("Nat", "Hat")))
+U_45_nat = with(jags_data, c(NA, rep(0.02, ny - 1)))
+U_45_hat = with(jags_data, c(NA, rep(0.08, ny - 1)))
+U = abind(list(cbind(U_45_nat * 0.25, U_45_nat, U_45_nat), cbind(U_45_hat * 0.75, U_45_hat, U_45_hat)), along = 3)
+dimnames(U) = with(jags_data, list(rownames(Ra_obs), kmin:kmax, c("Nat", "Hat")))
 
 # proportion of spawners by age and population that are female
-p_female = array(NA, dim = c(jags_data$nk, jags_data$nj))
-dimnames(p_female) = list(jags_data$kmin:jags_data$kmax, colnames(jags_data$Ra_obs))
-p_female["3",] = 0
-p_female["4","CAT"] = 0.55; p_female["4","LOS"] = 0.53; p_female["4","UGR"] = 0.57 
-p_female["5","CAT"] = 0.43; p_female["5","LOS"] = 0.41; p_female["5","UGR"] = 0.48 
-p_female["4","MIN"] = round(mean(p_female["4",], na.rm = TRUE), 2)
-p_female["5","MIN"] = round(mean(p_female["5",], na.rm = TRUE), 2)
+Omega = array(NA, dim = c(jags_data$nk, jags_data$nj))
[…]

### 2022-01-11 02-model/model-code.R

@@ -63,7 +63,7 @@ jags_model_code = function() {
     mu_phi_O2_O3[o_nat,j] <- mu_phi_O1_O2[o_nat,j]   # third winter at sea: to become SW3
     
     # log odds ratio between natural and hatchery origin
-    O_phi_scaler_nat_hat[j] ~ dt(0, 1/1.566^2, 7.763)
+    delta[j] ~ dt(0, 1/1.566^2, 7.763)
     
     # AR(1) coefficient for first year ocean survival
     kappa_phi_O0_O1[j] ~ dunif(-0.99,0.99)
@@ -75,29 +75,25 @@ jags_model_code = function() {
     sig_Lphi_O0_O1_init[j] <- sqrt(sig_Lphi_O0_O1[j]^2/(1 - kappa_phi_O0_O1[j]^2))
     
     # mean survival by ocean year transition for hatchery origin
-    logit(mu_phi_O0_O1[o_hat,j]) <- logit(mu_phi_O0_O1[o_nat,j]) + O_phi_scaler_nat_hat[j]
-    logit(mu_phi_O1_O2[o_hat,j]) <- logit(mu_phi_O1_O2[o_nat,j]) + O_phi_scaler_nat_hat[j]
-    logit(mu_phi_O2_O3[o_hat,j]) <- logit(mu_phi_O2_O3[o_nat,j]) + O_phi_scaler_nat_hat[j]
+    logit(mu_phi_O0_O1[o_hat,j]) <- logit(mu_phi_O0_O1[o_nat,j]) + delta[j]
+    logit(mu_phi_O1_O2[o_hat,j]) <- logit(mu_phi_O1_O2[o_nat,j]) + delta[j]
+    logit(mu_phi_O2_O3[o_hat,j]) <- logit(mu_phi_O2_O3[o_nat,j]) + delta[j]
     
     ### PRIORS: HATCHERY STRAYS RETURNING IN YEARS WITH NO ASSOCIATED SMOLT RELEASE ###
+    
+    # age composition of strays: only estimate for hatchery origin
+    p_G[1:nk,o_nat,j] <- rep(0, nk)
+    p_G[1:nk,o_hat,j] ~ ddirich(rep(1, nk))
+    
     # the number of hatchery strays: only estimate in years where no other mechanism for generating hatchery fish
[…]

### 2022-01-11 02-model/fit-model.R
Shorten the "very_short" MCMC scenario even more

@@ -275,11 +275,11 @@ jags_params = c(
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####
 
 jags_dims = list(
-  n_post = switch(mcmc_length,  "very_short" = 500, "short" = 2000, "medium" = 24000, "long" = 60000),
-  n_burn = switch(mcmc_length,  "very_short" = 100, "short" = 1000, "medium" = 20000, "long" = 60000),
+  n_post = switch(mcmc_length,  "very_short" = 100, "short" = 2000, "medium" = 24000, "long" = 60000),
+  n_burn = switch(mcmc_length,  "very_short" = 5, "short" = 1000, "medium" = 20000, "long" = 60000),
   n_thin = switch(mcmc_length,  "very_short" = 1,   "short" = 3,    "medium" = 8,     "long" = 20),
   n_chain = switch(mcmc_length, "very_short" = 3,   "short" = 3,    "medium" = 3,     "long" = 3),
-  n_adapt = switch(mcmc_length, "very_short" = 100, "short" = 1000, "medium" = 1000,  "long" = 1000),
+  n_adapt = switch(mcmc_length, "very_short" = 10, "short" = 1000, "medium" = 1000,  "long" = 1000),
   parallel = TRUE
 )
 

### 2022-01-11 02-model/fit-model.R
Rename model scenario: base

@@ -21,7 +21,7 @@ out_dir = "02-model/model-output"
 last_yr = 2050
 
 # specify a scenario name
-scenario = "new-BH"
+scenario = "base"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE

### 2022-01-11 100-math-description/GR-sslcm-math-description.Rmd
Update math document straying symbology
Get rid of the "T" convention, and replace with "G". T doesn't work in the JAGS model code, because it is interpreted as "TRUE".

@@
 We term this part of the model the "straying model", and apply it only in years/populations in which there is no other way to explain the presence of hatchery-origin adults.
-We denote the total number of strays that enter population $j$ in year $y$ as $T_{y,o,j}$; we forced all $T_{y,o=\mathrm{NOR},j} = 0$ and forced all $T_{y,o=\mathrm{HOR},j} = 0$ in years where hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
-We denote the age composition of these strays by $p^{T}_{k,j}$ (where $\sum_k^{n_k} p^{T}_{k,j} = 1$) and apportioned $T_{y,o,j}$ to age-specific values by $T_{y,k,o,j}=T_{y,o,j} \cdot p^{T}_{k,j}$.
+We denote the total number of strays that enter population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\mathrm{NOR},j} = 0$ and forced all $G_{y,o=\mathrm{HOR},j} = 0$ in years where hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
+We denote the age composition of these strays by $p^{G}_{k,j}$ (where $\sum_k^{n_k} p^{G}_{k,j} = 1$) and apportioned $G_{y,o,j}$ to age-specific values by $G_{y,k,o,j}=G_{y,o,j} \cdot p^{G}_{k,j}$.
 
@@
 \begin{equation}
-R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot \phi^{SL}_{y,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(T_{y,o,j} \cdot p^{T}_{k,j}\right)
+R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot \phi^{SL}_{y,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
 \label{eq:get-Ra}

### 2022-01-11 00-data/prep-bio-data.R
Replace all instances of Nat and Hat with NOR and HOR

@@ -454,5 +454,8 @@ bio_dat = merge(bio_dat, empty_df, by = c("population", "brood_year"), all = T)
 # make hatchery releases be zero if NA
 bio_dat$hatchery_smolt[is.na(bio_dat$hatchery_smolt) & bio_dat$population != "ALL"] = 0
 
+colnames(bio_dat) = stringr::str_replace(colnames(bio_dat), "Nat", "NOR")
+colnames(bio_dat) = stringr::str_replace(colnames(bio_dat), "Hat", "HOR")
+
 # remove unnecessary objects from workspace, retain only bio_dat
 rm(list = setdiff(ls(), "bio_dat"))

### 2022-01-11 01-functions/data-fns.R

@@ -21,7 +21,7 @@ get_logit_se = function(p_mean, p_se, p_lwr, p_upr, alpha) {
 
 
 ##### CREATE NAMES FOR A SPECIFIC COMPOSITION DATA SET #####
-# o_names = c("Nat", "Hat")
+# o_names = c("NOR", "HOR")
 # k_names = c(3, 4, 5)
 # type = "weir";# type = "carc"; type = "rm"
 
@@ -86,7 +86,7 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   y_names = (first_y - 1):last_y
   k_names = kmin:kmax
   i_names = paste0(c("fall", "spring"), "-mig")
-  o_names = c("Nat", "Hat")
+  o_names = c("NOR", "HOR")
   ko_names = c(paste0(k_names, "-", o_names[1]), paste0(k_names, "-", o_names[2]))
   
   ### JUVENILE ABUNDANCE DATA ###
@@ -139,23 +139,23 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   
   # spring logit(surv) to LGD
   Lphi_obs_Mb_Ma = array(NA, dim = c(ny, ni, no)); dimnames(Lphi_obs_Mb_Ma) = list(y_names, i_names, o_names)
-  Lphi_obs_Mb_Ma[y_names %in% sub$brood_year,i_names == "spring-mig","Nat"] = logit(sub$spring_surv_est)
-  Lphi_obs_Mb_Ma[y_names %in% sub$brood_year,i_names == "spring-mig","Hat"] = logit(sub$hatchery_spring_surv_est)
+  Lphi_obs_Mb_Ma[y_names %in% sub$brood_year,i_names == "spring-mig",o_names[1]] = logit(sub$spring_surv_est)
+  Lphi_obs_Mb_Ma[y_names %in% sub$brood_year,i_names == "spring-mig",o_names[2]] = logit(sub$hatchery_spring_surv_est)
   
   # sd spring logit(surv) to LGD
   sig_Lphi_obs_Mb_Ma = array(NA, dim = c(ny, ni, no)); dimnames(sig_Lphi_obs_Mb_Ma) = list(y_names, i_names, o_names)
[…]

### 2022-01-11 02-model/fit-model.R

@@ -51,7 +51,7 @@ jags_data = append_no_na_indices(jags_data)
 U_45_nat = with(jags_data, c(NA, rep(0.02, ny - 1)))
 U_45_hat = with(jags_data, c(NA, rep(0.08, ny - 1)))
 U = abind(list(cbind(U_45_nat * 0.25, U_45_nat, U_45_nat), cbind(U_45_hat * 0.75, U_45_hat, U_45_hat)), along = 3)
-dimnames(U) = with(jags_data, list(rownames(Ra_obs), kmin:kmax, c("Nat", "Hat")))
+dimnames(U) = with(jags_data, list(rownames(Ra_obs), kmin:kmax, c("NOR", "HOR")))
 
 # proportion of spawners by age and population that are female
 Omega = array(NA, dim = c(jags_data$nk, jags_data$nj))
@@ -81,8 +81,8 @@ add_jags_data = append(add_jags_data, add_jags_data2)
 add_jags_data3 = list(
   i_fall = 1,     # fall migrants are i = 1
   i_spring = 2,   # spring migrants are i = 2,
-  o_nat = 1,      # natural origin are o = 1,
-  o_hat = 2       # hatchery origin are o = 2,
+  o_nor = 1,      # natural origin are o = 1,
+  o_hor = 2       # hatchery origin are o = 2,
 )
 add_jags_data = append(add_jags_data, add_jags_data3)
 

### 2022-01-11 02-model/model-code.R

@@ -31,13 +31,13 @@ jags_model_code = function() {
     gamma1[i_spring,j] <- gamma1[i_fall,j]
     
     # natural origin movement survival (trib to LGD): estimate for spring migrants and assume the same value for fall migrants
-    mu_phi_Mb_Ma[i_spring,o_nat,j] ~ dbeta(1, 1)
-    sig_Lphi_Mb_Ma[o_nat,j] ~ dunif(0, 5)
-    mu_phi_Mb_Ma[i_fall,o_nat,j] <- mu_phi_Mb_Ma[i_spring,o_nat,j]
+    mu_phi_Mb_Ma[i_spring,o_nor,j] ~ dbeta(1, 1)
+    sig_Lphi_Mb_Ma[o_nor,j] ~ dunif(0, 5)
+    mu_phi_Mb_Ma[i_fall,o_nor,j] <- mu_phi_Mb_Ma[i_spring,o_nor,j]
 
     # hatchery origin movement survival (trib to LGD): have spring migrants only
-    mu_phi_Mb_Ma[i_spring,o_hat,j] ~ dbeta(1, 1)
-    sig_Lphi_Mb_Ma[o_hat,j] ~ dunif(0, 5)
+    mu_phi_Mb_Ma[i_spring,o_hor,j] ~ dbeta(1, 1)
+    sig_Lphi_Mb_Ma[o_hor,j] ~ dunif(0, 5)
     
     # pre-spawn survival (after brood-stock removal to successful spawning)
     mu_phi_Sb_Sa[j] ~ dbeta(1, 1)
@@ -58,9 +58,9 @@ jags_model_code = function() {
     
     ### PRIORS: OCEAN SURVIVAL ###
     # mean survival by ocean year transition for natural origin
-    mu_phi_O0_O1[o_nat,j] ~ dbeta(1,1)               # first winter at sea: to become SWA1
-    mu_phi_O1_O2[o_nat,j] ~ dbeta(60,15)             # second winter at sea: to become SWA2
-    mu_phi_O2_O3[o_nat,j] <- mu_phi_O1_O2[o_nat,j]   # third winter at sea: to become SW3
+    mu_phi_O0_O1[o_nor,j] ~ dbeta(1,1)               # first winter at sea: to become SWA1
[…]

### 2022-01-11 03-post-process/output-plots.Rmd

@@
 # extract the two key structures from this object
-# post = model_info$post
-post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
+post = model_info$post
+# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
 jags_data = model_info$jags_data

### 2022-01-11 03-post-process/output-plots.Rmd
Make Rmd plots react to whether these items were toggled on or off

@@
 
-```{r calculate-waic}
+```{r calculate-waic, eval = model_info$do_lppd}
 summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
@@
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
+```
+
+```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
+cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
 ```
@@
 
-```{r calculate-bayesian-pvals}
+```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
 # function to summarize bayesian p-values within a data source
@@
 
-```{r bayesian-pvals-table}
+```{r bayesian-pvals-table, eval = model_info$do_pp_check}
 # a function to color cells depending on the value
@@
   collapse_rows(1:5) 
+```
+
+```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
+cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
 ```

### 2022-01-11 03-post-process/compare-sim-to-obs.Rmd
Add ability to render the sim vs. obs output Rmd automatically
Just like for the standard output-plots.Rmd

@@
 # extract the two key structures from this object
-# post = model_info$post                               # full posterior takes a long time to run on this script
-post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
+post = model_info$post                               # full posterior takes a long time to run on this script
+# post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
 jags_data = model_info$jags_data

### 2022-01-11 02-model/fit-model.R

@@ -21,7 +21,7 @@ out_dir = "02-model/model-output"
 last_yr = 2050
 
 # include posterior predictive checks in JAGS code?
-do_pp_check = FALSE
+do_pp_check = TRUE
 
 # include posterior predictive density calculation in JAGS code?
 do_lppd = FALSE
@@ -37,7 +37,7 @@ rmd = as.logical(args[1])
 mcmc_length = args[2]
 
 if (is.na(rmd)) {
-  rmd = FALSE
+  rmd = TRUE
   cat("\n\n'rmd' was not supplied as a command line argument.", rmd, "will be used.")
 }
 
@@ -439,7 +439,7 @@ saveRDS(out_obj, file.path(out_dir, out_file))
 # delete the text file that contains the JAGS code
 unlink(jags_file)
 
-##### STEP 9: RENDER RMD #####
+##### STEP 9: RENDER RMDs #####
 
 # render the output plots if requested
 if (rmd) {
@@ -474,3 +474,35 @@ if (rmd) {
   cat("\n\nDone.")
 }
 
+# render the simulation vs. observed time series plots if requested and applicable
+if (rmd & last_yr > 2019) {
+  # start a timer, this can take a while
+  starttime = Sys.time()
+  
+  # print a progress message
+  cat("\nRendering Sim vs. Obs Rmd Output")
+  
+  # set working dir to post-processing directory
+  setwd("03-post-process")
+  
+  # file name of rendered output
+  rmd_out_file = paste0("sim-vs-obs-", scenario, ".html")
+  
+  # render the output
+  render(input = "compare-sim-to-obs.Rmd",
+         output_file = rmd_out_file,
+         params = list(scenario = scenario),
+         quiet = TRUE
+  )
+  
+  # open the rendered file when complete
+  file.show(rmd_out_file)
+  
+  # stop the timer
+  stoptime = Sys.time()
+  cat("\nSim vs. Obs Rmd elapsed:", format(round(stoptime - starttime, 2)))
+  
+  # set the working dir back
+  setwd("../")
+  cat("\n\nDone.")
+}

### 2022-01-25 03-post-process/compare-sim-to-obs.Rmd
Implement improved post-MCMC thinning in Rmds

@@
 subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
-output: html_document
+date: "`r paste0('Date Rendered: ', Sys.Date())`"
+output:
+   html_document:
+    toc: true
+    toc_float: true
 params:
@@
     input: text
+  thin_percent:
+    label: "Proportion of Posterior Samples to Retain?"
+    value: 1
+    input: numeric
 editor_options: 
@@
 
-# extract the two key structures from this object
-post = model_info$post                               # full posterior takes a long time to run on this script
-# post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
+# extract the posterior samples
+# post-MCMC thinning allowed to reduce run time of this document
+if (params$thin_percent < 1) {
+  post = post_thin(model_info$post, keep_percent = params$thin_percent)
+} else {
+  post = model_info$post
+}
+
+# extract the model data 
 jags_data = model_info$jags_data

### 2022-01-25 03-post-process/output-plots.Rmd
Implement improved post-MCMC thinning in Rmds

@@
 title: "Output Summary"
-subtitle: "Multi-Population Model"
+subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
+date: "`r paste0('Date Rendered: ', Sys.Date())`"
 output: 
@@
     label: "Include Simulated Years on Plots?"
-    value: FALSE
+    value: TRUE
     input: checkbox
+  thin_percent:
+    label: "Proportion of Posterior Samples to Retain?"
+    value: 1
+    input: numeric
 editor_options: 
@@
 
-# extract the two key structures from this object
+# extract the posterior samples
+# post-MCMC thinning allowed to reduce run time of this document
+if (params$thin_percent < 1) {
+  post = post_thin(model_info$post, keep_percent = params$thin_percent)
+} else {
   post = model_info$post
-# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
+}
+
+# extract the model data 
 jags_data = model_info$jags_data

### 2022-01-25 03-post-process/compare-sim-to-obs.Rmd
Enable non-zero MIN HOR strays in simulated years

@@
 x = do.call(abind, append(x, list(along = 4)))
+x[x == "Inf"] = 1; x[x == "NaN"] = 1
 vals_plots(x, "Proportion Age-3 Return: Estimates")
@@
 x = do.call(abind, append(x, list(along = 4)))
+x[x == "Inf"] = 1; x[x == "NaN"] = 1
 vals_plots(x, "Proportion Age-4 Return: Estimates")
@@
 x = do.call(abind, append(x, list(along = 4)))
+x[x == "Inf"] = 1; x[x == "NaN"] = 1
 vals_plots(x, "Proportion Age-5 Return: Estimates")

### 2022-01-25 02-model/fit-model.R

@@ -161,7 +161,11 @@ if (ny_sim > 0) {
   }
   
   jags_data$not_stray_yrs = not_stray_yrs_new
+  jags_data$stray_yrs = rbind(jags_data$stray_yrs, matrix(NA, ny_sim, jags_data$nj))
+  jags_data$not_stray_yrs[,"MIN"] = NA
+  jags_data$stray_yrs[,"MIN"] = 2:jags_data$ny
   jags_data$n_not_stray_yrs = colSums(!is.na(jags_data$not_stray_yrs))
+  jags_data$n_stray_yrs = colSums(!is.na(jags_data$stray_yrs))
   
   # append hypothetical future sea lion survival (by population)
   SL_yrs = as.character(2001:2019)

### 2022-01-25 02-model/model-code.R

@@ -88,8 +88,12 @@ jags_model_code = function() {
     # the number of hatchery strays: only estimate in years where no other mechanism for generating hatchery fish
     for (i in 1:n_stray_yrs[j]) {
       G[stray_yrs[i,j],o_nor,j] <- 0
-      G[stray_yrs[i,j],o_hor,j] ~ dunif(0, 500)
+      G_random1[stray_yrs[i,j],o_hor,j] ~ dunif(0, 500)  # prior if an observed year
+      G_random2[stray_yrs[i,j],o_hor,j] ~ dunif(50, 150) # prior if a simulated year, only applies for MIN
+      G[stray_yrs[i,j],o_hor,j] <- ifelse(stray_yrs[i,j] <= ny_obs, G_random1[stray_yrs[i,j],o_hor,j], G_random2[stray_yrs[i,j],o_hor,j])
     }
+    
+    # force zero strays in years where they aren't needed
     for (o in 1:no) {
       for (i in 1:n_not_stray_yrs[j]) {
         G[not_stray_yrs[i,j],o,j] <- 0

### 2022-01-26 03-post-process/output-plots.Rmd
Create an origin variable to use instead of c("NOR", "HOR") throughout Rmd

@@
 
+# origin names
+origins = c("NOR", "HOR")
+
 # dimension IDs
@@
 bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), c("NOR", "HOR"), pops)
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
 bp = bp[,"spring-mig",,]
@@
   name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
-  origin = rep(c("NOR", "HOR"), 4), LH_type = rep("Spring Migrants", 8),
+  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
   summarize_bp(bp)
@@
 bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
 phi_Ma_O0_bp = data.frame(
   name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
-  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
+  origin = origins, LH_type = rep("Combined", 2),
   summarize_bp(bp)
@@
 bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
 x_LGR_bp = data.frame(
   name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
-  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
+  origin = origins, LH_type = rep("Combined", 2),
   summarize_bp(bp)

### 2022-01-26 02-model/fit-model.R
Update MCMC dimensions

@@ -302,11 +302,11 @@ if (do_lppd) jags_params = c(jags_params, lppd_params)
 ##### STEP 4: SELECT MCMC ATTRIBUTES #####
 
 jags_dims = list(
-  n_post = switch(mcmc_length,  "very_short" = 100, "short" = 2000, "medium" = 24000, "long" = 60000),
-  n_burn = switch(mcmc_length,  "very_short" = 5, "short" = 1000, "medium" = 20000, "long" = 60000),
-  n_thin = switch(mcmc_length,  "very_short" = 1,   "short" = 3,    "medium" = 8,     "long" = 20),
+  n_post = switch(mcmc_length,  "very_short" = 100, "short" = 2000, "medium" = 24000, "long" = 50000),
+  n_burn = switch(mcmc_length,  "very_short" = 5,   "short" = 1000, "medium" = 20000, "long" = 30000),
+  n_thin = switch(mcmc_length,  "very_short" = 1,   "short" = 3,    "medium" = 8,     "long" = 10),
   n_chain = switch(mcmc_length, "very_short" = 3,   "short" = 3,    "medium" = 3,     "long" = 3),
-  n_adapt = switch(mcmc_length, "very_short" = 10, "short" = 1000, "medium" = 1000,  "long" = 1000),
+  n_adapt = switch(mcmc_length, "very_short" = 10,  "short" = 1000, "medium" = 3000,  "long" = 3000),
   parallel = TRUE
 )
 
@@ -436,6 +436,7 @@ out_obj = list(
   do_pp_check = do_pp_check,
   jags_time = c(starttime = format(starttime), stoptime = format(stoptime), elapsed = format(round(stoptime - starttime,2))),
   post = post,
+  last_yr = last_yr,
   scenario = scenario
 )
 

### 2022-01-26 03-post-process/output-plots.Rmd
Add extensive residual diagnostics
And remove old process model residual diagnostics. This is much more detailed now, and is similar to how observation model residuals are diagnosed

@@
 
-## Process Noise Diagnostics
-
-The model assumes mean-zero process noise for all components.
-That is, the model has an expected value for each component in a given year, and it estimates deviations from this expected value to obtain the realized value in that year.
-Deviations from the expectation are assumed to be equally likely to be positive or negative for any given year.
-We can average the process noise components across years to check if it is close to zero.
-Large deviations from zero in the table below indicate a problem.
-
-```{r get-resids-fn}
-# a function to extract the posterior mean of all process model residuals for a single population
-get_resids = function(post, j) {
-
-  out = list(
-    egg_to_parr_surv = post_summ(post, sub_index("^Lphi_E_Pb_resid[.+,pop]", pop = j))["mean",],
-    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
-    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
-    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
-    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
-    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
-    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
-    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
-    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
-    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
-    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
-    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
-    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
-    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
-    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
-    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
-  )
-  out = do.call(cbind, out)
-  rownames(out) = NULL
-  out
-}
-```
-
-```{r make-mean-zero-resid-table}
-# extract posterior mean residual time series for each population
-resids = lapply(1:4, get_resids, post = diag_post)
-
-# convert to array format (list elements become matrix slices)
-resids = do.call(abind, append(resids, list(along = 3)))
-dimnames(resids)[[3]] = c("CAT", "LOS", "MIN", "UGR")
-
-# calculate the mean of each time series: these should be close to 0
-resid_means = t(sapply(1:dim(resids)[2], function(p) colMeans(resids[,p,])))
-rownames(resid_means) = dimnames(resids)[[2]]
-resid_means = round(resid_means, 3)
-
-# determine the phase of each process model component
-is_fw_juvn = rownames(resid_means) %in% c("egg_to_parr_surv", "p_fall_mig", "ow_surv_fall", "ow_surv_spring", "toLGR_surv_nor", "toLGR_surv_hor", "LGR_to_BON_surv_nor", "LGR_to_BON_surv_hor")
-is_sw_juvn = stringr::str_detect(rownames(resid_means), "ocean|mat")
-
-# determine the origin of each
-is_nor = stringr::str_detect(rownames(resid_means), "nor|egg_to_parr|p_fall|ow_surv")
-is_hor = stringr::str_detect(rownames(resid_means), "hor")
-
-# determine the process type: Life History (pi & psi) or Survival (phi)
-is_surv = stringr::str_detect(rownames(resid_means), "surv")
-
-# determine the migratory strategy: fall/spring/combined
-is_fall = stringr::str_detect(rownames(resid_means), "fall")
-is_spring = stringr::str_detect(rownames(resid_means), "spring")
-
-# build ID data frame
-resid_IDs = data.frame(
-  life_phase = ifelse(is_fw_juvn, "FW Juvenile", ifelse(is_sw_juvn, "SW Juvenile", "FW Adult")),
-  type = ifelse(is_surv, "Survival", "Life History"),
-  desc = c("Egg-to-Parr", "Strategy Apportionment", "Overwinter", "Overwinter", "Trib to LGR", "Trib to LGR",
-           "LGR to BON", "LGR to BON", "Yr1 Ocean", "Age-3 Maturity", "Age-3 Maturity", "Age-4 Maturity", "Age-4 Maturity",
-           "BON to LGR", "BON to LGR", "Pre-Spawn"),
-  origin = ifelse(is_nor, "NOR", ifelse(is_hor, "HOR", "Combined")), 
-  mig_type = ifelse(is_fall, "Fall Migrants", ifelse(is_spring, "Spring Migrants", "Combined"))
-)
-
-# combine IDs with mean residual values by population
-out = cbind(resid_IDs, resid_means)
-
-# build a kable
-kable(out, "html", row.names = FALSE, col.names = c("Life Phase", "Process Type", "Description", "Origin", "Migratory Strategy", colnames(resid_means))) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  collapse_rows(1:5)
-```
-
 # Fit to Data
@@
 
+# Residual Diagnostics {.tabset .tabset-pills}
+
+```{r misc-resid-fns}
+get_yr_index = function(params) {
+  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
+  yr_index = stringr::str_remove(yr_index, "\\[")
+  yr_index = stringr::str_remove(yr_index, ",")
+  as.numeric(yr_index)
+}
+
+make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
+  f = function(x) {
+    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
+    xs = round(xs, 2)
+    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
+  }
+  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
+}
+
+oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
+  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
+  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
+}
+
+no_data_plot = function(main = NULL) {
+  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
+  text(0,0, "No Data", font = 3)
+}
+
+my_par = function() {
+  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
+}
+```
+
+#### Why Does this Matter?
+
+This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
+Specifically, the noise (or "residual") terms should be:
+
+* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
+* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
+* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
+
+The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
+
+#### What was Calculated?
+
+To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
+
+Standardized residuals were calculated differently depending on the type of random process:
+
+* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
+* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
+* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
+
+For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
+For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
+
+This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
+The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
+
+#### What is Shown?
+
+For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
+To summarize these time series quantitatively, three across-year summary statistics are reported:
+
+* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
+* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
+* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
+
+These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
+They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
+`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
+
+## Process Model Noise Terms {.tabset .tabset-pills}
+
+```{r plot-proc-resid-fn}
+
+# function to plot a residual time series for one pop/origin/LH_type/age combo
+# returns a data frame with identifiers and across-year summary statistics
+plot_proc_resid = function(resid_param, sig_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+
+  # extract posterior samples of residual time series
+  resid_post = post_subset(post, sub_index(resid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
+
+  # extract posterior samples of st. dev. parameter
+  sig_post = post_subset(post, sub_index(sig_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
+
+  # divide each residual by its estimated SD parameterize: to standardize
+  resid_post = apply(resid_post, 2, function(x) x/sig_post)
+
+  # extract the year indices available
+  y_ind = get_yr_index(colnames(resid_post))
+  y_ind_obs = y_ind %in% observable
+
+  # calculate posterior across-year mean and sd for each posterior sample
+  # only for years that are observable; don't want to include any simulated years in these stats
+  mn_post = apply(resid_post[,y_ind_obs], 1, mean)
+  sd_post = apply(resid_post[,y_ind_obs], 1, sd)
+
+  # calculate posterior mean(last half of years) - mean(first half of years)
+  y_first = 1:round(length(y_ind[y_ind_obs])/2)
+  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
+  mn_post_first = apply(resid_post[,y_first], 1, mean)
+  mn_post_last = apply(resid_post[,y_last], 1, mean)
+  first_last_mn_diff_post = mn_post_last - mn_post_first
+
+  # calculate posterior summaries of standardized residual time series
+  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+
+  # set the y-axis limits: want zero in center and leave room at top for legend
+  ylim = max(abs(c(resid["2.5%",], resid["97.5%",])), na.rm = TRUE) * c(-1.4,1.4)
+
+  # blank plot with correct dimensions
+  par(lend = "square")
+  plot(resid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
+       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", xlab = "", ylab = "")
+
+  # draw x-axis: years
+  at_x = seq(min(all_yrs[y_ind]), max(all_yrs[y_ind]), 4)
+  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
+
+  # draw the noise time series: mean and 95% CRI
+  polygon(x = c(all_yrs[y_ind], rev(all_yrs[y_ind])),
+          y = c(resid["2.5%",], rev(resid["97.5%",])),
+          border = NA, col = alpha("salmon", 0.5))
+  lines(resid["mean",] ~ all_yrs[y_ind], lwd = 2, col = "red")
+  lines(resid["2.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")
+  lines(resid["97.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")
+
+  # draw reference line at zero noise
+  abline(h = 0, lty = 2, col = "black", lwd = 2)
+
+  # draw posterior mean for first and half of time series
+  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+
+  # draw legend that shows estimate summaries
+  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.01, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+
+  # create output for building summary tables
+  data.frame(param = resid_param,
+             pop = ifelse(!is.null(pop), pop, NA),
+             origin = ifelse(!is.null(origin), origin, NA),
+             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
+             age = ifelse(!is.null(age), age, NA),
+             n_yrs = ncol(resid_post[,y_ind %in% observable]),
+             year_mean_mean = mean(mn_post),
+             year_mean_lwr = unname(quantile(mn_post, 0.025)),
+             year_mean_upr = unname(quantile(mn_post, 0.975)),
+             year_sd_mean = mean(sd_post),
+             year_sd_lwr = unname(quantile(sd_post, 0.025)),
+             year_sd_upr = unname(quantile(sd_post, 0.975)),
+             diff_mean = mean(first_last_mn_diff_post), 
+             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
+             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
+             )
+
+}
+
+# container for across-year summary statistics
+# is rbinded many times for each random process and pop/origin/LH_type/age combo
+proc_error_ests = NULL
+```
+
+### FW Juvenile {.tabset .tabset-pills}
+
+#### Egg-to-Parr Survival
+
+```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_E_Pb_resid[year,pop]", "sig_Lphi_E_Pb[pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Migratory Strategy Apportionment
+
+```{r pi-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpi_resid[year,pop]", "sig_Lpi[pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Over-winter Survival {.tabset .tabset-pills}
+
+##### Fall Migrants
+
+```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 1, main = pops[j]))
+oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### Spring Migrants
+
+```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 2, main = pops[j]))
+oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Trib to LGR {.tabset .tabset-pills}
+
+##### NOR
+
+```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 1, main = pops[j]))
+oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 2, main = pops[j]))
+oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### LGR to BON Survival
+
+```{r LGR-to-BON-surv-noise, fig.width = 7, fig.height = 4}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Ma_O0_resid[year,origin]", "sig_Lphi_Ma_O0[origin]", origin = o, main = origins[o]))
+oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### SW Juvenile {.tabset .tabset-pills}
+
+#### Yr1 Ocean Survival
+
+```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_O0_O1_resid[year,origin,pop]", "sig_Lphi_O0_O1[pop]", origin = 1, year = c(1, ts_yrs), pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pr(Mature at age-3) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 2, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pr(Mature at age-4) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 2, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### FW Adult {.tabset .tabset-pills}
+
+#### BON to LGR Survival
+
+```{r BON-to-LGR-surv-noise, fig.width = 7, fig.height = 4}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Rb_Ra_resid[year,origin]", "sig_Lphi_Rb_Ra[origin]", origin = o, main = origins[o]))
+oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pre-spawn Survival
+
+```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Sb_Sa_resid[year,pop]", "sig_Lphi_Sb_Sa[pop]", pop = j, main = pops[j]))
+oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### **SUMMARY TABLES** {.tabset .tabset-pills}
+
+These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
+Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
+
+```{r proc-error-table-prep}
+# rename parameters to human-readable format
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_resid\\[year,origin\\]", "LGR to BON Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_resid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_resid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_resid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_resid\\[year,origin\\]", "BON to LGR Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_resid\\[year,pop\\]", "Pre-spawn Survival")
+
+# correct origin indices
+proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
+proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
+
+# correct LH_type indices
+proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
+
+# correct pop indices
+proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
+
+# remove the age column
+proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
+
+# replace indices with names
+proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
+proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
+proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
+
+# which processes are in each life phase?
+fw_juv = c("Egg to Parr Survival", "Migratory Strategy Apportionment", "Overwinter Survival", "Trib to LGR Survival", "LGR to BON Survival")
+sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
+fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
+
+# add a life phase column
+proc_error_ests$phase = NA
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
+proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
+
+# add levels to each variable
+proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
+proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
+proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
+proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
+proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
+
+# determine whether posterior of across-year quantities overlaps the target value
+proc_error_ests$yr_mean_incl_zero = ifelse(proc_error_ests$year_mean_lwr <= 0 & proc_error_ests$year_mean_upr >= 0, TRUE, FALSE)
+proc_error_ests$yr_sd_incl_one = ifelse(proc_error_ests$year_sd_lwr <= 1 & proc_error_ests$year_sd_upr >= 1, TRUE, FALSE)
+proc_error_ests$diff_incl_zero = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
+
+# format the mean values to present in table
+# round and make bold if target value not in interval
+proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
+proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_zero, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
+proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
+proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_one, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
+proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
+proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_zero, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
+
+# drop unneeded columns
+proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
+```
+
+```{r proc-error-table-fn}
+proc_error_table = function(var) {
+  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
+  out[is.na(out)] = ""
+
+  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
+    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    collapse_rows(columns = 1:4)
+}
+```
+
+#### Across-Year Mean
+
+The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
+* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
+* Above 0 indicate that the time series of noise terms was biased high relative the expected value
+
+```{r proc-error-mean-table}
+proc_error_table("year_mean_mean")
+```
+
+#### Across-Year SD
+
+The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
+
+Values:
+
+* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
+* Below 1 indicate that the time series of noise terms was less variable than expected
+* Above 1 indicate that the time series of noise terms was more variable than expected
+
+```{r proc-error-sd-table}
+proc_error_table("year_sd_mean")
+```
+
+#### Last Half Mean - First Half Mean
+
+The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
+* Below 0 indicate an overall declining time trend in noise terms
+* Above 0 indicate an overall increasing time trend in noise terms
+
+```{r proc-error-diff-table}
+proc_error_table("diff_mean")
+```
+
+## Observation Model Noise Terms {.tabset .tabset-pills}
+
+```{r plot-obs-resid-fn}
+
+obs_resid_yrs = all_yrs[c(1,observable)]
+
+# function to plot a residual time series for one pop/origin/LH_type/age combo
+# returns a data frame with identifiers and across-year summary statistics
+plot_obs_resid = function(resid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+
+  # extract posterior samples of residual time series
+  resid_post = post_subset(post, sub_index(resid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
+
+  # extract the year indices available
+  y_ind = get_yr_index(colnames(resid_post))
+
+  # calculate posterior across-year mean and sd for each posterior sample
+  mn_post = apply(resid_post, 1, mean)
+  sd_post = apply(resid_post, 1, sd)
+
+  # calculate posterior summaries of residual time series
+  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+
+  # place residuals at correct place in a time series
+  # ie., insert missing values
+  empty = matrix(NA, nrow = 5, ncol = length(obs_resid_yrs))
+  empty[,y_ind] = resid
+  resid = empty[,observable]
+  rownames(resid) = c("mean", "sd", "50%", "2.5%", "97.5%")
+  empty_names = rep(NA, length(obs_resid_yrs))
+  empty_names[y_ind] = colnames(resid_post)
+
+  # calculate posterior mean(last half of years) - mean(first half of years)
+  y_first = 1:round(length(observable)/2)
+  y_last = (max(y_first) + 1):length(observable)
+  i_first = as.character(na.omit(empty_names[y_first]))
+  i_last = as.character(na.omit(empty_names[y_last]))
+  mn_post_first = apply(resid_post[,i_first], 1, mean)
+  mn_post_last = apply(resid_post[,i_last], 1, mean)
+  first_last_mn_diff_post = mn_post_last - mn_post_first
+
+  # set the y-axis limits: want zero in center and leave room at top for legend
+  ylim = max(abs(c(resid["2.5%",], resid["97.5%",])), na.rm = TRUE) * c(-1.4,1.4)
+
+  # blank plot with correct dimensions
+  par(lend = "square")
+  plot(resid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "")
+
+  # draw x-axis: years
+  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
+  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
+
+  # draw the noise time series: mean and 95% CRI
+  segments(all_yrs[observable], resid["2.5%",], all_yrs[observable], resid["97.5%",], col = "red")
+  points(resid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+  # draw reference line at zero noise
+  abline(h = 0, lty = 2, col = "black", lwd = 2)
+
+  # draw posterior mean for first and half of time series
+  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+
+  # draw legend that shows estimate summaries
+  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.01, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+
+  # create output for building summary tables
+  data.frame(param = resid_param,
+             pop = ifelse(!is.null(pop), pop, NA),
+             origin = ifelse(!is.null(origin), origin, NA),
+             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
+             age = ifelse(!is.null(age), age, NA),
+             n_yrs = ncol(resid_post[,y_ind %in% observable]),
+             year_mean_mean = mean(mn_post),
+             year_mean_lwr = unname(quantile(mn_post, 0.025)),
+             year_mean_upr = unname(quantile(mn_post, 0.975)),
+             year_sd_mean = mean(sd_post),
+             year_sd_lwr = unname(quantile(sd_post, 0.025)),
+             year_sd_upr = unname(quantile(sd_post, 0.975)),
+             diff_mean = mean(first_last_mn_diff_post), 
+             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
+             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
+  )
+}
+
+# container for across-year summary statistics
+# is rbinded many times for each random process and pop/origin/LH_type/age combo
+obs_error_ests = NULL
+```
+
+### Abundance Data {.tabset .tabset-pills}
+
+#### Fall Parr Abundance
+
+```{r fall-trap-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lPa_obs_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Spring Smolt Abundance
+
+```{r spring-trap-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lMb_obs_resid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Spring Trap Count) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Adult Return Abundance
+
+```{r adult-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lRa_obs_resid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Return Year", "log(Total Adult Count) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+### Survival Data {.tabset .tabset-pills}
+
+#### Summer Parr $\rightarrow$ LGR
+
+```{r summer-surv-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pb_Ma_resid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Fall Parr $\rightarrow$ LGR
+
+```{r fall-surv-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Winter Parr $\rightarrow$ LGR
+
+```{r winter-surv-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) {
+  if (j == 3) {
+    no_data_plot(main = pops[j])
+  } else {
+    plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
+  }
+})
+oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Spring Smolt $\rightarrow$ LGR (NOR)
+
+```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
+oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Spring Smolt $\rightarrow$ LGR (HOR)
+
+```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) {
+  if (j == 3) {
+    no_data_plot(main = pops[j])
+  } else {
+    plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
+  }
+})
+oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### LGR Smolt $\rightarrow$ Ocean
+
+```{r hydro-surv-resid, fig.width = 7, fig.height = 4}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("Lphi_obs_Ma_O0_resid[year,origin]", origin = o, main = origins[o]))
+oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### BON Adults $\rightarrow$ LGR
+
+```{r bon-adult-surv-resid, fig.width = 7, fig.height = 4}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("x_LGR_obs_resid[year,origin]", origin = o, main = origins[o]))
+oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Pre-spawn
+
+```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("x_carcass_spawned_obs_resid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+### Composition Data {.tabset .tabset-pills}
+
+#### Weir Sampling {.tabset .tabset-pills}
+
+```{r weir-comp-resid-plots-fn}
+ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
+             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
+
+weir_comp_resid_plots = function(j) {
+  my_par(); par(mfrow = c(2,3))
+  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Ra_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
+  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
+  do.call(rbind, tmp)
+}
+```
+
+##### CAT
+
+```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
+tmp = weir_comp_resid_plots(j_cat)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+##### LOS
+
+```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
+tmp = weir_comp_resid_plots(j_los)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+##### MIN
+
+_No weir data for MIN_
+
+##### UGR
+
+```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
+tmp = weir_comp_resid_plots(j_ugr)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+#### Carcass Sampling {.tabset .tabset-pills}
+
+```{r carcass-comp-resid-plots-fn}
+carcass_comp_resid_plots = function(j) {
+  my_par(); par(mfrow = c(2,3))
+  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Sa_prime_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
+  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
+  do.call(rbind, tmp)
+}
+```
+
+##### CAT
+
+```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
+tmp = carcass_comp_resid_plots(j_cat)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+##### LOS
+
+```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
+tmp = carcass_comp_resid_plots(j_los)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+##### MIN
+
+```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
+tmp = carcass_comp_resid_plots(j_min)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+##### UGR
+
+```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
+tmp = carcass_comp_resid_plots(j_ugr)
+obs_error_ests = rbind(obs_error_ests, tmp)
+```
+
+### **SUMMARY TABLES** {.tabset .tabset-pills}
+
+These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
+Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
+
+```{r obs-error-table-prep}
+# rename parameters to human-readable format
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_resid\\[year,LH_type,pop\\]", "Fall Screw Trap")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_resid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_resid\\[year,pop\\]", "Adult Return")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_resid\\[year,pop\\]", "Summer Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_resid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_resid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_resid\\[year,origin\\]", "LGR Smolt -> Ocean")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_resid\\[year,origin\\]", "BON Adults -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_resid\\[year,pop\\]", "Pre-spawn")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_resid\\[year,age,pop\\]", "Weir")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_resid\\[year,age,pop\\]", "Carcass")
+
+# correct parameter names
+obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
+obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
+obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
+obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
+
+# correct origin indices
+obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
+obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
+
+# correct LH_type indices
+obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
+
+# correct pop indices
+obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
+
+# correct origin indices based on age indices
+obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
+obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
+
+# replace indices with names
+obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
+obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
+obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
+obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
+obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
+
+# add a type column
+obs_error_ests$type = NA
+obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
+obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
+obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
+obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
+obs_error_ests$type = c("Abundance", "Survival", "Composition")[obs_error_ests$type]
+
+# add levels to each variable
+obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Composition"))
+obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Weir", "Carcass"))
+obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
+obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
+obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
+obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
+
+# determine whether posterior of across-year quantities overlaps the target value
+obs_error_ests$yr_mean_incl_zero = ifelse(obs_error_ests$year_mean_lwr <= 0 & obs_error_ests$year_mean_upr >= 0, TRUE, FALSE)
+obs_error_ests$yr_sd_incl_one = ifelse(obs_error_ests$year_sd_lwr <= 1 & obs_error_ests$year_sd_upr >= 1, TRUE, FALSE)
+obs_error_ests$diff_incl_zero = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
+
+# format the mean values to present in table
+# round and make bold if target value not in interval
+obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
+obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_zero, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
+obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
+obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_one, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
+obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
+obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_zero, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
+
+# drop unneeded columns
+obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
+```
+
+```{r obs-error-table-fn}
+obs_error_table = function(var) {
+  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
+  out[is.na(out)] = ""
+  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
+
+  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
+    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    collapse_rows(columns = 1:5)
+}
+```
+
+#### Across-Year Mean
+
+The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
+* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
+* Above 0 indicate that the time series of noise terms was biased high relative the expected value
+
+```{r obs-error-mean-table}
+obs_error_table("year_mean_mean")
+```
+
+#### Across-Year SD
+
+The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
+
+Values:
+
+* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
+* Below 1 indicate that the time series of noise terms was less variable than expected
+* Above 1 indicate that the time series of noise terms was more variable than expected
+
+```{r obs-error-sd-table}
+obs_error_table("year_sd_mean")
+```
+
+#### Last Half Mean - First Half Mean
+
+The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
+* Below 0 indicate an overall declining time trend in noise terms
+* Above 0 indicate an overall increasing time trend in noise terms
+
+```{r obs-error-diff-table}
+obs_error_table("diff_mean")
+```
+
 # JAGS Model and Data {.tabset .tabset-pills}

### 2022-01-26 03-post-process/output-plots.Rmd
Improve MCMC diagnostics

@@
 
-## Diagnostic Summaries
+## Sampling Diagnostics {.tabset .tabset-pills}
 
@@
 }
+
+# discard duplicate correlation terms: all rho parameters for a given process are equal
+all_rho = match_params(post, "^rho")
+rho_keep = match_params(post, "^rho_.+[2,1")
+rho_discard = all_rho[!(all_rho %in% rho_keep)]
+diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
 ```
@@
 
-diag_fn = function(params, L1 = NA, L2 = NA, L3 = NA) {
-
+summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
   # extract the posteriors of interest and format for 'posterior' package
@@
   diags = diags[!is.na(diags$rhat),]
+
+  # append the level names and return
+  cbind(
+    L1 = L1, L2 = L2, L3 = L3,
+    diags
+  )
+}
+
+summarize_diags = function(diags) {
 
@@
   # summarize the summaries
-  out = data.frame(
-    L1 = L1,
-    L2 = L2,
-    L3 = L3,
-    match = params,
+  data.frame(
+    L1 = unique(diags$L1),
+    L2 = unique(diags$L2),
+    L3 = unique(diags$L3),
+    match = unique(postpack:::drop_index(diags$variable)),
     n_params = nrow(diags),
+    Rhat_1.01 = sum(diags$rhat >= 1.01),
     Rhat_1.05 = sum(diags$rhat >= 1.05),
@@
   )
-
-  # return the summarized summaries
-  return(out)
-}
-
+}
 ```
@@
 ```{r calculate-mcmc-diagnostics}
+# containers
+diags_out = NULL
+summs_out = NULL
+
 # parr recruitment
 L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
-match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
-parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
+match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
-pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = c("phi_Pb_Pa[2,.]")
-phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))
-
-# Overwinter survival
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Overwinter survival: Fall Migrants
 L1 = "Overwinter Survival"
@@
 match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Overwinter survival: Spring Migrants
+L1 = "Overwinter Survival"
+L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants")))
-phi_Pa_Mb_diags = rbind(tmp1, tmp2)
-
-# Migration survival: trib to LGR
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# trib to LGR Migration survival: NOR 
 L1 = "Migration Survival (Trib to LGR)"
@@
 match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# trib to LGR Migration survival: HOR 
+L1 = "Migration Survival (Trib to LGR)"
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-phi_Mb_Ma_diags = rbind(tmp1, tmp2)
-
-# Migration survival: LGR to BON
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# LGR to Ocean Migration survival: NOR
 L1 = "Migration Survival (LGR to Ocean)"
@@
 match = sub_index(base, year = ".+", origin = o_nor)
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# LGR to Ocean Migration survival: HOR
+L1 = "Migration Survival (LGR to Ocean)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
 match = sub_index(base, year = ".+", origin = o_hor)
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-tmp3 = diag_fn("rho_Lphi_Ma_O0[2,1]", L1 = "Migration Survival (LGR to Ocean)", L2 = "Among-origin Correlation")
-phi_Ma_O0_diags = rbind(tmp1, tmp2, tmp3)
-
-# Probability of Maturing at Age-3
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# LGR to Ocean Migration survival correlation among origins
+tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
+tmp_summ =  summarize_diags(tmp_diags)
+diags_out = rbind(diags_out, tmp_diags)
+summs_out = rbind(summs_out, tmp_summ)
+
+# Probability of Maturing at Age-3: NOR
 L1 = "Pr(Mature at Age-3)"
@@
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Probability of Maturing at Age-3: HOR
+L1 = "Pr(Mature at Age-3)"
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-psi_O1_diags = rbind(tmp1, tmp2)
-
-# Probability of Maturing at Age-4
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Probability of Maturing at Age-4: NOR
 L1 = "Pr(Mature at Age-4)"
@@
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Probability of Maturing at Age-4: HOR
+L1 = "Pr(Mature at Age-4)"
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-psi_O2_diags = rbind(tmp1, tmp2)
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = sub_index(base, pop = ".")
-misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
-
-# Migration survival: BON to LGR
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# BON to LGR Migration survival: NOR 
 L1 = "Migration Survival (BON to LGR)"
@@
 match = sub_index(base, year = ".+", origin = o_nor)
-tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# BON to LGR Migration survival: HOR 
+L1 = "Migration Survival (BON to LGR)"
+L2 = c("Mean", "Process SD", "Realized")
+base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
 match = sub_index(base, year = ".+", origin = o_hor)
-tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
-tmp3 = diag_fn("rho_Lphi_Rb_Ra[2,1]", L1 = "Migration Survival (BON to LGR)", L2 = "Among-origin Correlation")
-phi_Rb_Ra_diags = rbind(tmp1, tmp2)
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# LGR to Ocean Migration survival correlation among origins
+tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
+tmp_summ =  summarize_diags(tmp_diags)
+diags_out = rbind(diags_out, tmp_diags)
+summs_out = rbind(summs_out, tmp_summ)
 
@@
 match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
-phi_Sb_Sa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-G_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))
-
-# combine diagnostic summaries into one massive table
-diags_table = rbind(
-  parr_recruit_diags,
-  pi_diags,
-  phi_Pb_Pa_diags,
-  phi_Pa_Mb_diags,
-  phi_Mb_Ma_diags,
-  phi_Ma_O0_diags,
-  psi_O1_diags,
-  psi_O2_diags,
-  phi_O0_O1_diags,
-  phi_O1_O2_diags,
-  phi_Rb_Ra_diags,
-  phi_Sb_Sa_diags,
-  misc_ocean_surv_diags,
-  z_diags,
-  init_diags,
-  G_diags
-)
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
@@
 # e.g., if that "parameter" takes on a fixed value in the model
+diags_table = summs_out
 diags_table = diags_table[diags_table$n_params > 0,]
 ```
+
+### Summary Table
 
@@
 Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had Rhat values greater than 1.05.
+E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
 Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
 
-* **Rhat** measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should not be used for inference (general rules).
+* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
+Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
 * **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
@@
 
-```{r mcmc-diag-table}
+```{r mcmc-diag-table, warning = FALSE}
 # duplicate the diagnostic output
@@
 # convert counts of offending parameters to percentages
+kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
 kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
@@
 # add basic formatting
-colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
+colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
 kable_table$Group[is.na(kable_table$Group)] = " "
@@
   names(cols) = bin_names
+  x[is.na(x)] = 0
   bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
@@
 kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("striped", "condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 3, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
+  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
+  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
   column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,7,10), border_right = TRUE) %>%
+  column_spec(c(4,8,11), border_right = TRUE) %>%
   column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
@@
   column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
+  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
   collapse_rows(columns = 1:2)
+```
+
+### Figures {.tabset .tabset-pills}
+
+```{r mcmc-diag-plots-prep}
+n_max_draw = 30
+
+# which parameters fall in each Rhat bin
+rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
+rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
+rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
+
+# extract the Rhat values and the names of the parameters with the 
+# worst Rhat values by bin
+rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
+rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
+rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
+rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
+rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
+rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]
+
+# subset out these parameters: makes postpack::diag_plots() much faster
+post_sub_1 = post_subset(post, rhat_1_params_draw)
+post_sub_2 = post_subset(post, rhat_2_params_draw)
+post_sub_3 = post_subset(post, rhat_3_params_draw)
+
+# function to plot a histogram of rhat values
+rhat_hist = function(rhat) {
+  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
+  breaks = seq(min(rhat), max(rhat), length = 20)
+  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
+  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
+  usr = par("usr")
+  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
+  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
+}
+```
+
+#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
+
+##### Distribution
+
+There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
+
+```{r rhat-hist-1, fig.width = 6, fig.height = 4}
+rhat_hist(rhat_1)
+```
+
+##### Least Converged
+
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+
+```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
+diag_plots(post_sub_1, "", show_diags = "never")
+```
+
+#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
+
+##### Distribution
+
+There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
+
+```{r rhat-hist-2, fig.width = 6, fig.height = 4}
+rhat_hist(rhat_2)
+```
+
+##### Least Converged
+
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+
+```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
+diag_plots(post_sub_2, "", show_diags = "never")
+```
+
+#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
+
+##### Distribution
+
+There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
+
+```{r rhat-hist-3, fig.width = 6, fig.height = 4}
+rhat_hist(rhat_3)
+```
+
+##### Least Converged
+
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+
+```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
+diag_plots(post_sub_3, "", show_diags = "never")
 ```

### 2022-01-26 03-post-process/compare-sim-to-obs.Rmd
Fix misc typos in Rmds

@@
 
-  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 3)
+  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 100)
   bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))

### 2022-01-26 03-post-process/output-plots.Rmd
Fix misc typos in Rmds

@@
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
+  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
                get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j])
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
 }
@@
   plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
   mtext(side = 1, outer = T, line = 0.25, "Return Year")
@@
   if (j == 1) {
-    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
+    legend("topright", legend = origins, title = "Origin",
          pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
@@
 par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
-my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
+my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
 my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
@@
 par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
-my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
+my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
+my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
 my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
@@
 
-```{r rho_plot, fig.width = 6, fig.height = 8}
+```{r rho_plot, fig.width = 6, fig.height = 7}
 # get the names of all rho parameters
@@
   "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_Lpi[2,1]" = "Mig. Stategy Apportionment",
+  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
   "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",

### 2022-01-26 03-post-process/output-plots.Rmd
Update text for pp checks - using Freeman-Tukey now

@@
 * **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
-* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, expect pre-spawn survival which used a binomial distribution.
-* **Binomial/Multinomial**: chi-squared fit statistic. This applies to all composition data and the pre-spawn survival data.
+* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation.
+This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
+* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
+This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
 

### 2022-01-31 03-post-process/compare-sim-to-obs.Rmd
Update scenario name

@@
     label: "Scenario"
-    value: "base"
+    value: "size-based-surv"
     input: text

### 2022-01-31 02-model/fit-model.R

@@ -27,7 +27,7 @@ do_pp_check = TRUE
 do_lppd = FALSE
 
 # specify a scenario name
-scenario = "base"
+scenario = "size-based-surv"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE

### 2022-02-18 03-post-process/output-plots.Rmd
Update output plots for new model

@@
 
+# summer parr mean length
+L1 = "Density-Dependent Summer Length"
+L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
+match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
 # LH apportionment
@@
 
+# growth from summer to spring
+# summer parr mean length
+L1 = "Summer to Spring Growth"
+L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
+match = c("mu_growth", "sig_lgrowth", "rho_lgrowth", "^growth[")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
 # trib to LGR Migration survival: NOR 
 L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
+L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
+base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
+match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
@@
 # Year 2 ocean survival
-L1 = "Year 2&3 Ocean Survival"
+L1 = "Year 2 Ocean Survival"
 L2 = c("Mean")
@@
 
+# Year 2 ocean survival
+L1 = "Year 3 Ocean Survival"
+L2 = c("Mean")
+base = c("mu_phi_O2_O3[origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
 # Misc ocean survival
 L1 = "Misc Ocean Survival"
-L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
-base = c("delta[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
+L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
+base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
 match = sub_index(base, pop = ".")
@@
 # spring trap
-new = post_subset(post, "Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "Mb_obs_dev", TRUE)
+new = post_subset(post, "^Mb_obs_new_dev", TRUE)
+obs = post_subset(post, "^Mb_obs_dev", TRUE)
 bp = array_format(colMeans(obs > new))
@@
 
+### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###
+
+# summer length
+new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
+obs = post_subset(post, "L_Pb_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+L_Pb_bp = data.frame(
+  name = rep("Summer Length", 4), pop = pops,
+  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(L_Pb_bp) = NULL
+
+# spring length
+new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
+obs = post_subset(post, "L_Mb_obs_dev", TRUE)
+bp = array_format(colMeans(obs > new))
+dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
+L_Mb_bp = data.frame(
+  name = rep("Spring Length", 4), pop = pops,
+  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
+  summarize_bp(bp)
+)
+rownames(L_Mb_bp) = NULL
+
 ### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
@@
   phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
+  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
 )
@@
 category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
+category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
 category[is.na(category)] = "Survival"
@@
 
+## Length Data {.tabset .tabset-pills}
+
+### Mean Length at Summer Tagging
+
+```{r summer-length-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
+```
+
+### Mean Length at Spring Tagging
+
+```{r spring-length-fit, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
+```
+
 # Spawner-to-Parr Relationship {.tabset .tabset-pills}
@@
 
-# Overwinter Survival Relationships
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j) {
-  # extract parr, scale it to WUL, and create new post object
-  Pa = post_subset(post, sub_index("^Pa[year,.,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  Pa_scaled = Pa/jags_data$wul[j]
-  colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
-  post_pa = post_convert(cbind(postpack:::id_mat(post), Pa_scaled))
-
-  # summarize posterior of scaled parr
-  Pa_scaled_mean = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["mean",])
-  Pa_scaled_lwr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["2.5%",])
-  Pa_scaled_upr = array_format(post_summ(post_pa, sub_index("Pa_scaled[.+,.+,pop]", pop = j))["97.5%",])
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  Pa_scaled_seq = matrix(NA, 30, 2)
-  Pa_scaled_seq[,i_fall] = seq(min(Pa_scaled_lwr[,i_fall,j], na.rm = TRUE), max(Pa_scaled_upr[,i_fall,j], na.rm = T), length = 30)
-  Pa_scaled_seq[,i_spring] = seq(min(Pa_scaled_lwr[,i_spring,j], na.rm = TRUE), max(Pa_scaled_upr[,i_spring,j], na.rm = T), length = 30)
+# Length Relationships {.tabset .tabset-pills}
+
+## Summer Tagging
+
+```{r}
+plot_f = function(j) {
+
+  # obtain posterior samples of total egg abundance scaled to WUL
+  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
+  E_scaled = (E/10000)/jags_data$wul[j]
+  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
+  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
+
+  # summarize scaled egg abundance
+  E_scaled_mean = post_summ(post_E, "")["mean",]
+  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
+  E_scaled_upr = post_summ(post_E, "")["97.5%",]
+
+  # create a vector of scaled egg abundances to calculate at
+  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
 
   # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[.,pop]", pop = j), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[.,pop]", pop = j), matrix = TRUE)
-
-  # extract/format posterior summaries of realized survivals
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["mean",])
-  phi_Pa_Mb_lwr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["2.5%",])
-  phi_Pa_Mb_upr = array_format(post_summ(post,  sub_index("^phi_Pa_Mb[year,.+,pop]", pop = j, year = ts_yrs))["97.5%",])
+  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
+  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
 
@@
   pred_fn = function(i) {
-    pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
-    pred_phi_Pa_Mb2 = plogis(gamma0[i,2] + gamma1[i,2] * Pa_scaled_seq[,2])
-
-    names(pred_phi_Pa_Mb1) = paste0("pred_phi_Pa_Mb[", 1:30, ",1]")
-    names(pred_phi_Pa_Mb2) = paste0("pred_phi_Pa_Mb[", 1:30, ",2]")
-
-    c(pred_phi_Pa_Mb1, pred_phi_Pa_Mb2)
+    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
+    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
+    pred_L_Pb
+  }
+
+  # calculate predicted survivals and add to posterior samples
+  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
+
+  # extract summarize predicted length
+  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
+  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
+  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
+
+  # make a blank plot with the correct dimensions
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+
+  plot(1,1, type = "n", 
+       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
+       xlim = range(0, E_scaled_seq), 
+       main = pops[j]
+  )
+
+  # expected relationship
+  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
+  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
+  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
+  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
+  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Eggs/WUL")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
+```
+
+## Spring Length {.tabset .tabset-pills}
+
+### Spring vs. Summer Length
+
+```{r}
+plot_f = function(j) {
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # create a vector of scaled egg abundances to calculate at
+  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+
+  # extract posteriors of coefficients
+  mu_growth = post_subset(post, sub_index("mu_growth[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted survival curves for one posterior sample
+  pred_fn = function(i) {
+    pred_L_Mb = L_Pb_seq * mu_growth[i]
+    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "1]")
+    pred_L_Mb
+  }
+
+  # calculate predicted survivals and add to posterior samples
+  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
+
+  # extract summarize predicted length
+  pred_L_Mb_mean = post_summ(post_pred_L_Mb, "")["mean",]
+  pred_L_Mb_lwr = post_summ(post_pred_L_Mb, "")["2.5%",]
+  pred_L_Mb_upr = post_summ(post_pred_L_Mb, "")["97.5%",]
+
+  # make a blank plot with the correct dimensions
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot(1,1, type = "n", 
+       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
+       xlim = range(L_Pb_seq), 
+       main = pops[j]
+  )
+
+  # expected relationship
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
+  points(L_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Spring\\,Tagging\\,(mm)$"))
+```
+
+### Growth Rate
+
+```{r}
+plot_f = function(j) {
+
+  growth_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j],
+                     lwr95 = NA, upr95 = NA)
+
+  plot_tseries(post_summ(post, sub_index("^growth[year,pop]$", year = ts_yrs, pop = j)),
+               growth_obs,
+               main = pops[j],
+               yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\Growth$"))
+```
+
+# Length-Based Survival Relationships {.tabset .tabset-pills}
+
+## Overwinter Survival
+
+```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
+plot_fn = function(j, i) {
+
+  # extract posterior summaries of spring length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # summarize posterior of overwinter survival outcomes
+  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
+  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
+  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
+
+  # create vectors to predict survival at: for credible regions and mean curve
+  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+
+  # extract posteriors of coefficients
+  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_seq)
+    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
+    pred_phi_Pa_Mb
   }
@@
   pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pa = post_bind(post_pa, pred_phi_Pa_Mb)
-
-  # summarize predicted survivals
-  pred_phi_Pa_Mb_mean = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["mean",])
-  pred_phi_Pa_Mb_lwr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["2.5%",])
-  pred_phi_Pa_Mb_upr = array_format(post_summ(post_pa, "pred_phi_Pa_Mb")["97.5%",])
-
-  # function to draw plot for one LH-type
-  plot_fn2 = function(i) {
-    # blank plot of correct dimensions
+  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
+
+  # extract summarize predicted length
+  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
+  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
+  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
+
+  # make a blank plot with the correct dimensions
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
   plot(1,1, type = "n", 
-         ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i,j], phi_Pa_Mb_upr[,i,j], na.rm = T),
-         xlim = range(0, Pa_scaled_seq), 
+       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
+       xlim = range(L_Pb_seq), 
        main = ifelse(i == 1, pops[j], "")
@@
   # expected relationship
-    polygon(c(Pa_scaled_seq[,i], rev(Pa_scaled_seq[,i])), c(pred_phi_Pa_Mb_lwr[,i], rev(pred_phi_Pa_Mb_upr[,i])), border = NA, col = alpha("salmon", 0.5))
-    lines(pred_phi_Pa_Mb_lwr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
-    lines(pred_phi_Pa_Mb_upr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
-    lines(pred_phi_Pa_Mb_mean[,i] ~ Pa_scaled_seq[,i], col = "red", lwd = 2)
-
-    # realized survivals
-    segments(Pa_scaled_lwr[,i,j], phi_Pa_Mb_mean[,i,j], Pa_scaled_upr[,i,j], phi_Pa_Mb_mean[,i,j], col = alpha("red", 0.5))
-    segments(Pa_scaled_mean[,i,j], phi_Pa_Mb_lwr[,i,j], Pa_scaled_mean[,i,j], phi_Pa_Mb_upr[,i,j], col = alpha("red", 0.5))
-    points(phi_Pa_Mb_mean[,i,j] ~ Pa_scaled_mean[,i,j], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  }
-
-  # create the plot
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
+  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+}
+
+plot_fn2 = function(j) {
+    # create the plots for both migratory strategies
+  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
+  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
+}
+
+par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
+junk = sapply(1:jags_data$nj, plot_fn2)
+mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
+mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
+```
+
+## Migration to LGR
+
+```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
+plot_fn = function(j, i) {
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # summarize posterior of migration survival outcomes
+  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
+  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
+  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
+
+  # create vectors to predict survival at: for credible regions and mean curve
+  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
+
+  # extract posteriors of coefficients
+  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
+  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_seq)
+    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
+    pred_phi_Mb_Ma
+  }
+
+  # calculate predicted survivals and add to posterior samples
+  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
+
+  # extract summarize predicted length
+  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
+  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
+  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
+
+  # make a blank plot with the correct dimensions
   par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn2(1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn2(2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
+  plot(1,1, type = "n", 
+       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
+       xlim = range(L_Mb_seq), 
+       main = pops[j]
+  )
+
+  # expected relationship
+  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
+  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
+  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
+  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, line = 1.5, outer = T, "LH-Specific Parr/WUL", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
+mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
+mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
 ```
@@
 
+## Summer Parr Size
+
+```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
+par(mfrow = c(1,4))
+my_boxplot("^omega0[.]$", "Intercept")
+my_boxplot("^omega1[.]$", "Slope")
+my_boxplot("^sig_lL_Pb[.]$", "Process SD")
+my_boxplot("^rho_lL_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
+```
+
 ## Life History Apportionment
@@
 
-### Mean
+### Mean/Logistic Model Parameters
 
 ```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_nor, pop = "."), "Average Migration Survival", main = "NOR", ylim = c(0,1))
+par(mfrow = c(1,3))
+my_boxplot(sub_index("tau0[pop]", pop = "."), "Intercept", main = "NOR", ylim = c(0,1))
+my_boxplot(sub_index("tau1[pop]", pop = "."), "Slope", main = "NOR", ylim = c(0,1))
 my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
@@
 
-**NOTE:** The Year 3 parameters are the same as the Year 2 parameters.
-
 ```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
@@
 
-### NOR:HOR Log Odds Ratio
+### NOR:HOR Log Odds Ratios
 
 ```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-my_boxplot(sub_index("delta[pop]", pop = "."), ylab = "Log Odds Ratio")
+par(mfrow = c(1,3))
+my_boxplot(sub_index("delta_O0_O1[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 1")
+my_boxplot(sub_index("delta_O1_O2[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 2")
+my_boxplot(sub_index("delta_O2_O3[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 3")
 ```
@@
   "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
+  "rho_lL_Pb[2,1]" = "Summer Mean Length",
+  "rho_lgrowth[2,1]" = "Summer to Spring Growth",
   "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
@@
 
+#### Summer Parr Mean Length
+
+```{r summer-length-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lL_Pb_resid[year,pop]", "sig_lL_Pb[pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
 #### Migratory Strategy Apportionment
@@
 
+#### Summer Parr to Spring Smolt Growth
+
+```{r growth-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lgrowth_resid[year,pop]", "sig_lgrowth[pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Summer to Spring Growth) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
 #### Trib to LGR {.tabset .tabset-pills}
@@
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_resid\\[year,pop\\]", "Summer Parr Length")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lgrowth_resid\\[year,pop\\]", "Summer to Spring Growth")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
@@
 # which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Migratory Strategy Apportionment", "Overwinter Survival", "Trib to LGR Survival", "LGR to BON Survival")
+fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring Growth", "Trib to LGR Survival", "LGR to BON Survival")
 sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
@@
 
+### Length Data {.tabset .tabset-pills}
+
+#### Summer Length
+
+```{r summer-length-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Pb_obs_resid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Mean Summer Length) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Spring Length
+
+```{r spring-length-resid, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Mb_obs_resid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Mean Spring Length) Residual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
 ### Composition Data {.tabset .tabset-pills}
@@
 obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_resid\\[year,pop\\]", "Pre-spawn")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_resid\\[year,pop\\]", "Summer Parr")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_resid\\[year,pop\\]", "Spring Smolt")
 obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_resid\\[year,age,pop\\]", "Weir")
@@
 obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
+obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
 
@@
 obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition")[obs_error_ests$type]
+obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
+obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
 
 # add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Weir", "Carcass"))
+obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
+obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
 obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))

### 2022-02-19 02-model/model-code.R
Update priors for surv-vs-length coefficients

@@ -29,8 +29,8 @@ jags_model_code = function() {
     # gamma0: LH-specific intercepts
     # gamma1: LH-common slopes
     for (i in 1:ni) {
-      gamma0[i,j] ~ dnorm(0, 1e-3)
-      gamma1[i,j] ~ dnorm(0, 1e-3)
+      gamma0[i,j] ~ dt(0, 1/1.566^2, 7.763)
+      gamma1[i,j] ~ dt(0, 1/1.566^2, 7.763)
       sig_Lphi_Pa_Mb[i,j] ~ dunif(0, 5)
     }
     # gamma1[i_fall,j] ~ dnorm(0, 1e-3)
@@ -43,8 +43,8 @@ jags_model_code = function() {
 
     # size-dependent NOR migration to LGR survival
     # assumed equal among migration types
-    tau0[j] ~ dnorm(0, 1e-3)
-    tau1[j] ~ dnorm(0, 1e-3)
+    tau0[j] ~ dt(0, 1/1.566^2, 7.763)
+    tau1[j] ~ dt(0, 1/1.566^2, 7.763)
     sig_Lphi_Mb_Ma[o_nor,j] ~ dunif(0, 5)
     
     # hatchery origin movement survival (trib to LGD): have spring migrants only

### 2022-02-19 02-model/fit-model.R
Add scaling and centering constants to jags_data

@@ -27,7 +27,7 @@ do_pp_check = TRUE
 do_lppd = FALSE
 
 # specify a scenario name
-scenario = "size-based-surv"
+scenario = "size-based-surv-scaled"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -102,6 +102,15 @@ add_jags_data = append(add_jags_data, list(first_x_LGR = min(which(!is.na(jags_d
 
 # set upper boundaries for early Rb states
 add_jags_data = append(add_jags_data, list(max_Rb_init = c(50, 200, 200)))
+
+# add variables to scale and center quantities used in regressions
+add_jags_data = append(add_jags_data, list(
+  E_scale = 10000,
+  L_Pb_center = apply(jags_data$L_Pb_obs, 2, mean, na.rm = TRUE),
+  L_Pb_scale = apply(jags_data$L_Pb_obs, 2, sd, na.rm = TRUE),
+  L_Mb_center = apply(jags_data$L_Mb_obs, 2, mean, na.rm = TRUE),
+  L_Mb_scale = apply(jags_data$L_Mb_obs, 2, sd, na.rm = TRUE)
+))
 
 # append all of this additional content to the data object
 jags_data = append(jags_data, add_jags_data)

### 2022-02-19 03-post-process/output-plots.Rmd
Update output plots to handle scaling/centering

@@
     label: "Include Simulated Years on Plots?"
-    value: TRUE
+    value: FALSE
     input: checkbox
@@
   E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/10000)/jags_data$wul[j]
+  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
   colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
@@
 
+xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
 par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Eggs/WUL")
+mtext(side = 1, outer = T, line = 0.25, xlab)
 mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
@@
 
+  # obtain scaled/centered versions
+  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
   # summarize posterior of overwinter survival outcomes
@@
   L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)
 
@@
   pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_seq)
+    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
     names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
@@
 
+  # obtain scaled/centered versions
+  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
+  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
+  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
+
   # summarize posterior of migration survival outcomes
@@
   L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
+  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
 
@@
   pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_seq)
+    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
     names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")

### 2022-03-18 100-math-description/GR-sslcm-math-description.Rmd
Fix typo found in index table footnotes

@@
 However, for fitting to compositional data by age and origin, we collapse these two dimensions into one such that a single vector of proportions can represent the composition by age and origin.
-$k \\\\in [1,2,3]$ represents age-3, age-4, and age-5 for natural-origin fish, respectively, and $k \\\\in [4,5,6]$ represents these same ages for hatchery-origin fish, respectively."
+$ko \\\\in [1,2,3]$ represents age-3, age-4, and age-5 for natural-origin fish, respectively, and $ko \\\\in [4,5,6]$ represents these same ages for hatchery-origin fish, respectively."
 )

### 2022-03-18 100-math-description/GR-sslcm-math-description.Rmd
Switch output type to bookdown::pdf_document2

@@
 output: 
-  pdf_document:
+  bookdown::pdf_document2:
     keep_tex: false

### 2022-03-18 100-math-description/GR-sslcm-math-description.Rmd
Change all table tables from XXX_table to XXX-table
bookdown doesn't like underscores in cross reference names for some reason

@@
 The model is framed in the Bayesian mode of inference, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
-Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \ref{tab:param_table}).
+Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \ref{tab:param-table}).
 A final benefit of using the Bayesian framework is the seamless propagation of uncertainty from directly estimated parameters to derived quantities (of which there are many) -- all unknown quantities, either estimated parameters or deterministic functions of estimated parameters, receive a posterior distribution in the Bayesian framework.
@@
 In our mathematical representation of quantities in the model, we have striven for consistency, but this has created somewhat non-intuitive conventions which require devoted explanation.
-All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \ref{tab:index_table}, \ref{tab:symbol_table}, \ref{tab:param_table}, and \ref{tab:data_table} for reference and a catalog of all equations is provided in Table \ref{tab:equation_table}.
+All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \ref{tab:index-table}, \ref{tab:symbol-table}, \ref{tab:param-table}, and \ref{tab:data-table} for reference and a catalog of all equations is provided in Table \ref{tab:equation-table}.
 
@@
 \end{equation}
-Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \ref{tab:param_table}) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
+Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \ref{tab:param-table}) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
 \ref{eq:generic-Sigma4by4} and \ref{eq:generic-Sigma2by2}.
@@
 We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same deterministic value each year (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
-We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \ref{tab:param_table}).
+We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \ref{tab:param-table}).
 To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
@@
 This is because the life cycle dynamics must start somewhere, and no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
-Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \ref{tab:param_table}) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
+Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \ref{tab:param-table}) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
 Initial abundance of hatchery-origin returns was handled by the "straying model", described below.
@@
 
-No data sources were used to inform ocean juvenile population dynamics -- estimation of these quantities was enabled by (_i_) reasonably precise information about the abundance and composition of fish entering the ocean and returning to natal tributaries, (_ii_) the simplifying assumptions described above (i.e., time-constant second and third year ocean survival and perfectly correlated but offset origin-specific survival), and (_iii_) through the use of reasonably strong priors for second and third year ocean survival (Table \ref{tab:param_table}).
+No data sources were used to inform ocean juvenile population dynamics -- estimation of these quantities was enabled by (_i_) reasonably precise information about the abundance and composition of fish entering the ocean and returning to natal tributaries, (_ii_) the simplifying assumptions described above (i.e., time-constant second and third year ocean survival and perfectly correlated but offset origin-specific survival), and (_iii_) through the use of reasonably strong priors for second and third year ocean survival (Table \ref{tab:param-table}).
 
@@
 
-```{r index_table}
+```{r index-table}
 # read in csv version of table
@@
 symbol_tab_cap = "The symbology used to represent the key states (i.e., abundance at life stage/group) and rates (i.e., transition probabilities among states) in the presentation of the state-space life cycle model for Grande Ronde spring Chinook salmon.
-The majority of rates presented in this table are hierarchically structured/estimated, where the population- and/or origin-specific expected value and standard deviation are free parameters (or a function of free parameters) presented in Table \\ref{tab:param_table}.
+The majority of rates presented in this table are hierarchically structured/estimated, where the population- and/or origin-specific expected value and standard deviation are free parameters (or a function of free parameters) presented in Table \\ref{tab:param-table}.
 Equation numbers reference any equation that uses that quantity -- these may include the equation where the quantity is first defined, where it is used in process model, or where it is used in the observation model."
@@
 
-```{r symbol_table}
+```{r symbol-table}
 tab = read.csv("02-symbols.csv", allowEscapes = TRUE)
@@
 
-```{r param_table}
+```{r param-table}
 tab = read.csv("03-params.csv", allowEscapes = TRUE)
@@
 
-```{r data_table}
+```{r data-table}
 tab = read.csv("04-data.csv", allowEscapes = TRUE)
@@
 
-```{r equation_table}
+```{r equation-table}
 tab = read.csv("05-equations.csv", allowEscapes = TRUE)

### 2022-03-18 100-math-description/GR-sslcm-math-description.Rmd
Replace all \ref{} with \@ref()
This is general bookdown syntax and renders to word, HTML, and PDF

@@
 The model is framed in the Bayesian mode of inference, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
-Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \ref{tab:param-table}).
+Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \@ref(tab:param-table)).
 A final benefit of using the Bayesian framework is the seamless propagation of uncertainty from directly estimated parameters to derived quantities (of which there are many) -- all unknown quantities, either estimated parameters or deterministic functions of estimated parameters, receive a posterior distribution in the Bayesian framework.
@@
 
-We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \ref{fig:diagram}): freshwater juvenile, ocean juvenile, and freshwater adult.
+We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \@ref(fig:diagram)): freshwater juvenile, ocean juvenile, and freshwater adult.
 For each life phase, we describe the process model dynamics as a set of stochastic and deterministic processes followed by how they are informed by empirical data as part of the observation model.
@@
 \ref{eq:generic-Sigma4by4} and \ref{eq:generic-Sigma2by2}.
+Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \@ref(tab:param-table)) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
+\@ref(eq:generic-Sigma4by4) and \@ref(eq:generic-Sigma2by2).
 
@@
 
-Total egg production is the sum product of age-specific spawner abundance (from eq. \ref{eq:get-Sa}, below), proportion female, and fecundity:
+Total egg production is the sum product of age-specific spawner abundance (from eq. \@ref(eq:get-Sa), below), proportion female, and fecundity:
 \begin{equation}
@@
 Realized (i.e., with process noise) egg-to-parr survival was a multivariate logit-normal random variable around the deterministic value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) predicted by the Beverton-Holt function in eq.
-\ref{eq:get-phi-E-Pb-dot} with covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:get-phi-E-Pb-dot) with covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 For fall migrants, this proportion was a multivariate logit-normal random variable around a time-constant mean ($\dot{\pi}_{i = \mathrm{fall},j}$) with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$ (constructed of $\sigma_{\pi_{i=\mathrm{fall},j}}$ and $\rho_{\pi_{i=\mathrm{fall}}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 Overwinter survival from the end of the parr year (i.e., age-1) to the start of the smolt year (i.e., age-2), denoted by $\phi^{P^{a} \rightarrow M^{b}}_{y,i,j}$, was modeled as a logit-linear function of parr density (scaled to the same metric of weighted usable habitat length [$\mathrm{WUL}_j$] used in eq.
-\ref{eq:beta-random}).
+\@ref(eq:beta-random)).
 Deterministic overwinter survival was:
@@
 Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 We assume that year-specific realized survival values were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{b} \rightarrow M^{a}}_{o,j}$) with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}$ (constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{o,j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}_{o}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 We assumed these survival rates were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$ (constructed of $\sigma_{\phi^{M^{a} \rightarrow O^{0}}_{o}}$ and $\rho_{\phi^{M^{a} \rightarrow O^{0}}}$ following eq.
-\ref{eq:generic-Sigma2by2}):
+\@ref(eq:generic-Sigma2by2)):
 \begin{equation}
@@
 Note the summation across migratory strategies ($i$) in eq.
-\ref{eq:get-O0}, which indicates that the fates of fish with these different strategies were assumed to be the result of identical processes following arrival to LGR.
+\@ref(eq:get-O0), which indicates that the fates of fish with these different strategies were assumed to be the result of identical processes following arrival to LGR.
 
@@
 First year natural-origin ocean survival was assumed to be a multivariate logit-normal random variable around a time-constant and density-independent deterministic value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$ (constructed of $\sigma_{\phi^{O^{0} \rightarrow O^{1}}_{j}}$ and $\rho_{\phi^{O^{0} \rightarrow O^{1}}}$ following eq.
-\ref{eq:generic-Sigma4by4}), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion (all $o=\mathrm{NOR}$ in eq.
-\ref{eq:phi-O0-O1-random}, omitted for brevity):
+\@ref(eq:generic-Sigma4by4)), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion (all $o=\mathrm{NOR}$ in eq.
+\@ref(eq:phi-O0-O1-random), omitted for brevity):
 \begin{equation}
@@
 We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same deterministic value each year (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
-We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \ref{tab:param-table}).
+We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
 To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
@@
 \end{equation}
+
 Maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) were assumed to vary by ocean age, origin, brood year, and population and were treated as multivariate logit-normal random variables around time-constant and density-independent deterministic values ($\dot{\psi}^{O^{w}}_{o,j}$, $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}_o}$ (one matrix per origin, each constructed of $\sigma_{\psi^{O^{w}}_{o,j}}$ and $\rho_{\psi^{O^{w}}_{o}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 This is because the life cycle dynamics must start somewhere, and no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
-Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \ref{tab:param-table}) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
+Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \@ref(tab:param-table)) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
 Initial abundance of hatchery-origin returns was handled by the "straying model", described below.
@@
 
-No data sources were used to inform ocean juvenile population dynamics -- estimation of these quantities was enabled by (_i_) reasonably precise information about the abundance and composition of fish entering the ocean and returning to natal tributaries, (_ii_) the simplifying assumptions described above (i.e., time-constant second and third year ocean survival and perfectly correlated but offset origin-specific survival), and (_iii_) through the use of reasonably strong priors for second and third year ocean survival (Table \ref{tab:param-table}).
+No data sources were used to inform ocean juvenile population dynamics -- estimation of these quantities was enabled by (_i_) reasonably precise information about the abundance and composition of fish entering the ocean and returning to natal tributaries, (_ii_) the simplifying assumptions described above (i.e., time-constant second and third year ocean survival and perfectly correlated but offset origin-specific survival), and (_iii_) through the use of reasonably strong priors for second and third year ocean survival (Table \@ref(tab:param-table)).
 
@@
 Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around deterministic values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$ (constructed of $\sigma_{\phi^{R^{b} \rightarrow R^{a}}_o}$ and $\rho_{\phi^{R^{b} \rightarrow R^{a}}}$ following eq.
-\ref{eq:generic-Sigma2by2}).
+\@ref(eq:generic-Sigma2by2)).
 In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the deterministic expectation in these years for parameter identifiability purposes:
@@
 We term this phenomenon "pre-spawn survival", denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, which we assume are multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$) with covariance matrix $\Sigma_{\phi^{S^{b} \rightarrow S^{a}}}$ (constructed of $\sigma_{\phi^{S^{b} \rightarrow S^{a}}_j}$ and $\rho_{\phi^{S^{b} \rightarrow S^{a}}}$ following eq.
-\ref{eq:generic-Sigma4by4}):
+\@ref(eq:generic-Sigma4by4)):
 \begin{equation}
@@
 \end{equation}
-It is this $S^{a}_{y,k,o,j}$ value from which total egg production ($E_{y,j}$) is calculated in eq. \ref{eq:get-E} to complete the life cycle.
+It is this $S^{a}_{y,k,o,j}$ value from which total egg production ($E_{y,j}$) is calculated in eq. \@ref(eq:get-E) to complete the life cycle.
 

### 2022-03-18 100-math-description/GR-sslcm-math-description.Rmd
Whoops missed a couple -- see previous commit

@@
 In our mathematical representation of quantities in the model, we have striven for consistency, but this has created somewhat non-intuitive conventions which require devoted explanation.
-All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \ref{tab:index-table}, \ref{tab:symbol-table}, \ref{tab:param-table}, and \ref{tab:data-table} for reference and a catalog of all equations is provided in Table \ref{tab:equation-table}.
+All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \@ref(tab:index-table), \@ref(tab:symbol-table), \@ref(tab:param-table), and \@ref(tab:data-table) for reference and a catalog of all equations is provided in Table \@ref(tab:equation-table).
 
@@
 \end{equation}
-Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \ref{tab:param-table}) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
-\ref{eq:generic-Sigma4by4} and \ref{eq:generic-Sigma2by2}.
 Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \@ref(tab:param-table)) and the $\Sigma$ matrices were constructed using the structures defined in eqs.

### 2022-03-23 100-math-description/GR-sslcm-math-description.Rmd
Improve inclusion of figure to use bookdown

@@
   - \usepackage{microtype}
+  - \usepackage{float}
   - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
@@
 
+\rhead{\empty}
+\lhead{\empty}
+\renewcommand{\headrulewidth}{0pt}
+
 ```{r diagram_fig_cap}
@@
 
-```{r diagram, fig.cap = diagram_fig_cap, eval = FALSE}
+```{r diagram, fig.cap = diagram_fig_cap, fig.pos = "H", out.extra = ""}
 include_graphics("GR-sslcm-diagram.pdf")
 ```
-
-\rhead{\empty}
-\lhead{\empty}
-\renewcommand{\headrulewidth}{0pt}
-
-\begin{figure}[H]
-\centering
-\caption{Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.}
-\includegraphics{GR-sslcm-diagram.pdf}
-\label{fig:diagram}
-\end{figure}
 

### 2022-03-23 100-math-description/GR-sslcm-math-description.Rmd
Update equation labels to use bookdown syntax

@@
 \logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
-\label{eq:generic-random}
+(\#eq:generic-random)
 \end{equation}
@@
 \right]
-\label{eq:generic-Sigma4by4}
+(\#eq:generic-Sigma4by4)
 \end{equation}
@@
 \right]
-\label{eq:generic-Sigma2by2}
+(\#eq:generic-Sigma2by2)
 \end{equation}
@@
 E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k,j} \cdot f_{k}
-\label{eq:get-E}
+(\#eq:get-E)
 \end{equation}
@@
 \dot{\phi}^{E \rightarrow P^{b}}_{y,j} = \frac{1}{\frac{1}{\alpha_j} + \frac{E_{y,j}}{\beta_j}}
-\label{eq:get-phi-E-Pb-dot}
+(\#eq:get-phi-E-Pb-dot)
 \end{equation}
@@
 \log(\beta_j) \sim \mathcal{N}\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
-\label{eq:beta-random}
+(\#eq:beta-random)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
-\label{eq:phi-E-Pb-random}
+(\#eq:phi-E-Pb-random)
 \end{equation}
@@
 P^{b}_{y,j} = \phi^{E \rightarrow P^{b}}_{y,j} \cdot E_{y,j}
-\label{eq:get-Pb}
+(\#eq:get-Pb)
 \end{equation}
@@
 P^{a}_{y,i,j} = P^{b}_{y,j} \cdot \pi_{y,i,j}
-\label{eq:get-Pa}
+(\#eq:get-Pa)
 \end{equation}
@@
 \logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
-\label{eq:pi-random}
+(\#eq:pi-random)
 \end{equation}
@@
 \logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot \left(\frac{P^{a}_{y,i,j}}{\mathrm{WUL}_j}\right)
-\label{eq:get-phi-Pa-Mb-dot}
+(\#eq:get-phi-Pa-Mb-dot)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
-\label{eq:phi-Pa-Mb-random}
+(\#eq:phi-Pa-Mb-random)
 \end{equation}
@@
 M^{b}_{y,i,o=\mathrm{NOR},j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \rightarrow M^{b}}_{y,i,j}
-\label{eq:get-Mb-NOR}
+(\#eq:get-Mb-NOR)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
-\label{eq:phi-Mb-Ma-random}
+(\#eq:phi-Mb-Ma-random)
 \end{equation}
@@
 M^{a}_{y,i,o,j} = M^{b}_{y,i,o,j} \cdot \phi^{M^{b} \rightarrow M^{a}}_{y,o,j}
-\label{eq:get-Ma}
+(\#eq:get-Ma)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
-\label{eq:phi-Ma-O0-random}
+(\#eq:phi-Ma-O0-random)
 \end{equation}
@@
 O^{0}_{y,o,j} = \phi^{M^{a} \rightarrow O^{0}}_{y,o} \sum_i^{n_i} M^{a}_{y,i,o,j}
-\label{eq:get-O0}
+(\#eq:get-O0)
 \end{equation}
@@
 \log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
-\label{eq:fall-count-data}
+(\#eq:fall-count-data)
 \end{equation}
@@
 \log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
-\label{eq:spring-count-data}
+(\#eq:spring-count-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \mathcal{N}\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
-\label{eq:summer-surv-data}
+(\#eq:summer-surv-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
-\label{eq:fall-surv-data}
+(\#eq:fall-surv-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
-\label{eq:winter-surv-data}
+(\#eq:winter-surv-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
-\label{eq:spring-surv-data}
+(\#eq:spring-surv-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
-\label{eq:spring-surv-HOR-data}
+(\#eq:spring-surv-HOR-data)
 \end{equation}
@@
 \logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
-\label{eq:hydro-surv-data}
+(\#eq:hydro-surv-data)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
-\label{eq:phi-O0-O1-random}
+(\#eq:phi-O0-O1-random)
 \end{equation}
@@
 \end{aligned}
-\label{eq:get-phi-O-HOR}
+(\#eq:get-phi-O-HOR)
 \end{equation}
@@
 \end{aligned}
-\label{eq:psi-random}
+(\#eq:psi-random)
 \end{equation}
@@
 \end{aligned}
-\label{eq:get-Os}
+(\#eq:get-Os)
 \end{equation}
@@
 \end{aligned}
-\label{eq:get-Rbs}
+(\#eq:get-Rbs)
 \end{equation}
@@
 \end{cases}
-\label{eq:phi-Rb-Ra-random}
+(\#eq:phi-Rb-Ra-random)
 \end{equation}
@@
 R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot \phi^{SL}_{y,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
-\label{eq:get-Ra}
+(\#eq:get-Ra)
 \end{equation}
@@
 S^{b}_{y,k,o,j} = \max\left(R^{a}_{y,k,o,j} - B_{y,k,o,j}, 1\right)
-\label{eq:get-Sb}
+(\#eq:get-Sb)
 \end{equation}
@@
 \logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
-\label{eq:phi-Sb-Sa-random}
+(\#eq:phi-Sb-Sa-random)
 \end{equation}
@@
 S^{a}_{y,k,o,j} = S^{b}_{y,k,o,j} \cdot \phi^{S^{b} \rightarrow S^{a}}_{y,j}
-\label{eq:get-Sa}
+(\#eq:get-Sa)
 \end{equation}
@@
 \log\left(\hat{R}^{a}_{y,j}\right) \sim \mathcal{N}\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
-\label{eq:Ra-data}
+(\#eq:Ra-data)
 \end{equation}
@@
 \hat{x}^{\mathrm{LGR}}_{y,o} \sim \mathcal{B}\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
-\label{eq:upstream-surv-data}
+(\#eq:upstream-surv-data)
 \end{equation}
@@
 \hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \mathcal{B}\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
-\label{eq:prespawn-surv-data}
+(\#eq:prespawn-surv-data)
 \end{equation}
@@
 p^{R^{a}}_{y,ko,j} = \frac{R^{a}_{y,ko,j}}{\sum_{ko}^{n_{ko}} R^{a}_{y,ko,j}}
-\label{eq:get-pRa}
+(\#eq:get-pRa)
 \end{equation}
@@
 \boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
-\label{eq:weir-comp-data}
+(\#eq:weir-comp-data)
 \end{equation}
@@
 z_{k,j} \sim \mathcal{N}(\dot{z}_{k}, \sigma_{z_k})
-\label{eq:z-random}
+(\#eq:z-random)
 \end{equation}
@@
 \log(\zeta_{k,j}) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
-\label{eq:get-zeta-no-minam}
+(\#eq:get-zeta-no-minam)
 \end{equation}
@@
 \zeta_{k,j=\mathrm{MIN}} = \mathrm{mean}(\zeta_{k,j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]})
-\label{eq:get-zeta-minam}
+(\#eq:get-zeta-minam)
 \end{equation}
@@
 p^{S^{a^{\prime}}}_{y,ko,j} = \frac{S^{a}_{y,ko,j} \cdot \zeta_{k,j}}{\sum_{ko}^{n_{ko}} S^{a}_{y,ko,j} \cdot \zeta_{k,j}}
-\label{eq:get-pSa-prime}
+(\#eq:get-pSa-prime)
 \end{equation}
@@
 \boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
-\label{eq:carcass-comp-data}
+(\#eq:carcass-comp-data)
 \end{equation}

### 2022-03-23 100-math-description/GR-sslcm-math-description.Rmd

@@
     citation_package: natbib
+  # bookdown::word_document2
 fontfamily: mathpazo
@@
   - \renewcommand{\contentsname}{Table of Contents}
+  - \renewcommand{\eqref}[1]{\ref{#1}}
 ---
@@
 We denote its random variability across years and populations as:
+
 \begin{equation}
@@
 \end{equation}
+
 where $\Sigma_{\phi^{A \rightarrow B}}$ is an $n_j \times n_j$ matrix with the structure:
+
 \begin{equation}
@@
 \end{equation}
+
 That is, all populations ($j$) have unique variance terms $(\sigma_{\phi^{A \rightarrow B}_j})^2$ but we assume the correlation component of the covariance calculation ($\rho_{\phi^{A \rightarrow B}}$) is identical for all population pairs.
 In cases where a quantity varies annually and is different by origin but not by population, $\Sigma$ would have dimensions $n_o \times n_o$:
+
 \begin{equation}
@@
 \end{equation}
+
 Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \@ref(tab:param-table)) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
@@
 Total egg production is the sum product of age-specific spawner abundance (from eq. \@ref(eq:get-Sa), below), proportion female, and fecundity:
+
 \begin{equation}
@@
 \end{equation}
+
 The proportion of spawners at age that are female ($\Omega_{k,j}$) was calculated from carcass survey data and averaged across years and fecundity ($f_k$) was calculated from samples taken from Grande Ronde-origin hatchery broodstock.
@@
 Deterministic egg-to-parr survival is density-dependent and follows a Beverton-Holt relationship with productivity parameter $\alpha_j$ and capacity parameter $\beta_j$:
+
 \begin{equation}
@@
 \end{equation}
+
 To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\mathrm{WUL}_j$).
@@
 We modeled capacity ($\beta_j$) as a function of this $\mathrm{WUL}_j$ metric:
+
 \begin{equation}
@@
 \end{equation}
+
 where $\lambda$ is the expected change in parr capacity per 1 km change in weighted usable habitat length, and $\sigma_{\beta}$ is the log-normal standard deviation of variability in this relationship not captured by $\mathrm{WUL}$ values.
@@
 \@ref(eq:generic-Sigma4by4)):
+
 \begin{equation}
@@
 \end{equation}
+
 Parr recruitment ($P^{b}_{y,j}$) to the end of summer was then the product of total egg production and egg-to-parr survival:
+
 \begin{equation}
@@
 To enable building an observation model that could accommodate this feature of the populations in our model, summer parr was apportioned to these two strategies:
+
 \begin{equation}
@@
 \end{equation}
+
 where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
@@
 \end{equation}
+
 and the proportion that are spring migrants was obtained as its complement ($\pi_{y,i = \mathrm{spring},j} = 1 - \pi_{y,i = \mathrm{fall},j}$).
@@
 Deterministic overwinter survival was:
+
 \begin{equation}
@@
 \end{equation}
+
 Note the migratory strategy-specific intercept ($\gamma_{0,i,j}$) but common slope terms ($\gamma_{1,j}$).
@@
 \end{equation}
+
 Natural-origin (indexed by $o=\mathrm{NOR}$) parr surviving to the beginning of the following year was then:
+
 \begin{equation}
@@
 \end{equation}
+
 For populations with hatchery supplementation, hatchery-origin smolt releases (assumed known without error) were introduced at this point as well and stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
@@
 \end{equation}
+
 Thus, the abundance of smolt reaching LGR was:
+
 \begin{equation}
@@
 \end{equation}
+
 After reaching LGR, we modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
@@
 \@ref(eq:generic-Sigma2by2)):
+
 \begin{equation}
@@
 \end{equation}
+
 Thus, the abundance of fish reaching the ocean by origin was:
+
 \begin{equation}
@@
 \end{equation}
+
 Note the summation across migratory strategies ($i$) in eq.
@@
 The estimated passage during these time periods were used in log-normal likelihoods by assuming:
+
 \begin{equation}
@@
 \end{equation}
+
 for the fall screw trap estimate and
+
 \begin{equation}
@@
 \end{equation}
+
 for the spring screw trap estimate.
@@
 These estimates (and their associated standard errors) were used in logit-normal likelihoods by assuming:
+
 \begin{equation}
@@
 \end{equation}
+
 for the summer tagging group,
+
 \begin{equation}
@@
 \end{equation}
+
 for the fall tagging group,
+
 \begin{equation}
@@
 \end{equation}
+
 for the winter tagging group (where $\phi^{P^{b} \rightarrow P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$),
+
 \begin{equation}
@@
 \end{equation}
+
 for the spring tagging group, and
+
 \begin{equation}
@@
 \end{equation}
+
 for hatchery-origin smolt releases ($j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$).
@@
 Similar to the other survival data sets, we assumed these estimates are made with logit-normal random error around the life cycle model estimate to build the likelihood:
+
 \begin{equation}
@@
 \@ref(eq:phi-O0-O1-random), omitted for brevity):
+
 \begin{equation}
@@
 \end{equation}
+
 We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same deterministic value each year (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
@@
 To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
+
 \begin{equation}
@@
 \end{equation}
+
 Since we assumed age-5 to be the last age of maturity, all fish alive and in the ocean after the third year at sea must mature and return that year (i.e., all $\psi^{O^{3}}_{y,o,j} = 1$).
@@
 We modeled ocean population dynamics as a sequence of survival, maturation of surviving fish, and survival of non-maturing fish:
+
 \begin{equation}
@@
 \end{equation}
+
 That is, fish reaching the ocean as age-2 juveniles ($O^{0}_{y,o,j}$) must survive one winter to become age-3 ocean juveniles ($O^{1}_{y,o,j}$); if they do not mature at age-3 ($1 - \psi^{O^{1}}_{y,o,j}$), then they must survive another winter to become age-4 ocean juveniles ($O^{2}_{y,o,j}$), and if they do not mature at that point ($1 - \psi^{O^{2}}_{y,o,j}$), they must survive a third winter to become age-5 ocean juveniles ($O^{3}_{y,o,j}$).
@@
 Thus, the abundance of fish spawned in brood year $y$ returning as age-3, age-4, and age-5, respectively, was:
+
 \begin{equation}
@@
 \end{equation}
+
 Note, however, that this leaves 12 age/year combinations per origin unpopulated (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns).
@@
 In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the deterministic expectation in these years for parameter identifiability purposes:
+
 \begin{equation}
@@
 \end{equation}
+
 Examination of the adult data indicated that hatchery-origin adults returned to Grande Ronde populations in years that could not be attributed to hatchery-origin smolt releases to these populations.
@@
 We can now define the abundance of adults arriving to their natal spawning tributaries by age and origin ($R^{a}_{y,k,o,j}$) as:
+
 \begin{equation}
@@
 \end{equation}
+
 Upon arrival in the tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \mathrm{MIN}$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
@@
 Thus, the abundance of fish passed upstream of the weir and that would have a chance to spawn each year was (the maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$):
+
 \begin{equation}
@@
 \end{equation}
+
 As a final step before spawning, these fish on the spawning grounds must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
@@
 \end{equation}
+
 Thus, the abundance of total successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
+
 \begin{equation}
@@
 \end{equation}
+
 It is this $S^{a}_{y,k,o,j}$ value from which total egg production ($E_{y,j}$) is calculated in eq. \@ref(eq:get-E) to complete the life cycle.
@@
 We assumed the point estimate is made with log-normal observation error around the model-predicted total returns to the tributary to build the likelihood for this component:
+
 \begin{equation}
@@
 We assumed the latter was a binomial random variable to build the likelihood component for this data set:
+
 \begin{equation}
@@
 \end{equation}
+
 The other survival data set informing the freshwater adult observation model was for spawning success, i.e., pre-spawn survival.
@@
 We assumed these counts were gathered using binomial sampling to build the likelihood:
+
 \begin{equation}
@@
 The model-expected composition by age and origin ($p^{R^{a}}_{y,ko,j}$) was calculated from the return abundance by age and origin, reorganized such that age and origin fell along the same array dimension ($R^{a}_{y,ko,j}$) rather than along two dimensions as shown in the process model ($R^{a}_{y,k,o,j}$):
+
 \begin{equation}
@@
 \end{equation}
+
 which we used as the multinomial expected frequency to build the likelihood:
+
 \begin{equation}
@@
 \end{equation}
+
 Due to the age sampling bias of carcass surveys we discovered, we required a correction to ensure reliable fits to all data sets while still recovering unbiased true age composition data for the Minam River population, which had only carcass composition data (the other three populations had both weir and carcass composition data).
 For the three populations with paired composition data (i.e., $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$), we estimated correction factors in a hierarchical fashion:
+
 \begin{equation}
@@
 \end{equation}
+
 where $k=1$ or $k=3$ ($k=2$ was treated as the baseline category), $z_{k,j}$ are age- and population-specific coefficients, $\dot{z}_{k}$ are their expectations across populations, and $\sigma_{z_k}$ are their standard deviations across populations.
 These coefficients were used in the following log-linear model to derive the correction factors ($\zeta_{k,j}$):
+
 \begin{equation}
@@
 \end{equation}
+
 where $k \in [1,2,3]$, $\boldsymbol{\mathrm{age3}}_{1:n_k} = [1~0~0]$ is a dummy variable indicating whether each value of $k$ corresponds to age-3, and $\boldsymbol{\mathrm{age5}}_{1:n_k} = [0~0~1]$ is a dummy variable indicating whether each value of $k$ corresponds to age-5.
 These correction factors were averaged across populations to obtain the correction factors for the Minam River population:
+
 \begin{equation}
@@
 \end{equation}
+
 We used these correction factors to calculate the expected proportions by age and origin for carcass surveys ($p^{S^{a^{\prime}}}_{y,ko,j}$):
+
 \begin{equation}
@@
 \end{equation}
+
 which we used as the multinomial expected frequency to build the likelihood by assuming:
+
 \begin{equation}

### 2022-04-04 03-post-process/output-plots.Rmd
Make the growth factor a function of summer length

@@
 # summer parr mean length
-L1 = "Summer to Spring Growth"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_growth", "sig_lgrowth", "rho_lgrowth", "^growth[")
+L1 = "Summer to Spring 'Growth Factor'"
+L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
+match = c("int_lgrowth", "slp_lgrowth", "sig_lgrowth", "rho_lgrowth", "^growth[")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
 
-### Spring vs. Summer Length
+### "Growth Factor" vs. Summer Length
 
@@
 
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
+  # extract posterior summaries of growth outcomes
+  growth_mean = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["mean",]
+  growth_lwr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  growth_upr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # create a vector of scaled summer lengths to calculate at
   L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
 
   # extract posteriors of coefficients
-  mu_growth = post_subset(post, sub_index("mu_growth[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curves for one posterior sample
+  int_lgrowth = post_subset(post, sub_index("int_lgrowth[pop]", pop = j), matrix = TRUE)
+  slp_lgrowth = post_subset(post, sub_index("slp_lgrowth[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted curves for one posterior sample
   pred_fn = function(i) {
-    pred_L_Mb = L_Pb_seq * mu_growth[i]
-    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "1]")
-    pred_L_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
-
-  # extract summarize predicted length
-  pred_L_Mb_mean = post_summ(post_pred_L_Mb, "")["mean",]
-  pred_L_Mb_lwr = post_summ(post_pred_L_Mb, "")["2.5%",]
-  pred_L_Mb_upr = post_summ(post_pred_L_Mb, "")["97.5%",]
+    pred_growth = exp(int_lgrowth[i] + slp_lgrowth[i] * L_Pb_star_seq)
+    names(pred_growth) = paste0("pred_growth[", 1:30, "1]")
+    pred_growth
+  }
+
+  # calculate predicted growth values and add to posterior samples
+  pred_growth = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_growth = post_convert(cbind(postpack:::id_mat(post), pred_growth))
+
+  # extract summarize predicted growth
+  pred_growth_mean = post_summ(post_pred_growth, "")["mean",]
+  pred_growth_lwr = post_summ(post_pred_growth, "")["2.5%",]
+  pred_growth_upr = post_summ(post_pred_growth, "")["97.5%",]
 
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
+       ylim = range(pred_growth_lwr, pred_growth_upr, growth_lwr, growth_upr, na.rm = TRUE),
        xlim = range(L_Pb_seq), 
@@
   # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_growth_lwr, rev(pred_growth_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_growth_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_growth_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_growth_mean ~ L_Pb_seq, col = "red", lwd = 2)
 
   # realized pairs
-  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
-  points(L_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(L_Pb_lwr, growth_mean, L_Pb_upr, growth_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, growth_lwr, L_Pb_mean, growth_upr, col = alpha("red", 0.5))
+  points(growth_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
 
@@
 mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Spring\\,Tagging\\,(mm)$"))
-```
-
-### Growth Rate
+mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
+```
+
+### "Growth Factor" Time Series
 
@@
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\Growth$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
 ```
@@
   "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lgrowth[2,1]" = "Summer to Spring Growth",
+  "rho_lgrowth[2,1]" = "Summer to Spring 'Growth Factor'",
   "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
@@
 
-#### Summer Parr to Spring Smolt Growth
+#### Summer Parr to Spring Smolt "Growth Factor"
 
@@
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lgrowth_resid\\[year,pop\\]", "Summer to Spring Growth")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lgrowth_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
@@
 # which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring Growth", "Trib to LGR Survival", "LGR to BON Survival")
+fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
 sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")

### 2022-04-04 02-model/fit-model.R

@@ -27,7 +27,7 @@ do_pp_check = TRUE
 do_lppd = FALSE
 
 # specify a scenario name
-scenario = "size-based-surv-scaled"
+scenario = "size-based-surv-growth-relationship"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -239,7 +239,7 @@ jags_params = c(
 
   # length-related quantities
   "omega0", "omega1", "Sig_lL_Pb", 
-  "mu_growth", "Sig_lgrowth", "tau0", "tau1",
+  "int_lgrowth", "slp_lgrowth", "Sig_lgrowth", "tau0", "tau1",
   
   # overwinter survival coefficients
   "gamma0", "gamma1",
@@ -514,7 +514,7 @@ if (rmd) {
 }
 
 # render the simulation vs. observed time series plots if requested and applicable
-if (rmd & last_yr > 2019) {
+if (rmd & last_yr > 2019 & FALSE) {
   # start a timer, this can take a while
   starttime = Sys.time()
   

### 2022-04-04 02-model/model-code.R

@@ -37,8 +37,8 @@ jags_model_code = function() {
     # gamma1[i_spring,j] <- gamma1[i_fall,j]
     
     # growth coefficient from end of summer to spring tagging
-    mu_lgrowth[j] ~ dnorm(0, 1e-3)
-    mu_growth[j] <- exp(mu_lgrowth[j])
+    int_lgrowth[j] ~ dnorm(0, 1e-3)
+    slp_lgrowth[j] ~ dnorm(0, 1e-3)
     sig_lgrowth[j] ~ dunif(0, 0.5)
 
     # size-dependent NOR migration to LGR survival
@@ -254,8 +254,8 @@ jags_model_code = function() {
     Lphi_Pa_Mb[y,i_fall,1:nj] ~ dmnorm.vcov(gamma0[i_fall,1:nj] + gamma1[i_fall,1:nj] * L_Pb_star[y,1:nj], Sig_Lphi_Pa_Mb[1:nj,1:nj,i_fall])
     Lphi_Pa_Mb[y,i_spring,1:nj] ~ dmnorm.vcov(gamma0[i_spring,1:nj] + gamma1[i_spring,1:nj] * L_Pb_star[y,1:nj], Sig_Lphi_Pa_Mb[1:nj,1:nj,i_spring])
 
-    # summer to spring growth rate
-    lgrowth[y,1:nj] ~ dmnorm.vcov(log(mu_growth[1:nj]), Sig_lgrowth[1:nj,1:nj])
+    # summer to spring growth factor
+    lgrowth[y,1:nj] ~ dmnorm.vcov(int_lgrowth[1:nj] + slp_lgrowth[1:nj] * L_Pb_star[y,1:nj], Sig_lgrowth[1:nj,1:nj])
     
     # size-based migration survival from trib to LGR: NOR
     Lphi_Mb_Ma[y,i_spring,o_nor,1:nj] ~ dmnorm.vcov(tau0[1:nj] + tau1[1:nj] * L_Mb_star[y,1:nj], Sig_Lphi_Mb_Ma[1:nj,1:nj,o_nor])
@@ -817,7 +817,7 @@ jags_model_code = function() {
       }
       
       # summer to spring growth rate
-      lgrowth_resid[y,j] <- lgrowth[y,j] - mu_lgrowth[j]
[…]

### 2022-04-05 03-post-process/output-plots.Rmd
Rename "growth" to "Delta_L_Pb_Mb" for consistency throughout

@@
     label: "Scenario"
-    value: "size-based-surv"
+    value: "size-based-surv-growth-relationship"
     input: text
@@
 L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("int_lgrowth", "slp_lgrowth", "sig_lgrowth", "rho_lgrowth", "^growth[")
+match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
   # extract posterior summaries of growth outcomes
-  growth_mean = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["mean",]
-  growth_lwr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  growth_upr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
 
@@
   # extract posteriors of coefficients
-  int_lgrowth = post_subset(post, sub_index("int_lgrowth[pop]", pop = j), matrix = TRUE)
-  slp_lgrowth = post_subset(post, sub_index("slp_lgrowth[pop]", pop = j), matrix = TRUE)
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
 
@@
   pred_fn = function(i) {
-    pred_growth = exp(int_lgrowth[i] + slp_lgrowth[i] * L_Pb_star_seq)
-    names(pred_growth) = paste0("pred_growth[", 1:30, "1]")
-    pred_growth
+    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
+    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
+    pred_Delta_L_Pb_Mb
   }
@@
   # calculate predicted growth values and add to posterior samples
-  pred_growth = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_growth = post_convert(cbind(postpack:::id_mat(post), pred_growth))
+  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
 
   # extract summarize predicted growth
-  pred_growth_mean = post_summ(post_pred_growth, "")["mean",]
-  pred_growth_lwr = post_summ(post_pred_growth, "")["2.5%",]
-  pred_growth_upr = post_summ(post_pred_growth, "")["97.5%",]
+  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
+  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
+  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
 
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_growth_lwr, pred_growth_upr, growth_lwr, growth_upr, na.rm = TRUE),
+       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
        xlim = range(L_Pb_seq), 
@@
   # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_growth_lwr, rev(pred_growth_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_growth_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_growth_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_growth_mean ~ L_Pb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
 
   # realized pairs
-  segments(L_Pb_lwr, growth_mean, L_Pb_upr, growth_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, growth_lwr, L_Pb_mean, growth_upr, col = alpha("red", 0.5))
-  points(growth_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
+  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
 
@@
 plot_f = function(j) {
-
-  growth_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j],
-                     lwr95 = NA, upr95 = NA)
-
-  plot_tseries(post_summ(post, sub_index("^growth[year,pop]$", year = ts_yrs, pop = j)),
-               growth_obs,
+  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               Delta_L_Pb_Mb_obs,
                main = pops[j],
@@
   "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lgrowth[2,1]" = "Summer to Spring 'Growth Factor'",
+  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
   "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lgrowth_resid[year,pop]", "sig_lgrowth[pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth) Residual")
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lDelta_L_Pb_Mb_resid[year,pop]", "sig_lDelta_L_Pb_Mb[pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lgrowth_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")

### 2022-04-05 02-model/fit-model.R

@@ -219,7 +219,7 @@ toggle_rho_estimation("rho_Lphi_E_Pb")     # parr recruitment process noise
 toggle_rho_estimation("rho_lL_Pb")         # mean length at end of summer process noise
 toggle_rho_estimation("rho_Lpi")           # parr apportionment to LH type process noise
 toggle_rho_estimation("rho_Lphi_Pa_Mb")    # parr -> smolt overwinter survival process noise (both LH types)
-toggle_rho_estimation("rho_lgrowth")       # growth rate from summer mean length to spring mean length
+toggle_rho_estimation("rho_lDelta_L_Pb_Mb")# growth factor from summer mean length to spring mean length
 toggle_rho_estimation("rho_Lphi_Mb_Ma")    # migration to LGR survival process noise
 toggle_rho_estimation("rho_Lphi_Ma_O0")    # migration from LGR to ocean survival process noise
 toggle_rho_estimation("rho_Lphi_O0_O1")    # first year ocean survival process noise
@@ -239,7 +239,7 @@ jags_params = c(
 
   # length-related quantities
   "omega0", "omega1", "Sig_lL_Pb", 
-  "int_lgrowth", "slp_lgrowth", "Sig_lgrowth", "tau0", "tau1",
+  "theta0", "theta1", "Sig_lDelta_L_Pb_Mb", "tau0", "tau1",
   
   # overwinter survival coefficients
   "gamma0", "gamma1",
@@ -258,7 +258,7 @@ jags_params = c(
   "pi", "phi_Pa_Mb", "phi_Mb_Ma", "phi_Ma_O0", 
   "psi_O1", "psi_O2", "phi_Sb_Sa",
   "phi_O0_O1", "phi_O1_O2", "phi_O2_O3",
-  "phi_Rb_Ra", "growth",
+  "phi_Rb_Ra", "Delta_L_Pb_Mb",
   
   # derived survival terms
   "phi_Pb_Ma", "phi_Pa_Ma",
@@ -287,7 +287,7 @@ jags_params = c(
[…]

### 2022-04-05 02-model/model-code.R

@@ -25,7 +25,7 @@ jags_model_code = function() {
     mu_pi[i_spring,j] <- 1 - mu_pi[i_fall,j]
     
     # overwinter survival parameters: LH-specific
-    # uses logistic relationship to introduce density-dependence
+    # uses logistic relationship to introduce size-dependence
     # gamma0: LH-specific intercepts
     # gamma1: LH-common slopes
     for (i in 1:ni) {
@@ -33,13 +33,11 @@ jags_model_code = function() {
       gamma1[i,j] ~ dt(0, 1/1.566^2, 7.763)
       sig_Lphi_Pa_Mb[i,j] ~ dunif(0, 5)
     }
-    # gamma1[i_fall,j] ~ dnorm(0, 1e-3)
-    # gamma1[i_spring,j] <- gamma1[i_fall,j]
-    
-    # growth coefficient from end of summer to spring tagging
-    int_lgrowth[j] ~ dnorm(0, 1e-3)
-    slp_lgrowth[j] ~ dnorm(0, 1e-3)
-    sig_lgrowth[j] ~ dunif(0, 0.5)
+
+    # coefficients for obtaining summer mean length to spring mean length growth factor
+    theta0[j] ~ dnorm(0, 1e-3)
+    theta1[j] ~ dnorm(0, 1e-3)
+    sig_lDelta_L_Pb_Mb[j] ~ dunif(0, 0.5)
 
     # size-dependent NOR migration to LGR survival
     # assumed equal among migration types
@@ -138,7 +136,7 @@ jags_model_code = function() {
   rho_Lpi <- 0
   rho_Lphi_Pa_Mb[i_fall] <- 0
   rho_Lphi_Pa_Mb[i_spring] <- 0
-  rho_lgrowth <- 0
+  rho_lDelta_L_Pb_Mb <- 0
   rho_Lphi_Mb_Ma[o_nor] <- 0
   rho_Lphi_Mb_Ma[o_hor] <- 0
   rho_Lphi_Ma_O0 <- 0
@@ -168,7 +166,7 @@ jags_model_code = function() {
       }
       
       # covariance matrix of summer to spring growth rate
[…]

### 2022-04-05 03-post-process/compare-sim-to-obs.Rmd
Add size-based quantities to obs-v-sim diagnostics

@@
   x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Proportion Fall Migrants", "Overwinter Survival", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
+  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
   x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
@@
 
+#### Parr Mean Size
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("^L_Pb[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Parr Mean Size: Estimates")
+ratio_plots(x, "Parr Mean Size: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Parr Mean Size"))
+```
+
 #### Proportion Fall Migrants
@@
 est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Overwinter Survival"))
+```
+
+#### Parr to Smolt Mean Size "Growth Factor"
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("^Delta_L_Pb_Mb[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Parr to Smolt Mean Size 'Growth Factor': Estimates")
+ratio_plots(x, "Parr to Smolt Mean Size 'Growth Factor': Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Parr to Smolt Mean Size 'Growth Factor'"))
+```
+
+#### Smolt Size
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("^L_Mb[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Smolt Mean Size: Estimates")
+ratio_plots(x, "Smolt Mean Size: Ratios")
+est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Smolt Mean Size"))
 ```
@@
 
+#### Parr Mean Size
+
+```{r}
+pop_ts_plots("^L_Pb[year,pop]")
+```
+
 #### Proportion Fall Migrants
@@
 pop_ts_plots("^phi_Pa_Mb[year,LH_type,pop]", LH_type = 2)
+```
+
+#### Parr to Smolt Mean Size "Growth Factor"
+
+```{r}
+pop_ts_plots("^Delta_L_Pb_Mb[year,pop]")
+```
+
+#### Smolt Mean Size
+
+```{r}
+pop_ts_plots("^L_Mb[year,pop]")
 ```

### 2022-04-05 03-post-process/compare-sim-to-obs.Rmd
Last minute house-keeping prior to merge

@@
     label: "Scenario"
-    value: "size-based-surv"
+    value: "base"
     input: text

### 2022-04-05 02-model/fit-model.R

@@ -27,7 +27,7 @@ do_pp_check = TRUE
 do_lppd = FALSE
 
 # specify a scenario name
-scenario = "size-based-surv-growth-relationship"
+scenario = "base"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -514,7 +514,7 @@ if (rmd) {
 }
 
 # render the simulation vs. observed time series plots if requested and applicable
-if (rmd & last_yr > 2019 & FALSE) {
+if (rmd & last_yr > 2019) {
   # start a timer, this can take a while
   starttime = Sys.time()
   

### 2022-04-05 03-post-process/output-plots.Rmd

@@
     label: "Scenario"
-    value: "size-based-surv-growth-relationship"
+    value: "base"
     input: text

### 2022-04-12 03-post-process/output-plots.Rmd
Fix duplication/subsetting issues with MCMC diagnostic summary table

@@
 L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
+match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
 L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
@@
 L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
+base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
 match = sub_index(base, year = ".+", origin = o_nor)
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
+base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
 match = sub_index(base, year = ".+", origin = o_hor)
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
+base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
+base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
+base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
+base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
+base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
 match = sub_index(base, year = ".+", origin = o_nor)
@@
 L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
+base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
 match = sub_index(base, year = ".+", origin = o_hor)
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
+match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
   # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
+  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
@@
   # predict parr recruits along a sequence of spawner abundances
-  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
+  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
   E_pred = seq(0, max(E[5,]), length = 30)

### 2022-04-21 03-post-process/output-plots.Rmd
Small bugfix to output plots

@@
   Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
+  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
   Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))

### 2022-04-21 03-post-process/output-plots.Rmd
Update residual visuals: observation model quantile residuals

@@
 ```{r plot-obs-resid-fn}
-
-obs_resid_yrs = all_yrs[c(1,observable)]
+obs_qresid_yrs = all_yrs[c(1,observable)]
 
@@
 # returns a data frame with identifiers and across-year summary statistics
-plot_obs_resid = function(resid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
 
   # extract posterior samples of residual time series
-  resid_post = post_subset(post, sub_index(resid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
+  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
 
   # extract the year indices available
-  y_ind = get_yr_index(colnames(resid_post))
+  y_ind = get_yr_index(colnames(qresid_post))
 
   # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(resid_post, 1, mean)
-  sd_post = apply(resid_post, 1, sd)
-
-  # calculate posterior summaries of residual time series
-  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place residuals at correct place in a time series
+  mn_post = apply(qresid_post, 1, mean)
+  sd_post = apply(qresid_post, 1, sd)
+
+  # calculate posterior summaries of qresidual time series
+  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+
+  # place qresiduals at correct place in a time series
   # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_resid_yrs))
-  empty[,y_ind] = resid
-  resid = empty[,observable]
-  rownames(resid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_resid_yrs))
-  empty_names[y_ind] = colnames(resid_post)
+  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
+  empty[,y_ind] = qresid
+  qresid = empty[,observable]
+  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
+  empty_names = rep(NA, length(obs_qresid_yrs))
+  empty_names[y_ind] = colnames(qresid_post)
 
@@
   i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(resid_post[,i_first], 1, mean)
-  mn_post_last = apply(resid_post[,i_last], 1, mean)
+  mn_post_first = apply(qresid_post[,i_first], 1, mean)
+  mn_post_last = apply(qresid_post[,i_last], 1, mean)
   first_last_mn_diff_post = mn_post_last - mn_post_first
 
-  # set the y-axis limits: want zero in center and leave room at top for legend
-  ylim = max(abs(c(resid["2.5%",], resid["97.5%",])), na.rm = TRUE) * c(-1.4,1.4)
+  # set the y-axis limits: leave room at top for legend
+  ylim = c(0,1.3)
 
@@
   par(lend = "square")
-  plot(resid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "")
+  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
 
@@
   axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
+  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
 
   # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], resid["2.5%",], all_yrs[observable], resid["97.5%",], col = "red")
-  points(resid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at zero noise
-  abline(h = 0, lty = 2, col = "black", lwd = 2)
+  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+  # draw reference line at 25%, 50%, and 75% quantiles
+  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
 
@@
   usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.01, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
+  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+  box()
 
   # create output for building summary tables
-  data.frame(param = resid_param,
+  data.frame(param = qresid_param,
              pop = ifelse(!is.null(pop), pop, NA),
@@
              age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(resid_post[,y_ind %in% observable]),
+             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
              year_mean_mean = mean(mn_post),
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lPa_obs_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
 oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lMb_obs_resid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
 oma_labels("Brood Year", "log(Spring Trap Count) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lRa_obs_resid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
 oma_labels("Return Year", "log(Total Adult Count) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pb_Ma_resid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
 oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
 oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
@@
   } else {
-    plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
+    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
   }
@@
 
-#### Spring Smolt $\rightarrow$ LGR (NOR)
+#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
+
+##### NOR
 
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
 oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
@@
 
-#### Spring Smolt $\rightarrow$ LGR (HOR)
+##### HOR
 
@@
   } else {
-    plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
+    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
   }
@@
 
-```{r hydro-surv-resid, fig.width = 7, fig.height = 4}
+```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
 my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("Lphi_obs_Ma_O0_resid[year,origin]", origin = o, main = origins[o]))
+tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
 oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
@@
 
-```{r bon-adult-surv-resid, fig.width = 7, fig.height = 4}
+```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
 my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("x_LGR_obs_resid[year,origin]", origin = o, main = origins[o]))
+tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
 oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("x_carcass_spawned_obs_resid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
 oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Pb_obs_resid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
 oma_labels("Brood Year", "log(Mean Summer Length) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Mb_obs_resid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
 oma_labels("Brood Year", "log(Mean Spring Length) Residual")
@@
 
-weir_comp_resid_plots = function(j) {
+weir_comp_qresid_plots = function(j) {
   my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Ra_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
+  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
   oma_labels("Return Year", "Weir Age/Origin Composition Residual")
@@
 ```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_resid_plots(j_cat)
+tmp = weir_comp_qresid_plots(j_cat)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_resid_plots(j_los)
+tmp = weir_comp_qresid_plots(j_los)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_resid_plots(j_ugr)
+tmp = weir_comp_qresid_plots(j_ugr)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r carcass-comp-resid-plots-fn}
-carcass_comp_resid_plots = function(j) {
+carcass_comp_qresid_plots = function(j) {
   my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Sa_prime_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
+  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
   oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
@@
 ```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_resid_plots(j_cat)
+tmp = carcass_comp_qresid_plots(j_cat)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_resid_plots(j_los)
+tmp = carcass_comp_qresid_plots(j_los)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_resid_plots(j_min)
+tmp = carcass_comp_qresid_plots(j_min)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 ```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_resid_plots(j_ugr)
+tmp = carcass_comp_qresid_plots(j_ugr)
 obs_error_ests = rbind(obs_error_ests, tmp)
@@
 # rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_resid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_resid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_resid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_resid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_resid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_resid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_resid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_resid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_resid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_resid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_resid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_resid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_resid\\[year,age,pop\\]", "Carcass")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
+obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
 
@@
 # determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_zero = ifelse(obs_error_ests$year_mean_lwr <= 0 & obs_error_ests$year_mean_upr >= 0, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_one = ifelse(obs_error_ests$year_sd_lwr <= 1 & obs_error_ests$year_sd_upr >= 1, TRUE, FALSE)
-obs_error_ests$diff_incl_zero = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
+obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
+obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
+obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
 
@@
 obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_zero, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
+obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
 obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_one, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
+obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
 obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_zero, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
+obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
 

### 2022-04-21 03-post-process/output-plots.Rmd
Update residual visuals: process model quantile residuals

@@
 
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_proc_resid = function(resid_param, sig_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
 
   # extract posterior samples of residual time series
-  resid_post = post_subset(post, sub_index(resid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract posterior samples of st. dev. parameter
-  sig_post = post_subset(post, sub_index(sig_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # divide each residual by its estimated SD parameterize: to standardize
-  resid_post = apply(resid_post, 2, function(x) x/sig_post)
+  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
 
   # extract the year indices available
-  y_ind = get_yr_index(colnames(resid_post))
+  y_ind = get_yr_index(colnames(qresid_post))
   y_ind_obs = y_ind %in% observable
@@
   # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(resid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(resid_post[,y_ind_obs], 1, sd)
+  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
+  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
 
@@
   y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(resid_post[,y_first], 1, mean)
-  mn_post_last = apply(resid_post[,y_last], 1, mean)
+  mn_post_first = apply(qresid_post[,y_first], 1, mean)
+  mn_post_last = apply(qresid_post[,y_last], 1, mean)
   first_last_mn_diff_post = mn_post_last - mn_post_first
 
-  # calculate posterior summaries of standardized residual time series
-  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # set the y-axis limits: want zero in center and leave room at top for legend
-  ylim = max(abs(c(resid["2.5%",], resid["97.5%",])), na.rm = TRUE) * c(-1.4,1.4)
+  # calculate posterior summaries of standardized qresidual time series
+  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+
+    # set the y-axis limits: leave room at top for legend
+  ylim = c(0,1.3)
 
@@
   par(lend = "square")
-  plot(resid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[y_ind]), max(all_yrs[y_ind]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-
-  # draw the noise time series: mean and 95% CRI
-  polygon(x = c(all_yrs[y_ind], rev(all_yrs[y_ind])),
-          y = c(resid["2.5%",], rev(resid["97.5%",])),
-          border = NA, col = alpha("salmon", 0.5))
-  lines(resid["mean",] ~ all_yrs[y_ind], lwd = 2, col = "red")
-  lines(resid["2.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")
-  lines(resid["97.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")
-
-  # draw reference line at zero noise
-  abline(h = 0, lty = 2, col = "black", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.01, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-
-  # create output for building summary tables
-  data.frame(param = resid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(resid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_E_Pb_resid[year,pop]", "sig_Lphi_E_Pb[pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lL_Pb_resid[year,pop]", "sig_lL_Pb[pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpi_resid[year,pop]", "sig_Lpi[pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lDelta_L_Pb_Mb_resid[year,pop]", "sig_lDelta_L_Pb_Mb[pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 7, fig.height = 4}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Ma_O0_resid[year,origin]", "sig_Lphi_Ma_O0[origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_O0_O1_resid[year,origin,pop]", "sig_Lphi_O0_O1[pop]", origin = 1, year = c(1, ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 7, fig.height = 4}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Rb_Ra_resid[year,origin]", "sig_Lphi_Rb_Ra[origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Sb_Sa_resid[year,pop]", "sig_Lphi_Sb_Sa[pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_resid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_resid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_resid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_resid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_resid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_resid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_resid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_zero = ifelse(proc_error_ests$year_mean_lwr <= 0 & proc_error_ests$year_mean_upr >= 0, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_one = ifelse(proc_error_ests$year_sd_lwr <= 1 & proc_error_ests$year_sd_upr >= 1, TRUE, FALSE)
-proc_error_ests$diff_incl_zero = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_zero, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_one, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_zero, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
+  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
+       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
 
@@
 
+  # draw reference line at 25%, 50%, and 75% quantiles
+  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
+
+  # draw posterior mean for first and half of time series
+  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+
   # draw the noise time series: mean and 95% CRI
@@
   points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
 
@@
              )
+
+}
+
+# container for across-year summary statistics
+# is rbinded many times for each random process and pop/origin/LH_type/age combo
+proc_error_ests = NULL
+```
+
+### FW Juvenile {.tabset .tabset-pills}
+
+#### Egg-to-Parr Survival
+
+```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Summer Parr Mean Length
+
+```{r summer-length-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Migratory Strategy Apportionment
+
+```{r pi-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Over-winter Survival {.tabset .tabset-pills}
+
+##### Fall Migrants
+
+```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
+oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### Spring Migrants
+
+```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
+oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Summer Parr to Spring Smolt "Growth Factor"
+
+```{r growth-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Trib to LGR {.tabset .tabset-pills}
+
+##### NOR
+
+```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
+oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
+oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### LGR to BON Survival
+
+```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
+oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### SW Juvenile {.tabset .tabset-pills}
+
+#### Yr1 Ocean Survival
+
+```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pr(Mature at age-3) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pr(Mature at age-4) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR
+
+```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
+oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### FW Adult {.tabset .tabset-pills}
+
+#### BON to LGR Survival
+
+```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
+my_par(); par(mfrow = c(1,2))
+tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
+oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Pre-spawn Survival
+
+```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
+my_par()
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
+oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### **SUMMARY TABLES** {.tabset .tabset-pills}
+
+These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
+Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
+
+```{r proc-error-table-prep}
+# rename parameters to human-readable format
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
+
+# correct origin indices
+proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
+proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
+
+# correct LH_type indices
+proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
+
+# correct pop indices
+proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
+
+# remove the age column
+proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
+
+# replace indices with names
+proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
+proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
+proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
+
+# which processes are in each life phase?
+fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
+sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
+fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
+
+# add a life phase column
+proc_error_ests$phase = NA
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
+proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
+proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
+
+# add levels to each variable
+proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
+proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
+proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
+proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
+proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
+
+# determine whether posterior of across-year quantities overlaps the target value
+proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
+proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
+proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
+
+# format the mean values to present in table
+# round and make bold if target value not in interval
+proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
+proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
+proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
+proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
+proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
+proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
+
+# drop unneeded columns
+proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
+```
+
+```{r proc-error-table-fn}
+proc_error_table = function(var) {
+  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
+  out[is.na(out)] = ""
+
+  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
+    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    collapse_rows(columns = 1:4)
+}
+```
+
+#### Across-Year Mean
+
+The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
+* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
+* Above 0 indicate that the time series of noise terms was biased high relative the expected value
+
+```{r proc-error-mean-table}
+proc_error_table("year_mean_mean")
+```
+
+#### Across-Year SD
+
+The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
+
+Values:
+
+* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
+* Below 1 indicate that the time series of noise terms was less variable than expected
+* Above 1 indicate that the time series of noise terms was more variable than expected
+
+```{r proc-error-sd-table}
+proc_error_table("year_sd_mean")
+```
+
+#### Last Half Mean - First Half Mean
+
+The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
+
+Values:
+
+* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
+* Below 0 indicate an overall declining time trend in noise terms
+* Above 0 indicate an overall increasing time trend in noise terms
+
+```{r proc-error-diff-table}
+proc_error_table("diff_mean")
+```
+
+## Observation Model Noise Terms {.tabset .tabset-pills}
+
+```{r plot-obs-resid-fn}
+obs_qresid_yrs = all_yrs[c(1,observable)]
+
+# function to plot a residual time series for one pop/origin/LH_type/age combo
+# returns a data frame with identifiers and across-year summary statistics
+plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+
+  # extract posterior samples of residual time series
+  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
+
+  # extract the year indices available
+  y_ind = get_yr_index(colnames(qresid_post))
+
+  # calculate posterior across-year mean and sd for each posterior sample
+  mn_post = apply(qresid_post, 1, mean)
+  sd_post = apply(qresid_post, 1, sd)
+
+  # calculate posterior summaries of qresidual time series
+  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+
+  # place qresiduals at correct place in a time series
+  # ie., insert missing values
+  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
+  empty[,y_ind] = qresid
+  qresid = empty[,observable]
+  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
+  empty_names = rep(NA, length(obs_qresid_yrs))
+  empty_names[y_ind] = colnames(qresid_post)
+
+  # calculate posterior mean(last half of years) - mean(first half of years)
+  y_first = 1:round(length(observable)/2)
+  y_last = (max(y_first) + 1):length(observable)
+  i_first = as.character(na.omit(empty_names[y_first]))
+  i_last = as.character(na.omit(empty_names[y_last]))
+  mn_post_first = apply(qresid_post[,i_first], 1, mean)
+  mn_post_last = apply(qresid_post[,i_last], 1, mean)
+  first_last_mn_diff_post = mn_post_last - mn_post_first
+
+  # set the y-axis limits: leave room at top for legend
+  ylim = c(0,1.3)
+
+  # blank plot with correct dimensions
+  par(lend = "square")
+  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
+
+  # draw x-axis: years
+  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
+  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
+  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
+
+  # draw the noise time series: mean and 95% CRI
+  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+
+  # draw reference line at 25%, 50%, and 75% quantiles
+  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
+
+  # draw posterior mean for first and half of time series
+  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+
+  # draw legend that shows estimate summaries
+  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
+  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+  box()
+
+  # create output for building summary tables
+  data.frame(param = qresid_param,
+             pop = ifelse(!is.null(pop), pop, NA),
+             origin = ifelse(!is.null(origin), origin, NA),
+             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
+             age = ifelse(!is.null(age), age, NA),
+             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
+             year_mean_mean = mean(mn_post),
+             year_mean_lwr = unname(quantile(mn_post, 0.025)),
+             year_mean_upr = unname(quantile(mn_post, 0.975)),
+             year_sd_mean = mean(sd_post),
+             year_sd_lwr = unname(quantile(sd_post, 0.025)),
+             year_sd_upr = unname(quantile(sd_post, 0.975)),
+             diff_mean = mean(first_last_mn_diff_post), 
+             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
+             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
+  )
 }

### 2022-04-21 03-post-process/output-plots.Rmd
Update all residual diagnostic text

@@
 
-# Residual Diagnostics {.tabset .tabset-pills}
+# Random Noise Diagnostics {.tabset .tabset-pills}
 
@@
 
+This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
+Diagnostics are separate by process model and observation model and the time series of noise terms is displayed to visually detect issues.
+Each model component (process or observation) includes summary tables that quantitatively summarize the results displayed on the time series figures.
+
 #### Why Does this Matter?
 
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
+The presence of egregious assumption violations is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
+If the assumptions are reasonably met, the noise (or "residual", representing inter-annual variability) terms should be:
+
+1.
+**Non-existent on average**: each year has an expected value and the noise term represents how far the realized value falls from the expectation, either higher or lower.
+Thus, the expectation for any given noise term is "no noise"; i.e., if the same year was replicated many times over under the same random process, the average of the realized values would be the expected value.
+2.
+**IID**: all noise terms for a process are generated by the same random process, i.e., with mean zero and common variance; noise terms are assumed independent from year to year, except in cases with an auto-regressive process included.
+3. **Free of time series patterns**: this is implied by the above two assumptions, i.e., there should be no time trends or cyclical "regime shifts."
 
@@
 
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
+Because the model used several different types of probability distributions for accounting for process and observational noise (logit-normal, log-normal, binomial, and multinomial), we wished to use a standardization technique that would enable using the same metrics to assess assumption validity for all random processes.
+We chose to use a quantile standardization, wherein the noise term for a given process in a given year is expressed as a value between zero and one and is obtained as the cumulative probability of the realized value when treating the posterior predictive distribution for that year as the CDF.
+
+For example, consider an arbitrary outcome $x_y$ in a given year from a random process with density/mass function $f()$ with parameter vector $\mathbf{\theta}$ and lower bound of $l$ (e.g., $l=-\infty$ or $l = 0$, depending on the domain of $f()$).
+The standardized residual is then:
+
+$$
+\Pr(X \leq x_y) = \int_{l}^{x_y} f(v; \mathbf{\theta}) dv
+$$
+
+If repeated realizations $x_y, x_{y+1},\dots,x_{y+n}$ are consistent with the random process $f$, then their quantile-standardized values will be distributed uniformly between zero and one (i.e., $\Pr(X \leq x_y) \sim \mathrm{U}(0,1)$).
+If the parameter vector $\mathbf{\theta}$ varies annually, then $\mathbf{\theta}_y$ can be substituted and the same uniform property should hold if the realized outcomes are consistent with both (_a_) the random process $f()$ and (_b_) the (probably deterministic) process generating inter-annual variability in $\mathbf{\theta}_y$.
+
+The interpretation of these quantile-standardized noise terms is:
+
+* **Equal to 0.5**: The realized outcome was exactly in the center of $f()$
+* **Less than 0.5**: The realized outcome was somewhere in the lower tail of $f()$, values closer to zero are more extreme noise outcomes
+* **Greater than 0.5**: The realized outcome was somewhere in the upper tail of $f()$, values closer to one are more extreme noise outcomes
+
+Because the parameter vector $\theta$ has a posterior distribution, we calculated these standardized noise terms for each MCMC sample, which provides posterior distributions of the noise terms as well.
+
+We performed this calculation for each random process (of both the observation and process components) in the model using the built-in cumulative distribution functions in JAGS.
+E.g., for some arbitrary survival term `phi` which has logit-normal process noise around the expected value `mu_phi` with logit-scale standard deviation of `sigma_phi`:
+
+```
+# priors
+mu_phi ~ dbeta(1,1)
+sigma_phi ~ dunif(0,5)
+
+for (y in 1:ny) {
+  # random process
+  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_phi^2)
+  phi[y] <- ilogit(Lphi[y])
+
+  # standardized noise term
+  phi_qresid[y] <- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_phi^2)
+}
+```
+
+Continuing with this example, suppose we have counts of tagged fish we know survived (`x_surv[y]`) and the total number of fish tagged (`n_tagged[y]`).
+We can calculate the noise term of `x_surv[y]` when assuming it is a binomial random variable using:
+
+```
+for (y in 1:ny) {
+  # likelihood statement for fitting model
+  x_surv[y] ~ dbin(phi[y], n_tagged[y])
+
+  # standardized noise term
+  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
+}
+```
+
+For multinomial random variables (i.e., adult age/origin composition), we used category-specific binomial distributions to assess noise.
+This allowed assessing the validity of age/origin-specific noise terms needed to accommodate the data.
 
@@
 
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
+For each random process in the model, the time series of standardized noise terms is plotted below:
+
+* red points/bars: year-specific posterior mean/95% CRI
+* blue horizontal lines: first and last half of time series mean values
+* grey horizontal lines: expected 25%, 50%, and 75% quantiles of the standardized residuals).
+
+To summarize these time series quantitatively, we report three across-year summary statistics:
+
+* **Across-year mean** -- intended to verify that noise terms are centered on the expected value overall (ideally equal to 0.5; the expected value of a $\mathrm{U}(0,1)$ distribution)
+* **Across-year SD** --- intended to verify that noise terms are as variable as expected overall (ideally equal to $\sqrt{1/12}$ = `r round(sqrt(1/12), 2)`; the standard deviation of a $\mathrm{U}(0,1)$ distribution)
 * **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
@@
 
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
+The posterior mean of the mean standardized noise value across all years; bold indicates the 95% CRI did not encompass the target value of 0.5.
+
+**Interpretation of Values**:
+
+* **Close to 0.5** indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
+* **Below 0.5** indicate that the time series of noise terms was biased low relative to the center of the distribution
+* **Above 0.5** indicate that the time series of noise terms was biased high relative the center of the distribution
 
@@
 
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
+The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass $\sqrt{1/12}$ = `r round(sqrt(1/12), 2)`; the standard deviation of a $\mathrm{U}(0,1)$ distribution.
+
+**Interpretation of Values**:
+
+* **Close to `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
+* **Below `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was less variable than expected
+* **Above `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was more variable than expected
 
@@
 
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
+**Interpretation of Values**:
+
+* **Close to 0** indicate a lack of an overall time trend (i.e., assumption met)
+* **Below 0** indicate an overall declining time trend in noise terms
+* **Above 0** indicate an overall increasing time trend in noise terms
 

### 2022-04-25 03-post-process/compare-sim-to-obs.Rmd
Move all output rmd sections to separate child documents

@@
     label: "Scenario"
-    value: "base"
+    value: "base-vlong"
     input: text

### 2022-04-25 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Move all output rmd sections to separate child documents

--- 2022-04-21 03-post-process/output-plots.Rmd
@@
----
-title: "Output Summary"
-subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
-date: "`r paste0('Date Rendered: ', Sys.Date())`"
-output: 
-  html_document:
-    toc: true
-    toc_float: true
-params:
-  scenario:
-    label: "Scenario"
-    value: "base"
-    input: text
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
-    input: checkbox
-  thin_percent:
-    label: "Proportion of Posterior Samples to Retain?"
-    value: 1
-    input: numeric
-editor_options: 
-  chunk_output_type: console
----
-
-```{r directories, include = F}
-# set root directory to the project directory: one level up from this location
-knitr::opts_knit$set(root.dir = "../")
-```
-
-```{r setup, include = FALSE}
-# set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
-
-# load packages
-source("00-packages.R")
-
-# load all necessary functions
-invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))
-
-# set the input directory
-in_dir = "02-model/model-output"
-
-# read information from this model
-model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
-
-# extract the posterior samples
-# post-MCMC thinning allowed to reduce run time of this document
-if (params$thin_percent < 1) {
-  post = post_thin(model_info$post, keep_percent = params$thin_percent)
-} else {
-  post = model_info$post
-}
-
-# extract the model data 
-jags_data = model_info$jags_data
-```
-
-```{r dimension-ids}
-# the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
-
-# which years are "observable" for at least some quantities?
-observable = 2:jags_data$ny_obs
-
-# which years are simulated for at least some quantities?
-simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
-
-# which years should be included in time series plots?
-if (params$include_sim_years) {
-  ts_yrs = c(observable, simulated)
-} else {
-  ts_yrs = observable
-}
-
-# which years can be plotted for SARs? Drop off last kmax years
-# since brood year adult returns not complete
-sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
-
-# population names
-pops = colnames(jags_data$Ra_obs)
-
-# origin names
-origins = c("NOR", "HOR")
-
-# dimension IDs
-i_fall   = 1  # fall migrants are i = 1
-i_spring = 2  # spring migrants are i = 2,
-o_nor    = 1  # natural origin are o = 1,
-o_hor    = 2  # hatchery origin are o = 2,
-j_cat    = 1  # Catherine Creek is j = 1
-j_los    = 2  # Lostine River is j = 2
-j_min    = 3  # Minam River is j = 3
-j_ugr    = 4  # Upper Grande Ronde River is j = 4
-k_3      = 1  # age 3 is k = 1
-k_4      = 2  # age 4 is k = 2
-k_5      = 3  # age 5 is k = 3
-
-# ko represents "age/origin" combo
-# e.g., ko = 1 is age 3 NORs
-# e.g., ko = 5 is age 4 HORs
-# these objects specify which elements of ko are for different aggregations of these
-ko_age = list(
-  ko_3 = c(1, 4),
-  ko_4 = c(2, 5),
-  ko_5 = c(3, 6)
-)
-
-ko_origin = list(
-  ko_nor = 1:3,
-  ko_hor = 4:6
-)
-
-# make the labels for which elements of the rho matrices contain unique elements
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-```
-
-# MCMC Information {.tabset .tabset-pills}
-
-## Time Information
-
-```{r mcmc-time-info}
-# Calculate hours per 10,000 iterations
-hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
-  # calculation of total iters differs if parallel or not
-  if (parallel) {
-    total_iters = n_adapt + n_post + n_burn
-  } else {
-    total_iters = (n_adapt + n_post + n_burn) * n_chains
-  }
-  ten_thousands_of_total_iters = total_iters/10000
-
-  # calculate hours elapsed
-  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
-  time_number = as.numeric(time_diff)
-  time_units = attributes(time_diff)$units
-  hour_convert = switch(time_units,
-                        "secs" = 3600,
-                        "mins" = 60,
-                        "hours" = 1,
-                        "days" = 1/24)
-  hours_diff = time_number/hour_convert
-
-  # calculate/round rate
-  round(hours_diff/ten_thousands_of_total_iters, 2)
-})
-
-# combine relevant info into a data frame
-df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
-
-# make a kable for printing in output
-kable(df) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Attributes
-
-This table shows some dimensions of the MCMC run.
-
-```{r mcmc-dims}
-# query the dimensions of the posterior samples
-dims = post_dim(post)
-
-# build a data frame for printing
-df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
-
-# render the table
-kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Sampling Diagnostics {.tabset .tabset-pills}
+# MCMC Diagnostics {.tabset .tabset-pills}
 
@@
 
-### Summary Table
+## Summary Table
 
@@
 
-### Figures {.tabset .tabset-pills}
+## Figures {.tabset .tabset-pills}
 
@@
 
-#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
-
-##### Distribution
+### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
+
+#### Distribution
 
@@
 
-##### Least Converged
+#### Least Converged
 
@@
 
-#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
+### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
+
+#### Distribution
 
@@
 
-#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
+### $\hat{R} > 1.1$ {.tabset .tabset-pills}
+
+#### Distribution
 
@@
 ```
-
-## WAIC
-
-WAIC is a measure of model parsimony.
-The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
-There are two methods of calculating `pD`, both are shown below.
-As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
-
-```{r calculate-waic, eval = model_info$do_lppd}
-summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
-  # calculate total lppd summed across all data sets within a given year
-  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
-
-  tmp_log = log(apply(exp(total_lppd), 2, mean))
-  tmp_sum = -2 * sum(tmp_log)
-
-  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
-  pD2 = sum(apply(total_lppd, 2, var))
-  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
-}
-
-waic_out = summarize_lppd("_lppd[year,.+]$")
-
-waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
-```
-
-```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
-cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
-```
-
-## Posterior Predictive Checks
-
-This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
-For each observed data point and MCMC iteration, a value was simulated from the model.
-The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
-P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
-Across years within a data set, p-values were summarized as the median and central 95% intervals.
-The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.
-
-The fit criterion differed depending on the likelihood function used to fit the model to the data set:
-
-* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
-* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation.
-This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
-This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
-
-```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
-# function to summarize bayesian p-values within a data source
-summarize_bp = function(bp) {
-  data.frame(
-    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
-    "median" = apply(bp, 2, median, na.rm = TRUE),
-    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
-    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
-    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
-    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
-  )
-}
-
-### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###
-
-# fall trap
-new = post_subset(post, "Pa_obs_new_dev", TRUE)
-obs = post_subset(post, "Pa_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
-bp = bp[,"fall-mig",]
-Pa_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Pa_bp) = NULL
-
-# spring trap
-new = post_subset(post, "^Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "^Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
-bp = bp[,"spring-mig","NOR",]
-Mb_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Mb_bp) = NULL
-
-# adult abundance
-new = post_subset(post, "Ra_obs_new_dev", TRUE)
-obs = post_subset(post, "Ra_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-Ra_bp = data.frame(
-  name = rep("Adults", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(Ra_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###
-
-# summer tagging survival
-new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-phi_Pb_Ma_bp = data.frame(
-  name = rep("Summer Tagging to LGR", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pb_Ma_bp) = NULL
-
-# fall & winter trap survival
-new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
-bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
-           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
-           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
-           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
-phi_Pa_Ma_bp = data.frame(
-  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
-  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pa_Ma_bp) = NULL
-
-# trib to lgr survival
-new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
-bp = bp[,"spring-mig",,]
-bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
-           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
-           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
-           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
-phi_Mb_Ma_bp = data.frame(
-  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
-  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
-  summarize_bp(bp)
-)
-rownames(phi_Mb_Ma_bp) = NULL
-
-# hydropower survival
-new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-phi_Ma_O0_bp = data.frame(
-  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(phi_Ma_O0_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###
-
-# summer length
-new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Pb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Pb_bp = data.frame(
-  name = rep("Summer Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Pb_bp) = NULL
-
-# spring length
-new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Mb_bp = data.frame(
-  name = rep("Spring Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Mb_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
-
-# weir composition
-new = post_subset(post, "x_Ra_new_dev", TRUE)
-obs = post_subset(post, "x_Ra_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
-x_Ra_bp = data.frame(
-  name = rep("Weir", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Ra_bp) = NULL
-
-# carcass composition
-new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
-obs = post_subset(post, "x_Sa_prime_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
-x_Sa_prime_bp = data.frame(
-  name = rep("Carcasses", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Sa_prime_bp) = NULL
-
-# pre-spawn survival
-new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
-obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-x_carcass_spawned_bp = data.frame(
-  name = rep("Prespawn", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_carcass_spawned_bp) = NULL
-
-# movement survival from BON to LGR
-new = post_subset(post, "x_LGR_new_dev", TRUE)
-obs = post_subset(post, "x_LGR_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-x_LGR_bp = data.frame(
-  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(x_LGR_bp) = NULL
-
-### COMBINE INTO ONE TABLE ###
-bp_tab = rbind(
-  Pa_bp, Mb_bp, Ra_bp,
-  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
-)
-
-# add a main data category variable
-category = rep(NA, nrow(bp_tab))
-category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
-category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
-category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
-category[is.na(category)] = "Survival"
-bp_tab = data.frame(category = category, bp_tab)
-
-# drop the several cases with no data
-# MIN HOR survival to LGR and MIN weir data
-bp_tab = bp_tab[bp_tab$N > 0,]
-
-# re-order output/misc formatting
-bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
-bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
-bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
-bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
-rownames(bp_tab) = NULL
-```
-
-```{r bayesian-pvals-table, eval = model_info$do_pp_check}
-# a function to color cells depending on the value
-assign_color = function(x) {
-  red_pal = colorRampPalette(c("white", "red"))
-  blue_pal = colorRampPalette(c("blue", "white"))
-  red_cols = red_pal(5)
-  blue_cols = blue_pal(5)
-  cols = c(blue_cols, red_cols)
-  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
-  names(cols) = bin_names
-  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-bp_tab %>%
-  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
-      align = c("lllllcccccc")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
-  column_spec(7, background = assign_color(bp_tab[,7])) %>%
-  column_spec(8, background = assign_color(bp_tab[,8])) %>%
-  column_spec(9, background = assign_color(bp_tab[,9])) %>%
-  collapse_rows(1:5) 
-```
-
-```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
-cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
-```
-
-# Fit to Data
-
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data {.tabset .tabset-pills}
-
-### Fall Parr Abundance
-
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
-```
-
-### Spring Smolt Abundance
-
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
-```
-
-### Adult Return Abundance
-
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
-```
-
-## Survival Data {.tabset .tabset-pills}
-
-### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (NOR)
-
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (HOR)
-
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
-```
-
-### LGR Smolt $\rightarrow O_0$ (NOR)
-
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### LGR Smolt $\rightarrow O_0$ (HOR)
-
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-```{r calculate-aggregated-comps-model}
-# extract the full posteriors of the two composition sets
-p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
-p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
-
-# primary containers: will store final recalculated output
-p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
-
-# number of posterior samples
-n = post_dim(post, "saved")
-
-# loop through posterior samples, calculate various aggregates of composition by type
-for (i in 1:n) {
-
-  # format the posterior draw as arrays -- easier to subset
-  p_Ra = array_format(p_Ra_full[i,])
-  p_Sa_prime = array_format(p_Sa_prime_full[i,])
-
-  ## BY AGE, AGGREGATED ACROSS ORIGINS
-
-  # containers
-  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
-  for (j in 1:jags_data$nj) {
-    for (k in 1:jags_data$nk) {
-      # calculate aggregate proportions for each age
-      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
-      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_age[,k,j] = 1:jags_data$ny
-      inds_2_age[,k,j] = k
-      inds_3_age[,k,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
-  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
-  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
-  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGES
-
-  # containers
-  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
-  for (j in 1:jags_data$nj) {
-    for (o in 1:jags_data$no) {
-      # calculate aggregate proportions for each origin
-      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
-      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_origin[,o,j] = 1:jags_data$ny
-      inds_2_origin[,o,j] = o
-      inds_3_origin[,o,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
-  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
-  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
-  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
-
-  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
-
-  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
-  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
-  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
-  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
-
-}
-
-# combine new calculated quantities into a big matrix
-q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
-
-# combine with the rest of the posterior samples
-post = post_bind(post, q_new)
-
-```
-
-```{r calculate-aggregated-comps-data}
-
-# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
-
-# containers
-x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
-
-for (j in 1:jags_data$nj) {
-  # calculate aggregate proportions for each age
-  for (k in 1:jags_data$nk) {
-    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
-    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each origin
-  for (o in 1:jags_data$no) {
-    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
-    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
-
-x_Ra_new_obs = list(
-  x_Ra_age_obs = x_Ra_age_obs,
-  x_Ra_origin_obs = x_Ra_origin_obs
-)
-
-x_Sa_prime_new_obs = list(
-  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
-  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
-)
-
-```
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-fit-funcs}
-
-# for multinomial sample size
-weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-weir_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each age, aggregated across origins
-weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
-
-##### CAT
-
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_ugr)
-```
-
-### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carc-comp-fit-funcs}
-
-# for multinomial sample size
-carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-carc_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
-}
-
-# for fits to each age, aggregated across origins
-carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
-
-##### CAT
-
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_ugr)
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
-
-junk = sapply(1:jags_data$nj, plot_f)
-```
-
-## Length Data {.tabset .tabset-pills}
-
-### Mean Length at Summer Tagging
-
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
-```
-
-### Mean Length at Spring Tagging
-
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
-```
-
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior samples of the BH productivity and capacity parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
-
-  # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
-
-  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
-  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
-
-  # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
-```
-
-## Total Eggs vs. Total Spawners
-
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
-The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
-
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(E["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(E["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
-
-  # yaxis ticks
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  abline(c(0, 1000), lty = 1)
-  abline(c(0, 1800), lty = 2)
-  abline(c(0, 3600), lty = 3)
-
-  if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-           lty = c(1,2,3), bty = "n", cex = 0.75)
-  }
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
-```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
-
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
-
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
-
-# empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
-     ylab = "Parr Capacity (000s)", yaxt = "n")
-at_y = axisTicks(par("usr")[3:4], log = FALSE)
-axis(side = 2, at = at_y, labels = at_y/1000)
-
-# draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
-
-# draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
-
-# draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
-```
-
-## Slope Parameter
-
-```{r beta-v-habitat-slope}
-# extract posterior summary of slope
-est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
-
-# print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
-```
-
-# Length Relationships {.tabset .tabset-pills}
-
-## Summer Tagging
-
-```{r}
-plot_f = function(j) {
-
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "")["mean",]
-  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
-  E_scaled_upr = post_summ(post_E, "")["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
-  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
-  plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-```
-
-## Spring Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Summer Length
-
-```{r}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-### "Growth Factor" Time Series
-
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-# Length-Based Survival Relationships {.tabset .tabset-pills}
-
-## Overwinter Survival
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
-  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
-  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
-
-  # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
-       xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-## Migration to LGR
-
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
-       xlim = range(L_Mb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
-```
-
-# Equivilency Rates {.tabset .tabset-pills}
-
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
-
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
-
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
-
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
-## Parr per Spawner
-
-"Spawner" means total spawners that survive pre-spawn mortality.
-
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-## Smolt per Spawner
-
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
-
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
-```
-
-## Spawners per Spawner
-
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
-
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
- abline(h = 1, lty = 2)
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
-```
-
-# Straying Dynamics {.tabset .tabset-pills}
-
-## Number of Strays
-
-```{r n-stray, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
-```
-
-## Stray Composition
-
-```{r stray-comp, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
-  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
-}
-
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
-```
-
-# Ocean Survival {.tabset .tabset-pills}
-
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
-```
-
-# Maturity {.tabset .tabset-pills}
-
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
-```
-
-## CAT
-
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
-```
-
-## LOS
-
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
-```
-
-## MIN
-
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
-
-## UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
-```
-
-# Parameter Summaries {.tabset .tabset-dropdown}
-
-```{r my-boxplot-function}
-my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), ...) {
-  # extract posterior samples and rename them
-  post_sub = post_subset(post, params, matrix = TRUE)
-
-  if (ncol(post_sub) >= 2) {
-    colnames(post_sub) = ticklabs
-  }
-
-  # initialize a boxplot object
-  bp = boxplot(post_sub, plot = FALSE)
-
-  # replace the summary stats with my preferred quantiles
-  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
-  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
-      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
-} 
-```
-
-## Parr Recruitment
-
-```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^alpha[.]$", "Productivity")
-my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
-my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Summer Parr Size
-
-```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^omega0[.]$", "Intercept")
-my_boxplot("^omega1[.]$", "Slope")
-my_boxplot("^sig_lL_Pb[.]$", "Process SD")
-my_boxplot("^rho_lL_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Life History Apportionment
-
-```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
-my_boxplot("^sig_Lpi[.]$", "Process SD")
-my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Overwinter Survival {.tabset .tabset-pills}
-
-### Logistic Function Parameters
-
-```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope")
-```
-
-### Process SD
-
-```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
-```
-
-### Among-pop Correlation
-
-```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to LGR {.tabset .tabset-pills}
-
-### Mean/Logistic Model Parameters
-
-```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("tau0[pop]", pop = "."), "Intercept", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("tau1[pop]", pop = "."), "Slope", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to Ocean
-
-```{r lgr-to-ocean-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Means
-
-```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
-
-### Means
-
-```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Ocean Survival {.tabset .tabset-pills}
-
-### Year 1 {.tabset .tabset-pills}
-
-#### Mean
-
-```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-#### Process SD and Correlation
-
-```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
-my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
-```
-
-### Year 2 {.tabset .tabset-pills}
-
-```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### Year 3 {.tabset .tabset-pills}
-
-```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### NOR:HOR Log Odds Ratios
-
-```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("delta_O0_O1[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 1")
-my_boxplot(sub_index("delta_O1_O2[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 2")
-my_boxplot(sub_index("delta_O2_O3[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 3")
-```
-
-## Movement Survival BON to LGR
-
-```{r bon-to-lgr-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Pre-spawn Survival
-
-```{r prespawn-surv-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
-my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
-my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
-```
-
-# Correlation Parameters
-
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
-)
-
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
-
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
-
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
-
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
-
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
-abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
-box()
-```
-
-# Residual Diagnostics {.tabset .tabset-pills}
-
-```{r misc-resid-fns}
-get_yr_index = function(params) {
-  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
-  yr_index = stringr::str_remove(yr_index, "\\[")
-  yr_index = stringr::str_remove(yr_index, ",")
-  as.numeric(yr_index)
-}
-
-make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
-  f = function(x) {
-    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
-    xs = round(xs, 2)
-    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
-  }
-  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
-}
-
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
-no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
-}
-```
-
-#### Why Does this Matter?
-
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
-
-#### What was Calculated?
-
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
-
-#### What is Shown?
-
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
-* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
-
-These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
-They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
-
-## Process Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-proc-resid-fn}
-
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-  y_ind_obs = y_ind %in% observable
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(y_ind[y_ind_obs])/2)
-  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(qresid_post[,y_first], 1, mean)
-  mn_post_last = apply(qresid_post[,y_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-    # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-  )
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-obs_error_ests = NULL
-```
-
-### Abundance Data {.tabset .tabset-pills}
-
-#### Fall Parr Abundance
-
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt Abundance
-
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Adult Return Abundance
-
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Survival Data {.tabset .tabset-pills}
-
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### BON Adults $\rightarrow$ LGR
-
-```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Length Data {.tabset .tabset-pills}
-
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Composition Data {.tabset .tabset-pills}
-
-#### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-resid-plots-fn}
-ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
-             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
-
-weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-_No weir data for MIN_
-
-##### UGR
-
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-#### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carcass-comp-resid-plots-fn}
-carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_min)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### UGR
-
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r obs-error-table-prep}
-# rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
-
-# correct parameter names
-obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
-obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
-obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
-obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
-
-# correct origin indices
-obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
-obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
-
-# correct LH_type indices
-obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
-
-# correct pop indices
-obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
-
-# correct origin indices based on age indices
-obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
-obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
-
-# replace indices with names
-obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
-obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
-obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
-obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
-obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
-
-# add a type column
-obs_error_ests$type = NA
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
-
-# add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
-obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
-obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
-obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
-obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
-
-# drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r obs-error-table-fn}
-obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:5)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r obs-error-mean-table}
-obs_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r obs-error-sd-table}
-obs_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r obs-error-diff-table}
-obs_error_table("diff_mean")
-```
-
-# JAGS Model and Data {.tabset .tabset-pills}
-
-## JAGS Model Code
-
-```{r jags-model, comment = NA}
-# print the JAGS model code
-cat(model_info$jags_model_code, sep = "\n")
-```
-
-## JAGS Model Data
-
-```{r jags-data, comment = NA}
-# print the JAGS model data
-model_info$jags_data
-```

### 2022-04-25 03-post-process/output-plots-children/03a-pp-checks.Rmd
Move all output rmd sections to separate child documents

--- 2022-04-21 03-post-process/output-plots.Rmd
@@
----
-title: "Output Summary"
-subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
-date: "`r paste0('Date Rendered: ', Sys.Date())`"
-output: 
-  html_document:
-    toc: true
-    toc_float: true
-params:
-  scenario:
-    label: "Scenario"
-    value: "base"
-    input: text
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
-    input: checkbox
-  thin_percent:
-    label: "Proportion of Posterior Samples to Retain?"
-    value: 1
-    input: numeric
-editor_options: 
-  chunk_output_type: console
----
-
-```{r directories, include = F}
-# set root directory to the project directory: one level up from this location
-knitr::opts_knit$set(root.dir = "../")
-```
-
-```{r setup, include = FALSE}
-# set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
-
-# load packages
-source("00-packages.R")
-
-# load all necessary functions
-invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))
-
-# set the input directory
-in_dir = "02-model/model-output"
-
-# read information from this model
-model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
-
-# extract the posterior samples
-# post-MCMC thinning allowed to reduce run time of this document
-if (params$thin_percent < 1) {
-  post = post_thin(model_info$post, keep_percent = params$thin_percent)
-} else {
-  post = model_info$post
-}
-
-# extract the model data 
-jags_data = model_info$jags_data
-```
-
-```{r dimension-ids}
-# the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
-
-# which years are "observable" for at least some quantities?
-observable = 2:jags_data$ny_obs
-
-# which years are simulated for at least some quantities?
-simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
-
-# which years should be included in time series plots?
-if (params$include_sim_years) {
-  ts_yrs = c(observable, simulated)
-} else {
-  ts_yrs = observable
-}
-
-# which years can be plotted for SARs? Drop off last kmax years
-# since brood year adult returns not complete
-sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
-
-# population names
-pops = colnames(jags_data$Ra_obs)
-
-# origin names
-origins = c("NOR", "HOR")
-
-# dimension IDs
-i_fall   = 1  # fall migrants are i = 1
-i_spring = 2  # spring migrants are i = 2,
-o_nor    = 1  # natural origin are o = 1,
-o_hor    = 2  # hatchery origin are o = 2,
-j_cat    = 1  # Catherine Creek is j = 1
-j_los    = 2  # Lostine River is j = 2
-j_min    = 3  # Minam River is j = 3
-j_ugr    = 4  # Upper Grande Ronde River is j = 4
-k_3      = 1  # age 3 is k = 1
-k_4      = 2  # age 4 is k = 2
-k_5      = 3  # age 5 is k = 3
-
-# ko represents "age/origin" combo
-# e.g., ko = 1 is age 3 NORs
-# e.g., ko = 5 is age 4 HORs
-# these objects specify which elements of ko are for different aggregations of these
-ko_age = list(
-  ko_3 = c(1, 4),
-  ko_4 = c(2, 5),
-  ko_5 = c(3, 6)
-)
-
-ko_origin = list(
-  ko_nor = 1:3,
-  ko_hor = 4:6
-)
-
-# make the labels for which elements of the rho matrices contain unique elements
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-```
-
-# MCMC Information {.tabset .tabset-pills}
-
-## Time Information
-
-```{r mcmc-time-info}
-# Calculate hours per 10,000 iterations
-hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
-  # calculation of total iters differs if parallel or not
-  if (parallel) {
-    total_iters = n_adapt + n_post + n_burn
-  } else {
-    total_iters = (n_adapt + n_post + n_burn) * n_chains
-  }
-  ten_thousands_of_total_iters = total_iters/10000
-
-  # calculate hours elapsed
-  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
-  time_number = as.numeric(time_diff)
-  time_units = attributes(time_diff)$units
-  hour_convert = switch(time_units,
-                        "secs" = 3600,
-                        "mins" = 60,
-                        "hours" = 1,
-                        "days" = 1/24)
-  hours_diff = time_number/hour_convert
-
-  # calculate/round rate
-  round(hours_diff/ten_thousands_of_total_iters, 2)
-})
-
-# combine relevant info into a data frame
-df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
-
-# make a kable for printing in output
-kable(df) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Attributes
-
-This table shows some dimensions of the MCMC run.
-
-```{r mcmc-dims}
-# query the dimensions of the posterior samples
-dims = post_dim(post)
-
-# build a data frame for printing
-df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
-
-# render the table
-kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Sampling Diagnostics {.tabset .tabset-pills}
-
-```{r make-diag-post}
-# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
-# there is no point in calculating diagnostic summaries for future years
-if (length(simulated) > 0) {
-  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
-} else {
-  diag_post = post
-}
-
-# discard duplicate correlation terms: all rho parameters for a given process are equal
-all_rho = match_params(post, "^rho")
-rho_keep = match_params(post, "^rho_.+[2,1")
-rho_discard = all_rho[!(all_rho %in% rho_keep)]
-diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
-```
-
-```{r mcmc-diag-function}
-# a function to get MCMC diagnoses for a group of parameters
-# params: a string to match with postpack::match_params()
-# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
-# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
-# L3: a "Level-3" group label; such as NOR or HOR
-
-summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
-  # extract the posteriors of interest and format for 'posterior' package
-  post_sub = as_draws_df(post_subset(diag_post, params))
-
-  # summarize the posteriors
-  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
-
-  # discard any parameters that were the same value every MCMC iteration
-  # (will have an NA for rhat)
-  diags = diags[!is.na(diags$rhat),]
-
-  # append the level names and return
-  cbind(
-    L1 = L1, L2 = L2, L3 = L3,
-    diags
-  )
-}
-
-summarize_diags = function(diags) {
-
-  # add "Monte Carlo CV"
-  diags$mccv_mean = diags$mcse_mean/diags$mean
-  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
-  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
-
-  # summarize the summaries
-  data.frame(
-    L1 = unique(diags$L1),
-    L2 = unique(diags$L2),
-    L3 = unique(diags$L3),
-    match = unique(postpack:::drop_index(diags$variable)),
-    n_params = nrow(diags),
-    Rhat_1.01 = sum(diags$rhat >= 1.01),
-    Rhat_1.05 = sum(diags$rhat >= 1.05),
-    Rhat_1.1 = sum(diags$rhat >= 1.1),
-    Rhat_1.2 = sum(diags$rhat >= 1.2),
-    ess_mean_400 = sum(diags$ess_mean < 400),
-    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
-    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
-    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
-    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
-    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
-  )
-}
-```
-
-```{r calculate-mcmc-diagnostics}
-# containers
-diags_out = NULL
-summs_out = NULL
-
-# parr recruitment
-L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# summer parr mean length
-L1 = "Density-Dependent Summer Length"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LH apportionment
-L1 = "Life History Apportionment"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# parr survival from summer to winter tagging
-L1 = "Survival From Summer to Winter"
-match = c("phi_Pb_Pa[2,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Fall Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Spring Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# growth from summer to spring
-# summer parr mean length
-L1 = "Summer to Spring 'Growth Factor'"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: NOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
-match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: HOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: NOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: HOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Probability of Maturing at Age-3: NOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-3: HOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: NOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: HOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 1 ocean survival
-L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Misc ocean survival
-L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
-match = sub_index(base, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: NOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: HOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Pre-spawn Survival
-L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Carcass Correction
-L1 = "Carcass Correction Factor"
-L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
-match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Initial adult recruitment
-L1 = "Initial Adult Returns"
-L2 = c("Age-3", "Age-4", "Age-5")
-match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Straying
-L1 = "Strays"
-L2 = c("Realized Total Number", "Age Comp")
-match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# remove any summaries for nodes that don't have diagnostics
-# e.g., if that "parameter" takes on a fixed value in the model
-diags_table = summs_out
-diags_table = diags_table[diags_table$n_params > 0,]
-```
-
-### Summary Table
-
-This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
-Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
-Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
-
-* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
-* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
-* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
-
-The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
-
-```{r mcmc-diag-table, warning = FALSE}
-# duplicate the diagnostic output
-kable_table = diags_table
-
-# order the rows
-kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
-kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]
-
-# keep only relevant columns for kable
-kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]
-
-# convert counts of offending parameters to percentages
-kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")
-
-# add basic formatting
-colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
-kable_table$Group[is.na(kable_table$Group)] = " "
-kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "
-
-assign_color = function(x, colors = c("white","red")) {
-  pal = colorRampPalette(colors)
-  cols = pal(6)
-  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
-  names(cols) = bin_names
-  x[is.na(x)] = 0
-  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
-  column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,8,11), border_right = TRUE) %>%
-  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
-  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
-  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
-  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
-  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
-  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
-  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
-  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
-  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
-  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
-  collapse_rows(columns = 1:2)
-```
-
-### Figures {.tabset .tabset-pills}
-
-```{r mcmc-diag-plots-prep}
-n_max_draw = 30
-
-# which parameters fall in each Rhat bin
-rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
-rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
-rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
-
-# extract the Rhat values and the names of the parameters with the 
-# worst Rhat values by bin
-rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
-rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
-rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
-rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
-rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
-rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]
-
-# subset out these parameters: makes postpack::diag_plots() much faster
-post_sub_1 = post_subset(post, rhat_1_params_draw)
-post_sub_2 = post_subset(post, rhat_2_params_draw)
-post_sub_3 = post_subset(post, rhat_3_params_draw)
-
-# function to plot a histogram of rhat values
-rhat_hist = function(rhat) {
-  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
-  breaks = seq(min(rhat), max(rhat), length = 20)
-  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
-  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
-  usr = par("usr")
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
-}
-```
-
-#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
-
-```{r rhat-hist-1, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_1)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_1, "", show_diags = "never")
-```
-
-#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-2, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_2)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_2, "", show_diags = "never")
-```
-
-#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-3, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_3)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_3, "", show_diags = "never")
-```
-
-## WAIC
-
-WAIC is a measure of model parsimony.
-The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
-There are two methods of calculating `pD`, both are shown below.
-As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
-
-```{r calculate-waic, eval = model_info$do_lppd}
-summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
-  # calculate total lppd summed across all data sets within a given year
-  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
-
-  tmp_log = log(apply(exp(total_lppd), 2, mean))
-  tmp_sum = -2 * sum(tmp_log)
-
-  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
-  pD2 = sum(apply(total_lppd, 2, var))
-  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
-}
-
-waic_out = summarize_lppd("_lppd[year,.+]$")
-
-waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
-```
-
-```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
-cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
-```
-
 ## Posterior Predictive Checks
@@
 The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
-P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
+
+P-values close to 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
+
 Across years within a data set, p-values were summarized as the median and central 95% intervals. 
@@
 This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
-This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
+* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities by performing calculations on the square root of observed and expected counts..
+This applies to all composition data, the survival from BON to LGR data, and the spawn status data.
 
-```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
+```{r calculate-bayesian-pvals}
 # function to summarize bayesian p-values within a data source
@@
 
-```{r bayesian-pvals-table, eval = model_info$do_pp_check}
+```{r bayesian-pvals-table}
 # a function to color cells depending on the value
@@
 ```
-
-```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
-cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
-```
-
-# Fit to Data
-
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data {.tabset .tabset-pills}
-
-### Fall Parr Abundance
-
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
-```
-
-### Spring Smolt Abundance
-
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
-```
-
-### Adult Return Abundance
-
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
-```
-
-## Survival Data {.tabset .tabset-pills}
-
-### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (NOR)
-
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (HOR)
-
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
-```
-
-### LGR Smolt $\rightarrow O_0$ (NOR)
-
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### LGR Smolt $\rightarrow O_0$ (HOR)
-
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-```{r calculate-aggregated-comps-model}
-# extract the full posteriors of the two composition sets
-p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
-p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
-
-# primary containers: will store final recalculated output
-p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
-
-# number of posterior samples
-n = post_dim(post, "saved")
-
-# loop through posterior samples, calculate various aggregates of composition by type
-for (i in 1:n) {
-
-  # format the posterior draw as arrays -- easier to subset
-  p_Ra = array_format(p_Ra_full[i,])
-  p_Sa_prime = array_format(p_Sa_prime_full[i,])
-
-  ## BY AGE, AGGREGATED ACROSS ORIGINS
-
-  # containers
-  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
-  for (j in 1:jags_data$nj) {
-    for (k in 1:jags_data$nk) {
-      # calculate aggregate proportions for each age
-      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
-      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_age[,k,j] = 1:jags_data$ny
-      inds_2_age[,k,j] = k
-      inds_3_age[,k,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
-  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
-  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
-  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGES
-
-  # containers
-  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
-  for (j in 1:jags_data$nj) {
-    for (o in 1:jags_data$no) {
-      # calculate aggregate proportions for each origin
-      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
-      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_origin[,o,j] = 1:jags_data$ny
-      inds_2_origin[,o,j] = o
-      inds_3_origin[,o,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
-  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
-  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
-  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
-
-  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
-
-  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
-  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
-  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
-  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
-
-}
-
-# combine new calculated quantities into a big matrix
-q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
-
-# combine with the rest of the posterior samples
-post = post_bind(post, q_new)
-
-```
-
-```{r calculate-aggregated-comps-data}
-
-# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
-
-# containers
-x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
-
-for (j in 1:jags_data$nj) {
-  # calculate aggregate proportions for each age
-  for (k in 1:jags_data$nk) {
-    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
-    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each origin
-  for (o in 1:jags_data$no) {
-    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
-    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
-
-x_Ra_new_obs = list(
-  x_Ra_age_obs = x_Ra_age_obs,
-  x_Ra_origin_obs = x_Ra_origin_obs
-)
-
-x_Sa_prime_new_obs = list(
-  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
-  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
-)
-
-```
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-fit-funcs}
-
-# for multinomial sample size
-weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-weir_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each age, aggregated across origins
-weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
-
-##### CAT
-
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_ugr)
-```
-
-### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carc-comp-fit-funcs}
-
-# for multinomial sample size
-carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-carc_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
-}
-
-# for fits to each age, aggregated across origins
-carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
-
-##### CAT
-
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_ugr)
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
-
-junk = sapply(1:jags_data$nj, plot_f)
-```
-
-## Length Data {.tabset .tabset-pills}
-
-### Mean Length at Summer Tagging
-
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
-```
-
-### Mean Length at Spring Tagging
-
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
-```
-
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior samples of the BH productivity and capacity parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
-
-  # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
-
-  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
-  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
-
-  # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
-```
-
-## Total Eggs vs. Total Spawners
-
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
-The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
-
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(E["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(E["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
-
-  # yaxis ticks
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  abline(c(0, 1000), lty = 1)
-  abline(c(0, 1800), lty = 2)
-  abline(c(0, 3600), lty = 3)
-
-  if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-           lty = c(1,2,3), bty = "n", cex = 0.75)
-  }
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
-```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
-
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
-
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
-
-# empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
-     ylab = "Parr Capacity (000s)", yaxt = "n")
-at_y = axisTicks(par("usr")[3:4], log = FALSE)
-axis(side = 2, at = at_y, labels = at_y/1000)
-
-# draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
-
-# draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
-
-# draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
-```
-
-## Slope Parameter
-
-```{r beta-v-habitat-slope}
-# extract posterior summary of slope
-est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
-
-# print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
-```
-
-# Length Relationships {.tabset .tabset-pills}
-
-## Summer Tagging
-
-```{r}
-plot_f = function(j) {
-
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "")["mean",]
-  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
-  E_scaled_upr = post_summ(post_E, "")["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
-  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
-  plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-```
-
-## Spring Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Summer Length
-
-```{r}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-### "Growth Factor" Time Series
-
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-# Length-Based Survival Relationships {.tabset .tabset-pills}
-
-## Overwinter Survival
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
-  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
-  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
-
-  # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
-       xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-## Migration to LGR
-
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
-       xlim = range(L_Mb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
-```
-
-# Equivilency Rates {.tabset .tabset-pills}
-
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
-
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
-
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
-
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
-## Parr per Spawner
-
-"Spawner" means total spawners that survive pre-spawn mortality.
-
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-## Smolt per Spawner
-
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
-
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
-```
-
-## Spawners per Spawner
-
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
-
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
- abline(h = 1, lty = 2)
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
-```
-
-# Straying Dynamics {.tabset .tabset-pills}
-
-## Number of Strays
-
-```{r n-stray, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
-```
-
-## Stray Composition
-
-```{r stray-comp, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
-  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
-}
-
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
-```
-
-# Ocean Survival {.tabset .tabset-pills}
-
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
-```
-
-# Maturity {.tabset .tabset-pills}
-
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
-```
-
-## CAT
-
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
-```
-
-## LOS
-
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
-```
-
-## MIN
-
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
-
-## UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
-```
-
-# Parameter Summaries {.tabset .tabset-dropdown}
-
-```{r my-boxplot-function}
-my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), ...) {
-  # extract posterior samples and rename them
-  post_sub = post_subset(post, params, matrix = TRUE)
-
-  if (ncol(post_sub) >= 2) {
-    colnames(post_sub) = ticklabs
-  }
-
-  # initialize a boxplot object
-  bp = boxplot(post_sub, plot = FALSE)
-
-  # replace the summary stats with my preferred quantiles
-  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
-  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
-      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
-} 
-```
-
-## Parr Recruitment
-
-```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^alpha[.]$", "Productivity")
-my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
-my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Summer Parr Size
-
-```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^omega0[.]$", "Intercept")
-my_boxplot("^omega1[.]$", "Slope")
-my_boxplot("^sig_lL_Pb[.]$", "Process SD")
-my_boxplot("^rho_lL_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Life History Apportionment
-
-```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
-my_boxplot("^sig_Lpi[.]$", "Process SD")
-my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Overwinter Survival {.tabset .tabset-pills}
-
-### Logistic Function Parameters
-
-```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope")
-```
-
-### Process SD
-
-```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
-```
-
-### Among-pop Correlation
-
-```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to LGR {.tabset .tabset-pills}
-
-### Mean/Logistic Model Parameters
-
-```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("tau0[pop]", pop = "."), "Intercept", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("tau1[pop]", pop = "."), "Slope", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to Ocean
-
-```{r lgr-to-ocean-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Means
-
-```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
-
-### Means
-
-```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Ocean Survival {.tabset .tabset-pills}
-
-### Year 1 {.tabset .tabset-pills}
-
-#### Mean
-
-```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-#### Process SD and Correlation
-
-```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
-my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
-```
-
-### Year 2 {.tabset .tabset-pills}
-
-```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### Year 3 {.tabset .tabset-pills}
-
-```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### NOR:HOR Log Odds Ratios
-
-```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("delta_O0_O1[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 1")
-my_boxplot(sub_index("delta_O1_O2[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 2")
-my_boxplot(sub_index("delta_O2_O3[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 3")
-```
-
-## Movement Survival BON to LGR
-
-```{r bon-to-lgr-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Pre-spawn Survival
-
-```{r prespawn-surv-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
-my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
-my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
-```
-
-# Correlation Parameters
-
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
-)
-
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
-
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
-
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
-
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
-
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
-abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
-box()
-```
-
-# Residual Diagnostics {.tabset .tabset-pills}
-
-```{r misc-resid-fns}
-get_yr_index = function(params) {
-  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
-  yr_index = stringr::str_remove(yr_index, "\\[")
-  yr_index = stringr::str_remove(yr_index, ",")
-  as.numeric(yr_index)
-}
-
-make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
-  f = function(x) {
-    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
-    xs = round(xs, 2)
-    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
-  }
-  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
-}
-
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
-no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
-}
-```
-
-#### Why Does this Matter?
-
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
-
-#### What was Calculated?
-
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
-
-#### What is Shown?
-
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
-* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
-
-These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
-They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
-
-## Process Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-proc-resid-fn}
-
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-  y_ind_obs = y_ind %in% observable
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(y_ind[y_ind_obs])/2)
-  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(qresid_post[,y_first], 1, mean)
-  mn_post_last = apply(qresid_post[,y_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-    # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-  )
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-obs_error_ests = NULL
-```
-
-### Abundance Data {.tabset .tabset-pills}
-
-#### Fall Parr Abundance
-
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt Abundance
-
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Adult Return Abundance
-
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Survival Data {.tabset .tabset-pills}
-
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### BON Adults $\rightarrow$ LGR
-
-```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Length Data {.tabset .tabset-pills}
-
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Composition Data {.tabset .tabset-pills}
-
-#### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-resid-plots-fn}
-ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
-             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
-
-weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-_No weir data for MIN_
-
-##### UGR
-
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-#### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carcass-comp-resid-plots-fn}
-carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_min)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### UGR
-
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r obs-error-table-prep}
-# rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
-
-# correct parameter names
-obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
-obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
-obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
-obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
-
-# correct origin indices
-obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
-obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
-
-# correct LH_type indices
-obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
-
-# correct pop indices
-obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
-
-# correct origin indices based on age indices
-obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
-obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
-
-# replace indices with names
-obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
-obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
-obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
-obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
-obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
-
-# add a type column
-obs_error_ests$type = NA
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
-
-# add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
-obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
-obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
-obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
-obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
-
-# drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r obs-error-table-fn}
-obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:5)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r obs-error-mean-table}
-obs_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r obs-error-sd-table}
-obs_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r obs-error-diff-table}
-obs_error_table("diff_mean")
-```
-
-# JAGS Model and Data {.tabset .tabset-pills}
-
-## JAGS Model Code
-
-```{r jags-model, comment = NA}
-# print the JAGS model code
-cat(model_info$jags_model_code, sep = "\n")
-```
-
-## JAGS Model Data
-
-```{r jags-data, comment = NA}
-# print the JAGS model data
-model_info$jags_data
-```

### 2022-04-25 03-post-process/output-plots-children/05-length-based-values.Rmd
Move all output rmd sections to separate child documents

--- 2022-04-21 03-post-process/output-plots.Rmd
@@
----
-title: "Output Summary"
-subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
-date: "`r paste0('Date Rendered: ', Sys.Date())`"
-output: 
-  html_document:
-    toc: true
-    toc_float: true
-params:
-  scenario:
-    label: "Scenario"
-    value: "base"
-    input: text
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
-    input: checkbox
-  thin_percent:
-    label: "Proportion of Posterior Samples to Retain?"
-    value: 1
-    input: numeric
-editor_options: 
-  chunk_output_type: console
----
-
-```{r directories, include = F}
-# set root directory to the project directory: one level up from this location
-knitr::opts_knit$set(root.dir = "../")
-```
-
-```{r setup, include = FALSE}
-# set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
-
-# load packages
-source("00-packages.R")
-
-# load all necessary functions
-invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))
-
-# set the input directory
-in_dir = "02-model/model-output"
-
-# read information from this model
-model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
-
-# extract the posterior samples
-# post-MCMC thinning allowed to reduce run time of this document
-if (params$thin_percent < 1) {
-  post = post_thin(model_info$post, keep_percent = params$thin_percent)
-} else {
-  post = model_info$post
-}
-
-# extract the model data 
-jags_data = model_info$jags_data
-```
-
-```{r dimension-ids}
-# the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
-
-# which years are "observable" for at least some quantities?
-observable = 2:jags_data$ny_obs
-
-# which years are simulated for at least some quantities?
-simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
-
-# which years should be included in time series plots?
-if (params$include_sim_years) {
-  ts_yrs = c(observable, simulated)
-} else {
-  ts_yrs = observable
-}
-
-# which years can be plotted for SARs? Drop off last kmax years
-# since brood year adult returns not complete
-sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
-
-# population names
-pops = colnames(jags_data$Ra_obs)
-
-# origin names
-origins = c("NOR", "HOR")
-
-# dimension IDs
-i_fall   = 1  # fall migrants are i = 1
-i_spring = 2  # spring migrants are i = 2,
-o_nor    = 1  # natural origin are o = 1,
-o_hor    = 2  # hatchery origin are o = 2,
-j_cat    = 1  # Catherine Creek is j = 1
-j_los    = 2  # Lostine River is j = 2
-j_min    = 3  # Minam River is j = 3
-j_ugr    = 4  # Upper Grande Ronde River is j = 4
-k_3      = 1  # age 3 is k = 1
-k_4      = 2  # age 4 is k = 2
-k_5      = 3  # age 5 is k = 3
-
-# ko represents "age/origin" combo
-# e.g., ko = 1 is age 3 NORs
-# e.g., ko = 5 is age 4 HORs
-# these objects specify which elements of ko are for different aggregations of these
-ko_age = list(
-  ko_3 = c(1, 4),
-  ko_4 = c(2, 5),
-  ko_5 = c(3, 6)
-)
-
-ko_origin = list(
-  ko_nor = 1:3,
-  ko_hor = 4:6
-)
-
-# make the labels for which elements of the rho matrices contain unique elements
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-```
-
-# MCMC Information {.tabset .tabset-pills}
-
-## Time Information
-
-```{r mcmc-time-info}
-# Calculate hours per 10,000 iterations
-hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
-  # calculation of total iters differs if parallel or not
-  if (parallel) {
-    total_iters = n_adapt + n_post + n_burn
-  } else {
-    total_iters = (n_adapt + n_post + n_burn) * n_chains
-  }
-  ten_thousands_of_total_iters = total_iters/10000
-
-  # calculate hours elapsed
-  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
-  time_number = as.numeric(time_diff)
-  time_units = attributes(time_diff)$units
-  hour_convert = switch(time_units,
-                        "secs" = 3600,
-                        "mins" = 60,
-                        "hours" = 1,
-                        "days" = 1/24)
-  hours_diff = time_number/hour_convert
-
-  # calculate/round rate
-  round(hours_diff/ten_thousands_of_total_iters, 2)
-})
-
-# combine relevant info into a data frame
-df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
-
-# make a kable for printing in output
-kable(df) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Attributes
-
-This table shows some dimensions of the MCMC run.
-
-```{r mcmc-dims}
-# query the dimensions of the posterior samples
-dims = post_dim(post)
-
-# build a data frame for printing
-df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
-
-# render the table
-kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Sampling Diagnostics {.tabset .tabset-pills}
-
-```{r make-diag-post}
-# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
-# there is no point in calculating diagnostic summaries for future years
-if (length(simulated) > 0) {
-  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
-} else {
-  diag_post = post
-}
-
-# discard duplicate correlation terms: all rho parameters for a given process are equal
-all_rho = match_params(post, "^rho")
-rho_keep = match_params(post, "^rho_.+[2,1")
-rho_discard = all_rho[!(all_rho %in% rho_keep)]
-diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
-```
-
-```{r mcmc-diag-function}
-# a function to get MCMC diagnoses for a group of parameters
-# params: a string to match with postpack::match_params()
-# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
-# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
-# L3: a "Level-3" group label; such as NOR or HOR
-
-summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
-  # extract the posteriors of interest and format for 'posterior' package
-  post_sub = as_draws_df(post_subset(diag_post, params))
-
-  # summarize the posteriors
-  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
-
-  # discard any parameters that were the same value every MCMC iteration
-  # (will have an NA for rhat)
-  diags = diags[!is.na(diags$rhat),]
-
-  # append the level names and return
-  cbind(
-    L1 = L1, L2 = L2, L3 = L3,
-    diags
-  )
-}
-
-summarize_diags = function(diags) {
-
-  # add "Monte Carlo CV"
-  diags$mccv_mean = diags$mcse_mean/diags$mean
-  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
-  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
-
-  # summarize the summaries
-  data.frame(
-    L1 = unique(diags$L1),
-    L2 = unique(diags$L2),
-    L3 = unique(diags$L3),
-    match = unique(postpack:::drop_index(diags$variable)),
-    n_params = nrow(diags),
-    Rhat_1.01 = sum(diags$rhat >= 1.01),
-    Rhat_1.05 = sum(diags$rhat >= 1.05),
-    Rhat_1.1 = sum(diags$rhat >= 1.1),
-    Rhat_1.2 = sum(diags$rhat >= 1.2),
-    ess_mean_400 = sum(diags$ess_mean < 400),
-    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
-    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
-    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
-    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
-    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
-  )
-}
-```
-
-```{r calculate-mcmc-diagnostics}
-# containers
-diags_out = NULL
-summs_out = NULL
-
-# parr recruitment
-L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# summer parr mean length
-L1 = "Density-Dependent Summer Length"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LH apportionment
-L1 = "Life History Apportionment"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# parr survival from summer to winter tagging
-L1 = "Survival From Summer to Winter"
-match = c("phi_Pb_Pa[2,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Fall Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Spring Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# growth from summer to spring
-# summer parr mean length
-L1 = "Summer to Spring 'Growth Factor'"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: NOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
-match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: HOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: NOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: HOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Probability of Maturing at Age-3: NOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-3: HOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: NOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: HOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 1 ocean survival
-L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Misc ocean survival
-L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
-match = sub_index(base, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: NOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: HOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Pre-spawn Survival
-L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Carcass Correction
-L1 = "Carcass Correction Factor"
-L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
-match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Initial adult recruitment
-L1 = "Initial Adult Returns"
-L2 = c("Age-3", "Age-4", "Age-5")
-match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Straying
-L1 = "Strays"
-L2 = c("Realized Total Number", "Age Comp")
-match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# remove any summaries for nodes that don't have diagnostics
-# e.g., if that "parameter" takes on a fixed value in the model
-diags_table = summs_out
-diags_table = diags_table[diags_table$n_params > 0,]
-```
-
-### Summary Table
-
-This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
-Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
-Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
-
-* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
-* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
-* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
-
-The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
-
-```{r mcmc-diag-table, warning = FALSE}
-# duplicate the diagnostic output
-kable_table = diags_table
-
-# order the rows
-kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
-kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]
-
-# keep only relevant columns for kable
-kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]
-
-# convert counts of offending parameters to percentages
-kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")
-
-# add basic formatting
-colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
-kable_table$Group[is.na(kable_table$Group)] = " "
-kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "
-
-assign_color = function(x, colors = c("white","red")) {
-  pal = colorRampPalette(colors)
-  cols = pal(6)
-  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
-  names(cols) = bin_names
-  x[is.na(x)] = 0
-  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
-  column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,8,11), border_right = TRUE) %>%
-  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
-  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
-  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
-  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
-  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
-  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
-  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
-  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
-  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
-  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
-  collapse_rows(columns = 1:2)
-```
-
-### Figures {.tabset .tabset-pills}
-
-```{r mcmc-diag-plots-prep}
-n_max_draw = 30
-
-# which parameters fall in each Rhat bin
-rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
-rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
-rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
-
-# extract the Rhat values and the names of the parameters with the 
-# worst Rhat values by bin
-rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
-rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
-rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
-rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
-rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
-rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]
-
-# subset out these parameters: makes postpack::diag_plots() much faster
-post_sub_1 = post_subset(post, rhat_1_params_draw)
-post_sub_2 = post_subset(post, rhat_2_params_draw)
-post_sub_3 = post_subset(post, rhat_3_params_draw)
-
-# function to plot a histogram of rhat values
-rhat_hist = function(rhat) {
-  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
-  breaks = seq(min(rhat), max(rhat), length = 20)
-  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
-  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
-  usr = par("usr")
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
-}
-```
-
-#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
-
-```{r rhat-hist-1, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_1)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_1, "", show_diags = "never")
-```
-
-#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-2, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_2)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_2, "", show_diags = "never")
-```
-
-#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-3, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_3)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_3, "", show_diags = "never")
-```
-
-## WAIC
-
-WAIC is a measure of model parsimony.
-The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
-There are two methods of calculating `pD`, both are shown below.
-As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
-
-```{r calculate-waic, eval = model_info$do_lppd}
-summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
-  # calculate total lppd summed across all data sets within a given year
-  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
-
-  tmp_log = log(apply(exp(total_lppd), 2, mean))
-  tmp_sum = -2 * sum(tmp_log)
-
-  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
-  pD2 = sum(apply(total_lppd, 2, var))
-  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
-}
-
-waic_out = summarize_lppd("_lppd[year,.+]$")
-
-waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
-```
-
-```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
-cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
-```
-
-## Posterior Predictive Checks
-
-This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
-For each observed data point and MCMC iteration, a value was simulated from the model.
-The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
-P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
-Across years within a data set, p-values were summarized as the median and central 95% intervals.
-The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.
-
-The fit criterion differed depending on the likelihood function used to fit the model to the data set:
-
-* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
-* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation.
-This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
-This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
-
-```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
-# function to summarize bayesian p-values within a data source
-summarize_bp = function(bp) {
-  data.frame(
-    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
-    "median" = apply(bp, 2, median, na.rm = TRUE),
-    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
-    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
-    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
-    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
-  )
-}
-
-### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###
-
-# fall trap
-new = post_subset(post, "Pa_obs_new_dev", TRUE)
-obs = post_subset(post, "Pa_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
-bp = bp[,"fall-mig",]
-Pa_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Pa_bp) = NULL
-
-# spring trap
-new = post_subset(post, "^Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "^Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
-bp = bp[,"spring-mig","NOR",]
-Mb_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Mb_bp) = NULL
-
-# adult abundance
-new = post_subset(post, "Ra_obs_new_dev", TRUE)
-obs = post_subset(post, "Ra_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-Ra_bp = data.frame(
-  name = rep("Adults", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(Ra_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###
-
-# summer tagging survival
-new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-phi_Pb_Ma_bp = data.frame(
-  name = rep("Summer Tagging to LGR", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pb_Ma_bp) = NULL
-
-# fall & winter trap survival
-new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
-bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
-           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
-           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
-           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
-phi_Pa_Ma_bp = data.frame(
-  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
-  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pa_Ma_bp) = NULL
-
-# trib to lgr survival
-new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
-bp = bp[,"spring-mig",,]
-bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
-           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
-           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
-           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
-phi_Mb_Ma_bp = data.frame(
-  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
-  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
-  summarize_bp(bp)
-)
-rownames(phi_Mb_Ma_bp) = NULL
-
-# hydropower survival
-new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-phi_Ma_O0_bp = data.frame(
-  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(phi_Ma_O0_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###
-
-# summer length
-new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Pb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Pb_bp = data.frame(
-  name = rep("Summer Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Pb_bp) = NULL
-
-# spring length
-new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Mb_bp = data.frame(
-  name = rep("Spring Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Mb_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
-
-# weir composition
-new = post_subset(post, "x_Ra_new_dev", TRUE)
-obs = post_subset(post, "x_Ra_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
-x_Ra_bp = data.frame(
-  name = rep("Weir", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Ra_bp) = NULL
-
-# carcass composition
-new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
-obs = post_subset(post, "x_Sa_prime_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
-x_Sa_prime_bp = data.frame(
-  name = rep("Carcasses", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Sa_prime_bp) = NULL
-
-# pre-spawn survival
-new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
-obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-x_carcass_spawned_bp = data.frame(
-  name = rep("Prespawn", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_carcass_spawned_bp) = NULL
-
-# movement survival from BON to LGR
-new = post_subset(post, "x_LGR_new_dev", TRUE)
-obs = post_subset(post, "x_LGR_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-x_LGR_bp = data.frame(
-  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(x_LGR_bp) = NULL
-
-### COMBINE INTO ONE TABLE ###
-bp_tab = rbind(
-  Pa_bp, Mb_bp, Ra_bp,
-  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
-)
-
-# add a main data category variable
-category = rep(NA, nrow(bp_tab))
-category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
-category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
-category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
-category[is.na(category)] = "Survival"
-bp_tab = data.frame(category = category, bp_tab)
-
-# drop the several cases with no data
-# MIN HOR survival to LGR and MIN weir data
-bp_tab = bp_tab[bp_tab$N > 0,]
-
-# re-order output/misc formatting
-bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
-bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
-bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
-bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
-rownames(bp_tab) = NULL
-```
-
-```{r bayesian-pvals-table, eval = model_info$do_pp_check}
-# a function to color cells depending on the value
-assign_color = function(x) {
-  red_pal = colorRampPalette(c("white", "red"))
-  blue_pal = colorRampPalette(c("blue", "white"))
-  red_cols = red_pal(5)
-  blue_cols = blue_pal(5)
-  cols = c(blue_cols, red_cols)
-  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
-  names(cols) = bin_names
-  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-bp_tab %>%
-  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
-      align = c("lllllcccccc")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
-  column_spec(7, background = assign_color(bp_tab[,7])) %>%
-  column_spec(8, background = assign_color(bp_tab[,8])) %>%
-  column_spec(9, background = assign_color(bp_tab[,9])) %>%
-  collapse_rows(1:5) 
-```
-
-```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
-cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
-```
-
-# Fit to Data
-
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data {.tabset .tabset-pills}
-
-### Fall Parr Abundance
-
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
-```
-
-### Spring Smolt Abundance
-
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
-```
-
-### Adult Return Abundance
-
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
-```
-
-## Survival Data {.tabset .tabset-pills}
-
-### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (NOR)
-
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (HOR)
-
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
-```
-
-### LGR Smolt $\rightarrow O_0$ (NOR)
-
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### LGR Smolt $\rightarrow O_0$ (HOR)
-
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-```{r calculate-aggregated-comps-model}
-# extract the full posteriors of the two composition sets
-p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
-p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
-
-# primary containers: will store final recalculated output
-p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
-
-# number of posterior samples
-n = post_dim(post, "saved")
-
-# loop through posterior samples, calculate various aggregates of composition by type
-for (i in 1:n) {
-
-  # format the posterior draw as arrays -- easier to subset
-  p_Ra = array_format(p_Ra_full[i,])
-  p_Sa_prime = array_format(p_Sa_prime_full[i,])
-
-  ## BY AGE, AGGREGATED ACROSS ORIGINS
-
-  # containers
-  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
-  for (j in 1:jags_data$nj) {
-    for (k in 1:jags_data$nk) {
-      # calculate aggregate proportions for each age
-      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
-      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_age[,k,j] = 1:jags_data$ny
-      inds_2_age[,k,j] = k
-      inds_3_age[,k,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
-  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
-  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
-  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGES
-
-  # containers
-  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
-  for (j in 1:jags_data$nj) {
-    for (o in 1:jags_data$no) {
-      # calculate aggregate proportions for each origin
-      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
-      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_origin[,o,j] = 1:jags_data$ny
-      inds_2_origin[,o,j] = o
-      inds_3_origin[,o,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
-  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
-  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
-  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
-
-  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
-
-  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
-  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
-  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
-  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
-
-}
-
-# combine new calculated quantities into a big matrix
-q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
-
-# combine with the rest of the posterior samples
-post = post_bind(post, q_new)
-
-```
-
-```{r calculate-aggregated-comps-data}
-
-# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
-
-# containers
-x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
-
-for (j in 1:jags_data$nj) {
-  # calculate aggregate proportions for each age
-  for (k in 1:jags_data$nk) {
-    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
-    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each origin
-  for (o in 1:jags_data$no) {
-    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
-    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
-
-x_Ra_new_obs = list(
-  x_Ra_age_obs = x_Ra_age_obs,
-  x_Ra_origin_obs = x_Ra_origin_obs
-)
-
-x_Sa_prime_new_obs = list(
-  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
-  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
-)
-
-```
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-fit-funcs}
-
-# for multinomial sample size
-weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-weir_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each age, aggregated across origins
-weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
-
-##### CAT
-
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_ugr)
-```
-
-### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carc-comp-fit-funcs}
-
-# for multinomial sample size
-carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-carc_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
-}
-
-# for fits to each age, aggregated across origins
-carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
-
-##### CAT
-
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_ugr)
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
-
-junk = sapply(1:jags_data$nj, plot_f)
-```
-
-## Length Data {.tabset .tabset-pills}
-
-### Mean Length at Summer Tagging
-
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
-```
-
-### Mean Length at Spring Tagging
-
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
-```
-
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior samples of the BH productivity and capacity parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
-
-  # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
-
-  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
-  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
-
-  # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
-```
-
-## Total Eggs vs. Total Spawners
-
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
-The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
-
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(E["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(E["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
-
-  # yaxis ticks
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  abline(c(0, 1000), lty = 1)
-  abline(c(0, 1800), lty = 2)
-  abline(c(0, 3600), lty = 3)
-
-  if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-           lty = c(1,2,3), bty = "n", cex = 0.75)
-  }
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
-```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
-
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
-
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
-
-# empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
-     ylab = "Parr Capacity (000s)", yaxt = "n")
-at_y = axisTicks(par("usr")[3:4], log = FALSE)
-axis(side = 2, at = at_y, labels = at_y/1000)
-
-# draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
-
-# draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
-
-# draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
-```
-
-## Slope Parameter
-
-```{r beta-v-habitat-slope}
-# extract posterior summary of slope
-est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
-
-# print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
-```
-
-# Length Relationships {.tabset .tabset-pills}
-
-## Summer Tagging
+# Length-Based Quantities {.tabset .tabset-dropdown}
+
+## Mean Parr Length vs. Egg Density
 
@@
 
-## Spring Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Summer Length
+## Smolt Mean Length {.tabset .tabset-pills}
+
+### "Growth Factor" vs. Parr Mean Length
 
@@
 
-# Length-Based Survival Relationships {.tabset .tabset-pills}
-
-## Overwinter Survival
+## Parr $\rightarrow$ Smolt Overwinter Survival vs. Parr Mean Length
 
@@
 
-## Migration to LGR
+## Smolt Survival to LGR vs. Smolt Mean Length
 
@@
 ```
-
-# Equivilency Rates {.tabset .tabset-pills}
-
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
-
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
-
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
-
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
-## Parr per Spawner
-
-"Spawner" means total spawners that survive pre-spawn mortality.
-
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-## Smolt per Spawner
-
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
-
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
-```
-
-## Spawners per Spawner
-
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
-
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
- abline(h = 1, lty = 2)
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
-```
-
-# Straying Dynamics {.tabset .tabset-pills}
-
-## Number of Strays
-
-```{r n-stray, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
-```
-
-## Stray Composition
-
-```{r stray-comp, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
-  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
-}
-
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
-```
-
-# Ocean Survival {.tabset .tabset-pills}
-
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
-```
-
-# Maturity {.tabset .tabset-pills}
-
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
-```
-
-## CAT
-
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
-```
-
-## LOS
-
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
-```
-
-## MIN
-
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
-
-## UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
-```
-
-# Parameter Summaries {.tabset .tabset-dropdown}
-
-```{r my-boxplot-function}
-my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), ...) {
-  # extract posterior samples and rename them
-  post_sub = post_subset(post, params, matrix = TRUE)
-
-  if (ncol(post_sub) >= 2) {
-    colnames(post_sub) = ticklabs
-  }
-
-  # initialize a boxplot object
-  bp = boxplot(post_sub, plot = FALSE)
-
-  # replace the summary stats with my preferred quantiles
-  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
-  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
-      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
-} 
-```
-
-## Parr Recruitment
-
-```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^alpha[.]$", "Productivity")
-my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
-my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Summer Parr Size
-
-```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^omega0[.]$", "Intercept")
-my_boxplot("^omega1[.]$", "Slope")
-my_boxplot("^sig_lL_Pb[.]$", "Process SD")
-my_boxplot("^rho_lL_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Life History Apportionment
-
-```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
-my_boxplot("^sig_Lpi[.]$", "Process SD")
-my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Overwinter Survival {.tabset .tabset-pills}
-
-### Logistic Function Parameters
-
-```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope")
-```
-
-### Process SD
-
-```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
-```
-
-### Among-pop Correlation
-
-```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to LGR {.tabset .tabset-pills}
-
-### Mean/Logistic Model Parameters
-
-```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("tau0[pop]", pop = "."), "Intercept", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("tau1[pop]", pop = "."), "Slope", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to Ocean
-
-```{r lgr-to-ocean-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Means
-
-```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
-
-### Means
-
-```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Ocean Survival {.tabset .tabset-pills}
-
-### Year 1 {.tabset .tabset-pills}
-
-#### Mean
-
-```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-#### Process SD and Correlation
-
-```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
-my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
-```
-
-### Year 2 {.tabset .tabset-pills}
-
-```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### Year 3 {.tabset .tabset-pills}
-
-```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### NOR:HOR Log Odds Ratios
-
-```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("delta_O0_O1[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 1")
-my_boxplot(sub_index("delta_O1_O2[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 2")
-my_boxplot(sub_index("delta_O2_O3[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 3")
-```
-
-## Movement Survival BON to LGR
-
-```{r bon-to-lgr-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Pre-spawn Survival
-
-```{r prespawn-surv-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
-my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
-my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
-```
-
-# Correlation Parameters
-
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
-)
-
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
-
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
-
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
-
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
-
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
-abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
-box()
-```
-
-# Residual Diagnostics {.tabset .tabset-pills}
-
-```{r misc-resid-fns}
-get_yr_index = function(params) {
-  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
-  yr_index = stringr::str_remove(yr_index, "\\[")
-  yr_index = stringr::str_remove(yr_index, ",")
-  as.numeric(yr_index)
-}
-
-make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
-  f = function(x) {
-    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
-    xs = round(xs, 2)
-    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
-  }
-  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
-}
-
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
-no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
-}
-```
-
-#### Why Does this Matter?
-
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
-
-#### What was Calculated?
-
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
-
-#### What is Shown?
-
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
-* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
-
-These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
-They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
-
-## Process Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-proc-resid-fn}
-
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-  y_ind_obs = y_ind %in% observable
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(y_ind[y_ind_obs])/2)
-  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(qresid_post[,y_first], 1, mean)
-  mn_post_last = apply(qresid_post[,y_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-    # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-  )
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-obs_error_ests = NULL
-```
-
-### Abundance Data {.tabset .tabset-pills}
-
-#### Fall Parr Abundance
-
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt Abundance
-
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Adult Return Abundance
-
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Survival Data {.tabset .tabset-pills}
-
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### BON Adults $\rightarrow$ LGR
-
-```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Length Data {.tabset .tabset-pills}
-
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Composition Data {.tabset .tabset-pills}
-
-#### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-resid-plots-fn}
-ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
-             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
-
-weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-_No weir data for MIN_
-
-##### UGR
-
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-#### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carcass-comp-resid-plots-fn}
-carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_min)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### UGR
-
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r obs-error-table-prep}
-# rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
-
-# correct parameter names
-obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
-obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
-obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
-obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
-
-# correct origin indices
-obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
-obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
-
-# correct LH_type indices
-obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
-
-# correct pop indices
-obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
-
-# correct origin indices based on age indices
-obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
-obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
-
-# replace indices with names
-obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
-obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
-obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
-obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
-obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
-
-# add a type column
-obs_error_ests$type = NA
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
-
-# add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
-obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
-obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
-obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
-obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
-
-# drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r obs-error-table-fn}
-obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:5)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r obs-error-mean-table}
-obs_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r obs-error-sd-table}
-obs_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r obs-error-diff-table}
-obs_error_table("diff_mean")
-```
-
-# JAGS Model and Data {.tabset .tabset-pills}
-
-## JAGS Model Code
-
-```{r jags-model, comment = NA}
-# print the JAGS model code
-cat(model_info$jags_model_code, sep = "\n")
-```
-
-## JAGS Model Data
-
-```{r jags-data, comment = NA}
-# print the JAGS model data
-model_info$jags_data
-```

### 2022-04-25 03-post-process/output-plots-children/11-param-summaries.Rmd
Move all output rmd sections to separate child documents

--- 2022-04-21 03-post-process/output-plots.Rmd
@@
----
-title: "Output Summary"
-subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
-date: "`r paste0('Date Rendered: ', Sys.Date())`"
-output: 
-  html_document:
-    toc: true
-    toc_float: true
-params:
-  scenario:
-    label: "Scenario"
-    value: "base"
-    input: text
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
-    input: checkbox
-  thin_percent:
-    label: "Proportion of Posterior Samples to Retain?"
-    value: 1
-    input: numeric
-editor_options: 
-  chunk_output_type: console
----
-
-```{r directories, include = F}
-# set root directory to the project directory: one level up from this location
-knitr::opts_knit$set(root.dir = "../")
-```
-
-```{r setup, include = FALSE}
-# set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
-
-# load packages
-source("00-packages.R")
-
-# load all necessary functions
-invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))
-
-# set the input directory
-in_dir = "02-model/model-output"
-
-# read information from this model
-model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
-
-# extract the posterior samples
-# post-MCMC thinning allowed to reduce run time of this document
-if (params$thin_percent < 1) {
-  post = post_thin(model_info$post, keep_percent = params$thin_percent)
-} else {
-  post = model_info$post
-}
-
-# extract the model data 
-jags_data = model_info$jags_data
-```
-
-```{r dimension-ids}
-# the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
-
-# which years are "observable" for at least some quantities?
-observable = 2:jags_data$ny_obs
-
-# which years are simulated for at least some quantities?
-simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))
-
-# which years should be included in time series plots?
-if (params$include_sim_years) {
-  ts_yrs = c(observable, simulated)
-} else {
-  ts_yrs = observable
-}
-
-# which years can be plotted for SARs? Drop off last kmax years
-# since brood year adult returns not complete
-sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
-
-# population names
-pops = colnames(jags_data$Ra_obs)
-
-# origin names
-origins = c("NOR", "HOR")
-
-# dimension IDs
-i_fall   = 1  # fall migrants are i = 1
-i_spring = 2  # spring migrants are i = 2,
-o_nor    = 1  # natural origin are o = 1,
-o_hor    = 2  # hatchery origin are o = 2,
-j_cat    = 1  # Catherine Creek is j = 1
-j_los    = 2  # Lostine River is j = 2
-j_min    = 3  # Minam River is j = 3
-j_ugr    = 4  # Upper Grande Ronde River is j = 4
-k_3      = 1  # age 3 is k = 1
-k_4      = 2  # age 4 is k = 2
-k_5      = 3  # age 5 is k = 3
-
-# ko represents "age/origin" combo
-# e.g., ko = 1 is age 3 NORs
-# e.g., ko = 5 is age 4 HORs
-# these objects specify which elements of ko are for different aggregations of these
-ko_age = list(
-  ko_3 = c(1, 4),
-  ko_4 = c(2, 5),
-  ko_5 = c(3, 6)
-)
-
-ko_origin = list(
-  ko_nor = 1:3,
-  ko_hor = 4:6
-)
-
-# make the labels for which elements of the rho matrices contain unique elements
-dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
-dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
-vcov_cols = dummy_cols[lower.tri(dummy_cols)]
-vcov_rows = dummy_rows[lower.tri(dummy_rows)]
-vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
-```
-
-# MCMC Information {.tabset .tabset-pills}
-
-## Time Information
-
-```{r mcmc-time-info}
-# Calculate hours per 10,000 iterations
-hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
-  # calculation of total iters differs if parallel or not
-  if (parallel) {
-    total_iters = n_adapt + n_post + n_burn
-  } else {
-    total_iters = (n_adapt + n_post + n_burn) * n_chains
-  }
-  ten_thousands_of_total_iters = total_iters/10000
-
-  # calculate hours elapsed
-  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
-  time_number = as.numeric(time_diff)
-  time_units = attributes(time_diff)$units
-  hour_convert = switch(time_units,
-                        "secs" = 3600,
-                        "mins" = 60,
-                        "hours" = 1,
-                        "days" = 1/24)
-  hours_diff = time_number/hour_convert
-
-  # calculate/round rate
-  round(hours_diff/ten_thousands_of_total_iters, 2)
-})
-
-# combine relevant info into a data frame
-df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
-
-# make a kable for printing in output
-kable(df) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Attributes
-
-This table shows some dimensions of the MCMC run.
-
-```{r mcmc-dims}
-# query the dimensions of the posterior samples
-dims = post_dim(post)
-
-# build a data frame for printing
-df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
-
-# render the table
-kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
-  column_spec(1, bold = TRUE)
-```
-
-## Sampling Diagnostics {.tabset .tabset-pills}
-
-```{r make-diag-post}
-# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
-# there is no point in calculating diagnostic summaries for future years
-if (length(simulated) > 0) {
-  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
-} else {
-  diag_post = post
-}
-
-# discard duplicate correlation terms: all rho parameters for a given process are equal
-all_rho = match_params(post, "^rho")
-rho_keep = match_params(post, "^rho_.+[2,1")
-rho_discard = all_rho[!(all_rho %in% rho_keep)]
-diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
-```
-
-```{r mcmc-diag-function}
-# a function to get MCMC diagnoses for a group of parameters
-# params: a string to match with postpack::match_params()
-# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
-# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
-# L3: a "Level-3" group label; such as NOR or HOR
-
-summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
-  # extract the posteriors of interest and format for 'posterior' package
-  post_sub = as_draws_df(post_subset(diag_post, params))
-
-  # summarize the posteriors
-  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
-
-  # discard any parameters that were the same value every MCMC iteration
-  # (will have an NA for rhat)
-  diags = diags[!is.na(diags$rhat),]
-
-  # append the level names and return
-  cbind(
-    L1 = L1, L2 = L2, L3 = L3,
-    diags
-  )
-}
-
-summarize_diags = function(diags) {
-
-  # add "Monte Carlo CV"
-  diags$mccv_mean = diags$mcse_mean/diags$mean
-  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
-  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
-
-  # summarize the summaries
-  data.frame(
-    L1 = unique(diags$L1),
-    L2 = unique(diags$L2),
-    L3 = unique(diags$L3),
-    match = unique(postpack:::drop_index(diags$variable)),
-    n_params = nrow(diags),
-    Rhat_1.01 = sum(diags$rhat >= 1.01),
-    Rhat_1.05 = sum(diags$rhat >= 1.05),
-    Rhat_1.1 = sum(diags$rhat >= 1.1),
-    Rhat_1.2 = sum(diags$rhat >= 1.2),
-    ess_mean_400 = sum(diags$ess_mean < 400),
-    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
-    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
-    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
-    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
-    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
-  )
-}
-```
-
-```{r calculate-mcmc-diagnostics}
-# containers
-diags_out = NULL
-summs_out = NULL
-
-# parr recruitment
-L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# summer parr mean length
-L1 = "Density-Dependent Summer Length"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LH apportionment
-L1 = "Life History Apportionment"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# parr survival from summer to winter tagging
-L1 = "Survival From Summer to Winter"
-match = c("phi_Pb_Pa[2,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Fall Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Spring Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# growth from summer to spring
-# summer parr mean length
-L1 = "Summer to Spring 'Growth Factor'"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: NOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
-match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: HOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: NOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: HOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Probability of Maturing at Age-3: NOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-3: HOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: NOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: HOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 1 ocean survival
-L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Misc ocean survival
-L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
-match = sub_index(base, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: NOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: HOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Pre-spawn Survival
-L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Carcass Correction
-L1 = "Carcass Correction Factor"
-L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
-match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Initial adult recruitment
-L1 = "Initial Adult Returns"
-L2 = c("Age-3", "Age-4", "Age-5")
-match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Straying
-L1 = "Strays"
-L2 = c("Realized Total Number", "Age Comp")
-match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# remove any summaries for nodes that don't have diagnostics
-# e.g., if that "parameter" takes on a fixed value in the model
-diags_table = summs_out
-diags_table = diags_table[diags_table$n_params > 0,]
-```
-
-### Summary Table
-
-This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
-Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
-Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
-
-* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
-* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
-* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
-
-The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
-
-```{r mcmc-diag-table, warning = FALSE}
-# duplicate the diagnostic output
-kable_table = diags_table
-
-# order the rows
-kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
-kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]
-
-# keep only relevant columns for kable
-kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]
-
-# convert counts of offending parameters to percentages
-kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")
-
-# add basic formatting
-colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
-kable_table$Group[is.na(kable_table$Group)] = " "
-kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "
-
-assign_color = function(x, colors = c("white","red")) {
-  pal = colorRampPalette(colors)
-  cols = pal(6)
-  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
-  names(cols) = bin_names
-  x[is.na(x)] = 0
-  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
-  column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,8,11), border_right = TRUE) %>%
-  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
-  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
-  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
-  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
-  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
-  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
-  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
-  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
-  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
-  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
-  collapse_rows(columns = 1:2)
-```
-
-### Figures {.tabset .tabset-pills}
-
-```{r mcmc-diag-plots-prep}
-n_max_draw = 30
-
-# which parameters fall in each Rhat bin
-rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
-rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
-rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
-
-# extract the Rhat values and the names of the parameters with the 
-# worst Rhat values by bin
-rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
-rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
-rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
-rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
-rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
-rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]
-
-# subset out these parameters: makes postpack::diag_plots() much faster
-post_sub_1 = post_subset(post, rhat_1_params_draw)
-post_sub_2 = post_subset(post, rhat_2_params_draw)
-post_sub_3 = post_subset(post, rhat_3_params_draw)
-
-# function to plot a histogram of rhat values
-rhat_hist = function(rhat) {
-  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
-  breaks = seq(min(rhat), max(rhat), length = 20)
-  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
-  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
-  usr = par("usr")
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
-}
-```
-
-#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
-
-```{r rhat-hist-1, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_1)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_1, "", show_diags = "never")
-```
-
-#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-2, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_2)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_2, "", show_diags = "never")
-```
-
-#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-3, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_3)
-```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_3, "", show_diags = "never")
-```
-
-## WAIC
-
-WAIC is a measure of model parsimony.
-The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
-There are two methods of calculating `pD`, both are shown below.
-As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
-
-```{r calculate-waic, eval = model_info$do_lppd}
-summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
-  # calculate total lppd summed across all data sets within a given year
-  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
-
-  tmp_log = log(apply(exp(total_lppd), 2, mean))
-  tmp_sum = -2 * sum(tmp_log)
-
-  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
-  pD2 = sum(apply(total_lppd, 2, var))
-  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
-}
-
-waic_out = summarize_lppd("_lppd[year,.+]$")
-
-waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
-```
-
-```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
-cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
-```
-
-## Posterior Predictive Checks
-
-This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
-For each observed data point and MCMC iteration, a value was simulated from the model.
-The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
-P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
-Across years within a data set, p-values were summarized as the median and central 95% intervals.
-The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.
-
-The fit criterion differed depending on the likelihood function used to fit the model to the data set:
-
-* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
-* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation.
-This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
-This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
-
-```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
-# function to summarize bayesian p-values within a data source
-summarize_bp = function(bp) {
-  data.frame(
-    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
-    "median" = apply(bp, 2, median, na.rm = TRUE),
-    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
-    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
-    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
-    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
-  )
-}
-
-### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###
-
-# fall trap
-new = post_subset(post, "Pa_obs_new_dev", TRUE)
-obs = post_subset(post, "Pa_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
-bp = bp[,"fall-mig",]
-Pa_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Pa_bp) = NULL
-
-# spring trap
-new = post_subset(post, "^Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "^Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
-bp = bp[,"spring-mig","NOR",]
-Mb_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Mb_bp) = NULL
-
-# adult abundance
-new = post_subset(post, "Ra_obs_new_dev", TRUE)
-obs = post_subset(post, "Ra_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-Ra_bp = data.frame(
-  name = rep("Adults", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(Ra_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###
-
-# summer tagging survival
-new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-phi_Pb_Ma_bp = data.frame(
-  name = rep("Summer Tagging to LGR", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pb_Ma_bp) = NULL
-
-# fall & winter trap survival
-new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
-bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
-           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
-           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
-           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
-phi_Pa_Ma_bp = data.frame(
-  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
-  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pa_Ma_bp) = NULL
-
-# trib to lgr survival
-new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
-bp = bp[,"spring-mig",,]
-bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
-           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
-           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
-           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
-phi_Mb_Ma_bp = data.frame(
-  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
-  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
-  summarize_bp(bp)
-)
-rownames(phi_Mb_Ma_bp) = NULL
-
-# hydropower survival
-new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-phi_Ma_O0_bp = data.frame(
-  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(phi_Ma_O0_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###
-
-# summer length
-new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Pb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Pb_bp = data.frame(
-  name = rep("Summer Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Pb_bp) = NULL
-
-# spring length
-new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Mb_bp = data.frame(
-  name = rep("Spring Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Mb_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
-
-# weir composition
-new = post_subset(post, "x_Ra_new_dev", TRUE)
-obs = post_subset(post, "x_Ra_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
-x_Ra_bp = data.frame(
-  name = rep("Weir", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Ra_bp) = NULL
-
-# carcass composition
-new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
-obs = post_subset(post, "x_Sa_prime_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
-x_Sa_prime_bp = data.frame(
-  name = rep("Carcasses", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Sa_prime_bp) = NULL
-
-# pre-spawn survival
-new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
-obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-x_carcass_spawned_bp = data.frame(
-  name = rep("Prespawn", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_carcass_spawned_bp) = NULL
-
-# movement survival from BON to LGR
-new = post_subset(post, "x_LGR_new_dev", TRUE)
-obs = post_subset(post, "x_LGR_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-x_LGR_bp = data.frame(
-  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(x_LGR_bp) = NULL
-
-### COMBINE INTO ONE TABLE ###
-bp_tab = rbind(
-  Pa_bp, Mb_bp, Ra_bp,
-  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
-)
-
-# add a main data category variable
-category = rep(NA, nrow(bp_tab))
-category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
-category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
-category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
-category[is.na(category)] = "Survival"
-bp_tab = data.frame(category = category, bp_tab)
-
-# drop the several cases with no data
-# MIN HOR survival to LGR and MIN weir data
-bp_tab = bp_tab[bp_tab$N > 0,]
-
-# re-order output/misc formatting
-bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
-bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
-bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
-bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
-rownames(bp_tab) = NULL
-```
-
-```{r bayesian-pvals-table, eval = model_info$do_pp_check}
-# a function to color cells depending on the value
-assign_color = function(x) {
-  red_pal = colorRampPalette(c("white", "red"))
-  blue_pal = colorRampPalette(c("blue", "white"))
-  red_cols = red_pal(5)
-  blue_cols = blue_pal(5)
-  cols = c(blue_cols, red_cols)
-  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
-  names(cols) = bin_names
-  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-bp_tab %>%
-  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
-      align = c("lllllcccccc")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
-  column_spec(7, background = assign_color(bp_tab[,7])) %>%
-  column_spec(8, background = assign_color(bp_tab[,8])) %>%
-  column_spec(9, background = assign_color(bp_tab[,9])) %>%
-  collapse_rows(1:5) 
-```
-
-```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
-cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
-```
-
-# Fit to Data
-
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data {.tabset .tabset-pills}
-
-### Fall Parr Abundance
-
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
-```
-
-### Spring Smolt Abundance
-
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
-```
-
-### Adult Return Abundance
-
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
-```
-
-## Survival Data {.tabset .tabset-pills}
-
-### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (NOR)
-
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (HOR)
-
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
-```
-
-### LGR Smolt $\rightarrow O_0$ (NOR)
-
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### LGR Smolt $\rightarrow O_0$ (HOR)
-
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-```{r calculate-aggregated-comps-model}
-# extract the full posteriors of the two composition sets
-p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
-p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
-
-# primary containers: will store final recalculated output
-p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
-
-# number of posterior samples
-n = post_dim(post, "saved")
-
-# loop through posterior samples, calculate various aggregates of composition by type
-for (i in 1:n) {
-
-  # format the posterior draw as arrays -- easier to subset
-  p_Ra = array_format(p_Ra_full[i,])
-  p_Sa_prime = array_format(p_Sa_prime_full[i,])
-
-  ## BY AGE, AGGREGATED ACROSS ORIGINS
-
-  # containers
-  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
-  for (j in 1:jags_data$nj) {
-    for (k in 1:jags_data$nk) {
-      # calculate aggregate proportions for each age
-      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
-      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_age[,k,j] = 1:jags_data$ny
-      inds_2_age[,k,j] = k
-      inds_3_age[,k,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
-  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
-  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
-  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGES
-
-  # containers
-  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
-  for (j in 1:jags_data$nj) {
-    for (o in 1:jags_data$no) {
-      # calculate aggregate proportions for each origin
-      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
-      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_origin[,o,j] = 1:jags_data$ny
-      inds_2_origin[,o,j] = o
-      inds_3_origin[,o,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
-  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
-  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
-  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
-
-  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
-
-  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
-  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
-  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
-  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
-
-}
-
-# combine new calculated quantities into a big matrix
-q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
-
-# combine with the rest of the posterior samples
-post = post_bind(post, q_new)
-
-```
-
-```{r calculate-aggregated-comps-data}
-
-# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
-
-# containers
-x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
-
-for (j in 1:jags_data$nj) {
-  # calculate aggregate proportions for each age
-  for (k in 1:jags_data$nk) {
-    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
-    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each origin
-  for (o in 1:jags_data$no) {
-    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
-    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
-
-x_Ra_new_obs = list(
-  x_Ra_age_obs = x_Ra_age_obs,
-  x_Ra_origin_obs = x_Ra_origin_obs
-)
-
-x_Sa_prime_new_obs = list(
-  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
-  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
-)
-
-```
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-fit-funcs}
-
-# for multinomial sample size
-weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-weir_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each age, aggregated across origins
-weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
-
-##### CAT
-
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_ugr)
-```
-
-### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carc-comp-fit-funcs}
-
-# for multinomial sample size
-carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-carc_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
-}
-
-# for fits to each age, aggregated across origins
-carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
-
-##### CAT
-
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_ugr)
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
-
-junk = sapply(1:jags_data$nj, plot_f)
-```
-
-## Length Data {.tabset .tabset-pills}
-
-### Mean Length at Summer Tagging
-
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
-```
-
-### Mean Length at Spring Tagging
-
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
-```
-
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior samples of the BH productivity and capacity parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
-
-  # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
-
-  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
-  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
-
-  # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
-```
-
-## Total Eggs vs. Total Spawners
-
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
-The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
-
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(E["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(E["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
-
-  # yaxis ticks
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  abline(c(0, 1000), lty = 1)
-  abline(c(0, 1800), lty = 2)
-  abline(c(0, 3600), lty = 3)
-
-  if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-           lty = c(1,2,3), bty = "n", cex = 0.75)
-  }
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
-```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
-
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
-
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
-
-# empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
-     ylab = "Parr Capacity (000s)", yaxt = "n")
-at_y = axisTicks(par("usr")[3:4], log = FALSE)
-axis(side = 2, at = at_y, labels = at_y/1000)
-
-# draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
-
-# draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
-
-# draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
-```
-
-## Slope Parameter
-
-```{r beta-v-habitat-slope}
-# extract posterior summary of slope
-est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
-
-# print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
-```
-
-# Length Relationships {.tabset .tabset-pills}
-
-## Summer Tagging
-
-```{r}
-plot_f = function(j) {
-
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "")["mean",]
-  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
-  E_scaled_upr = post_summ(post_E, "")["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
-  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
-  plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-```
-
-## Spring Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Summer Length
-
-```{r}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-### "Growth Factor" Time Series
-
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-# Length-Based Survival Relationships {.tabset .tabset-pills}
-
-## Overwinter Survival
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
-  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
-  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
-
-  # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
-       xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-## Migration to LGR
-
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
-       xlim = range(L_Mb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
-```
-
-# Equivilency Rates {.tabset .tabset-pills}
-
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
-
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
-
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
-
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
-## Parr per Spawner
-
-"Spawner" means total spawners that survive pre-spawn mortality.
-
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-## Smolt per Spawner
-
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
-
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
-```
-
-## Spawners per Spawner
-
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
-
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
- abline(h = 1, lty = 2)
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
-```
-
-# Straying Dynamics {.tabset .tabset-pills}
-
-## Number of Strays
-
-```{r n-stray, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
-```
-
-## Stray Composition
-
-```{r stray-comp, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
-  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
-}
-
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
-```
-
-# Ocean Survival {.tabset .tabset-pills}
-
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
-```
-
-# Maturity {.tabset .tabset-pills}
-
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
-```
-
-## CAT
-
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
-```
-
-## LOS
-
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
-```
-
-## MIN
-
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
-
-## UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
-```
-
 # Parameter Summaries {.tabset .tabset-dropdown}
@@
 ```
-
-# Correlation Parameters
-
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
-)
-
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
-
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
-
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
-
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
-
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
-abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
-box()
-```
-
-# Residual Diagnostics {.tabset .tabset-pills}
-
-```{r misc-resid-fns}
-get_yr_index = function(params) {
-  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
-  yr_index = stringr::str_remove(yr_index, "\\[")
-  yr_index = stringr::str_remove(yr_index, ",")
-  as.numeric(yr_index)
-}
-
-make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
-  f = function(x) {
-    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
-    xs = round(xs, 2)
-    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
-  }
-  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
-}
-
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
-no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
-}
-```
-
-#### Why Does this Matter?
-
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
-
-#### What was Calculated?
-
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
-
-#### What is Shown?
-
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
-* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
-
-These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
-They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
-
-## Process Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-proc-resid-fn}
-
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-  y_ind_obs = y_ind %in% observable
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(y_ind[y_ind_obs])/2)
-  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(qresid_post[,y_first], 1, mean)
-  mn_post_last = apply(qresid_post[,y_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-    # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-  )
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-obs_error_ests = NULL
-```
-
-### Abundance Data {.tabset .tabset-pills}
-
-#### Fall Parr Abundance
-
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt Abundance
-
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Adult Return Abundance
-
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Survival Data {.tabset .tabset-pills}
-
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### BON Adults $\rightarrow$ LGR
-
-```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Length Data {.tabset .tabset-pills}
-
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Composition Data {.tabset .tabset-pills}
-
-#### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-resid-plots-fn}
-ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
-             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
-
-weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-_No weir data for MIN_
-
-##### UGR
-
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-#### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carcass-comp-resid-plots-fn}
-carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_min)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### UGR
-
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r obs-error-table-prep}
-# rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
-
-# correct parameter names
-obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
-obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
-obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
-obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
-
-# correct origin indices
-obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
-obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
-
-# correct LH_type indices
-obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
-
-# correct pop indices
-obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
-
-# correct origin indices based on age indices
-obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
-obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
-
-# replace indices with names
-obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
-obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
-obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
-obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
-obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
-
-# add a type column
-obs_error_ests$type = NA
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
-
-# add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
-obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
-obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
-obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
-obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
-
-# drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r obs-error-table-fn}
-obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:5)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r obs-error-mean-table}
-obs_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r obs-error-sd-table}
-obs_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r obs-error-diff-table}
-obs_error_table("diff_mean")
-```
-
-# JAGS Model and Data {.tabset .tabset-pills}
-
-## JAGS Model Code
-
-```{r jags-model, comment = NA}
-# print the JAGS model code
-cat(model_info$jags_model_code, sep = "\n")
-```
-
-## JAGS Model Data
-
-```{r jags-data, comment = NA}
-# print the JAGS model data
-model_info$jags_data
-```

### 2022-04-25 03-post-process/output-plots.Rmd
Move all output rmd sections to separate child documents

--- 2022-04-21 03-post-process/output-plots.Rmd
@@
     input: text
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
-    input: checkbox
   thin_percent:
@@
     input: numeric
+  include_sim_years:
+    label: "Include Simulated Years on Plots?"
+    value: FALSE
+  include_mcmc_diags:
+    label: "Include MCMC Diagnostic Output?"
+    value: TRUE
+  include_fit_to_data:
+    label: "Include Model Fit Output?"
+    value: TRUE
+  include_egg_to_parr_surv:
+    label: "Include Egg-to-Parr Survival Output?"
+    value: TRUE
+  include_length_based_values:
+    label: "Include Length-Based Output?"
+    value: TRUE
+  include_capacity_vs_habitat:
+    label: "Include Capacity vs. Habitat Output?"
+    value: TRUE
+  include_misc_process_model:
+    label: "Include Misc. Process Model Output?"
+    value: TRUE
+  include_equiv_rates:
+    label: "Include Equivilency Rate Output?"
+    value: TRUE
+  include_rho_params:
+    label: "Include Process Model Correlation Output?"
+    value: TRUE
+  include_noise_term_diags:
+    label: "Include Noise Term Diagnostic Output?"
+    value: TRUE
+  include_param_summaries:
+    label: "Include Posterior Boxplot Output?"
+    value: TRUE
+  include_jags_info:
+    label: "Include JAGS Code/Data?"
+    value: TRUE
 editor_options: 
@@
 
-# MCMC Information {.tabset .tabset-pills}
-
-## Time Information
-
-```{r mcmc-time-info}
-# Calculate hours per 10,000 iterations
-hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
-  # calculation of total iters differs if parallel or not
-  if (parallel) {
-    total_iters = n_adapt + n_post + n_burn
-  } else {
-    total_iters = (n_adapt + n_post + n_burn) * n_chains
-  }
-  ten_thousands_of_total_iters = total_iters/10000
-
-  # calculate hours elapsed
-  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
-  time_number = as.numeric(time_diff)
-  time_units = attributes(time_diff)$units
-  hour_convert = switch(time_units,
-                        "secs" = 3600,
-                        "mins" = 60,
-                        "hours" = 1,
-                        "days" = 1/24)
-  hours_diff = time_number/hour_convert
-
-  # calculate/round rate
-  round(hours_diff/ten_thousands_of_total_iters, 2)
-})
-
-# combine relevant info into a data frame
-df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
-rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")
-
-# make a kable for printing in output
-kable(df) %>%
-  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
-  column_spec(1, bold = TRUE)
+```{r model-info, child = "output-plots-children/01-model-info.Rmd"}
 ```
 
-## Attributes
-
-This table shows some dimensions of the MCMC run.
-
-```{r mcmc-dims}
-# query the dimensions of the posterior samples
-dims = post_dim(post)
-
-# build a data frame for printing
-df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))
-
-# render the table
-kable(df, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
-  column_spec(1, bold = TRUE)
+```{r mcmc, child = "output-plots-children/02-mcmc-diags.Rmd", eval = params$include_mcmc_diags}
 ```
 
-## Sampling Diagnostics {.tabset .tabset-pills}
-
-```{r make-diag-post}
-# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
-# there is no point in calculating diagnostic summaries for future years
-if (length(simulated) > 0) {
-  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
-} else {
-  diag_post = post
-}
-
-# discard duplicate correlation terms: all rho parameters for a given process are equal
-all_rho = match_params(post, "^rho")
-rho_keep = match_params(post, "^rho_.+[2,1")
-rho_discard = all_rho[!(all_rho %in% rho_keep)]
-diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
+```{r fit-to-data, child = "output-plots-children/03-fit-to-data.Rmd", eval = params$include_fit_to_data}
 ```
 
-```{r mcmc-diag-function}
-# a function to get MCMC diagnoses for a group of parameters
-# params: a string to match with postpack::match_params()
-# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
-# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
-# L3: a "Level-3" group label; such as NOR or HOR
-
-summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
-  # extract the posteriors of interest and format for 'posterior' package
-  post_sub = as_draws_df(post_subset(diag_post, params))
-
-  # summarize the posteriors
-  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
-
-  # discard any parameters that were the same value every MCMC iteration
-  # (will have an NA for rhat)
-  diags = diags[!is.na(diags$rhat),]
-
-  # append the level names and return
-  cbind(
-    L1 = L1, L2 = L2, L3 = L3,
-    diags
-  )
-}
-
-summarize_diags = function(diags) {
-
-  # add "Monte Carlo CV"
-  diags$mccv_mean = diags$mcse_mean/diags$mean
-  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
-  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
-
-  # summarize the summaries
-  data.frame(
-    L1 = unique(diags$L1),
-    L2 = unique(diags$L2),
-    L3 = unique(diags$L3),
-    match = unique(postpack:::drop_index(diags$variable)),
-    n_params = nrow(diags),
-    Rhat_1.01 = sum(diags$rhat >= 1.01),
-    Rhat_1.05 = sum(diags$rhat >= 1.05),
-    Rhat_1.1 = sum(diags$rhat >= 1.1),
-    Rhat_1.2 = sum(diags$rhat >= 1.2),
-    ess_mean_400 = sum(diags$ess_mean < 400),
-    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
-    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
-    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
-    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
-    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
-  )
-}
+```{r egg-to-parr-surv, child = "output-plots-children/04-egg-to-parr-surv.Rmd", eval = params$include_egg_to_parr_surv}
 ```
 
-```{r calculate-mcmc-diagnostics}
-# containers
-diags_out = NULL
-summs_out = NULL
-
-# parr recruitment
-L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# summer parr mean length
-L1 = "Density-Dependent Summer Length"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LH apportionment
-L1 = "Life History Apportionment"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# parr survival from summer to winter tagging
-L1 = "Survival From Summer to Winter"
-match = c("phi_Pb_Pa[2,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Fall Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Overwinter survival: Spring Migrants
-L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# growth from summer to spring
-# summer parr mean length
-L1 = "Summer to Spring 'Growth Factor'"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: NOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
-match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# trib to LGR Migration survival: HOR 
-L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
-match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: NOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival: HOR
-L1 = "Migration Survival (LGR to Ocean)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Probability of Maturing at Age-3: NOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-3: HOR
-L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: NOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Probability of Maturing at Age-4: HOR
-L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 1 ocean survival
-L1 = "Year 1 Ocean Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Year 2 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Misc ocean survival
-L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
-match = sub_index(base, pop = ".")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: NOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_nor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# BON to LGR Migration survival: HOR 
-L1 = "Migration Survival (BON to LGR)"
-L2 = c("Mean", "Process SD", "Realized")
-base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
-match = sub_index(base, year = ".+", origin = o_hor)
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# LGR to Ocean Migration survival correlation among origins
-tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
-tmp_summ =  summarize_diags(tmp_diags)
-diags_out = rbind(diags_out, tmp_diags)
-summs_out = rbind(summs_out, tmp_summ)
-
-# Pre-spawn Survival
-L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Carcass Correction
-L1 = "Carcass Correction Factor"
-L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
-match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Initial adult recruitment
-L1 = "Initial Adult Returns"
-L2 = c("Age-3", "Age-4", "Age-5")
-match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# Straying
-L1 = "Strays"
-L2 = c("Realized Total Number", "Age Comp")
-match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
-# remove any summaries for nodes that don't have diagnostics
-# e.g., if that "parameter" takes on a fixed value in the model
-diags_table = summs_out
-diags_table = diags_table[diags_table$n_params > 0,]
+```{r length-based-values, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_length_based_values}
 ```
 
-### Summary Table
-
-This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
-Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
-Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
-
-* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
-* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
-* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
-
-The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
-
-```{r mcmc-diag-table, warning = FALSE}
-# duplicate the diagnostic output
-kable_table = diags_table
-
-# order the rows
-kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
-kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]
-
-# keep only relevant columns for kable
-kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]
-
-# convert counts of offending parameters to percentages
-kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
-kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
-kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")
-
-# add basic formatting
-colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
-kable_table$Group[is.na(kable_table$Group)] = " "
-kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "
-
-assign_color = function(x, colors = c("white","red")) {
-  pal = colorRampPalette(colors)
-  cols = pal(6)
-  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
-  names(cols) = bin_names
-  x[is.na(x)] = 0
-  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
-  column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,8,11), border_right = TRUE) %>%
-  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
-  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
-  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
-  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
-  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
-  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
-  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
-  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
-  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
-  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
-  collapse_rows(columns = 1:2)
+```{r capacity-vs-habitat, child = "output-plots-children/06-capacity-vs-habitat.Rmd", eval = params$include_capacity_vs_habitat}
 ```
 
-### Figures {.tabset .tabset-pills}
-
-```{r mcmc-diag-plots-prep}
-n_max_draw = 30
-
-# which parameters fall in each Rhat bin
-rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
-rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
-rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
-
-# extract the Rhat values and the names of the parameters with the 
-# worst Rhat values by bin
-rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
-rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
-rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
-rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
-rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
-rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]
-
-# subset out these parameters: makes postpack::diag_plots() much faster
-post_sub_1 = post_subset(post, rhat_1_params_draw)
-post_sub_2 = post_subset(post, rhat_2_params_draw)
-post_sub_3 = post_subset(post, rhat_3_params_draw)
-
-# function to plot a histogram of rhat values
-rhat_hist = function(rhat) {
-  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
-  breaks = seq(min(rhat), max(rhat), length = 20)
-  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
-  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
-  usr = par("usr")
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
-}
+```{r misc-process-model, child = "output-plots-children/07-misc-process-model.Rmd", eval = params$include_misc_process_model}
 ```
 
-#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
-
-```{r rhat-hist-1, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_1)
+```{r equiv-rates, child = "output-plots-children/08-equiv-rates.Rmd", eval = params$include_equiv_rates}
 ```
 
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_1, "", show_diags = "never")
+```{r rho-params, child = "output-plots-children/09-rho-params.Rmd", eval = params$include_rho_params}
 ```
 
-#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-2, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_2)
+```{r noise-term-diags, child = "output-plots-children/10-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
 ```
 
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_2, "", show_diags = "never")
+```{r param-summaries, child = "output-plots-children/11-param-summaries.Rmd", eval = params$include_param_summaries}
 ```
 
-#### $\hat{R} > 1.1$ {.tabset .tabset-pills}
-
-##### Distribution
-
-There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
-
-```{r rhat-hist-3, fig.width = 6, fig.height = 4}
-rhat_hist(rhat_3)
+```{r jags-info, child = "output-plots-children/12-jags-model-info.Rmd", eval = params$include_jags_info}
 ```
-
-##### Least Converged
-
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
-
-```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_3, "", show_diags = "never")
-```
-
-## WAIC
-
-WAIC is a measure of model parsimony.
-The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
-There are two methods of calculating `pD`, both are shown below.
-As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.
-
-```{r calculate-waic, eval = model_info$do_lppd}
-summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
-  # calculate total lppd summed across all data sets within a given year
-  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))
-
-  tmp_log = log(apply(exp(total_lppd), 2, mean))
-  tmp_sum = -2 * sum(tmp_log)
-
-  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
-  pD2 = sum(apply(total_lppd, 2, var))
-  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
-}
-
-waic_out = summarize_lppd("_lppd[year,.+]$")
-
-waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
-```
-
-```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
-cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
-```
-
-## Posterior Predictive Checks
-
-This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
-For each observed data point and MCMC iteration, a value was simulated from the model.
-The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.
-P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected).
-Across years within a data set, p-values were summarized as the median and central 95% intervals.
-The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.
-
-The fit criterion differed depending on the likelihood function used to fit the model to the data set:
-
-* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
-* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation.
-This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities.
-This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.
-
-```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
-# function to summarize bayesian p-values within a data source
-summarize_bp = function(bp) {
-  data.frame(
-    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
-    "median" = apply(bp, 2, median, na.rm = TRUE),
-    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
-    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
-    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
-    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
-  )
-}
-
-### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###
-
-# fall trap
-new = post_subset(post, "Pa_obs_new_dev", TRUE)
-obs = post_subset(post, "Pa_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
-bp = bp[,"fall-mig",]
-Pa_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Pa_bp) = NULL
-
-# spring trap
-new = post_subset(post, "^Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "^Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
-bp = bp[,"spring-mig","NOR",]
-Mb_bp = data.frame(
-  name = rep("Juveniles", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
-  summarize_bp(bp)
-)
-rownames(Mb_bp) = NULL
-
-# adult abundance
-new = post_subset(post, "Ra_obs_new_dev", TRUE)
-obs = post_subset(post, "Ra_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-Ra_bp = data.frame(
-  name = rep("Adults", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(Ra_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###
-
-# summer tagging survival
-new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-phi_Pb_Ma_bp = data.frame(
-  name = rep("Summer Tagging to LGR", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pb_Ma_bp) = NULL
-
-# fall & winter trap survival
-new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
-bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
-           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
-           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
-           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
-phi_Pa_Ma_bp = data.frame(
-  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
-  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
-  summarize_bp(bp)
-)
-rownames(phi_Pa_Ma_bp) = NULL
-
-# trib to lgr survival
-new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
-bp = bp[,"spring-mig",,]
-bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
-           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
-           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
-           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
-phi_Mb_Ma_bp = data.frame(
-  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
-  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
-  summarize_bp(bp)
-)
-rownames(phi_Mb_Ma_bp) = NULL
-
-# hydropower survival
-new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
-obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-phi_Ma_O0_bp = data.frame(
-  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(phi_Ma_O0_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###
-
-# summer length
-new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Pb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Pb_bp = data.frame(
-  name = rep("Summer Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Pb_bp) = NULL
-
-# spring length
-new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
-obs = post_subset(post, "L_Mb_obs_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-L_Mb_bp = data.frame(
-  name = rep("Spring Length", 4), pop = pops,
-  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(L_Mb_bp) = NULL
-
-### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###
-
-# weir composition
-new = post_subset(post, "x_Ra_new_dev", TRUE)
-obs = post_subset(post, "x_Ra_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
-x_Ra_bp = data.frame(
-  name = rep("Weir", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Ra_bp) = NULL
-
-# carcass composition
-new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
-obs = post_subset(post, "x_Sa_prime_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
-x_Sa_prime_bp = data.frame(
-  name = rep("Carcasses", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_Sa_prime_bp) = NULL
-
-# pre-spawn survival
-new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
-obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-x_carcass_spawned_bp = data.frame(
-  name = rep("Prespawn", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_carcass_spawned_bp) = NULL
-
-# movement survival from BON to LGR
-new = post_subset(post, "x_LGR_new_dev", TRUE)
-obs = post_subset(post, "x_LGR_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
-x_LGR_bp = data.frame(
-  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
-  origin = origins, LH_type = rep("Combined", 2),
-  summarize_bp(bp)
-)
-rownames(x_LGR_bp) = NULL
-
-### COMBINE INTO ONE TABLE ###
-bp_tab = rbind(
-  Pa_bp, Mb_bp, Ra_bp,
-  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
-)
-
-# add a main data category variable
-category = rep(NA, nrow(bp_tab))
-category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
-category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
-category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
-category[is.na(category)] = "Survival"
-bp_tab = data.frame(category = category, bp_tab)
-
-# drop the several cases with no data
-# MIN HOR survival to LGR and MIN weir data
-bp_tab = bp_tab[bp_tab$N > 0,]
-
-# re-order output/misc formatting
-bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
-bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
-bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
-bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
-rownames(bp_tab) = NULL
-```
-
-```{r bayesian-pvals-table, eval = model_info$do_pp_check}
-# a function to color cells depending on the value
-assign_color = function(x) {
-  red_pal = colorRampPalette(c("white", "red"))
-  blue_pal = colorRampPalette(c("blue", "white"))
-  red_cols = red_pal(5)
-  blue_cols = blue_pal(5)
-  cols = c(blue_cols, red_cols)
-  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
-  names(cols) = bin_names
-  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
-  cols_use = cols[as.character(bins)]
-  alpha(unname(cols_use), 0.5)
-}
-
-# produce the kable
-bp_tab %>%
-  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
-      align = c("lllllcccccc")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
-  column_spec(7, background = assign_color(bp_tab[,7])) %>%
-  column_spec(8, background = assign_color(bp_tab[,8])) %>%
-  column_spec(9, background = assign_color(bp_tab[,9])) %>%
-  collapse_rows(1:5) 
-```
-
-```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
-cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
-```
-
-# Fit to Data
-
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
-
-## Abundance Data {.tabset .tabset-pills}
-
-### Fall Parr Abundance
-
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
-```
-
-### Spring Smolt Abundance
-
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
-```
-
-### Adult Return Abundance
-
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
-```
-
-## Survival Data {.tabset .tabset-pills}
-
-### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (NOR)
-
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
-```
-
-### Spring Smolt $\rightarrow$ LGR (HOR)
-
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
-```
-
-### LGR Smolt $\rightarrow O_0$ (NOR)
-
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### LGR Smolt $\rightarrow O_0$ (HOR)
-
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-## Composition Data {.tabset .tabset-pills .tabset-fade}
-
-```{r calculate-aggregated-comps-model}
-# extract the full posteriors of the two composition sets
-p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
-p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)
-
-# primary containers: will store final recalculated output
-p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL
-
-# number of posterior samples
-n = post_dim(post, "saved")
-
-# loop through posterior samples, calculate various aggregates of composition by type
-for (i in 1:n) {
-
-  # format the posterior draw as arrays -- easier to subset
-  p_Ra = array_format(p_Ra_full[i,])
-  p_Sa_prime = array_format(p_Sa_prime_full[i,])
-
-  ## BY AGE, AGGREGATED ACROSS ORIGINS
-
-  # containers
-  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
-  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
-  for (j in 1:jags_data$nj) {
-    for (k in 1:jags_data$nk) {
-      # calculate aggregate proportions for each age
-      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
-      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_age[,k,j] = 1:jags_data$ny
-      inds_2_age[,k,j] = k
-      inds_3_age[,k,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
-  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
-  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
-  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
-  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]
-
-  ## BY ORIGIN, AGGREGATED ACROSS AGES
-
-  # containers
-  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
-  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
-  for (j in 1:jags_data$nj) {
-    for (o in 1:jags_data$no) {
-      # calculate aggregate proportions for each origin
-      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
-      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])
-
-      # build the element identifiers - for building names later
-      inds_1_origin[,o,j] = 1:jags_data$ny
-      inds_2_origin[,o,j] = o
-      inds_3_origin[,o,j] = j
-    }
-  }
-
-  # vectorize, add names, and remove NAs
-  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
-  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
-  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
-  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
-  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]
-
-  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES
-
-  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
-  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
-  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
-  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)
-
-}
-
-# combine new calculated quantities into a big matrix
-q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)
-
-# combine with the rest of the posterior samples
-post = post_bind(post, q_new)
-
-```
-
-```{r calculate-aggregated-comps-data}
-
-# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)
-
-# containers
-x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
-x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))
-
-for (j in 1:jags_data$nj) {
-  # calculate aggregate proportions for each age
-  for (k in 1:jags_data$nk) {
-    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
-    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
-  }
-
-  # calculate aggregate proportions for each origin
-  for (o in 1:jags_data$no) {
-    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
-    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
-  }
-}
-
-dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]
-
-x_Ra_new_obs = list(
-  x_Ra_age_obs = x_Ra_age_obs,
-  x_Ra_origin_obs = x_Ra_origin_obs
-)
-
-x_Sa_prime_new_obs = list(
-  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
-  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
-)
-
-```
-
-Within a single year, the values across all panels sum to one.
-
-### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-fit-funcs}
-
-# for multinomial sample size
-weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-weir_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each age, aggregated across origins
-weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.
-
-##### CAT
-
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
-weir_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
-weir_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
-weir_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
-weir_sample_size(j_ugr)
-```
-
-### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carc-comp-fit-funcs}
-
-# for multinomial sample size
-carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
-  usr = par("usr")
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-}
-
-# for completely disaggregated fits
-carc_comp_fit_plot = function(j) {
-
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
-}
-
-# for fits to each age, aggregated across origins
-carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-# for fits to each origin, aggregated across ages
-carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
-}
-
-```
-
-#### By Age/Origin {.tabset .tabset-pills}
-
-This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.
-
-##### CAT
-
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
-carc_comp_fit_plot(j_ugr)
-```
-
-#### By Age {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.
-
-##### CAT
-
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
-carc_comp_fit_plot_age(j_ugr)
-```
-
-#### By Origin {.tabset .tabset-pills}
-
-These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.
-
-##### CAT
-
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_los)
-```
-
-##### MIN
-
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
-carc_comp_fit_plot_origin(j_ugr)
-```
-
-#### Total Sample Size {.tabset .tabset-pills}
-
-These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.
-
-##### CAT
-
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_cat)
-```
-
-##### LOS
-
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_los)
-```
-
-##### MIN
-
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_min)
-```
-
-##### UGR
-
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
-carc_sample_size(j_ugr)
-```
-
-## Spawn Status Data
-
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
-  box()
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
-}
-
-junk = sapply(1:jags_data$nj, plot_f)
-```
-
-## Length Data {.tabset .tabset-pills}
-
-### Mean Length at Summer Tagging
-
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
-```
-
-### Mean Length at Spring Tagging
-
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
-```
-
-# Spawner-to-Parr Relationship {.tabset .tabset-pills}
-
-## Beverton-Holt
-
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
-
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior samples of the BH productivity and capacity parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total parr recruits by brood year
-  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))
-
-  # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
-
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
-
-  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
-  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
-
-  # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
-```
-
-## Total Eggs vs. Total Spawners
-
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
-The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
-
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(E["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(E["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
-
-  # yaxis ticks
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)
-
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-  abline(c(0, 1000), lty = 1)
-  abline(c(0, 1800), lty = 2)
-  abline(c(0, 3600), lty = 3)
-
-  if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
-           lty = c(1,2,3), bty = "n", cex = 0.75)
-  }
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
-```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
-
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
-
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
-
-# empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
-     ylab = "Parr Capacity (000s)", yaxt = "n")
-at_y = axisTicks(par("usr")[3:4], log = FALSE)
-axis(side = 2, at = at_y, labels = at_y/1000)
-
-# draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
-
-# draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
-
-# draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
-```
-
-## Slope Parameter
-
-```{r beta-v-habitat-slope}
-# extract posterior summary of slope
-est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
-
-# print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
-```
-
-# Migratory Strategy Apportionment
-
-```{r pi-plots, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
-```
-
-# Length Relationships {.tabset .tabset-pills}
-
-## Summer Tagging
-
-```{r}
-plot_f = function(j) {
-
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "")["mean",]
-  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
-  E_scaled_upr = post_summ(post_E, "")["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
-  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
-  plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-```
-
-## Spring Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Summer Length
-
-```{r}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-### "Growth Factor" Time Series
-
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-# Length-Based Survival Relationships {.tabset .tabset-pills}
-
-## Overwinter Survival
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_lwr = (L_Pb_lwr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-  L_Pb_star_upr = (L_Pb_upr - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
-  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
-  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
-
-  # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
-       xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-## Migration to LGR
-
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
-       xlim = range(L_Mb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
-```
-
-# Equivilency Rates {.tabset .tabset-pills}
-
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
-
-### LGR to Tributary
-
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
-
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
-
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # get a max value for ylim
-  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])
-
-  # make hatchery values NA in year with no smolt
-  phi_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
-
-  # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
-
-  if (j == 1) {
-    legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
-  }
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
-```
-
-## Parr per Spawner
-
-"Spawner" means total spawners that survive pre-spawn mortality.
-
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```
-
-## Smolt per Spawner
-
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
-
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
-```
-
-## Spawners per Spawner
-
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
-
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
- abline(h = 1, lty = 2)
-}
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
-```
-
-# Straying Dynamics {.tabset .tabset-pills}
-
-## Number of Strays
-
-```{r n-stray, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
-```
-
-## Stray Composition
-
-```{r stray-comp, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
-  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
-  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
-}
-
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
-```
-
-# Ocean Survival {.tabset .tabset-pills}
-
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
-}
-```
-
-## CAT
-
-```{r}
-ocean_surv_plot(j_cat)
-```
-
-## LOS
-
-```{r}
-ocean_surv_plot(j_los)
-```
-
-## MIN
-
-```{r}
-ocean_surv_plot(j_min)
-```
-
-## UGR
-
-```{r}
-ocean_surv_plot(j_ugr)
-```
-
-# Maturity {.tabset .tabset-pills}
-
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
-```
-
-## CAT
-
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
-```
-
-## LOS
-
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
-```
-
-## MIN
-
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
-
-## UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
-```
-
-# Parameter Summaries {.tabset .tabset-dropdown}
-
-```{r my-boxplot-function}
-my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), ...) {
-  # extract posterior samples and rename them
-  post_sub = post_subset(post, params, matrix = TRUE)
-
-  if (ncol(post_sub) >= 2) {
-    colnames(post_sub) = ticklabs
-  }
-
-  # initialize a boxplot object
-  bp = boxplot(post_sub, plot = FALSE)
-
-  # replace the summary stats with my preferred quantiles
-  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
-  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
-  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, ...,
-      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
-} 
-```
-
-## Parr Recruitment
-
-```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^alpha[.]$", "Productivity")
-my_boxplot("^beta[.]$", "Capacity")
-my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
-my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Summer Parr Size
-
-```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot("^omega0[.]$", "Intercept")
-my_boxplot("^omega1[.]$", "Slope")
-my_boxplot("^sig_lL_Pb[.]$", "Process SD")
-my_boxplot("^rho_lL_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Life History Apportionment
-
-```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("^mu_pi[1,.]$", "Mean Proportion Fall Migrants")
-my_boxplot("^sig_Lpi[.]$", "Process SD")
-my_boxplot("^rho_Lpi", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
-```
-
-## Overwinter Survival {.tabset .tabset-pills}
-
-### Logistic Function Parameters
-
-```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope")
-```
-
-### Process SD
-
-```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_fall, pop = "."), "Process SD (Fall)")
-my_boxplot(sub_index("sig_Lphi_Pa_Mb[pop,LH_type]", LH_type = i_spring, pop = "."), "Process SD (Spring)")
-```
-
-### Among-pop Correlation
-
-```{r overwinter-survival-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_fall), "Among-pop Correlation (Fall)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Pa_Mb[.,.,LH_type]", LH_type = i_spring), "Among-pop Correlation (Spring)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to LGR {.tabset .tabset-pills}
-
-### Mean/Logistic Model Parameters
-
-```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("tau0[pop]", pop = "."), "Intercept", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("tau1[pop]", pop = "."), "Slope", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_nor, pop = "."), "Process SD", main = "NOR")
-my_boxplot(sub_index("sig_Lphi_Mb_Ma[pop,origin]", origin = o_hor, pop = "."), "Process SD", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r trib-to-lgr-bxp3, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lphi_Mb_Ma[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Movement Survival to Ocean
-
-```{r lgr-to-ocean-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Means
-
-```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O1[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age3-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O1[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
-
-### Means
-
-```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
-```
-
-### Process SD
-
-```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_nor, pop = "."), "", main = "NOR")
-my_boxplot(sub_index("sig_Lpsi_O2[pop,origin]", origin = o_hor, pop = "."), "", main = "HOR")
-```
-
-### Among-pop Correlation
-
-```{r age4-rho-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_nor), "Among-pop Correlation (NOR)", ticklabs = vcov_labels, las = 3)
-my_boxplot(sub_index("rho_Lpsi_O2[.,.,origin]", origin = o_hor), "Among-pop Correlation (HOR)", ticklabs = vcov_labels, las = 3)
-```
-
-## Ocean Survival {.tabset .tabset-pills}
-
-### Year 1 {.tabset .tabset-pills}
-
-#### Mean
-
-```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-#### Process SD and Correlation
-
-```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("sig_Lphi_O0_O1[pop]", pop = "."), ylab = "Process SD")
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation")
-my_boxplot("rho_Lphi_O0_O1[", ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1), las = 2)
-```
-
-### Year 2 {.tabset .tabset-pills}
-
-```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### Year 3 {.tabset .tabset-pills}
-
-```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_nor, pop = "."), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = "."), main = "HOR", ylim = c(0,1), ylab = "Average Survival")
-```
-
-### NOR:HOR Log Odds Ratios
-
-```{r ocean-surv-scaler, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("delta_O0_O1[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 1")
-my_boxplot(sub_index("delta_O1_O2[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 2")
-my_boxplot(sub_index("delta_O2_O3[pop]", pop = "."), ylab = "Log Odds Ratio", main = "Year 3")
-```
-
-## Movement Survival BON to LGR
-
-```{r bon-to-lgr-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
-my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
-```
-
-## Pre-spawn Survival
-
-```{r prespawn-surv-bxp}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_phi_Sb_Sa[pop]", pop = "."), "Average Survival", ylim = c(0,1))
-my_boxplot(sub_index("sig_Lphi_Sb_Sa[pop]", pop = "."), "Process SD")
-my_boxplot("rho_Lphi_Sb_Sa", "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels)
-```
-
-# Correlation Parameters
-
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
-)
-
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
-
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
-
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
-
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
-
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
-abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
-box()
-```
-
-# Residual Diagnostics {.tabset .tabset-pills}
-
-```{r misc-resid-fns}
-get_yr_index = function(params) {
-  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
-  yr_index = stringr::str_remove(yr_index, "\\[")
-  yr_index = stringr::str_remove(yr_index, ",")
-  as.numeric(yr_index)
-}
-
-make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
-  f = function(x) {
-    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
-    xs = round(xs, 2)
-    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
-  }
-  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
-}
-
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
-no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
-}
-```
-
-#### Why Does this Matter?
-
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Specifically, the noise (or "residual") terms should be:
-
-* **Mean-Zero**: each year has an expected value for the realized outcome, and across years errors should cancel out such that the expected residual in any given year is zero.
-* **IID**: all residuals are generated by the same random process, i.e., with mean zero and SD equal to one; with the exception of cases with an auto-regressive process included residuals among years are assumed independent.
-* **Lack of time series patterns** is implied by these two assumptions, i.e., there should be no time trends or cyclical "regime shifts".
-
-The presence of egregious violations in these assumptions is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
-
-#### What was Calculated?
-
-To examine whether these assumptions were consistently met or violated, residuals from the process model and observation model were calculated and standardized.
-
-Standardized residuals were calculated differently depending on the type of random process:
-
-* **Log-normal** (e.g., for abundance data likelihoods): `(log(realized) - log(expected))/SD`, i.e., noise in log space
-* **Logit-normal** (e.g., for survival data likelihoods, survival process noise): `(logit(realized) - logit(expected))/SD`, i.e., noise in logit space
-* **Binomial and multinomial** (e.g., for carcass count likelihoods): `sqrt(realized) - sqrt(expected)`; for multinomial counts, these were calculated for each category separately, i.e., the Freeman-Tukey statistic, which is similar to the $\chi^2$ statistic but better handles cases where some bin probabilities are small.
-
-For observation model residuals, `SD` represents the assumed observation error variability supplied to the model as known.
-For process model residuals, `SD` represents the model-estimated `sig` parameter associated with that random process.
-
-This standardization enables comparison across model components that are on different scales (e.g., abundance vs. probability terms) and have different variances, either process or observation.
-The specific standardization used implies that the mean of the residuals from a given model component should be zero across all years, should have a standard deviation of 1, and 95% of the residuals should fall between approximately -2 and 2.
-
-#### What is Shown?
-
-For each random process in the model, the time series of standardized noise terms is plotted below (mean and 95% CRI in red, first and last half mean values in blue).
-To summarize these time series quantitatively, three across-year summary statistics are reported:
-
-* **Across-year mean** -- intended to verify that noise is centered on the expected value overall (ideally equal to 0)
-* **Across-year SD** -- intended to verify that noise is as variable as expected overall (ideally equal to 1)
-* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)
-
-These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
-They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
-
-## Process Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-proc-resid-fn}
-
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-  y_ind_obs = y_ind %in% observable
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  # only for years that are observable; don't want to include any simulated years in these stats
-  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
-  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(y_ind[y_ind_obs])/2)
-  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
-  mn_post_first = apply(qresid_post[,y_first], 1, mean)
-  mn_post_last = apply(qresid_post[,y_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-    # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
-       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-             )
-
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-proc_error_ests = NULL
-```
-
-### FW Juvenile {.tabset .tabset-pills}
-
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Migratory Strategy Apportionment
-
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Over-winter Survival {.tabset .tabset-pills}
-
-##### Fall Migrants
-
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
-
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
-
-#### Yr1 Ocean Survival
-
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-3) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pr(Mature at age-4) {.tabset .tabset-pills}
-
-##### NOR
-
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
-
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r proc-error-table-prep}
-# rename parameters to human-readable format
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
-
-# correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
-proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
-
-# correct LH_type indices
-proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3
-
-# correct pop indices
-proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5
-
-# remove the age column
-proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]
-
-# replace indices with names
-proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
-proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
-proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]
-
-# which processes are in each life phase?
-fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
-sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
-
-# add a life phase column
-proc_error_ests$phase = NA
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
-proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
-proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]
-
-# add levels to each variable
-proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
-proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
-proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
-proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
-
-# drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r proc-error-table-fn}
-proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:4)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r proc-error-mean-table}
-proc_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r proc-error-sd-table}
-proc_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r proc-error-diff-table}
-proc_error_table("diff_mean")
-```
-
-## Observation Model Noise Terms {.tabset .tabset-pills}
-
-```{r plot-obs-resid-fn}
-obs_qresid_yrs = all_yrs[c(1,observable)]
-
-# function to plot a residual time series for one pop/origin/LH_type/age combo
-# returns a data frame with identifiers and across-year summary statistics
-plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
-
-  # extract posterior samples of residual time series
-  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)
-
-  # extract the year indices available
-  y_ind = get_yr_index(colnames(qresid_post))
-
-  # calculate posterior across-year mean and sd for each posterior sample
-  mn_post = apply(qresid_post, 1, mean)
-  sd_post = apply(qresid_post, 1, sd)
-
-  # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
-
-  # place qresiduals at correct place in a time series
-  # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
-  empty[,y_ind] = qresid
-  qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
-  empty_names = rep(NA, length(obs_qresid_yrs))
-  empty_names[y_ind] = colnames(qresid_post)
-
-  # calculate posterior mean(last half of years) - mean(first half of years)
-  y_first = 1:round(length(observable)/2)
-  y_last = (max(y_first) + 1):length(observable)
-  i_first = as.character(na.omit(empty_names[y_first]))
-  i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
-  first_last_mn_diff_post = mn_post_last - mn_post_first
-
-  # set the y-axis limits: leave room at top for legend
-  ylim = c(0,1.3)
-
-  # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
-
-  # draw x-axis: years
-  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
-  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
-  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)
-
-  # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  # draw reference line at 25%, 50%, and 75% quantiles
-  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)
-
-  # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
-
-  # draw legend that shows estimate summaries
-  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
-
-  # create output for building summary tables
-  data.frame(param = qresid_param,
-             pop = ifelse(!is.null(pop), pop, NA),
-             origin = ifelse(!is.null(origin), origin, NA),
-             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
-             age = ifelse(!is.null(age), age, NA),
-             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
-             year_mean_mean = mean(mn_post),
-             year_mean_lwr = unname(quantile(mn_post, 0.025)),
-             year_mean_upr = unname(quantile(mn_post, 0.975)),
-             year_sd_mean = mean(sd_post),
-             year_sd_lwr = unname(quantile(sd_post, 0.025)),
-             year_sd_upr = unname(quantile(sd_post, 0.975)),
-             diff_mean = mean(first_last_mn_diff_post), 
-             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
-             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
-  )
-}
-
-# container for across-year summary statistics
-# is rbinded many times for each random process and pop/origin/LH_type/age combo
-obs_error_ests = NULL
-```
-
-### Abundance Data {.tabset .tabset-pills}
-
-#### Fall Parr Abundance
-
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt Abundance
-
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Adult Return Abundance
-
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Survival Data {.tabset .tabset-pills}
-
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
-
-##### NOR
-
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
-
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) {
-  if (j == 3) {
-    no_data_plot(main = pops[j])
-  } else {
-    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
-  }
-})
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### BON Adults $\rightarrow$ LGR
-
-```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
-tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Length Data {.tabset .tabset-pills}
-
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-### Composition Data {.tabset .tabset-pills}
-
-#### Weir Sampling {.tabset .tabset-pills}
-
-```{r weir-comp-resid-plots-fn}
-ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
-             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")
-
-weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-_No weir data for MIN_
-
-##### UGR
-
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
-tmp = weir_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-#### Carcass Sampling {.tabset .tabset-pills}
-
-```{r carcass-comp-resid-plots-fn}
-carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
-  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
-  do.call(rbind, tmp)
-}
-```
-
-##### CAT
-
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_cat)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### LOS
-
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_los)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### MIN
-
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_min)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-##### UGR
-
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
-tmp = carcass_comp_qresid_plots(j_ugr)
-obs_error_ests = rbind(obs_error_ests, tmp)
-```
-
-### **SUMMARY TABLES** {.tabset .tabset-pills}
-
-These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
-
-```{r obs-error-table-prep}
-# rename parameters to human-readable format
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")
-
-# correct parameter names
-obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
-obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
-obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
-obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3
-
-# correct origin indices
-obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
-obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
-
-# correct LH_type indices
-obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3
-
-# correct pop indices
-obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5
-
-# correct origin indices based on age indices
-obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
-obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2
-
-# replace indices with names
-obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
-obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
-obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
-obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
-obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"
-
-# add a type column
-obs_error_ests$type = NA
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
-obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
-obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]
-
-# add levels to each variable
-obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
-obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
-obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
-obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
-obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))
-
-# determine whether posterior of across-year quantities overlaps the target value
-obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
-obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
-obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)
-
-# format the mean values to present in table
-# round and make bold if target value not in interval
-obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
-obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
-obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
-
-# drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
-```
-
-```{r obs-error-table-fn}
-obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    collapse_rows(columns = 1:5)
-}
-```
-
-#### Across-Year Mean
-
-The posterior mean of the mean noise value across all years; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
-* Below 0 indicate that the time series of noise terms was biased low relative to the expected value
-* Above 0 indicate that the time series of noise terms was biased high relative the expected value
-
-```{r obs-error-mean-table}
-obs_error_table("year_mean_mean")
-```
-
-#### Across-Year SD
-
-The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass 1 (all noise terms were standardized).
-
-Values:
-
-* Close to 1 indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
-* Below 1 indicate that the time series of noise terms was less variable than expected
-* Above 1 indicate that the time series of noise terms was more variable than expected
-
-```{r obs-error-sd-table}
-obs_error_table("year_sd_mean")
-```
-
-#### Last Half Mean - First Half Mean
-
-The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.
-
-Values:
-
-* Close to 0 indicate a lack of an overall time trend (i.e., assumption met)
-* Below 0 indicate an overall declining time trend in noise terms
-* Above 0 indicate an overall increasing time trend in noise terms
-
-```{r obs-error-diff-table}
-obs_error_table("diff_mean")
-```
-
-# JAGS Model and Data {.tabset .tabset-pills}
-
-## JAGS Model Code
-
-```{r jags-model, comment = NA}
-# print the JAGS model code
-cat(model_info$jags_model_code, sep = "\n")
-```
-
-## JAGS Model Data
-
-```{r jags-data, comment = NA}
-# print the JAGS model data
-model_info$jags_data
-```

### 2022-04-28 03-post-process/output-plots-children/01-model-info.Rmd

# Model Info {.tabset .tabset-pills}

**Scenario Name:** `r params$scenario`

**Post-MCMC Percent of Samples Retained:** `r paste0(params$thin_percent * 100, "%")`

## Attributes

```{r mcmc-dims}
# query the dimensions of the posterior samples
dims = post_dim(post)

# build a data frame for printing
df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))

# render the table
kable(df, format.args = list(big.mark = ","), caption = "Dimensions of the MCMC run. If post-MCMC percent of samples retained (above) is less than 100%, the numbers in this table are unreliable.") %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1, bold = TRUE)
```

## Run Time

```{r mcmc-time-info}
# Calculate hours per 10,000 iterations
hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
  # calculation of total iters differs if parallel or not
  if (parallel) {
    total_iters = n_adapt + n_post + n_burn
  } else {
    total_iters = (n_adapt + n_post + n_burn) * n_chains
  }
  ten_thousands_of_total_iters = total_iters/10000

  # calculate hours elapsed
  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
  time_number = as.numeric(time_diff)
  time_units = attributes(time_diff)$units
  hour_convert = switch(time_units,
                        "secs" = 3600,
                        "mins" = 60,
                        "hours" = 1,
                        "days" = 1/24)
  hours_diff = time_number/hour_convert

  # calculate/round rate
  round(hours_diff/ten_thousands_of_total_iters, 2)
})

# combine relevant info into a data frame
df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")

# make a kable for printing in output
kable(df, caption = "Run time for MCMC sampling. Includes any time the computer spent sleeping and not running MCMC. If post-MCMC percent of samples retained (above) is less than 100%, the numbers in this table are unreliable.") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
  column_spec(1, bold = TRUE)
```

### 2022-04-28 03-post-process/output-plots-children/03-fit-to-data.Rmd

# Fit to Data {.tabset .tabset-pills}

## Figures {.tabset .tabset-dropdown}

In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

### Abundance Data {.tabset .tabset-pills}

#### Fall Parr Abundance

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
```

#### Spring Smolt Abundance

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
```

#### Adult Return Abundance

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
```

### Survival Data {.tabset .tabset-dropdown}

#### Summer Parr $\rightarrow$ LGR

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
```

#### Fall Parr $\rightarrow$ LGR

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
```

#### Winter Parr $\rightarrow$ LGR

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
```

#### Spring Smolt $\rightarrow$ LGR (NOR)

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
```

#### Spring Smolt $\rightarrow$ LGR (HOR)

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
```

#### LGR Smolt $\rightarrow O_0$ (NOR)

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### LGR Smolt $\rightarrow O_0$ (HOR)

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### BON Adults $\rightarrow$ LGR (NOR)

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

#### BON Adults $\rightarrow$ LGR (HOR)

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### Composition Data {.tabset .tabset-pills}

```{r calculate-aggregated-comps-model}
# extract the full posteriors of the two composition sets
p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)

# primary containers: will store final recalculated output
p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL

# number of posterior samples
n = post_dim(post, "saved")

# loop through posterior samples, calculate various aggregates of composition by type
for (i in 1:n) {

  # format the posterior draw as arrays -- easier to subset
  p_Ra = array_format(p_Ra_full[i,])
  p_Sa_prime = array_format(p_Sa_prime_full[i,])

  ## BY AGE, AGGREGATED ACROSS ORIGINS

  # containers
  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])

      # build the element identifiers - for building names later
      inds_1_age[,k,j] = 1:jags_data$ny
      inds_2_age[,k,j] = k
      inds_3_age[,k,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]

  ## BY ORIGIN, AGGREGATED ACROSS AGES

  # containers
  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])

      # build the element identifiers - for building names later
      inds_1_origin[,o,j] = 1:jags_data$ny
      inds_2_origin[,o,j] = o
      inds_3_origin[,o,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]

  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES

  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)

}

# combine new calculated quantities into a big matrix
q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)

# combine with the rest of the posterior samples
post = post_bind(post, q_new)

```

```{r calculate-aggregated-comps-data}

# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)

# containers
x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
  }
}

dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]

x_Ra_new_obs = list(
  x_Ra_age_obs = x_Ra_age_obs,
  x_Ra_origin_obs = x_Ra_origin_obs
)

x_Sa_prime_new_obs = list(
  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
)

```

Within a single year, the values across all panels sum to one.

#### Weir Sampling {.tabset .tabset-dropdown}

```{r weir-comp-fit-funcs}

# for multinomial sample size
weir_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

# for completely disaggregated fits
weir_comp_fit_plot = function(j) {

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])

  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
weir_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))

  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

##### By Age/Origin {.tabset .tabset-pills}

This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.

###### CAT

```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_cat)
```

###### LOS

```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_los)
```

###### MIN

```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_min)
```

###### UGR

```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_ugr)
```

##### By Age {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by age, aggregated across origins.

###### CAT

```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_cat)
```

###### LOS

```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_los)
```

###### MIN

```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_min)
```

###### UGR

```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_ugr)
```

##### By Origin {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.

###### CAT

```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_cat)
```

###### LOS

```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_los)
```

###### MIN

```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_min)
```

###### UGR

```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_ugr)
```

##### Total Sample Size {.tabset .tabset-pills}

These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

###### CAT

```{r cat-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_cat)
```

###### LOS

```{r los-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_los)
```

###### MIN

```{r min-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_min)
```

###### UGR

```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
weir_sample_size(j_ugr)
```

#### Carcass Sampling {.tabset .tabset-dropdown}

```{r carc-comp-fit-funcs}

# for multinomial sample size
carc_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Sa_prime[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

# for completely disaggregated fits
carc_comp_fit_plot = function(j) {

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

# for fits to each age, aggregated across origins
carc_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
carc_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

```

##### By Age/Origin {.tabset .tabset-pills}

This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.

###### CAT

```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_cat)
```

###### LOS

```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_los)
```

###### MIN

```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_min)
```

###### UGR

```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_ugr)
```

##### By Age {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.

###### CAT

```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_cat)
```

###### LOS

```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_los)
```

###### MIN

```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_min)
```

###### UGR

```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_ugr)
```

##### By Origin {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.

###### CAT

```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_cat)
```

###### LOS

```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_los)
```

###### MIN

```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_min)
```

###### UGR

```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_ugr)
```

##### Total Sample Size {.tabset .tabset-pills}

These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

###### CAT

```{r cat-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_cat)
```

###### LOS

```{r los-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_los)
```

###### MIN

```{r min-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_min)
```

###### UGR

```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
carc_sample_size(j_ugr)
```

#### Spawn Status Data

```{r spawn-status-fits, fig.width = 8, fig.height = 5}
par(oma = c(2,2,0,0))
layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
  box()

  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
}

junk = sapply(1:jags_data$nj, plot_f)
```

#### Mean Length Data {.tabset .tabset-pills}

##### Summer Parr

```{r summer-length-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
```

##### Spring Smolt

```{r spring-length-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
```

```{r pp-check-output, child = "03a-pp-checks.Rmd", eval = model_info$do_pp_check}
```

```{r waic-output, child = "03b-waic.Rmd", eval = model_info$do_lppd}
```

### 2022-04-28 03-post-process/output-plots-children/03b-waic.Rmd

## WAIC

WAIC is a measure of model parsimony.
The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data.
There are two methods of calculating `pD`, both are shown below.
As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.

```{r calculate-waic, eval = model_info$do_lppd}
summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
  # calculate total lppd summed across all data sets within a given year
  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))

  tmp_log = log(apply(exp(total_lppd), 2, mean))
  tmp_sum = -2 * sum(tmp_log)

  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
  pD2 = sum(apply(total_lppd, 2, var))
  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
}

waic_out = summarize_lppd("_lppd[year,.+]$")

waic_out = as.data.frame(as.list(waic_out))
waic_out %>%
  kbl(format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
```

### 2022-04-28 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

# Egg-to-Parr Survival {.tabset .tabset-pills}

## Beverton-Holt

All red components are posterior summaries (medians and 95% credible intervals). The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.

```{r eggs-to-parr, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)

  # extract posterior summaries of total spawners by brood year
  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total parr recruits by brood year
  Pb = post_summ(post, sub_index("^Pb[year,pop]", pop = j, year = ts_yrs))

  # predict parr recruits along a sequence of spawner abundances
  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  E_pred = seq(0, max(E[5,]), length = 30)

  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
  Pb_pred = post_summ(Pb_pred, "Pb_pred")

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)

  # draw fitted relationship: Bayesian
  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
```

## Total Eggs vs. Total Spawners

This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model. The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.

```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(E["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(E["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, yaxt = "n")

  # yaxis ticks
  y_ticks = axisTicks(par("usr")[3:4], log = F)
  axis(side = 2, at = y_ticks, labels = y_ticks/1e6, las = 2)

  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
  abline(c(0, 1000), lty = 1)
  abline(c(0, 1800), lty = 2)
  abline(c(0, 3600), lty = 3)

  if (j == 1) {
    legend("bottomright", title = "If Each Spawner Had:",
           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
```

## Parr per Egg

This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))

  # max survival
  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(Pb_per_E["mean",] ~ E["mean",],
       ylim = c(0, 1),
       xlim = c(0, max(E["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])

  # x-axis
  x_ticks = axisTicks(par("usr")[1:2], log = F)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)

  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
  abline(h = alpha["mean",], lwd = 2, col = "red")
  box()
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
```

## Parr per Spawner

This figure is identical to above, but shows parr production per spawner instead of per egg.

```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # graphical parameters
  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))

  # empty plot
  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1)

  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
```

### 2022-04-28 03-post-process/output-plots-children/06-capacity-vs-habitat.Rmd

# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}

## Scatterplot

Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.

```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
# extract posterior summaries of the capacity parameters
beta_ests = post_summ(post, "^beta[", probs = c(0.1, 0.5, 0.9))

# extract posterior samples of the slope parameter
beta_per = post_subset(post, "lambda", TRUE)

# create a sequence of WUL values to predict capacity at
wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)

# obtain the regression line for each posterior sample
pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))

# select a subset of posterior samples at random to draw
i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)

# empty plot with correct labeling/dimensions
par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
plot(1,1, type = "n", xlim = range(wul_seq),
     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
     xlab = "Weighted Usable Length (km)",
     ylab = "Parr Capacity (000s)", yaxt = "n")
at_y = axisTicks(par("usr")[3:4], log = FALSE)
axis(side = 2, at = at_y, labels = at_y/1000)

# draw the random regression lines
junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))

# draw the posterior mean regression line
lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)

# draw the population-specific capacity estimates w/error bars and labels
points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
```

## Slope Parameter

```{r beta-v-habitat-slope}
# extract posterior summary of slope
est = post_summ(post, "^lambda$")
colnames(est) = "slope"

# print a table 
kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
```

### 2022-04-28 03-post-process/output-plots-children/07-misc-process-model.Rmd

# Miscellaneous Process Model Components {.tabset .tabset-pills}

## Migratory Strategy Apportionment

```{r pi-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
```

## Ocean Survival {.tabset .tabset-pills}

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

### CAT

```{r}
ocean_surv_plot(j_cat)
```

### LOS

```{r}
ocean_surv_plot(j_los)
```

### MIN

```{r}
ocean_surv_plot(j_min)
```

### UGR

```{r}
ocean_surv_plot(j_ugr)
```

## Maturity {.tabset .tabset-pills}

```{r maturity-plot-fn}
maturity_plot = function(j) {
  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))

  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
}
```

### CAT

```{r maturity-cat, fig.width = 6, fig.height = 5}
maturity_plot(j_cat)
```

### LOS

```{r maturity-los, fig.width = 6, fig.height = 5}
maturity_plot(j_los)
```

### MIN

```{r maturity-min, fig.width = 6, fig.height = 5}
maturity_plot(j_min)
```

### UGR

```{r maturity-ugr, fig.width = 6, fig.height = 5}
maturity_plot(j_ugr)
```

## Straying Dynamics {.tabset .tabset-pills}

### Number of Strays

```{r n-stray, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
```

### Stray Composition

```{r stray-comp, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))

  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
}

par(mfrow = c(2,2), oma = c(0,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
```

### 2022-04-28 03-post-process/output-plots-children/08-equiv-rates.Rmd

# Equivilency Rates {.tabset .tabset-pills}

## Smolt-to-Adult Rates {.tabset .tabset-pills}

### LGR to Tributary

This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).

The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years. For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996. The calculation is done for hatchery and natural origin fish separately. Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.

```{r adults-per-smolt, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100

  # make hatchery values NA in year with no smolt
  Ra_per_Ma_hor[,zero_hor_smolt] = NA

  # plot natural origin time series
  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
```

### BON to BON

```{r bon-to-bon, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

  # summarize rates
  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))

  # get a max value for ylim
  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = "."))["97.5%",])

  # make hatchery values NA in year with no smolt
  phi_hor[,zero_hor_smolt] = NA

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```

## Parr per Spawner

"Spawner" means total spawners that survive pre-spawn mortality.

```{r parr-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
```

## Smolt per Spawner

"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.

```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
```

## Spawners per Spawner

This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years). "Brood year" refers to the year the returning production was spawned.

```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
 abline(h = 1, lty = 2)
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
```

### 2022-04-28 03-post-process/output-plots-children/09-rho-params.Rmd

# Correlation Parameters

```{r rho_plot, fig.width = 6, fig.height = 7}
# get the names of all rho parameters
# these are elements of a correlation matrix
# but because the rho term is the same for all population pairs, it is sufficient 
# to summarize just one element from each matrix
rho_params = c(
  match_params(post, "rho_.+[2,1]"),
  match_params(post, "rho_.+[2,1,1]"),
  match_params(post, "rho_.+[2,1,2]")
)

# calculate/format posterior summaries
rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
rho_summs = as.data.frame(rho_summs)
rho_summs = cbind(param = rownames(rho_summs), rho_summs)
rownames(rho_summs) = NULL

# make prettier names for each term
rho_names = c(
  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
  "rho_lL_Pb[2,1]" = "Summer Mean Length",
  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
  )
rho_summs$name = rho_names[rho_summs$param]

# reorder by decreasing mean correlation
rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
at_y = nrow(rho_summs):1

# use different colors for correlations that are between origins vs. between populations
col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")

# make the plot
par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
abline(v = 0, lty = 2)
segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
abline(h = at_y - 0.5, col = "grey")
legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
box()
```

### 2022-04-28 03-post-process/output-plots-children/10-noise-term-diags.Rmd

# Random Noise Diagnostics {.tabset .tabset-pills}

```{r misc-resid-fns}
get_yr_index = function(params) {
  yr_index = stringr::str_extract(params, "\\[[0-9]+,")
  yr_index = stringr::str_remove(yr_index, "\\[")
  yr_index = stringr::str_remove(yr_index, ",")
  as.numeric(yr_index)
}

make_legend_text = function(mn_post, sd_post, first_last_mn_diff_post) {
  f = function(x) {
    xs = c(mean(x), quantile(x, c(0.025, 0.975)))
    xs = round(xs, 2)
    paste0(xs[1], " (", xs[2], " - ", xs[3], ")")
  }
  c(paste0("Mean: ", f(mn_post)), paste0("SD: ", f(sd_post)), paste0("Diff: ", f(first_last_mn_diff_post)))
}

oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
}

no_data_plot = function(main = NULL) {
  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
  text(0,0, "No Data", font = 3)
}

my_par = function() {
  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
}
```

This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
Diagnostics are separate by process model and observation model and the time series of noise terms is displayed to visually detect issues.
Each model component (process or observation) includes summary tables that quantitatively summarize the results displayed on the time series figures.

#### Why Does this Matter?

The presence of egregious assumption violations is an indication that the model may give predictions that are inconsistent with the historical data and assumed hypotheses/mechanisms.
If the assumptions are reasonably met, the noise (or "residual", representing inter-annual variability) terms should be:

1. **Non-existent on average**: each year has an expected value and the noise term represents how far the realized value falls from the expectation, either higher or lower. Thus, the expectation for any given noise term is "no noise"; i.e., if the same year was replicated many times over under the same random process, the average of the realized values would be the expected value.
2. **IID**: all noise terms for a process are generated by the same random process, i.e., with mean zero and common variance; noise terms are assumed independent from year to year, except in cases with an auto-regressive process included.
3. **Free of time series patterns**: this is implied by the above two assumptions, i.e., there should be no time trends or cyclical "regime shifts."

#### What was Calculated?

Because the model used several different types of probability distributions for accounting for process and observational noise (logit-normal, log-normal, binomial, and multinomial), we wished to use a standardization technique that would enable using the same metrics to assess assumption validity for all random processes.
We chose to use a quantile standardization, wherein the noise term for a given process in a given year is expressed as a value between zero and one and is obtained as the cumulative probability of the realized value when treating the posterior predictive distribution for that year as the CDF.

For example, consider an arbitrary outcome $x_y$ in a given year from a random process with density/mass function $f()$ with parameter vector $\mathbf{\theta}$ and lower bound of $l$ (e.g., $l=-\infty$ or $l = 0$, depending on the domain of $f()$).
The standardized residual is then:

$$
\Pr(X \leq x_y) = \int_{l}^{x_y} f(v; \mathbf{\theta}) dv
$$

If repeated realizations $x_y, x_{y+1},\dots,x_{y+n}$ are consistent with the random process $f$, then their quantile-standardized values will be distributed uniformly between zero and one (i.e., $\Pr(X \leq x_y) \sim \mathrm{U}(0,1)$).
If the parameter vector $\mathbf{\theta}$ varies annually, then $\mathbf{\theta}_y$ can be substituted and the same uniform property should hold if the realized outcomes are consistent with both (_a_) the random process $f()$ and (_b_) the (probably deterministic) process generating inter-annual variability in $\mathbf{\theta}_y$.

The interpretation of these quantile-standardized noise terms is:

* **Equal to 0.5**: The realized outcome was exactly in the center of $f()$
* **Less than 0.5**: The realized outcome was somewhere in the lower tail of $f()$, values closer to zero are more extreme noise outcomes
* **Greater than 0.5**: The realized outcome was somewhere in the upper tail of $f()$, values closer to one are more extreme noise outcomes

Because the parameter vector $\theta$ has a posterior distribution, we calculated these standardized noise terms for each MCMC sample, which provides posterior distributions of the noise terms as well.

We performed this calculation for each random process (of both the observation and process components) in the model using the built-in cumulative distribution functions in JAGS.
For multinomial random variables (i.e., adult age/origin composition), we used category-specific binomial distributions to assess noise.
This allowed assessing the validity of age/origin-specific noise terms needed to accommodate the data.

##### JAGS Code Example

Consider one process in the model in which the survival probability varies annually (`phi[y]`) around a time constant mean (`mu_phi`) with logit-normal variability and standard deviation of `sigma_Lphi`.
Further, suppose we have counts of tagged fish we know survived (`x_surv[y]`) and the total number of fish tagged (`n_tagged[y]`) each year.
We wish to calculate the process model noise terms as quantile-standardized residuals (`phi_qresid[y]` and `x_surv_qresid[y]`).
The code below illustrates this calculation for this reduced example:

<details>
<summary>Click to Show Example Code</summary>
<pre>
# priors
mu_phi ~ dbeta(1,1)
sigma_Lphi ~ dunif(0,5)
&nbsp;
for (y in 1:ny) {
  # random process
  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_Lphi^2)
  phi[y] &lt;- ilogit(Lphi[y])
  &nbsp;
  # standardized process noise term
  phi_qresid[y] &lt;- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_Lphi^2)
  &nbsp;
  # likelihood statement for fitting model
  x_surv[y] ~ dbin(phi[y], n_tagged[y])
  &nbsp;
  # standardized observation noise term
  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
} </pre>
</details>

#### What is Shown?

For each random process in the model, the time series of standardized noise terms is plotted below:

* red points/bars: year-specific posterior mean/95% CRI
* blue horizontal lines: first and last half of time series mean values
* grey horizontal lines: expected 25%, 50%, and 75% quantiles of the standardized residuals).

To summarize these time series quantitatively, we report three across-year summary statistics:

* **Across-year mean** -- intended to verify that noise terms are centered on the expected value overall (ideally equal to 0.5; the expected value of a $\mathrm{U}(0,1)$ distribution)
* **Across-year SD** --- intended to verify that noise terms are as variable as expected overall (ideally equal to $\sqrt{1/12}$ = `r round(sqrt(1/12), 2)`; the standard deviation of a $\mathrm{U}(0,1)$ distribution)
* **mean(last half) - mean(first half)** -- intended to verify that noise is not time-trending (ideally equal to 0)

These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`

## Process Model Noise Terms {.tabset .tabset-pills}

```{r plot-proc-resid-fn}

plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract posterior samples of residual time series
  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)

  # extract the year indices available
  y_ind = get_yr_index(colnames(qresid_post))
  y_ind_obs = y_ind %in% observable

  # calculate posterior across-year mean and sd for each posterior sample
  # only for years that are observable; don't want to include any simulated years in these stats
  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(y_ind[y_ind_obs])/2)
  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
  mn_post_first = apply(qresid_post[,y_first], 1, mean)
  mn_post_last = apply(qresid_post[,y_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # calculate posterior summaries of standardized qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

    # set the y-axis limits: leave room at top for legend
  ylim = c(0,1.3)

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

  # draw x-axis: years
  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)

  # draw reference line at 25%, 50%, and 75% quantiles
  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box()

  # create output for building summary tables
  data.frame(param = qresid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
             )

}

# container for across-year summary statistics
# is rbinded many times for each random process and pop/origin/LH_type/age combo
proc_error_ests = NULL
```

### FW Juvenile {.tabset .tabset-pills}

#### Egg-to-Parr Survival

```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Summer Parr Mean Length

```{r summer-length-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Migratory Strategy Apportionment

```{r pi-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Over-winter Survival {.tabset .tabset-pills}

##### Fall Migrants

```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### Spring Migrants

```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Summer Parr to Spring Smolt "Growth Factor"

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Trib to LGR {.tabset .tabset-pills}

##### NOR

```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### LGR to BON Survival

```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### SW Juvenile {.tabset .tabset-pills}

#### Yr1 Ocean Survival

```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Pr(Mature at age-3) {.tabset .tabset-pills}

##### NOR

```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Pr(Mature at age-4) {.tabset .tabset-pills}

##### NOR

```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### FW Adult {.tabset .tabset-pills}

#### BON to LGR Survival

```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

#### Pre-spawn Survival

```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

### **SUMMARY TABLES** {.tabset .tabset-pills}

These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel). Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.

```{r proc-error-table-prep}
# rename parameters to human-readable format
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")

# correct origin indices
proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1

# correct LH_type indices
proc_error_ests$LH_type[is.na(proc_error_ests$LH_type)] = 3

# correct pop indices
proc_error_ests$pop[is.na(proc_error_ests$pop)] = 5

# remove the age column
proc_error_ests = proc_error_ests[,-which(colnames(proc_error_ests) == "age")]

# replace indices with names
proc_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[proc_error_ests$pop]
proc_error_ests$origin = c("NOR", "HOR", "Combined")[proc_error_ests$origin]
proc_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[proc_error_ests$LH_type]

# which processes are in each life phase?
fw_juv = c("Egg to Parr Survival", "Summer Parr Length", "Migratory Strategy Apportionment", "Overwinter Survival", "Summer to Spring 'Growth Factor'", "Trib to LGR Survival", "LGR to BON Survival")
sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")

# add a life phase column
proc_error_ests$phase = NA
proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_juv, 1, proc_error_ests$phase)
proc_error_ests$phase = ifelse(proc_error_ests$param %in% sw_juv, 2, proc_error_ests$phase)
proc_error_ests$phase = ifelse(proc_error_ests$param %in% fw_adult, 3, proc_error_ests$phase)
proc_error_ests$phase = c("FW Juvenile", "SW Juvenile", "FW Adult")[proc_error_ests$phase]

# add levels to each variable
proc_error_ests$phase = factor(proc_error_ests$phase, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
proc_error_ests$param = factor(proc_error_ests$param, levels = c(fw_juv, sw_juv, fw_adult))
proc_error_ests$origin = factor(proc_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
proc_error_ests$LH_type = factor(proc_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
proc_error_ests$pop = factor(proc_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))

# determine whether posterior of across-year quantities overlaps the target value
proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)

# drop unneeded columns
proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
```

```{r proc-error-table-fn}
proc_error_table = function(var) {
  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
  out[is.na(out)] = ""

  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    collapse_rows(columns = 1:4)
}
```

#### Across-Year Mean

The posterior mean of the mean standardized noise value across all years; bold indicates the 95% CRI did not encompass the target value of 0.5.

**Interpretation of Values**:

* **Close to 0.5** indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
* **Below 0.5** indicate that the time series of noise terms was biased low relative to the center of the distribution
* **Above 0.5** indicate that the time series of noise terms was biased high relative the center of the distribution

```{r proc-error-mean-table}
proc_error_table("year_mean_mean")
```

#### Across-Year SD

The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass $\sqrt{1/12}$ = `r round(sqrt(1/12), 2)`; the standard deviation of a $\mathrm{U}(0,1)$ distribution.

**Interpretation of Values**:

* **Close to `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
* **Below `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was less variable than expected
* **Above `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was more variable than expected

```{r proc-error-sd-table}
proc_error_table("year_sd_mean")
```

#### Last Half Mean - First Half Mean

The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.

**Interpretation of Values**:

* **Close to 0** indicate a lack of an overall time trend (i.e., assumption met)
* **Below 0** indicate an overall declining time trend in noise terms
* **Above 0** indicate an overall increasing time trend in noise terms

```{r proc-error-diff-table}
proc_error_table("diff_mean")
```

## Observation Model Noise Terms {.tabset .tabset-pills}

```{r plot-obs-resid-fn}
obs_qresid_yrs = all_yrs[c(1,observable)]

# function to plot a residual time series for one pop/origin/LH_type/age combo
# returns a data frame with identifiers and across-year summary statistics
plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract posterior samples of residual time series
  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)

  # extract the year indices available
  y_ind = get_yr_index(colnames(qresid_post))

  # calculate posterior across-year mean and sd for each posterior sample
  mn_post = apply(qresid_post, 1, mean)
  sd_post = apply(qresid_post, 1, sd)

  # calculate posterior summaries of qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # place qresiduals at correct place in a time series
  # ie., insert missing values
  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
  empty[,y_ind] = qresid
  qresid = empty[,observable]
  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
  empty_names = rep(NA, length(obs_qresid_yrs))
  empty_names[y_ind] = colnames(qresid_post)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(observable)/2)
  y_last = (max(y_first) + 1):length(observable)
  i_first = as.character(na.omit(empty_names[y_first]))
  i_last = as.character(na.omit(empty_names[y_last]))
  mn_post_first = apply(qresid_post[,i_first], 1, mean)
  mn_post_last = apply(qresid_post[,i_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # set the y-axis limits: leave room at top for legend
  ylim = c(0,1.3)

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")

  # draw x-axis: years
  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  # draw reference line at 25%, 50%, and 75% quantiles
  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)

  # draw posterior mean for first and half of time series
  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box()

  # create output for building summary tables
  data.frame(param = qresid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
  )
}

# container for across-year summary statistics
# is rbinded many times for each random process and pop/origin/LH_type/age combo
obs_error_ests = NULL
```

### Abundance Data {.tabset .tabset-pills}

#### Fall Parr Abundance

```{r fall-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt Abundance

```{r spring-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Spring Trap Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Adult Return Abundance

```{r adult-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "log(Total Adult Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Survival Data {.tabset .tabset-pills}

#### Summer Parr $\rightarrow$ LGR

```{r summer-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Fall Parr $\rightarrow$ LGR

```{r fall-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Winter Parr $\rightarrow$ LGR

```{r winter-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

##### NOR

```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

##### HOR

```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### LGR Smolt $\rightarrow$ Ocean

```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### BON Adults $\rightarrow$ LGR

```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Pre-spawn

```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Length Data {.tabset .tabset-pills}

#### Summer Length

```{r summer-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Summer Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Length

```{r spring-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Spring Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

### Composition Data {.tabset .tabset-pills}

#### Weir Sampling {.tabset .tabset-pills}

```{r weir-comp-resid-plots-fn}
ko_names = c("Age-3 (NOR)", "Age-4 (NOR)", "Age-5 (NOR)",
             "Age-3 (HOR)", "Age-4 (HOR)", "Age-5 (HOR)")

weir_comp_qresid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

##### CAT

```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

##### LOS

```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

##### MIN

_No weir data for MIN_

##### UGR

```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

#### Carcass Sampling {.tabset .tabset-pills}

```{r carcass-comp-resid-plots-fn}
carcass_comp_qresid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

##### CAT

```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

##### LOS

```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

##### MIN

```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_min)
obs_error_ests = rbind(obs_error_ests, tmp)
```

##### UGR

```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

### **SUMMARY TABLES** {.tabset .tabset-pills}

These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel). Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.

```{r obs-error-table-prep}
# rename parameters to human-readable format
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")

# correct parameter names
obs_error_ests$param[obs_error_ests$param == "Fall Tagging -> LGR" & obs_error_ests$LH_type == 2] = "Winter Tagging -> LGR"
obs_error_ests$param[obs_error_ests$param == "Spring Tagging -> LGR" & obs_error_ests$origin == 2] = "Smolt Release -> LGR"
obs_error_ests$origin[obs_error_ests$param == "Fall Screw Trap"] = 1
obs_error_ests$origin[obs_error_ests$param == "Adult Return"] = 3

# correct origin indices
obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1

# correct LH_type indices
obs_error_ests$LH_type[is.na(obs_error_ests$LH_type)] = 3

# correct pop indices
obs_error_ests$pop[is.na(obs_error_ests$pop)] = 5

# correct origin indices based on age indices
obs_error_ests$origin[obs_error_ests$age %in% c(1,2,3)] = 1
obs_error_ests$origin[obs_error_ests$age %in% c(4,5,6)] = 2

# replace indices with names
obs_error_ests$pop = c("CAT", "LOS", "MIN", "UGR", "Combined")[obs_error_ests$pop]
obs_error_ests$origin = c("NOR", "HOR", "Combined")[obs_error_ests$origin]
obs_error_ests$LH_type = c("Fall Mig.", "Spring Mig.", "Combined")[obs_error_ests$LH_type]
obs_error_ests$age = c("Age-3", "Age-4", "Age-5", "Age-3", "Age-4", "Age-5")[obs_error_ests$age]
obs_error_ests$age[is.na(obs_error_ests$age)] = "Combined"

# add a type column
obs_error_ests$type = NA
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Fall Screw Trap", "Spring Screw Trap", "Adult Return"), 1, obs_error_ests$type)
obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Summer Parr", "Spring Smolt"), 4, obs_error_ests$type)
obs_error_ests$type = c("Abundance", "Survival", "Composition", "Mean Length")[obs_error_ests$type]

# add levels to each variable
obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))
obs_error_ests$LH_type = factor(obs_error_ests$LH_type, levels = c("Fall Mig.", "Spring Mig.", "Combined"))
obs_error_ests$age = factor(obs_error_ests$age, levels = c("Age-3", "Age-4", "Age-5", "Combined"))
obs_error_ests$pop = factor(obs_error_ests$pop, levels = c("CAT", "LOS", "MIN", "UGR", "Combined"))

# determine whether posterior of across-year quantities overlaps the target value
obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)

# drop unneeded columns
obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
```

```{r obs-error-table-fn}
obs_error_table = function(var) {
  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
  out[is.na(out)] = ""
  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")

  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    collapse_rows(columns = 1:5)
}
```

#### Across-Year Mean

The posterior mean of the mean standardized noise value across all years; bold indicates the 95% CRI did not encompass the target value of 0.5.

**Interpretation of Values**:

* **Close to 0.5** indicate that the time series of noise terms was not biased relative to the expected value (i.e., assumption met)
* **Below 0.5** indicate that the time series of noise terms was biased low relative to the center of the distribution
* **Above 0.5** indicate that the time series of noise terms was biased high relative the center of the distribution

```{r obs-error-mean-table}
obs_error_table("year_mean_mean")
```

#### Across-Year SD

The posterior mean of the SD of noise value across all years; bold indicates the 95% CRI did not encompass $\sqrt{1/12}$ = `r round(sqrt(1/12), 2)`; the standard deviation of a $\mathrm{U}(0,1)$ distribution.

**Interpretation of Values**:

* **Close to `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was as variable as expected (i.e., assumption met)
* **Below `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was less variable than expected
* **Above `r round(sqrt(1/12), 2)`** indicate that the time series of noise terms was more variable than expected

```{r obs-error-sd-table}
obs_error_table("year_sd_mean")
```

#### Last Half Mean - First Half Mean

The posterior mean of `mean(noise term in last half of years) - mean(noise term in first half of years)`; bold indicates the 95% CRI did not encompass 0.

**Interpretation of Values**:

* **Close to 0** indicate a lack of an overall time trend (i.e., assumption met)
* **Below 0** indicate an overall declining time trend in noise terms
* **Above 0** indicate an overall increasing time trend in noise terms

```{r obs-error-diff-table}
obs_error_table("diff_mean")
```

### 2022-06-16 03-post-process/output-plots.Rmd

@@
 # set root directory to the project directory: one level up from this location
-knitr::opts_knit$set(root.dir = "../")
+# knitr::opts_knit$set(root.dir = "../")
 ```
@@
 # load packages
-source("00-packages.R")
+source("../00-packages.R")
 
 # load all necessary functions
-invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))
+invisible(sapply(list.files(path = "../01-functions", pattern = "\\.R$", full.names = T), source))
 
 # set the input directory
-in_dir = "02-model/model-output"
+in_dir = "../02-model/model-output"
 

### 2022-06-16 02-model/fit-model.R
Lower survival past sea lions in early years
See #153

@@ -52,6 +52,9 @@ if (is.na(mcmc_length)) {
 jags_data = create_jags_data_mult(c("CAT", "LOS", "MIN", "UGR"))
 jags_data = append_no_na_indices(jags_data)
 
+# reduce assumed survival past sea lions in the early years
+jags_data$phi_SL[as.character(1991:2000),] = 0.85
+
 # 1995 UGR spring tagging has mean length but no SE?
 # is.na(jags_data$L_Pb_obs) == is.na(jags_data$sig_L_Pb_obs)
 # is.na(jags_data$L_Mb_obs) == is.na(jags_data$sig_L_Mb_obs)

### 2022-06-27 02-model/model-code.R
Tighten priors on process variance terms

@@ -10,7 +10,7 @@ jags_model_code = function() {
     alpha[j] ~ dbeta(1, 1)
     lbeta[j] ~ dnorm(log(lambda * wul[j]), 1/sig_lbeta^2) %_% T(,15) # log capacity. bound to prevent nonsensically large draws
     beta[j] <- exp(lbeta[j])
-    sig_Lphi_E_Pb[j] ~ dunif(0, 5)
+    sig_Lphi_E_Pb[j] ~ dunif(0, 1)
     lambda_pop[j] <- beta[j]/wul[j]  # derived pop-specific lambda, includes process noise in regression
 
     # length at end of summer vs. eggs relationship: density-dependent spring/summer growth
@@ -21,7 +21,7 @@ jags_model_code = function() {
     ### PRIORS: FRESHWATER PARAMETERS ###
     # aggregate parr to LH-specific parr
     mu_pi[i_fall,j] ~ dbeta(1, 1)
-    sig_Lpi[j] ~ dunif(0, 5)
+    sig_Lpi[j] ~ dunif(0, 1)
     mu_pi[i_spring,j] <- 1 - mu_pi[i_fall,j]
     
     # overwinter survival parameters: LH-specific
@@ -31,7 +31,7 @@ jags_model_code = function() {
     for (i in 1:ni) {
       gamma0[i,j] ~ dt(0, 1/1.566^2, 7.763)
       gamma1[i,j] ~ dt(0, 1/1.566^2, 7.763)
-      sig_Lphi_Pa_Mb[i,j] ~ dunif(0, 5)
+      sig_Lphi_Pa_Mb[i,j] ~ dunif(0, 1)
     }
 
     # coefficients for obtaining summer mean length to spring mean length growth factor
@@ -43,15 +43,15 @@ jags_model_code = function() {
     # assumed equal among migration types
     tau0[j] ~ dt(0, 1/1.566^2, 7.763)
     tau1[j] ~ dt(0, 1/1.566^2, 7.763)
-    sig_Lphi_Mb_Ma[o_nor,j] ~ dunif(0, 5)
+    sig_Lphi_Mb_Ma[o_nor,j] ~ dunif(0, 1)
     
     # hatchery origin movement survival (trib to LGD): have spring migrants only
     mu_phi_Mb_Ma[i_spring,o_hor,j] ~ dbeta(1, 1)
[…]

### 2022-06-27 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Fix typos in mcmc-diags Rmd
Turn off priors for yr2&3 ocean survival

@@
 # Year 2 ocean survival
-L1 = "Year 2 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O1_O2[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+# L1 = "Year 2 Ocean Survival"
+# L2 = c("Mean")
+# base = c("mu_phi_O1_O2[origin,pop]")
+# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
 # Year 2 ocean survival
-L1 = "Year 3 Ocean Survival"
-L2 = c("Mean")
-base = c("mu_phi_O2_O3[origin,pop]")
-match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+# L1 = "Year 3 Ocean Survival"
+# L2 = c("Mean")
+# base = c("mu_phi_O2_O3[origin,pop]")
+# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 

### 2022-06-27 02-model/fit-model.R

@@ -27,7 +27,7 @@ do_pp_check = TRUE
 do_lppd = FALSE
 
 # specify a scenario name
-scenario = "base"
+scenario = "survival-edits-no-O1-prior-fix-ocean-surv"
 
 # handle command line arguments
 # run this script via command line: Rscript 02-model/fit-model.R LOS TRUE
@@ -42,7 +42,7 @@ if (is.na(rmd)) {
 }
 
 if (is.na(mcmc_length)) {
-  mcmc_length = "very_short"
+  mcmc_length = "short"
   cat("\n\n'mcmc_length' was not supplied as a command line argument.", mcmc_length, "will be used.")
 }
 
@@ -109,6 +109,7 @@ add_jags_data = append(add_jags_data, list(
 
 # add hyperparameters of priors on ocean survival parameters
 add_jags_data = append(add_jags_data, list(
+  mu_phi_O0_O1_prior = c(1, 1),
   mu_phi_O1_O2_prior = c(60, 40),
   mu_phi_O2_O3_prior = c(70, 30)
 ))
@@ -554,3 +555,4 @@ if (rmd & last_yr > 2019) {
   setwd("../")
   cat("\n\nDone.")
 }
+

### 2022-06-27 02-model/model-code.R

@@ -68,9 +68,11 @@ jags_model_code = function() {
     
     ### PRIORS: OCEAN SURVIVAL ###
     # mean survival by ocean year transition for natural origin
-    mu_phi_O0_O1[o_nor,j] ~ dbeta(1,1)                                          # first winter at sea: to become SWA1
-    mu_phi_O1_O2[o_nor,j] ~ dbeta(mu_phi_O1_O2_prior[1], mu_phi_O1_O2_prior[2]) # second winter at sea: to become SWA2
-    mu_phi_O2_O3[o_nor,j] ~ dbeta(mu_phi_O2_O3_prior[1], mu_phi_O2_O3_prior[2]) # third winter at sea: to become SW3
+    mu_phi_O0_O1[o_nor,j] ~ dbeta(mu_phi_O0_O1_prior[1], mu_phi_O0_O1_prior[2]) # first winter at sea: to become SWA1
+    # mu_phi_O1_O2[o_nor,j] ~ dbeta(mu_phi_O1_O2_prior[1], mu_phi_O1_O2_prior[2]) # second winter at sea: to become SWA2
+    # mu_phi_O2_O3[o_nor,j] ~ dbeta(mu_phi_O2_O3_prior[1], mu_phi_O2_O3_prior[2]) # third winter at sea: to become SW3
+    mu_phi_O1_O2[o_nor,j] <- 0.6
+    mu_phi_O2_O3[o_nor,j] <- 0.7
     
     # log odds ratio between natural and hatchery origin
     delta_O0_O1[j] ~ dt(0, 1/1.566^2, 7.763)

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Update new math operator defns

@@
   - \renewcommand{\eqref}[1]{\ref{#1}}
+  - \renewcommand*{\log}{\mathrm{log}\hspace{-0.20em}}
+  - \renewcommand*{\max}{\mathrm{max}\hspace{-0.20em}}
+  - \newcommand{\logit}{\mathrm{logit}\hspace{-0.20em}}
+  - \newcommand{\ilogit}{\mathrm{logit}^{-1}\hspace{-0.20em}}
+  - \newcommand{\MVNdist}{\mathcal{MVN}\hspace{-0.20em}}
+  - \newcommand{\Ndist}{\mathcal{N}\hspace{-0.20em}}
+  - \newcommand{\Bdist}{\mathcal{B}\hspace{-0.20em}}
+  - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
 ---
@@
 ```
-
-\newcommand{\logit}{\mathrm{logit}}
-\newcommand{\ilogit}{\mathrm{logit}^{-1}}
 

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Implement new math operators

@@
 For example, to denote that $k$ should take on only the values of 1 and 3 (not 2), we would write, $k \in [1,3]$.
-* $\log(x)$ represents the natural logarithm of $x$ (i.e., $\log_e(x)$) and it is implied that the constraint $x > 0$ is satisfied.
-* $\logit(p)$ represents the log odds of $p$ (i.e., $\log[p/(1-p)])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
+* $\log\left(x\right)$ represents the natural logarithm of $x$ and it is implied that the constraint $x > 0$ is satisfied.
+* $\logit\left(p\right)$ represents the log odds of $p$ (i.e., $\log\left[p/(1-p)\right])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
 * All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \rightarrow B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \rightarrow B}_{y,j}}$, which we use as a direct estimate of observation error variability).
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
+\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
 (\#eq:generic-random)
@@
 \begin{equation}
-\log(\beta_j) \sim \mathcal{N}\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
+\log\left(\beta_j\right) \sim \Ndist\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
 (\#eq:beta-random)
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
+\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
 (\#eq:phi-E-Pb-random)
@@
 \begin{equation}
-\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
+\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
 (\#eq:pi-random)
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
+\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
 (\#eq:phi-Pa-Mb-random)
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
+\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
 (\#eq:phi-Ma-O0-random)
@@
 \begin{equation}
-\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
+\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
 (\#eq:fall-count-data)
@@
 \begin{equation}
-\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
+\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
 (\#eq:spring-count-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \mathcal{N}\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
+\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
 (\#eq:summer-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
 (\#eq:fall-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
 (\#eq:winter-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
 (\#eq:spring-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
 (\#eq:spring-surv-HOR-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
+\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \Ndist\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
 (\#eq:hydro-surv-data)
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
+\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
 (\#eq:phi-O0-O1-random)
@@
 \begin{aligned}
-\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
-\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
+\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
+\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
 \end{aligned}
@@
 = \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
-\sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
+\sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
 \end{cases}
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
+\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
 (\#eq:phi-Sb-Sa-random)
@@
 \begin{equation}
-\log\left(\hat{R}^{a}_{y,j}\right) \sim \mathcal{N}\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
+\log\left(\hat{R}^{a}_{y,j}\right) \sim \Ndist\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
 (\#eq:Ra-data)
@@
 \begin{equation}
-\hat{x}^{\mathrm{LGR}}_{y,o} \sim \mathcal{B}\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
+\hat{x}^{\mathrm{LGR}}_{y,o} \sim \Bdist\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
 (\#eq:upstream-surv-data)
@@
 \begin{equation}
-\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \mathcal{B}\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
+\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \Bdist\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
 (\#eq:prespawn-surv-data)
@@
 \begin{equation}
-\boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
+\boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \Mdist\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
 (\#eq:weir-comp-data)
@@
 \begin{equation}
-z_{k,j} \sim \mathcal{N}(\dot{z}_{k}, \sigma_{z_k})
+z_{k,j} \sim \Ndist(\dot{z}_{k}, \sigma_{z_k})
 (\#eq:z-random)
@@
 \begin{equation}
-\log(\zeta_{k,j}) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
+\log\left(\zeta_{k,j}\right) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
 (\#eq:get-zeta-no-minam)
@@
 \begin{equation}
-\boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
+\boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \Mdist\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
 (\#eq:carcass-comp-data)

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write summer parr size process dynamics text

@@
 
-### Reproduction and Parr Recruitment
+### Egg Production, Parr Recruitment, and Parr Mean Size
 
@@
 (\#eq:get-Pb)
+\end{equation}
+
+In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
+It is well known that juvenile survival is related to body size \todo{Insert References} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
+We modeled expected mean parr length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:
+
+\begin{equation}
+\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \frac{E_{y,j}}{\mathrm{WUL}_j}
+(\#eq:get-L-Pb-dot)
+\end{equation}
+
+and the realized mean parr length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$ (constructed of $\sigma_{L_{j}^{P^{b}}}$ and $\rho_{L^{P^{b}}}$ following eq.
+\@ref(eq:generic-Sigma4by4)):
+
+\begin{equation}
+\log\left(\boldsymbol{L}^{P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left[\log\left(\boldsymbol{\dot{L}}^{P^{b}}_{y,1:n_j}\right), \Sigma_{L^{P^{b}}}\right]
+(\#eq:L-Pb-random)
 \end{equation}

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write spring smolt size process dynamics text

@@
 
-### Survival to Smolt Stage and Hatchery Inputs
+### Survival to Smolt Stage and Mean Smolt Size
 
-Overwinter survival from the end of the parr year (i.e., age-1) to the start of the smolt year (i.e., age-2), denoted by $\phi^{P^{a} \rightarrow M^{b}}_{y,i,j}$, was modeled as a logit-linear function of parr density (scaled to the same metric of weighted usable habitat length [$\mathrm{WUL}_j$] used in eq.
-\@ref(eq:beta-random)).
+Overwinter survival from the end of the parr year (i.e., age-1) to the start of the smolt year (i.e., age-2), denoted by $\phi^{P^{a} \rightarrow M^{b}}_{y,i,j}$, was modeled as a logit-linear function of mean parr size.
 Deterministic overwinter survival was:
@@
 \begin{equation}
-\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot \left(\frac{P^{a}_{y,i,j}}{\mathrm{WUL}_j}\right)
+\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,i,j} \cdot L^{*P^{b}}_{y,j}
 (\#eq:get-phi-Pa-Mb-dot)
@@
 
-Note the migratory strategy-specific intercept ($\gamma_{0,i,j}$) but common slope terms ($\gamma_{1,j}$).
+Where $L^{*P^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed mean parr length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation.
 Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq.
@@
 For populations with hatchery supplementation, hatchery-origin smolt releases (assumed known without error) were introduced at this point as well and stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
+We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
+Because only spring migrants are measured for mean smolt length in the spring (as they pass the screw trap), we must assume equal lengths for fall migrant smolt and thus omit the $i$ subscript from these quantities related to mean smolt length.
+Preliminary analyses on the observed mean length data revealed that mean smolt length was positively related with parr length, but that the relationship was non-linear.
+We thus modeled the expected multiplicative change in mean size between the parr and smolt stage as a log-linear function of (standardized) parr mean size:
+
+\begin{equation}
+\log\left(\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}\right) = \theta_{0,j} + \theta_{1,j} \cdot L^{*P^{b}}_{y,j}
+(\#eq:get-Delta-L-Pb-L-Mb-dot)
+\end{equation}
+
+and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ (constructed of $\sigma_{\Delta_{j}^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ and $\rho_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ following eq.
+\@ref(eq:generic-Sigma4by4)):
+
+\begin{equation}
+\log\left(\boldsymbol{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,1:n_j}\right) \sim \MVNdist\left[\log\left(\boldsymbol{\dot{\Delta}}^{L^{P^{b} \rightarrow L^{M^{b}}}}_{y,1:n_j}\right), \Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}\right]
+(\#eq:Delta-L-Pb-L-Mb-random)
+\end{equation}
+
+Mean smolt length was then the product:
+
+\begin{equation}
+L^{M^{b}}_{y,j} = L^{P^{b}}_{y,j} \cdot \Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}
+(\#eq:get-L-Mb)
+\end{equation}
 

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Move mention of HOR release to own section

@@
 
-For populations with hatchery supplementation, hatchery-origin smolt releases (assumed known without error) were introduced at this point as well and stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
 We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
@@
 \end{equation}
+
+### Hatchery Inputs
+
+For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error) were stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
+The abundance of hatchery-origin fish for all subsequent life stages was tracked separately from natural-origin fish.
 

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write size-based migration survival text

@@
 We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams encountered in the downstream migration, and (_ii_) from LGR to the ocean.
-For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these parameter below), but we were able to model natural-origin survival separately from hatchery-origin.
-We assume that year-specific realized survival values were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{b} \rightarrow M^{a}}_{o,j}$) with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}$ (constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{o,j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}_{o}}$ following eq.
+For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin.
+
+We modeled deterministic out-of-basin migration for natural-origin smolt as a logit-linear function of smolt size:
+
+\begin{equation}
+\logit\left(\dot{\phi}^{M^{b} \rightarrow M^{a}}_{y,o=\mathrm{NOR},j}\right) = \tau_{0,j} + \tau_{1,j} \cdot L^{*M^{b}}_{y,j}
+(\#eq:get-phi-Mb-Ma-dot)
+\end{equation}
+
+Where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed mean smolt length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
+Realized out-of-basin migration survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}}$ (each matrix constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
+\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
 (\#eq:phi-Mb-Ma-random)

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write size data likelihood assumptions text

@@
 
+### Mean Length Data Sources
+
+Upon capture for PIT tagging, individual fish lengths are measured.
+We calculated the mean length (and the associated standard errors) of all captured fish (tagged and untagged; only fish $\ge$ 55mm can receive a PIT tag) and used them in log-normal likelihoods by assuming:
+
+\begin{equation}
+\log\left(\hat{L}^{P^{b}}_{y,j}\right) \sim \Ndist\left[\log\left(L^{P^{b}}_{y,j}\right), \hat{\sigma}_{L^{P^{b}}_{y,j}}\right]
+(\#eq:L-Pb-data)
+\end{equation}
+
+for mean length data for the summer parr tagging group and
+
+\begin{equation}
+\log\left(\hat{L}^{M^{b}}_{y,j}\right) \sim \Ndist\left[\log\left(L^{M^{b}}_{y,j}\right), \hat{\sigma}_{L^{M^{b}}_{y,j}}\right]
+(\#eq:L-Mb-data)
+\end{equation}
+
+for mean length data for the smolt tagging group.
+Because the each population has approximately 1,000 fish tagged and measured during each tagging event, the standard errors on the mean length estimates were quite small.
+
 # Ocean Juvenile Phase
@@
   "surv" = "Survival",
+  "length" = "Length",
   "comp" = "Composition"

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Disable the repeat_header_continued kable feature
This causes a bug where the last line of the TeX is duplicated and printed as output at the bottom of the table. A kableExtra bug.

@@
 kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
-  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
+  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
+                # repeat_header_continued = "\\textit{(Continued on next page...)}"
+                ) %>%
   row_spec(0, bold = TRUE) %>%
@@
 kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
-  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
+  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
+                # repeat_header_continued = "\\textit{(Continued on next page...)}"
+                ) %>%
   row_spec(0, bold = TRUE) %>%
@@
 
-kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE) %>%
-  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
+kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE, longtable = TRUE) %>%
+  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
+                # repeat_header_continued = "\\textit{(Continued on next page...)}"
+                ) %>%
   row_spec(0, bold = TRUE) %>%
@@
 kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
-  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
+  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
+                # repeat_header_continued = "\\textit{(Continued on next page...)}"
+                ) %>%
   row_spec(0, bold = TRUE) %>%

### 2022-06-28 100-math-description/GR-sslcm-math-description.Rmd
Include todolist package

@@
 fontfamily: mathpazo
-geometry: margin=1in
+geometry: [top=1in,bottom=1in,left=0.25in,right=1.75in]
 linkcolor: cyan
@@
   - \usepackage{float}
+  - \usepackage{xcolor}
+  - \definecolor{my-blue}{HTML}{E6F0FF}
+  - \usepackage[textwidth=1.5in]{todonotes}
+  - \setuptodonotes{backgroundcolor=my-blue,textcolor=black,linecolor=ProcessBlue,bordercolor=my-blue,size=footnotesize}
   - \usepackage[labelfont={bf,sc},labelsep=period]{caption}

### 2022-06-28 100-math-description/GR-sslcm-math-description.Rmd
Shorten text in intro/syntax sections

@@
 
-The purpose of the state-space life cycle model for Grande Ronde spring Chinook salmon is to synthesize the abundant and diverse biological data sets that have been collected as part of routine monitoring programs into a self-contained and internally consistent population dynamics model.
+The purpose of the state-space life cycle model for Grande Ronde spring Chinook salmon is to synthesize data sets that have been collected as part of routine monitoring programs into a self-contained and internally consistent population dynamics model.
 Such a synthesis can provide richer insights about unobserved quantities (e.g., total parr recruitment abundance) and the relationships between them than allowed by more piecemeal analyses.
-Further, because the model estimates expected values and the magnitude of inter-annual variability in a time series framework, the output will be useful for structuring simulation models of future population dynamics.
-These simulation exercises will ultimately allow decision-makers to posit plausible future states of nature (e.g., climate change) or management strategies (e.g., habitat restoration or harvest policies) and to receive a distribution of possible future outcomes weighted by their probability of occurrence as suggested by historical population dynamics.
-The outputs of those analyses will be useful in decision frameworks that seek to prioritize certain actions over others, while helping to set reasonable expectations for what might likely occur in the face of future challenges.
+Further, because the model estimates expected values and the magnitude of inter-annual variability in a time series framework, the output will be useful for structuring simulation models of future population dynamics to evaluate different management strategies.
 Although this is the ultimate goal and purpose of developing the state-space life cycle model described herein, we do not discuss this concept further, as it is beyond the scope of the statistical population dynamics model, which is the topic of this document.
 
-The state-space life cycle model tracks the fates of $n_y$ cohorts of fish from egg to adulthood within a statistical population dynamics model.
-The model is fundamentally statistical because it receives input data in the form of empirical observations (or externally derived estimates informed by empirical observations, with uncertainty in the external estimation propagated to this model) and estimates unknown parameters that must be internally consistent with the data and one another.
-The model is considered "state-space" because it captures two discrete types of variability: (_i_) process noise, i.e., variability in the biological and environmental processes that give rise to latent (i.e., true but unobserved) population dynamics and outcomes and (_ii_) observation error, i.e., variability in the measurement processes that result in the observed data representing an imperfect (but generally unbiased) perception of the true states and transitions among them.
-As such, the model is inherently a time series model: spawners in one year produce eggs, which then become parr, then smolt, ocean juveniles, and ultimately spawners in future years -- along this life cycle, it is the same pool of fish at one life stage that is decremented (via survival rate transition probabilities) to become a pool of fish at a later stage of the life cycle.
+The state-space life cycle model tracks the fates of multiple cohorts of fish from egg to adulthood within a statistical population dynamics model.
+The model receives input data in the form of empirical observations or pre-processed output from other models (e.g., to derive survival rates from PIT tag records) and estimates unknown parameters that must be internally consistent with the data and one another.
+The model is considered "state-space" because it captures two discrete types of variability: (_i_) process noise, i.e., variability in the biological and environmental processes that produce population dynamics and outcomes and (_ii_) observation error, i.e., variability in the measurement processes that result in the observed data representing an imperfect perception of the true value being measured.
+As such, the model is inherently a time series model: spawners in one year produce eggs, which move through several life stages and ultimately return as spawners in future years -- it is the same pool of fish at one life stage that is decremented (via survival rate transition probabilities) to become a pool of fish used in the calculations for a later stage of the life cycle.
+We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \@ref(fig:diagram)): freshwater juvenile, ocean juvenile, and freshwater adult.
 
-Furthermore, the model has several dimensions and the majority of processes are assumed to operate differently (i.e., have varying numerical values) along each dimension.
-One dimension is age structure: anadromous Chinook salmon in the Grande Ronde basin return predominately as age-3, age-4, or age-5 adults, these outcomes are mutually exclusive but can occur for any fish from a given cohort.
-This important feature of Chinook salmon life history means monitoring activities in one year of adult returns sample fish that are progeny from from 3 consecutive brood (i.e., i.e., spawning) years; due to the resulting time linkages in the data this creates, it is essential that our model account for it.
-Another dimension is origin structure: adults returning in any given year may be the result of either natural spawning/rearing in the wild or via captive spawning/rearing in a hatchery setting.
-Critical outputs of the model are productivity (i.e., fish produced per fish) and capacity (i.e., declining productivity with increasing density) which makes it crucial that we track the fates of naturally and hatchery produced fish separately.
-Among naturally produced juveniles, an additional dimension is migratory strategy structure: some individuals rear over their first winter as free-swimming juveniles in the headwaters near where they were spawned, while others migrate to areas lower in the basin to rear overwinter; regardless, all individuals migrate out to sea the following spring as age-2 smolt.
-This phenological life history complexity is important to capture because these two groups of fish are monitored separately and they may have different survival outcomes while inhabiting heterogeneous habitats.
-A final dimension is population structure: there are several tributaries within the Grande Ronde basin that support spawning Chinook salmon, and local environmental conditions and genetic adaptations may result in their population dynamics differing in terms of productivity, capacity, or overall life cycle fitness.
-Four tributaries, which we consider to be distinct spawning populations, have been monitored using largely consistent methods for nearly three decades; these include Catherine Creek, Lostine River, Minam River, and Upper Grande Ronde River.
-Although we model their population dynamics separately, it is also reasonable to expect that these populations should show some level of synchronicity in the conditions they face and the resulting production and survival outcomes.
-Thus, wherever possible we attempt to capture the covariability among population-specific dynamics.
+The model has several dimensions and the majority of processes are assumed to operate differently (i.e., have varying numerical values) along each dimension. These include:
 
-The model is framed in the Bayesian mode of inference, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
-Further, Bayesian inference provides an intuitive framework to constrain population dynamics parameters to take on only biologically plausible values through the use of prior information -- we intentionally employ nearly exclusively uninformative prior information, but in several rare cases we were required to bring in auxiliary information in the form of reasonably strong priors (Table \@ref(tab:param-table)).
-A final benefit of using the Bayesian framework is the seamless propagation of uncertainty from directly estimated parameters to derived quantities (of which there are many) -- all unknown quantities, either estimated parameters or deterministic functions of estimated parameters, receive a posterior distribution in the Bayesian framework.
-Due to the analytical intractability of the complexity of the model, we employ Markov Chain Monte Carlo methods (implemented via the JAGS probabilistic programming language) to sample from the joint posterior distribution of all unknown quantities in the model.
+* **Age of Return** -- Anadromous Chinook salmon in the Grande Ronde basin return predominately as age-3, age-4, or age-5 adults.
+This means that monitoring activities in one year of adult returns sample fish that are progeny from from 3 consecutive brood (i.e., i.e., spawning) years, creating time linkages in the time series that are important to account for.
+* **Origin** -- Adults returning in any given year may be the result of either natural spawning/rearing in the wild or via captive spawning/rearing in a hatchery setting.
+These are critical to track separately because the productivity and capacity of naturally spawning salmon are key outputs of the model.
+* **Juvenile Migratory Strategy** -- Grande Ronde spring Chinook salmon juveniles exhibit two main phenological migratory strategies which may have different vital rates and require additional complexity in the observation model.
+* **Population** -- Four tributaries of the Grande Ronde River have been monitored using largely consistent methods for nearly three decades; these include Catherine Creek, Lostine River, Minam River, and Upper Grande Ronde River.
+We track the abundance and survival of each separately because they are monitored separately and local environmental conditions and/or genetic adaptations may result in population dynamics differing in terms of productivity, capacity, or overall life cycle fitness.
 
-We begin our description of the mathematical structure of the life cycle model with an overview of several syntax and statistical conventions we employ.
-In our mathematical representation of quantities in the model, we have striven for consistency, but this has created somewhat non-intuitive conventions which require devoted explanation.
-All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \@ref(tab:index-table), \@ref(tab:symbol-table), \@ref(tab:param-table), and \@ref(tab:data-table) for reference and a catalog of all equations is provided in Table \@ref(tab:equation-table).
-
-We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \@ref(fig:diagram)): freshwater juvenile, ocean juvenile, and freshwater adult.
-For each life phase, we describe the process model dynamics as a set of stochastic and deterministic processes followed by how they are informed by empirical data as part of the observation model.
-Although we present these phases and model components in discrete sections, note that they are all components of a single integrated population dynamics model that is statistical in the sense that unknown quantities are estimated with uncertainty from input data.
+We used the Bayesian mode of inference to fit the model to data, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
+Further, Bayesian inference provides an intuitive framework to constrain parameters to take on only values known _a priori_ to be plausible -- we intentionally employ nearly exclusively uninformative prior information, but in several cases we were required to use auxiliary information in the form of reasonably strong priors (Table \@ref(tab:param-table)).
+An additional benefit of using the Bayesian framework is the seamless propagation of uncertainty from estimated parameters to derived quantities (of which there are many) -- all unknown quantities receive a posterior distribution.
+We employed Markov Chain Monte Carlo methods (implemented via the JAGS probabilistic programming language) to sample from the joint posterior distribution of all unknown quantities in the model.
 
@@
 
-* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn -- this includes age-3 fish which are generally referred to as "jacks".
+We have striven for consistency in our mathematical representation of quantities in the model but this has created somewhat non-intuitive conventions which require devoted explanation.
+All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \@ref(tab:index-table), \@ref(tab:symbol-table), \@ref(tab:param-table), and \@ref(tab:data-table) for reference and a catalog of all equations is provided in Table \@ref(tab:equation-table).
+
+* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn including age-3 "jacks".
 * Life stage-specific states are defined by capital letters, e.g., parr ($P$), smolt ($M$), or spawners ($S$)
 * Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are denoted by Greek symbols, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
-* Subscripts denote the structure of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population.
+* Subscripts denote the index of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population (see Table \@ref(tab:index-table)).
 * We use the convention $b$ to indicate "before event" and $a$ to indicate "after event" for a quantity that occurs at the same life stage.
@@
 * Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \rightarrow B}_{y,j}$.
-* Most terms vary annually to capture process noise in population dynamics.
-We denote the deterministic (i.e., expected) value in the absence of process noise with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$.
-We use the term "deterministic" in the sense that it is the expected value for a stochastic (i.e., with process noise) quantity; the deterministic quantity still has a posterior probability density function.
+* We denote the expected value of a stochastic process with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$ -- this is the value expected in the absence of process variability.
 * In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array).
 Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax.
-E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for a given population.
+E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for each population.
 * Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.

### 2022-06-28 100-math-description/GR-sslcm-math-description.Rmd
Edit FW juvenile phase text for clarity and consistency

@@
 ```
+
+\listoftodos
 
@@
 
-### Egg Production, Parr Recruitment, and Parr Mean Size
+### Egg Production, Parr Recruitment, and Parr Mean Length
 
-Total egg production is the sum product of age-specific spawner abundance (from eq. \@ref(eq:get-Sa), below), proportion female, and fecundity:
+We begin our description of the life cycle at the egg stage immediately after spawning.
+We assumed total egg production was the sum product of age-specific spawner abundance (from eq. \@ref(eq:get-Sa), below), proportion female, and fecundity:
 
@@
 
-The proportion of spawners at age that are female ($\Omega_{k,j}$) was calculated from carcass survey data and averaged across years and fecundity ($f_k$) was calculated from samples taken from Grande Ronde-origin hatchery broodstock.
-Both quantities were supplied to the model assuming no error or inter-annual variability.
+We calculated the proportion of spawners at age that are female ($\Omega_{k,j}$) from carcass survey data and averaged across years and fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
+We supplied both quantities to the model assuming no error or inter-annual variability.
 
-Deterministic egg-to-parr survival is density-dependent and follows a Beverton-Holt relationship with productivity parameter $\alpha_j$ and capacity parameter $\beta_j$:
+We assumed expected egg-to-parr survival was density-dependent following a Beverton-Holt relationship with productivity parameter $\alpha_j$ and capacity parameter $\beta_j$:
 
@@
 
-To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\mathrm{WUL}_j$).
-Derivation of $\mathrm{WUL}_j$ is too detailed to describe fully here, but briefly, the "value" of stream segments with different habitat characteristics were quantified by a complex generalized linear mixed model that treated detectability-adjusted snorkel counts as the response variable and habitat features (e.g., pool frequency, water temperature, large wood density, etc.) as predictor variables and weights were assigned to stream segments based on their relative value to the segment with the highest value; $\mathrm{WUL}_j$ was then the sum of segment-specific weight and length within the known spawning and rearing extent for each population.
-We modeled capacity ($\beta_j$) as a function of this $\mathrm{WUL}_j$ metric:
+To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\mathrm{WUL}_j$)^[Derivation of $\mathrm{WUL}_j$ is too detailed to describe fully here.
+Briefly, the relative ability of stream segments with different habitat characteristics to hold rearing parr was expressed in terms of the density of fish predicted to reside there by a complex generalized linear mixed model.
+The model was fitted to density estimates based on detectability-adjusted [@staton-etal-2022] summer snorkel counts with local habitat characteristics (e.g., pool frequency, water temperature, large wood density, etc.) as predictor variables.
+The weight of each stream segment was assigned based on the predicted density relative value to the segment with the highest value; $\mathrm{WUL}_j$ was then equal to the sum of segment-specific weight and length within the known spawning and rearing extent for each population.].
+We modeled parr recruitment capacity ($\beta_j$) as a function of this $\mathrm{WUL}_j$ metric:
 
@@
 
-Realized (i.e., with process noise) egg-to-parr survival was a multivariate logit-normal random variable around the deterministic value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) predicted by the Beverton-Holt function in eq.
+We modeled realized (i.e., with process noise) egg-to-parr survival as a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) from eq.
 \@ref(eq:get-phi-E-Pb-dot) with covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
@@
 In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
-It is well known that juvenile survival is related to body size \todo{Insert References} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
-We modeled expected mean parr length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:
+It is well known that juvenile survival is related to body size \todo{Insert references about survival being related to size} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
+We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:
 
@@
 
-and the realized mean parr length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$ (constructed of $\sigma_{L_{j}^{P^{b}}}$ and $\rho_{L^{P^{b}}}$ following eq.
+and the realized parr mean length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$ (constructed of $\sigma_{L_{j}^{P^{b}}}$ and $\rho_{L^{P^{b}}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 
-Not all summer parr ($P^{b}_{y,j}$) stay in the headwaters to rear overwinter -- some migrate out in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \mathrm{fall}$) and others migrate out the following spring (termed "spring migrants" and indexed by $i = \mathrm{spring}$).
-Due to this difference in migratory phenology, these two groups of fish are monitored separately.
-To enable building an observation model that could accommodate this feature of the populations in our model, summer parr was apportioned to these two strategies:
+Like many populations of stream-type spring Chinook salmon in the Columbia River basin \todo{Insert references about other CRB populations displaying the fall/spring migratory strategy}, there is life history diversity among the juveniles with respect to their migratory phenology and habitat types occupied for rearing overwinter.
+Some portion of the summer parr ($P^{b}_{y,j}$)  migrate out of the headwaters near where they were spawned in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \mathrm{fall}$) and the remaining portion migrate out the following spring (termed "spring migrants" and indexed by $i = \mathrm{spring}$).
+Due to this difference in migratory phenology, these two groups of fish are monitored separately \todo{Insert a reference to a recent ODFW screw trap monitoring report where it is stated (or implied) that migratory strategies are monitored separately.} depending on when they pass the rotary screw trap located in each tributary\todo{Create a map and include reference it here}.
+To enable building an observation model that could accommodate this feature of the populations in our model, we apportioned summer parr to each of these two strategies:
 
@@
 where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
-For fall migrants, this proportion was a multivariate logit-normal random variable around a time-constant mean ($\dot{\pi}_{i = \mathrm{fall},j}$) with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$ (constructed of $\sigma_{\pi_{i=\mathrm{fall},j}}$ and $\rho_{\pi_{i=\mathrm{fall}}}$ following eq.
+We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \mathrm{fall},j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$ (constructed of $\sigma_{\pi_{i=\mathrm{fall},j}}$ and $\rho_{\pi_{i=\mathrm{fall}}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 
-and the proportion that are spring migrants was obtained as its complement ($\pi_{y,i = \mathrm{spring},j} = 1 - \pi_{y,i = \mathrm{fall},j}$).
+Since there are only two migratory strategies, we obtained the proportion that are spring migrants as the complement ($\pi_{y,i = \mathrm{spring},j} = 1 - \pi_{y,i = \mathrm{fall},j}$).
 
-### Survival to Smolt Stage and Mean Smolt Size
+### Survival to Smolt Stage and Smolt Mean Length
 
-Overwinter survival from the end of the parr year (i.e., age-1) to the start of the smolt year (i.e., age-2), denoted by $\phi^{P^{a} \rightarrow M^{b}}_{y,i,j}$, was modeled as a logit-linear function of mean parr size.
-Deterministic overwinter survival was:
+We modeled expected survival from the parr (age-1) to in-basin smolt (age-2) stage (termed "overwinter" survival and denoted by $\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}$) as a logit-linear function of parr mean length:
 
@@
 
-Where $L^{*P^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed mean parr length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation.
-Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq.
+where $L^{*P^{b}}_{y,j}$ is parr mean length scaled and centered by subtracting the historical average observed parr mean length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation.
+Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 
-Natural-origin (indexed by $o=\mathrm{NOR}$) parr surviving to the beginning of the following year was then:
+Since hatchery-origin smolts are released into the population in spring (see Section \@ref(hatchery-inputs)), we introduce the origin index ($o$) starting at the in-basin smolt stage prior to out-migration ($M^{b}_{y,i,o,j}$).
+The abundance of natural-origin (indexed by $o=\mathrm{NOR}$) smolt was then:
 
@@
 We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
-Because only spring migrants are measured for mean smolt length in the spring (as they pass the screw trap), we must assume equal lengths for fall migrant smolt and thus omit the $i$ subscript from these quantities related to mean smolt length.
-Preliminary analyses on the observed mean length data revealed that mean smolt length was positively related with parr length, but that the relationship was non-linear.
-We thus modeled the expected multiplicative change in mean size between the parr and smolt stage as a log-linear function of (standardized) parr mean size:
+Because only spring migrants are measured for smolt mean length in the spring (as they pass the screw trap), we were forced to assume equal lengths for fall migrant smolt and we thus omit the $i$ subscript from these quantities related to smolt mean length.
+Preliminary analyses on the observed mean length data revealed that smolt mean length was positively related with parr mean length, but that the relationship was non-linear.
+To capture this non-linearity, we modeled the expected multiplicative change in mean length between the parr and smolt stage as a log-linear function of (standardized) parr mean length:
 
@@
 
-Mean smolt length was then the product:
+Smolt mean length was then the product:
 
@@
 
-For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error) were stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
-The abundance of hatchery-origin fish for all subsequent life stages was tracked separately from natural-origin fish.
+For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error \todo{Insert reference to a document that gives info about these smolt releases}) were stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
+For all subsequent life stages, we tracked the abundance (and often survival) of hatchery-origin fish separately from natural-origin fish.
 
@@
 
-In-basin smolt ($M^{b}_{y,i,o,j}$) migrate to the ocean in the spring of the year they become age-2.
-We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams encountered in the downstream migration, and (_ii_) from LGR to the ocean.
-For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin.
+All in-basin smolt ($M^{b}_{y,i,o,j}$) migrate to the ocean in the spring of the year they become age-2 regardless of their migratory strategy ($i$).
+We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams\todo{Insert reference to a document describing dams} encountered in the downstream migration, and (_ii_) from LGR to the ocean.
+For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
 
-We modeled deterministic out-of-basin migration for natural-origin smolt as a logit-linear function of smolt size:
+We modeled expected out-of-basin migration survival for natural-origin smolt as a logit-linear function of smolt mean length:
 
@@
 
-Where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed mean smolt length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
-Realized out-of-basin migration survival was a multivariate logit-normal random variable around the deterministic logistic model prediction with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}}$ (each matrix constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}}$ following eq.
+where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed smolt mean length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
+For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \rightarrow M^{a}}_{y,o=\mathrm{HOR},j}$ were equal within a population).
+For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}$ (each matrix constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{o,j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}_o}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
+\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
 (\#eq:phi-Mb-Ma-random)
@@
 
-Thus, the abundance of smolt reaching LGR was:
+and the abundance of smolt reaching LGR after surviving the migration out-of-basin was:
 
@@
 
-After reaching LGR, we modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
-We assumed these survival rates were multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$ (constructed of $\sigma_{\phi^{M^{a} \rightarrow O^{0}}_{o}}$ and $\rho_{\phi^{M^{a} \rightarrow O^{0}}}$ following eq.
+We modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
+We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$ (constructed of $\sigma_{\phi^{M^{a} \rightarrow O^{0}}_{o}}$ and $\rho_{\phi^{M^{a} \rightarrow O^{0}}}$ following eq.
 \@ref(eq:generic-Sigma2by2)):
@@
 
-Thus, the abundance of fish reaching the ocean by origin was:
+and the abundance of fish reaching the ocean by origin and population was:
 
@@
 
-The observation model components for the freshwater juvenile life stage were fitted to two primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary) in either the fall or spring and (_ii_) survival of juveniles from several PIT tagging events to LGR.
-For both types, the information supplied to the model were externally compiled estimates (e.g., survival from Cormack-Jolly-Seber models) and the estimated standard error was supplied to the model as a measure of observation error variability.
+The observation model components for the freshwater juvenile life stage were fitted to three primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary, \todo{Include reference to document describing methods of juvenile passage estimation}) in either the fall or spring, (_ii_) survival of juveniles from several PIT tagging events to LGR \todo{Include reference to document describing methods of juvenile survival estimation based on PIT tags}, and (iii) the mean length of sampled individuals during two of the PIT tagging events \todo{Include reference to document describing methods of juvenile mean length estimation}.
+For all types, the information supplied to the model were externally compiled estimates (e.g., survival from Cormack-Jolly-Seber models) and the estimated standard error was supplied to the model as a measure of observation error variability.
+A more fully integrated model would involve constructing the likelihood based on the frequency of PIT tag detection histories, however we thought unnecessary given the pre-compiled nature of currently available estimates and their uncertainty  \todo{Consider citing Staton et al.
+(2017) integrated vs.
+sequential SSSRA paper here}.
 
@@
 
-Fish with the fall migratory strategy pass the screw trap in the fall and fish with the spring migratory strategy pass the screw trap the following spring.
+Fish with the fall migratory strategy pass the screw trap in the fall as parr and fish with the spring migratory strategy pass the screw trap the following spring as smolt.
 The estimated passage during these time periods were used in log-normal likelihoods by assuming:
@@
 
-Much quantitative research has been devoted to studying the survival of Chinook salmon smolts migrating through the hydrosystem located on the Snake and Columbia rivers.
-As a result, we thought it best to utilize the findings from some of this research as input data to our modeling effort rather than attempt to have our model freely estimate survival along this migration -- doing so would give us the flexibility to more freely estimate quantities which have received less directed research, namely ocean survival.
-We used the output from the most recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
+Much quantitative research has been devoted to studying the survival of Chinook salmon smolt migrating through the hydrosystem located on the Snake and Columbia rivers and we thought it best to utilize the findings from some of this research as input data to our modeling effort rather than attempt to have our model freely estimate survival along this migration.
+Using external estimates of survival here so would give us the flexibility to more freely estimate quantities which have received less directed research, namely ocean survival.
+We used the output from a recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
 Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{NOR}}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{HOR}}$ here).
@@
 
+\clearpage
+
+\missingfigure{Create a map figure to go here.}
+
+\clearpage
+
 # Tables {-}
+
+\todo{Shorten the footnotes on the table describing the index notation -- they are excessively long.}
 
@@
 tab$Eqs. = unname(sapply(tab$Eqs., handle_eqs))
+colnames(tab)[4] = "Eq(s)."
 
@@
 colnames(tab)[3] = "Prior\\textsuperscript{1,2,3,4,5}"
+colnames(tab)[4] = "Eq."
 
@@
 tab$Type = type_key[as.character(tab$Type)]
+
+colnames(tab)[4] = "Eq."
 

### 2022-06-29 100-math-description/GR-sslcm-math-description.Rmd
Move list of todos to the end of document
Edit ocean juvenile text for clarity and consistency

@@
 ```
-
-\listoftodos
 
@@
 
-Spring Chinook salmon in the Grande Ronde basin migrate to sea as age-2 smolts and can return as either age-3, age-4, or age-5 adults.
-That is, ocean juveniles spend between 1 and 3 winters at sea and some fraction will mature and make the return migration after each winter and before the following winter at sea (which we term the "maturation rate").
-Thus, we divided ocean population dynamics into two types of demographic rates: survival and maturation rates.
-We treated survival in the first year with the most complexity and we vastly simplified survival in the second and third years for parameter identifiability purposes.
-Further, we wished to account for differences in ocean survival among natural- and hatchery-origin fish, but were limited in the level of complexity that was estimable; thus we assumed natural- and hatchery-origin survival at sea was perfectly correlated over time, but shifted by a log-odds ratio.
+Spring Chinook salmon in the Grande Ronde basin migrate to sea as age-2 smolt and can return as either age-3, age-4, or age-5 adults.
+That is, ocean juveniles spend between 1 and 3 winters at sea and some fraction will make the return migration after each winter and before the following winter at sea.
+Thus, we divided ocean population dynamics into two types of demographic rates and their process noise: survival and maturation.
+Due to the confounding of these parameters\todo{Insert a reference to a paper that describes this ocean survival/maturation rate confounding?}, we were unable to freely estimate all rates and were instead required to make some simplifying assumptions and use more informative priors than in other parts of the model.
 
-First year natural-origin ocean survival was assumed to be a multivariate logit-normal random variable around a time-constant and density-independent deterministic value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$ (constructed of $\sigma_{\phi^{O^{0} \rightarrow O^{1}}_{j}}$ and $\rho_{\phi^{O^{0} \rightarrow O^{1}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion (all $o=\mathrm{NOR}$ in eq.
-\@ref(eq:phi-O0-O1-random), omitted for brevity):
+### Survival Rates {#ocean-survival}
+
+We assumed first year natural-origin^[All $o=\mathrm{NOR}$ in eq.
+\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$ (constructed of $\sigma_{\phi^{O^{0} \rightarrow O^{1}}_{j}}$ and $\rho_{\phi^{O^{0} \rightarrow O^{1}}}$ following eq.
+\@ref(eq:generic-Sigma4by4)), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
+paper on PDO}:
 
@@
 
-We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same deterministic value each year (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
-We further discovered that not all maturity and ocean survival terms were uniquely identifiable based solely on adult return abundance and age composition -- we thus relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
+We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
+Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
+\todo{Are we using priors or fixed values? Include reference to reports where we can reference the specific values used.}
 To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
@@
 
-Maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) were assumed to vary by ocean age, origin, brood year, and population and were treated as multivariate logit-normal random variables around time-constant and density-independent deterministic values ($\dot{\psi}^{O^{w}}_{o,j}$, $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}_o}$ (one matrix per origin, each constructed of $\sigma_{\psi^{O^{w}}_{o,j}}$ and $\rho_{\psi^{O^{w}}_{o}}$ following eq.
+This $\delta_j$ parameter allows hatchery- and natural-origin to have different survival for each ocean year, but assumes the origin effect is equal for all brood years and ocean ages within a population, implying an assumption that ocean survival among origins is perfectly correlated.
+
+### Maturation Rates {#maturity}
+
+We treated realized maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) as multivariate logit-normal random variables around time-constant expected values ($\dot{\psi}^{O^{w}}_{o,j}$; $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}_o}$ (one matrix per origin, each constructed of $\sigma_{\psi^{O^{w}}_{o,j}}$ and $\rho_{\psi^{O^{w}}_{o}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 
-Now that we have defined the sources of process noise in the ocean demographic rates, we can define the process equations that result in transitioning ocean juveniles through the various ocean ages.
+### Return to Columbia River {#return-to-columbia-river}
+
+Now that we have defined the sources of process noise in the ocean demographic rates, we can define the process equations that result in transitioning ocean juveniles through the various ocean ages and ultimately at the mouth of the Columbia River for the upstream migration.
 We modeled ocean population dynamics as a sequence of survival, maturation of surviving fish, and survival of non-maturing fish:
@@
 
-That is, fish reaching the ocean as age-2 juveniles ($O^{0}_{y,o,j}$) must survive one winter to become age-3 ocean juveniles ($O^{1}_{y,o,j}$); if they do not mature at age-3 ($1 - \psi^{O^{1}}_{y,o,j}$), then they must survive another winter to become age-4 ocean juveniles ($O^{2}_{y,o,j}$), and if they do not mature at that point ($1 - \psi^{O^{2}}_{y,o,j}$), they must survive a third winter to become age-5 ocean juveniles ($O^{3}_{y,o,j}$).
+That is, fish reaching the ocean as age-2 juveniles ($O^{0}_{y,o,j}$) must survive one winter to become age-3 ocean juveniles ($O^{1}_{y,o,j}$); if they do not mature at age-3 (with probability $1 - \psi^{O^{1}}_{y,o,j}$), then they must survive another winter to become age-4 ocean juveniles ($O^{2}_{y,o,j}$), and if they do not mature at that point (with probability $1 - \psi^{O^{2}}_{y,o,j}$), they must survive a third winter to become age-5 ocean juveniles ($O^{3}_{y,o,j}$).
 
-Now, we must place the maturing portion of each of $O^{1}_{y,o,j}$, $O^{2}_{y,o,j}$, and $O^{3}_{y,o,j}$ into the correct year and age of return to the mouth of the Columbia River ($R^{b}_{y,k,o,j}$).
-Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age at maturity in year $y + k_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $k_{\mathrm{min}}$ = 3).
-As an example, fish spawned in brood year $y$ = 2000 will return in 2003 as age-3 ($k$ = 1), in 2004 as age-4 ($k$ = 2), or in 2005 as age-5 ($k$ = 3).
+The abundances of ocean juveniles ($O^{1}_{y,o,j}$, $O^{2}_{y,o,j}$, and $O^{3}_{y,o,j}$) are organized by brood year, however they will return in different years to spawn (and be observed) because they are of different ages.
+We placed returning mature fish into the correct year and age of return to the mouth of the Columbia River before the upstream migration ($R^{b}_{y,k,o,j}$) based on the following rule.
+Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age of maturity in year $y + k_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $k_{\mathrm{min}}$ = 3).
+As an example, fish spawned in brood year $y$ = 2000 will return in 2003 as age-3 ($k$ = 1), in 2004 as age-4 ($k$ = 2), or in 2005 as age-5 ($k$ = 3) -- see Table \@ref(tab:year-table) for a visual of this example.
 Thus, the abundance of fish spawned in brood year $y$ returning as age-3, age-4, and age-5, respectively, was:
@@
 
-Note, however, that this leaves 12 age/year combinations per origin unpopulated (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns).
-This is because the life cycle dynamics must start somewhere, and no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
-Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as free parameters with fairly restrictive priors (Table \@ref(tab:param-table)) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
-Initial abundance of hatchery-origin returns was handled by the "straying model", described below.
+Note, however, that this leaves 12 age/year combinations per origin unpopulated with returning adults (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns; see Table \@ref(tab:year-table)).
+This is because no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
+Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as unknown parameters with fairly restrictive priors (Table \@ref(tab:param-table)) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
+Initial abundance of hatchery-origin returns was handled by the "straying model" (see Section \@ref(processes-between-bon-and-lgr), below).
 
@@
 
+```{r}
+year_tab_caption = "Year of return based on age of return and brood year.
+For example, adults that are progeny of the spawners in returning in 2000 (the brood year) return to spawn in the year 2003 as age-3, 2004 as age-4, and in 2005 as age-5 (shown in blue, example also given in the text in Section \\ref{return-to-columbia-river}).
+The return years with red brood years show the age-specific return abundances that were estimated because no previous states (e.g., parr, smolt) were available for these early brood years (see Section \\ref{return-to-columbia-river} for more details)."
+```
+
+```{r year-table}
+
+return_year = 1991:2019
+age_3 = 1988:2016
+age_4 = 1987:2015
+age_5 = 1986:2014
+
+tab_full = data.frame(return_year, age_3, age_4, age_5)
+tab_NA = data.frame(return_year = NA, age_3 = NA, age_4 = NA, age_5 = NA)
+
+tab_start = tab_full[tab_full$return_year %in% c(1991:1996),]
+tab_end = tab_full[tab_full$return_year %in% c(2019),]
+tab_middle = tab_full[tab_full$return_year %in% c(2003:2005),]
+tab = rbind(tab_start, tab_NA, tab_middle, tab_NA, tab_end)
+
+tab[,-1][tab[,-1] < 1991 & !is.na(tab[,-1])] = kableExtra::cell_spec(tab[,-1][tab[,-1] < 1991 & !is.na(tab[,-1])], format = "latex", color = "red")
+tab[,-1][tab[,-1] == 2000 & !is.na(tab[,-1])] = kableExtra::cell_spec(tab[,-1][tab[,-1] == 2000 & !is.na(tab[,-1])], format = "latex", color = "blue")
+
+tab[is.na(tab)] = "$\\vdots$"
+
+kable(tab, "latex", booktabs = TRUE, align = "cccc", linesep = "", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), escape = FALSE,
+      caption = year_tab_caption, row.names = FALSE) %>%
+  kable_styling(full_width = FALSE) %>%
+  add_header_above(c(" " = 1, "Brood Year of Returning Adults by Age" = 3), bold = TRUE) %>%
+  row_spec(0, bold = TRUE) %>%
+  column_spec(1, bold = TRUE) %>%
+  column_spec(2:4, width = "50px")
+```
+
+\clearpage
+
+\listoftodos
+
+\clearpage
+
 # References {-}

### 2022-06-29 100-math-description/GR-sslcm-math-description.Rmd
Edit FW adult text for clarity and consistency

@@
 
-There are several sources of mortality that occur on the upstream migration between the mouth of the Columbia River and the natal tributaries in the Grande Ronde basin.
-Downstream of Bonneville Dam (BON, the first dam encountered in this upstream migration), returning adults are subject to predation mortality (survival denoted by $\phi^{SL}_{y,j}$) from sea lions and harvest mortality from fisheries (harvest rate after sea lion predation denoted by $U_{y,k,o}$).
-We compiled the best available estimates of these quantities, but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error.
-Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around deterministic values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$ (constructed of $\sigma_{\phi^{R^{b} \rightarrow R^{a}}_o}$ and $\rho_{\phi^{R^{b} \rightarrow R^{a}}}$ following eq.
+We attempted to partition several sources of mortality that occur between the upstream migration from the mouth of the Columbia River to the point of spawning in natal tributaries in Grande Ronde basin.
+For ease of presentation, we separate these processes into three categories depending on where they occur spatiotemporally: (_i_) downstream of Bonneville Dam (BON) at the beginning of the upstream migration, (_ii_) along the upstream migration in the mainstem Columbia and Snake rivers between BON and LGR, and (_iii_) after arrival to the natal tributaries and up until the point of spawning.
+
+### Processes Downstream of BON
+
+Prior to reaching BON, we subject the returning adults to predation mortality from sea lions (survival denoted by $\phi^{SL}_{y,j}$) and harvest mortality from fisheries (harvest rate on fish surviving sea lion predation denoted by $U_{y,k,o}$).\todo{Insert information about where harvest rates and sea lion predation estimates came from.}
+We compiled the best available estimates of these quantities, but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error (used in eq.
+\@ref(eq:get-Ra), below).
+
+### Processes Between BON and LGR
+
+Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$ (constructed of $\sigma_{\phi^{R^{b} \rightarrow R^{a}}_o}$ and $\rho_{\phi^{R^{b} \rightarrow R^{a}}}$ following eq.
 \@ref(eq:generic-Sigma2by2)).
-In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the deterministic expectation in these years for parameter identifiability purposes:
+In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the expected value in these years for parameter identifiability purposes:
 
@@
 
-Examination of the adult data indicated that hatchery-origin adults returned to Grande Ronde populations in years that could not be attributed to hatchery-origin smolt releases to these populations.
-Further, the Minam River population (which has no hatchery supplementation program) has had hatchery adults return in many of the years with adult data.
+Examination of the adult composition data indicated that hatchery-origin adults returned to Grande Ronde populations in years that could not be attributed to hatchery-origin smolt releases to these populations.
+Further, the Minam River population (which has no hatchery supplementation program) has had hatchery adults return in many of the years included in our model.
 Since there were non-zero observations of hatchery-origin adults in cases without a process model component to produce them, we required a process model mechanism to populate non-zero expected values for the observation model to remain valid based on the available data.
-We term this part of the model the "straying model", and apply it only in years/populations in which there is no other way to explain the presence of hatchery-origin adults.
-We denote the total number of strays that enter population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\mathrm{NOR},j} = 0$ and forced all $G_{y,o=\mathrm{HOR},j} = 0$ in years where hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
+We term this model component the "straying model", and applied it only in years/populations in which the presence of non-zero hatchery-origin returning adults could not otherwise be explained due to zero-valued hatchery-origin smolt releases.
+We denote the total number of strays that entered population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\mathrm{NOR},j} = 0$ and forced all $G_{y,o=\mathrm{HOR},j} = 0$ in years where non-zero hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
 We denote the age composition of these strays by $p^{G}_{k,j}$ (where $\sum_k^{n_k} p^{G}_{k,j} = 1$) and apportioned $G_{y,o,j}$ to age-specific values by $G_{y,k,o,j}=G_{y,o,j} \cdot p^{G}_{k,j}$.
@@
 
-Upon arrival in the tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \mathrm{MIN}$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
-These weir removals (denoted by $B_{y,k,o,j}$) were passed to the model as perfectly known values and $B_{y,k,o,j=\mathrm{MIN}} = 0$.
-Thus, the abundance of fish passed upstream of the weir and that would have a chance to spawn each year was (the maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$):
+\todo{Include note that no mortality is assumed between LGR and the natal tributary.}
+
+### Processes in Natal Tributary
+
+Upon arrival to the natal tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \mathrm{MIN}$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
+We supplied these weir removals (denoted by $B_{y,k,o,j}$) to the model as known without error and set all $B_{y,k,o,j=\mathrm{MIN}} = 0$.
+Thus, the abundance of adults that would have a chance to spawn each year was (the maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$):
 
@@
 
-As a final step before spawning, these fish on the spawning grounds must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
-We term this phenomenon "pre-spawn survival", denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, which we assume are multivariate logit-normal random variables around a time-constant and density-independent deterministic value ($\dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$) with covariance matrix $\Sigma_{\phi^{S^{b} \rightarrow S^{a}}}$ (constructed of $\sigma_{\phi^{S^{b} \rightarrow S^{a}}_j}$ and $\rho_{\phi^{S^{b} \rightarrow S^{a}}}$ following eq.
+As a final step prior to spawning, these adults must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
+We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, as multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$) with covariance matrix $\Sigma_{\phi^{S^{b} \rightarrow S^{a}}}$ (constructed of $\sigma_{\phi^{S^{b} \rightarrow S^{a}}_j}$ and $\rho_{\phi^{S^{b} \rightarrow S^{a}}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 
-Thus, the abundance of total successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
+Thus, the abundance of successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
 
@@
 
-Total return abundance is estimated annually external to the model using a combination of weir counts, mark-recapture methods, and spawning ground surveys.
+Total return abundance is estimated annually external to the model using a combination of weir counts, mark-recapture methods, and spawning ground surveys\todo{Insert reference about adult return monitoring methods}.
 For each population and year, these have been compiled into a point estimate ($\hat{R}^{a}_{y,j}$; note the lack of $o$ or $k$ indices -- this indicates the estimate is aggregated across these dimensions) and an estimate of observation uncertainty ($\hat{\sigma}_{R^{a}_{y,j}}$, expressed as a log-normal standard error).
@@
 
-For the observation model component informing migration survival upstream through the hydropower system, we relied on counts of PIT tag detections of known Grande Ronde-origin fish passing BON ($\hat{x}^{\mathrm{BON}}_{y,o}$) and LGR ($\hat{x}^{\mathrm{LGR}}_{y,o}$).
+For the observation model component informing migration survival upstream from BON to LGR, we relied on counts of PIT tag detections of known Grande Ronde-origin fish passing BON ($\hat{x}^{\mathrm{BON}}_{y,o}$) and LGR ($\hat{x}^{\mathrm{LGR}}_{y,o}$)\todo{Insert reference to DART website where we obtained the BON to LGR PIT tag count data}.
 We assumed the latter was a binomial random variable to build the likelihood component for this data set:
@@
 The other survival data set informing the freshwater adult observation model was for spawning success, i.e., pre-spawn survival.
-In annual spawning ground carcass surveys, surveyors record the counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$).
-Females are counted this way because it is too difficult to tell if a male has successfully spawned based on their gonads alone, thus we assumed that males and females experience the same pre-spawn survival.
+In annual spawning ground carcass surveys, surveyors record the counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$; \todo{Insert reference about carcass/spawning success data monitoring methods}).
+Only females are counted this way because it is too difficult to tell if a male has successfully spawned based on their gonads alone, thus we assumed that males and females experience the same pre-spawn survival.
 We assumed these counts were gathered using binomial sampling to build the likelihood:
@@
 These took the form of two sources: (_i_) those collected at the weirs located within three of the four populations we model ($\hat{x}^{R^{a}}_{y,ko,j}$) and (_ii_) those collected during carcass surveys ($\hat{x}^{S^{a^{\prime}}}_{y,ko,j}$), given the Minam River population does not have a weir.
-We assumed the weir sampled fish representatively with respect to age and origin composition, however we discovered there was an age sampling bias for carcass surveys relative to the weir.
+We assumed the weir sampled fish representatively with respect to age and origin composition, however we discovered there was an age sampling bias for carcass surveys relative to the weir which required a correction factor (see eqs.
+\@ref(eq:z-random) -- \@ref(eq:get-pSa-prime), below).
 We fitted to these data assuming multinomial sampling in which there were $n_{ko} = 6$ possible outcomes: $n_k = 3$ ages of return by $n_o = 2$ origins.

### 2022-08-31 03-post-process/compare-sim-to-obs.Rmd
Fix typos in compare-sim-to-obs Rmd
See #151

@@
   x$Class = factor(x$Class, levels = c("Abundance", "Production Rates", "SAR", "Adult Composition"))
-  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
+  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Eggs per Spawner", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
   x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
@@
   colnames(x)[which(colnames(x) == "LH_type")] = "Mig. Type"
-  colnames(x)[which(colnames(x) == "Origin")] = "Origin"
+  colnames(x)[which(colnames(x) == "origin")] = "Origin"
 
@@
 
+#### Eggs per Spawner
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("E_per_Sa[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Eggs per Spawner: Estimates")
+ratio_plots(x, "Eggs per Spawner: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Eggs per Spawner"))
+```
+
 #### Parr per Spawner
@@
 ```{r}
-pop_ts_plots("phi_O0_O1[year,origin,pop]", origin = 1)
+pop_ts_plots("phi_O0_O1[year,origin,pop]", origin = 2)
 ```
@@
 ```{r}
-pop_ts_plots("^psi_O1[year,origin,pop]", origin = 1)
+pop_ts_plots("^psi_O1[year,origin,pop]", origin = 2)
 ```
@@
 ```{r}
-pop_ts_plots("^psi_O2[year,origin,pop]", origin = 1)
+pop_ts_plots("^psi_O2[year,origin,pop]", origin = 2)
 ```
@@
 
+#### Eggs per Spawner
+
+```{r}
+pop_ts_plots("E_per_Sa[year,pop]")
+```
+
 #### Parr per Spawner

### 2022-09-16 03-post-process/compare-sim-to-obs.Rmd
Add quantities to sim vs. obs comparison
Previously, these quantities were only shown in aggregate within a population; the finer resolution has already helped to pinpoint where some issues may be.

* Adult return to estuary by origin
* Adult return to tributary by origin
* Spawners by origin
* Total egg production by origin
* Eggs per spawner by origin
* Proportion hatchery return by age
* Age composition by origin

--- 2022-04-25 03-post-process/compare-sim-to-obs.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4)
+knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, warning = FALSE)
 knitr::opts_knit$set(root.dir = "../")
@@
 jags_data = model_info$jags_data
+
+o_nor = 1   # o = 1 is NOR
+o_hor = 2   # o = 2 is HOR
+k_3 = 1     # k = 1 is age-3
+k_4 = 2     # k = 2 is age-4
+k_5 = 3     # k = 3 is age-5
+j_cat = 1   # j = 1 is CAT
+j_los = 2   # j = 2 is LOS
+j_min = 3   # j = 3 is MIN
+j_ugr = 4   # j = 4 is UGR
 ```
@@
 
-```{r add-Rb-tot}
+```{r add-p-hos-age}
 # extract spawners returning to tributary
+Ra = post_subset(post, "^Ra[", matrix = TRUE)
+
+# for each posterior sample, calculate the fraction that are hatchery origin
+out_3 = out_4 = out_5 = NULL
+for (i in 1:nrow(Ra)) {
+  Ra_i = array_format(Ra[i,])
+
+  p_hor_3 = Ra_i[,k_3,o_hor,]/(Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,])
+  p_hor_4 = Ra_i[,k_4,o_hor,]/(Ra_i[,k_4,o_nor,] + Ra_i[,k_4,o_hor,])
+  p_hor_5 = Ra_i[,k_5,o_hor,]/(Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,])
+
+  out_3 = rbind(out_3, as.numeric(p_hor_3))
+  out_4 = rbind(out_4, as.numeric(p_hor_4))
+  out_5 = rbind(out_5, as.numeric(p_hor_5))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(p_hor_3), ncol(p_hor_3))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(p_hor_3), each = nrow(p_hor_3))
+
+# make element names
+colnames(out_3) = paste0("p_hor_a[", r_ind, ",1,", c_ind, "]")
+colnames(out_4) = paste0("p_hor_a[", r_ind, ",2,", c_ind, "]")
+colnames(out_5) = paste0("p_hor_a[", r_ind, ",3,", c_ind, "]")
+out = cbind(out_3, out_4, out_5)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-Rb-tot-origin}
+# extract returns to estuary
 Rb = post_subset(post, "^Rb[", matrix = TRUE)
 
-# for each posterior sample, calculate the fraction that are hatchery origin
-out = NULL
+# for each posterior sample, calculate the abundance by origin and total
+out_tot = out_nor = out_hor = NULL
 for (i in 1:nrow(Rb)) {
@@
   hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
-  out = rbind(out, as.numeric(nor + hor))
+  tot = nor + hor
+
+  out_nor = rbind(out_nor, as.numeric(nor))
+  out_hor = rbind(out_hor, as.numeric(hor))
+  out_tot = rbind(out_tot, as.numeric(tot))
 }
@@
 # make element names
-colnames(out) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")
+colnames(out_nor) = paste0("Rb_tot_org[", r_ind, ",1,", c_ind, "]")
+colnames(out_hor) = paste0("Rb_tot_org[", r_ind, ",2,", c_ind, "]")
+colnames(out_tot) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")
+out = cbind(out_nor, out_hor, out_tot)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-Ra-tot-origin}
+# extract returns to tributary
+Ra = post_subset(post, "^Ra[", matrix = TRUE)
+
+# for each posterior sample, calculate the abundance by origin and total
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ra)) {
+  Ra_i = array_format(Ra[i,])
+  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
+  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
+
+  out_nor = rbind(out_nor, as.numeric(nor))
+  out_hor = rbind(out_hor, as.numeric(hor))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(nor), ncol(nor))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(nor), each = nrow(nor))
+
+# make element names
+colnames(out_nor) = paste0("Ra_tot_org[", r_ind, ",1,", c_ind, "]")
+colnames(out_hor) = paste0("Ra_tot_org[", r_ind, ",2,", c_ind, "]")
+out = cbind(out_nor, out_hor)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-Sa-tot-origin}
+# extract spawners
+Sa = post_subset(post, "^Sa[", matrix = TRUE)
+
+# for each posterior sample, calculate the abundance by origin and total
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ra)) {
+  Sa_i = array_format(Sa[i,])
+  nor = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
+  hor = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
+
+  out_nor = rbind(out_nor, as.numeric(nor))
+  out_hor = rbind(out_hor, as.numeric(hor))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(nor), ncol(nor))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(nor), each = nrow(nor))
+
+# make element names
+colnames(out_nor) = paste0("Sa_tot_org[", r_ind, ",1,", c_ind, "]")
+colnames(out_hor) = paste0("Sa_tot_org[", r_ind, ",2,", c_ind, "]")
+out = cbind(out_nor, out_hor)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-E-origin}
+E = post_subset(post, "^E_sep[", matrix = TRUE)
+
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ra)) {
+  E_i = array_format(E[i,])
+  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
+  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]
+
+  out_nor = rbind(out_nor, as.numeric(E_nor_i))
+  out_hor = rbind(out_hor, as.numeric(E_hor_i))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(nor), ncol(nor))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(nor), each = nrow(nor))
+
+# make element names
+colnames(out_nor) = paste0("E_org[", r_ind, ",1,", c_ind, "]")
+colnames(out_hor) = paste0("E_org[", r_ind, ",2,", c_ind, "]")
+out = cbind(out_nor, out_hor)
+
+# drop out those that have NA values (first k_max years)
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-E-per-Sa-origin}
+Sa = post_subset(post, "^Sa[", matrix = TRUE)
+E = post_subset(post, "^E_sep[", matrix = TRUE)
+
+out_nor = out_hor = NULL
+for (i in 1:nrow(Ra)) {
+  Sa_i = array_format(Sa[i,])
+  Sa_nor_i = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
+  Sa_hor_i = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
+  E_i = array_format(E[i,])
+  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
+  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]
+
+  out_nor = rbind(out_nor, as.numeric(E_nor_i/Sa_nor_i))
+  out_hor = rbind(out_hor, as.numeric(E_hor_i/Sa_hor_i))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(nor), ncol(nor))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(nor), each = nrow(nor))
+
+# make element names
+colnames(out_nor) = paste0("E_per_Sa_org[", r_ind, ",1,", c_ind, "]")
+colnames(out_hor) = paste0("E_per_Sa_org[", r_ind, ",2,", c_ind, "]")
+out = cbind(out_nor, out_hor)
 
@@
 out = cbind(p3_nor_out, p4_nor_out, p5_nor_out, p3_hor_out, p4_hor_out, p5_hor_out)
+
+# drop out those that have NA values (first k_max years)
+out[out == "NaN"] = 0
+na_ind = which(!is.na(out[1,]))
+out = out[,na_ind]
+
+# combine this with the rest of the posterior samples
+post = post_bind(post, out)
+```
+
+```{r add-age-comp-combined}
+Ra = post_subset(post, "^Ra[", matrix = TRUE)
+
+p3_out = p4_out = p5_out = NULL
+for (i in 1:nrow(Ra)) {
+  Ra_i = array_format(Ra[i,])
+
+  a3_tot = Ra_i[,1,1,] + Ra_i[,1,2,]
+  a4_tot = Ra_i[,2,1,] + Ra_i[,2,2,]
+  a5_tot = Ra_i[,3,1,] + Ra_i[,3,2,]
+  tot = a3_tot + a4_tot + a5_tot
+
+  p3 = Ra_i[,1,1,]/tot
+  p4 = Ra_i[,2,1,]/tot
+  p5 = Ra_i[,3,1,]/nor_tot
+
+  p3_out = rbind(p3_out, as.numeric(p3))
+  p4_out = rbind(p4_out, as.numeric(p4))
+  p5_out = rbind(p5_out, as.numeric(p5))
+}
+
+# build the row indices for each element: the year
+r_ind = rep(1:nrow(p3), ncol(p3))
+
+# build the column indices for each element: the population
+c_ind = rep(1:ncol(p3), each = nrow(p3))
+
+# make element names
+colnames(p3_out) = paste0("Ra_comp_a[", r_ind, ",", "1", ",", c_ind, "]")
+colnames(p4_out) = paste0("Ra_comp_a[", r_ind, ",", "2", ",", c_ind, "]")
+colnames(p5_out) = paste0("Ra_comp_a[", r_ind, ",", "3", ",", c_ind, "]")
+
+out = cbind(p3_out, p4_out, p5_out)
 
@@
   x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
-  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
+  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
   x = x[order(x$Class, x$Type, x$LH_type, x$origin),]
@@
   x$Class = factor(x$Class, levels = c("Abundance", "Production Rates", "SAR", "Adult Composition"))
-  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
+  x$Type = factor(x$Type, levels = c("Total Adults (Estuary)", "Total Adults (To Tributary)", "Total Spawners", "Total Egg Production", "Total Parr Recruitment", "Total LGR Smolt", "Aggregate Total Adult Return (To Tributary)", "Aggregate Total Smolt (At LGR)", "Eggs per Spawner", "Parr per Spawner", "Smolt in Tributary per Spawner", "Spawners per Spawner", "Smolt in Tributary per Parr", "Smolt at LGR per Parr", "BON to BON", "LGR to LGR", "Proportion Hatchery Return (Age-3)", "Proportion Hatchery Return (Age-4)", "Proportion Hatchery Return (Age-5)", "Proportion Hatchery Return (All Ages)", "Proportion Age-3 Return", "Proportion Age-4 Return", "Proportion Age-5 Return"))
   x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
-  x$origin = factor(x$origin, levels = c("Combined", "NOR", "HOR"))
+  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
   x = x[order(x$Class, x$Type, x$LH_type, x$origin),]
@@
 
-For us to use the state-space model as a simulation model, it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.
-
-This document is intended to identify whether simulated outcomes are similar to observed outcomes.
+For us to use the state-space model as a simulation model (which is the ultimate intent), it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.
+
+This document is intended to identify whether outcomes simulated from the state-space model are similar to observed outcomes.
 It looks at two primary types of quantities: stochastic time series parameters that are directly estimated by the model (e.g., egg to parr survival fluctuations not attributable to density dependence) and emergent outcomes calculated as derived quantities from stochastic parameters (e.g., total adult return abundance, BON to BON SAR rates, etc.).
@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^Rb_tot[year,pop]", obs_y, sim_y, pop = j))
+# by origin: plot and table
+x = append(
+  lapply(1:4, function(j) get_ratio("Rb_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
+  lapply(1:4, function(j) get_ratio("Rb_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
+)
 x = do.call(abind, append(x, list(along = 4)))
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Rb_tot[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (Estuary)"))
+```
+
 #### Total Adult Return (To Tributary)
@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^Ra_tot[year,pop]", obs_y, sim_y, pop = j))
+# by origin: plot and table
+x = append(
+  lapply(1:4, function(j) get_ratio("Ra_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
+  lapply(1:4, function(j) get_ratio("Ra_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
+)
 x = do.call(abind, append(x, list(along = 4)))
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Ra_tot[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Adults (To Tributary)"))
+```
+
 #### Total Spawners
@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^Sa_tot[year,pop]", obs_y, sim_y, pop = j))
+# by origin: plot and table
+x = append(
+  lapply(1:4, function(j) get_ratio("Sa_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
+  lapply(1:4, function(j) get_ratio("Sa_tot_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
+)
 x = do.call(abind, append(x, list(along = 4)))
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Sa_tot[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Spawners"))
+```
+
 #### Total Egg Production
@@
 ```{r}
-x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
+# by origin: plot and table
+x = append(
+  lapply(1:4, function(j) get_ratio("^E_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
+  lapply(1:4, function(j) get_ratio("^E_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
+)
 x = do.call(abind, append(x, list(along = 4)))
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
+```
+
 #### Total Parr Recruitment
@@
 
+#### Eggs per Spawner
+
+```{r}
+# by origin: plot and table
+x = append(
+  lapply(1:4, function(j) get_ratio("E_per_Sa_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
+  lapply(1:4, function(j) get_ratio("E_per_Sa_org[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
+)
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Eggs per Spawner: Estimates")
+ratio_plots(x, "Eggs per Spawner: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Eggs per Spawner"))
+```
+
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^E_per_Sa[year,pop]", obs_y, sim_y, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Production Rates", Type = "Eggs per Spawner"))
+```
+
 #### Parr per Spawner
@@
 
-#### Proportion Hatchery Return
+#### Proportion Hatchery Return {.tabset .tabset-pills}
+
+##### Age-3
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 1, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Proportion Hatchery Return (Age-3): Estimates")
+ratio_plots(x, "Proportion Hatchery Return (Age-3): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-3)"))
+```
+
+##### Age-4
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 2, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Proportion Hatchery Return (Age-4): Estimates")
+ratio_plots(x, "Proportion Hatchery Return (Age-4): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-4)"))
+```
+
+##### Age-5
+
+```{r}
+x = lapply(1:4, function(j) get_ratio("p_hor_a[year,age,pop]", obs_y, sim_y, age = 3, pop = j))
+x = do.call(abind, append(x, list(along = 4)))
+vals_plots(x, "Proportion Hatchery Return (Age-5): Estimates")
+ratio_plots(x, "Proportion Hatchery Return (Age-5): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (Age-5)"))
+```
+
+##### All Ages
 
@@
 x = do.call(abind, append(x, list(along = 4)))
-vals_plots(x, "Proportion Hatchery Return: Estimates")
-ratio_plots(x, "Proportion Hatchery Return: Ratios")
-derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return"))
+vals_plots(x, "Proportion Hatchery Return (All Ages): Estimates")
+ratio_plots(x, "Proportion Hatchery Return (All Ages): Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Hatchery Return (All Ages)"))
 ```
@@
 ```{r}
+# by origin: plot and table
 x = append(
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 1))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-3 Return"))
+```
+
 #### Proportion Age-4 Return
@@
 
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 2))
+x = do.call(abind, append(x, list(along = 4)))
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-4 Return"))
+```
+
 #### Proportion Age-5 Return
@@
 ratio_plots(x, "Proportion Age-5 Return: Ratios")
+derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
+```
+
+```{r}
+# combined: table only
+x = lapply(1:4, function(j) get_ratio("^Ra_comp_a[year,age,pop]", obs_y, sim_y, pop = j, age = 3))
+x = do.call(abind, append(x, list(along = 4)))
 derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Adult Composition", Type = "Proportion Age-5 Return"))
@@
 
-#### Total Adult Return (To Estuary)
+#### Total Adult Return (To Estuary) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r}
+pop_ts_plots("^Rb_tot_org[year,origin,pop]", origin = 1)
+```
+
+##### HOR
+
+```{r}
+pop_ts_plots("^Rb_tot_org[year,origin,pop]", origin = 2)
+```
+
+##### Combined
 
@@
 
-#### Total Adult Return (To Tributary)
+#### Total Adult Return (To Tributary) {.tabset .tabset-pills}
+
+##### NOR
+
+```{r}
+pop_ts_plots("^Ra_tot_org[year,origin,pop]", origin = 1)
+```
+
+##### HOR
+
+```{r}
+pop_ts_plots("^Ra_tot_org[year,origin,pop]", origin = 2)
+```
+
+##### Combined
 
@@
 
-#### Total Spawners
+#### Total Spawners {.tabset .tabset-pills}
+
+##### NOR
+
+```{r}
+pop_ts_plots("^Sa_tot_org[year,origin,pop]", origin = 1)
+```
+
+##### HOR
+
+```{r}
+pop_ts_plots("^Sa_tot_org[year,origin,pop]", origin = 2)
+```
+
+##### Combined
 
@@
 
-#### Total Egg Production
+#### Total Egg Production {.tabset .tabset-pills}
+
+##### NOR
+
+```{r}
+pop_ts_plots("^E_org[year,origin,pop]", origin = 1)
+```
+
+##### HOR
+
+```{r}
+pop_ts_plots("^E_org[year,origin,pop]", origin = 2)
+```
+
+##### Combined
 
@@
 
+#### Eggs per Spawner {.tabset .tabset-pills}
+
+##### NOR
+
+```{r}
+pop_ts_plots("^E_per_Sa_org[year,origin,pop]", origin = 1)
+```
+
+##### HOR
+
+```{r}
+pop_ts_plots("^E_per_Sa_org[year,origin,pop]", origin = 2)
+```
+
+##### Combined
+
+```{r}
+pop_ts_plots("^E_per_Sa[year,pop]")
+```
+
 #### Parr per Spawner
@@
 
-#### Proportion Hatchery Return
+#### Proportion Hatchery Return {.tabset .tabset-pills}
+
+##### Age-3
+
+```{r}
+pop_ts_plots("p_hor_a[year,age,pop]", age = 1)
+```
+
+##### Age-4
+
+```{r}
+pop_ts_plots("p_hor_a[year,age,pop]", age = 2)
+```
+
+##### Age-5
+
+```{r}
+pop_ts_plots("p_hor_a[year,age,pop]", age = 3)
+```
+
+##### Combined
 
@@
 
+##### Combined
+
+```{r}
+pop_ts_plots("Ra_comp_a[year,age,pop]", age = 1)
+```
+
 #### Proportion Age-4 Return {.tabset .tabset-pills}
@@
 
+##### Combined
+
+```{r}
+pop_ts_plots("Ra_comp_a[year,age,pop]", age = 2)
+```
+
 #### Proportion Age-5 Return {.tabset .tabset-pills}
@@
 ```
+
+##### Combined
+
+```{r}
+pop_ts_plots("Ra_comp_a[year,age,pop]", age = 3)
+```

### 2022-09-16 03-post-process/output-plots-children/03-fit-to-data.Rmd
Fix header levels in fit-to-data Rmd
Fix issues with file paths in output-plots Rmd

@@
 
-#### Spawn Status Data
+### Spawn Status Data
 
@@
 
-#### Mean Length Data {.tabset .tabset-pills}
+### Mean Length Data {.tabset .tabset-pills}
 
-##### Summer Parr
+#### Summer Parr
 
@@
 
-##### Spring Smolt
+#### Spring Smolt
 
@@
 
-```{r pp-check-output, child = "03a-pp-checks.Rmd", eval = model_info$do_pp_check}
+```{r pp-check-output, child = "output-plots-children/03a-pp-checks.Rmd", eval = model_info$do_pp_check}
 ```
 
-```{r waic-output, child = "03b-waic.Rmd", eval = model_info$do_lppd}
+```{r waic-output, child = "output-plots-children/03b-waic.Rmd", eval = model_info$do_lppd}
 ```

### 2022-09-16 03-post-process/compare-sim-to-obs.Rmd

@@
     label: "Scenario"
-    value: "base-vlong"
+    value: "base"
     input: text

### 2022-09-16 03-post-process/output-plots.Rmd

@@
 # set root directory to the project directory: one level up from this location
-# knitr::opts_knit$set(root.dir = "../")
+knitr::opts_knit$set(root.dir = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process")
 ```

### 2023-01-26 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # MCMC Diagnostics {.tabset .tabset-pills}
@@
 L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr3 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "delta_O2_O3[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
+L2 = c("Yr1 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
+base = c("delta_O0_O1[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
 match = sub_index(base, pop = ".")
@@
 L2 = c("Realized Total Number", "Age Comp")
-match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
+match = c(sub_index("^G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
 ```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_1, "", show_diags = "never")
+diag_plots(post_sub_1, ".", show_diags = "never")
 ```
@@
 ```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_2, "", show_diags = "never")
+diag_plots(post_sub_2, ".", show_diags = "never")
 ```
@@
 ```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
-diag_plots(post_sub_3, "", show_diags = "never")
+diag_plots(post_sub_3, ".", show_diags = "never")
 ```

### 2023-01-26 03-post-process/output-plots-children/05-length-based-values.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Length-Based Quantities {.tabset .tabset-dropdown}
@@
   # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "")["mean",]
-  E_scaled_lwr = post_summ(post_E, "")["2.5%",]
-  E_scaled_upr = post_summ(post_E, "")["97.5%",]
+  E_scaled_mean = post_summ(post_E, ".")["mean",]
+  E_scaled_lwr = post_summ(post_E, ".")["2.5%",]
+  E_scaled_upr = post_summ(post_E, ".")["97.5%",]
 
@@
   # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, "")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, "")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, "")["97.5%",]
+  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
+  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
+  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]
 
@@
   # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]
+  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
+  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
+  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]
 
@@
   # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, "")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, "")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, "")["97.5%",]
+  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
+  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
+  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]
 
@@
   # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, "")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, "")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, "")["97.5%",]
+  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
+  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
+  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
 

### 2023-01-30 03-post-process/output-plots-children/10-noise-term-diags.Rmd
Tiny qresid bug fix
apply() was throwing errors in the case that i_first had only one element; this enables apply to be used regardless

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Random Noise Diagnostics {.tabset .tabset-pills}
@@
   i_last = as.character(na.omit(empty_names[y_last]))
-  mn_post_first = apply(qresid_post[,i_first], 1, mean)
-  mn_post_last = apply(qresid_post[,i_last], 1, mean)
+  mn_post_first = apply(as.matrix(qresid_post[,i_first]), 1, mean)
+  mn_post_last = apply(as.matrix(qresid_post[,i_last]), 1, mean)
   first_last_mn_diff_post = mn_post_last - mn_post_first

### 2023-02-28 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Add posterior vs. prior plots to output-plots
Only for the handful of parameters with potentially informative priors. Consider adding greater flexibility later

---
editor_options: 
  chunk_output_type: console
---

# Prior vs. Posterior {.tabset .tabset-pills}

```{r post-v-prior-fig-sizes}
# set global knitting options
knitr::opts_chunk$set(fig.width = 6, fig.height = 5)
```

```{r post-v-prior-fn}
# argument list:
# post_samps & prior_samps: samples from their respective PDFs
# post_col & prior_col: (non-transparent) colors for each PDF (will be made transparent for bar fills based on the alpha argument)
# main: plot title
# y_max: maximum bin probability height to display; should be [0,1]
# legend_loc: position of the legend (e.g., "topright")
# n_bins: the number of bins
# alpha: transparency setting for bar fills

post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
                        main = NULL, y_max = 0.3, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {

  # get the range of all samples
  rng = range(post_samps, prior_samps)

  # if xlim was provided, take it into consideration when creating breaks
  if (is.null(xlim)) {
    breaks = seq(rng[1], rng[2], length = n_bins)
  } else {
    breaks = seq(min(rng[1], xlim[1]), max(rng[2], xlim[2]), length = n_bins)
  }

  # calculate the data for the histogram
  prior_hist = hist(prior_samps, plot = FALSE, breaks = breaks)
  post_hist = hist(post_samps, plot = FALSE, breaks = breaks)

  # convert bin counts to probabilities
  prior_probs = prior_hist$counts/sum(prior_hist$counts)
  post_probs = post_hist$counts/sum(post_hist$counts)

  # graphics parameters
  par(xaxs = "i", yaxs = "i", mgp = c(2,0.2,0), cex.axis = 0.8, tcl = -0.15, mar = c(1.5,1,1.5,0.5), lend = "square", ljoin = "mitre")

  # create a y_max if not supplied
  if (is.null(y_max)) {
    y_max = max(prior_probs, post_probs)
  }

  # create the histogram for prior PDF
  # barplot where height is equal to bin prob
  mp = barplot(
    prior_probs, ylim = c(0,y_max), space = 0, border = prior_col, col = scales::alpha(prior_col, alpha), axes = FALSE
    )

  # create the histogram for posterior PDF
  mp = barplot(
    post_probs, ylim = c(0,y_max), space = 0, border = post_col, col = scales::alpha(post_col, alpha), axes = FALSE, add = TRUE
    )

  # draw the x-axis
  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = mp[at_x], labels = round(prior_hist$breaks[at_x], 1))

  # draw the y-axis
  axis(side = 2)

  # draw segments to connect axes at origin
  usr = par("usr")
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)

  # add a legend in the desired location if not NULL
  if (!is.na(legend_loc)) {
    legend(legend_loc, legend = c("Prior", "Posterior"), bty = "n", pch = 22, pt.cex = 1.75, cex = 0.8, col = c(prior_col, post_col), pt.bg = scales::alpha(c(prior_col, post_col), 0.5))
  }
}
```

```{r}
# wrapper to create plot for all populations
post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, ...) {
  # function to plot one population
  plot_f = function(j) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
      prior_samps = post_subset(post, prior_param, matrix = TRUE),
      main = pops[j], 
      legend_loc = ifelse(j == 1, legend_loc, NA),
      xlim = xlim
    )
  }

  # apply to each population
  par(mfrow = c(2,2), oma = c(1,1.5,0,0))
  junk = sapply(1:jags_data$nj, plot_f)
  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
}
```

## "Location" Parameters {.tabset .tabset-dropdown}

### Max. Egg-to-Parr Survival

**Prior Used**: `dbeta(`r jags_data$alpha_prior[1]`, `r jags_data$alpha_prior[2]`)`

```{r alpha-post-v-prior}
post_v_prior_pops(post_param = "alpha[pop]", prior_param = "alpha_pr", xlim = c(0,1))
```

### Mean Ocean Survival (NOR) {.tabset .tabset-pills}

#### Yr1

**Prior Used**: `dbeta(`r jags_data$mu_phi_O0_O1[1]`, `r jags_data$mu_phi_O0_O1[2]`)`

```{r mu_phi_O0_O1-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O0_O1[origin,pop]", prior_param = "mu_phi_O0_O1_pr",
                  origin = o_nor, xlim = c(0,1)
)
```

#### Yr2

**Prior Used**: `dbeta(`r jags_data$mu_phi_O1_O2[1]`, `r jags_data$mu_phi_O1_O2[2]`)`

```{r mu_phi_O1_O2-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O1_O2[origin,pop]", prior_param = "mu_phi_O1_O2_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
)
```

#### Yr3

**Prior Used**: `dbeta(`r jags_data$mu_phi_O2_O3[1]`, `r jags_data$mu_phi_O2_O3[2]`)`

```{r mu_phi_O2_O3-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O2_O3[origin,pop]", prior_param = "mu_phi_O2_O3_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
)
```

### Mean Maturation {.tabset .tabset-pills}

#### Age-3 {.tabset .tabset-pills}

**Prior Used**: `dbeta(`r jags_data$mu_psi_O1[1]`, `r jags_data$mu_psi_O1[2]`)`

##### NOR

```{r mu_psi_O1_nor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_nor, xlim = c(0,1)
)
```

##### HOR

```{r mu_psi_O1_hor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_hor, xlim = c(0,1)
)
```

#### Age-4 {.tabset .tabset-pills}

**Prior Used**: `dbeta(`r jags_data$mu_psi_O2[1]`, `r jags_data$mu_psi_O2[2]`)`

##### NOR

```{r mu_psi_O2_nor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O2[origin,pop]", prior_param = "mu_psi_O2_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
)
```

##### HOR

```{r mu_psi_O2_hor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O2[origin,pop]", prior_param = "mu_psi_O2_pr",
                  origin = o_hor, xlim = c(0,1), legend_loc = "topleft"
)
```

## "Scale" Parameters {.tabset .tabset-dropdown}

### SD Logit Egg-to-Parr Survival

**Prior Used**: `dt(0, 1/`r jags_data$sig_Lphi_E_Pb_prior`^2, 1) T(0, `r jags_data$dt_upr`)`

```{r sig_Lphi_E_Pb-post-v-prior}
post_v_prior_pops(post_param = "sig_Lphi_E_Pb[pop]", prior_param = "sig_Lphi_E_Pb_pr",
                  xlim = c(0, jags_data$dt_upr)
)
```

### SD Logit Yr1 Ocean Survival

**Prior Used**: `dt(0, 1/`r jags_data$sig_Lphi_O0_O1_prior`^2, 1) T(0, `r jags_data$dt_upr`)`

```{r sig_Lphi_O0_O1-post-v-prior}
post_v_prior_pops(post_param = "sig_Lphi_O0_O1[pop]", prior_param = "sig_Lphi_O0_O1_pr",
                  xlim = c(0, jags_data$dt_upr)
)
```

### SD Logit Maturation {.tabset .tabset-pills}

#### Age-3 {.tabset .tabset-pills}

**Prior Used**: `dt(0, 1/`r jags_data$sig_Lpsi_O1`^2, 1) T(0, `r jags_data$dt_upr`)`

##### NOR

```{r sig_Lpsi_O1_nor-post-v-prior}
post_v_prior_pops(post_param = "sig_Lpsi_O1[pop,origin]", prior_param = "sig_Lpsi_O1_pr",
                  origin = o_nor, xlim = c(0, jags_data$dt_upr)
)
```

##### HOR

```{r sig_Lpsi_O1_hor-post-v-prior}
post_v_prior_pops(post_param = "sig_Lpsi_O1[pop,origin]", prior_param = "sig_Lpsi_O1_pr",
                  origin = o_hor, xlim = c(0, jags_data$dt_upr)
)
```

#### Age-4 {.tabset .tabset-pills}

**Prior Used**: `dt(0, 1/`r jags_data$sig_Lpsi_O2`^2, 1) T(0, `r jags_data$dt_upr`)`

##### NOR

```{r sig_Lpsi_O2_nor-post-v-prior}
post_v_prior_pops(post_param = "sig_Lpsi_O2[pop,origin]", prior_param = "sig_Lpsi_O2_pr",
                  origin = o_nor, xlim = c(0, jags_data$dt_upr)
)
```

##### HOR

```{r sig_Lpsi_O2_hor-post-v-prior}
post_v_prior_pops(post_param = "sig_Lpsi_O2[pop,origin]", prior_param = "sig_Lpsi_O2_pr",
                  origin = o_hor, xlim = c(0, jags_data$dt_upr)
)
```

### 2023-02-28 03-post-process/compare-sim-to-obs.Rmd
Fix small typo in sim-v-obs rmd
Improve memory usage of post-MCMC calculations
Sim-v-obs compares many derived quantities that are not monitored via mcmc. The old code was super memory heavy, this code is (much) faster and take less memory

@@
     label: "Scenario"
-    value: "base"
+    value: "tack-on-all-priors"
     input: text
@@
     label: "Proportion of Posterior Samples to Retain?"
-    value: 1
+    value: 0.5
     input: numeric
@@
 j_ugr = 4     # j = 4 is UGR
+i_fall = 1    # i = 1 is fall migrants
+i_spring = 2  # i = 2 is spring migrants
+
+rm(model_info)
 ```
@@
 ```{r add-p-hos}
-# extract spawners returning to tributary
+f = function() {
+  # extract adults returning to tributary
   Ra = post_subset(post, "^Ra[", matrix = TRUE)
 
-# for each posterior sample, calculate the fraction that are hatchery origin
-out = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_1 = array_format(Ra[1,])
+  nor_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ra_i = array_format(Ra[i,])
-  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
-  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
-  out = rbind(out, as.numeric(hor/(nor + hor)))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
+    hor = Ra_i[,k_3,o_hor,] + Ra_i[,k_4,o_hor,] + Ra_i[,k_5,o_hor,]
+    nor = Ra_i[,k_3,o_nor,] + Ra_i[,k_4,o_nor,] + Ra_i[,k_5,o_nor,]
+    as.numeric(hor/(nor + hor))
+  }
+
+  # apply to each posterior sample
+  out = t(sapply(1:nrow(Ra), g))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
 
   # make element names
-colnames(out) = paste0("p_hor[", r_ind, ",", c_ind, "]")
+  colnames(out) = paste0("p_hor[", y_ind, ",", j_ind, "]")
 
@@
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-p-hos-age}
-# extract spawners returning to tributary
+f = function() {
+  # extract adults returning to tributary
   Ra = post_subset(post, "^Ra[", matrix = TRUE)
 
-# for each posterior sample, calculate the fraction that are hatchery origin
-out_3 = out_4 = out_5 = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_1 = array_format(Ra[1,])
+  p_hor_3_1 = Ra_1[,k_3,o_hor,]/(Ra_1[,k_3,o_nor,] + Ra_1[,k_3,o_hor,])
+  p_hor_4_1 = Ra_1[,k_4,o_hor,]/(Ra_1[,k_4,o_nor,] + Ra_1[,k_4,o_hor,])
+  p_hor_5_1 = Ra_1[,k_5,o_hor,]/(Ra_1[,k_5,o_nor,] + Ra_1[,k_5,o_hor,])
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ra_i = array_format(Ra[i,])
-
     p_hor_3 = Ra_i[,k_3,o_hor,]/(Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,])
@@
     p_hor_5 = Ra_i[,k_5,o_hor,]/(Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,])
-
-  out_3 = rbind(out_3, as.numeric(p_hor_3))
-  out_4 = rbind(out_4, as.numeric(p_hor_4))
-  out_5 = rbind(out_5, as.numeric(p_hor_5))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(p_hor_3), ncol(p_hor_3))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(p_hor_3), each = nrow(p_hor_3))
-
-# make element names
-colnames(out_3) = paste0("p_hor_a[", r_ind, ",1,", c_ind, "]")
-colnames(out_4) = paste0("p_hor_a[", r_ind, ",2,", c_ind, "]")
-colnames(out_5) = paste0("p_hor_a[", r_ind, ",3,", c_ind, "]")
-out = cbind(out_3, out_4, out_5)
-
-# drop out those that have NA values (first k_max years)
+    c(as.numeric(p_hor_3), as.numeric(p_hor_4), as.numeric(p_hor_5))
+  }
+
+  # apply to each posterior sample
+  out = t(sapply(1:nrow(Ra), g))
+
+  # build element indices: the year
+  y_ind = rep(rep(1:nrow(p_hor_3_1), ncol(p_hor_3_1)), 3)
+
+  # build element indices: the population
+  j_ind = rep(rep(1:ncol(p_hor_3_1), each = nrow(p_hor_3_1)), 3)
+
+  # build element indices: the age
+  k3_ind = rep(1, nrow(p_hor_3_1) * ncol(p_hor_3_1))
+  k4_ind = rep(2, nrow(p_hor_3_1) * ncol(p_hor_3_1))
+  k5_ind = rep(3, nrow(p_hor_3_1) * ncol(p_hor_3_1))
+  k_ind = c(k3_ind, k4_ind, k5_ind)
+
+  # build element names
+  colnames(out) = paste0("p_hor_a[", y_ind, ",", k_ind, ",", j_ind, "]")
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
+  out[,na_ind]
+}
 
 # combine this with the rest of the posterior samples
-post = post_bind(post, out)
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-Rb-tot-origin}
+f = function() {
   # extract returns to estuary
@@
 
-# for each posterior sample, calculate the abundance by origin and total
-out_tot = out_nor = out_hor = NULL
-for (i in 1:nrow(Rb)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Rb_1 = array_format(Rb[1,])
+  nor_1 = Rb_1[,k_3,o_nor,] + Rb_1[,k_4,o_nor,] + Rb_1[,k_5,o_nor,]
+  hor_1 = Rb_1[,k_3,o_hor,] + Rb_1[,k_4,o_hor,] + Rb_1[,k_5,o_hor,]
+  tot_1 = nor_1 + hor_1
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Rb_i = array_format(Rb[i,])
-  nor = Rb_i[,1,1,] + Rb_i[,2,1,] + Rb_i[,3,1,]
-  hor = Rb_i[,1,2,] + Rb_i[,2,2,] + Rb_i[,3,2,]
+    nor = Rb_i[,k_3,o_nor,] + Rb_i[,k_4,o_nor,] + Rb_i[,k_5,o_nor,]
+    hor = Rb_i[,k_3,o_hor,] + Rb_i[,k_4,o_hor,] + Rb_i[,k_5,o_hor,]
     tot = nor + hor
 
-  out_nor = rbind(out_nor, as.numeric(nor))
-  out_hor = rbind(out_hor, as.numeric(hor))
-  out_tot = rbind(out_tot, as.numeric(tot))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("Rb_tot_org[", r_ind, ",1,", c_ind, "]")
-colnames(out_hor) = paste0("Rb_tot_org[", r_ind, ",2,", c_ind, "]")
-colnames(out_tot) = paste0("Rb_tot[", r_ind, ",", c_ind, "]")
-out = cbind(out_nor, out_hor, out_tot)
-
-# drop out those that have NA values (first k_max years)
+    list(nor = as.numeric(nor), hor = as.numeric(hor), tot = as.numeric(tot))
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Rb), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+  tot_out = do.call(rbind, lapply(out, function(x) x$tot))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("Rb_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("Rb_tot_org[", y_ind, ",", "2", ",", j_ind, "]")
+  colnames(tot_out) = paste0("Rb_tot[", y_ind, ",", j_ind, "]")
+
+  # combine matrices
+  out = cbind(nor_out, hor_out, tot_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-Ra-tot-origin}
+f = function() {
   # extract returns to tributary
@@
 
-# for each posterior sample, calculate the abundance by origin and total
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_1 = array_format(Ra[1,])
+  nor_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ra_i = array_format(Ra[i,])
-  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
-  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
-
-  out_nor = rbind(out_nor, as.numeric(nor))
-  out_hor = rbind(out_hor, as.numeric(hor))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("Ra_tot_org[", r_ind, ",1,", c_ind, "]")
-colnames(out_hor) = paste0("Ra_tot_org[", r_ind, ",2,", c_ind, "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+    list(
+      nor = as.numeric(Ra_i[,k_3,o_nor,] + Ra_i[,k_4,o_nor,] + Ra_i[,k_5,o_nor,]),
+      hor = as.numeric(Ra_i[,k_3,o_hor,] + Ra_i[,k_4,o_hor,] + Ra_i[,k_5,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ra), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("Ra_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("Ra_tot_org[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-Sa-tot-origin}
-# extract spawners
+f = function() {
+  # extract posterior samples of spawners
   Sa = post_subset(post, "^Sa[", matrix = TRUE)
 
-# for each posterior sample, calculate the abundance by origin and total
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Sa_1 = array_format(Sa[1,])
+  nor_1 = Sa_1[,k_3,o_nor,] + Sa_1[,k_4,o_nor,] + Sa_1[,k_5,o_nor,]
+  hor_1 = Sa_1[,k_3,o_hor,] + Sa_1[,k_4,o_hor,] + Sa_1[,k_5,o_hor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Sa_i = array_format(Sa[i,])
-  nor = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
-  hor = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
-
-  out_nor = rbind(out_nor, as.numeric(nor))
-  out_hor = rbind(out_hor, as.numeric(hor))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("Sa_tot_org[", r_ind, ",1,", c_ind, "]")
-colnames(out_hor) = paste0("Sa_tot_org[", r_ind, ",2,", c_ind, "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+    list(
+      nor = as.numeric(Sa_i[,k_3,o_nor,] + Sa_i[,k_4,o_nor,] + Sa_i[,k_5,o_nor,]),
+      hor = as.numeric(Sa_i[,k_3,o_hor,] + Sa_i[,k_4,o_hor,] + Sa_i[,k_5,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Sa), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("Sa_tot_org[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("Sa_tot_org[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-E-origin}
+f = function() {
+  # extract posterior samples of egg production
   E = post_subset(post, "^E_sep[", matrix = TRUE)
 
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  E_1 = array_format(E[1,])
+  nor_1 = E_1[,k_3,o_nor,] + E_1[,k_4,o_nor,] + E_1[,k_5,o_nor,]
+  hor_1 = E_1[,k_3,o_hor,] + E_1[,k_4,o_hor,] + E_1[,k_5,o_hor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     E_i = array_format(E[i,])
-  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
-  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]
-
-  out_nor = rbind(out_nor, as.numeric(E_nor_i))
-  out_hor = rbind(out_hor, as.numeric(E_hor_i))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("E_org[", r_ind, ",1,", c_ind, "]")
-colnames(out_hor) = paste0("E_org[", r_ind, ",2,", c_ind, "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+    list(
+      nor = as.numeric(E_i[,k_3,o_nor,] + E_i[,k_4,o_nor,] + E_i[,k_5,o_nor,] + 1),
+      hor = as.numeric(E_i[,k_3,o_hor,] + E_i[,k_4,o_hor,] + E_i[,k_5,o_hor,] + 1)
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(E), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("E_org[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("E_org[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-E-per-Sa-origin}
-Sa = post_subset(post, "^Sa[", matrix = TRUE)
-E = post_subset(post, "^E_sep[", matrix = TRUE)
-
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ra)) {
-  Sa_i = array_format(Sa[i,])
-  Sa_nor_i = Sa_i[,1,1,] + Sa_i[,2,1,] + Sa_i[,3,1,]
-  Sa_hor_i = Sa_i[,1,2,] + Sa_i[,2,2,] + Sa_i[,3,2,]
-  E_i = array_format(E[i,])
-  E_nor_i = E_i[,1,1,] + E_i[,2,1,] + E_i[,3,1,]
-  E_hor_i = E_i[,1,2,] + E_i[,2,2,] + E_i[,3,2,]
-
-  out_nor = rbind(out_nor, as.numeric(E_nor_i/Sa_nor_i))
-  out_hor = rbind(out_hor, as.numeric(E_hor_i/Sa_hor_i))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("E_per_Sa_org[", r_ind, ",1,", c_ind, "]")
-colnames(out_hor) = paste0("E_per_Sa_org[", r_ind, ",2,", c_ind, "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+f = function() {
+  # extract posterior samples of egg production
+  E_org = post_subset(post, "^E_org[", matrix = TRUE)
+  Sa_org = post_subset(post, "^Sa_tot_org[", matrix = TRUE)
+
+  # perform basic operations for one iteration -- for making dimension names later
+  E_org_1 = array_format(E_org[1,])
+  Sa_org_1 = array_format(Sa_org[1,])
+  nor_1 = E_org_1[,o_nor,]/Sa_org_1[,o_nor,]
+  hor_1 = E_org_1[,o_hor,]/Sa_org_1[,o_hor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
+    E_org_i = array_format(E_org[i,])
+    Sa_org_i = array_format(Sa_org[i,])
+
+    list(
+      nor = as.numeric(E_org_i[,o_nor,]/Sa_org_i[,o_nor,]),
+      hor = as.numeric(E_org_i[,o_hor,]/Sa_org_i[,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(E_org), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("E_per_Sa_org[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("E_per_Sa_org[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-Ma-tot}
-# extract smolt at LGR
+f = function() {
+  # extract posterior samples of smolt at LGR
   Ma = post_subset(post, "^Ma[", matrix = TRUE)
 
-# for each posterior sample, calculate the number of NOR and HOR smolt at LGR
-out_nor = NULL
-out_hor = NULL
-for (i in 1:nrow(Ma)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ma_1 = array_format(Ma[1,])
+  nor_1 = Ma_1[,i_fall,o_nor,] + Ma_1[,i_spring,o_nor,]
+  hor_1 = Ma_1[,i_spring,o_hor,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ma_i = array_format(Ma[i,])
-  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
-  hor = Ma_i[,2,2,]
-  out_nor = rbind(out_nor, as.numeric(nor))
-  out_hor = rbind(out_hor, as.numeric(hor))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(nor), ncol(nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(nor), each = nrow(nor))
-
-# make element names
-colnames(out_nor) = paste0("Ma_tot[", r_ind, ",", "1", ",", c_ind, "]")
-colnames(out_hor) = paste0("Ma_tot[", r_ind, ",", "2", ",", c_ind, "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+    list(
+      nor = as.numeric(Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]),
+      hor = as.numeric(Ma_i[,i_spring,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ma), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(nor_1), ncol(nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(nor_1), each = nrow(nor_1))
+
+  # build element names
+  colnames(nor_out) = paste0("Ma_tot[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(hor_out) = paste0("Ma_tot[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-age-comp}
+f = function() {
+  # extract posterior samples of smolt at LGR
   Ra = post_subset(post, "^Ra[", matrix = TRUE)
 
-# for each posterior sample, calculate the fraction that of each age by origin
-p3_nor_out = p4_nor_out = p5_nor_out = p3_hor_out = p4_hor_out = p5_hor_out = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_1 = array_format(Ra[1,])
+  nor_tot_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_4,o_nor,] + Ra_1[,k_5,o_nor,]
+  hor_tot_1 = Ra_1[,k_3,o_hor,] + Ra_1[,k_4,o_hor,] + Ra_1[,k_5,o_hor,]
+  p3_nor_1 = Ra_1[,k_3,o_nor,]/nor_tot_1
+  p4_nor_1 = Ra_1[,k_4,o_nor,]/nor_tot_1
+  p5_nor_1 = Ra_1[,k_5,o_nor,]/nor_tot_1
+  p3_hor_1 = Ra_1[,k_3,o_hor,]/hor_tot_1
+  p4_hor_1 = Ra_1[,k_4,o_hor,]/hor_tot_1
+  p5_hor_1 = Ra_1[,k_5,o_hor,]/hor_tot_1
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ra_i = array_format(Ra[i,])
-  nor_tot = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
-  hor_tot = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
-
-  p3_nor = Ra_i[,1,1,]/nor_tot
-  p4_nor = Ra_i[,2,1,]/nor_tot
-  p5_nor = Ra_i[,3,1,]/nor_tot
-  p3_hor = Ra_i[,1,2,]/hor_tot
-  p4_hor = Ra_i[,2,2,]/hor_tot
-  p5_hor = Ra_i[,3,2,]/hor_tot
-
-  p3_nor_out = rbind(p3_nor_out, as.numeric(p3_nor))
-  p4_nor_out = rbind(p4_nor_out, as.numeric(p4_nor))
-  p5_nor_out = rbind(p5_nor_out, as.numeric(p5_nor))
-  p3_hor_out = rbind(p3_hor_out, as.numeric(p3_hor))
-  p4_hor_out = rbind(p4_hor_out, as.numeric(p4_hor))
-  p5_hor_out = rbind(p5_hor_out, as.numeric(p5_hor))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(p3_nor), ncol(p3_nor))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(p3_nor), each = nrow(p3_nor))
-
-# make element names
-colnames(p3_nor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "1", ",", c_ind, "]")
-colnames(p4_nor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "1", ",", c_ind, "]")
-colnames(p5_nor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "1", ",", c_ind, "]")
-colnames(p3_hor_out) = paste0("Ra_comp[", r_ind, ",", "1", ",", "2", ",", c_ind, "]")
-colnames(p4_hor_out) = paste0("Ra_comp[", r_ind, ",", "2", ",", "2", ",", c_ind, "]")
-colnames(p5_hor_out) = paste0("Ra_comp[", r_ind, ",", "3", ",", "2", ",", c_ind, "]")
-
+    nor_tot_i = Ra_i[,k_3,o_nor,] + Ra_i[,k_4,o_nor,] + Ra_i[,k_5,o_nor,]
+    hor_tot_i = Ra_i[,k_3,o_hor,] + Ra_i[,k_4,o_hor,] + Ra_i[,k_5,o_hor,]
+    list(
+      p3_nor = as.numeric(Ra_i[,k_3,o_nor,]/nor_tot_i),
+      p4_nor = as.numeric(Ra_i[,k_4,o_nor,]/nor_tot_i),
+      p5_nor = as.numeric(Ra_i[,k_5,o_nor,]/nor_tot_i),
+      p3_hor = as.numeric(Ra_i[,k_3,o_hor,]/hor_tot_i),
+      p4_hor = as.numeric(Ra_i[,k_4,o_hor,]/hor_tot_i),
+      p5_hor = as.numeric(Ra_i[,k_5,o_hor,]/hor_tot_i)
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ra), g)
+
+  # convert these to their own matrices for easier element construction
+  p3_nor_out = do.call(rbind, lapply(out, function(x) x$p3_nor))
+  p4_nor_out = do.call(rbind, lapply(out, function(x) x$p4_nor))
+  p5_nor_out = do.call(rbind, lapply(out, function(x) x$p5_nor))
+  p3_hor_out = do.call(rbind, lapply(out, function(x) x$p3_hor))
+  p4_hor_out = do.call(rbind, lapply(out, function(x) x$p4_hor))
+  p5_hor_out = do.call(rbind, lapply(out, function(x) x$p5_hor))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(p3_nor_1), ncol(p3_nor_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(p3_nor_1), each = nrow(p3_nor_1))
+
+  # build element names
+  colnames(p3_nor_out) = paste0("Ra_comp[", y_ind, ",", "1", ",", "1", ",", j_ind, "]")
+  colnames(p4_nor_out) = paste0("Ra_comp[", y_ind, ",", "2", ",", "1", ",", j_ind, "]")
+  colnames(p5_nor_out) = paste0("Ra_comp[", y_ind, ",", "3", ",", "1", ",", j_ind, "]")
+  colnames(p3_hor_out) = paste0("Ra_comp[", y_ind, ",", "1", ",", "2", ",", j_ind, "]")
+  colnames(p4_hor_out) = paste0("Ra_comp[", y_ind, ",", "2", ",", "2", ",", j_ind, "]")
+  colnames(p5_hor_out) = paste0("Ra_comp[", y_ind, ",", "3", ",", "2", ",", j_ind, "]")
+
+  # combine
   out = cbind(p3_nor_out, p4_nor_out, p5_nor_out, p3_hor_out, p4_hor_out, p5_hor_out)
 
-# drop out those that have NA values (first k_max years)
+  # drop out those that have NA values
   out[out == "NaN"] = 0
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-age-comp-combined}
+f = function() {
+  # extract posterior samples of return to tributary
   Ra = post_subset(post, "^Ra[", matrix = TRUE)
 
-p3_out = p4_out = p5_out = NULL
-for (i in 1:nrow(Ra)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_1 = array_format(Ra[1,])
+  a3_1 = Ra_1[,k_3,o_nor,] + Ra_1[,k_3,o_hor,]
+  a4_1 = Ra_1[,k_4,o_nor,] + Ra_1[,k_4,o_hor,]
+  a5_1 = Ra_1[,k_5,o_nor,] + Ra_1[,k_5,o_hor,]
+  tot_1 = a3_1 + a4_1 + a5_1
+  p3_1 = a3_1/tot_1
+  p4_1 = a4_1/tot_1
+  p5_1 = a5_1/tot_1
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ra_i = array_format(Ra[i,])
-
-  a3_tot = Ra_i[,1,1,] + Ra_i[,1,2,]
-  a4_tot = Ra_i[,2,1,] + Ra_i[,2,2,]
-  a5_tot = Ra_i[,3,1,] + Ra_i[,3,2,]
-  tot = a3_tot + a4_tot + a5_tot
-
-  p3 = Ra_i[,1,1,]/tot
-  p4 = Ra_i[,2,1,]/tot
-  p5 = Ra_i[,3,1,]/nor_tot
-
-  p3_out = rbind(p3_out, as.numeric(p3))
-  p4_out = rbind(p4_out, as.numeric(p4))
-  p5_out = rbind(p5_out, as.numeric(p5))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:nrow(p3), ncol(p3))
-
-# build the column indices for each element: the population
-c_ind = rep(1:ncol(p3), each = nrow(p3))
-
-# make element names
-colnames(p3_out) = paste0("Ra_comp_a[", r_ind, ",", "1", ",", c_ind, "]")
-colnames(p4_out) = paste0("Ra_comp_a[", r_ind, ",", "2", ",", c_ind, "]")
-colnames(p5_out) = paste0("Ra_comp_a[", r_ind, ",", "3", ",", c_ind, "]")
-
+    a3_i = Ra_i[,k_3,o_nor,] + Ra_i[,k_3,o_hor,]
+    a4_i = Ra_i[,k_4,o_nor,] + Ra_i[,k_4,o_hor,]
+    a5_i = Ra_i[,k_5,o_nor,] + Ra_i[,k_5,o_hor,]
+    tot_i = a3_i + a4_i + a5_i
+    list(
+      p3 = as.numeric(a3_i/tot_i),
+      p4 = as.numeric(a4_i/tot_i),
+      p5 = as.numeric(a5_i/tot_i)
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ra), g)
+
+  # convert these to their own matrices for easier element construction
+  p3_out = do.call(rbind, lapply(out, function(x) x$p3))
+  p4_out = do.call(rbind, lapply(out, function(x) x$p4))
+  p5_out = do.call(rbind, lapply(out, function(x) x$p5))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(p3_1), ncol(p3_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(p3_1), each = nrow(p3_1))
+
+  # build element names
+  colnames(p3_out) = paste0("Ra_comp_a[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(p4_out) = paste0("Ra_comp_a[", y_ind, ",", "2", ",", j_ind, "]")
+  colnames(p5_out) = paste0("Ra_comp_a[", y_ind, ",", "3", ",", j_ind, "]")
+
+  # combine
   out = cbind(p3_out, p4_out, p5_out)
 
-# drop out those that have NA values (first k_max years)
+  # drop out those that have NA values
   out[out == "NaN"] = 0
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-trib-smolt-per-parr}
+f = function() {
+  # extract posterior samples of tributary smolt and parr
   Mb = post_subset(post, "^Mb[", matrix = TRUE)
@@
 
-# for each posterior sample, calculate survival from parr to lgr smolt by LH type
-out_fall = out_spring = NULL
-
-for (i in 1:nrow(Mb)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Mb_1 = array_format(Mb[1,])
+  Pa_1 = array_format(Pa[1,])
+  Mb_per_Pa_1 = Mb_1[,,o_nor,]/Pa_1
+  fall_1 = Mb_per_Pa_1[,i_fall,]
+  spring_1 = Mb_per_Pa_1[,i_spring,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Mb_i = array_format(Mb[i,])
     Pa_i = array_format(Pa[i,])
-
-  Mb_per_Pa = Mb_i[,,1,]/Pa_i
-
-  out_fall = rbind(out_fall, as.numeric(Mb_per_Pa[,1,]))
-  out_spring = rbind(out_spring, as.numeric(Mb_per_Pa[,2,]))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:dim(Mb_per_Pa)[1], dim(Mb_per_Pa)[3])
-
-# build the column indices for each element: the population
-c_ind = rep(1:dim(Mb_per_Pa)[3], each = dim(Mb_per_Pa)[1])
-
-# make element names
-colnames(out_fall) = paste0("Mb_per_Pa[", r_ind, ",", "1", ",", c_ind, "]")
-colnames(out_spring) = paste0("Mb_per_Pa[", r_ind, ",", "2", ",", c_ind, "]")
-
-out = cbind(out_fall, out_spring)
-
-# drop out those that have NA values (first k_max years)
+    Mb_per_Pa_i = Mb_i[,,o_nor,]/Pa_i
+    list(
+      fall = as.numeric(Mb_per_Pa_i[,i_fall,]),
+      spring = as.numeric(Mb_per_Pa_i[,i_spring,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Mb), g)
+
+  # convert these to their own matrices for easier element construction
+  fall_out = do.call(rbind, lapply(out, function(x) x$fall))
+  spring_out = do.call(rbind, lapply(out, function(x) x$spring))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(fall_1), ncol(fall_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(fall_1), each = nrow(fall_1))
+
+  # build element names
+  colnames(fall_out) = paste0("Mb_per_Pa[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(spring_out) = paste0("Mb_per_Pa[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(fall_out, spring_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-lgr-smolt-per-parr}
+f = function() {
+  # extract posterior samples of tributary smolt and parr
   Ma = post_subset(post, "^Ma[", matrix = TRUE)
@@
 
-# for each posterior sample, calculate survival from parr to lgr smolt by LH type
-out_fall = out_spring = NULL
-
-for (i in 1:nrow(Ma)) {
+  # perform basic operations for one iteration -- for making dimension names later
+  Ma_1 = array_format(Ma[1,])
+  Pa_1 = array_format(Pa[1,])
+  Ma_per_Pa_1 = Ma_1[,,o_nor,]/Pa_1
+  fall_1 = Ma_per_Pa_1[,i_fall,]
+  spring_1 = Ma_per_Pa_1[,i_spring,]
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
     Ma_i = array_format(Ma[i,])
     Pa_i = array_format(Pa[i,])
-
-  Ma_per_Pa = Ma_i[,,1,]/Pa_i
-
-  out_fall = rbind(out_fall, as.numeric(Ma_per_Pa[,1,]))
-  out_spring = rbind(out_spring, as.numeric(Ma_per_Pa[,2,]))
-}
-
-# build the row indices for each element: the year
-r_ind = rep(1:dim(Ma_per_Pa)[1], dim(Ma_per_Pa)[3])
-
-# build the column indices for each element: the population
-c_ind = rep(1:dim(Ma_per_Pa)[3], each = dim(Ma_per_Pa)[1])
-
-# make element names
-colnames(out_fall) = paste0("Ma_per_Pa[", r_ind, ",", "1", ",", c_ind, "]")
-colnames(out_spring) = paste0("Ma_per_Pa[", r_ind, ",", "2", ",", c_ind, "]")
-
-out = cbind(out_fall, out_spring)
-
-# drop out those that have NA values (first k_max years)
+    Ma_per_Pa_i = Ma_i[,,o_nor,]/Pa_i
+    list(
+      fall = as.numeric(Ma_per_Pa_i[,i_fall,]),
+      spring = as.numeric(Ma_per_Pa_i[,i_spring,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ma), g)
+
+  # convert these to their own matrices for easier element construction
+  fall_out = do.call(rbind, lapply(out, function(x) x$fall))
+  spring_out = do.call(rbind, lapply(out, function(x) x$spring))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(fall_1), ncol(fall_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(fall_1), each = nrow(fall_1))
+
+  # build element names
+  colnames(fall_out) = paste0("Ma_per_Pa[", y_ind, ",", "1", ",", j_ind, "]")
+  colnames(spring_out) = paste0("Ma_per_Pa[", y_ind, ",", "2", ",", j_ind, "]")
+
+  # combine
+  out = cbind(fall_out, spring_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
-
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-nor-lgr-smolt-aggregate}
+f = function() {
   # extract smolt at LGR
-Ma = post_subset(post, "^Ma[", matrix = TRUE)
-
-# for each posterior sample, calculate the total aggregate return
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ma)) {
-  Ma_i = array_format(Ma[i,])
-  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
-  hor = Ma_i[,2,2,]
-
-  out_nor = rbind(out_nor, rowSums(nor))
-  out_hor = rbind(out_hor, rowSums(hor))
-}
-
-# build the indices for each element: the year
-r_ind = 1:nrow(nor)
-
-# make element names
-colnames(out_nor) = paste0("Ma_aggregate[", r_ind, ",", "1", "]")
-colnames(out_hor) = paste0("Ma_aggregate[", r_ind, ",", "2", "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+  Ma_tot = post_subset(post, "^Ma_tot[", matrix = TRUE)
+
+  # perform basic operations for one iteration -- for making dimension names later
+  Ma_tot_1 = array_format(Ma_tot[1,])
+  Ma_nor_1 = rowSums(Ma_tot_1[,o_nor,])
+  Ma_hor_1 = rowSums(Ma_tot_1[,o_hor,])
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
+    Ma_tot_i = array_format(Ma_tot[i,])
+    list(
+      nor = rowSums(Ma_tot_i[,o_nor,]),
+      hor = rowSums(Ma_tot_i[,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ma_tot), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = 1:length(Ma_nor_1)
+
+  # build element names
+  colnames(nor_out) = paste0("Ma_aggregate[", y_ind, ",", "1", "]")
+  colnames(hor_out) = paste0("Ma_aggregate[", y_ind, ",", "2", "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```
@@
 ```{r add-Ra-aggregate}
-# extract spawners returning to tributary
-Ra = post_subset(post, "^Ra[", matrix = TRUE)
-
-# for each posterior sample, calculate the total aggregate return
-out_nor = out_hor = NULL
-for (i in 1:nrow(Ra)) {
-  Ra_i = array_format(Ra[i,])
-  nor = Ra_i[,1,1,] + Ra_i[,2,1,] + Ra_i[,3,1,]
-  hor = Ra_i[,1,2,] + Ra_i[,2,2,] + Ra_i[,3,2,]
-  tot = nor + hor
-
-  out_nor = rbind(out_nor, rowSums(nor))
-  out_hor = rbind(out_hor, rowSums(hor))
-}
-
-# build the indices for each element: the year
-r_ind = 1:nrow(nor)
-
-# make element names
-colnames(out_nor) = paste0("Ra_aggregate[", r_ind, ",", "1", "]")
-colnames(out_hor) = paste0("Ra_aggregate[", r_ind, ",", "2", "]")
-out = cbind(out_nor, out_hor)
-
-# drop out those that have NA values (first k_max years)
+f = function() {
+  # extract smolt at LGR
+  Ra_tot = post_subset(post, "^Ra_tot_org[", matrix = TRUE)
+
+  # perform basic operations for one iteration -- for making dimension names later
+  Ra_tot_1 = array_format(Ra_tot[1,])
+  Ra_nor_1 = rowSums(Ra_tot_1[,o_nor,])
+  Ra_hor_1 = rowSums(Ra_tot_1[,o_hor,])
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
+    Ra_tot_i = array_format(Ra_tot[i,])
+    list(
+      nor = rowSums(Ra_tot_i[,o_nor,]),
+      hor = rowSums(Ra_tot_i[,o_hor,])
+    )
+  }
+
+  # apply to each posterior sample
+  out = lapply(1:nrow(Ra_tot), g)
+
+  # convert these to their own matrices for easier element construction
+  nor_out = do.call(rbind, lapply(out, function(x) x$nor))
+  hor_out = do.call(rbind, lapply(out, function(x) x$hor))
+
+  # build element indices: the year
+  y_ind = 1:length(Ra_nor_1)
+
+  # build element names
+  colnames(nor_out) = paste0("Ra_aggregate[", y_ind, ",", "1", "]")
+  colnames(hor_out) = paste0("Ra_aggregate[", y_ind, ",", "2", "]")
+
+  # combine
+  out = cbind(nor_out, hor_out)
+
+  # drop out those that have NA values
   na_ind = which(!is.na(out[1,]))
-out = out[,na_ind]
-
-# combine this with the rest of the posterior samples
-post = post_bind(post, out)
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
 ```

### 2023-03-01 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run
Update egg-to-parr surv output plots
* Include a set of plots showing survival as a time series
* Include set of plots showing fitted beverton holt on the scale of egg-to-parr survival vs. egg abundance
* Discard old "parr per egg" plot set
* Discard parr per spawner plot set

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Egg-to-Parr Survival {.tabset .tabset-pills}
 
-## Beverton-Holt
+## Survival Time Series
 
-All red components are posterior summaries (medians and 95% credible intervals).
-The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.
+```{r phi_E_Pb-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+## Survival vs. Total Egg Production
+
+This is the scale the Beverton-Holt recruitment function is estimated on.
+
+```{r egg-surv-vs-eggs, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # extract posterior samples of the BH productivity and capacity parameters
+  alpha = post_subset(post, sub_index("alpha[pop]", pop = j), matrix = TRUE)
+  beta = post_subset(post, sub_index("beta[pop]", pop = j), matrix = TRUE)
+
+  # extract posterior summaries of total egg production by brood year
+  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
+
+  # extract posterior summaries egg-to-parr survival by brood year
+  phi_E_Pb = post_summ(post, sub_index("^phi_E_Pb[year,pop]", pop = j, year = ts_yrs))
+
+  # predict egg-to-parr survival along a sequence of egg abundances
+  E_pred = seq(0, max(E[5,]), length = 30)
+  phi_E_Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) 1/(1/alpha[i,] + E_pred/beta[i,])))
+  colnames(phi_E_Pb_pred) = paste0("phi_E_Pb_pred[", 1:length(E_pred), "]")
+  phi_E_Pb_pred = post_convert(cbind(postpack:::id_mat(post), phi_E_Pb_pred))
+  phi_E_Pb_pred = post_summ(phi_E_Pb_pred, "Pb_pred")
+
+  # graphical parameters
+  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+
+  # empty plot
+  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, phi_E_Pb[5,], phi_E_Pb_pred[5,]),
+       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
+
+  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
+  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+  axis(side = 2, at = y_ticks)
+
+  # draw fitted relationship
+  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred[4,], rev(phi_E_Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
+  lines(phi_E_Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
+  lines(phi_E_Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
+  lines(phi_E_Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
+
+  # draw state pairs + uncertainty
+  segments(E[4,], phi_E_Pb[3,], E[5,], phi_E_Pb[3,], col = alpha("red", 0.5))
+  segments(E[3,], phi_E_Pb[4,], E[3,], phi_E_Pb[5,], col = alpha("red", 0.5))
+  points(phi_E_Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+## Parr vs. Total Egg Production
+
+Parr abundance is the product of egg-to-parr survival and total egg production; in this way we can back-out the standard Beverton-Holt function.
 
@@
 ```
-
-## Parr per Egg
-
-This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases.
-The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.
-
-```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))
-
-  # max survival
-  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_E["mean",] ~ E["mean",],
-       ylim = c(0, 1),
-       xlim = c(0, max(E["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])
-
-  # x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
-  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
-  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
-  abline(h = alpha["mean",], lwd = 2, col = "red")
-  box()
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
-```
-
-## Parr per Spawner
-
-This figure is identical to above, but shows parr production per spawner instead of per egg.
-
-```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # extract posterior summaries of total spawners by brood year
-  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # conversion rates
-  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))
-
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
-  # empty plot
-  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
-       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
-       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1)
-
-  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
-  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
-```

### 2023-03-09 03-post-process/compare-sim-to-obs.Rmd
Remove unneeded content from sim-v-obs

@@
 
-# param = "phi_O0_Rb_BON[year,origin,pop]"
-# obs_y_use = obs_sar_y
-# sim_y_use = sim_sar_y
-# origin = 1
-# main = "main"
-
 ts_plot = function(param, main = NULL, obs_y_use = obs_y, sim_y_use = sim_y, ...) {
@@
   sim_vals = post_subset(post, sub_index(param, year = sim_y_use, ...), matrix = TRUE)
-  # obs_vals = post_summ(post, sub_index(param, year = obs_y_use, pop = 1, origin = 1))
-  # sim_vals = post_subset(post, sub_index(param, year = sim_y_use, pop = 1, origin = 1), matrix = TRUE)
 

### 2023-03-09 03-post-process/compare-sim-to-obs.Rmd
Fix year problem in sim-v-obs TS plots
This was legacy code left over from the time when I was using the initialization strategy that required 5 empty years at the start of the time series. The new approach needs only 1 empty year (to store residuals from AR(1) year 0)

@@
 isim = sample(1:post_dim(post, "saved"), n_sim_draw, replace = FALSE)
-obs_y = 6:jags_data$ny_obs
-obs_sar_y = 6:(jags_data$ny_obs-jags_data$kmax)
+obs_y = 2:jags_data$ny_obs
+obs_sar_y = 2:(jags_data$ny_obs-jags_data$kmax)
 sim_sar_y = (jags_data$ny_obs-jags_data$kmax+1):(jags_data$ny-jags_data$kmax)
@@
   par(mar = c(1,2,2,1), mgp = c(2,0.35,0), tcl = -0.15)
-  plot(obs_vals["mean",] ~ obs_y_use, type = "n", xlim = range(6, sim_y_use),
+  plot(obs_vals["mean",] ~ obs_y_use, type = "n", xlim = range(obs_y_use, sim_y_use),
        ylim = range(obs_vals[c("2.5%", "97.5%"),], sim_vals[isim,]), xaxt = "n", xlab = "", ylab = "", main = main)
   usr = par("usr"); at_x = axisTicks(usr[1:2], log = FALSE)
-  at_x = c(6, at_x[!(at_x %in% c(0, 6, max(sim_y_use)))], max(sim_y_use))
+  at_x = c(2, at_x[!(at_x %in% c(0, 6, max(sim_y_use)))])
   axis(side = 1, at = at_x, labels = all_yrs[at_x])

### 2023-03-10 03-post-process/compare-sim-to-obs.Rmd
Use geometric mean for sim-v-obs ratio summaries
See #168 for complete details

@@
 
+```{r geomean fn}
+geomean = function(x) exp(mean(log(x)))
+```
+
 ```{r dim_names fn}
@@
 ```{r ratio_plot fn}
-ratio_plot = function(ratios, line_y, ...) {
+ratio_plot = function(ratios, line_y, pt_fn = mean, ...) {
 
@@
   summs = apply(ratios, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE))
+
+  # replace median with output of supplied point estimate function
+  summs["50%",] = apply(ratios, 2, pt_fn)
 
@@
   par(mfrow = c(1,3), oma = c(0,2,2,0))
-  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", line_y = 1)
-  ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", line_y = 1)
-  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", line_y = 0)
+  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", pt_fn = geomean, line_y = 1)
+  ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", pt_fn = geomean, line_y = 1)
+  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", pt_fn = mean, line_y = 0)
   mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Ratio (Sim:Obs)")
@@
 ```{r summarize_ratios fn}
+# function to summarize a matrix of ratios
+col_summs = function(x) {
+  c(cv = geomean(x[,"cv"]), mean = geomean(x[,"mean"]), acf = mean(x[,"acf"]))
+}
+
 summarize_ratios = function(x, Class, Type) {
-  xsumm = as.data.frame(t(apply(x[,"sim-v-obs",,], 3, colMeans)))
+  xsumm = as.data.frame(t(apply(x[,"sim-v-obs",,], 3, col_summs)))
   xsumm = cbind(Class = Class, Type = Type, ID = rownames(xsumm), xsumm); rownames(xsumm) = NULL
@@
 
-These plots show summaries of a quantity in the model:
-
-1. **Inter-annual CV**: measures how variable the quantity is among years
-2. **Inter-annual mean**: measures the central tendency of the quantity across years
+These plots show the distribution of a quantity in the model:
+
+1. **Inter-annual CV**: measures how variable the quantity is among years (uses arithmetic mean)
+2. **Inter-annual mean**: measures the central tendency of the quantity across years (uses arithmetic mean)
 3. **Lag-1 autocorrelation**: measures whether consecutive years are independent
@@
 These summary statistics were calculated for each posterior sample.
-In all plots, the cross mark represents the posterior median, the thick bar represents the central 50% of posterior samples, and the thin bar represents the central 95% of posterior samples.
+In estimate plots, the cross mark represents the posterior median, the thick bar represents the central 50% of posterior samples, and the thin bar represents the central 95% of posterior samples.
+The ratio plots have the same interpretation, except the cross mark represents the posterior geometric mean for the "CV" and "Mean" panels, and the posterior arithmetic mean for the "ACF" panels.
+The geometric mean is used to summarize central tendency of ratios across posterior samples because it is more appropriate for calculations based on multiplicative, rather than additive, variability (see issue [#168](https://github.com/bstaton1/GR-sslcm/issues/168) for more details).
 
@@
 
-These tables summarize the mean ratio values shown in the plots above, and are intended to be a quick visual for identifying areas where the simulated outcomes are systematically different in some way (central tendency, interannual variability, or temporal autocorrelation) from the observed outcomes.
-The number in each cell represents the posterior mean value of:
+These tables summarize the ratio values shown in the plots above, and are intended to be a quick visual for identifying areas where the simulated outcomes are systematically different in some way (central tendency, interannual variability, or temporal autocorrelation) from the observed outcomes.
+The number in each cell represents the posterior mean (geometric for across year mean and across year CV; arithmetic for lag-1 autocorrelation) value of:
 
 * **Across Year Mean** is the ratio `mean(simulated years)/mean(observed years)`. Values greater than 1 indicate the value in simulated years is larger in magnitude than in observed years.
-* **Across Year CV** is the ratio `cv(simulated years)/cv(observed years)`. Values greater than 1 indicate the variability from one year to the next is larger larger than in observed years.
+* **Across Year CV** is the ratio `cv(simulated years)/cv(observed years)`. Values greater than 1 indicate the variability from one year to the next is larger than in observed years.
 * **Lag-1 Autocorrelation** is the difference `acf(simulated years) - acf(observed years)`.

### 2023-03-10 03-post-process/output-plots-children/05-length-based-values.Rmd
Add year labels to scatter plots in output-plots

@@
   segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
+  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
   segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
-
+  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
 mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
 ```
@@
   segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
   segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }

### 2023-03-13 03-post-process/output-plots-children/02-mcmc-diags.Rmd

@@
 L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
+L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
+base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
 match = sub_index(base, pop = ".")

### 2023-03-13 03-post-process/output-plots-children/10-noise-term-diags.Rmd

@@
   # calculate posterior summaries of standardized qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975, 0.25, 0.75))))
 
@@
   # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
+  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)
 
@@
   # calculate posterior summaries of qresidual time series
-  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975, 0.25, 0.75))))
 
@@
   # ie., insert missing values
-  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
+  empty = matrix(NA, nrow = 7, ncol = length(obs_qresid_yrs))
   empty[,y_ind] = qresid
   qresid = empty[,observable]
-  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
+  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%", "25%", "75%")
   empty_names = rep(NA, length(obs_qresid_yrs))

### 2023-03-13 03-post-process/compare-sim-to-obs.Rmd

@@
     label: "Scenario"
-    value: "tack-on-all-priors"
+    value: "base"
     input: text

### 2023-03-13 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

@@
   segments(E[3,], phi_E_Pb[4,], E[3,], phi_E_Pb[5,], col = alpha("red", 0.5))
-  points(phi_E_Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  points(phi_E_Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(phi_E_Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
   segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  points(Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
   segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
+  points(E["mean",] ~ Sa_tot["mean",], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(E["mean",] ~ Sa_tot["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+
   abline(c(0, 1000), lty = 1)

### 2023-03-13 03-post-process/output-plots.Rmd

@@
     label: "Include JAGS Code/Data?"
+    value: TRUE
+  include_post_v_prior:
+    label: "Include Posterior vs. Prior Densities?"
     value: TRUE
@@
 ```
+
+```{r post-v-prior, child = "output-plots-children/13-post-vs-prior.Rmd", eval = params$include_post_v_prior}
+```

### 2023-03-13 02-model/model-code.R
Use power function in DD growth JAGS code

@@ -255,7 +255,7 @@ jags_model_code = function() {
     Lphi_E_Pb[y,1:nj] ~ dmnorm.vcov(logit(1/(1/alpha[1:nj] + E[y,1:nj]/beta[1:nj])), Sig_Lphi_E_Pb[1:nj,1:nj])
 
     # density-dependent length at end of summer
-    lL_Pb[y,1:nj] ~ dmnorm.vcov(omega0[1:nj] + omega1[1:nj] * ((E[y,1:nj]/E_scale)/wul[1:nj]), Sig_lL_Pb[1:nj,1:nj])
+    lL_Pb[y,1:nj] ~ dmnorm.vcov(omega0[1:nj] + omega1[1:nj] * log((E[y,1:nj]/E_scale)/wul[1:nj]), Sig_lL_Pb[1:nj,1:nj])
     
     # LH apportionment
     Lpi1[y,1:nj] ~ dmnorm.vcov(logit(mu_pi[i_fall,1:nj]), Sig_Lpi[1:nj,1:nj])
@@ -828,8 +828,8 @@ jags_model_code = function() {
       Lphi_E_Pb_qresid[y,j] <- pnorm(Lphi_E_Pb[y,j], logit(1/(1/alpha[j] + E[y,j]/beta[j])), 1/sig_Lphi_E_Pb[j]^2)
 
       # summer mean length
-      lL_Pb_resid[y,j] <- lL_Pb[y,j] - (omega0[j] + omega1[j] * ((E[y,j]/10000)/wul[j]))
-      lL_Pb_qresid[y,j] <- pnorm(lL_Pb[y,j], omega0[j] + omega1[j] * ((E[y,j]/10000)/wul[j]), 1/sig_lL_Pb[j]^2)
+      lL_Pb_resid[y,j] <- lL_Pb[y,j] - (omega0[j] + omega1[j] * log((E[y,j]/10000)/wul[j]))
+      lL_Pb_qresid[y,j] <- pnorm(lL_Pb[y,j], omega0[j] + omega1[j] * log((E[y,j]/10000)/wul[j]), 1/sig_lL_Pb[j]^2)
       
       # proportion of summer parr that become fall migrants
       Lpi_resid[y,j] <- logit(pi[y,i_fall,j]) - logit(mu_pi[i_fall,j])

### 2023-03-13 100-math-description/GR-sslcm-math-description.Rmd
Use power function in DD growth math doc
Update math doc to account for 50:50 sex ratio
See #167, should have included this in #171

@@
 \begin{equation}
-E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k,j} \cdot f_{k}
+E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k} \cdot f_{k}
 (\#eq:get-E)
@@
 
-We calculated the proportion of spawners at age that are female ($\Omega_{k,j}$) from carcass survey data and averaged across years and fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
+We assumed that spawners age-4 or age-5 were 50% female and age-3 spawners were all male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data) and estimated fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
 We supplied both quantities to the model assuming no error or inter-annual variability.
@@
 It is well known that juvenile survival is related to body size \todo{Insert references about survival being related to size} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
-We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:
+We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a power function of egg density, which expressed on the logarithmic scale was:
 
 \begin{equation}
-\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \frac{E_{y,j}}{\mathrm{WUL}_j}
+\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \log\left(\frac{E_{y,j}}{\mathrm{WUL}_j}\right)
 (\#eq:get-L-Pb-dot)

### 2023-03-13 03-post-process/output-plots-children/05-length-based-values.Rmd

@@
   pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
+    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
     names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")

### 2023-03-14 02-model/fit-model.R
Add AR(1) process on egg-to-parr surv in model

@@ -239,7 +239,7 @@ toggle_data_diagnostics(do_lppd, do_pp_check)
 # nodes to monitor for any model
 jags_params = c(
   # reproduction
-  "alpha", "beta", "Sig_Lphi_E_Pb", "phi_E_Pb", "lambda", "sig_lbeta",
+  "alpha", "beta", "Sig_Lphi_E_Pb", "phi_E_Pb", "lambda", "sig_lbeta", "kappa_phi_E_Pb", "phi_E_Pb_dot",
 
   # length-related quantities
   "omega0", "omega1", "Sig_lL_Pb", 

### 2023-03-14 02-model/model-code.R

@@ -2,17 +2,29 @@ jags_model_code = function() {
   
   ### PRIORS: capacity vs. weighted usable habitat length relationship ###
   lambda ~ dnorm(0, 1e-8) %_% T(0,)
+  lambda_pop[1:nj] <- beta[1:nj]/wul[1:nj]
   sig_lbeta ~ dunif(0, 5)
   
   for (j in 1:nj) {
     ### PRIORS: RECRUITMENT FUNCTION ###
     # total egg production to aggregate parr recruitment function
+    # max egg-to-parr survival
     alpha[j] ~ dbeta(alpha_prior[1], alpha_prior[2])
+    
+    # max parr recruitment
     lbeta[j] ~ dnorm(log(lambda * wul[j]), 1/sig_lbeta^2) %_% T(,15) # log capacity. bound to prevent nonsensically large draws
     beta[j] <- exp(lbeta[j])
+    
+    # AR(1) coefficient for egg-to-parr survival
+    kappa_phi_E_Pb[j] ~ dunif(-0.99,0.99)
+    
+    # SD of process white noise on egg-to-parr survival
     sig_Lphi_E_Pb[j] ~ dt(0,1/sig_Lphi_E_Pb_prior^2,1) %_% T(0,dt_upr)
-    lambda_pop[j] <- beta[j]/wul[j]  # derived pop-specific lambda, includes process noise in regression
-
+    
+    # SD of process noise on egg-to-parr survival for year 0
+    sig_Lphi_E_Pb_init[j] <- sqrt(sig_Lphi_E_Pb[j]^2/(1 - kappa_phi_E_Pb[j]^2))
+    
+    ### PRIORS: DENSITY-DEPENDENT GROWTH ###
     # length at end of summer vs. eggs relationship: density-dependent spring/summer growth
     omega0[j] ~ dnorm(0, 1e-3)  # intercept
     omega1[j] ~ dnorm(0, 1e-3)  # slope
@@ -151,8 +163,11 @@ jags_model_code = function() {
   # construct all population covariance matrices
   for (i in 1:nj) {
     for (j in 1:nj) {
-      # covariance matrix of parr recruitment
[…]

### 2023-03-14 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Add output for new params in output plots
* new kappa parameters
* year 0 residual

@@
 L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Initial Residual", "Among-pop Correlation", "Realized")
+match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "Lphi_E_Pb_resid[1,", "rho_Lphi_E_Pb", "^phi_E_Pb[")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))

### 2023-03-14 100-math-description/GR-sslcm-math-description.Rmd
Update math doc to include AR(1) egg to parr surv

@@
 We modeled realized (i.e., with process noise) egg-to-parr survival as a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) from eq.
-\@ref(eq:get-phi-E-Pb-dot) with covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
+\@ref(eq:get-phi-E-Pb-dot).
+Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \rightarrow P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
 \@ref(eq:generic-Sigma4by4)):
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
+\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right) + \boldsymbol{\kappa}^{E \rightarrow P^{b}}_{1:n_j} \cdot \left[\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y-1,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y-1,1:n_j}\right)\right], \Sigma_{\phi^{E \rightarrow P^{b}}} \right\}
 (\#eq:phi-E-Pb-random)

### 2023-03-14 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

@@
 
-## Survival Time Series
+## Survival Time Series {.tabset .tabset-pills}
+
+These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.
+
+### Realized Alone
+
+Just the realized time series shown.
 
@@
                main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+### Realized & BH
+
+The blue shows the time series with variability explained only by Beverton-Holt dynamics.
+
+```{r phi_E_Pb_dot-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+
+  # draw on the posterior time series that includes BH prediction only
+  dot_col = "royalblue"
+  dot = post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", pop = j, year = ts_yrs))
+  polygon(x = c(all_yrs[ts_yrs], rev(all_yrs[ts_yrs])),
+          y = c(dot["2.5%",], rev(dot["97.5%",])),
+          col = scales::alpha(dot_col, 0.15), border = NA)
+  lines(dot["mean",] ~ all_yrs[ts_yrs], col = dot_col, lwd = 2)
+  lines(dot["2.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
+  lines(dot["97.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+### Realized & [BH + AR(1)]
+
+The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.
+
+```{r phi_E_Pb_dot2-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+
+  # draw on the posterior time series that includes BH prediction and the carry over residual from last year
+  dot_col = "royalblue"
+  dot = post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", pop = j, year = ts_yrs))
+  polygon(x = c(all_yrs[ts_yrs], rev(all_yrs[ts_yrs])),
+          y = c(dot["2.5%",], rev(dot["97.5%",])),
+          col = scales::alpha(dot_col, 0.15), border = NA)
+  lines(dot["mean",] ~ all_yrs[ts_yrs], col = dot_col, lwd = 2)
+  lines(dot["2.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
+  lines(dot["97.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
 }

### 2023-03-14 03-post-process/output-plots-children/11-param-summaries.Rmd

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Parameter Summaries {.tabset .tabset-dropdown}
@@
 ```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
+par(mfrow = c(1,5))
 my_boxplot("^alpha[.]$", "Productivity")
@@
 my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
+my_boxplot("^kappa_phi_E_Pb[.]$", "AR(1) Coef.")
 my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)

### 2023-03-16 02-model/fit-model.R
Implement toggle_HOR_Rb_init() function

@@ -163,6 +163,12 @@ toggle_rho_estimation("rho_Lphi_Sb_Sa")    # pre-spawn survival process noise
 # toggle on/off the calculation of pp checks and lppd
 toggle_data_diagnostics(do_lppd, do_pp_check)
 
+# toggle Rb_init for HOR fish
+# (this is only for the sim vs. obs)
+if (do_sim_vs_obs) {
+  toggle_HOR_Rb_init()
+}
+
 ##### STEP 3: SELECT NODES TO MONITOR #####
 
 # nodes to monitor for any model

### 2023-03-29 03-post-process/output-plots.Rmd
Choose which output content to show
Turn off anything that will break with new model

@@
     label: "Scenario"
-    value: "base"
+    value: "scaled-wishart"
     input: text
@@
     label: "Include MCMC Diagnostic Output?"
-    value: TRUE
+    value: FALSE
   include_fit_to_data:
@@
     label: "Include Process Model Correlation Output?"
-    value: TRUE
+    value: FALSE
   include_noise_term_diags:
     label: "Include Noise Term Diagnostic Output?"
-    value: TRUE
+    value: FALSE
   include_param_summaries:
     label: "Include Posterior Boxplot Output?"
-    value: TRUE
+    value: FALSE
   include_jags_info:
@@
     label: "Include Posterior vs. Prior Densities?"
-    value: TRUE
+    value: FALSE
 editor_options: 

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Update how upper triangle of rho_mat is excluded
From MCMC diagnostics

@@
 
-# discard duplicate correlation terms: all rho parameters for a given process are equal
-all_rho = match_params(post, "^rho")
-rho_keep = match_params(post, "^rho_.+[2,1")
+# discard any node that simply track prior densities, no need to MCMC diagnose them
+pr_rm = c(match_params(diag_post, "_pr["), match_params(diag_post, "_pr$"))
+diag_post = suppressMessages(post_remove(diag_post, pr_rm, ask = FALSE))
+```
+
+```{r discard-rho-upper-tri}
+# duplicate correlation parameters do not need to have MCMC diagnostics ran
+# those on the diagonal have already been discarded 
+# this code discards those in the upper triangle 
+rho_params = match_params(diag_post, "rho", type = "base_only")
+rho_keep = unlist(lapply(rho_params, function(x) paste0(x, vcov_inds)))
+all_rho = match_params(diag_post, "^rho", type = "base_index")
 rho_discard = all_rho[!(all_rho %in% rho_keep)]

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Discard Yr0 resids from MCMC diagnostics
Must be forced to zero in this parameterization unfortunately

JAGS returns "cannot find appropriate sample for Tau" if you try to invert it, insert the sig_init parameter, then reinvert for usage to inform the yr0 resid. I've had to do this before, and am not concerned with it affecting any model inference

@@
 L1 = "Egg-to-Parr Survival"
-L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Initial Residual", "Among-pop Correlation", "Realized")
-match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "Lphi_E_Pb_resid[1,", "rho_Lphi_E_Pb", "^phi_E_Pb[")
+L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Among-pop Correlation", "Realized")
+match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
@@
 L1 = "Misc Ocean Survival"
-L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
-base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
+L2 = c("Yr1 NOR:HOR Scaler", "Yr 1 AR(1) Coefficient")
+base = c("delta_O0_O1[pop]", "kappa_phi_O0_O1[pop]")
 match = sub_index(base, pop = ".")

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Update MCMC diagnostics for sigma and rho params
To reflect (a) the Tau parameterization and (b) the simplification of common matrices for origins/LH types where applicable

@@
 L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
+L2 = c("Intercept", "Slope", "Realized")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
@@
 L1 = "Overwinter Survival"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
+L2 = c("Intercept", "Slope", "Realized")
+base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Overwinter survival: Process variance
+L1 = "Overwinter Survival"
+L2 = c("Process SD", "Among Pop. Correlation")
+base = c("sig_Lphi_Pa_Mb", "rho_Lphi_Pa_Mb")
+tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
 tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
@@
 L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
-base = c("tau0", "tau1", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
+L2 = c("Intercept", "Slope", "Realized")
+base = c("tau0", "tau1", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
 match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
@@
 L1 = "Migration Survival (Trib to LGR)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
+L2 = c("Mean", "Realized")
+base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "phi_Mb_Ma[year,LH_type,origin,pop]")
 match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# trib to LGR Migration survival: Process variance
+L1 = "Migration Survival (Trib to LGR)"
+L2 = c("Process SD", "Among Pop. Correlation")
+base = c("sig_Lphi_Mb_Ma", "rho_Lphi_Mb_Ma")
+tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
 tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
@@
 L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
+L2 = c("Mean", "Realized")
+base = c("mu_psi_O1[origin,pop]", "^psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L1 = "Pr(Mature at Age-3)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[pop,origin]", "rho_Lpsi_O1[.,.,origin]", "^psi_O1[.+,origin,pop]")
+L2 = c("Mean", "Realized")
+base = c("mu_psi_O1[origin,pop]", "^psi_O1[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
@@
 
+# Process Variance: Probability of Maturity at Age-3
+L1 = "Pr(Mature at Age-3)"
+L2 = c("Process SD", "Among-pop Correlation")
+base = c("sig_Lpsi_O1", "rho_Lpsi_O1")
+tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
 # Probability of Maturing at Age-4: NOR
 L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
+L2 = c("Mean", "Realized")
+base = c("mu_psi_O2[origin,pop]", "^psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
@@
 L1 = "Pr(Mature at Age-4)"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[pop,origin]", "rho_Lpsi_O2[.,.,origin]", "^psi_O2[.+,origin,pop]")
+L2 = c("Mean", "Realized")
+base = c("mu_psi_O2[origin,pop]", "^psi_O2[.+,origin,pop]")
 match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+
+# Process Variance: Probability of Maturity at Age-4
+L1 = "Pr(Mature at Age-4)"
+L2 = c("Process SD", "Among-pop Correlation")
+base = c("sig_Lpsi_O2", "rho_Lpsi_O2")
+tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
 tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
@@
 L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa[.+,.]")
+match = c("mu_phi_Sb_Sa", "sig_Lphi_Sb_Sa", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Add Yr2 & Yr3 ocean surv to MCMC diags again
Why not -- these aren't key parameters

@@
 # Year 2 ocean survival
-# L1 = "Year 2 Ocean Survival"
-# L2 = c("Mean")
-# base = c("mu_phi_O1_O2[origin,pop]")
-# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+L1 = "Year 2 Ocean Survival"
+L2 = c("Mean")
+base = c("mu_phi_O1_O2[origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 
 # Year 2 ocean survival
-# L1 = "Year 3 Ocean Survival"
-# L2 = c("Mean")
-# base = c("mu_phi_O2_O3[origin,pop]")
-# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
-# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
+L1 = "Year 3 Ocean Survival"
+L2 = c("Mean")
+base = c("mu_phi_O2_O3[origin,pop]")
+match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
+tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
+tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
+diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
+summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
 

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Update MCMC diagnostic text

@@
 * $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
+Values close to 1 are ideal but values greater than 1.2 should be considered not well-converged (general rules of thumb).
 * **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
+Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- Vehtari et al.
+[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggests 400 as a good rule of thumb.
 * **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.
+Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has deemed an acceptable level of imprecision.
 

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Remove MIN HOR quantities from MCMC diags
See #178

@@
 diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
+```
+
+```{r discard-MIN-HOR}
+# specify the nodes where Minam parameters aren't informed by data, and thus need no MCMC diagnostics
+discard_params = c(
+  "mu_phi_Mb_Ma[LH_type,origin,pop]",
+  "^phi_Mb_Ma[year,LH_type,origin,pop]",
+  "delta_O0_O1[pop]",
+  "mu_psi_O1[origin,pop]",
+  "^psi_O1[year,origin,pop]",
+  "mu_psi_O2[origin,pop]",
+  "^psi_O2[year,origin,pop]"
+)
+
+# replace the placeholder index names with the specific elements in question
+no_mcmc_diags_Minam = lapply(discard_params, sub_index, pop = j_min) |>
+  lapply(sub_index, LH_type = i_spring) |>
+  lapply(sub_index, origin = o_hor) |>
+  lapply(sub_index, year = ts_yrs) |>
+  lapply(unique) |>
+  unlist()
+
+# remove these nodes from the posterior samples that will have MCMC diagnostics ran
+diag_post = suppressMessages(post_remove(diag_post, params = no_mcmc_diags_Minam, ask = FALSE))
 ```
@@
 
-This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model.
+This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model (excluding those that are not informed by data, such as HOR Minam maturation or HOR smolt survival; these parameters are sampled purely for organizational purposes in the model).
 Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.

### 2023-03-31 03-post-process/output-plots-children/09-rho-params.Rmd
Update rho summary plot for SIW model

@@
-# Correlation Parameters
+---
+editor_options: 
+  chunk_output_type: console
+---
 
-```{r rho_plot, fig.width = 6, fig.height = 7}
-# get the names of all rho parameters
-# these are elements of a correlation matrix
-# but because the rho term is the same for all population pairs, it is sufficient 
-# to summarize just one element from each matrix
-rho_params = c(
-  match_params(post, "rho_.+[2,1]"),
-  match_params(post, "rho_.+[2,1,1]"),
-  match_params(post, "rho_.+[2,1,2]")
+# Correlation Parameters {.tabset .tabset-pills}
+
+## Summary Across Processes
+
+```{r summarize-rho-means}
+# get posterior summaries of the mean correlation across all pop pairs
+# for each process separately
+rho_params1 = match_params(post, "rho", type = "base_only")
+rho_params2 = match_params(post, "rho_.+_pr", type = "base_only")
+rho_params = rho_params1[!(rho_params1 %in% rho_params2)]
+f = function(p) {
+  x = rowMeans(post_subset(post, p, matrix = TRUE))
+  c(mean = mean(x), sd = sd(x), quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))
+}
+rho_mean_out = t(sapply(rho_params, f))
+rho_mean_out = rho_mean_out[order(rho_mean_out[,"mean"]),]
+
+# assign names to the different rho parameters
+rho_labels = c(
+  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
+  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
+  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
+  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
+  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
+  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
+  "rho_lL_Pb" = "Mean Parr Length",
+  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
+  "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
+  "rho_Lphi_Rb_Ra" = "BON -> UGR Survival",
+  "rho_Lpi" = "Pr(Fall Migrant)",
+  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
 )
+```
 
-# calculate/format posterior summaries
-rho_summs = t(post_summ(post, rho_params, probs = c(0.025, 0.25, 0.5, 0.75, 0.975)))
-rho_summs = as.data.frame(rho_summs)
-rho_summs = cbind(param = rownames(rho_summs), rho_summs)
-rownames(rho_summs) = NULL
+Posterior summaries of the correlation matrices for all process model components that used a multivariate (logit- or log-) normal distribution model inter-annual variability.
+All processes assumed covariance among population pairs except "LGR to Ocean" and "BON to LGR", which had equal values for all populations but covaried across origin types.
 
-# make prettier names for each term
-rho_names = c(
-  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
-  "rho_lL_Pb[2,1]" = "Summer Mean Length",
-  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
-  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
-  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
-  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
-  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
-  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
-  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
-  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
-  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
-  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
-  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
-  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
-  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
-  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
-  )
-rho_summs$name = rho_names[rho_summs$param]
+Notation:
 
-# reorder by decreasing mean correlation
-rho_summs = rho_summs[order(rho_summs$mean, decreasing = TRUE),]
-at_y = nrow(rho_summs):1
+* Blue: Mean of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
+* Red: Individual population pairs ("+" = posterior mean, lines = 50% CRI)
+* Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness)
 
-# use different colors for correlations that are between origins vs. between populations
-col = ifelse(rho_summs$param %in% c("rho_Lphi_Ma_O0[2,1]", "rho_Lphi_Rb_Ra[2,1]"), "red", "black")
+```{r rho-mean-plot, fig.width = 5, fig.height = 5}
+# plot to show summary of correlation parameters across processes
+# mean across pairs shown as blue
+# individual population pairs shown as red
 
-# make the plot
-par(lend = "square", mar = c(3,10,1,1), tcl = -0.15, mgp = c(1.5,0.35,0))
-plot(1,1, type = "n", xlim = c(-1,1), ylim = c(1,nrow(rho_summs)), xlab = "Correlation", ylab = "", yaxt = "n")
+# set up empty plotting region
+par(mar = c(2,8,1,1), cex.axis = 0.8, lend = "square", tcl = -0.15, mgp = c(2,0.35,0), yaxs = "i", lend = "square", ljoin ="mitre")
+mp = barplot(rho_mean_out[,"mean"], 
+             horiz = TRUE, xlim = c(-1,1),
+             names.arg = rho_labels[rownames(rho_mean_out)],
+             las = 1, col = "white", border = "white")
+usr = par("usr")
+
+# draw on the prior distribution
+rho_pr = post_summ(post, "rho_Lphi_Ma_O0_pr[2,1]", probs = c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975))
+rect(rho_pr["2.5%",], usr[3], rho_pr["97.5%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
+rect(rho_pr["10%",], usr[3], rho_pr["90%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
+rect(rho_pr["25%",], usr[3], rho_pr["75%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
 abline(v = 0, lty = 2)
-segments(rho_summs$`2.5%`, at_y, rho_summs$`97.5%`, col = col)
-segments(rho_summs$`25%`, at_y, rho_summs$`75%`, lwd = 4, col = col)
-points(y = at_y, x = rho_summs$mean, cex = 1, pch = 3, lwd = 2, col = col)
-axis(side = 2, at = at_y, labels = rho_summs$name, las = 2, cex.axis = 0.8)
-abline(h = at_y - 0.5, col = "grey")
-legend("topleft", legend = c("Across Populations", "Across Origins"), text.col = c("black", "red"), bty = "n", cex = 0.8)
+
+# param = rownames(rho_mean_out)[4]
+# at_mp = mp[4,]
+pop_rhos = function(param, at_mp) {
+
+  # if the process is not one of the hydropower migration survival ones, do this
+  # those processes are correlated across origins, because all populations share the same values each year
+  if (!(param %in% c("rho_Lphi_Ma_O0", "rho_Lphi_Rb_Ra"))) {
+    x = post_summ(post, paste0(param, vcov_inds), probs = c(0.1, 0.25, 0.75, 0.9))
+    y = at_mp + runif(6, -0.4, 0.4)
+    points(y ~ x["mean",], col = "salmon", pch = 3, lwd = 1.5)
+    segments(x["25%",], y, x["75%",], y, col = scales::alpha("salmon", 0.5))
+  } 
+}
+
+junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = scales::alpha("royalblue", 0.55))
+segments(rho_mean_out[,"10%"], mp, rho_mean_out[,"90%"], mp, col = scales::alpha("royalblue", 0.55))
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "royalblue", lwd = 3)
+
+abline(h = mp + rbind(diff(mp)/2, NA), xpd = FALSE, col = "grey50", lty = 2)
+par(tcl = -7)
+axis(side = 2, at = mp + rbind(diff(mp)/2, NA), col = "grey50", line = NA, labels = FALSE, lty = 2)
 box()

### 2023-03-31 03-post-process/output-plots-children/09-rho-params.Rmd
Create correlograms for each process

@@
 box()
+
 ```
+
+## Process-Specific Summaries {.tabset .tabset-dropdown}
+
+```{r rho_mat_plot-fns}
+
+# one correlagram: for one summary statistic
+rho_mat_plot = function(param, q = "mean", main) {
+  rho_ests = post_summ(post, param, probs = c(0.1, 0.9))
+  rho_mat = array_format(rho_ests[q,])
+  rownames(rho_mat) = colnames(rho_mat) = pops
+  col = colorRampPalette(c("salmon", "white", "royalblue"))(20)
+  corrplot::corrplot(rho_mat, method = "color", type = "lower", tl.srt = 45, col = col, addCoef.col = "black", diag = FALSE, cl.pos = "n")
+  mtext(line = -2.5, text = main, side = 3, font = 2, cex = 1, col = "grey50")
+}
+
+# a set of three: 80% quantiles & mean
+rho_mat_plots = function(param, is_prior = FALSE) {
+  par(mfrow = c(1,3), mar = c(1,1,1,1), cex = 1)
+  dist = ifelse(is_prior, "Prior", "Posterior")
+  rho_mat_plot(param = param, q = "10%", main = paste0(dist, " 10%"))
+  rho_mat_plot(param = param, q = "mean", main = paste0(dist, " Mean"))
+  rho_mat_plot(param = param, q = "90%", main = paste0(dist, " 90%"))
+}
+
+rho_mat_fig_h = 4
+rho_mat_fig_w = 8
+```
+
+### Prior
+
+```{r rho_prior-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_E_Pb_pr[", is_prior = TRUE)
+```
+
+### Egg-to-Parr Survival
+
+```{r rho_Lphi_E_Pb-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_E_Pb[")
+```
+
+### Mean Parr Length
+
+```{r rho_lL_Pb-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_lL_Pb[")
+```
+
+### Proportion Fall Migrants
+
+```{r rho_Lpi-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lpi[")
+```
+
+### Overwinter Survival
+
+```{r rho_Lphi_Pa_Mb-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_Pa_Mb[")
+```
+
+### 'Growth' Factor
+
+```{r rho_lDelta_L_Pb_Mb-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_lDelta_L_Pb_Mb[")
+```
+
+### Trib. to LGR Survival
+
+```{r rho_Lphi_Mb_Ma-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_Mb_Ma[")
+```
+
+### LGR to Ocean Survival
+
+```{r rho_Lphi_Mb_O0-plot}
+est = post_summ(post, "rho_Lphi_Ma_O0[2,1]")
+kable(t(est), digits = 3, row.names = FALSE) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
+```
+
+### Yr1 Ocean Survival
+
+```{r rho_Lphi_O0_O1-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_O0_O1[")
+```
+
+### Maturity {.tabset .tabset-pills}
+
+#### Pr(Age-3)
+
+```{r rho_Lpsi_O1-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lpsi_O1[")
+```
+
+#### Pr(Age-4)
+
+```{r rho_Lpsi_O2-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lpsi_O2[")
+```
+
+### BON to LGR Survival
+
+```{r rho_Lphi_Rb_Ra-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+est = post_summ(post, "rho_Lphi_Rb_Ra[2,1]")
+kable(t(est), digits = 3, row.names = FALSE) %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
+```
+
+### Pre-Spawn Survival
+
+```{r rho_Lphi_Sb_Sa-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
+rho_mat_plots("rho_Lphi_Sb_Sa[")
+```

### 2023-03-31 02-model/fit-model.R
Update MCMC dimensions

@@ -277,7 +277,7 @@ jags_dims = list(
   n_post = switch(mcmc_length,  "very_short" = 100,  "short" = 2000, "medium" = 24000, "long" = 50000, "very_long" = 100000),
   n_burn = switch(mcmc_length,  "very_short" = 10,  "short" = 1000, "medium" = 20000, "long" = 30000, "very_long" = 50000),
   n_thin = switch(mcmc_length,  "very_short" = 1,   "short" = 3,    "medium" = 8,     "long" = 10,    "very_long" = 25),
-  n_chain = switch(mcmc_length, "very_short" = 2,   "short" = 2,    "medium" = 4,     "long" = 4,     "very_long" = 4),
+  n_chain = switch(mcmc_length, "very_short" = 2,   "short" = 4,    "medium" = 4,     "long" = 4,     "very_long" = 4),
   n_adapt = switch(mcmc_length, "very_short" = 100,  "short" = 10,  "medium" = 1000,  "long" = 3000,  "very_long" = 5000),
   parallel = TRUE
 )

### 2023-04-03 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Update post-v-prior plots for SIW

@@
 
-```{r}
+```{r post-v-prior-wrappers}
 # wrapper to create plot for all populations
-post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, ...) {
-  # function to plot one population
+post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, is_rho = FALSE, y_max = 0.3, ...) {
+
+  if (is_rho) {
+    n = length(vcov_labels)
+    titles = vcov_labels
+    mfrow = c(3,2)
+    looping = vcov_inds
+    prior_param = paste0(prior_param, "pop")
+    post_param = paste0(post_param, "pop")
+  } else {
+    n = jags_data$nj
+    titles = pops
+    mfrow = c(2,2)
+    looping = 1:jags_data$nj
+  }
+
+  # function to plot one population/pair
   plot_f = function(j) {
@@
       post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
-      prior_samps = post_subset(post, prior_param, matrix = TRUE),
-      main = pops[j], 
-      legend_loc = ifelse(j == 1, legend_loc, NA),
+      prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
+      main = titles[j], 
+      legend_loc = ifelse(j == looping[1], legend_loc, NA),
+      y_max = y_max,
       xlim = xlim
@@
 
-  # apply to each population
-  par(mfrow = c(2,2), oma = c(1,1.5,0,0))
-  junk = sapply(1:jags_data$nj, plot_f)
+  # apply to each population/pair
+  par(mfrow = mfrow, oma = c(1,1.75,0,0))
+  junk = sapply(1:n, function(j) plot_f(looping[j]))
+  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
+  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+}
+
+# wrapper to create plot for all origins
+post_v_prior_origins = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, ...) {
+  # function to plot one population
+  plot_f = function(o) {
+    post_v_prior(
+      post_samps = post_subset(post, sub_index(post_param, origin = o, ...), matrix = TRUE),
+      prior_samps = post_subset(post, sub_index(prior_param, origin = o, ...), matrix = TRUE),
+      main = c("NOR", "HOR")[o], 
+      legend_loc = ifelse(o == 1, legend_loc, NA),
+      xlim = xlim
+    )
+  }
+
+  # apply to each origin
+  par(mfrow = c(1,2), oma = c(1,1.5,0,0))
+  junk = sapply(1:jags_data$no, plot_f)
   mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
@@
 
-### SD Logit Egg-to-Parr Survival
+### Egg-to-Parr Survival
 
-**Prior Used**: `dt(0, 1/`r jags_data$sig_Lphi_E_Pb_prior`^2, 1) T(0, `r jags_data$dt_upr`)`
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
 
 ```{r sig_Lphi_E_Pb-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lphi_E_Pb[pop]", prior_param = "sig_Lphi_E_Pb_pr",
-                  xlim = c(0, jags_data$dt_upr)
+post_v_prior_pops(post_param = "sig_Lphi_E_Pb[pop]", prior_param = "sig_Lphi_E_Pb_pr[pop]",
+                  xlim = c(0, 2)
 )
@@
 
-### SD Logit Yr1 Ocean Survival
+### Parr Mean Length
 
-**Prior Used**: `dt(0, 1/`r jags_data$sig_Lphi_O0_O1_prior`^2, 1) T(0, `r jags_data$dt_upr`)`
+**Process Noise Distribution**: Multivariate log-normal
 
-```{r sig_Lphi_O0_O1-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lphi_O0_O1[pop]", prior_param = "sig_Lphi_O0_O1_pr",
-                  xlim = c(0, jags_data$dt_upr)
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_lL_Pb-post-v-prior}
+post_v_prior_pops(post_param = "sig_lL_Pb[pop]", prior_param = "sig_lL_Pb_pr[pop]",
+                  xlim = c(0, 2)
 )
@@
 
-### SD Logit Maturation {.tabset .tabset-pills}
+### Proportion Fall Migrants
 
-#### Age-3 {.tabset .tabset-pills}
+**Process Noise Distribution**: Multivariate logit-normal
 
-**Prior Used**: `dt(0, 1/`r jags_data$sig_Lpsi_O1`^2, 1) T(0, `r jags_data$dt_upr`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
 
-##### NOR
-
-```{r sig_Lpsi_O1_nor-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lpsi_O1[pop,origin]", prior_param = "sig_Lpsi_O1_pr",
-                  origin = o_nor, xlim = c(0, jags_data$dt_upr)
+```{r sig_Lpi-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lpi[pop]", prior_param = "sig_Lpi_pr[pop]",
+                  xlim = c(0, 2)
 )
@@
 
-##### HOR
+### Overwinter Survival
 
-```{r sig_Lpsi_O1_hor-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lpsi_O1[pop,origin]", prior_param = "sig_Lpsi_O1_pr",
-                  origin = o_hor, xlim = c(0, jags_data$dt_upr)
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_Pa_Mb-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lphi_Pa_Mb[pop]", prior_param = "sig_Lphi_Pa_Mb_pr[pop]",
+                  xlim = c(0, 2)
 )
@@
 
-#### Age-4 {.tabset .tabset-pills}
+### "Growth" Factor
 
-**Prior Used**: `dt(0, 1/`r jags_data$sig_Lpsi_O2`^2, 1) T(0, `r jags_data$dt_upr`)`
+**Process Noise Distribution**: Multivariate log-normal
 
-##### NOR
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
 
-```{r sig_Lpsi_O2_nor-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lpsi_O2[pop,origin]", prior_param = "sig_Lpsi_O2_pr",
-                  origin = o_nor, xlim = c(0, jags_data$dt_upr)
+```{r sig_lDelta_L_Pb_Mb-post-v-prior}
+post_v_prior_pops(post_param = "sig_lDelta_L_Pb_Mb[pop]", prior_param = "sig_lDelta_L_Pb_Mb_pr[pop]",
+                  xlim = c(0, 2)
 )
@@
 
-##### HOR
+### Trib to LGR Survival
 
-```{r sig_Lpsi_O2_hor-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lpsi_O2[pop,origin]", prior_param = "sig_Lpsi_O2_pr",
-                  origin = o_hor, xlim = c(0, jags_data$dt_upr)
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_Mb_Ma-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lphi_Mb_Ma[pop]", prior_param = "sig_Lphi_Mb_Ma_pr[pop]",
+                  xlim = c(0, 2)
 )
 ```
+
+### LGR to Ocean Survival
+
+**Process Noise Distribution**: Bivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_Ma_O0-post-v-prior, fig.width = 6, fig.height = 3}
+post_v_prior_origins(post_param = "sig_Lphi_Ma_O0[origin]", prior_param = "sig_Lphi_Ma_O0_pr[origin]",
+                  xlim = c(0, 2)
+)
+```
+
+### Yr 1 Ocean Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_O0_O1-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lphi_O0_O1[pop]", prior_param = "sig_Lphi_O0_O1_pr[pop]",
+                  xlim = c(0, 2)
+)
+```
+
+### Maturity {.tabset .tabset-pills}
+
+#### Pr(Age-3)
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lpsi-O1-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lpsi_O1[pop]", prior_param = "sig_Lpsi_O1_pr[pop]",
+                  xlim = c(0, 2)
+)
+```
+
+#### Pr(Age-4)
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lpsi_O2-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lpsi_O2[pop]", prior_param = "sig_Lpsi_O2_pr[pop]",
+                  xlim = c(0, 2)
+)
+```
+
+### BON to LGR Survival
+
+**Process Noise Distribution**: Bivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_Rb_Ra-post-v-prior, fig.width = 6, fig.height = 3}
+post_v_prior_origins(post_param = "sig_Lphi_Rb_Ra[origin]", prior_param = "sig_Lphi_Rb_Ra_pr[origin]",
+                  xlim = c(0, 2)
+)
+```
+
+### Pre-spawn Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r sig_Lphi_Sb_Sa-post-v-prior}
+post_v_prior_pops(post_param = "sig_Lphi_Sb_Sa[pop]", prior_param = "sig_Lphi_Sb_Sa_pr[pop]",
+                  xlim = c(0, 2)
+)
+```
+
+## Correlation Parameters {.tabset .tabset-dropdown}
+
+```{r}
+# set these figure options for all plots in this section
+y_max = 0.2
+xlim = c(-1,1)
+knitr::opts_chunk$set(fig.width = 5, fig.height = 6)
+```
+
+### Egg-to-Parr Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_E_Pb-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lphi_E_Pb", prior_param = "rho_Lphi_E_Pb_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### Parr Mean Length
+
+**Process Noise Distribution**: Multivariate log-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_lL_Pb-post-v-prior}
+post_v_prior_pops(post_param = "rho_lL_Pb", prior_param = "rho_lL_Pb_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### Proportion Fall Migrants
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lpi-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lpi", prior_param = "rho_Lpi_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### Overwinter Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_Pa_Mb-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lphi_Pa_Mb", prior_param = "rho_Lphi_Pa_Mb_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### "Growth" Factor
+
+**Process Noise Distribution**: Multivariate log-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_lDelta_L_Pb_Mb-post-v-prior}
+post_v_prior_pops(post_param = "rho_lDelta_L_Pb_Mb", prior_param = "rho_lDelta_L_Pb_Mb_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### Trib to LGR Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_Mb_Ma-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lphi_Mb_Ma", prior_param = "rho_Lphi_Mb_Ma_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### LGR to Ocean Survival
+
+**Process Noise Distribution**: Bivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_Ma_O0-post-v-prior, fig.width = 3, fig.height = 3}
+par(oma = c(1,1.75,0,0))
+post_v_prior(post_samps = post_subset(post, "rho_Lphi_Ma_O0[2,1]", matrix = TRUE),
+             prior_samps = post_subset(post, "rho_Lphi_Ma_O0_pr[2,1]", matrix = TRUE),
+             xlim = xlim, y_max = y_max)
+mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
+mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+```
+
+### Yr 1 Ocean Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_O0_O1-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lphi_O0_O1", prior_param = "rho_Lphi_O0_O1_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### Maturity {.tabset .tabset-pills}
+
+#### Pr(Age-3)
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lpsi-O1-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lpsi_O1", prior_param = "rho_Lpsi_O1_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+#### Pr(Age-4)
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lpsi_O2-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lpsi_O2", prior_param = "rho_Lpsi_O2_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```
+
+### BON to LGR Survival
+
+**Process Noise Distribution**: Bivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_Rb_Ra-post-v-prior, fig.width = 3, fig.height = 3}
+par(oma = c(1,1.75,0,0))
+post_v_prior(post_samps = post_subset(post, "rho_Lphi_Rb_Ra[2,1]", matrix = TRUE),
+             prior_samps = post_subset(post, "rho_Lphi_Rb_Ra_pr[2,1]", matrix = TRUE),
+             xlim = xlim, y_max = y_max)
+mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
+mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+```
+
+### Pre-spawn Survival
+
+**Process Noise Distribution**: Multivariate logit-normal
+
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+
+```{r rho_Lphi_Sb_Sa-post-v-prior}
+post_v_prior_pops(post_param = "rho_Lphi_Sb_Sa", prior_param = "rho_Lphi_Sb_Sa_pr",
+                  xlim = xlim, y_max = y_max, is_rho = TRUE
+)
+```

### 2023-04-03 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Improve Tau prior specification
Now each process has their own DF parameter

@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_E_Pb_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_lL_Pb_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpi_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Pa_Mb_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_lDelta_L_Pb_Mb_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Mb_Ma_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior[1]`,`r jags_data$no`),`r jags_data$Tau_Lphi_Ma_O0_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_O0_O1_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpsi_O1_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpsi_O2_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior`,`r jags_data$no`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior[1]`,`r jags_data$no`),`r jags_data$Tau_Lphi_Rb_Ra_prior[2]`)`
 
@@
 
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`
+**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Sb_Sa_prior[2]`)`
 

### 2023-04-03 02-model/fit-model.R

@@ -121,19 +121,18 @@ add_jags_data = append(add_jags_data, list(
   mu_phi_O2_O3_prior =        c(70,30),
   mu_psi_O1_prior =             c(1,9),
   mu_psi_O2_prior =         c(8.5,1.5),
-  Tau_Lphi_E_Pb_prior =            0.3,
-  Tau_lL_Pb_prior =                0.1,
-  Tau_Lpi_prior =                  0.3,
-  Tau_Lphi_Pa_Mb_prior =           0.3,
-  Tau_lDelta_L_Pb_Mb_prior =       0.1,
-  Tau_Lphi_Mb_Ma_prior =           0.3,
-  Tau_Lphi_Ma_O0_prior =           0.3,
-  Tau_Lphi_O0_O1_prior =           0.3,
-  Tau_Lpsi_O1_prior =             0.15,
-  Tau_Lpsi_O2_prior =              0.3,
-  Tau_Lphi_Rb_Ra_prior =           0.3,
-  Tau_Lphi_Sb_Sa_prior =          0.15,
-  isw_df = ifelse(do_sim_vs_obs, 1000, 20)
+  Tau_Lphi_E_Pb_prior =            c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)), 
+  Tau_lL_Pb_prior =                c(0.10, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lpi_prior =                  c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lphi_Pa_Mb_prior =           c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_lDelta_L_Pb_Mb_prior =       c(0.15, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lphi_Mb_Ma_prior =           c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lphi_Ma_O0_prior =           c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lphi_O0_O1_prior =           c(0.30, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
+  Tau_Lpsi_O1_prior =              c(0.15, ifelse(do_sim_vs_obs, sim_siw_df, 20)),
[…]

### 2023-04-03 02-model/model-code.R

@@ -8,52 +8,52 @@ jags_model_code = function() {
   ### PRIORS: Precision Matrices for Process Noise
   
   # egg to parr survival
-  Tau_Lphi_E_Pb[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lphi_E_Pb_prior, nj), isw_df)
-  Tau_Lphi_E_Pb_pr[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lphi_E_Pb_prior, nj), isw_df)
+  Tau_Lphi_E_Pb[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lphi_E_Pb_prior[1], nj), Tau_Lphi_E_Pb_prior[2])
+  Tau_Lphi_E_Pb_pr[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lphi_E_Pb_prior[1], nj), Tau_Lphi_E_Pb_prior[2])
   
   # parr mean length
-  Tau_lL_Pb[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_lL_Pb_prior, nj), isw_df)
-  Tau_lL_Pb_pr[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_lL_Pb_prior, nj), isw_df)
+  Tau_lL_Pb[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_lL_Pb_prior[1], nj), Tau_lL_Pb_prior[2])
+  Tau_lL_Pb_pr[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_lL_Pb_prior[1], nj), Tau_lL_Pb_prior[2])
 
   # proportion of parr that are fall migrants
-  Tau_Lpi[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lpi_prior, nj), isw_df)
-  Tau_Lpi_pr[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lpi_prior, nj), isw_df)
+  Tau_Lpi[1:nj,1:nj] ~ dscaled.wishart(rep(Tau_Lpi_prior[1], nj), Tau_Lpi_prior[2])
[…]

### 2023-04-04 02-model/fit-model.R
Add "dot" time series to model and tracked list
Will help with:
* calculation of process model quantile residuals
* cool plots like those that currently exist for time series of egg-to-parr survival (showing realized, expected value, expected value + serial autocorrelation)

@@ -165,7 +165,7 @@ if (do_sim_vs_obs) {
 # nodes to monitor for any model
 jags_params = c(
   # reproduction
-  "alpha", "beta", "phi_E_Pb", "lambda", "sig_lbeta", "kappa_phi_E_Pb", "phi_E_Pb_dot", "phi_E_Pb_dot2",
+  "alpha", "beta", "phi_E_Pb", "lambda", "sig_lbeta", "kappa_phi_E_Pb", 
 
   # length-related quantities
   "omega0", "omega1", 
@@ -178,6 +178,10 @@ jags_params = c(
   "mu_pi", "mu_phi_Mb_Ma", "mu_phi_Ma_O0",
   "mu_psi_O1", "mu_psi_O2", "mu_phi_Sb_Sa",
   "mu_phi_O0_O1", "mu_phi_O1_O2", "mu_phi_O2_O3", "mu_phi_Rb_Ra",
+  
+  # "dot" parameters -- expected values after accounting for relationships (dot), AR(1) (dot2)
+  "phi_E_Pb_dot", "phi_E_Pb_dot2", "L_Pb_dot", "phi_Pa_Mb_dot",
+  "Delta_L_Pb_Mb_dot", "phi_Mb_Ma_dot", "phi_O0_O1_dot2",
   
   # year-specific parameters
   "pi", "phi_Pa_Mb", "phi_Mb_Ma", "phi_Ma_O0", 

### 2023-04-04 02-model/model-code.R

@@ -208,20 +208,25 @@ jags_model_code = function() {
     Lphi_E_Pb[y,1:nj] ~ dmnorm(logit(phi_E_Pb_dot[y,1:nj]) + Lphi_E_Pb_resid[y-1,1:nj] * kappa_phi_E_Pb[1:nj], Tau_Lphi_E_Pb[1:nj,1:nj])
 
     # density-dependent length at end of summer
-    lL_Pb[y,1:nj] ~ dmnorm(omega0[1:nj] + omega1[1:nj] * log((E[y,1:nj]/E_scale)/wul[1:nj]), Tau_lL_Pb[1:nj,1:nj])
+    lL_Pb_dot[y,1:nj] <- omega0[1:nj] + omega1[1:nj] * log((E[y,1:nj]/E_scale)/wul[1:nj])
+    lL_Pb[y,1:nj] ~ dmnorm(lL_Pb_dot[y,1:nj], Tau_lL_Pb[1:nj,1:nj])
     
     # LH apportionment
     Lpi1[y,1:nj] ~ dmnorm(logit(mu_pi[i_fall,1:nj]), Tau_Lpi[1:nj,1:nj])
 
     # overwinter survival by LH type: function of size
-    Lphi_Pa_Mb[y,i_fall,1:nj] ~ dmnorm(gamma0[i_fall,1:nj] + gamma1[i_fall,1:nj] * L_Pb_star[y,1:nj], Tau_Lphi_Pa_Mb[1:nj,1:nj])
-    Lphi_Pa_Mb[y,i_spring,1:nj] ~ dmnorm(gamma0[i_spring,1:nj] + gamma1[i_spring,1:nj] * L_Pb_star[y,1:nj], Tau_Lphi_Pa_Mb[1:nj,1:nj])
+    for (i in 1:ni) {
+      Lphi_Pa_Mb_dot[y,i,1:nj] <- gamma0[i,1:nj] + gamma1[i,1:nj] * L_Pb_star[y,1:nj]
+      Lphi_Pa_Mb[y,i,1:nj] ~ dmnorm(Lphi_Pa_Mb_dot[y,i,1:nj], Tau_Lphi_Pa_Mb[1:nj,1:nj])
+    }
 
     # summer to spring growth factor
-    lDelta_L_Pb_Mb[y,1:nj] ~ dmnorm(theta0[1:nj] + theta1[1:nj] * L_Pb_star[y,1:nj], Tau_lDelta_L_Pb_Mb[1:nj,1:nj])
[…]

### 2023-04-04 03-post-process/output-plots-children/10-noise-term-diags.Rmd
Process model qresids now in Rmd

@@
 
+```{r make-process-noise-terms, results = "hide"}
+# create quantile residuals for a time series from one process
+# e.g., Pr(mature age-3) for all years for one population, origin, and age combination
+make_qresid = function(real_param, mean_param, sig_param, f_real = qlogis, f_mean = qlogis, yrs = observable, ...) {
+
+  # extract posterior samples of the correct quantities for all years, and apply the correct transformation where needed
+  real_samps = f_real(post_subset(post, sub_index(real_param, year = yrs, ...), matrix = TRUE))  # realized value from ppd
+  mean_samps = f_mean(post_subset(post, sub_index(mean_param, year = yrs, ...), matrix = TRUE))  # mean parameter ppd
+  sig_samps = as.numeric(post_subset(post, sub_index(sig_param, ...), matrix = TRUE))            # sd parameter of ppd
+
+  # remove any ^ or $ symbols used in specifying specific parameters
+  real_param = postpack:::rm_regex_lock(real_param)
+  mean_param = postpack:::rm_regex_lock(mean_param)
+
+  # calculate the quantile of the realized value given the mean and sd parameter
+  # performed MCMC draw by draw for each year separately
+  out = sapply(1:length(yrs), function(y) {
+    pnorm(
+      real_samps[,sub_index(real_param, year = yrs[y], ...)],
+      mean_samps[,sub_index(mean_param, year = yrs[y], ...)],
+      sig_samps
+    )
+  })
+
+  # create new names for the output
+  # basically add "_qresid" to the end of the realized node name
+  new_names = sub_index(real_param, year = yrs, ...)
+  new_names = stringr::str_replace(new_names, "\\[", "_qresid[")
+
+  # include the correct letter to indicate transformation performed (L = logit or l = log) and drop any ^
+  new_names = paste0(ifelse(f_real(1) == log(1), "l", "L"), new_names)
+  colnames(out) = new_names
+
+  # return the output: a matrix of posterior samples for the desired process
+  return(out)
+}
+
+# create quantile residuals for all time series from one process
+# e.g., Pr(mature age-3) for all years, all populations, and age-combinations
+# type = "pop" is for processes that vary by population
+# type = "origin" is for processes that very by origin
+make_qresid_all = function(real_param, mean_param, sig_param, f_real = qlogis, f_mean = qlogis, type = "pop", ...) {
+
+  # print an indicator for which process is being analyzed
+  process_name = postpack:::rm_regex_lock(real_param)
+  process_name = postpack:::drop_index(process_name)
+  cat("  ", process_name, "\n")
+
+  # loop over populations if appropriate
+  if (type == "pop") {
+    qresid_out = lapply(1:jags_data$nj, function(j) {
+      cat("\r    Population: ", c("CAT", "LOS", "MIN", "UGR")[j], sep = "")
+      out = make_qresid(real_param, mean_param, sig_param, f_real = f_real, f_mean = f_mean, pop = j, ...)
+      return(out)
+    })
+  }
+
+  # loop over origins if appropriate
+  if (type == "origin") {
+    qresid_out = lapply(1:jags_data$no, function(o) {
+      cat("\r    Origin: ", c("NOR", "HOR")[o], sep = "")
+      out = make_qresid(real_param, mean_param, sig_param, f_real = f_real, f_mean = f_mean, origin = o, ...)
+      return(out)
+    });
+  }
+
+  # print a newline
+  cat("\n")
+
+  # combine list elements into one matrix
+  qresid_out = do.call(cbind, qresid_out)
+
+  # return the output
+  return(qresid_out)
+}
+
+# container object to append output to
+qresid_post = postpack:::id_mat(post)
+
+# the years to calculate residuals for
+observable = 2:jags_data$ny_obs
+# "^phi_E_Pb[year,pop]""phi_E_Pb_dot2[year,pop]", "sig_Lphi_E_Pb[pop]"
+
+# egg to parr survival
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_E_Pb[year,pop]",
+                                    "phi_E_Pb_dot2[year,pop]",
+                                    "sig_Lphi_E_Pb[pop]",
+                                    type = "pop")
+)
+
+# parr mean length
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^L_Pb[year,pop]",
+                                    "^L_Pb_dot[year,pop]",
+                                    "sig_lL_Pb[pop]",
+                                    type = "pop", f_real = log, f_mean = log)
+)
+
+# Pr(fall migrant)
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^pi[year,LH_type,pop]",
+                                    "mu_pi[LH_type,pop]",
+                                    "sig_Lpi[pop]",
+                                    type = "pop", LH_type = jags_data$i_fall)
+)
+
+# overwinter survival: fall migrants
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Pa_Mb[year,LH_type,pop]",
+                                    "^phi_Pa_Mb_dot[year,LH_type,pop]",
+                                    "sig_Lphi_Pa_Mb[pop]",
+                                    type = "pop", LH_type = jags_data$i_fall)
+)
+
+# overwinter survival: spring migrants
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Pa_Mb[year,LH_type,pop]",
+                                    "^phi_Pa_Mb_dot[year,LH_type,pop]",
+                                    "sig_Lphi_Pa_Mb[pop]",
+                                    type = "pop", LH_type = jags_data$i_spring)
+)
+
+# "growth" factor
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^Delta_L_Pb_Mb[year,pop]",
+                                    "^Delta_L_Pb_Mb_dot[year,pop]",
+                                    "sig_Lphi_Pa_Mb[pop]",
+                                    type = "pop", f_real = log, f_mean = log)
+)
+
+# trib to LGR survival: NOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Mb_Ma[year,LH_type,origin,pop]",
+                                    "^phi_Mb_Ma_dot[year,LH_type,origin,pop]",
+                                    "sig_Lphi_Mb_Ma[pop]",
+                                    type = "pop", LH_type = jags_data$i_spring, origin = jags_data$o_nor)
+)
+
+# trib to LGR survival: HOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Mb_Ma[year,LH_type,origin,pop]",
+                                    "^mu_phi_Mb_Ma[LH_type,origin,pop]",
+                                    "sig_Lphi_Mb_Ma[pop]",
+                                    type = "pop", LH_type = jags_data$i_spring, origin = jags_data$o_hor)
+)
+
+# LGR to ocean survival
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Ma_O0[year,origin]",
+                                    "mu_phi_Ma_O0[origin]",
+                                    "sig_Lphi_Ma_O0[origin]",
+                                    type = "origin")
+)
+
+# Yr1 ocean survival
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_O0_O1[year,origin,pop]",
+                                    "^phi_O0_O1_dot2[year,origin,pop]",
+                                    "sig_Lphi_O0_O1[pop]",
+                                    type = "pop", origin = jags_data$o_nor)
+)
+
+# Pr(mature age-3): NOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^psi_O1[year,origin,pop]",
+                                    "^mu_psi_O1[origin,pop]",
+                                    "sig_Lpsi_O1[pop]",
+                                    type = "pop", origin = jags_data$o_nor)
+)
+
+# Pr(mature age-3): HOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^psi_O1[year,origin,pop]",
+                                    "^mu_psi_O1[origin,pop]",
+                                    "sig_Lpsi_O1[pop]",
+                                    type = "pop", origin = jags_data$o_hor)
+)
+
+# Pr(mature age-3): NOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^psi_O2[year,origin,pop]",
+                                    "^mu_psi_O2[origin,pop]",
+                                    "sig_Lpsi_O2[pop]",
+                                    type = "pop", origin = jags_data$o_nor)
+)
+
+# Pr(mature age-3): HOR
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^psi_O2[year,origin,pop]",
+                                    "^mu_psi_O2[origin,pop]",
+                                    "sig_Lpsi_O2[pop]",
+                                    type = "pop", origin = jags_data$o_hor)
+)
+
+# BON to LGR survival
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Rb_Ra[year,origin]",
+                                    "mu_phi_Rb_Ra[origin]",
+                                    "sig_Lphi_Rb_Ra[origin]",
+                                    type = "origin")
+)
+
+# Pre-spawn survival
+qresid_post = cbind(qresid_post,
+                    make_qresid_all("^phi_Sb_Sa[year,pop]",
+                                    "^mu_phi_Sb_Sa[pop]",
+                                    "sig_Lphi_Sb_Sa[pop]",
+                                    type = "pop", origin = jags_data$o_hor)
+)
+
+qresid_post = qresid_post[,-c(1:2)]
+
+post = post_bind(post, qresid_post)
+```
+
 ```{r plot-proc-resid-fn}
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
 oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
 oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
@@
 my_par()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
 oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
@@
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,LH_type,pop\\]", "Migratory Strategy Apportionment")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
+proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Trib to LGR Survival")
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")

### 2023-04-04 02-model/fit-model.R

@@ -219,13 +219,6 @@ jags_params = c(
   "Lphi_Sb_Sa_resid", "Lphi_E_Pb_resid", "Lphi_Rb_Ra_resid",
   "lL_Pb_resid", "lDelta_L_Pb_Mb_resid",
   
-  # quantile residuals: process model
-  "Lpi_qresid", "Lphi_Pa_Mb_qresid", "Lphi_Mb_Ma_qresid",
-  "Lphi_Ma_O0_qresid", "Lpsi_O1_qresid",
-  "Lpsi_O2_qresid", "Lphi_O0_O1_qresid",
-  "Lphi_Sb_Sa_qresid", "Lphi_E_Pb_qresid", "Lphi_Rb_Ra_qresid",
-  "lL_Pb_qresid", "lDelta_L_Pb_Mb_qresid",
-  
   # quantile residuals: observation model
   "x_Ra_obs_qresid", "x_Sa_prime_obs_qresid",
   "lPa_obs_qresid", "lMb_obs_qresid", "lRa_obs_qresid",

### 2023-04-04 03-post-process/output-plots.Rmd
Create object storing the indices of lwr triangle rhos
E.g., [2,1], [3,1], etc. Useful later.

This change should have been included with an earlier commit on rho plotting

@@
 vcov_rows = dummy_rows[lower.tri(dummy_rows)]
+vcov_inds = paste0("[", vcov_rows, ",", vcov_cols, "]")
 vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])

### 2023-04-05 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Update post_v_prob() plot function
xlim argument was not working

@@
 ```{r post-v-prior-fn}
-# argument list:
-# post_samps & prior_samps: samples from their respective PDFs
-# post_col & prior_col: (non-transparent) colors for each PDF (will be made transparent for bar fills based on the alpha argument)
-# main: plot title
-# y_max: maximum bin probability height to display; should be [0,1]
-# legend_loc: position of the legend (e.g., "topright")
-# n_bins: the number of bins
-# alpha: transparency setting for bar fills
+post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
+                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {
 
-post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
-                        main = NULL, y_max = 0.3, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {
+  if (!is.null(xlim)) {
+    post_samps_keep = post_samps[post_samps >= xlim[1] & post_samps <= xlim[2]]
+    prior_samps_keep = prior_samps[prior_samps >= xlim[1] & prior_samps <= xlim[2]]
+  } else {
+    post_samps_keep = post_samps
+    prior_samps_keep = prior_samps
+  }
+  p_post_keep = length(post_samps_keep)/length(post_samps)
+  p_prior_keep = length(prior_samps_keep)/length(prior_samps)
 
   # get the range of all samples
-  rng = range(post_samps, prior_samps)
+  rng = range(post_samps_keep, prior_samps_keep)
+  if (!is.null(xlim)) rng[2] = max(xlim[2], rng[2])
 
-  # if xlim was provided, take it into consideration when creating breaks
-  if (is.null(xlim)) {
+  # set bins
   breaks = seq(rng[1], rng[2], length = n_bins)
-  } else {
-    breaks = seq(min(rng[1], xlim[1]), max(rng[2], xlim[2]), length = n_bins)
-  }
 
   # calculate the data for the histogram
-  prior_hist = hist(prior_samps, plot = FALSE, breaks = breaks)
-  post_hist = hist(post_samps, plot = FALSE, breaks = breaks)
+  prior_hist = hist(prior_samps_keep, plot = FALSE, breaks = breaks)
+  post_hist = hist(post_samps_keep, plot = FALSE, breaks = breaks)
 
   # convert bin counts to probabilities
-  prior_probs = prior_hist$counts/sum(prior_hist$counts)
-  post_probs = post_hist$counts/sum(post_hist$counts)
+  # account for fraction not shown
+  prior_probs = prior_hist$counts/sum(prior_hist$counts) * p_prior_keep
+  post_probs = post_hist$counts/sum(post_hist$counts) * p_post_keep
 
@@
   mp = barplot(
-    prior_probs, ylim = c(0,y_max), space = 0, border = prior_col, col = scales::alpha(prior_col, alpha), axes = FALSE
+    prior_probs, ylim = c(0,y_max), space = 0, border = prior_col,
+    col = scales::alpha(prior_col, alpha), axes = FALSE
   )
@@
   # draw segments to connect axes at origin
-  usr = par("usr")
+  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
   segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
@@
   }
+
+  # if some portion of one of the dists is not shown, include a message
+  if (p_post_keep < 1 | p_prior_keep < 1) {
+    nice_round = function(x, digits = 2) {
+      x_round = round(x, digits = digits)
+      if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
+      x_out
+    }
+
+    legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
+           legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
+           text.col = c(prior_col, post_col), bty = "n", title.col = "black",
+           title = "P Not Shown", cex = 0.8
+    )
+  }
 }
@@
 # wrapper to create plot for all populations
-post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, is_rho = FALSE, y_max = 0.3, ...) {
+post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, is_rho = FALSE, y_max = 0.5, ...) {
 

### 2023-04-05 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Use better x/y lims in post-v-prior plots

@@
 post_v_prior_pops(post_param = "mu_phi_O0_O1[origin,pop]", prior_param = "mu_phi_O0_O1_pr",
-                  origin = o_nor, xlim = c(0,1)
+                  origin = o_nor, xlim = c(0,1), y_max = 0.75
 )
@@
 post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
-                  origin = o_nor, xlim = c(0,1)
+                  origin = o_nor, xlim = c(0,1), y_max = 0.75
 )
@@
 post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
-                  origin = o_hor, xlim = c(0,1)
+                  origin = o_hor, xlim = c(0,1), y_max = 0.75
 )
@@
 post_v_prior_pops(post_param = "sig_lL_Pb[pop]", prior_param = "sig_lL_Pb_pr[pop]",
-                  xlim = c(0, 2)
+                  xlim = c(0, 1), y_max = 0.75
 )
@@
 post_v_prior_pops(post_param = "sig_lDelta_L_Pb_Mb[pop]", prior_param = "sig_lDelta_L_Pb_Mb_pr[pop]",
-                  xlim = c(0, 2)
+                  xlim = c(0,1), y_max = 0.75
 )
@@
 # set these figure options for all plots in this section
-y_max = 0.2
+y_max = 0.15
 xlim = c(-1,1)

### 2023-04-05 03-post-process/compare-sim-to-obs.Rmd
Start sim-vs-obs in 2000 for Rmd comparisons
Update scenario name

@@
     label: "Scenario"
-    value: "base"
+    value: "siw"
     input: text
@@
 # may want to use 2001 to cut off years without hatchery supplementation
-fy_obs = which(all_yrs == 2001)
+fy_obs = which(all_yrs == 2000)
 

### 2023-04-05 03-post-process/output-plots.Rmd
Update scenario name

@@
     label: "Scenario"
-    value: "scaled-wishart"
+    value: "siw"
     input: text

### 2023-04-05 02-model/fit-model.R

@@ -25,7 +25,7 @@ do_sim_vs_obs = as.logical(args[3])
 rmd = as.logical(args[4])
 
 # scenario name: change this
-if (is.na(scenario_name)) scenario_name = "siw-DF2"
+if (is.na(scenario_name)) scenario_name = "siw"
 
 # set mcmc length
 if (is.na(mcmc_length)) mcmc_length = "vshort"

### 2023-04-11 03-post-process/output-plots-children/09-rho-params.Rmd
Fix bug in correlation summary plot
Was including both posterior and prior in summarization -- should have only been posterior

@@
 rho_params = rho_params1[!(rho_params1 %in% rho_params2)]
+
 f = function(p) {
-  x = rowMeans(post_subset(post, p, matrix = TRUE))
+  x = rowMeans(post_subset(post, paste0("^", p, "["), matrix = TRUE))
   c(mean = mean(x), sd = sd(x), quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))
@@
   "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
-  "rho_Lphi_Rb_Ra" = "BON -> UGR Survival",
+  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
   "rho_Lpi" = "Pr(Fall Migrant)",
@@
 
-* Blue: Mean of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
-* Red: Individual population pairs ("+" = posterior mean, lines = 50% CRI)
+* Blue: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
+* Red: Correlation of individual population pairs ("+" = posterior mean, lines = 50% CRI)
 * Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness)

### 2023-04-11 03-post-process/output-plots-children/06-length-based-survival.Rmd
Reorganize length-based output plots
Now in two sections: mean length and length vs. survival relationships

--- 2023-03-10 03-post-process/output-plots-children/05-length-based-values.Rmd
@@
 
-# Length-Based Quantities {.tabset .tabset-dropdown}
+# Length-Based Survival {.tabset .tabset-pills}
 
-## Mean Parr Length vs. Egg Density
-
-```{r}
-plot_f = function(j) {
-
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, ".")["mean",]
-  E_scaled_lwr = post_summ(post_E, ".")["2.5%",]
-  E_scaled_upr = post_summ(post_E, ".")["97.5%",]
-
-  # create a vector of scaled egg abundances to calculate at
-  E_scaled_seq = seq(min(E_scaled_lwr), max(E_scaled_upr), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarize predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
-  plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
-}
-
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-```
-
-## Smolt Mean Length {.tabset .tabset-pills}
-
-### "Growth Factor" vs. Parr Mean Length
-
-```{r}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-### "Growth Factor" Time Series
-
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
-
-## Parr $\rightarrow$ Smolt Overwinter Survival vs. Parr Mean Length
+## Parr $\to$ Smolt Overwinter Survival
 
@@
 junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
+mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
 mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
@@
 
-## Smolt Survival to LGR vs. Smolt Mean Length
+## Smolt Survival to LGR
 
 ```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
+plot_fn = function(j) {
 
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
+mtext(side = 1, outer = T, line = 0.25, "Smolt Mean Length (mm)")
 mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")

### 2023-04-11 03-post-process/output-plots.Rmd
Reorganize length-based output plots
Now in two sections: mean length and length vs. survival relationships

@@
     value: TRUE
-  include_length_based_values:
-    label: "Include Length-Based Output?"
+  include_mean_length:
+    label: "Include Mean Length Output?"
+    value: TRUE
+  include_surv_vs_length:
+    label: "Length-based Survival Output?"
     value: TRUE
@@
 
-```{r length-based-values, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_length_based_values}
+```{r mean-length, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_mean_length}
+```
+
+```{r length-based-values, child = "output-plots-children/06-length-based-survival.Rmd", eval = params$include_surv_vs_length}
 ```

### 2023-04-12 03-post-process/output-plots-children/05-length.Rmd
Update file names on output-plots children

--- 2023-03-13 03-post-process/output-plots-children/05-length-based-values.Rmd
@@
 
-# Length-Based Quantities {.tabset .tabset-dropdown}
+# Parr & Smolt Mean Length {.tabset .tabset-pills}
 
-## Mean Parr Length vs. Egg Density
+## Parr Mean Length {.tabset .tabset-pills}
 
-```{r}
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r L_Pb_tseries-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
+```
+
+#### Realized & Predicted
+
+```{r L_Pb_tseries-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+
+  # draw the predicted time series
+  add_tseries(est = post_summ(post, sub_index("^L_Pb_dot[year,pop]", pop = j, year = ts_yrs)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
+```
+
+### Density-Dependent Relationship
+
+```{r L_Pb-relationship, fig.width = 6, fig.height = 5}
 plot_f = function(j) {
@@
 mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\,(mm)$"))
 ```
@@
 
-### "Growth Factor" vs. Parr Mean Length
+### Time Series {.tabset .tabset-pills}
 
-```{r}
+#### Realized Alone
+
+```{r L_Mb-tseries-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
+```
+
+#### Realized & Predicted
+
+```{r get-L_Mb_dot}
+# function to get posterior samples of expected smolt length
+# not calculated in JAGS model, add to post object here
+f = function() {
+  # extract posterior samples of parr mean length and parr to smolt growth factor
+  L_Pb = post_subset(post, "^L_Pb[", matrix = TRUE)
+  Delta_L_Pb_Mb_dot = post_subset(post, "^Delta_L_Pb_Mb_dot[", matrix = TRUE)
+
+  # perform basic operations for one iteration -- for making dimension names later
+  L_Pb_1 = array_format(L_Pb[1,])
+  Delta_L_Pb_Mb_dot_1 = array_format(Delta_L_Pb_Mb_dot[1,])
+  L_Mb_dot_1 = L_Pb_1 * Delta_L_Pb_Mb_dot_1
+
+  # function to perform the calculation for one MCMC sample
+  g = function(i) {
+    L_Pb_i = array_format(L_Pb[i,])
+    Delta_L_Pb_Mb_dot_i = array_format(Delta_L_Pb_Mb_dot[i,])
+    L_Mb_dot_i = L_Pb_i * Delta_L_Pb_Mb_dot_i
+    as.numeric(L_Mb_dot_i)
+  }
+
+  # apply to each posterior sample
+  out = t(sapply(1:nrow(L_Pb), g))
+
+  # build element indices: the year
+  y_ind = rep(1:nrow(L_Pb_1), ncol(L_Pb_1))
+
+  # build element indices: the population
+  j_ind = rep(1:ncol(L_Pb_1), each = nrow(L_Pb_1))
+
+  # make element names
+  colnames(out) = paste0("L_Mb_dot[", y_ind, ",", j_ind, "]")
+
+  # drop out those that have NA values (first k_max years)
+  na_ind = which(!is.na(out[1,]))
+  out[,na_ind]
+}
+
+# combine with the rest of the posterior samples
+post = post_bind(post, f()); rm(f)
+```
+
+```{r L_Mb-tseries-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+
+  # draw the realized time series
+  add_tseries(est = post_summ(post, sub_index("^L_Mb_dot[year,pop]", year = ts_yrs, pop = j)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
+```
+
+## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}
+
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & "Data"
+
+```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & Predicted
+
+```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # draw the realized time series
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
+
+  # draw the predicted time series
+  add_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb_dot[year,pop]", pop = j, year = ts_yrs)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+### Relationship
+
+```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
 plot_f = function(j) {
@@
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
+mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
 ```
 
-### "Growth Factor" Time Series
+## Smolt vs. Parr Mean Length
 
-```{r}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs,
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
-}
+```{r L_Mb-v-L_Pb, fig.width = 6, fig.height = 5}
+plot_fn = function(j) {
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
-```
+  # extract posterior summaries of parr mean length outcomes
+  L_Pb_summ = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))
+  L_Pb_mean = L_Pb_summ["mean",]
+  L_Pb_lwr = L_Pb_summ["2.5%",]
+  L_Pb_upr = L_Pb_summ["97.5%",]
 
-## Parr $\rightarrow$ Smolt Overwinter Survival vs. Parr Mean Length
-
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+  # extract posterior summaries of parr mean length outcomes
+  L_Mb_summ = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))
+  L_Mb_mean = L_Mb_summ["mean",]
+  L_Mb_lwr = L_Mb_summ["2.5%",]
+  L_Mb_upr = L_Mb_summ["97.5%",]
 
@@
 
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
-  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
-  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
+  # create vectors to predict smolt mean length at: for credible regions and mean curve
   L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
@@
   # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
 
@@
   pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
+    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
+    pred_L_Mb = L_Pb_seq * pred_Delta_L_Pb_Mb
+    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "]")
+    pred_L_Mb
   }
@@
   # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
+  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
 
   # extract summarize predicted length
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]
+  pred_L_Mb_summ = post_summ(post_pred_L_Mb, ".")
+  pred_L_Mb_mean = pred_L_Mb_summ["mean",]
+  pred_L_Mb_lwr = pred_L_Mb_summ["2.5%",]
+  pred_L_Mb_upr = pred_L_Mb_summ["97.5%",]
 
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
+       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
        xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
-}
-
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
-}
-
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
-```
-
-## Smolt Survival to LGR vs. Smolt Mean Length
-
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
-plot_fn = function(j, i) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
-  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # extract summarize predicted length
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
-       xlim = range(L_Mb_seq), 
        main = pops[j]
@@
   # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
 
   # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
+  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(L_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
+mtext(side = 1, outer = T, line = 0.25, "Parr Mean Length (mm)")
+mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
 ```

### 2023-04-12 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Update file names on output-plots children

--- 2023-04-04 03-post-process/output-plots-children/10-noise-term-diags.Rmd
@@
                                     "^Delta_L_Pb_Mb_dot[year,pop]",
-                                    "sig_Lphi_Pa_Mb[pop]",
+                                    "sig_lDelta_L_Pb_Mb[pop]",
                                     type = "pop", f_real = log, f_mean = log)

### 2023-04-12 03-post-process/output-plots-children/12-param-summaries.Rmd
Update file names on output-plots children

---
editor_options: 
  chunk_output_type: console
---

# Parameter Summaries {.tabset .tabset-dropdown}

```{r my-boxplot-function}
my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), las = 3, ...) {
  # extract posterior samples and rename them
  post_sub = post_subset(post, params, matrix = TRUE)

  if (ncol(post_sub) >= 2) {
    colnames(post_sub) = ticklabs
  }

  # initialize a boxplot object
  bp = boxplot(post_sub, plot = FALSE)

  # replace the summary stats with my preferred quantiles
  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, las = las, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
} 
```

## Egg-to-Parr Survival {.tabset .tabset-pills}

### Beverton-Holt Parameters

```{r egg-to-parr-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("^alpha[.]", "Productivity")
my_boxplot("^beta[.]", "Capacity")
```

### Process SD & Correlation

```{r egg-to-parr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("^sig_Lphi_E_Pb[.]", "Process SD", ylim = c(0,2))
my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); abline(h = 0, lty = 2)
my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklabs = vcov_labels); abline(h = 0, lty = 2)
```

## Summer Parr Size

```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^omega0[.]$", "Intercept")
my_boxplot("^omega1[.]$", "Slope"); abline(h = 0, lty = 2)
my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Life History Apportionment

```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Mean Proportion Fall Migrants", ylim = c(0,1))
my_boxplot("sig_Lpi[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("^rho_Lpi", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Overwinter Survival {.tabset .tabset-pills}

### Logistic Function Parameters

```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope (Fall)"); abline(h = 0, lty = 2)
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope (Spring)"); abline(h = 0, lty = 2)
```

### Process SD & Correlation

```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lphi_Pa_Mb[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels); abline(h = 0, lty = 2)
```

## "Growth" Factor

```{r growth-factor-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^theta0[.]$", "Intercept")
my_boxplot("^theta1[.]$", "Slope"); abline(h = 0, lty = 2)
my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Movement Survival to LGR {.tabset .tabset-pills}

### Mean/Logistic Model Parameters

```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("tau0", "Intercept", main = "NOR")
my_boxplot("tau1", "Slope", main = "NOR"); abline(h = 0, lty = 2)
my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
```

### Process SD & Correlation

```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Movement Survival to Ocean

```{r lgr-to-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Ma_O0", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Ma_O0[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
```

## Probability of Maturing at Age-3 {.tabset .tabset-pills}

### Means

```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
```

### Process SD & Correlation

```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Probability of Maturing at Age-4 {.tabset .tabset-pills}

### Means

```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
```

### Process SD & Correlation

```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lpsi_O2[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Ocean Survival {.tabset .tabset-pills}

### Year 1 {.tabset .tabset-pills}

#### Means

```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

#### Process SD & Correlation

```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); abline(h = 0, lty = 2)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1)); abline(h = 0, lty = 2)
```

### Year 2 {.tabset .tabset-pills}

```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

### Year 3 {.tabset .tabset-pills}

```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

### NOR:HOR Log Odds Ratios

```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5}

# par(mfrow = c(1,3))
tmp_ylim = c(-1.5,1.5)
my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 1", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
# my_boxplot(sub_index("delta_O1_O2[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 2", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
# my_boxplot(sub_index("delta_O2_O3[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 3", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
```

## Movement Survival BON to LGR

```{r bon-to-lgr-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Rb_Ra", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot("sig_Lphi_Rb_Ra[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
```

## Pre-spawn Survival

```{r prespawn-surv-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = c(0,1))
my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels); abline(h = 0, lty = 2)
```

### 2023-04-12 03-post-process/output-plots.Rmd
Update file names on output-plots children

@@
     value: TRUE
+  include_post_v_prior:
+    label: "Include Posterior vs. Prior Densities?"
+    value: TRUE
   include_jags_info:
     label: "Include JAGS Code/Data?"
-    value: TRUE
-  include_post_v_prior:
-    label: "Include Posterior vs. Prior Densities?"
     value: TRUE
@@
 
-```{r mean-length, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_mean_length}
+```{r mean-length, child = "output-plots-children/05-length.Rmd", eval = params$include_mean_length}
 ```
@@
 
-```{r capacity-vs-habitat, child = "output-plots-children/06-capacity-vs-habitat.Rmd", eval = params$include_capacity_vs_habitat}
+```{r capacity-vs-habitat, child = "output-plots-children/07-capacity-vs-habitat.Rmd", eval = params$include_capacity_vs_habitat}
 ```
 
-```{r misc-process-model, child = "output-plots-children/07-misc-process-model.Rmd", eval = params$include_misc_process_model}
+```{r misc-process-model, child = "output-plots-children/08-misc-process-model.Rmd", eval = params$include_misc_process_model}
 ```
 
-```{r equiv-rates, child = "output-plots-children/08-equiv-rates.Rmd", eval = params$include_equiv_rates}
+```{r equiv-rates, child = "output-plots-children/09-equiv-rates.Rmd", eval = params$include_equiv_rates}
 ```
 
-```{r rho-params, child = "output-plots-children/09-rho-params.Rmd", eval = params$include_rho_params}
+```{r rho-params, child = "output-plots-children/10-rho-params.Rmd", eval = params$include_rho_params}
 ```
 
-```{r noise-term-diags, child = "output-plots-children/10-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
+```{r noise-term-diags, child = "output-plots-children/11-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
 ```
 
-```{r param-summaries, child = "output-plots-children/11-param-summaries.Rmd", eval = params$include_param_summaries}
-```
-
-```{r jags-info, child = "output-plots-children/12-jags-model-info.Rmd", eval = params$include_jags_info}
+```{r param-summaries, child = "output-plots-children/12-param-summaries.Rmd", eval = params$include_param_summaries}
 ```
@@
 ```
+
+```{r jags-info, child = "output-plots-children/14-jags-model-info.Rmd", eval = params$include_jags_info}
+```

### 2023-04-18 03-post-process/output-plots-children/08-misc-process-model.Rmd
Update file names on output-plots children
Reorganize ocean survival & maturity  plots

--- 2022-04-28 03-post-process/output-plots-children/07-misc-process-model.Rmd
@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Miscellaneous Process Model Components {.tabset .tabset-pills}
@@
 
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
+### Yr1 {.tabset .tabset-pills}
+
+#### NOR {.tabset .tabset-pills}
+
+##### Realized Alone
+
+```{r phi-O0-O1-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
 }
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (NOR)")
 ```
 
-### CAT
+##### Realized & [Predicted + AR(1)]
 
-```{r}
-ocean_surv_plot(j_cat)
+```{r phi-O0-O1-plots2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
+
+  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (NOR)")
 ```
 
-### LOS
+#### HOR {.tabset .tabset-pills}
 
-```{r}
-ocean_surv_plot(j_los)
+##### Realized Alone
+
+```{r phi-O0-O1-hor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (HOR)")
 ```
 
-### MIN
+### Yr2 {.tabset .tabset-pills}
 
-```{r}
-ocean_surv_plot(j_min)
+#### NOR
+
+```{r phi-O1-O2-nor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr2 Ocean Survival (NOR)")
 ```
 
-### UGR
+#### HOR
 
-```{r}
-ocean_surv_plot(j_ugr)
+```{r phi-O1-O2-hor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr2 Ocean Survival (HOR)")
+```
+
+### Yr3 {.tabset .tabset-pills}
+
+#### NOR
+
+```{r phi-O2-O3-nor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr3 Ocean Survival (NOR)")
+```
+
+#### HOR
+
+```{r phi-O2-O3-hor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Yr3 Ocean Survival (HOR)")
 ```
@@
 
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
+### Pr(Age-3) {.tabset .tabset-pills}
+
+#### NOR
+
+```{r psi-O1-nor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
+}
+
 par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-
+junk = sapply(1:jags_data$nj, plot_f)
 mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
-}
+mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-3|NOR)")
 ```
 
-### CAT
+#### HOR
 
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
+```{r psi-O1-hor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-3|HOR)")
 ```
 
-### LOS
+### Pr(Age-4) {.tabset .tabset-pills}
 
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
+#### NOR
+
+```{r psi-O2-nor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-4|NOR)")
 ```
 
-### MIN
+#### HOR
 
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
+```{r psi-O2-hor-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
+}
 
-### UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-4|HOR)")
 ```

### 2023-04-18 03-post-process/output-plots-children/06-length-based-survival.Rmd
Place boundaries on xlim for length-based survival

@@
   # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)
+  mean_diff = diff(range(L_Mb_mean)) * 0.1
+  L_Mb_seq = seq(min(L_Mb_mean) - mean_diff, max(L_Mb_mean) + mean_diff, length = 30)
+  L_Mb_star_seq = (L_Mb_seq - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
 

### 2023-04-18 03-post-process/output-plots-children/05-length.Rmd
Reorganize length plots

@@
 
+## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}
+
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & "Data"
+
+```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & Predicted
+
+```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # draw the realized time series
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,1.6))
+
+  # draw the predicted time series
+  add_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb_dot[year,pop]", pop = j, year = ts_yrs)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+### Relationship
+
+```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # extract posterior summaries of growth outcomes
+  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # create a vector of scaled summer lengths to calculate at
+  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # extract posteriors of coefficients
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted curves for one posterior sample
+  pred_fn = function(i) {
+    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
+    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
+    pred_Delta_L_Pb_Mb
+  }
+
+  # calculate predicted growth values and add to posterior samples
+  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
+
+  # extract summarize predicted growth
+  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
+  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
+  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]
+
+  # make a blank plot with the correct dimensions
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot(1,1, type = "n", 
+       # ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
+       ylim = c(1, 1.6),
+       xlim = range(L_Pb_seq), 
+       main = pops[j]
+  )
+
+  # expected relationship
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
+  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
+```
+
 ## Smolt Mean Length {.tabset .tabset-pills}
@@
   plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(75,110)
   )
@@
 mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
-```
-
-## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}
-
-### Time Series {.tabset .tabset-pills}
-
-#### Realized Alone
-
-```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
-```
-
-#### Realized & "Data"
-
-```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
-```
-
-#### Realized & Predicted
-
-```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-  # draw the realized time series
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
-
-  # draw the predicted time series
-  add_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb_dot[year,pop]", pop = j, year = ts_yrs)),
-              yrs = all_yrs[ts_yrs])
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
-```
-
-### Relationship
-
-```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
-plot_f = function(j) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # extract posterior summaries of growth outcomes
-  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
-  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
-  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
-
-  # create a vector of scaled summer lengths to calculate at
-  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
-    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
-    pred_Delta_L_Pb_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
-
-  # extract summarize predicted growth
-  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
-  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
-  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]
-
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot(1,1, type = "n", 
-       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
-  )
-
-  # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
-
-  # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
-}
-
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
 ```
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
+       # ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
+       ylim = c(75,110),
        xlim = range(L_Pb_seq), 

### 2023-04-18 03-post-process/compare-sim-to-obs.Rmd
Update sim-vs-obs to use +/- 20% as okay range

@@
 
-  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 100)
+  breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.2, 1.4, 1.6, 1.8, 100)
   bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
@@
 
-  breaks = c(-1, -0.75, -0.5, -0.25, -0.1, 0.1, 0.25, 0.5, 0.75, 1)
+  breaks = c(-1, -0.8, -0.6, -0.4, -0.2, 0.2, 0.4, 0.6, 0.8, 1)
   bin_names = levels(cut(runif(1e6, -1, 1), breaks = breaks, include.lowest = TRUE))
@@
 
-Values close to 1 are ideal for the mean and CV ratios and cells are color-coded based on how far they fall from 1: less than 1 are blue and greater than 1 are red; values between 0.9 and 1.1 might be considered "good enough", and have been assigned no color.
-
-Values close to 0 are ideal for the autocorrelation differences and cells are color-coded based on how far they fall from zero: less than zero are blue and greater than zero are red; values between -0.1 and 0.1 might be considered "good enough", and have been assigned no color.
+Values close to 1 are ideal for the mean and CV ratios and cells are color-coded based on how far they fall from 1: less than 1 are blue and greater than 1 are red; values between 0.8 and 1.2 (i.e., <20% off) might be considered "good enough", and have been assigned no color.
+
+Values close to 0 are ideal for the autocorrelation differences and cells are color-coded based on how far they fall from zero: less than zero are blue and greater than zero are red; values between -0.2 and 0.2 might be considered "good enough", and have been assigned no color.
 

### 2023-04-18 03-post-process/compare-sim-to-obs.Rmd
Aesthetic updates to sim-vs-obs

@@
 ```{r ratio_plot fn}
-ratio_plot = function(ratios, line_y, pt_fn = mean, ...) {
+ratio_plot = function(ratios, line_y, pt_fn = mean, ylim = NULL, ylab = FALSE, ...) {
 
@@
   # set graphics parameters
-  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
+  par(mar = c(7,1.25,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
 
   # make an empty plot with the right dimensions
-  mp = barplot(summs["50%",], col = "white", ylab = "", border = "white", las = 2,
-               ylim = c(min(0, min(summs, na.rm = TRUE)), max(summs, na.rm = TRUE)) * 1.1, ...)
+  if (is.null(ylim)) {
+    ymin = 0
+    ymax = max(2, max(summs, na.rm = TRUE) * 1.025)
+  } else {
+    ymin = ylim[1]
+    ymax = ylim[2]
+  }
+
+  mp = barplot(summs["50%",], col = "white", xlab = "", border = "white", las = 2,
+               ylim = c(ymin, ymax), ylab = "", ...)
+
+  if (ylab) {
+    mtext(side = 2, line = 2.25, "Ratio (Sim:Obs)")
+  }
 
@@
   # create an "acceptable region"
-  usr = par("usr"); rect(usr[1], line_y - 0.25, usr[2], line_y + 0.25, col = "grey90", border = NA)
+  usr = par("usr"); rect(usr[1], line_y - 0.2, usr[2], line_y + 0.2, col = "grey90", border = NA)
   abline(h = line_y, lty = 2, col = "grey")
@@
 ratio_plots = function(x, main) {
-  par(mfrow = c(1,3), oma = c(0,2,2,0))
-  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", pt_fn = geomean, line_y = 1)
+  par(mfrow = c(1,3), oma = c(0,2.5,2,0))
+  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", pt_fn = geomean, line_y = 1, ylab = TRUE)
   ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", pt_fn = geomean, line_y = 1)
-  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", pt_fn = mean, line_y = 0)
-  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Ratio (Sim:Obs)")
+  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", pt_fn = mean, line_y = 0, ylim = c(-1,1))
   mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
@@
 ```{r vals_plot fn}
-vals_plot = function(vals, ...) {
+vals_plot = function(vals, legend = FALSE, ylab = FALSE, ...) {
   f = function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE)
@@
 
-  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
+  par(mar = c(7,1.25,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
   mp = barplot(summs[,"50%",], beside = TRUE, col = "white", border = "white", ylim = range(summs, na.rm = TRUE) + diff(range(summs, na.rm = TRUE)) * c(-0.05,0.05), xaxt = "n", ...)
-  segments(mp, summs[,"2.5%",], mp, summs[,"97.5%",], col = c("red", "blue"))
-  segments(mp, summs[,"25%",], mp, summs[,"75%",], col = c("red", "blue"), lwd = 6)
-  points(y = summs[,"50%",], x = mp, col = c("red", "blue"), pch = 3, cex = 1.5)
+
+  if (ylab) {
+    mtext(side = 2, line = 2.25, "Value")
+  }
+
+  segments(mp, summs[,"2.5%",], mp, summs[,"97.5%",], col = c("salmon", "royalblue"))
+  segments(mp, summs[,"25%",], mp, summs[,"75%",], col = c("salmon", "royalblue"), lwd = 6)
+  points(y = summs[,"50%",], x = mp, col = c("salmon", "royalblue"), pch = 3, cex = 1.5)
   axis(side = 1, at = colSums(mp)/2, labels = dimnames(summs)[[3]], las = 2)
   box()
+
+  if (legend) {
+    legend("topleft", legend = c("Obs", "Sim"), pch = 15, col = c("salmon", "royalblue"), pt.cex = 1.75, bty = "n")
+  }
 }
@@
 vals_plots = function(x, main) {
-  par(mfrow = c(1,3), oma = c(0,2,2,0))
-  vals_plot(x[,c("obs", "sim"),"cv",], main = "CV")
+  par(mfrow = c(1,3), oma = c(0,2.5,2,0))
+  vals_plot(x[,c("obs", "sim"),"cv",], main = "CV", legend = TRUE, ylab = TRUE)
   vals_plot(x[,c("obs", "sim"),"mean",], main = "Mean")
   vals_plot(x[,c("obs", "sim"),"acf",], main = "ACF")
-  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Value")
   mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)

### 2023-04-19 03-post-process/compare-sim-to-obs.Rmd

@@
     label: "Scenario"
-    value: "siw"
+    value: "base"
     input: text

### 2023-04-19 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

--- 2023-03-13 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
@@
                main = pops[j])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+### Realized & BH
+
+The blue shows the time series with variability explained only by Beverton-Holt dynamics.
+
+```{r phi_E_Pb_dot-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+
+  # draw on the posterior time series that includes BH prediction only
+  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", year = ts_yrs, pop = j)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+```
+
+### Realized & [BH + AR(1)]
+
+The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.
+
+```{r phi_E_Pb_dot2-plots, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs],
+               main = pops[j])
+
+  # draw on the posterior time series that includes BH prediction and the carry over residual from last year
+  # draw on the posterior time series that includes BH prediction only
+  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", year = ts_yrs, pop = j)),
+              yrs = all_yrs[ts_yrs])
 }

### 2023-04-19 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd

--- 2022-04-28 03-post-process/output-plots-children/06-capacity-vs-habitat.Rmd
@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
@@
 # select a subset of posterior samples at random to draw
-i = sample(1:post_dim(post, "saved"), 100, replace = FALSE)
+i = sample(1:post_dim(post, "saved"), min(100, post_dim(post, "saved")), replace = FALSE)
 

### 2023-04-19 03-post-process/output-plots-children/10-rho-params.Rmd

--- 2023-04-11 03-post-process/output-plots-children/09-rho-params.Rmd
@@
 
-# draw on the prior distribution
-rho_pr = post_summ(post, "rho_Lphi_Ma_O0_pr[2,1]", probs = c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975))
-rect(rho_pr["2.5%",], usr[3], rho_pr["97.5%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
-rect(rho_pr["10%",], usr[3], rho_pr["90%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
-rect(rho_pr["25%",], usr[3], rho_pr["75%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
+box_upr = mp - rbind(diff(mp)/2, NA)
+box_lwr = mp + rbind(diff(mp)/2, NA)
+box_upr[nrow(box_upr),] = box_upr[nrow(box_upr)-1,] + diff(box_upr[1:2])
+box_lwr[nrow(box_lwr),] = box_lwr[nrow(box_upr)-1,] + diff(box_lwr[1:2])
+
+# draw on the prior distribution for rho
+draw_rho_prior = function(param, box_lwr, box_upr) {
+  rho_pr = post_summ(post, paste0(param, "_pr[2,1]"), probs = c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975))
+  rect(rho_pr["2.5%",], box_lwr, rho_pr["97.5%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
+  rect(rho_pr["10%",], box_lwr, rho_pr["90%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
+  rect(rho_pr["25%",], box_lwr, rho_pr["75%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
   abline(v = 0, lty = 2)
+}
 
-# param = rownames(rho_mean_out)[4]
-# at_mp = mp[4,]
 pop_rhos = function(param, at_mp) {
@@
     y = at_mp + runif(6, -0.4, 0.4)
-    points(y ~ x["mean",], col = "salmon", pch = 3, lwd = 1.5)
-    segments(x["25%",], y, x["75%",], y, col = scales::alpha("salmon", 0.5))
+    points(y ~ x["mean",], col = "royalblue", pch = 3, lwd = 1.5)
+    # segments(x["25%",], y, x["75%",], y, col = scales::alpha("royalblue", 0.5))
   } 
@@
 
+junk = sapply(1:nrow(mp), function(i) draw_rho_prior(rownames(rho_mean_out)[i], box_lwr[i,], box_upr[i,]))
 junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))

### 2023-04-20 03-post-process/output-plots-children/06-length-based-survival.Rmd

@@
 
-## Parr $\to$ Smolt Overwinter Survival
+## Parr $\to$ Smolt Overwinter Survival {.tabset .tabset-pills}
 
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
+### Time Series {.tabset .tabset-pills}
+
+#### Fall Migrants {.tabset .tabset-pills}
+
+##### Realized Alone
+
+```{r phi_Pa_Mb_tseries-fall-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
+```
+
+##### Realized + Predicted
+
+```{r phi_Pa_Mb_tseries-fall-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+
+  # add the predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
+              yrs = all_yrs[t])
+
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
+```
+
+#### Spring Migrants {.tabset .tabset-pills}
+
+##### Realized Alone
+
+```{r phi_Pa_Mb_tseries-spring-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
+```
+
+##### Realized + Predicted
+
+```{r phi_Pa_Mb_tseries-spring-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+
+  # add the predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)),
+              yrs = all_yrs[ts_yrs])
+
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
+```
+
+### Mean Length Relationship {.tabset .tabset-pills}
+
+```{r}
+plot_f = function(j, i) {
 
@@
 }
+```
 
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
+#### Fall Migrants
+
+```{r phi_Pa_Mb_fall_relationship, fig.width = 6, fig.height = 5}
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f, i = 1)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
+```
+
+#### Spring Migrants
+
+```{r phi_Pa_Mb_spring_relationship, fig.width = 6, fig.height = 5}
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f, i = 2)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
+```
+
+## Smolt $\to$ LGR Survival {.tabset .tabset-pills}
+
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r phi_Mb_Ma_tseries-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
 }
 
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Smolt to LGR Survival (NOR)")
 ```
 
-## Smolt Survival to LGR
+#### Realized + Predicted
+
+```{r phi_Mb_Ma_tseries-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # draw the realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
+               main = pops[j], yrs = all_yrs[ts_yrs]
+  )
+
+  # add the predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Mb_Ma_dot[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)),
+              yrs = all_yrs[ts_yrs])
+
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, "Smolt to LGR Survival (NOR)")
+```
+
+### Mean Length Relationship
 

### 2023-04-27 03-post-process/output-plots-children/05-length.Rmd
Use common y-axis limits for some output plots
The mean length figures and length-based survival figures. Better shows among-population/LH type heterogeneity. Should consider doing this for other plots as well.

--- 2023-04-12 03-post-process/output-plots-children/05-length.Rmd
@@
 ## Parr Mean Length {.tabset .tabset-pills}
+
+```{r L_Pb_lim}
+L_Pb_lim = make_lim_param(post, "^L_Pb[year,")
+```
 
@@
   plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
   )
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
+       # ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
+       ylim = L_Pb_lim,
        xlim = range(0, E_scaled_seq), 
@@
 
+## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}
+
+```{r Delta_L_Pb_Mb_lim}
+Delta_L_Pb_Mb_lim = make_lim_param(post, "^Delta_L_Pb_Mb[year,")
+```
+
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & "Data"
+
+```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+#### Realized & Predicted
+
+```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+  # draw the realized time series
+  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+
+  # draw the predicted time series
+  add_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb_dot[year,pop]", pop = j, year = ts_yrs)),
+              yrs = all_yrs[ts_yrs])
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, "Brood Year")
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+```
+
+### Relationship
+
+```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
+plot_f = function(j) {
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # extract posterior summaries of growth outcomes
+  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
+  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
+  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]
+
+  # create a vector of scaled summer lengths to calculate at
+  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
+  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # extract posteriors of coefficients
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted curves for one posterior sample
+  pred_fn = function(i) {
+    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
+    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
+    pred_Delta_L_Pb_Mb
+  }
+
+  # calculate predicted growth values and add to posterior samples
+  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))
+
+  # extract summarize predicted growth
+  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, ".")["mean",]
+  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["2.5%",]
+  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, ".")["97.5%",]
+
+  # make a blank plot with the correct dimensions
+  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
+  plot(1,1, type = "n", 
+       # ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
+       ylim = Delta_L_Pb_Mb_lim,
+       xlim = range(L_Pb_seq), 
+       main = pops[j]
+  )
+
+  # expected relationship
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
+  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
+  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+
+  # realized pairs
+  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
+  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
+  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+}
+
+par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+junk = sapply(1:jags_data$nj, plot_f)
+mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
+mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
+```
+
 ## Smolt Mean Length {.tabset .tabset-pills}
+
+```{r L_Mb_lim}
+L_Mb_lim = make_lim_param(post, "^L_Mb[year,")
+```
 
@@
   plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
   )
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
-       xlim = range(L_Pb_seq), 
+       # ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
+       # ylim = c(75,110),
+       # xlim = range(L_Pb_seq), 
+       xlim = L_Pb_lim,
+       ylim = L_Mb_lim,
        main = pops[j]

### 2023-04-27 01-functions/plot-fns.R

@@ -316,3 +316,18 @@ compare_BH = function(post_list, pop, main = "", legend = "topleft", cols = NULL
     legend(legend, legend = names(post_list), pch = 15, col = cols, pt.cex = 2, bty = "n")
   }
 }
+
+##### GENERALIZED PLOTTING FUNCTIONS #####
+
+# given a parameter name, return the axis limits that would include the 95% CRI
+make_lim_param = function(post, param) {
+  
+  # which rows of post_summ() output should be used in calculating axis limits
+  use_in_lim = c(FALSE, FALSE, FALSE, TRUE, TRUE)
+  
+  # get the range of relevant posterior summaries
+  sub_index(sub_index(param, year = ts_yrs)) |>
+    post_summ(post, param = _) |>
+    subset(use_in_lim) |>
+    range()
+}

### 2023-04-27 03-post-process/output-plots-children/06-length-based-survival.Rmd

@@
 ## Parr $\to$ Smolt Overwinter Survival {.tabset .tabset-pills}
+
+```{r phi_Pa_Mb_lim}
+phi_Pa_Mb_lim = make_lim_param(post, "^phi_Pa_Mb[")
+```
 
@@
   plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
   )
@@
   plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
   )
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
+       # ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
+       ylim = phi_Pa_Mb_lim,
        xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
+       main = pops[j]
   )
@@
 
+```{r phi_Mb_Ma_lim}
+phi_Mb_Ma_lim = sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = ".", LH_type = i_spring, origin = o_nor) |>
+  make_lim_param(post, param = _)
+```
+
 ### Time Series {.tabset .tabset-pills}
@@
   plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
-               main = pops[j], yrs = all_yrs[ts_yrs]
+               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
   )
@@
   plot(1,1, type = "n", 
-       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
+       # ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
+       ylim = phi_Mb_Ma_lim,
        xlim = range(L_Mb_seq), 

### 2023-05-02 01-functions/plot-fns.R
Add new plotting infrastructure
* make_lim()
* panel_label()
* axis_labels()
* mypar()

@@ -52,7 +52,53 @@ get_obs_ests_log_normal = function(lmean, lsig) {
   return(out)
 }
 
-##### PLOT A TIME SERIES OF ESTIMATES, WITH DATA IF AVAILABLE #####
+##### PLOTTING INFRASTRUCTURE FUNCTIONS #####
+
+# create a nice axis limit
+make_lim = function(..., buffer = c(0, 0.1)) {
+  lim = range(..., na.rm = TRUE)
+  lim_diff = diff(lim)
+  lim = lim + lim_diff * buffer
+  lim
+}
+
+# include a label in the corner of a plot
+panel_label = function(label_text, label_loc = "topleft", cex = 1,
+                       font = 2, x_inp = 0.015, y_inp = 0.05, col = par("col.axis"), ...) {
+  
+  accepted = c("topleft", "topright", "bottomleft", "bottomright")
+  
+  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+  
+  is_left = stringr::str_detect(label_loc, "left")
+  is_top = stringr::str_detect(label_loc, "top")
+  xsign = ifelse(is_left, -1, 1)
+  ysign = ifelse(is_top, -1, 1)
+  xi = ifelse(is_left, 1, 2)
+  yi = ifelse(is_top, 4, 3)
+  pos = ifelse(is_left, 4, 2)
+  
+  text(x = usr[xi] + xsign * xdiff * x_inp,
+       y = usr[yi] + ysign * ydiff * y_inp,
+       labels = label_text, cex = cex, pos = pos, font = font, col = col, ...)
+}
+
+# draw axes labels
+axis_labels = function(xlab = NULL, ylab = NULL, xline = 0.4, yline = 0.4, outer = TRUE, ...) {
+  mtext(side = 1, line = xline, text = xlab, outer = outer, ...)
+  mtext(side = 2, line = yline, text = ylab, outer = outer, ...)
+} 
+
+# default par()
+mypar = function(mar = c(1,1,0.5,0.5),
+                 mfrow = c(2,2), 
+                 oma = c(1.5,1.5,0,0), mgp = c(200,0.05,0), 
+                 tcl = 0, lend = "square",
+                 ljoin = "mitre",
+                 col.axis = "grey40", cex.axis = 0.85, ...) {
+  
+  do.call(par, c(as.list(environment()), list(...)))
+}
 
 # est: output from postpack::post_summ()
 # obs: optional vector of observed data to plot on top of estimates

### 2023-05-02 01-functions/plot-fns.R
Update plot_tseries() function

@@ -100,64 +100,57 @@ mypar = function(mar = c(1,1,0.5,0.5),
   do.call(par, c(as.list(environment()), list(...)))
 }
 
-# est: output from postpack::post_summ()
-# obs: optional vector of observed data to plot on top of estimates
-# main: plot title
-# xaxis: plot the xaxis?
-# yaxis_side: 2 or 4 or NULL, where should the y-axis be placed?
-# set_par: set some par() options internally?
 
-plot_tseries = function(est, obs = NULL, main = NULL, xaxis = T, yaxis_side = 2, set_par = T, ylim = NULL, yrs = NULL) {
+##### PLOT A TIME SERIES OF ESTIMATES, WITH DATA IF AVAILABLE #####
+
+plot_tseries = function(est, obs = NULL, ylim = NULL, yrs = NULL, xaxis = TRUE, yaxis_side = 2, label_text = NULL, label_loc = "topleft", y_scale = 1, pt_cex = 1.3) {
   
   # extract year labels
   if (is.null(yrs)) {
     yrs = as.numeric(rownames(obs))
   }
   
+  est = est/y_scale
+  obs = obs/y_scale
+  
   # set y limits
   if (is.null(ylim)) {
-    ylim = range(list(est[c("2.5%", "97.5%"),], obs), na.rm = T)
+    ylim = make_lim(list(est[c("2.5%", "97.5%"),], obs))
   }
-  
-  # set the graphics device parameters
-  if (set_par) par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
   
   # create empty plot with correct dimensions/labels
   plot(1,1, type = "n", 
        xlim = range(yrs), ylim = ylim,
-       xlab = "", las = 1, ylab = "", main = main, xaxt = "n", yaxt = "n")
+       xlab = "", ylab = "", main = "", xaxt = "n", yaxt = "n")
   
   # draw band representing 95% credible region
-  polygon(x = c(yrs, rev(yrs)), y = c(est["2.5%",], rev(est["97.5%",])), border = NA, col = alpha("salmon", 0.5))
-  lines(est["2.5%",] ~ yrs, col = "red", lty = 2)
-  lines(est["97.5%",] ~ yrs, col = "red", lty = 2)
[…]

### 2023-05-02 03-post-process/output-plots.Rmd
Fix small file path bug introduced by recent changes
Very minor: I changed the output file to be called "output_scenario.rds" instead of "output-scenario.rds" in a commit as part of #185
Create new figure settings section in output-plots

@@
 # read information from this model
-model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))
+model_info = readRDS(file.path(in_dir, paste0("output_", params$scenario, ".rds")))
 
@@
 
+```{r set-plot-opts}
+# select main colors
+main_cols = c(
+  "model" = "salmon",
+  "model2" = "forestgreen",
+  "data" = "royalblue"
+)
+
+# set the transparent versions based on main color
+tran_cols = sapply(main_cols, scales::alpha, alpha = 0.25)
+
+# size of points on figures
+pt_cex = 1.4
+
+# figure dimensions: a figure of two panels (inches)
+p2_width = 6.5
+p2_height = 2.75
+
+# figure dimensions: a figure of three panels (inches)
+p3_width = 6.5
+p3_height = 2
+
+# figure dimensions: a figure of four panels (inches)
+p4_width = 6.5
+p4_height = 4.5
+
+# figure dimensions: a figure of 6 panels (inches)
+p6_width = 6.5
+p6_height = 3.75
+
+# actual ylim to use for [0,1]
+# allows showing panel label in upper corner
+ylim_01 = c(0, 1.05)
+```
+
 ```{r model-info, child = "output-plots-children/01-model-info.Rmd"}

### 2023-05-02 03-post-process/output-plots-children/03-fit-to-data.Rmd
Consistency updates: 03-fit-to-data.Rmd

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Fit to Data {.tabset .tabset-pills}
@@
 
-```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
+```{r fall-trap-N-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
+               obs = get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
+               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
+axis_labels("Brood Year", "Fall Parr Abundance (1000s)")
 ```
@@
 
-```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
+```{r spring-trap-N-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
-               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
+               obs = get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
+               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
+axis_labels("Brood Year", "Spring Smolt Abundance (1000s)")
 ```
@@
 
-```{r adult-N-fit, fig.width = 6, fig.height = 5}
+```{r adult-N-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
+               obs = get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
+               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000, pt_cex = pt_cex)
+
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
+axis_labels("Return Year", "Adult Return Abundance (1000s)")
 ```
@@
 
-```{r summer-surv-fit, fig.width = 6, fig.height = 5}
+```{r summer-surv-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
+axis_labels("Brood Year", "Summer Parr \u2192 LGR Survival")
 ```
@@
 
-```{r fall-surv-fit, fig.width = 6, fig.height = 5}
+```{r fall-surv-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
+axis_labels("Brood Year", "Fall Parr \u2192 LGR Survival")
 ```
@@
 
-```{r winter-surv-fit, fig.width = 6, fig.height = 5}
+```{r winter-surv-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
-               main = pops[j],
-               yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
+axis_labels("Brood Year", "Winter Parr \u2192 LGR Survival")
 ```
@@
 
-```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
+```{r spring-surv-fit-nor, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
+axis_labels("Brood Year", "Spring Smolt \u2192 LGR Survival (NOR)")
 ```
@@
 
-```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
+```{r spring-surv-fit-hor, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
-               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
-               main = pops[j], yrs = all_yrs[ts_yrs])
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
+axis_labels("Brood Year", "Spring Smolt \u2192 LGR Survival (HOR)")
 ```
 
-#### LGR Smolt $\rightarrow O_0$ (NOR)
+#### LGR Smolt $\rightarrow$ BON
 
-```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
+```{r hydro-down-surv-fit, fig.width = p2_width, fig.height = p2_height}
+# function to create the plot for one origin type
+plot_f = function(o) {
+  plot_tseries(est = post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o)),
+               obs = get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o], jags_data$sig_Lphi_obs_Ma_O0[observable,o]),
+               label_text = c("NOR", "HOR")[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
+}
+
+# loop over origins
+mypar(mfrow = c(1,2))
+junk = sapply(1:jags_data$no, plot_f)
+axis_labels("Brood Year", "LGR Smolt \u2192 BON")
 ```
 
-#### LGR Smolt $\rightarrow O_0$ (HOR)
+#### BON Adults $\rightarrow$ LGR
 
-```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
-             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
+```{r hydro-up-nor-surv-fit, fig.width = p2_width, fig.height = p2_height}
+# function to create the plot for one origin type
+plot_f = function(o) {
+  plot_tseries(est = post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o)),
+               obs = get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o], jags_data$x_BON[observable,o] - jags_data$x_LGR[observable,o]), 1),
+               label_text = c("NOR", "HOR")[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
+}
 
-#### BON Adults $\rightarrow$ LGR (NOR)
-
-```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
-```
-
-#### BON Adults $\rightarrow$ LGR (HOR)
-
-```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
-par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
-plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
-             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
-             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
-             yrs = all_yrs[ts_yrs])
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Survival")
+# loop over origins
+mypar(mfrow = c(1,2))
+junk = sapply(1:jags_data$no, plot_f)
+axis_labels("Brood Year", "BON \u2192 LGR Survival")
 ```
@@
 ```{r weir-comp-fit-funcs}
-
 # for multinomial sample size
 weir_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
+  mypar(mfrow = c(1,1))
+  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = tran_cols["data"], border = main_cols["data"],
+               ylim = make_lim(0, jags_data$nx_Ra[observable,j]),
+               xlab = "", ylab = "")
   usr = par("usr")
@@
   segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
+  axis_labels("Return Year", "Weir Sample Size")
 }
@@
 
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
+  base_param = sub_index("^p_Ra[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = paste0("Age-", rep(jags_data$kmin:jags_data$kmax, jags_data$no), " (", rep(c("NOR", "HOR"), each = jags_data$nk), ")")
 
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+  # function to draw the time series for one panel: one population/age/origin combo
+  plot_f = function(ko) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(ko))),
+                 obs = get_obs_ests_multinomial(jags_data$x_Ra[observable,,j], ko),
+                 label_text = labels[ko], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
+  }
+
+  mypar(mfrow = c(2,3))
+  junk = sapply(1:jags_data$nko, plot_f)
+  axis_labels("Return Year", "Proportion of Return")
 }
@@
 weir_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+
+  base_param = sub_index("^p_Ra_age[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = paste0("Age-", jags_data$kmin:jags_data$kmax)
+
+  # function to draw the time series for one panel: one population/age combo
+  plot_f = function(k) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(k))),
+                 obs = get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_age_obs[observable,,j], k),
+                 label_text = labels[k], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
+  }
+
+  mypar(mfrow = c(1,3))
+  junk = sapply(1:jags_data$nk, plot_f)
+  axis_labels("Return Year", "Proportion of Return")
 }
@@
 weir_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
 
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+  base_param = sub_index("^p_Ra_origin[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = c("NOR", "HOR")
+
+  # function to draw the time series for one panel: one population/origin combo
+  plot_f = function(o) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(o))),
+                 obs = get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], o),
+                 label_text = labels[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
+  }
+
+  mypar(mfrow = c(1,2))
+  junk = sapply(1:jags_data$no, plot_f)
+  axis_labels("Return Year", "Proportion of Return")
 }
@@
 
-```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
+```{r cat-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
 weir_comp_fit_plot(j_cat)
@@
 
-```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
+```{r los-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
 weir_comp_fit_plot(j_los)
@@
 
-```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
+```{r min-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
 weir_comp_fit_plot(j_min)
@@
 
-```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
+```{r ugr-weir-comp-fit, fig.width = p6_width, fig.height = p6_height}
 weir_comp_fit_plot(j_ugr)
@@
 
-```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r cat-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 weir_comp_fit_plot_age(j_cat)
@@
 
-```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r los-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 weir_comp_fit_plot_age(j_los)
@@
 
-```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r min-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 weir_comp_fit_plot_age(j_min)
@@
 
-```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r ugr-weir-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 weir_comp_fit_plot_age(j_ugr)
@@
 
-```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r cat-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 weir_comp_fit_plot_origin(j_cat)
@@
 
-```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r los-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 weir_comp_fit_plot_origin(j_los)
@@
 
-```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r min-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 weir_comp_fit_plot_origin(j_min)
@@
 
-```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r ugr-weir-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 weir_comp_fit_plot_origin(j_ugr)
@@
 
-```{r cat-weir-ss, fig.width = 6, fig.height = 4}
+```{r cat-weir-ss, fig.width = 5, fig.height = 2.5}
 weir_sample_size(j_cat)
@@
 
-```{r los-weir-ss, fig.width = 6, fig.height = 4}
+```{r los-weir-ss, fig.width = 5, fig.height = 2.5}
 weir_sample_size(j_los)
@@
 
-```{r min-weir-ss, fig.width = 6, fig.height = 4}
+```{r min-weir-ss, fig.width = 5, fig.height = 2.5}
 weir_sample_size(j_min)
@@
 
-```{r ugr-weir-ss, fig.width = 6, fig.height = 4}
+```{r ugr-weir-ss, fig.width = 5, fig.height = 2.5}
 weir_sample_size(j_ugr)
@@
 ```{r carc-comp-fit-funcs}
-
 # for multinomial sample size
 carc_sample_size = function(j) {
-  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
-               ylim = c(0, max(jags_data$nx_Sa_prime[observable,j], na.rm = TRUE)),
-               xlab = "Return Year", ylab = "Carcasses Sampled for Composition")
+  mypar(mfrow = c(1,1))
+  mp = barplot(jags_data$nx_Sa_prime[observable,j], xaxt = "n", col = tran_cols["data"], border = main_cols["data"],
+               ylim = make_lim(0, max(jags_data$nx_Sa_prime[observable,j])),
+               xlab = "", ylab = "")
   usr = par("usr")
@@
   segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
+  axis_labels("Return Year", "Carcass Sample Size")
 }
@@
 
-  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
+  base_param = sub_index("^p_Sa_prime[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = paste0("Age-", rep(jags_data$kmin:jags_data$kmax, jags_data$no), " (", rep(c("NOR", "HOR"), each = jags_data$nk), ")")
+
+  # function to draw the time series for one panel: one population/age/origin combo
+  plot_f = function(ko) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(ko))),
+                 obs = get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], ko),
+                 label_text = labels[ko], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
+  }
+
+  mypar(mfrow = c(2,3))
+  junk = sapply(1:jags_data$nko, plot_f)
+  axis_labels("Return Year", "Proportion of Carcasses")
 }
@@
 carc_comp_fit_plot_age = function(j) {
-  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+
+  base_param = sub_index("^p_Sa_prime_age[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = paste0("Age-", jags_data$kmin:jags_data$kmax)
+
+  # function to draw the time series for one panel: one population/age combo
+  plot_f = function(k) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(k))),
+                 obs = get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_age_obs[observable,,j], k),
+                 label_text = labels[k], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
+  }
+
+  mypar(mfrow = c(1,3))
+  junk = sapply(1:jags_data$nk, plot_f)
+  axis_labels("Return Year", "Proportion of Carcasses")
 }
@@
 carc_comp_fit_plot_origin = function(j) {
-  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 1), main = TeX("$NOR$"), yrs = all_yrs[ts_yrs])
-  plot_tseries(post_summ(post, sub_index("^p_Sa_prime_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], 2), main = TeX("$HOR$"), yrs = all_yrs[ts_yrs])
-  mtext(side = 1, outer = T, line = 0.25, "Return Year")
-  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
+
+  base_param = sub_index("^p_Sa_prime_origin[year,DIM,pop]$", pop = j, year = ts_yrs)
+  labels = c("NOR", "HOR")
+
+  # function to draw the time series for one panel: one population/origin combo
+  plot_f = function(o) {
+    plot_tseries(est = post_summ(post, stringr::str_replace(base_param, "DIM", as.character(o))),
+                 obs = get_obs_ests_multinomial(x_Sa_prime_new_obs$x_Sa_prime_origin_obs[observable,,j], o),
+                 label_text = labels[o], yrs = all_yrs[ts_yrs], pt_cex = pt_cex, ylim = ylim_01)
   }
 
+  mypar(mfrow = c(1,2))
+  junk = sapply(1:jags_data$no, plot_f)
+  axis_labels("Return Year", "Proportion of Carcasses")
+}
 ```
@@
 
-```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
+```{r cat-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
 carc_comp_fit_plot(j_cat)
@@
 
-```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
+```{r los-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
 carc_comp_fit_plot(j_los)
@@
 
-```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
+```{r min-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
 carc_comp_fit_plot(j_min)
@@
 
-```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
+```{r ugr-carc-comp-fit, fig.width = p6_width, fig.height = p6_height}
 carc_comp_fit_plot(j_ugr)
@@
 
-```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r cat-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 carc_comp_fit_plot_age(j_cat)
@@
 
-```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r los-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 carc_comp_fit_plot_age(j_los)
@@
 
-```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r min-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 carc_comp_fit_plot_age(j_min)
@@
 
-```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
+```{r ugr-carc-comp-fit-age, fig.width = p3_width, fig.height = p3_height}
 carc_comp_fit_plot_age(j_ugr)
@@
 
-```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r cat-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 carc_comp_fit_plot_origin(j_cat)
@@
 
-```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r los-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 carc_comp_fit_plot_origin(j_los)
@@
 
-```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r min-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 carc_comp_fit_plot_origin(j_min)
@@
 
-```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
+```{r ugr-carc-comp-fit-origin, fig.width = p2_width, fig.height = p2_height}
 carc_comp_fit_plot_origin(j_ugr)
@@
 
-```{r cat-carc-ss, fig.width = 6, fig.height = 4}
+```{r cat-carc-ss, fig.width = 5, fig.height = 2.5}
 carc_sample_size(j_cat)
@@
 
-```{r los-carc-ss, fig.width = 6, fig.height = 4}
+```{r los-carc-ss, fig.width = 5, fig.height = 2.5}
 carc_sample_size(j_los)
@@
 
-```{r min-carc-ss, fig.width = 6, fig.height = 4}
+```{r min-carc-ss, fig.width = 5, fig.height = 2.5}
 carc_sample_size(j_min)
@@
 
-```{r ugr-carc-ss, fig.width = 6, fig.height = 4}
+```{r ugr-carc-ss, fig.width = 5, fig.height = 2.5}
 carc_sample_size(j_ugr)
@@
 
-```{r spawn-status-fits, fig.width = 8, fig.height = 5}
-par(oma = c(2,2,0,0))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
+```{r spawn-status-fits, fig.width = p6_width, fig.height = p6_height}
+plot_f = function(j) {
+  # top plot: pre-spawn survival time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
+               obs = get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
+               label_text = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs], pt_cex = pt_cex, label_loc = "bottomleft")
 
-plot_f = function(j) {
-  par(yaxs = "r")
-  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               main = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs])
-  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
-
-  if (j == 1) mtext(side = 2, "Survival Probability", line = 2)
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = c(0, max(jags_data$x_carcass_total, na.rm = T)) + c(0, 5))
-  at_x = seq(1, length(observable), 4)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$carcs_sampled[observable,j]), 3, 4)[at_x])
+  if (j == 1) mtext(side = 2, "Pre-Spawn Survival", line = 1, cex = 0.9)
+  # om = par("mar"); nm = om; nm[1] = 2; par(mar = nm); on.exit(par(mar = om))
+  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = make_lim(0, jags_data$x_carcass_total),
+               col = tran_cols["data"], border = main_cols["data"])
+  at_x = axisTicks(par("usr")[1:2], log = FALSE)
+  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$x_carcass_total[observable,j]), 3, 4)[at_x])
   box()
 
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 2)
+  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 1, cex = 0.9)
 }
 
+mypar(mfrow = c(1,1))
+layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
 junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Return Year")
 ```
@@
 
-```{r summer-length-fit, fig.width = 6, fig.height = 5}
+```{r summer-length-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               obs = get_obs_ests_log_normal(log(jags_data$L_Pb_obs[observable,j]), jags_data$sig_L_Pb_obs[observable,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Summer Tagging (mm)")
+axis_labels("Brood Year", "Parr Mean Length (mm)")
 ```
@@
 
-```{r spring-length-fit, fig.width = 6, fig.height = 5}
+```{r spring-length-fit, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               obs = get_obs_ests_log_normal(log(jags_data$L_Mb_obs[observable,j]), jags_data$sig_L_Mb_obs[observable,j]),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Mean Length at Spring Tagging (mm)")
+axis_labels("Brood Year", "Smolt Mean Length (mm)")
 ```

### 2023-05-03 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Consistency updates: 04-fit-to-data.Rmd

--- 2023-03-13 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
@@
 
-## Survival Time Series
+## Survival Time Series {.tabset .tabset-pills}
 
-```{r phi_E_Pb-plots, fig.width = 6, fig.height = 5}
+These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.
+
+### Realized Alone
+
+Just the realized time series shown.
+
+```{r phi_E_Pb-plots, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs], label_text = pops[j])
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+# loop over populations
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+axis_labels("Brood Year", "Egg \u2192 Parr Survival")
+```
+
+### Realized & BH
+
+The blue shows the time series with variability explained only by Beverton-Holt dynamics.
+
+```{r phi_E_Pb_dot-plots, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
+plot_f = function(j) {
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs], label_text = pops[j])
+
+  # time series that includes BH prediction only
+  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", year = ts_yrs, pop = j)),
+              yrs = all_yrs[ts_yrs])
+}
+
+# loop over populations
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Egg \u2192 Parr Survival")
+```
+
+### Realized & [BH + AR(1)]
+
+The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.
+
+```{r phi_E_Pb_dot2-plots, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
+plot_f = function(j) {
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
+               yrs = all_yrs[ts_yrs], label_text = pops[j])
+
+  # time series that includes BH prediction only
+  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", year = ts_yrs, pop = j)),
+              yrs = all_yrs[ts_yrs])
+}
+
+# loop over populations
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Egg \u2192 Parr Survival")
 ```
@@
 
-```{r egg-surv-vs-eggs, fig.width = 6, fig.height = 5}
+```{r egg-surv-vs-eggs, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
@@
 
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+  # empty plot
+  plot(1, 1, type = "n", xlim = range(0, E["97.5%",]),
+       ylim = range(0, phi_E_Pb["97.5%",], phi_E_Pb_pred["97.5%",]),
+       xlab = "", ylab = "", xaxt = "n", yaxt = "n")
 
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, phi_E_Pb[5,], phi_E_Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
+  # add panel label
+  panel_label(pops[j], "topright")
 
@@
   # draw fitted relationship
-  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred[4,], rev(phi_E_Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(phi_E_Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(phi_E_Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(phi_E_Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
+  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred["2.5%",], rev(phi_E_Pb_pred["97.5%",])), col = tran_cols["model"], border = NA)
+  lines(phi_E_Pb_pred["mean",] ~ E_pred, col = main_cols["model"], lwd = 2)
 
   # draw state pairs + uncertainty
-  segments(E[4,], phi_E_Pb[3,], E[5,], phi_E_Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], phi_E_Pb[4,], E[3,], phi_E_Pb[5,], col = alpha("red", 0.5))
-  points(phi_E_Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(phi_E_Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  segments(E["2.5%",], phi_E_Pb["mean",], E["97.5%",], phi_E_Pb["mean",], col = main_cols["model"])
+  segments(E["mean",], phi_E_Pb["2.5%",], E["mean",], phi_E_Pb["97.5%",], col = main_cols["model"])
+  points(phi_E_Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
+  text(phi_E_Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
+axis_labels("Total Egg Production (Millions)", "Egg \u2192 Parr Survival")
 ```
@@
 
-```{r eggs-to-parr, fig.width = 6, fig.height = 5}
+```{r eggs-to-parr, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
@@
   bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # extract posterior summaries of total spawners by brood year
-  # Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))
 
@@
   # predict parr recruits along a sequence of spawner abundances
-  # Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
-  E_pred = seq(0, max(E[5,]), length = 30)
+  E_pred = seq(0, max(E[c("2.5%", "97.5%"),]), length = 30)
 
@@
 
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
+  # empty plot
+  plot(1, 1, type = "n", xlim = range(0, E["97.5%",]), ylim = range(0, Pb["97.5%",], Pb_pred["97.5%",]),
+       xlab = "", ylab = "", xaxt = "n", yaxt = "n")
 
-  # empty plot
-  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
-       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])
+  panel_label(pops[j])
 
@@
   # draw fitted relationship: Bayesian
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
-  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
-  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)
+  polygon(c(E_pred, rev(E_pred)), c(Pb_pred["2.5%",], rev(Pb_pred["97.5%",])), col = tran_cols["model"], border = NA)
+  lines(Pb_pred["mean",] ~ E_pred, col = main_cols["model"], lwd = 2)
 
   # draw state pairs + uncertainty
-  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
-  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
-  points(Pb[3,] ~ E[3,], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
-  text(Pb[3,] ~ E[3,], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  segments(E["2.5%",], Pb["mean",], E["97.5%",], Pb["mean",], col = main_cols["model"])
+  segments(E["mean",], Pb["2.5%",], E["mean",], Pb["97.5%",], col = main_cols["model"])
+  points(Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
+  text(Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
-mtext(side = 2, outer = T, line = 0.25, "Parr Recruits (Thousands)")
+axis_labels("Total Egg Production (Millions)", "Parr Recruits (Thousands)")
 ```
@@
 
-```{r eggs-vs-spawners, fig.width = 6, fig.height = 5}
+```{r eggs-vs-spawners, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
@@
 
-  # graphical parameters
-  par(mar = c(1.5,1.5,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
-
   # empty plot
@@
        xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
-       ylab = "", xlab = "", las = 1, yaxt = "n")
+       ylab = "", xlab = "", yaxt = "n")
+  panel_label(pops[j])
 
@@
 
-  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
-  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
-  points(E["mean",] ~ Sa_tot["mean",], pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = main_cols["model"])
+  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = main_cols["model"])
+  points(E["mean",] ~ Sa_tot["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
   text(E["mean",] ~ Sa_tot["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
@@
   if (j == 1) {
-    legend("bottomright", title = "If Each Spawner Had:",
-           legend = c("1000 Eggs", "1800 Eggs", "3600 Eggs"),
+    legend("bottomright", title = "Eggs/Spawner:",
+           legend = c("1,000", "1,800", "3,600"),
            lty = c(1,2,3), bty = "n", cex = 0.75)
@@
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
-mtext(side = 2, outer = T, line = 0.25, "Total Egg Production (Millions)")
+axis_labels("Total Spawners", "Total Egg Production (Millions)")
 ```

### 2023-05-03 03-post-process/output-plots.Rmd
Consistency updates: 04-fit-to-data.Rmd

@@
 # set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
+knitr::opts_chunk$set(echo = FALSE, fig.align = "center", dpi = 600, out.width = "75%")
 
@@
   "model" = "salmon",
-  "model2" = "forestgreen",
+  "model2" = "royalblue",
   "data" = "royalblue"

### 2023-05-03 01-functions/plot-fns.R

@@ -111,7 +111,8 @@ plot_tseries = function(est, obs = NULL, ylim = NULL, yrs = NULL, xaxis = TRUE, 
   }
   
   est = est/y_scale
-  obs = obs/y_scale
+  
+  if (!is.null(obs)) obs = obs/y_scale
   
   # set y limits
   if (is.null(ylim)) {

### 2023-05-03 03-post-process/output-plots-children/05-length.Rmd
Consistency updates: 05-length.Rmd

@@
 
-```{r L_Pb_tseries-1, fig.width = 6, fig.height = 5}
+```{r L_Pb_tseries-1, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
 
-  # draw the realized time series
+  # realized time series
   plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
   )
@@
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
+axis_labels("Brood Year", "Parr Mean Length (mm)")
 ```
@@
 
-```{r L_Pb_tseries-2, fig.width = 6, fig.height = 5}
+```{r L_Pb_tseries-2, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
 
-  # draw the realized time series
+  # realized time series
   plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
   )
 
-  # draw the predicted time series
+  # predicted time series
   add_tseries(est = post_summ(post, sub_index("^L_Pb_dot[year,pop]", pop = j, year = ts_yrs)),
@@
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
+axis_labels("Brood Year", "Parr Mean Length (mm)")
+
 ```
@@
 
-```{r L_Pb-relationship, fig.width = 6, fig.height = 5}
+```{r L_Pb-relationship, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
@@
 
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-
   plot(1,1, type = "n", 
-       # ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
        ylim = L_Pb_lim,
-       xlim = range(0, E_scaled_seq), 
-       main = pops[j]
+       xlim = range(0, E_scaled_seq)
   )
+  panel_label(pops[j], "topright")
 
   # expected relationship
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)
+  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = tran_cols["model"])
+  lines(pred_L_Pb_mean ~ E_scaled_seq, col = main_cols["model"], lwd = 2)
 
   # realized pairs
-  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
-  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
-  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = main_cols["model"])
+  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = main_cols["model"])
+  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
   text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  box(col = par("col.axis"))
 }
 
-xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, xlab)
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\,(mm)$"))
+axis_labels(
+  paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)"),
+  "Parr Mean Length (mm)"
+)
 ```
@@
 
-```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
+```{r Delta_L_Pb_Mb-1, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
 ```
@@
 
-```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
+```{r Delta_L_Pb_Mb-2, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
   Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               obs = Delta_L_Pb_Mb_obs, label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim, pt_cex = pt_cex)
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
 ```
@@
 
-```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
+```{r Delta_L_Pb_Mb-3, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
   # draw the realized time series
-  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
+  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
 
@@
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
+axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
 ```
@@
 
-```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
+```{r Delta_L_Pb_Mb-relationship, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
@@
 
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
   plot(1,1, type = "n", 
-       # ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
        ylim = Delta_L_Pb_Mb_lim,
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
+       xlim = range(L_Pb_seq)
   )
+  panel_label(pops[j], "topright")
 
   # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = tran_cols["model"])
+  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)
 
   # realized pairs
-  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
-  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = main_cols["model"])
+  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = main_cols["model"])
+  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
   text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+
+  box(col = par("col.axis"))
+
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
-mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
+axis_labels("Parr Mean Length (mm)", "Parr \u2192 Smolt Growth Factor")
 ```
@@
 
-```{r L_Mb-tseries-1, fig.width = 6, fig.height = 5}
+```{r L_Mb-tseries-1, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
 
-  # draw the realized time series
+  # realized time series
   plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
   )
@@
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
+axis_labels("Brood Year", "Smolt Mean Length (mm)")
 ```
@@
 
-```{r L_Mb-tseries-2, fig.width = 6, fig.height = 5}
+```{r L_Mb-tseries-2, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
 
-  # draw the realized time series
+  # realized time series
   plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
-               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
   )
@@
 
-```{r L_Mb-v-L_Pb, fig.width = 6, fig.height = 5}
-plot_fn = function(j) {
+```{r L_Mb-v-L_Pb, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
 
@@
 
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
   plot(1,1, type = "n", 
-       # ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
-       # ylim = c(75,110),
-       # xlim = range(L_Pb_seq), 
        xlim = L_Pb_lim,
-       ylim = L_Mb_lim,
-       main = pops[j]
+       ylim = L_Mb_lim
   )
 
+  panel_label(pops[j])
+
   # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = tran_cols["model"])
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)
 
   # realized pairs
-  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
-  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = main_cols["model"])
+  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = main_cols["model"])
+  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
   text(L_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  box(col = par("col.axis"))
+
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Parr Mean Length (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Parr Mean Length (mm)", "Smolt Mean Length (mm)")
 ```

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Consistency updates: 06-length-based-survival.Rmd

--- 2023-04-18 03-post-process/output-plots-children/06-length-based-survival.Rmd
@@
 
-## Parr $\to$ Smolt Overwinter Survival
+## Parr $\to$ Smolt Overwinter Survival {.tabset .tabset-pills}
 
-```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
-plot_fn = function(j, i) {
+```{r phi_Pa_Mb_lim}
+phi_Pa_Mb_lim = make_lim_param(post, "^phi_Pa_Mb[")
+```
+
+### Time Series {.tabset .tabset-pills}
+
+#### Fall Migrants {.tabset .tabset-pills}
+
+##### Realized Alone
+
+```{r phi_Pa_Mb_tseries-fall-1, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
+  )
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Overwinter Survival (Fall Migrants)")
+```
+
+##### Realized + Predicted
+
+```{r phi_Pa_Mb_tseries-fall-2, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
+  )
+
+  # predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
+              yrs = all_yrs[t])
+
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Overwinter Survival (Fall Migrants)")
+```
+
+#### Spring Migrants {.tabset .tabset-pills}
+
+##### Realized Alone
+
+```{r phi_Pa_Mb_tseries-spring-1, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
+  )
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Overwinter Survival (Spring Migrants)")
+```
+
+##### Realized + Predicted
+
+```{r phi_Pa_Mb_tseries-spring-2, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
+  )
+
+  # predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)),
+              yrs = all_yrs[ts_yrs])
+
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Overwinter Survival (Spring Migrants)")
+```
+
+### Mean Length Relationship {.tabset .tabset-pills}
+
+```{r}
+plot_f = function(j, i) {
 
@@
 
-  # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
   plot(1,1, type = "n", 
-       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
+       ylim = phi_Pa_Mb_lim,
        xlim = range(L_Pb_seq), 
-       main = ifelse(i == 1, pops[j], "")
+       main = pops[j]
   )
@@
   # expected relationship
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = tran_cols["model"])
+  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)
 
   # realized pairs
-  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
-  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = main_cols["model"])
+  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = main_cols["model"])
+  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
   text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  box(col = par("col.axis"))
+}
+```
+
+#### Fall Migrants
+
+```{r phi_Pa_Mb_fall_relationship, fig.width = p4_width, fig.height = p4_height}
+mypar()
+junk = sapply(1:jags_data$nj, plot_f, i = 1)
+axis_labels("Parr Mean Length (mm)", "Overwinter Survival (Fall Migrants)")
+```
+
+#### Spring Migrants
+
+```{r phi_Pa_Mb_spring_relationship, fig.width = p4_width, fig.height = p4_height}
+mypar()
+junk = sapply(1:jags_data$nj, plot_f, i = 2)
+axis_labels("Parr Mean Length (mm)", "Overwinter Survival (Spring Migrants)")
+```
+
+## Smolt $\to$ LGR Survival {.tabset .tabset-pills}
+
+```{r phi_Mb_Ma_lim}
+phi_Mb_Ma_lim = sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = ".", LH_type = i_spring, origin = o_nor) |>
+  make_lim_param(post, param = _)
+```
+
+### Time Series {.tabset .tabset-pills}
+
+#### Realized Alone
+
+```{r phi_Mb_Ma_tseries-1, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
+  )
 }
 
-plot_fn2 = function(j) {
-    # create the plots for both migratory strategies
-  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
-  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
-  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR)")
+```
+
+#### Realized + Predicted
+
+```{r phi_Mb_Ma_tseries-2, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
+               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
+  )
+
+  # predicted time series
+  add_tseries(post_summ(post, sub_index("^phi_Mb_Ma_dot[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)),
+              yrs = all_yrs[ts_yrs])
+
 }
 
-par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
-junk = sapply(1:jags_data$nj, plot_fn2)
-mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
-mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR)")
 ```
 
-## Smolt Survival to LGR
+### Mean Length Relationship
 
-```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
+```{r toLGR-survival-plots, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
@@
   # expected relationship
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
-  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)
+  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tran_cols["model"])
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = tran_cols["model"], lwd = 2)
 
   # realized pairs
-  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
-  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
+  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = main_cols["model"])
+  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = main_cols["model"])
+  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
   text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+  box(col = par("col.axis"))
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Smolt Mean Length (mm)")
-mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
+axis_labels("Smolt Mean Length (mm)", "Smolt \u2192 LGR Survival (NOR)")
 ```

### 2023-05-04 03-post-process/output-plots-children/12-param-summaries.Rmd
Consistency updates: 06-length-based-survival.Rmd

@@
 ```{r my-boxplot-function}
-my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), las = 3, ...) {
+my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = tran_cols["model"], border = main_cols["model"], las = 3, label_text = NULL, ...) {
   # extract posterior samples and rename them
@@
   # replace the summary stats with my preferred quantiles
-  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
   bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
+  if (is.null(ylim)) ylim = make_lim(bp$stats)
   bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, las = las, ...,
       staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
+
+  axis_labels(ylab = ylab, outer = FALSE, yline = 1)
+  panel_label(label_text, "topleft")
 }
+
+ref_line = function(h) {
+  abline(h = h, col = par("col.axis"), lty = 2)
+}
+
+bp_mar = c(3,2,1,1)
+bp_oma = c(0.2,0.2,0,0)
 ```
 
-## Egg-to-Parr Survival {.tabset .tabset-pills}
+## Egg $\to$ Parr Survival {.tabset .tabset-pills}
 
-### Beverton-Holt Parameters
+### Coefficients (BH Parameters)
 
-```{r egg-to-parr-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
+```{r egg-to-parr-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
 my_boxplot("^alpha[.]", "Productivity")
@@
 
-```{r egg-to-parr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
+```{r egg-to-parr-bxp2, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
 my_boxplot("^sig_Lphi_E_Pb[.]", "Process SD", ylim = c(0,2))
-my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); abline(h = 0, lty = 2)
-my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklabs = vcov_labels); abline(h = 0, lty = 2)
+my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); ref_line(h = 0)
+my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Correlation", ylim = c(-1,1), ticklabs = vcov_labels); ref_line(h = 0)
 ```
 
-## Summer Parr Size
+## Parr Mean Length {.tabset .tabset-pills}
 
-```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
+### Coefficients
+
+```{r summer-size-bxp1, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
 my_boxplot("^omega0[.]$", "Intercept")
-my_boxplot("^omega1[.]$", "Slope"); abline(h = 0, lty = 2)
-my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
-my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
+my_boxplot("^omega1[.]$", "Slope"); ref_line(h = 0)
 ```
 
-## Life History Apportionment
+### Process SD & Correlation
 
-```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Mean Proportion Fall Migrants", ylim = c(0,1))
+```{r summer-size-bxp2, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
+my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
+```
+
+## Migratory Strategy Apportionment
+
+```{r LH-type-bxp, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Average Pr(Fall)", ylim = ylim_01)
 my_boxplot("sig_Lpi[", "Process SD", ylim = c(0,2))
-my_boxplot(paste0("^rho_Lpi", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
+my_boxplot(paste0("^rho_Lpi", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
 ```
@@
 
-### Logistic Function Parameters
+### Coefficients
 
-```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
-my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope (Fall)"); abline(h = 0, lty = 2)
-my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope (Spring)"); abline(h = 0, lty = 2)
+```{r overwinter-survival-bxp1, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept", label_text = "Fall Migrants")
+my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept", label_text = "Spring Migrants")
+my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope", label_text = "Fall & Spring Migrants"); ref_line(h = 0)
 ```
@@
 
-```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
+```{r overwinter-survival-bxp2, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
 my_boxplot("sig_Lphi_Pa_Mb[", "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels); abline(h = 0, lty = 2)
+my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels); ref_line(h = 0)
 ```
 
-## "Growth" Factor
+## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}
 
-```{r growth-factor-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,4))
+### Coefficients
+
+```{r growth-factor-bxp1, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
 my_boxplot("^theta0[.]$", "Intercept")
-my_boxplot("^theta1[.]$", "Slope"); abline(h = 0, lty = 2)
-my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
-my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
-```
-
-## Movement Survival to LGR {.tabset .tabset-pills}
-
-### Mean/Logistic Model Parameters
-
-```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("tau0", "Intercept", main = "NOR")
-my_boxplot("tau1", "Slope", main = "NOR"); abline(h = 0, lty = 2)
-my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
+my_boxplot("^theta1[.]$", "Slope"); ref_line(h = 0)
 ```
@@
 
-```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
+```{r growth-factor-bxp2, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
+my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
 ```
 
-## Movement Survival to Ocean
+## Smolt $\to$ LGR Survival {.tabset .tabset-pills}
 
-```{r lgr-to-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("mu_phi_Ma_O0", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
-my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
-my_boxplot("rho_Lphi_Ma_O0[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
-```
+### Coefficients
 
-## Probability of Maturing at Age-3 {.tabset .tabset-pills}
-
-### Means
-
-```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```{r trib-to-lgr-bxp1, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot("tau0", "Intercept", label_text = "NOR")
+my_boxplot("tau1", "Slope", label_text = "NOR"); ref_line(h = 0)
+my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = c(1,2,4)), "Average Survival", label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01)
 ```
@@
 
-```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
+```{r trib-to-lgr-bxp2, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
+my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
 ```
 
-## Probability of Maturing at Age-4 {.tabset .tabset-pills}
+## LGR $\to$ BON Survival
+
+```{r lgr-to-ocean-bxp, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot("mu_phi_Ma_O0", "Average Survival", ylim = ylim_01, ticklab = origins)
+my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
+my_boxplot("rho_Lphi_Ma_O0[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
+```
+
+## Pr(Mature Age-3) {.tabset .tabset-pills}
 
@@
 
-```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
-my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
+```{r age3-mean-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-3)", label_text = "NOR", ylim = ylim_01)
+my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-3)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
 ```
@@
 
-```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
+```{r age3-sd-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
+my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
+```
+
+## Pr(Mature Age-4) {.tabset .tabset-pills}
+
+### Means
+
+```{r age4-mean-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-4)", label_text = "NOR", ylim = ylim_01)
+my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-4)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
+```
+
+### Process SD & Correlation
+
+```{r age4-sd-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
 my_boxplot("sig_Lpsi_O2[", ylab = "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
+my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
 ```
@@
 
-```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
+```{r yr1-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
 ```
@@
 
-```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
+```{r yr1-ocean-bxp2, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
 my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); abline(h = 0, lty = 2)
-my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1)); abline(h = 0, lty = 2)
+my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); ref_line(h = 0)
+my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
 ```
@@
 
-```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
+```{r yr2-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
 ```
@@
 
-```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,2))
-my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
-my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
+```{r yr3-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
+my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
 ```
@@
 
-```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5}
-
-# par(mfrow = c(1,3))
-tmp_ylim = c(-1.5,1.5)
-my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 1", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
-# my_boxplot(sub_index("delta_O1_O2[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 2", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
-# my_boxplot(sub_index("delta_O2_O3[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 3", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
+```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5, out.width = "50%"}
+mypar(mfrow = c(1,1), mar = bp_mar, oma = bp_oma)
+my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", ticklabs = pops[c(1,2,4)], ylim = c(-1.5,1.5)); ref_line(h = 0)
 ```
 
-## Movement Survival BON to LGR
+## BON $\to$ LGR Survival
 
-```{r bon-to-lgr-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("mu_phi_Rb_Ra", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
+```{r bon-to-lgr-bxp, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot("mu_phi_Rb_Ra", "Average Survival", ylim = ylim_01, ticklab = origins)
 my_boxplot("sig_Lphi_Rb_Ra[", "Process SD", ticklab = origins, ylim = c(0,2))
-my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
+my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
 ```
@@
 
-```{r prespawn-surv-bxp, fig.width = 8, fig.height = 3.5}
-par(mfrow = c(1,3))
-my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = c(0,1))
+```{r prespawn-surv-bxp, fig.width = p3_width, fig.height = p3_height}
+mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
+my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
 my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels); abline(h = 0, lty = 2)
+my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Correlation", ylim = c(-1,1), ticklab = vcov_labels); ref_line(h = 0)
 ```

### 2023-05-04 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Consistency updates: 06-length-based-survival.Rmd

@@
 post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
-                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {
+                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, label_text = NULL, n_bins = 50, alpha = 0.5) {
 
@@
   # graphics parameters
-  par(xaxs = "i", yaxs = "i", mgp = c(2,0.2,0), cex.axis = 0.8, tcl = -0.15, mar = c(1.5,1,1.5,0.5), lend = "square", ljoin = "mitre")
+  par(xaxs = "i", yaxs = "i")
 
@@
 
+  panel_label(label_text)
+
   # draw the x-axis
@@
   usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
+  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE, col = par("col.axis"))
+  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
 
@@
       prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
-      main = titles[j], 
+      label_text = titles[j], 
       legend_loc = ifelse(j == looping[1], legend_loc, NA),
@@
   # apply to each population/pair
-  par(mfrow = mfrow, oma = c(1,1.75,0,0))
+  mypar(mfrow = mfrow)
   junk = sapply(1:n, function(j) plot_f(looping[j]))
-  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
-  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+  axis_labels("Parameter Value", "Probability")
 }
@@
       prior_samps = post_subset(post, sub_index(prior_param, origin = o, ...), matrix = TRUE),
-      main = c("NOR", "HOR")[o], 
+      label_text = c("NOR", "HOR")[o], 
       legend_loc = ifelse(o == 1, legend_loc, NA),
@@
   # apply to each origin
-  par(mfrow = c(1,2), oma = c(1,1.5,0,0))
+  mypar(mfrow = c(1,2))
   junk = sapply(1:jags_data$no, plot_f)
-  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
-  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+  axis_labels("Parameter Value", "Probability")
 }
@@
 ```{r rho_Lphi_Ma_O0-post-v-prior, fig.width = 3, fig.height = 3}
-par(oma = c(1,1.75,0,0))
+mypar(mfrow = c(1,1))
 post_v_prior(post_samps = post_subset(post, "rho_Lphi_Ma_O0[2,1]", matrix = TRUE),
@@
              xlim = xlim, y_max = y_max)
-mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
-mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
+axis_labels("Parameter Value", "Probability")
 ```

### 2023-05-04 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Consistency updates: 07-capacity-vs-habitat.Rmd

@@
 
-```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 5}
+```{r beta-v-habitat-relationship, fig.width = 5, fig.height = 4, out.width="50%"}
 # extract posterior summaries of the capacity parameters
@@
 # empty plot with correct labeling/dimensions
-par(mar = c(3,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
+mypar(mfrow = c(1,1))
 plot(1,1, type = "n", xlim = range(wul_seq),
-     ylim = c(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
-     xlab = "Weighted Usable Length (km)",
+     ylim = make_lim(0, max(beta_ests["90%",], beta_ests["90%",], pred_beta[i,])),
+     xlab = "",
      ylab = "Parr Capacity (000s)", yaxt = "n")
@@
 # draw the random regression lines
-junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = alpha("grey25", 0.15)))
+junk = sapply(i, function(k) lines(pred_beta[k,] ~ wul_seq, col = tran_cols["model"]))
 
 # draw the posterior mean regression line
-lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, lty = 2)
+lines(apply(pred_beta, 2, mean) ~ wul_seq, lwd = 3, col = main_cols["model"])
 
 # draw the population-specific capacity estimates w/error bars and labels
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 16)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",])
-text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2)
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = "white", bg = "white")
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = main_cols["model"], bg = tran_cols["model"])
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = main_cols["model"])
+text(x = jags_data$wul, y = beta_ests["mean",], labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,4,4), font = 2, col = par("col.axis"))
+axis_labels("Weighted Usable Length (km)", "Parr Capacity (000s)")
+box(col = par("col.axis"))
 ```

### 2023-05-04 03-post-process/output-plots-children/09-equiv-rates.Rmd
Update file names on output-plots children
Consistency updates: 09-equiv-rates.Rmd

--- 2022-04-28 03-post-process/output-plots-children/08-equiv-rates.Rmd
@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 # Equivilency Rates {.tabset .tabset-pills}
@@
 
-```{r adults-per-smolt, fig.width = 6, fig.height = 5}
+```{r adults-per-smolt, fig.width = p4_width, fig.height = p4_height}
+j = 1
+
 plot_fn = function(j) {
@@
   # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))
+  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 10))
 
   # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
+  add_tseries(est = Ra_per_Ma_hor, yrs = all_yrs[sar_yrs])
 
-  if (j == 1) {
+  if (j == 2) {
     legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
+           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
   }
 }
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
+axis_labels("Brood Year", "Adults per 100 Smolt")
 ```
@@
 
-```{r bon-to-bon, fig.width = 6, fig.height = 5}
+```{r bon-to-bon, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
@@
   # plot natural origin time series
-  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))
+  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, ymax))
 
   # add hatchery origin time series
-  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
-  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
-  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)
+  add_tseries(est = phi_hor, yrs = all_yrs[sar_yrs])
 
-  if (j == 1) {
+  if (j == 2) {
     legend("topright", legend = origins, title = "Origin",
-         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
+           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
   }
 }
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
+axis_labels("Brood Year", "BON \u2192 BON Survival")
 ```
@@
 
-```{r parr-per-spawner, fig.width = 6, fig.height = 5}
+```{r parr-per-spawner, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], label_text = pops[j])
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
+axis_labels("Brood Year", "Parr per Spawner")
 ```
@@
 
-```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
+```{r smolt-per-spawner, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], label_text = pops[j])
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
+axis_labels("Brood Year", "Smolt per Spawner")
 ```
@@
 
-```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
+```{r spawners-per-spawner, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], label_text = pops[j])
   abline(h = 1, lty = 2)
 }
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
+axis_labels("Brood Year", "Spawners per Spawner")
 ```

### 2023-05-04 03-post-process/output-plots-children/10-rho-params.Rmd
Consistency updates: 10-rho-params.Rmd

@@
   x = rowMeans(post_subset(post, paste0("^", p, "["), matrix = TRUE))
-  c(mean = mean(x), sd = sd(x), quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))
+  c(mean = mean(x), sd = sd(x), quantile(x, c(0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975)))
 }
@@
 
-* Blue: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 80% CRI)
-* Red: Correlation of individual population pairs ("+" = posterior mean, lines = 50% CRI)
-* Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness)
+* Main: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 95% CRI)
+* Dots: Posterior mean correlation of individual population pairs
+<!-- * Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness) -->
 
-```{r rho-mean-plot, fig.width = 5, fig.height = 5}
+```{r rho-mean-plot, fig.width = 5, fig.height = 5, out.width = "50%"}
 # plot to show summary of correlation parameters across processes
@@
 # set up empty plotting region
-par(mar = c(2,8,1,1), cex.axis = 0.8, lend = "square", tcl = -0.15, mgp = c(2,0.35,0), yaxs = "i", lend = "square", ljoin ="mitre")
+mypar(mar = c(2,8,1,1), yaxs = "i", mfrow = c(1,1), oma = c(0,0,0,0), mgp = c(2,0.25,0))
 mp = barplot(rho_mean_out[,"mean"], 
@@
     y = at_mp + runif(6, -0.4, 0.4)
-    points(y ~ x["mean",], col = "royalblue", pch = 3, lwd = 1.5)
-    # segments(x["25%",], y, x["75%",], y, col = scales::alpha("royalblue", 0.5))
+    points(y ~ x["mean",], pch = 21, col = main_cols["model"], bg = tran_cols["model"])
   } 
@@
 
-junk = sapply(1:nrow(mp), function(i) draw_rho_prior(rownames(rho_mean_out)[i], box_lwr[i,], box_upr[i,]))
+# junk = sapply(1:nrow(mp), function(i) draw_rho_prior(rownames(rho_mean_out)[i], box_lwr[i,], box_upr[i,]))
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = main_cols["model"])
+segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = main_cols["model"])
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = main_cols["model"], lwd = 3)
 junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
-segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = scales::alpha("royalblue", 0.55))
-segments(rho_mean_out[,"10%"], mp, rho_mean_out[,"90%"], mp, col = scales::alpha("royalblue", 0.55))
-points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "royalblue", lwd = 3)
 
-abline(h = mp + rbind(diff(mp)/2, NA), xpd = FALSE, col = "grey50", lty = 2)
+abline(h = mp + rbind(diff(mp)/2, NA), xpd = FALSE, col = par("col.axis"), lty = 2)
+abline(v = 0, lty = 2, col = par("col.axis"))
 par(tcl = -7)
-axis(side = 2, at = mp + rbind(diff(mp)/2, NA), col = "grey50", line = NA, labels = FALSE, lty = 2)
-box()
-
+axis(side = 2, at = mp + rbind(diff(mp)/2, NA), col = par("col.axis"), line = NA, labels = FALSE, lty = 2)
+box(col = par("col.axis"))
 ```
@@
 rho_mat_plot = function(param, q = "mean", main) {
-  rho_ests = post_summ(post, param, probs = c(0.1, 0.9))
+  rho_ests = post_summ(post, param, probs = c(0.025, 0.975))
   rho_mat = array_format(rho_ests[q,])
@@
   dist = ifelse(is_prior, "Prior", "Posterior")
-  rho_mat_plot(param = param, q = "10%", main = paste0(dist, " 10%"))
+  rho_mat_plot(param = param, q = "2.5%", main = paste0(dist, " 2.5%"))
   rho_mat_plot(param = param, q = "mean", main = paste0(dist, " Mean"))
-  rho_mat_plot(param = param, q = "90%", main = paste0(dist, " 90%"))
+  rho_mat_plot(param = param, q = "97.5%", main = paste0(dist, " 97.5%"))
 }

### 2023-05-04 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Consistency updates: 11-noise-term-diags.Rmd

@@
 
-oma_labels = function(xlab = "", ylab = "", xline = 0.75, yline = 0.75, ...) {
-  mtext(side = 1, outer = TRUE, line = xline, text = xlab, ...)
-  mtext(side = 2, outer = TRUE, line = yline, text = ylab, ...)
-}
-
 no_data_plot = function(main = NULL) {
@@
   text(0,0, "No Data", font = 3)
-}
-
-my_par = function() {
-  par(mfrow = c(2,2), mar = c(1,1,2,2), oma = c(2,2,0,0), tcl = -0.15, mgp = c(2,0.35,0))
 }
@@
   # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
+  plot(qresid["mean",] ~ all_yrs[y_ind], type = "n",
        ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
@@
   # draw posterior mean for first and half of time series
-  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[y_ind[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = main_cols["model2"], lty = 3, lwd = 2)
+  lines(x = all_yrs[y_ind[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = main_cols["model2"], lty = 3, lwd = 2)
 
   # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
-  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)
+  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = main_cols["model"])
+  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = main_cols["model"], lwd = 4)
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "white", bg = "white", cex = 1.25)
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = main_cols["model"], bg = tran_cols["model"], cex = 1.25)
 
@@
   usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
-  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
-  box()
+  rect(usr[1], 1, usr[2], usr[4], border = par("col.axis"), col = "grey95")
+  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, text.col = par("col.axis"), legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
+  box(col = par("col.axis"))
+  panel_label(main, "topright")
 
@@
 
-#### Egg-to-Parr Survival
-
-```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
-my_par()
+#### Egg $\to$ Parr Survival
+
+```{r egg-to-parr-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr Mean Length
-
-```{r summer-length-noise, fig.width = 6, fig.height = 5}
-my_par()
+axis_labels("Brood Year", "logit(Egg \u2192 Parr Survival) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Parr Mean Length
+
+```{r summer-length-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
+axis_labels("Brood Year", "log(Summer Parr Mean Length) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r pi-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r pi-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
-oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
+axis_labels("Brood Year", "logit(Proportion Fall Migrants) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
-my_par()
+```{r overwinter-surv-noise-fall, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
+axis_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
-my_par()
+```{r overwinter-surv-noise-spring, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Summer Parr to Spring Smolt "Growth Factor"
-
-```{r growth-noise, fig.width = 6, fig.height = 5}
-my_par()
+axis_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Parr $\to$ Smolt "Growth Factor"
+
+```{r growth-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib to LGR {.tabset .tabset-pills}
+axis_labels("Brood Year", "log(Parr \u2192 Smolt 'Growth' Factor) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Trib $\to$ LGR {.tabset .tabset-pills}
 
@@
 
-```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
-my_par()
+```{r trib-to-LGR-surv-nor, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
+axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [NOR]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
-my_par()
+```{r trib-to-LGR-surv-hor, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
-oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR to BON Survival
-
-```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
+axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [HOR]) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### LGR $\to$ BON Survival
+
+```{r LGR-to-BON-surv-noise, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2))
 tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
+axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r yr1-ocean-surv-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
+axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r pr-mat-3-nor-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
+axis_labels("Brood Year", "logit(Mature at Age-3 [NOR]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r pr-mat-3-hor-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
+axis_labels("Brood Year", "logit(Mature at Age-3 [HOR]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r pr-mat-4-nor-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
+axis_labels("Brood Year", "logit(Mature at Age-4 [NOR]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r pr-mat-4-hor-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
+axis_labels("Brood Year", "logit(Mature at Age-4 [HOR]) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-#### BON to LGR Survival
-
-```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
+#### BON $\to$ LGR Survival
+
+```{r BON-to-LGR-surv-noise, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2))
 tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
+axis_labels("Return Year", "logit(BON \u2192 LGR Survival) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
-my_par()
+```{r prespawn-surv-noise, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
+axis_labels("Return Year", "logit(Pre-spawn Survival) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
   # blank plot with correct dimensions
-  par(lend = "square")
-  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
+  plot(qresid["mean",] ~ all_yrs[observable], type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")
 
@@
   # draw the noise time series: mean and 95% CRI
-  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
-  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
-  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)
+  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = main_cols["model"])
+  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = main_cols["model"], lwd = 4)
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "white", bg = "white", cex = 1.25)
+  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = main_cols["model"], bg = tran_cols["model"], cex = 1.25)
 
@@
   # draw posterior mean for first and half of time series
-  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = "blue", lty = 3, lwd = 2)
-  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = "blue", lty = 3, lwd = 2)
+  lines(x = all_yrs[observable[y_first]], y = rep(mean(mn_post_first), length(y_first)), col = main_cols["model2"], lty = 3, lwd = 2)
+  lines(x = all_yrs[observable[y_last]], y = rep(mean(mn_post_last), length(y_last)), col = main_cols["model2"], lty = 3, lwd = 2)
 
@@
 
-```{r fall-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
+```{r fall-trap-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
+axis_labels("Brood Year", "log(Fall Parr Abundance) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-```{r spring-trap-resid, fig.width = 6, fig.height = 5}
-my_par()
+```{r spring-trap-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Spring Trap Count) Residual")
+axis_labels("Brood Year", "log(Spring Trap Count) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-```{r adult-resid, fig.width = 6, fig.height = 5}
-my_par()
+```{r adult-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "log(Total Adult Count) Residual")
+axis_labels("Return Year", "log(Total Adult Count) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-#### Summer Parr $\rightarrow$ LGR
-
-```{r summer-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
+#### Summer Parr $\to$ LGR
+
+```{r summer-surv-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Fall Parr $\rightarrow$ LGR
-
-```{r fall-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
+axis_labels("Brood Year", "logit(Summer Parr \u2192 LGR Survival) QResidual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Fall Parr $\to$ LGR
+
+```{r fall-surv-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Winter Parr $\rightarrow$ LGR
-
-```{r winter-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
+axis_labels("Brood Year", "logit(Fall Parr \u2192 LGR Survival) QResidual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Winter Parr $\to$ LGR
+
+```{r winter-surv-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) {
@@
 })
-oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
+axis_labels("Brood Year", "logit(Winter Parr \u2192 LGR Survival) QResidual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Spring Smolt $\to$ LGR {.tabset .tabset-pills}
 
@@
 
-```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
-my_par()
+```{r spring-surv-resid-nor, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
+axis_labels("Brood Year", "logit(NOR Smolt \u2192 LGR Survival) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
-my_par()
+```{r spring-surv-resid-hor, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) {
@@
 })
-oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### LGR Smolt $\rightarrow$ Ocean
-
-```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
+axis_labels("Brood Year", "logit(HOR Smolt \u2192 LGR Survival) QResidual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### LGR Smolt $\to$ BON
+
+```{r hydro-surv-resid, fig.width = p2_width, fig.height = p2_height}
+mypar(mfrow = c(1,2))
 tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
+axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 ```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
-my_par(); par(mfrow = c(1,2))
+mypar(mfrow = c(1,2))
 tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
-oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
+axis_labels("Return Year", "Count of PIT Tagged Adults at LGR QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
-my_par()
+```{r pre-spawn-surv-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
+axis_labels("Return Year", "Count of Female Spawned-out Carcasses QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-#### Summer Length
-
-```{r summer-length-resid, fig.width = 6, fig.height = 5}
-my_par()
+#### Parr Mean Length
+
+```{r summer-length-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Summer Length) Residual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
-#### Spring Length
-
-```{r spring-length-resid, fig.width = 6, fig.height = 5}
-my_par()
+axis_labels("Brood Year", "log(Parr Mean Length) QResidual")
+obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
+```
+
+#### Smolt Mean Length
+
+```{r spring-length-resid, fig.width = p4_width, fig.height = p4_height}
+mypar()
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-oma_labels("Brood Year", "log(Mean Spring Length) Residual")
+axis_labels("Brood Year", "log(Smolt Mean Length) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 weir_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
+  mypar(mfrow = c(2,3))
   tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
+  axis_labels("Return Year", "Weir Age/Origin Composition QResidual")
   do.call(rbind, tmp)
@@
 
-```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
+```{r cat-weir-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = weir_comp_qresid_plots(j_cat)
@@
 
-```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
+```{r los-weir-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = weir_comp_qresid_plots(j_los)
@@
 
-```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
+```{r ugr-weir-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = weir_comp_qresid_plots(j_ugr)
@@
 carcass_comp_qresid_plots = function(j) {
-  my_par(); par(mfrow = c(2,3))
+  mypar(mfrow = c(2,3))
   tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
-  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
+  axis_labels("Return Year", "Carcass Age/Origin Composition QResidual")
   do.call(rbind, tmp)
@@
 
-```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
+```{r cat-carcass-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = carcass_comp_qresid_plots(j_cat)
@@
 
-```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
+```{r los-carcas-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = carcass_comp_qresid_plots(j_los)
@@
 
-```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
+```{r min-carcas-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = carcass_comp_qresid_plots(j_min)
@@
 
-```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
+```{r ugr-carcass-comp-resids, fig.width = p6_width, fig.height = p6_height}
 tmp = carcass_comp_qresid_plots(j_ugr)

### 2023-05-04 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Consistency updates: 13-post-vs-prior.Rmd

@@
 # set global knitting options
-knitr::opts_chunk$set(fig.width = 6, fig.height = 5)
+knitr::opts_chunk$set(fig.width = p4_width, fig.height = p4_height)
 ```
@@
   # if some portion of one of the dists is not shown, include a message
-  if (p_post_keep < 1 | p_prior_keep < 1) {
-    nice_round = function(x, digits = 2) {
-      x_round = round(x, digits = digits)
-      if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
-      x_out
-    }
-
-    legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
-           legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
-           text.col = c(prior_col, post_col), bty = "n", title.col = "black",
-           title = "P Not Shown", cex = 0.8
-    )
-  }
+  # if (p_post_keep < 1 | p_prior_keep < 1) {
+  #   nice_round = function(x, digits = 2) {
+  #     x_round = round(x, digits = digits)
+  #     if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
+  #     x_out
+  #   }
+  #   
+  #   legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
+  #          legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
+  #          text.col = c(prior_col, post_col), bty = "n", title.col = "black",
+  #          title = "P Not Shown", cex = 0.8
+  #   )
+  # }
 }
@@
 post_v_prior_pops(post_param = "mu_phi_O1_O2[origin,pop]", prior_param = "mu_phi_O1_O2_pr",
-                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
+                  origin = o_nor, xlim = c(0,1), legend_loc = "topright"
 )
@@
 post_v_prior_pops(post_param = "mu_phi_O2_O3[origin,pop]", prior_param = "mu_phi_O2_O3_pr",
-                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
+                  origin = o_nor, xlim = c(0,1), legend_loc = "topright"
 )
@@
 xlim = c(-1,1)
-knitr::opts_chunk$set(fig.width = 5, fig.height = 6)
+knitr::opts_chunk$set(fig.width = p4_height, fig.height = p4_width, out.width = "50%")
 ```

### 2023-05-04 03-post-process/output-plots-children/03-fit-to-data.Rmd
Add colorized text describing meaning of line plots

@@
 
-In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).
+Figures in this section show the consistencies between the `r colorize("posterior", main_cols["model"])` (mean with 95% equal-tailed credible interval) and the `r colorize("data", main_cols["data"])` (point estimate with approximate 95% confidence interval illustrating the magnitude of assumed observation error).
 
@@
   axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$x_carcass_total[observable,j]), 3, 4)[at_x])
-  box()
+  box(col = par("col.axis"))
 

### 2023-05-04 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Add colorized text describing meaning of line plots

@@
 
-These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.
-
 ### Realized Alone
 
-Just the realized time series shown.
+The `r colorize("realized time series", main_cols["model"])`.
 
@@
 
-The blue shows the time series with variability explained only by Beverton-Holt dynamics.
+The `r colorize("realized time series", main_cols["model"])` and the `r colorize("time series with variability explained only by Beverton-Holt dynamics", main_cols["model2"])`.
 
@@
 
-The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.
+The `r colorize("realized time series", main_cols["model"])` and the `r colorize("time series with variability explained by Beverton-Holt dynamics and the carry-over residual", main_cols["model2"])`.
 
@@
 
-This is the scale the Beverton-Holt recruitment function is estimated on.
+This is the scale the Beverton-Holt recruitment function is modeled on.
 
@@
   text(phi_E_Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+
+  box(col = par("col.axis"))
 }
@@
   text(Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
+
+  box(col = par("col.axis"))
 }
@@
 
-This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model.
+This figure shows that total spawner abundance is a reasonable index of total egg production, according to the assumptions of our model (eggs = spawners-age-4/5 * 50% * age-specific fecundity).
 The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.
@@
   }
+
+  box(col = par("col.axis"))
 }

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Add colorized text describing meaning of line plots

@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r phi_Pa_Mb_tseries-fall-1, fig.width = p4_width, fig.height = p4_height}
@@
 
-##### Realized + Predicted
+##### Realized & Expected
+
+The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).
 
@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r phi_Pa_Mb_tseries-spring-1, fig.width = p4_width, fig.height = p4_height}
@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r phi_Mb_Ma_tseries-1, fig.width = p4_width, fig.height = p4_height}
@@
 
-#### Realized + Predicted
+#### Realized & Expected
+
+The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).
 
@@
   # make a blank plot with the correct dimensions
-  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
   plot(1,1, type = "n", 
-       # ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
        ylim = phi_Mb_Ma_lim,
-       xlim = range(L_Mb_seq), 
-       main = pops[j]
+       xlim = range(L_Mb_seq)
   )
+  panel_label(pops[j])
 

### 2023-05-04 01-functions/util-fns.R

@@ -337,3 +337,13 @@ my_cat = function(label, value, total_width = 60, indent = 2, first = FALSE) {
   cat(paste(c(rep(" ", indent), "|-", rep("-", total_width - 3 - indent), "|"), collapse = ""), "\n", sep = "")
   Sys.sleep(0.25)
 }
+
+##### COLOR TEXT FOR PRINTING IN RMD #####
+
+# ADAPTED FROM https://bookdown.org/yihui/rmarkdown-cookbook/font-color.html#using-an-r-function-to-write-raw-html-or-latex-code
+
+colorize = function(x, color) {
+  if (knitr::is_html_output()) {
+    sprintf("<span style='color: %s;'>%s</span>", color, x)
+  } else x
+}

### 2023-05-04 01-functions/plot-fns.R
Update default plot aesthetics

@@ -84,9 +84,9 @@ panel_label = function(label_text, label_loc = "topleft", cex = 1,
 }
 
 # draw axes labels
-axis_labels = function(xlab = NULL, ylab = NULL, xline = 0.4, yline = 0.4, outer = TRUE, ...) {
-  mtext(side = 1, line = xline, text = xlab, outer = outer, ...)
-  mtext(side = 2, line = yline, text = ylab, outer = outer, ...)
+axis_labels = function(xlab = NULL, ylab = NULL, xline = 0.4, yline = 0.4, outer = TRUE, col = par("col.axis"), ...) {
+  mtext(side = 1, line = xline, text = xlab, outer = outer, col = col, ...)
+  mtext(side = 2, line = yline, text = ylab, outer = outer, col = col, ...)
 } 
 
 # default par()
@@ -95,7 +95,7 @@ mypar = function(mar = c(1,1,0.5,0.5),
                  oma = c(1.5,1.5,0,0), mgp = c(200,0.05,0), 
                  tcl = 0, lend = "square",
                  ljoin = "mitre",
-                 col.axis = "grey40", cex.axis = 0.85, ...) {
+                 col.axis = "grey30", cex.axis = 0.85, ...) {
   
   do.call(par, c(as.list(environment()), list(...)))
 }
@@ -141,17 +141,19 @@ plot_tseries = function(est, obs = NULL, ylim = NULL, yrs = NULL, xaxis = TRUE, 
   # draw axes/labels
   if (xaxis) {
     at_yrs = axisTicks(par("usr")[1:2], log = FALSE)
-    axis(side = 1, at = at_yrs, labels = substr(at_yrs, 3, 4))
+    axis(side = 1, at = at_yrs, labels = paste0("'", substr(at_yrs, 3, 4)))
   } 
   if (!is.null(yaxis_side)) axis(side = yaxis_side)
   panel_label(label_text, label_loc)
+  
+  box(col = par("col.axis"))
 }
 
 add_tseries = function(est, yrs, main_col = main_cols["model2"], tran_col = tran_cols["model2"]) {
-  polygon(x = c(all_yrs[ts_yrs], rev(all_yrs[ts_yrs])),
+  polygon(x = c(yrs, rev(yrs)),
           y = c(est["2.5%",], rev(est["97.5%",])),
           col = tran_col, border = NA)
[…]

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Clean up misc typos

@@
   add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
-              yrs = all_yrs[t])
+              yrs = all_yrs[ts_yrs])
 
@@
        ylim = phi_Pa_Mb_lim,
-       xlim = range(L_Pb_seq), 
-       main = pops[j]
+       xlim = range(L_Pb_seq)
   )
+  panel_label(pops[j])
 

### 2023-05-04 03-post-process/output-plots-children/05-length.Rmd

@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r L_Pb_tseries-1, fig.width = p4_width, fig.height = p4_height}
@@
 
-#### Realized & Predicted
+#### Realized & Expected
+
+The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).
 
@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r Delta_L_Pb_Mb-1, fig.width = p4_width, fig.height = p4_height}
@@
 
+The `r colorize("realized time series", main_cols["model"])` and the `r colorize("ratio between observed smolt and parr mean length", main_cols["model2"])`.
+
 ```{r Delta_L_Pb_Mb-2, fig.width = p4_width, fig.height = p4_height}
@@
 
+The `r colorize("realized time series", main_cols["model"])`.
+
 ```{r L_Mb-tseries-1, fig.width = p4_width, fig.height = p4_height}

### 2023-05-04 03-post-process/output-plots-children/08-misc-process-model.Rmd

--- 2022-04-28 03-post-process/output-plots-children/07-misc-process-model.Rmd
@@
 
-```{r pi-plots, fig.width = 6, fig.height = 5}
+```{r pi-plots, fig.width = p4_width, fig.height = p4_height}
 plot_f = function(j) {
-  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
-               yrs = all_yrs[ts_yrs],
-               main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
+               label_text = pops[j], yrs = all_yrs[ts_yrs])
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_f)
-mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
+axis_labels("Brood Year", "Proportion of Parr with Fall Migration Strategy")
 ```
@@
 
-```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
-ocean_surv_plot = function(j) {
-  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
-               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
-  mtext(side = 2, outer = T, line = 0, "Survival")
+### Yr1 {.tabset .tabset-pills}
+
+#### NOR {.tabset .tabset-pills}
+
+##### Realized Alone
+
+The `r colorize("realized time series", main_cols["model"])`.
+
+```{r phi-O0-O1-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
 }
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
 ```
 
-### CAT
+##### Realized & [Expected + AR(1)]
 
-```{r}
-ocean_surv_plot(j_cat)
+The `r colorize("realized time series", main_cols["model"])` and the `r colorize("expected time series including the carry-over residual", main_cols["model2"])`.
+
+```{r phi-O0-O1-plots2, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+
+  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
 ```
 
-### LOS
+#### HOR {.tabset .tabset-pills}
 
-```{r}
-ocean_surv_plot(j_los)
+##### Realized Alone
+
+The `r colorize("realized time series", main_cols["model"])`.
+
+```{r phi-O0-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr1 Ocean Survival (HOR)")
 ```
 
-### MIN
+### Yr2 {.tabset .tabset-pills}
 
-```{r}
-ocean_surv_plot(j_min)
+#### NOR
+
+```{r phi-O1-O2-nor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr2 Ocean Survival (NOR)")
 ```
 
-### UGR
+#### HOR
 
-```{r}
-ocean_surv_plot(j_ugr)
+```{r phi-O1-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr2 Ocean Survival (HOR)")
+```
+
+### Yr3 {.tabset .tabset-pills}
+
+#### NOR
+
+```{r phi-O2-O3-nor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr3 Ocean Survival (NOR)")
+```
+
+#### HOR
+
+```{r phi-O2-O3-hor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Yr3 Ocean Survival (HOR)")
 ```
@@
 
-```{r maturity-plot-fn}
-maturity_plot = function(j) {
-  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
-  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
+### Pr(Age-3) {.tabset .tabset-pills}
 
-  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
-  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
+#### NOR
+
+```{r psi-O1-nor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
 }
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Pr(Mature Age-3|NOR)")
 ```
 
-### CAT
+#### HOR
 
-```{r maturity-cat, fig.width = 6, fig.height = 5}
-maturity_plot(j_cat)
+```{r psi-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Pr(Mature Age-3|HOR)")
 ```
 
-### LOS
+### Pr(Age-4) {.tabset .tabset-pills}
 
-```{r maturity-los, fig.width = 6, fig.height = 5}
-maturity_plot(j_los)
+#### NOR
+
+```{r psi-O2-nor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Pr(Mature Age-4|NOR)")
 ```
 
-### MIN
+#### HOR
 
-```{r maturity-min, fig.width = 6, fig.height = 5}
-maturity_plot(j_min)
-```
+```{r psi-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
+  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+}
 
-### UGR
-
-```{r maturity-ugr, fig.width = 6, fig.height = 5}
-maturity_plot(j_ugr)
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Pr(Mature Age-4|HOR)")
 ```
@@
 
-```{r n-stray, fig.width = 6, fig.height = 5}
+```{r n-stray, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
-  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
+  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], label_text = pops[j])
 }
 
-par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 1, outer = T, line = 0.25, "Return Year")
-mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
+axis_labels("Return Year", "Number of Strays Entering Population")
 ```
@@
 
-```{r stray-comp, fig.width = 6, fig.height = 5}
+```{r stray-comp, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
@@
 
-  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
-  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
+  mp = barplot(x["mean",], ylim = ylim_01, xaxt = "n", col = tran_cols["model"], border = main_cols["model"])
   segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
-  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
-  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
+  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 1)
+  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
+  segments(par("usr")[1], par("usr")[3], par("usr")[1], par("usr")[4], xpd = TRUE, col = par("col.axis"))
+  panel_label(pops[j])
 }
 
-par(mfrow = c(2,2), oma = c(0,1.5,0,0))
+mypar()
 junk = sapply(1:jags_data$nj, plot_fn)
-mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
+axis_labels("Age of Return", "Proportion of Strays by Age")
 ```

### 2023-05-04 03-post-process/output-plots.Rmd

@@
     label: "Scenario"
-    value: "base"
+    value: "test-rmd_vshort"
     input: text
@@
 
-```{r directories, include = F}
+```{r directories, include = FALSE}
 # set root directory to the project directory: one level up from this location

### 2023-05-10 01-functions/init-fns.R
Update initial values generator for fec & harv changes

@@ -2,7 +2,6 @@
 # SCRIPT TO HOUSE FUNCTIONS FOR GENERATING INITIAL MCMC VALUES #
 # :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::: #
 
-
 # reconstruct total parr
 get_Pb_obs = function(jags_data, fill_missing = FALSE, append_sim_yrs = FALSE) {
   
@@ -66,8 +65,13 @@ get_E_obs = function(jags_data, fill_missing = FALSE, append_sim_yrs = FALSE) {
     
     # get the broodstock removed
     broodstock = B
-    broodstock = lapply(1:nj, function(j) cbind(broodstock[1:ny_obs,,1,j], broodstock[1:ny_obs,,1,j]))
+    broodstock = lapply(1:nj, function(j) cbind(broodstock[1:ny_obs,,o_nor,j], broodstock[1:ny_obs,,o_hor,j]))
     broodstock = do.call(abind, append(broodstock, list(along = 3)))
+    
+    # get the harvest removed
+    harvest = H
+    harvest = lapply(1:nj, function(j) cbind(harvest[1:ny_obs,,o_nor,j], harvest[1:ny_obs,,o_hor,j]))
+    harvest = do.call(abind, append(harvest, list(along = 3)))
     
     # get the pre-spawn survival
     prespawn_surv = x_carcass_spawned/x_carcass_total
@@ -86,8 +90,8 @@ get_E_obs = function(jags_data, fill_missing = FALSE, append_sim_yrs = FALSE) {
     })
     age_origin_return = do.call(abind, append(age_origin_return, list(along = 3)))
     
-    # remove brood_stock
-    age_origin_above_weir = age_origin_return - broodstock
+    # remove brood_stock & harvest
+    age_origin_above_weir = age_origin_return - broodstock - harvest
     age_origin_above_weir[age_origin_above_weir < 0] = 5
     
     # remove prespawn morts
@@ -104,15 +108,18 @@ get_E_obs = function(jags_data, fill_missing = FALSE, append_sim_yrs = FALSE) {
     females_age_origin = do.call(abind, append(females_age_origin, list(along = 3)))
     
     # get total egg output
-    f_age_origin = c(f, f)
     eggs_age_origin = lapply(1:nj, function(j) {
-      t(apply(females_age_origin[,,j], 1, function(y) y * f_age_origin))
+      f_age_origin = cbind(f[,,j], f[,,j])
[…]

### 2023-05-10 03-post-process/output-plots-children/06-length-based-survival.Rmd
Tiny plotting bug fix

@@
   polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tran_cols["model"])
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = tran_cols["model"], lwd = 2)
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = main_cols["model"], lwd = 2)
 

### 2023-05-11 03-post-process/output-plots-children/10-rho-params.Rmd
Remove time-varying prespawn mort from all output plots

@@
   "rho_Lphi_Pa_Mb" = "Overwinter Survival",
-  "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
   "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
@@
 ```
-
-### Pre-Spawn Survival
-
-```{r rho_Lphi_Sb_Sa-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
-rho_mat_plots("rho_Lphi_Sb_Sa[")
-```

### 2023-05-11 03-post-process/output-plots-children/12-param-summaries.Rmd
Remove time-varying prespawn mort from all output plots

@@
 
-```{r prespawn-surv-bxp, fig.width = p3_width, fig.height = p3_height}
+```{r prespawn-surv-bxp, fig.width = p4_width, fig.height = p4_height, out.width = "50%"}
 mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
 my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
-my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
-my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Correlation", ylim = c(-1,1), ticklab = vcov_labels); ref_line(h = 0)
 ```

### 2023-05-11 03-post-process/compare-sim-to-obs.Rmd
Fix small file path bug introduced by recent changes
Very minor: I changed the output file to be called "output_scenario.rds" instead of "output-scenario.rds" in a commit as part of #185
Remove time-varying prespawn mort from sim-vs-obs

@@
   x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
-  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
+  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival"))
   x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
@@
 
-#### Pre-Spawn Survival
-
-```{r}
-x = lapply(1:4, function(j) get_ratio("^phi_Sb_Sa[year,pop]", obs_y, sim_y, pop = j))
-x = do.call(abind, append(x, list(along = 4)))
-vals_plots(x, "Pre-Spawn Survival: Estimates")
-ratio_plots(x, "Pre-Spawn Survival: Ratios")
-est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "Pre-Spawn Survival"))
-```
-
 ## Emergent Properties {.tabset .tabset-pills}
@@
 
-#### Pre-Spawn Survival
-
-```{r}
-pop_ts_plots("^phi_Sb_Sa[year,pop]")
-```
-
 ## Emergent Properties {.tabset .tabset-pills}

### 2023-05-12 03-post-process/output-plots-children/02-mcmc-diags.Rmd

@@
 L1 = "Pre-spawn Survival"
-L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
-match = c("mu_phi_Sb_Sa", "sig_Lphi_Sb_Sa", "rho_Lphi_Sb_Sa", "^phi_Sb_Sa")
+L2 = c("Mean")
+match = c("mu_phi_Sb_Sa")
 tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))

### 2023-05-12 03-post-process/output-plots-children/11-noise-term-diags.Rmd

@@
 
-# the years to calculate residuals for
-observable = 2:jags_data$ny_obs
-# "^phi_E_Pb[year,pop]""phi_E_Pb_dot2[year,pop]", "sig_Lphi_E_Pb[pop]"
-
 # egg to parr survival
@@
                                     type = "origin")
-)
-
-# Pre-spawn survival
-qresid_post = cbind(qresid_post,
-                    make_qresid_all("^phi_Sb_Sa[year,pop]",
-                                    "^mu_phi_Sb_Sa[pop]",
-                                    "sig_Lphi_Sb_Sa[pop]",
-                                    type = "pop", origin = jags_data$o_hor)
 )
@@
 
-#### Pre-spawn Survival
-
-```{r prespawn-surv-noise, fig.width = p4_width, fig.height = p4_height}
-mypar()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Return Year", "logit(Pre-spawn Survival) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
 ### **SUMMARY TABLES** {.tabset .tabset-pills}
@@
 proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
-proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")
 
 # correct origin indices
-proc_error_ests$origin[proc_error_ests$param == "Pre-spawn Survival"] = 3
 proc_error_ests$origin[is.na(proc_error_ests$origin)] = 1
@@
 sw_juv = c("Yr1 Ocean Survival", "Pr(Mature Age-3)", "Pr(Mature Age-4)")
-fw_adult = c("BON to LGR Survival", "Pre-spawn Survival")
+fw_adult = c("BON to LGR Survival")
 

### 2023-05-12 03-post-process/output-plots-children/13-post-vs-prior.Rmd

@@
 
-### Pre-spawn Survival
-
-**Process Noise Distribution**: Multivariate logit-normal
-
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Sb_Sa_prior[2]`)`
-
-```{r sig_Lphi_Sb_Sa-post-v-prior}
-post_v_prior_pops(post_param = "sig_Lphi_Sb_Sa[pop]", prior_param = "sig_Lphi_Sb_Sa_pr[pop]",
-                  xlim = c(0, 2)
-)
-```
-
 ## Correlation Parameters {.tabset .tabset-dropdown}
@@
 ```
-
-### Pre-spawn Survival
-
-**Process Noise Distribution**: Multivariate logit-normal
-
-**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Sb_Sa_prior[2]`)`
-
-```{r rho_Lphi_Sb_Sa-post-v-prior}
-post_v_prior_pops(post_param = "rho_Lphi_Sb_Sa", prior_param = "rho_Lphi_Sb_Sa_pr",
-                  xlim = xlim, y_max = y_max, is_rho = TRUE
-)
-```

### 2023-05-26 00-data/prep-bio-data.R
Update data file names
No longer have numbered prefixes

@@ -24,7 +24,7 @@ data_dir = "../GR-sslcm-data/bio"
 ##### ADULT ABUNDANCE DATA #####
 
 # read the data
-tmp = read.csv(file.path(data_dir, "01-adult-abundance.csv"), stringsAsFactors = F)
+tmp = read.csv(file.path(data_dir, "adult-abundance.csv"), stringsAsFactors = F)
 
 # keep only relevant columns
 tmp = tmp[,c("population", "return_year", "n_returned", "n_above_weir", "abund_cv")]
@@ -44,7 +44,7 @@ adult_abundance = tmp; rm(tmp)
 ##### ADULT COMPOSITION: CARCASS DATA #####
 
 # read the data
-tmp = read.csv(file.path(data_dir, "02a-adult-indiv-carcass.csv"), stringsAsFactors = F)
+tmp = read.csv(file.path(data_dir, "adult-indiv-carcass.csv"), stringsAsFactors = F)
 
 # new age_best variable
 # some of the age_best are NA, but there are age records in the other columns
@@ -93,7 +93,7 @@ adult_carc_composition = tmp; rm(tmp)
 ##### ADULT COMPOSITION: WEIR DATA #####
 
 # read the data
-tmp = read.csv(file.path(data_dir, "02b-adult-indiv-weir.csv"), stringsAsFactors = F)
+tmp = read.csv(file.path(data_dir, "adult-indiv-weir.csv"), stringsAsFactors = F)
 
 # new age_best variable
 # some of the age_best are NA, but there are age records in the other columns
@@ -166,7 +166,7 @@ adult_weir_composition = tmp; rm(tmp)
 ##### ADULT COMPOSITION: WEIR REMOVAL DATA #####
 
 # read the data
-tmp = read.csv(file.path(data_dir, "02b-adult-indiv-weir.csv"), stringsAsFactors = F)
+tmp = read.csv(file.path(data_dir, "adult-indiv-weir.csv"), stringsAsFactors = F)
 
 # new age_best variable
 # some of the age_best are NA, but there are age records in the other columns
@@ -238,7 +238,7 @@ adult_rm_composition = tmp; rm(tmp)
 status_count_threshold = 10
 
 # read the data
-tmp = read.csv(file.path(data_dir, "02a-adult-indiv-carcass.csv"), stringsAsFactors = F)
[…]

### 2023-05-26 00-data/prep-bio-data.R
Remove references to sea lion survival
No longer part of model. Was discovered to be causing problems for ocean survival estimates (the stair-step mixed with a time-constant ocean survival was not working well)

@@ -277,23 +277,6 @@ tmp$carcs_samp_for_status[tmp$carcs_samp_for_status <= status_count_threshold] =
 # rename the data frame, and remove "tmp" objects
 adult_prespawn = tmp; rm(tmp)
 
-##### ADULT SURVIVAL PAST SEA LIONS #####
-
-# read the data
-tmp = read.csv(file.path(data_dir, "07-sea-lion-survival.csv"))
-
-# reformat to long format
-tmp = melt(tmp, id.vars = "year", value.name = "surv_est_sea_lions", variable.name = "population")
-
-# update column names
-# note: return_year renamed to "brood_year" to allow merging with other data sets
-# and for consistent indexing in model.
-# just note that for adults, brood_year is the year is the year adults SPAWNED, NOT the year they WERE SPAWNED
-colnames(tmp)[1] = "brood_year"
-
-# rename object and remove "tmp" object
-sea_lion_survival = tmp; rm(tmp)
-
 ##### ADULT HARVEST RATES BELOW BON #####
 
 # read the data

### 2023-05-26 01-functions/data-fns.R

@@ -273,10 +273,6 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
   U[y_names %in% all$brood_year,"3","HOR"] = all$HR_HOR * 0.25
   U[y_names %in% all$brood_year,c("4", "5"),"HOR"] = all$HR_HOR
   
-  ### ADULT SURVIVAL PAST SEA LIONS ###
-  phi_SL = rep(NA, ny); names(phi_SL) = y_names
-  phi_SL[y_names %in% sub$brood_year] = sub$surv_est_sea_lions
-  
   ### COUNTS OF ADULT PIT TAG DETECTIONS AT BON ###
   x_BON = matrix(NA, ny, no); dimnames(x_BON) = list(y_names, o_names)
   x_BON[y_names %in% all$brood_year,o_names[1]] = all$NOR_BON_adults
@@ -374,8 +370,6 @@ create_jags_data_one = function(pop, first_y = 1991, last_y = 2019) {
     sig_Lphi_obs_Ma_O0 = sig_Lphi_obs_Ma_O0,
     
     ### ADULT SURVIVAL ###
-    # adult survival past sea lions (not fitted; assumed known w/o error)
-    phi_SL = phi_SL,
     
     # adult harvest rate below BON
     U = U,
@@ -487,9 +481,6 @@ create_jags_data_mult = function(pops, first_y = 1991, last_y = 2019) {
     # hydropower survival
     Lphi_obs_Ma_O0 = main_list[[1]]$Lphi_obs_Ma_O0,
     sig_Lphi_obs_Ma_O0 = main_list[[1]]$sig_Lphi_obs_Ma_O0,
-    
-    # adult survival past sea lions (not fitted; assumed known w/o error)
-    phi_SL = abind(lapply(main_list, function(x) x$phi_SL), along = 2),
     
     # adult PIT tag counts at BON
     x_BON = main_list[[1]]$x_BON,
@@ -669,21 +660,6 @@ append_values_for_sim = function(jags_data) {
   fill[,"MIN"] = NA
   jags_data$not_stray_yrs = rbind(jags_data$not_stray_yrs, fill)
   jags_data$n_not_stray_yrs = apply(jags_data$not_stray_yrs, 2, function(x) sum(!is.na(x)))
-  
-  ### KNOWN VALUES SOURCE X: SURVIVAL PAST SEA LIONS ###
-  
-  # homogenize and extract the values from the observed period
[…]

### 2023-05-26 02-model/fit-model.R

@@ -102,10 +102,6 @@ jags_data$sig_Mb_obs["2007","spring-mig","NOR","UGR"] = NA
 # add NA indices in the correct locations
 jags_data = append_no_na_indices(jags_data)
 
-# set assumed survival past sea lions to 1 in all years
-# past time-trending patterns were causing problems with ocean survival estimation/simulation
-jags_data$phi_SL[2:nrow(jags_data$phi_SL),] = 1
-
 # proportion of spawners by age and population that are female
 # assume 50% female for all fish aged 4 or 5; 0% for age-3
 # constant for all years/populations/origin types

### 2023-05-26 02-model/fit-model.R
Update years called by model

@@ -90,7 +90,14 @@ my_cat("Output File: ", out_file)
 ##### STEP 1: PREPARE DATA FOR JAGS #####
 
 # build JAGS data object
-jags_data = create_jags_data_mult(c("CAT", "LOS", "MIN", "UGR"), first_y = ifelse(!args$sim, 1991, 2000), last_y = 2019)
+jags_data = create_jags_data_mult(
+  pops = c("CAT", "LOS", "MIN", "UGR"),
+  first_y = ifelse(!args$sim, 1991, 2000),
+  last_y = max(bio_dat$brood_year)
+)
+
+# plug in values for harvest rates not yet available
+jags_data$U[c("2020", "2021", "2022"),,] = jags_data$U[c("2017", "2018", "2019"),,]
 
 # remove trap abundance data in BY 2007 for UGR
 # estimates impossibly low, causing problems with model

### 2023-05-30 03-post-process/compare-sim-to-obs.Rmd
Remove references to sea lion survival
No longer part of model. Was discovered to be causing problems for ocean survival estimates (the stair-step mixed with a time-constant ocean survival was not working well)
Fix bug with identifying which years are simulated

@@
     label: "Scenario"
-    value: "base"
+    value: "base_vlong_sim"
     input: text
@@
 ```{r select-years}
-# all of the years included in the model
-all_yrs = as.numeric(rownames(jags_data$phi_SL))
+# the years included in the model
+all_yrs = as.numeric(dimnames(jags_data$Mb_obs)[[1]])
 

### 2023-05-30 03-post-process/output-plots.Rmd
Remove references to sea lion survival
No longer part of model. Was discovered to be causing problems for ocean survival estimates (the stair-step mixed with a time-constant ocean survival was not working well)
Fix bug with identifying which years are simulated

@@
     label: "Scenario"
-    value: "test-rmd_vshort"
+    value: "base_vlong"
     input: text
@@
 ```{r dimension-ids}
-# the years included by the model
-all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])
+# the years included in the model
+all_yrs = as.numeric(dimnames(jags_data$Mb_obs)[[1]])
 

### 2023-06-02 03-post-process/output-plots-children/08-misc-processes.Rmd
Rename file: misc-processes

--- 2023-05-04 03-post-process/output-plots-children/08-misc-process-model.Rmd
@@
 
-# Miscellaneous Process Model Components {.tabset .tabset-pills}
+# Miscellaneous Processes {.tabset .tabset-pills}
 
@@
 ```
+
+## Correction for Carcass Age Bias
+
+ {.tabset .tabset-pills}
+
+Exploratory analyses indicated that older fish (age-4 and age-5) are over represented in carcass surveys relative to age-3 fish (based on comparisons between weir and carcass composition data.
+This could cause model fit inconsistencies, and because Minam River does not have a weir, using only the carcass data to inform its age composition could give biased estimates.
+We thus devised a correction factor that allowed the observation model to fit to biased carcass counts based on a corrected latent value.
+
+```{r add-p-Sa}
+# extract posterior samples of spawners[year,age,origin,pop]
+Sa_post = post_subset(post, "^Sa[", matrix = TRUE)
+
+# extract posterior samples of corrected spawner composition [year,age-origin,pop]
+p_Sa_prime_post = post_subset(post, "^p_Sa_prime[", matrix = TRUE)
+
+# function to get p_Sa (uncorrected spawner composition) for one posterior sample
+g = function(i) {
+  # cat("\r", i)
+  Sa_i = array_format(Sa_post[i,])
+  Sa_i = abind::abind(Sa_i[,,1,], Sa_i[,,2,], along = 2)
+  p_Sa_i = apply(Sa_i, 3, function(x) apply(x, 1, function(y) y/sum(y)), simplify = FALSE)
+  p_Sa_i = do.call(abind::abind, c(lapply(p_Sa_i, t), along = 3))
+  na_ind = which(!is.na(p_Sa_i))
+  p_Sa_i = p_Sa_i[na_ind]
+  names(p_Sa_i) = stringr::str_remove(colnames(p_Sa_prime_post), "_prime")
+  p_Sa_i
+}
+
+# apply the function
+p_Sa_post = sapply(1:nrow(Sa_post), g)
+post = post_bind(post, t(p_Sa_post))
+```
+
+```{r p-Sa-prime-plots-fn}
+# function to create the plot for one population
+plot_f = function(j, ko) {
+  ko_names = paste0("Age-", rep(3:5, 2))
+  ko_names = paste(ko_names, rep(c("(NOR)", "(HOR)"), each = 3))
+  # realized time series
+  plot_tseries(est = post_summ(post, sub_index("^p_Sa[year,age,pop]$", year = ts_yrs, pop = j, age = ko)),
+               yrs = all_yrs[ts_yrs], label_text = ko_names[ko])
+
+  # time series that includes BH prediction only
+  add_tseries(post_summ(post, sub_index("^p_Sa_prime[year,age,pop]", year = ts_yrs, pop = j, age = ko)),
+              yrs = all_yrs[ts_yrs])
+}
+```
+
+Spawner percent composition displayed as `r colorize("latent (actual) time series", main_cols["model"])`  and the `r colorize("observed (i.e., biased in sampling, but accounted for in model) time series", main_cols["model2"])`.
+Put another way, `r colorize("perceived", main_cols["model2"])` and `r colorize("reality", main_cols["model"])`.
+
+## CAT
+
+```{r p-Sa-prime-plots-CAT, fig.width = p6_width, fig.height = p6_height}
+# loop over age/origin combos for CAT
+mypar(mfrow = c(2,3))
+junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_cat, ko = ko))
+axis_labels("Brood Year", "% Composition")
+```
+
+## LOS
+
+```{r p-Sa-prime-plots-LOS, fig.width = p6_width, fig.height = p6_height}
+# loop over age/origin combos for CAT
+mypar(mfrow = c(2,3))
+junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_los, ko = ko))
+axis_labels("Brood Year", "% Composition")
+```
+
+## MIN
+
+```{r p-Sa-prime-plots-MIN, fig.width = p6_width, fig.height = p6_height}
+# loop over age/origin combos for CAT
+mypar(mfrow = c(2,3))
+junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_min, ko = ko))
+axis_labels("Brood Year", "% Composition")
+```
+
+## UGR
+
+```{r p-Sa-prime-plots-UGR, fig.width = p6_width, fig.height = p6_height}
+# loop over age/origin combos for CAT
+mypar(mfrow = c(2,3))
+junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_ugr, ko = ko))
+axis_labels("Brood Year", "% Composition")
+```

### 2023-06-02 03-post-process/output-plots-children/03-fit-to-data.Rmd
Implement empty_plot()

@@
 plot_f = function(j) {
+  if (j != j_min) {
     plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
@@
                label_text = pops[j], yrs = all_yrs[ts_yrs], pt_cex = pt_cex)
+  } else {
+    empty_plot(label_text = pops[j])
+  }
+
 }
@@
 ```{r min-weir-ss, fig.width = 5, fig.height = 2.5}
-weir_sample_size(j_min)
+mypar(mfrow = c(1,1), mar = c(1,1,1,1), oma = c(0,0,0,0))
+empty_plot(text = "No Weir Data")
 ```

### 2023-06-02 03-post-process/output-plots-children/08-misc-processes.Rmd
Implement empty_plot()

@@
 plot_f = function(j) {
+  if (j != j_min) {
     keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
     plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+  } else {
+    empty_plot(label_text = pops[j])
+  }
 }
@@
 plot_f = function(j) {
+  if (j != j_min) {
     keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
     plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+  } else {
+    empty_plot(label_text = pops[j])
+  }
 }
@@
 plot_f = function(j) {
+  if (j != j_min) {
     keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
     plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+  } else {
+    empty_plot(label_text = pops[j])
+  }
 }
@@
 plot_f = function(j) {
+  if (j != j_min) {
     keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
     plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+  } else {
+    empty_plot(label_text = pops[j])
+  }
 }
@@
 plot_f = function(j) {
+  if (j != j_min) {
     keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
     plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
+  } else {
+    empty_plot(label_text = pops[j])
+  }
 }
@@
 plot_fn = function(j) {
+  if (length(simulated) > 0 & j != j_min) {
+    empty_plot(label_text = pops[j])
+  } else {
     plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], label_text = pops[j])
+  }
 }
@@
 plot_fn = function(j) {
+
+  if (length(simulated) > 0 & j != j_min) {
+    empty_plot(label_text = pops[j])
+  } else {
     x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))
-
     mp = barplot(x["mean",], ylim = ylim_01, xaxt = "n", col = tran_cols["model"], border = main_cols["model"])
@@
   }
+}
 
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-axis_labels("Age of Return", "Proportion of Strays by Age")
+axis_labels("Age of Return", "Age Composition of Strays")
 ```

### 2023-06-02 03-post-process/output-plots.Rmd
Implement empty_plot()
Prevent warnings when rendering Rmd

@@
     value: TRUE
-  include_misc_process_model:
-    label: "Include Misc. Process Model Output?"
+  include_misc_processes:
+    label: "Include Misc. Processes Output?"
     value: TRUE
@@
 # set global knitting options
-knitr::opts_chunk$set(echo = FALSE, fig.align = "center", dpi = 600, out.width = "75%")
+knitr::opts_chunk$set(echo = FALSE, fig.align = "center", dpi = 600, out.width = "75%", warning = FALSE)
 
@@
 
-```{r misc-process-model, child = "output-plots-children/08-misc-process-model.Rmd", eval = params$include_misc_process_model}
+```{r misc-processes, child = "output-plots-children/08-misc-processes.Rmd", eval = params$include_misc_processes}
 ```

### 2023-06-02 03-post-process/output-plots-children/09-equiv-rates.Rmd
Standardize SAR units on output plots

@@
 
-### LGR to Tributary
+### LGR to LGR
 
-This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).
+This is survival from $M^{a}$ (smolt at the top of LGR by origin, NOR fish aggregated across migratory strategy type) to $R^{a}$ (adults arriving to LGR).
 
-The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
+The adult portion is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
 For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
 The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.
+Only SARs through brood year `r max(all_yrs[sar_yrs])` are calculated, since this is the last brood with of all adult ages (3, 4, and 5) accounted for in the model.
 
@@
   # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j)) * 100
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j)) * 100
+  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
+  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
 
@@
   # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 10))
+  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 0.1))
 
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-axis_labels("Brood Year", "Adults per 100 Smolt")
+axis_labels("Brood Year", "Smolt \u2192 Adult Survival Rate")
 ```
@@
 junk = sapply(1:jags_data$nj, plot_fn)
-axis_labels("Brood Year", "BON \u2192 BON Survival")
+axis_labels("Brood Year", "Smolt \u2192 Adult Survival")
 ```

### 2023-06-02 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Implement empty_plot()
Color code the noise summary tables
Rather than bold, the color now shows directionality

@@
 no_data_plot = function(main = NULL) {
-  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
-  text(0,0, "No Data", font = 3)
+  empty_plot(text = "No Data", label_text = main)
 }
@@
 These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
-Bold values denote that the target value for verifying model assumptions was not within the 95% CRI of the across-year summary statistic and indicates a potential problem.
+Cells with color backgrounds indicate that the posterior or the summary statistic did not include the target value in the 95% CRI; red indicates the posterior was higher than the target blue indicates lower than the target.
 
@@
 
+# function to assign a color to a cell
+assign_color = function(x, do, target) {
+  cols_use = ifelse(!do | is.na(x), "white", ifelse(x < target, "blue", "red"))
+  alpha(unname(cols_use), 0.25)
+}
+
 # format the mean values to present in table
@@
 proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
-proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
+proc_error_ests$year_mean_col = with(proc_error_ests, assign_color(year_mean_mean, !yr_mean_incl_target, 1))
 proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
-proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
+proc_error_ests$year_sd_col = with(proc_error_ests, assign_color(year_sd_mean, !yr_sd_incl_target, 1))
 proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
-proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
+proc_error_ests$diff_col = with(proc_error_ests, assign_color(diff_mean, !diff_incl_target, 0))
 
 # drop unneeded columns
-proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
+proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_mean_col", "year_sd_mean", "year_sd_col", "diff_mean", "diff_col")]
 ```
@@
 proc_error_table = function(var) {
-  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
-  out[is.na(out)] = ""
-
-  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
+  # extract the numbers to display
+  out_values = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
+  out_values[is.na(out_values)] = ""
+
+  # extract the colors for the cells
+  out_colors = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = stringr::str_replace(var, "_mean$", "_col"))
+  out_colors[is.na(out_colors)] = "#FFFFFF80"
+
+  # make the table
+  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
     kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    column_spec(5, background = out_colors[,5]) %>%
+    column_spec(6, background = out_colors[,6]) %>%
+    column_spec(7, background = out_colors[,7]) %>%
+    column_spec(8, background = out_colors[,8]) %>%
+    column_spec(9, background = out_colors[,9]) %>%
     collapse_rows(columns = 1:4)
@@
 obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
-obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
+obs_error_ests$year_mean_col = with(obs_error_ests, assign_color(year_mean_mean, !yr_mean_incl_target, 0.5))
 obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
-obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
+obs_error_ests$year_sd_col = with(obs_error_ests, assign_color(year_sd_mean, !yr_sd_incl_target, sqrt(1/12)))
 obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
-obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
+obs_error_ests$diff_col = with(obs_error_ests, assign_color(diff_mean, !diff_incl_target, 0))
 
 # drop unneeded columns
-obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
+obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_mean_col", "year_sd_mean", "year_sd_col", "diff_mean", "diff_col")]
 ```
@@
 obs_error_table = function(var) {
-  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
-  out[is.na(out)] = ""
-  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")
-
-  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
+ # extract the numbers to display
+  out_values = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
+  out_values[is.na(out_values)] = ""
+  out_values$param = stringr::str_replace(out_values$param, "->", "$\\\\rightarrow$")
+
+  # extract the colors for the cells
+  out_colors = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = stringr::str_replace(var, "_mean$", "_col"))
+  out_colors[is.na(out_colors)] = "#FFFFFF80"
+
+  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
     kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
+    column_spec(6, background = out_colors[,6]) %>%
+    column_spec(7, background = out_colors[,7]) %>%
+    column_spec(8, background = out_colors[,8]) %>%
+    column_spec(9, background = out_colors[,9]) %>%
+    column_spec(10, background = out_colors[,10]) %>%
     collapse_rows(columns = 1:5)

### 2023-06-02 03-post-process/compare-sim-to-obs.Rmd

@@
 
-For us to use the state-space model as a simulation model (which is the ultimate intent), it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.
+For us to use output from the state-space model to parameterize simulation models, it would be desirable if several features of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.
 
@@
 Several quantities are supplied to the model as known without error in the observed time series (weir removals, hatchery smolt releases, harvest rates below BON, etc.).
-These time series were extended to the future years external to the model using basic averages or resampling from historical outcomes as appropriate.
-This exercise is purely for model validation.
+These time series were extended to the future years external to the model by simply duplicating the time series and "tacking it on".
+This exercise is purely for model validation, so we deemed this simple approach suitable.
 
@@
 
-If these summary statistics are inconsistent among the observed and simulated time periods, that indicates that the state-space model has not sufficiently captured the random processes that have generated the observed outcomes and that we may have reason to question the reliability of its ability to simulate future outcomes, at least as a direct extension of the historical population dynamics.
-
 In all figures in this section, these time periods were used:
@@
 
-The entire 1991 - 2019 period isn't used for the observed period because the early years did not have a hatchery program but the simulation has hatchery input in all years.
-Thus, including the non-hatchery years may throw off the inference.
+The entire 1991 -- `r all_yrs[max(obs_y)]` period isn't used for the observed period because the early years did not have a hatchery program.
 

### 2023-06-02 03-post-process/output-plots-children/08-misc-processes.Rmd

@@
 
-## Correction for Carcass Age Bias
-
- {.tabset .tabset-pills}
+## Correction for Carcass Age Bias {.tabset .tabset-pills}
 
@@
 
-## CAT
+### CAT
 
@@
 junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_cat, ko = ko))
-axis_labels("Brood Year", "% Composition")
+axis_labels("Brood Year", "Proportion of Spawners")
 ```
 
-## LOS
+### LOS
 
@@
 junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_los, ko = ko))
-axis_labels("Brood Year", "% Composition")
+axis_labels("Brood Year", "Proportion of Spawners")
 ```
 
-## MIN
+### MIN
 
@@
 junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_min, ko = ko))
-axis_labels("Brood Year", "% Composition")
+axis_labels("Brood Year", "Proportion of Spawners")
 ```
 
-## UGR
+### UGR
 
@@
 junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_ugr, ko = ko))
-axis_labels("Brood Year", "% Composition")
+axis_labels("Brood Year", "Proportion of Spawners")
 ```

### 2023-06-02 03-post-process/output-plots-children/13-post-vs-prior.Rmd

@@
       prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
-      label_text = titles[j], 
+      label_text = titles[which(looping == j)], 
       legend_loc = ifelse(j == looping[1], legend_loc, NA),
@@
 xlim = c(-1,1)
-knitr::opts_chunk$set(fig.width = p4_height, fig.height = p4_width, out.width = "50%")
+knitr::opts_chunk$set(fig.width = p4_height * 1.1, fig.height = p4_width, out.width = "50%")
 ```

### 2023-06-07 100-math-description/GR-sslcm-math-description.Rmd
Edits to math document to reflect recent model changes
See check list in #183

@@
   bookdown::pdf_document2:
-    keep_tex: false
+    keep_tex: true
     toc: true
@@
 
-where $\Sigma_{\phi^{A \rightarrow B}}$ is an $n_j \times n_j$ matrix with the structure:
+where $\Sigma_{\phi^{A \rightarrow B}}$ is an $n_j \times n_j$ matrix constructed of population-specific variance terms $\left(\sigma_{\phi^{A \rightarrow B}_j}\right)^2$ and correlation terms specific to each pair of populations $j$ and $j^\prime$ $\rho_{\phi^{A \rightarrow B}_{j,j^{\prime}}}$:
 
@@
 \begin{array}{cccc}
-\left(\sigma_{\phi^{A \rightarrow B}_{j=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}} & \dots & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}} \\
-\sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \left(\sigma_{\phi^{A \rightarrow B}_{j=2}}\right)^2 & \dots & \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}} \\
+\left(\sigma_{\phi^{A \rightarrow B}_{j=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}_{j=1,j^{\prime}=2}} & \dots & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}_{j=1,j^{\prime}=n_j}} \\
+\sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}_{j=2,j^{\prime}=1}} & \left(\sigma_{\phi^{A \rightarrow B}_{j=2}}\right)^2 & \dots & \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}_{j=2,j^{\prime}=n_j}} \\
 \vdots & \vdots & \ddots & \vdots \\
-\sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}} & \dots & \left(\sigma_{\phi^{A \rightarrow B}_{j=n_j}}\right)^2
+\sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}_{j=n_j,j^{\prime}=1}} & \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}_{j=n_j,j^{\prime}=2}} & \dots & \left(\sigma_{\phi^{A \rightarrow B}_{j=n_j}}\right)^2
 \end{array}
@@
 
-That is, all populations ($j$) have unique variance terms $(\sigma_{\phi^{A \rightarrow B}_j})^2$ but we assume the correlation component of the covariance calculation ($\rho_{\phi^{A \rightarrow B}}$) is identical for all population pairs.
 In cases where a quantity varies annually and is different by origin but not by population, $\Sigma$ would have dimensions $n_o \times n_o$:
@@
 
-Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma_j$ (or $\sigma_o$) and $\rho$ terms that were assigned priors ($\mathcal{U}(0,5)$ and $\mathcal{U}(-1,1)$, respectively, Table \@ref(tab:param-table)) and the $\Sigma$ matrices were constructed using the structures defined in eqs.
-\@ref(eq:generic-Sigma4by4) and \@ref(eq:generic-Sigma2by2).
+We estimated these covariance matrices by assigning their inverse ($\Sigma^{-1}$) a scaled Wishart prior distribution (Table \@ref(tab:param-table)).
+Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma$ and $\rho$ terms that we were interested in for inference.
 
@@
 \begin{equation}
-E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k} \cdot f_{k}
+E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k} \cdot f_{y,k,j}
 (\#eq:get-E)
@@
 
-We assumed that spawners age-4 or age-5 were 50% female and age-3 spawners were all male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data) and estimated fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
+We assumed that spawners age-4 or age-5 were 50% female and age-3 spawners were all male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data) and estimated fecundity ($f_{y,k,j}$) from length-fecundity relationships based on Grande Ronde-origin hatchery broodstock.
 We supplied both quantities to the model assuming no error or inter-annual variability.
@@
 \@ref(eq:get-phi-E-Pb-dot).
-Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \rightarrow P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$ (constructed of $\sigma_{\phi^{E \rightarrow P^{b}}_j}$ and $\rho_{\phi^{E \rightarrow P^{b}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \rightarrow P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$:
 
@@
 
-and the realized parr mean length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$ (constructed of $\sigma_{L_{j}^{P^{b}}}$ and $\rho_{L^{P^{b}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+and the realized parr mean length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$:
 
@@
 where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
-We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \mathrm{fall},j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$ (constructed of $\sigma_{\pi_{i=\mathrm{fall},j}}$ and $\rho_{\pi_{i=\mathrm{fall}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \mathrm{fall},j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$:
 
@@
 \begin{equation}
-\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,i,j} \cdot L^{*P^{b}}_{y,j}
+\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot L^{*P^{b}}_{y,j}
 (\#eq:get-phi-Pa-Mb-dot)
@@
 
-where $L^{*P^{b}}_{y,j}$ is parr mean length scaled and centered by subtracting the historical average observed parr mean length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation.
-Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}$ (each matrix constructed of $\sigma_{\phi^{P^{a} \rightarrow M^{b}}_{i,j}}$ and $\rho_{\phi^{P^{a} \rightarrow M^{b}}_{i}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+where $L^{*P^{b}}_{y,j}$ is parr mean length scaled and centered by subtracting the historical average observed parr mean length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation in mean length across years.
+Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}}$ (assumed common among migratory strategies):
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
+\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}}\right]
 (\#eq:phi-Pa-Mb-random)
@@
 
+$\rho_{\pi_{i=\mathrm{fall},j,j^{\prime}}}$
+
 We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
@@
 
-and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ (constructed of $\sigma_{\Delta_{j}^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ and $\rho_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$:
 
@@
 For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \rightarrow M^{a}}_{y,o=\mathrm{HOR},j}$ were equal within a population).
-For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}$ (each matrix constructed of $\sigma_{\phi^{M^{b} \rightarrow M^{a}}_{o,j}}$ and $\rho_{\phi^{M^{b} \rightarrow M^{a}}_o}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}}$ (assumed common across origin types):
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}_o}\right]
+\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}}\right]
 (\#eq:phi-Mb-Ma-random)
@@
 We modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
-We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$ (constructed of $\sigma_{\phi^{M^{a} \rightarrow O^{0}}_{o}}$ and $\rho_{\phi^{M^{a} \rightarrow O^{0}}}$ following eq.
-\@ref(eq:generic-Sigma2by2)):
+We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$:
 
@@
 
-The observation model components for the freshwater juvenile life stage were fitted to three primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary, \todo{Include reference to document describing methods of juvenile passage estimation}) in either the fall or spring, (_ii_) survival of juveniles from several PIT tagging events to LGR \todo{Include reference to document describing methods of juvenile survival estimation based on PIT tags}, and (iii) the mean length of sampled individuals during two of the PIT tagging events \todo{Include reference to document describing methods of juvenile mean length estimation}.
+The observation model components for the freshwater juvenile life stage were fitted to three primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary, \todo{Include reference to document describing methods of juvenile passage estimation}) in either the fall or spring, (_ii_) survival of juveniles from several PIT tagging events to LGR \todo{Include reference to document describing methods of juvenile survival estimation based on PIT tags}, and (_iii_) the mean length of sampled individuals during two of the PIT tagging events \todo{Include reference to document describing methods of juvenile mean length estimation}.
 For all types, the information supplied to the model were externally compiled estimates (e.g., survival from Cormack-Jolly-Seber models) and the estimated standard error was supplied to the model as a measure of observation error variability.
@@
 We assumed first year natural-origin^[All $o=\mathrm{NOR}$ in eq.
-\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$ (constructed of $\sigma_{\phi^{O^{0} \rightarrow O^{1}}_{j}}$ and $\rho_{\phi^{O^{0} \rightarrow O^{1}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)), but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
+\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
 paper on PDO}:
@@
 
-We treated realized maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) as multivariate logit-normal random variables around time-constant expected values ($\dot{\psi}^{O^{w}}_{o,j}$; $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}_o}$ (one matrix per origin, each constructed of $\sigma_{\psi^{O^{w}}_{o,j}}$ and $\rho_{\psi^{O^{w}}_{o}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
+We treated realized maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) as multivariate logit-normal random variables around time-constant expected values ($\dot{\psi}^{O^{w}}_{o,j}$; $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}}$ (assumed common across origins):
 
@@
 \begin{aligned}
-\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
-\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
+\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}}\right] \\
+\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}}\right]
 \end{aligned}
@@
 We placed returning mature fish into the correct year and age of return to the mouth of the Columbia River before the upstream migration ($R^{b}_{y,k,o,j}$) based on the following rule.
-Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age of maturity in year $y + k_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $k_{\mathrm{min}}$ = 3).
+Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age of maturity in year $y + A_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $A_{\mathrm{min}}$ = 3).
 As an example, fish spawned in brood year $y$ = 2000 will return in 2003 as age-3 ($k$ = 1), in 2004 as age-4 ($k$ = 2), or in 2005 as age-5 ($k$ = 3) -- see Table \@ref(tab:year-table) for a visual of this example.
@@
 \begin{aligned}
-R^{b}_{y+k_{\mathrm{min}} + 1 - 1,1,o,j} &= O^{1}_{y,o,j} \cdot \psi^{O^{1}}_{y,o,j} \\
-R^{b}_{y+k_{\mathrm{min}} + 2 - 1,2,o,j} &= O^{2}_{y,o,j} \cdot \psi^{O^{2}}_{y,o,j} \\
-R^{b}_{y+k_{\mathrm{min}} + 3 - 1,3,o,j} &= O^{3}_{y,o,j} \cdot \psi^{O^{3}}_{y,o,j} \\
+R^{b}_{y+A_{\mathrm{min}} + 1 - 1,1,o,j} &= O^{1}_{y,o,j} \cdot \psi^{O^{1}}_{y,o,j} \\
+R^{b}_{y+A_{\mathrm{min}} + 2 - 1,2,o,j} &= O^{2}_{y,o,j} \cdot \psi^{O^{2}}_{y,o,j} \\
+R^{b}_{y+A_{\mathrm{min}} + 3 - 1,3,o,j} &= O^{3}_{y,o,j} \cdot \psi^{O^{3}}_{y,o,j} \\
 \end{aligned}
@@
 
-Prior to reaching BON, we subject the returning adults to predation mortality from sea lions (survival denoted by $\phi^{SL}_{y,j}$) and harvest mortality from fisheries (harvest rate on fish surviving sea lion predation denoted by $U_{y,k,o}$).\todo{Insert information about where harvest rates and sea lion predation estimates came from.}
-We compiled the best available estimates of these quantities, but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error (used in eq.
+Prior to reaching BON, we subject returning adults to harvest mortality from fisheries (harvest rate denoted by $U_{y,k,o}$).\todo{Insert information about where harvest rate estimates came from.}
+We compiled the best available estimates but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error (used in eq.
 \@ref(eq:get-Ra), below).
@@
 
-Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$ (constructed of $\sigma_{\phi^{R^{b} \rightarrow R^{a}}_o}$ and $\rho_{\phi^{R^{b} \rightarrow R^{a}}}$ following eq.
-\@ref(eq:generic-Sigma2by2)).
+Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$.
 In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the expected value in these years for parameter identifiability purposes:
@@
 \begin{equation}
-R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot \phi^{SL}_{y,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
+R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
 (\#eq:get-Ra)
 \end{equation}
-
-\todo{Include note that no mortality is assumed between LGR and the natal tributary.}
 
@@
 We supplied these weir removals (denoted by $B_{y,k,o,j}$) to the model as known without error and set all $B_{y,k,o,j=\mathrm{MIN}} = 0$.
-Thus, the abundance of adults that would have a chance to spawn each year was (the maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$):
+Similarly, fish are harvested in the natal tributaries prior to spawning, and we additionally supplied estimates of fish harvested ($H_{y,k,o,j}$).
+Thus, the abundance of adults that would have a chance to spawn each year was:
 
 \begin{equation}
-S^{b}_{y,k,o,j} = \max\left(R^{a}_{y,k,o,j} - B_{y,k,o,j}, 1\right)
+S^{b}_{y,k,o,j} = \max\left(R^{a}_{y,k,o,j} - B_{y,k,o,j} - H_{y,k,o,j}, 1\right)
 (\#eq:get-Sb)
@@
 
+The maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$.
 As a final step prior to spawning, these adults must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
-We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, as multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$) with covariance matrix $\Sigma_{\phi^{S^{b} \rightarrow S^{a}}}$ (constructed of $\sigma_{\phi^{S^{b} \rightarrow S^{a}}_j}$ and $\rho_{\phi^{S^{b} \rightarrow S^{a}}}$ following eq.
-\@ref(eq:generic-Sigma4by4)):
-
-\begin{equation}
-\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
-(\#eq:phi-Sb-Sa-random)
-\end{equation}
-
+We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, as having a time-constant value (i.e., all $\phi^{S^{b} \rightarrow S^{a}}_{y,j} = \dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$).
+We desired to allow for time-varying pre-spawn survival probabilities, but discovered that the observational data were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
 Thus, the abundance of successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
@@
 
+# replace year variables
+tab$Description = stringr::str_replace(tab$Description, "F_YEAR", "1991")
+tab$Description = stringr::str_replace(tab$Description, "L_YEAR", "2022")
+tab$Description = stringr::str_replace(tab$Description, "N_YEAR", as.character(length(1991:2022)))
+
 # specify footnote text (requires LaTeX syntax, and all instances of \ require four "\\\\")
@@
   "1" = "``Population'' is used to distinguish among the tributaries within the Grande Ronde basin with sufficient data to model complete life cycle population dynamics.
-Abbreviations are as follows: Catherine Creek (CAT), Lostine River (LOS), Minam River (MIN), and Upper Grande Ronde River (UGR).",
-  "2" = "``Year'' refers to the year of spawning; for juvenile phases this is the year fish were spawned (i.e., brood year) and for adult phases this is the year of spawning (i.e., return or calendar year).",
-  "3" = "``Age'' refers to the total age, i.e., the number of winters experienced post-spawning including the winter spent as an egg.
-For example, eggs fertilized in brood year 2000 are age-0 until they hatch in spring of 2001 (age-1), migrate to sea in spring/summer of 2002 (age-2), and return to spawn in one of 2003 (age-3), 2004 (age-4), or 2005 (age-5).
+Abbreviations are: Catherine Creek (CAT), Lostine River (LOS), Minam River (MIN), and Upper Grande Ronde River (UGR).",
+  "2" = "``Year'' refers to the year of spawning; for juvenile phases this is the year fish were spawned (i.e., brood year) and for adult phases this is the year of return (i.e., calendar year).",
+  "3" = "``Age'' refers to the total age, i.e., the number of winters experienced (including the winter spent as an egg).
+For example, eggs fertilized in brood year 2000 were age-0 until they hatched in spring of 2001 (age-1), migrated to sea in spring/summer of 2002 (age-2), and returned to spawn in one of 2003 (age-3), 2004 (age-4), or 2005 (age-5).
 $k=1$ is the first age of maturation (age-3) and $k=3$ is the last age of maturation (age-5).",
-  "4" = "``Migratory strategy'' refers to the timing of migration from headwaters rearing areas -- some fish (fall migrants) migrate out in the fall at age-1 and spend the winter downstream whereas others stay and migrate out at age-2 (spring migrants).
-Regardless of this migratory strategy, all fish make the seaward out-of-basin migration at age-2.",
-  "5" = "``Origin'' refers to the type of spawning that produced the fish in question: natural-origin (NOR) are fish that were spawned in the wild and hatchery-origin (HOR) are fish that were spawned in a hatchery setting.",
+  "4" = "``Migratory strategy'' refers to the timing of migration from headwaters rearing areas -- either as fall (as age-1) or spring (age-2) migrants.
+Regardless, all fish make the out-of-basin migration at age-2.",
+  "5" = "``Origin'' refers to the rearing type: natural-origin (NOR) vs. hatchery-origin (HOR).",
   "6" = "Most quantities treat age ($k$) and origin ($o$) as two separate dimensions of a larger array.
-However, for fitting to compositional data by age and origin, we collapse these two dimensions into one such that a single vector of proportions can represent the composition by age and origin.
+However, for fitting to compositional data by age and origin, we collapse these two dimensions into one.
 $ko \\\\in [1,2,3]$ represents age-3, age-4, and age-5 for natural-origin fish, respectively, and $ko \\\\in [4,5,6]$ represents these same ages for hatchery-origin fish, respectively."
@@
 ```{r param_tab_cap}
-param_tab_cap = "All free parameters (i.e., that have a prior that is not function of other free parameters) estimated by the state-space life cycle model for Grande Ronde spring Chinook salmon."
+param_tab_cap = "All free parameters (i.e., that have a prior that is not function of other free parameters) estimated by the state-space life cycle model for Grande Ronde spring Chinook salmon.
+Distributions and their parameterizations are defined in the footnotes."
 ```
@@
   "3" = "Uniform Distribution: $\\\\mathcal{U}(\\\\mathrm{lower}$, $\\\\mathrm{upper})$",
-  "4" = "$t$-Distribution: $t$(mean, precision, degrees of freedom)",
-  "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$"
+  "4" = "$t$-Distribution: $t$(mean, precision, degrees of freedom); this prior results in approximately a $\\\\mathcal{U}(0,1)$ prior after inverse-logit transformation \\\\citep{dorazio-etal-2011}.",
+  "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$",
+  "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see JAGS v4.3.0 user manual page 62 for details on this prior.
+Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale.
+Setting the degrees of freedom to 2 results in a $\\\\mathcal{U}(-1,1)$ prior on the $\\\\rho$ components."
 )
 
-colnames(tab)[3] = "Prior\\textsuperscript{1,2,3,4,5}"
+colnames(tab)[3] = "Prior\\textsuperscript{1,2,3,4,5,6}"
 colnames(tab)[4] = "Eq."
@@
 year_tab_caption = "Year of return based on age of return and brood year.
-For example, adults that are progeny of the spawners in returning in 2000 (the brood year) return to spawn in the year 2003 as age-3, 2004 as age-4, and in 2005 as age-5 (shown in blue, example also given in the text in Section \\ref{return-to-columbia-river}).
+For example, adults that were progeny of spawners in 2000 (their brood year) returned to spawn in 2003 as age-3, 2004 as age-4, and 2005 as age-5 (shown in blue).
 The return years with red brood years show the age-specific return abundances that were estimated because no previous states (e.g., parr, smolt) were available for these early brood years (see Section \\ref{return-to-columbia-river} for more details)."
@@
 
-return_year = 1991:2019
-age_3 = 1988:2016
-age_4 = 1987:2015
-age_5 = 1986:2014
+return_year = 1991:2022
+age_3 = 1988:2019
+age_4 = 1987:2018
+age_5 = 1986:2017
 
@@
 tab_start = tab_full[tab_full$return_year %in% c(1991:1996),]
-tab_end = tab_full[tab_full$return_year %in% c(2019),]
+tab_end = tab_full[tab_full$return_year %in% c(2022),]
 tab_middle = tab_full[tab_full$return_year %in% c(2003:2005),]

### 2023-06-07 100-math-description/GR-sslcm-math-description.Rmd
Replace \rightarrow with \to
Much more readable

@@
   - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
+  # - \newcommand{\fall}{\mathrm{fall}}
+  # - \newcommand{\spring}{\mathrm{spring}}
+  # - \newcommand{\NOR}{\mathrm{NOR}}
+  # - \newcommand{\HOR}{\mathrm{HOR}}
 ---
@@
 E.g., $M^{b}$ is not "$M$ raised to the power $b$"; if we must raise the quantity $M^{b}$ to the power $c$, it will be written $(M^{b})^c$.
-* Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \rightarrow B}_{y,j}$.
-* We denote the expected value of a stochastic process with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$ -- this is the value expected in the absence of process variability.
+* Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \to B}_{y,j}$.
+* We denote the expected value of a stochastic process with a dot, e.g., $\dot{\phi}^{A \to B}_j$ -- this is the value expected in the absence of process variability.
 * In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array).
 Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax.
-E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for each population.
+E.g., $\boldsymbol{\phi}^{A \to B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for each population.
 * Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.
@@
 * $\logit\left(p\right)$ represents the log odds of $p$ (i.e., $\log\left[p/(1-p)\right])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
-* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \rightarrow B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \rightarrow B}_{y,j}}$, which we use as a direct estimate of observation error variability).
+* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \to B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \to B}_{y,j}}$, which we use as a direct estimate of observation error variability).
 * Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (or mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution; generally $\theta_{1}$ is a location parameter specifying the expected value of $x_{y}$ and $\theta_{2}$ is a dispersion parameter specifying the variability of $x_{y}$ around the expected value.
@@
 The covariance matrix of these random variables are denoted by $\Sigma$, and have a common structure for all model components.
-Take the hypothetical survival term $\phi^{A \rightarrow B}_{y,j}$ as an example.
+Take the hypothetical survival term $\phi^{A \to B}_{y,j}$ as an example.
 We denote its random variability across years and populations as:
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
+\logit\left(\boldsymbol{\phi}^{A \to B}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \to B}_{y,1:n_j}\right), \Sigma_{\phi^{A \to B}} \right]
 (\#eq:generic-random)
@@
 
-where $\Sigma_{\phi^{A \rightarrow B}}$ is an $n_j \times n_j$ matrix constructed of population-specific variance terms $\left(\sigma_{\phi^{A \rightarrow B}_j}\right)^2$ and correlation terms specific to each pair of populations $j$ and $j^\prime$ $\rho_{\phi^{A \rightarrow B}_{j,j^{\prime}}}$:
+where $\Sigma_{\phi^{A \to B}}$ is an $n_j \times n_j$ matrix constructed of population-specific variance terms $\left(\sigma_{\phi^{A \to B}_j}\right)^2$ and correlation terms specific to each pair of populations $j$ and $j^\prime$ $\rho_{\phi^{A \to B}_{j,j^{\prime}}}$:
 
@@
 \begin{array}{cccc}
-\left(\sigma_{\phi^{A \rightarrow B}_{j=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}_{j=1,j^{\prime}=2}} & \dots & \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}_{j=1,j^{\prime}=n_j}} \\
-\sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}_{j=2,j^{\prime}=1}} & \left(\sigma_{\phi^{A \rightarrow B}_{j=2}}\right)^2 & \dots & \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \rho_{\phi^{A \rightarrow B}_{j=2,j^{\prime}=n_j}} \\
+\left(\sigma_{\phi^{A \to B}_{j=1}}\right)^2 & \sigma_{\phi^{A \to B}_{j=1}} \cdot \sigma_{\phi^{A \to B}_{j=2}} \cdot \rho_{\phi^{A \to B}_{j=1,j^{\prime}=2}} & \dots & \sigma_{\phi^{A \to B}_{j=1}} \cdot \sigma_{\phi^{A \to B}_{j=n_j}} \cdot \rho_{\phi^{A \to B}_{j=1,j^{\prime}=n_j}} \\
+\sigma_{\phi^{A \to B}_{j=2}} \cdot \sigma_{\phi^{A \to B}_{j=1}} \cdot \rho_{\phi^{A \to B}_{j=2,j^{\prime}=1}} & \left(\sigma_{\phi^{A \to B}_{j=2}}\right)^2 & \dots & \sigma_{\phi^{A \to B}_{j=2}} \cdot \sigma_{\phi^{A \to B}_{j=n_j}} \cdot \rho_{\phi^{A \to B}_{j=2,j^{\prime}=n_j}} \\
 \vdots & \vdots & \ddots & \vdots \\
-\sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=1}} \cdot \rho_{\phi^{A \rightarrow B}_{j=n_j,j^{\prime}=1}} & \sigma_{\phi^{A \rightarrow B}_{j=n_j}} \cdot \sigma_{\phi^{A \rightarrow B}_{j=2}} \cdot \rho_{\phi^{A \rightarrow B}_{j=n_j,j^{\prime}=2}} & \dots & \left(\sigma_{\phi^{A \rightarrow B}_{j=n_j}}\right)^2
+\sigma_{\phi^{A \to B}_{j=n_j}} \cdot \sigma_{\phi^{A \to B}_{j=1}} \cdot \rho_{\phi^{A \to B}_{j=n_j,j^{\prime}=1}} & \sigma_{\phi^{A \to B}_{j=n_j}} \cdot \sigma_{\phi^{A \to B}_{j=2}} \cdot \rho_{\phi^{A \to B}_{j=n_j,j^{\prime}=2}} & \dots & \left(\sigma_{\phi^{A \to B}_{j=n_j}}\right)^2
 \end{array}
@@
 \begin{array}{cc}
-\left(\sigma_{\phi^{A \rightarrow B}_{o=1}}\right)^2 & \sigma_{\phi^{A \rightarrow B}_{o=1}} \cdot \sigma_{\phi^{A \rightarrow B}_{o=2}} \cdot \rho_{\phi^{A \rightarrow B}} \\
-\sigma_{\phi^{A \rightarrow B}_{o=2}} \cdot \sigma_{\phi^{A \rightarrow B}_{o=1}} \cdot \rho_{\phi^{A \rightarrow B}} & \left(\sigma_{\phi^{A \rightarrow B}_{o=2}}\right)^2
+\left(\sigma_{\phi^{A \to B}_{o=1}}\right)^2 & \sigma_{\phi^{A \to B}_{o=1}} \cdot \sigma_{\phi^{A \to B}_{o=2}} \cdot \rho_{\phi^{A \to B}} \\
+\sigma_{\phi^{A \to B}_{o=2}} \cdot \sigma_{\phi^{A \to B}_{o=1}} \cdot \rho_{\phi^{A \to B}} & \left(\sigma_{\phi^{A \to B}_{o=2}}\right)^2
 \end{array}
@@
 We estimated these covariance matrices by assigning their inverse ($\Sigma^{-1}$) a scaled Wishart prior distribution (Table \@ref(tab:param-table)).
-Although the stochastic process requires the $\Sigma$ term, is is the component $\sigma$ and $\rho$ terms that we were interested in for inference.
+Although the stochastic process requires the $\Sigma$ term, it is the component $\sigma$ and $\rho$ terms that we were interested in for inference.
 
@@
 \begin{equation}
-\dot{\phi}^{E \rightarrow P^{b}}_{y,j} = \frac{1}{\frac{1}{\alpha_j} + \frac{E_{y,j}}{\beta_j}}
+\dot{\phi}^{E \to P^{b}}_{y,j} = \frac{1}{\frac{1}{\alpha_j} + \frac{E_{y,j}}{\beta_j}}
 (\#eq:get-phi-E-Pb-dot)
@@
 
-We modeled realized (i.e., with process noise) egg-to-parr survival as a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \rightarrow P^{b}}_{y,j}$) from eq.
+We modeled realized (i.e., with process noise) egg-to-parr survival as a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \to P^{b}}_{y,j}$) from eq.
 \@ref(eq:get-phi-E-Pb-dot).
-Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \rightarrow P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \rightarrow P^{b}}}$:
+Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \to P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \to P^{b}}}$:
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right) + \boldsymbol{\kappa}^{E \rightarrow P^{b}}_{1:n_j} \cdot \left[\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y-1,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y-1,1:n_j}\right)\right], \Sigma_{\phi^{E \rightarrow P^{b}}} \right\}
+\logit\left(\boldsymbol{\phi}^{E \to P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{E \to P^{b}}_{y,1:n_j}\right) + \boldsymbol{\kappa}^{E \to P^{b}}_{1:n_j} \cdot \left[\logit\left(\boldsymbol{\phi}^{E \to P^{b}}_{y-1,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{E \to P^{b}}_{y-1,1:n_j}\right)\right], \Sigma_{\phi^{E \to P^{b}}} \right\}
 (\#eq:phi-E-Pb-random)
@@
 \begin{equation}
-P^{b}_{y,j} = \phi^{E \rightarrow P^{b}}_{y,j} \cdot E_{y,j}
+P^{b}_{y,j} = \phi^{E \to P^{b}}_{y,j} \cdot E_{y,j}
 (\#eq:get-Pb)
@@
 
-We modeled expected survival from the parr (age-1) to in-basin smolt (age-2) stage (termed "overwinter" survival and denoted by $\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}$) as a logit-linear function of parr mean length:
+We modeled expected survival from the parr (age-1) to in-basin smolt (age-2) stage (termed "overwinter" survival and denoted by $\dot{\phi}^{P^{a} \to M^{b}}_{y,i,j}$) as a logit-linear function of parr mean length:
 
 \begin{equation}
-\logit\left(\dot{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot L^{*P^{b}}_{y,j}
+\logit\left(\dot{\phi}^{P^{a} \to M^{b}}_{y,i,j}\right) = \gamma_{0,i,j} + \gamma_{1,j} \cdot L^{*P^{b}}_{y,j}
 (\#eq:get-phi-Pa-Mb-dot)
@@
 where $L^{*P^{b}}_{y,j}$ is parr mean length scaled and centered by subtracting the historical average observed parr mean length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation in mean length across years.
-Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \rightarrow M^{b}}}$ (assumed common among migratory strategies):
+Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \to M^{b}}}$ (assumed common among migratory strategies):
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}}\right]
+\logit\left(\boldsymbol{\phi}^{P^{a} \to M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \to M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \to M^{b}}}\right]
 (\#eq:phi-Pa-Mb-random)
@@
 \begin{equation}
-M^{b}_{y,i,o=\mathrm{NOR},j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \rightarrow M^{b}}_{y,i,j}
+M^{b}_{y,i,o=\mathrm{NOR},j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \to M^{b}}_{y,i,j}
 (\#eq:get-Mb-NOR)
@@
 \begin{equation}
-\log\left(\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}\right) = \theta_{0,j} + \theta_{1,j} \cdot L^{*P^{b}}_{y,j}
+\log\left(\dot{\Delta}^{L^{P^{b}} \to L^{M^{b}}}_{y,j}\right) = \theta_{0,j} + \theta_{1,j} \cdot L^{*P^{b}}_{y,j}
 (\#eq:get-Delta-L-Pb-L-Mb-dot)
@@
 
-and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}$:
+and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \to L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \to L^{M^{b}}}}$:
 
 \begin{equation}
-\log\left(\boldsymbol{\Delta}^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,1:n_j}\right) \sim \MVNdist\left[\log\left(\boldsymbol{\dot{\Delta}}^{L^{P^{b} \rightarrow L^{M^{b}}}}_{y,1:n_j}\right), \Sigma_{\Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}}\right]
+\log\left(\boldsymbol{\Delta}^{L^{P^{b}} \to L^{M^{b}}}_{y,1:n_j}\right) \sim \MVNdist\left[\log\left(\boldsymbol{\dot{\Delta}}^{L^{P^{b} \to L^{M^{b}}}}_{y,1:n_j}\right), \Sigma_{\Delta^{L^{P^{b}} \to L^{M^{b}}}}\right]
 (\#eq:Delta-L-Pb-L-Mb-random)
@@
 \begin{equation}
-L^{M^{b}}_{y,j} = L^{P^{b}}_{y,j} \cdot \Delta^{L^{P^{b}} \rightarrow L^{M^{b}}}_{y,j}
+L^{M^{b}}_{y,j} = L^{P^{b}}_{y,j} \cdot \Delta^{L^{P^{b}} \to L^{M^{b}}}_{y,j}
 (\#eq:get-L-Mb)
@@
 We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams\todo{Insert reference to a document describing dams} encountered in the downstream migration, and (_ii_) from LGR to the ocean.
-For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
+For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
 
@@
 \begin{equation}
-\logit\left(\dot{\phi}^{M^{b} \rightarrow M^{a}}_{y,o=\mathrm{NOR},j}\right) = \tau_{0,j} + \tau_{1,j} \cdot L^{*M^{b}}_{y,j}
+\logit\left(\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\mathrm{NOR},j}\right) = \tau_{0,j} + \tau_{1,j} \cdot L^{*M^{b}}_{y,j}
 (\#eq:get-phi-Mb-Ma-dot)
@@
 where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed smolt mean length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
-For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \rightarrow M^{a}}_{y,o=\mathrm{HOR},j}$ were equal within a population).
-For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \rightarrow M^{a}}}$ (assumed common across origin types):
+For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\mathrm{HOR},j}$ were equal within a population).
+For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \to M^{a}}}$ (assumed common across origin types):
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \rightarrow M^{a}}_{y,o,1:n_j}\right), \Sigma_{\phi^{M^{b} \rightarrow M^{a}}}\right]
+\logit\left(\boldsymbol{\phi}^{M^{b} \to M^{a}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{b} \to M^{a}}_{y,o,1:n_j}\right), \Sigma_{\phi^{M^{b} \to M^{a}}}\right]
 (\#eq:phi-Mb-Ma-random)
@@
 \begin{equation}
-M^{a}_{y,i,o,j} = M^{b}_{y,i,o,j} \cdot \phi^{M^{b} \rightarrow M^{a}}_{y,o,j}
+M^{a}_{y,i,o,j} = M^{b}_{y,i,o,j} \cdot \phi^{M^{b} \to M^{a}}_{y,o,j}
 (\#eq:get-Ma)
@@
 
-We modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \rightarrow O^{0}}_{y,o}$).
-We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \rightarrow O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \rightarrow O^{0}}}$:
+We modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \to O^{0}}_{y,o}$).
+We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \to O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \to O^{0}}}$:
 
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
+\logit\left(\boldsymbol{\phi}^{M^{a} \to O^{0}}_{y,1:n_o}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \to O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \to O^{0}}}\right]
 (\#eq:phi-Ma-O0-random)
@@
 \begin{equation}
-O^{0}_{y,o,j} = \phi^{M^{a} \rightarrow O^{0}}_{y,o} \sum_i^{n_i} M^{a}_{y,i,o,j}
+O^{0}_{y,o,j} = \phi^{M^{a} \to O^{0}}_{y,o} \sum_i^{n_i} M^{a}_{y,i,o,j}
 (\#eq:get-O0)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
+\logit\left(\hat{\phi}^{P^{b} \to M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \to M^{a}}_{y,j}}\right]
 (\#eq:summer-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\mathrm{fall},j}}\right]
 (\#eq:fall-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \to P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\mathrm{spring},j}}\right]
 (\#eq:winter-surv-data)
@@
 
-for the winter tagging group (where $\phi^{P^{b} \rightarrow P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$),
+for the winter tagging group (where $\phi^{P^{b} \to P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$),
 
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
 (\#eq:spring-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
 (\#eq:spring-surv-HOR-data)
@@
 We used the output from a recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
-Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{NOR}}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o=\mathrm{HOR}}$ here).
+Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\mathrm{NOR}}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\mathrm{HOR}}$ here).
 We treated these estimates as representative of the survival for each population, which implies an assumption that the different populations we model experience similar conditions during this migration and ignores any effect of barge-transporting fish.
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \Ndist\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
+\logit\left(\hat{\phi}^{M^{a} \to O^{0}}_{y,o}\right) \sim \Ndist\left[\logit\left(\phi^{M^{a} \to O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \to O^{0}}_{y,o}}\right]
 (\#eq:hydro-surv-data)
@@
 We assumed first year natural-origin^[All $o=\mathrm{NOR}$ in eq.
-\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \rightarrow O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \rightarrow O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
+\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \to O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \to O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
 paper on PDO}:
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
+\logit\left(\boldsymbol{\phi}^{O^{0} \to O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \to O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \to O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \to O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \to O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \to O^{1}}} \right\}
 (\#eq:phi-O0-O1-random)
@@
 
-We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$, respectively).
-Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \rightarrow O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \rightarrow O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
+We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \to O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\mathrm{NOR},j}$, respectively).
+Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \to O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
 \todo{Are we using priors or fixed values? Include reference to reports where we can reference the specific values used.}
@@
 \begin{aligned}
-\logit\left(\phi^{O^{0} \rightarrow O^{1}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{0} \rightarrow O^{1}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
-\logit\left(\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{1} \rightarrow O^{2}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
-\logit\left(\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{2} \rightarrow O^{3}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
+\logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
+\logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
+\logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
 \end{aligned}
@@
 \begin{aligned}
-O^{1}_{y,o,j} &= O^{0}_{y,o,j} \cdot \phi^{O^{0} \rightarrow O^{1}}_{y,o,j} \\
-O^{2}_{y,o,j} &= O^{1}_{y,o,j} \cdot (1 - \psi^{O^{1}}_{y,o,j}) \cdot \phi^{O^{1} \rightarrow O^{2}}_{y,o,j} \\
-O^{3}_{y,o,j} &= O^{2}_{y,o,j} \cdot (1 - \psi^{O^{2}}_{y,o,j}) \cdot \phi^{O^{2} \rightarrow O^{3}}_{y,o,j} \\
+O^{1}_{y,o,j} &= O^{0}_{y,o,j} \cdot \phi^{O^{0} \to O^{1}}_{y,o,j} \\
+O^{2}_{y,o,j} &= O^{1}_{y,o,j} \cdot (1 - \psi^{O^{1}}_{y,o,j}) \cdot \phi^{O^{1} \to O^{2}}_{y,o,j} \\
+O^{3}_{y,o,j} &= O^{2}_{y,o,j} \cdot (1 - \psi^{O^{2}}_{y,o,j}) \cdot \phi^{O^{2} \to O^{3}}_{y,o,j} \\
 \end{aligned}
@@
 
-Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \rightarrow R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \rightarrow R^{a}}}$.
+Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \to R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \to R^{a}}}$.
 In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the expected value in these years for parameter identifiability purposes:
@@
 \begin{equation}
-\logit\left(\boldsymbol{\phi}^{R^{b} \rightarrow R^{a}}_{y,1:n_o}\right)
+\logit\left(\boldsymbol{\phi}^{R^{b} \to R^{a}}_{y,1:n_o}\right)
 \begin{cases}
-= \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
-\sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
+= \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \to R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
+\sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \to R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \to R^{a}}} \right] & \mbox{if $y \ge 10$}
 \end{cases}
@@
 \begin{equation}
-R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \rightarrow R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
+R^{a}_{y,k,o,j} = R^{b}_{y,k,o,j} \cdot (1 - U_{y,k,o}) \cdot \phi^{R^{b} \to R^{a}}_{y,o} + \left(G_{y,o,j} \cdot p^{G}_{k,j}\right)
 (\#eq:get-Ra)
@@
 As a final step prior to spawning, these adults must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
-We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \rightarrow S^{a}}_{y,j}$, as having a time-constant value (i.e., all $\phi^{S^{b} \rightarrow S^{a}}_{y,j} = \dot{\phi}^{S^{b} \rightarrow S^{a}}_{j}$).
+We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \to S^{a}}_{y,j}$, as having a time-constant value (i.e., all $\phi^{S^{b} \to S^{a}}_{y,j} = \dot{\phi}^{S^{b} \to S^{a}}_{j}$).
 We desired to allow for time-varying pre-spawn survival probabilities, but discovered that the observational data were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
@@
 \begin{equation}
-S^{a}_{y,k,o,j} = S^{b}_{y,k,o,j} \cdot \phi^{S^{b} \rightarrow S^{a}}_{y,j}
+S^{a}_{y,k,o,j} = S^{b}_{y,k,o,j} \cdot \phi^{S^{b} \to S^{a}}_{y,j}
 (\#eq:get-Sa)
@@
 \begin{equation}
-\hat{x}^{\mathrm{LGR}}_{y,o} \sim \Bdist\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
+\hat{x}^{\mathrm{LGR}}_{y,o} \sim \Bdist\left(\phi^{R^{b} \to R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
 (\#eq:upstream-surv-data)
@@
 \begin{equation}
-\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \Bdist\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
+\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \Bdist\left(\phi^{S^{b} \to S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
 (\#eq:prespawn-surv-data)
@@
 # Tables {-}
-
-\todo{Shorten the footnotes on the table describing the index notation -- they are excessively long.}
 

### 2023-06-07 100-math-description/GR-sslcm-math-description.Rmd
Create/implement shortcut commands
e.g., \NOR instead of having to type \mathrm{NOR}

@@
   - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
-  # - \newcommand{\fall}{\mathrm{fall}}
-  # - \newcommand{\spring}{\mathrm{spring}}
-  # - \newcommand{\NOR}{\mathrm{NOR}}
-  # - \newcommand{\HOR}{\mathrm{HOR}}
+  - \newcommand{\fall}{\mathrm{fall}}
+  - \newcommand{\spring}{\mathrm{spring}}
+  - \newcommand{\NOR}{\mathrm{NOR}}
+  - \newcommand{\HOR}{\mathrm{HOR}}
+  - \newcommand{\CAT}{\mathrm{CAT}}
+  - \newcommand{\LOS}{\mathrm{LOS}}
+  - \newcommand{\MIN}{\mathrm{MIN}}
+  - \newcommand{\UGR}{\mathrm{UGR}}
+  - \newcommand{\WUL}{\mathrm{WUL}}
 ---
@@
 
-To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\mathrm{WUL}_j$)^[Derivation of $\mathrm{WUL}_j$ is too detailed to describe fully here.
+To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\WUL_j$)^[Derivation of $\WUL_j$ is too detailed to describe fully here.
 Briefly, the relative ability of stream segments with different habitat characteristics to hold rearing parr was expressed in terms of the density of fish predicted to reside there by a complex generalized linear mixed model.
 The model was fitted to density estimates based on detectability-adjusted [@staton-etal-2022] summer snorkel counts with local habitat characteristics (e.g., pool frequency, water temperature, large wood density, etc.) as predictor variables.
-The weight of each stream segment was assigned based on the predicted density relative value to the segment with the highest value; $\mathrm{WUL}_j$ was then equal to the sum of segment-specific weight and length within the known spawning and rearing extent for each population.].
-We modeled parr recruitment capacity ($\beta_j$) as a function of this $\mathrm{WUL}_j$ metric:
+The weight of each stream segment was assigned based on the predicted density relative value to the segment with the highest value; $\WUL_j$ was then equal to the sum of segment-specific weight and length within the known spawning and rearing extent for each population.].
+We modeled parr recruitment capacity ($\beta_j$) as a function of this $\WUL_j$ metric:
 
 \begin{equation}
-\log\left(\beta_j\right) \sim \Ndist\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
+\log\left(\beta_j\right) \sim \Ndist\left[\log\left(\lambda \cdot \WUL_j\right), \sigma_{\beta} \right]
 (\#eq:beta-random)
@@
 
-where $\lambda$ is the expected change in parr capacity per 1 km change in weighted usable habitat length, and $\sigma_{\beta}$ is the log-normal standard deviation of variability in this relationship not captured by $\mathrm{WUL}$ values.
+where $\lambda$ is the expected change in parr capacity per 1 km change in weighted usable habitat length, and $\sigma_{\beta}$ is the log-normal standard deviation of variability in this relationship not captured by $\WUL$ values.
 
@@
 \begin{equation}
-\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \log\left(\frac{E_{y,j}}{\mathrm{WUL}_j}\right)
+\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \log\left(\frac{E_{y,j}}{\WUL_j}\right)
 (\#eq:get-L-Pb-dot)
@@
 Like many populations of stream-type spring Chinook salmon in the Columbia River basin \todo{Insert references about other CRB populations displaying the fall/spring migratory strategy}, there is life history diversity among the juveniles with respect to their migratory phenology and habitat types occupied for rearing overwinter.
-Some portion of the summer parr ($P^{b}_{y,j}$)  migrate out of the headwaters near where they were spawned in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \mathrm{fall}$) and the remaining portion migrate out the following spring (termed "spring migrants" and indexed by $i = \mathrm{spring}$).
+Some portion of the summer parr ($P^{b}_{y,j}$)  migrate out of the headwaters near where they were spawned in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \fall$) and the remaining portion migrate out the following spring (termed "spring migrants" and indexed by $i = \spring$).
 Due to this difference in migratory phenology, these two groups of fish are monitored separately \todo{Insert a reference to a recent ODFW screw trap monitoring report where it is stated (or implied) that migratory strategies are monitored separately.} depending on when they pass the rotary screw trap located in each tributary\todo{Create a map and include reference it here}.
@@
 where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
-We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \mathrm{fall},j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \mathrm{fall}}}$:
+We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \fall,j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \fall}}$:
 
 \begin{equation}
-\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
+\logit\left(\boldsymbol{\pi}_{y,i = \fall,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \fall,1:n_j}\right), \Sigma_{\pi_{i = \fall}}\right]
 (\#eq:pi-random)
@@
 
-Since there are only two migratory strategies, we obtained the proportion that are spring migrants as the complement ($\pi_{y,i = \mathrm{spring},j} = 1 - \pi_{y,i = \mathrm{fall},j}$).
+Since there are only two migratory strategies, we obtained the proportion that are spring migrants as the complement ($\pi_{y,i = \spring,j} = 1 - \pi_{y,i = \fall,j}$).
 
@@
 Since hatchery-origin smolts are released into the population in spring (see Section \@ref(hatchery-inputs)), we introduce the origin index ($o$) starting at the in-basin smolt stage prior to out-migration ($M^{b}_{y,i,o,j}$).
-The abundance of natural-origin (indexed by $o=\mathrm{NOR}$) smolt was then:
+The abundance of natural-origin (indexed by $o=\NOR$) smolt was then:
 
 \begin{equation}
-M^{b}_{y,i,o=\mathrm{NOR},j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \to M^{b}}_{y,i,j}
+M^{b}_{y,i,o=\NOR,j} = P^{a}_{y,i,j} \cdot \phi^{P^{a} \to M^{b}}_{y,i,j}
 (\#eq:get-Mb-NOR)
@@
 
-$\rho_{\pi_{i=\mathrm{fall},j,j^{\prime}}}$
+$\rho_{\pi_{i=\fall,j,j^{\prime}}}$
 
@@
 
-For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error \todo{Insert reference to a document that gives info about these smolt releases}) were stored in the variable $M^{b}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\mathrm{fall},o=\mathrm{HOR},j} = 0$.
+For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error \todo{Insert reference to a document that gives info about these smolt releases}) were stored in the variable $M^{b}_{y,i=\spring,o=\HOR,j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\fall,o=\HOR,j} = 0$.
 For all subsequent life stages, we tracked the abundance (and often survival) of hatchery-origin fish separately from natural-origin fish.
@@
 We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams\todo{Insert reference to a document describing dams} encountered in the downstream migration, and (_ii_) from LGR to the ocean.
-For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{fall},o=\mathrm{NOR},j} = \phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
+For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \to M^{a}}_{y,i=\fall,o=\NOR,j} = \phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
 
@@
 \begin{equation}
-\logit\left(\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\mathrm{NOR},j}\right) = \tau_{0,j} + \tau_{1,j} \cdot L^{*M^{b}}_{y,j}
+\logit\left(\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\NOR,j}\right) = \tau_{0,j} + \tau_{1,j} \cdot L^{*M^{b}}_{y,j}
 (\#eq:get-phi-Mb-Ma-dot)
@@
 where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed smolt mean length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
-For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\mathrm{HOR},j}$ were equal within a population).
+For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\HOR,j}$ were equal within a population).
 For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \to M^{a}}}$ (assumed common across origin types):
@@
 \begin{equation}
-\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
+\log\left(\hat{P}^{a}_{y,i=\fall,j}\right) \sim \Ndist\left[\log\left(P^{a}_{y,i=\fall,j} \right), \hat{\sigma}_{P^{a}_{y,i=\fall,j}}\right]
 (\#eq:fall-count-data)
@@
 \begin{equation}
-\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
+\log\left(\hat{M}^{b}_{y,i=\spring,o=\NOR,j}\right) \sim \Ndist\left[\log\left(M^{b}_{y,i=\spring,o=\NOR,j}\right), \hat{\sigma}_{M^{b}_{y,i=\spring,o=\NOR,j}}\right]
 (\#eq:spring-count-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{b} \to M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \to M^{a}}_{y,j}}\right]
+\logit\left(\hat{\phi}^{P^{b} \to M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\NOR,j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \to M^{a}}_{y,j}}\right]
 (\#eq:summer-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\mathrm{fall},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\fall,j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\fall,o=\NOR,j}}{P^{a}_{y,i=\fall,j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\fall,j}}\right]
 (\#eq:fall-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \to P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\mathrm{spring},j}}\right]
+\logit\left(\hat{\phi}^{P^{a} \to M^{a}}_{y,i=\spring,j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\spring,o=\NOR,j}}{P^{a}_{y,i=\spring,j} \cdot \phi^{P^{b} \to P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \to M^{a}}_{y,i=\spring,j}}\right]
 (\#eq:winter-surv-data)
@@
 
-for the winter tagging group (where $\phi^{P^{b} \to P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$),
+for the winter tagging group (where $\phi^{P^{b} \to P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\CAT, \LOS, \UGR]$),
 
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}}\right]
 (\#eq:spring-surv-data)
@@
 \begin{equation}
-\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
+\logit\left(\hat{\phi}^{M^{b} \to M^{a}}_{y,i=\spring,o=\HOR,j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\HOR,j}\right),\hat{\sigma}_{\phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\HOR,j}}\right]
 (\#eq:spring-surv-HOR-data)
@@
 
-for hatchery-origin smolt releases ($j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$).
+for hatchery-origin smolt releases ($j \in [\CAT, \LOS, \UGR]$).
 
@@
 We used the output from a recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
-Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\mathrm{NOR}}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\mathrm{HOR}}$ here).
+Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\NOR}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\HOR}$ here).
 We treated these estimates as representative of the survival for each population, which implies an assumption that the different populations we model experience similar conditions during this migration and ignores any effect of barge-transporting fish.
@@
 
-We assumed first year natural-origin^[All $o=\mathrm{NOR}$ in eq.
-\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \to O^{1}}_{o=\mathrm{NOR},j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \to O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
+We assumed first year natural-origin^[All $o=\NOR$ in eq.
+\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \to O^{1}}_{o=\NOR,j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \to O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
 paper on PDO}:
@@
 
-We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{NOR},j}$ and $\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{NOR},j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \to O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\mathrm{NOR},j}$, respectively).
-Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \to O^{2}}_{o=\mathrm{NOR},j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\mathrm{NOR},j}$ (Table \@ref(tab:param-table)).
+We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \to O^{2}}_{y,o=\NOR,j}$ and $\phi^{O^{2} \to O^{3}}_{y,o=\NOR,j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$, respectively).
+Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$ (Table \@ref(tab:param-table)).
 \todo{Are we using priors or fixed values? Include reference to reports where we can reference the specific values used.}
@@
 \begin{aligned}
-\logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
-\logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
-\logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{HOR},j}\right) &= \logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\mathrm{NOR},j}\right) + \delta_j \\
+\logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\HOR,j}\right) &= \logit\left(\phi^{O^{0} \to O^{1}}_{y,o=\NOR,j}\right) + \delta_j \\
+\logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\HOR,j}\right) &= \logit\left(\phi^{O^{1} \to O^{2}}_{y,o=\NOR,j}\right) + \delta_j \\
+\logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\HOR,j}\right) &= \logit\left(\phi^{O^{2} \to O^{3}}_{y,o=\NOR,j}\right) + \delta_j \\
 \end{aligned}
@@
 We term this model component the "straying model", and applied it only in years/populations in which the presence of non-zero hatchery-origin returning adults could not otherwise be explained due to zero-valued hatchery-origin smolt releases.
-We denote the total number of strays that entered population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\mathrm{NOR},j} = 0$ and forced all $G_{y,o=\mathrm{HOR},j} = 0$ in years where non-zero hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
+We denote the total number of strays that entered population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\NOR,j} = 0$ and forced all $G_{y,o=\HOR,j} = 0$ in years where non-zero hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
 We denote the age composition of these strays by $p^{G}_{k,j}$ (where $\sum_k^{n_k} p^{G}_{k,j} = 1$) and apportioned $G_{y,o,j}$ to age-specific values by $G_{y,k,o,j}=G_{y,o,j} \cdot p^{G}_{k,j}$.
@@
 
-Upon arrival to the natal tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \mathrm{MIN}$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
-We supplied these weir removals (denoted by $B_{y,k,o,j}$) to the model as known without error and set all $B_{y,k,o,j=\mathrm{MIN}} = 0$.
+Upon arrival to the natal tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \MIN$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
+We supplied these weir removals (denoted by $B_{y,k,o,j}$) to the model as known without error and set all $B_{y,k,o,j=\MIN} = 0$.
 Similarly, fish are harvested in the natal tributaries prior to spawning, and we additionally supplied estimates of fish harvested ($H_{y,k,o,j}$).
@@
 Due to the age sampling bias of carcass surveys we discovered, we required a correction to ensure reliable fits to all data sets while still recovering unbiased true age composition data for the Minam River population, which had only carcass composition data (the other three populations had both weir and carcass composition data).
-For the three populations with paired composition data (i.e., $j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]$), we estimated correction factors in a hierarchical fashion:
+For the three populations with paired composition data (i.e., $j \in [\CAT, \LOS, \UGR]$), we estimated correction factors in a hierarchical fashion:
 
@@
 \begin{equation}
-\zeta_{k,j=\mathrm{MIN}} = \mathrm{mean}(\zeta_{k,j \in [\mathrm{CAT}, \mathrm{LOS}, \mathrm{UGR}]})
+\zeta_{k,j=\MIN} = \mathrm{mean}(\zeta_{k,j \in [\CAT, \LOS, \UGR]})
 (\#eq:get-zeta-minam)

### 2023-06-08 100-math-description/GR-sslcm-math-description.Rmd
Improve rendering to .docx

@@
 
+```{r my-kable-fn}
+my_kable = function(x, ...) {
+
+  # detect the kable format
+  kable_format = ifelse(is_latex_output(), "latex", "markdown")
+
+  # build the kable with supplied options as well as my fixed defaults
+  kable(x = x, format = kable_format, escape = FALSE, booktabs = TRUE, linesep = "", ...)
+}
+```
+
 \pagenumbering{gobble}
@@
 
-$\rho_{\pi_{i=\fall,j,j^{\prime}}}$
-
 We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
@@
 
-\clearpage
+\newpage
 
@@
 
-```{r index-table}
+```{r index-table, warning = FALSE}
 # read in csv version of table
@@
 # build the table
-kable(tab[,1:3], "latex", booktabs = TRUE, linesep = "", caption = index_tab_cap, escape = FALSE) %>%
+my_kable(x = tab[,1:3], caption = index_tab_cap) %>%
   kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
@@
 
-```{r symbol-table}
+```{r symbol-table, warning = FALSE}
 tab = read.csv("02-symbols.csv", allowEscapes = TRUE)
@@
     x_split = stringr::str_remove_all(x_split, " ")
+    if (is_latex_output()) {
       x_refs = paste0("\\ref{eq:", x_split, "}")
+    } else {
+      x_refs = paste0("\\@ref(eq:", x_split, ")")
+    }
     out = paste(x_refs, collapse = ", ")
@@
 
-kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = symbol_tab_cap, longtable = TRUE) %>%
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
@@
 
-```{r param-table}
+```{r param-table, warning = FALSE}
 tab = read.csv("03-params.csv", allowEscapes = TRUE)
@@
   "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see JAGS v4.3.0 user manual page 62 for details on this prior.
-Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale.
+Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale.
 Setting the degrees of freedom to 2 results in a $\\\\mathcal{U}(-1,1)$ prior on the $\\\\rho$ components."
@@
 
-kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = param_tab_cap, longtable = TRUE) %>%
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
@@
 
-```{r data-table}
+```{r data-table, warning = FALSE}
 tab = read.csv("04-data.csv", allowEscapes = TRUE)
@@
 
-kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = data_tab_cap, longtable = TRUE) %>%
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
@@
 
-```{r equation-table}
+```{r equation-table, warning = FALSE}
 tab = read.csv("05-equations.csv", allowEscapes = TRUE)
@@
 
-kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
+my_kable(x = tab[,2:4], caption = equation_tab_cap, longtable = TRUE, align = "lrl") %>%
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
@@
 
-```{r year-table}
+```{r year-table, warning = FALSE}
 
@@
 
-kable(tab, "latex", booktabs = TRUE, align = "cccc", linesep = "", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), escape = FALSE,
+my_kable(x = tab, align = "cccc", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), 
          caption = year_tab_caption, row.names = FALSE) %>%

### 2023-06-15 100-math-description/GR-sslcm-math-description.Rmd
More improvements for docx output

@@
 ---
-title: "\\textsc{Mathematical Description}"
-subtitle: "\\textsc{State-Space Life Cycle Model for Grande Ronde Spring Chinook Salmon}"
+title: "Mathematical Description"
+subtitle: "State-Space Life Cycle  Model for Grande Ronde Spring Chinook Salmon"
 output: 
@@
 citecolor: black
-bibliography: cites.bib
-link-citations: true
+bibliography: "GR-sslcm-cites.bib"
+link-citations: "`r ifelse(knitr::is_latex_output(), 'true', 'false')`"
 biblio-style: apalike
+csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/canadian-journal-of-fisheries-and-aquatic-sciences.csl"
 editor_options: 
@@
   - \renewcommand{\eqref}[1]{\ref{#1}}
-  - \renewcommand*{\log}{\mathrm{log}\hspace{-0.20em}}
-  - \renewcommand*{\max}{\mathrm{max}\hspace{-0.20em}}
-  - \newcommand{\logit}{\mathrm{logit}\hspace{-0.20em}}
-  - \newcommand{\ilogit}{\mathrm{logit}^{-1}\hspace{-0.20em}}
-  - \newcommand{\MVNdist}{\mathcal{MVN}\hspace{-0.20em}}
-  - \newcommand{\Ndist}{\mathcal{N}\hspace{-0.20em}}
-  - \newcommand{\Bdist}{\mathcal{B}\hspace{-0.20em}}
-  - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
   - \newcommand{\fall}{\mathrm{fall}}
@@
 library(kableExtra)
+library(officedown)
 ```
@@
 }
+```
+
+```{r bookdown-post-latex, eval = TRUE}
+# https://github.com/rstudio/bookdown/issues/8#issuecomment-564689497
+# easy method of placing bibliography somewhere other than at the end of the document always
+options(bookdown.post.latex = function(x) {
+
+  # x is the content of the LaTeX output file
+  # str_replace can take a named vector of patterns and replacements
+  replace_patterns <- c(
+    "\\\\bibliography\\{GR-sslcm-cites.bib\\}" = "",         # Remove the default bibliography
+    "^BIB HERE$" = "\\\\bibliography{GR-sslcm-cites.bib}"    # Add it in a new spot
+  )
+
+  stringr::str_replace_all(x, replace_patterns)
+})
+```
+
+```{r highlight-fn}
+highlight = function(note) {
+  if (knitr::is_latex_output()) {
+    paste0("\\hl{", note, "}")
+  } else {
+    ft = officer::fp_text(shading.color = "yellow", font.family = "Times New Roman", font.size = 11)
+    officer::ftext(toString(note), prop = ft)
+  }
+}
+```
+
+```{r new-commands, results = "asis"}
+# these are shortcut math mode commands
+# the hspace helps the appearance in latex, but it won't render to word
+# the code below removes it if rendered to word output
+commands = c(
+  "\\renewcommand*{\\log}{\\mathrm{log}\\hspace{-0.20em}}",
+  "\\renewcommand*{\\max}{\\mathrm{max}\\hspace{-0.20em}}",
+  "\\newcommand{\\logit}{\\mathrm{logit}\\hspace{-0.20em}}",
+  "\\newcommand{\\ilogit}{\\mathrm{logit}^{-1}\\hspace{-0.20em}}",
+  "\\newcommand{\\MVNdist}{\\mathcal{MVN}\\hspace{-0.20em}}",
+  "\\newcommand{\\Ndist}{\\mathcal{N}\\hspace{-0.20em}}",
+  "\\newcommand{\\Bdist}{\\mathcal{B}\\hspace{-0.20em}}",
+  "\\newcommand{\\Mdist}{\\mathcal{M}\\hspace{-0.20em}}"
+)
+
+if (!is_latex_output()) {
+  commands = stringr::str_remove(commands, "\\\\hspace\\{-0\\.20em\\}")
+}
+
+cat(commands, sep = "\n")
 ```
@@
 
+`r if (is_latex_output()) "BIB HERE"`
+
+`r if (is_latex_output()) "\\newpage"`
+
 # Figures {-}
@@
 
-\newpage
+`r if (is_latex_output()) "\\newpage"`
 
@@
 
+if (!is_latex_output()) {
+  tab$Description = stringr::str_replace_all(tab$Description, "``", '"')
+  tab$Description = stringr::str_replace_all(tab$Description, "''", '"')
+}
+
 my_kable(x = tab[,2:5], caption = param_tab_cap, longtable = TRUE) %>%
@@
 \newpage
-
-\listoftodos
-
-\newpage
-
-# References {-}
+`r if (!is_latex_output()) "# References {-}"`

### 2023-06-15 100-math-description/GR-sslcm-math-description.Rmd

@@
     citation_package: natbib
-  # bookdown::word_document2
+  # bookdown::word_document2:
+  #   reference_docx: "C:/Users/bstaton/Desktop/Staton/3_general/Rmd-docx-template/Rmd-docx-template-basic-TNR.docx"
+  #   number_sections: true
 fontfamily: mathpazo
-geometry: [top=1in,bottom=1in,left=0.25in,right=1.75in]
+geometry: [top=1in,bottom=1in,left=1in,right=1in]
 linkcolor: cyan
@@
 header-includes:
+  - \usepackage{natbib}
+  - \usepackage{soul}
+  - \setcitestyle{aysep={}}
+  - \usepackage[hang,flushmargin,bottom]{footmisc}
   - \usepackage{microtype}
@@
   - \usepackage{xcolor}
-  - \definecolor{my-blue}{HTML}{E6F0FF}
-  - \usepackage[textwidth=1.5in]{todonotes}
-  - \setuptodonotes{backgroundcolor=my-blue,textcolor=black,linecolor=ProcessBlue,bordercolor=my-blue,size=footnotesize}
+  - \usepackage[textwidth=1.5in,tickmarkheight=3pt]{todonotes}
+  - \setuptodonotes{backgroundcolor=black!40,textcolor=white,linecolor=black!65,bordercolor=black!65,size=footnotesize}
   - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
@@
 
-The purpose of the state-space life cycle model for Grande Ronde spring Chinook salmon is to synthesize data sets that have been collected as part of routine monitoring programs into a self-contained and internally consistent population dynamics model.
-Such a synthesis can provide richer insights about unobserved quantities (e.g., total parr recruitment abundance) and the relationships between them than allowed by more piecemeal analyses.
-Further, because the model estimates expected values and the magnitude of inter-annual variability in a time series framework, the output will be useful for structuring simulation models of future population dynamics to evaluate different management strategies.
-Although this is the ultimate goal and purpose of developing the state-space life cycle model described herein, we do not discuss this concept further, as it is beyond the scope of the statistical population dynamics model, which is the topic of this document.
-
-The state-space life cycle model tracks the fates of multiple cohorts of fish from egg to adulthood within a statistical population dynamics model.
-The model receives input data in the form of empirical observations or pre-processed output from other models (e.g., to derive survival rates from PIT tag records) and estimates unknown parameters that must be internally consistent with the data and one another.
-The model is considered "state-space" because it captures two discrete types of variability: (_i_) process noise, i.e., variability in the biological and environmental processes that produce population dynamics and outcomes and (_ii_) observation error, i.e., variability in the measurement processes that result in the observed data representing an imperfect perception of the true value being measured.
-As such, the model is inherently a time series model: spawners in one year produce eggs, which move through several life stages and ultimately return as spawners in future years -- it is the same pool of fish at one life stage that is decremented (via survival rate transition probabilities) to become a pool of fish used in the calculations for a later stage of the life cycle.
-We have described the life cycle model calculations as divided into three distinct life "phases" (Figure \@ref(fig:diagram)): freshwater juvenile, ocean juvenile, and freshwater adult.
-
-The model has several dimensions and the majority of processes are assumed to operate differently (i.e., have varying numerical values) along each dimension. These include:
-
-* **Age of Return** -- Anadromous Chinook salmon in the Grande Ronde basin return predominately as age-3, age-4, or age-5 adults.
-This means that monitoring activities in one year of adult returns sample fish that are progeny from from 3 consecutive brood (i.e., i.e., spawning) years, creating time linkages in the time series that are important to account for.
-* **Origin** -- Adults returning in any given year may be the result of either natural spawning/rearing in the wild or via captive spawning/rearing in a hatchery setting.
-These are critical to track separately because the productivity and capacity of naturally spawning salmon are key outputs of the model.
-* **Juvenile Migratory Strategy** -- Grande Ronde spring Chinook salmon juveniles exhibit two main phenological migratory strategies which may have different vital rates and require additional complexity in the observation model.
-* **Population** -- Four tributaries of the Grande Ronde River have been monitored using largely consistent methods for nearly three decades; these include Catherine Creek, Lostine River, Minam River, and Upper Grande Ronde River.
-We track the abundance and survival of each separately because they are monitored separately and local environmental conditions and/or genetic adaptations may result in population dynamics differing in terms of productivity, capacity, or overall life cycle fitness.
-
-We used the Bayesian mode of inference to fit the model to data, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs. observational variability).
-Further, Bayesian inference provides an intuitive framework to constrain parameters to take on only values known _a priori_ to be plausible -- we intentionally employ nearly exclusively uninformative prior information, but in several cases we were required to use auxiliary information in the form of reasonably strong priors (Table \@ref(tab:param-table)).
-An additional benefit of using the Bayesian framework is the seamless propagation of uncertainty from estimated parameters to derived quantities (of which there are many) -- all unknown quantities receive a posterior distribution.
-We employed Markov Chain Monte Carlo methods (implemented via the JAGS probabilistic programming language) to sample from the joint posterior distribution of all unknown quantities in the model.
+The purpose of developing the state-space life cycle model for Grande Ronde spring Chinook salmon is to estimate posterior distributions of population dynamics parameters (e.g., average survival, rearing capacity, coefficients of relationships linking life stages, etc.).
+These posterior distributions can ultimately be sampled from to parameterize simulation models that evaluate habitat restoration and climate change scenarios grounded in empirical monitoring data.
+The model tracks the cohort-specific abundance of fish through various life stages and links these "state variables" over time across cohorts via production relationships (e.g., spawners produce eggs) or within cohorts via transition probabilities (e.g., parr become smolt after surviving overwinter).
+The model integrates many different data sources and fits to them simultaneously in a single joint likelihood; these data sources include rotary screw trap passage estimates, a variety of PIT tag-derived survival estimates, mean length data, hatchery smolt releases, adult return abundance, and the composition of adult returns by age and origin; other data sources that are used but are not fitted to include hatchery smolt release abundances, harvest information, fecundity estiamtes, and numbers of returning adults removed for hatchery operations.
+Four spawning populations within the Grande Ronde basin are simultaneously analyzed: Catherine Creek (CAT), Lostine River (LOS), Minam River (MIN) and the upper Grande Ronde River (UGR; `r highlight("FIGURE REFERENCE: map")`), and where relevant, the model stratifies life stages by juvenile migratory strategy (fall vs.
+spring migrants), rearing origin type (spawned in hatchery vs.
+natural setting), and adult return age (total age of 3, 4, or 5 years).
+
+Central to the notion of a "state-space" model is the partitioning of variability in the observed data sets into two types: (_i_) process noise, i.e., variability in the biological and environmental processes that produce population outcomes and (_ii_) observation error, i.e., variability in the measurement processes that result in an imperfect perception of the true value being measured.
+This is accomplished by (_i_) specifying a set of process equations that represent expected population responses to intrinsic (e.g., density affects survival) and extrinsic (e.g., quantity of available habitat affects capacity) drivers, (_ii_) adding process noise to obtain the "realized" or "latent" (i.e., true but partially or imperfectly observed) state, and (_iii_) assuming the data values have been observed conditioned on the latent values.
+The model does not attempt to estimate the magnitude of both process and observation noise variance; it is supplied estimates of the latter and attributes the remaining noise unexplained by process equations to process noise.
+This aspect critical because only variability due to the processes is of interest for parameterizing simulation models of future population dynamics, yet the data sets vary in their precision.
+Further, the state-space model is inherently a time series model, making it suitable for handling the time lags and linkages involved with modeling age-structured populations.
+
+Bayesian methods were used to fit the state-space life cycle model to data, as it is intuitive for the necessary integration over the many layers of uncertainty (i.e., process vs.
+observational variability).
+Further, Bayesian inference provides an intuitive framework to constrain parameters to take on only values known _a priori_ to be plausible -- mostly uninformative priors were intentionally used but several cases involved priors that were moderately or strongly informative.
+An additional benefit of using the Bayesian framework is the seamless propagation of uncertainty from estimated parameters to derived quantities -- all unknown quantities receive a posterior distribution.
+Markov Chain Monte Carlo methods [MCMC, implemented via the JAGS v4.3.1 probabilistic programming language, @plummer-2003] were used to sample from the joint posterior distribution.
+
+`r if (is_latex_output()) "\\newpage"`
 
@@
 
-We have striven for consistency in our mathematical representation of quantities in the model but this has created somewhat non-intuitive conventions which require devoted explanation.
-All quantities are defined (i.e., symbology and the specific equations that use them) in Tables \@ref(tab:index-table), \@ref(tab:symbol-table), \@ref(tab:param-table), and \@ref(tab:data-table) for reference and a catalog of all equations is provided in Table \@ref(tab:equation-table).
-
-* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn including age-3 "jacks".
-* Life stage-specific states are defined by capital letters, e.g., parr ($P$), smolt ($M$), or spawners ($S$)
-* Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are denoted by Greek symbols, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
-* Subscripts denote the index of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population (see Table \@ref(tab:index-table)).
-* We use the convention $b$ to indicate "before event" and $a$ to indicate "after event" for a quantity that occurs at the same life stage.
+The state-space life cycle model symbology aims for consistency in mathematical representation of quantities but this has created some conventions that require devoted explanation.
+All quantities are defined in Tables \@ref(tab:index-table), \@ref(tab:symbol-table), \@ref(tab:param-table), and \@ref(tab:data-table) and a catalog of all equations is provided in Table \@ref(tab:equation-table).
+
+* For simplicity, the term "adult" is used to refer to any mature individual returning to spawn, including age-3 "jacks".
+* Life stage-specific states are defined by capital letters, these include: eggs ($E$), parr ($P$), smolt ($M$), ocean juveniles ($O$), adults returning to river ($R$), or adults with potential to spawn ($S$).
+* Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are predominately denoted by Greek symbols and are used consistently where possible, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
+* Subscripts denote placement of a quantity in a larger array (i.e., the index), e.g., $y$ denotes a specific year and $j$ a specific population (see Table \@ref(tab:index-table)).
+* Superscripts are most often used syntactically to further describe the quantity, not in a mathematical sense.
 E.g., $M^{b}$ represents smolt abundance _before_ out-of-basin migration and $M^{a}$ represents smolt abundance _after_ out-of-basin migration.
-As such, superscripts are most often used syntactically, not mathematically.
-E.g., $M^{b}$ is not "$M$ raised to the power $b$"; if we must raise the quantity $M^{b}$ to the power $c$, it will be written $(M^{b})^c$.
+As such, $M^{b}$ is not "$M$ raised to the power $b$"; if the quantity $M^{b}$ must be raised to the power $c$, it will be written $(M^{b})^c$.
 * Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \to B}_{y,j}$.
-* We denote the expected value of a stochastic process with a dot, e.g., $\dot{\phi}^{A \to B}_j$ -- this is the value expected in the absence of process variability.
-* In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array).
+* The expected value of a stochastic process is expressed by a dot, e.g., $\dot{\phi}^{A \to B}_j$ -- this is the value expected in the absence of process (biological/environmental) variability.
+* In some cases, calculations are performed on vectors rather than scalars.
 Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax.
-E.g., $\boldsymbol{\phi}^{A \to B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for each population.
+E.g., $\boldsymbol{\phi}^{A \to B}_{y,1:n_j}$ represents a vector of parameters representing the transition (survival) probability from state $A$ to state $B$ in year $y$, where each element stores the value for each population.
 * Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.
@@
 * $\logit\left(p\right)$ represents the log odds of $p$ (i.e., $\log\left[p/(1-p)\right])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
-* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \to B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \to B}_{y,j}}$, which we use as a direct estimate of observation error variability).
-* Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (or mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution; generally $\theta_{1}$ is a location parameter specifying the expected value of $x_{y}$ and $\theta_{2}$ is a dispersion parameter specifying the variability of $x_{y}$ around the expected value.
-
-Process noise is introduced by assuming year-specific values are multivariate logit-normal random variables around the deterministic value.
-This is done to enable modeling covariability in process noise among populations (or origins, in the few cases where population structure is not modeled).
-The covariance matrix of these random variables are denoted by $\Sigma$, and have a common structure for all model components.
+* All quantities are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \to B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \to B}_{y,j}}$, which is used as a direct estimate of observation error variability).
+* Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution.
+
+Process noise is modeled by assuming year-specific values are multivariate logit-normal random variables around the deterministic value.
+This enables modeling covariability in demographic rates [@riecke-etal-2019; @bouchard-etal-2022] among populations or origins, which is advantageous for estimation involving incompletely overlapping time series and quantifies synchrony in demographic rates which influences the stability of the return aggregated across populations [@thorson-etal-2014; @connors-etal-2022].
+The covariance matrices of these random variables are denoted by $\Sigma$, and have a common structure for all model components.
 Take the hypothetical survival term $\phi^{A \to B}_{y,j}$ as an example.
-We denote its random variability across years and populations as:
+The random process introducing inter-annual variability and inter-population covariability is expressed as:
 
@@
 
-In cases where a quantity varies annually and is different by origin but not by population, $\Sigma$ would have dimensions $n_o \times n_o$:
+In cases where a quantity varies annually and covaries by origin but is identical across populations, $\Sigma_{\phi^{A \to B}}$ would have dimensions $n_o \times n_o$:
 
@@
 
-We estimated these covariance matrices by assigning their inverse ($\Sigma^{-1}$) a scaled Wishart prior distribution (Table \@ref(tab:param-table)).
-Although the stochastic process requires the $\Sigma$ term, it is the component $\sigma$ and $\rho$ terms that we were interested in for inference.
+These covariance matrices were estimated by assigning their inverse ($\Sigma^{-1}$) a scaled Wishart prior distribution [@gelman-etal-2014; @plummer-2017, Table \@ref(tab:param-table)].
+Although the stochastic process requires the $\Sigma$ term, it is the component $\sigma$ and $\rho$ terms that were of interest for inference.
 
@@
 
-We begin our description of the life cycle at the egg stage immediately after spawning.
-We assumed total egg production was the sum product of age-specific spawner abundance (from eq. \@ref(eq:get-Sa), below), proportion female, and fecundity:
+The life cycle begins at the egg stage immediately after spawning.
+Total egg production was the sum product of age-specific spawner abundance ($S^{a}_{y,k,o,j}$, from eq.
+\@ref(eq:get-Sa), below), proportion female-at-age ($\Omega_k$), and fecundity-at-age ($f_{y,k,j}$):
 
@@
 
-We assumed that spawners age-4 or age-5 were 50% female and age-3 spawners were all male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data) and estimated fecundity ($f_{y,k,j}$) from length-fecundity relationships based on Grande Ronde-origin hatchery broodstock.
-We supplied both quantities to the model assuming no error or inter-annual variability.
-
-We assumed expected egg-to-parr survival was density-dependent following a Beverton-Holt relationship with productivity parameter $\alpha_j$ and capacity parameter $\beta_j$:
+Spawners of age-4 or age-5 were assumed to be 50% female and age-3 spawners were assumed 100% male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data).
+Fecundity was predicted from length-fecundity relationships based on Grande Ronde-origin hatchery broodstock and time-varying mean length-at-age data.
+Both $\Omega_k$ and $f_{y,k,j}$ were assumed known without error.
+
+Expected egg-to-parr survival was assumed to be a density-dependent process following Beverton-Holt dynamics with "productivity" parameter $\alpha_j$ (i.e., theoretical maximum egg-to-parr survival probability, in the absence of density effects) and capacity parameter $\beta_j$ (i.e., theoretical maximum parr recruitment abundance):
 
@@
 
-To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, we modeled parr capacity as a function of weighted usable habitat length ($\WUL_j$)^[Derivation of $\WUL_j$ is too detailed to describe fully here.
+To facilitate later analyses (not documented here) investigating the effects of habitat restoration and climate change on population dynamics, parr capacity was modeled as a function of weighted usable habitat length specific to each population ($\WUL_j$)^[Derivation of $\WUL_j$ is too detailed to describe fully here.
 Briefly, the relative ability of stream segments with different habitat characteristics to hold rearing parr was expressed in terms of the density of fish predicted to reside there by a complex generalized linear mixed model.
 The model was fitted to density estimates based on detectability-adjusted [@staton-etal-2022] summer snorkel counts with local habitat characteristics (e.g., pool frequency, water temperature, large wood density, etc.) as predictor variables.
-The weight of each stream segment was assigned based on the predicted density relative value to the segment with the highest value; $\WUL_j$ was then equal to the sum of segment-specific weight and length within the known spawning and rearing extent for each population.].
-We modeled parr recruitment capacity ($\beta_j$) as a function of this $\WUL_j$ metric:
+The weight of each stream segment was assigned based on the predicted density relative value to the segment with the highest value; $\WUL_j$ was then equal to the sum of segment-specific weight and length within the known spawning and rearing extent for each population.]:
 
@@
 
-We modeled realized (i.e., with process noise) egg-to-parr survival as a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \to P^{b}}_{y,j}$) from eq.
+Realized (i.e., with process noise) egg-to-parr survival was a multivariate logit-normal random variable around the expected value ($\dot{\phi}^{E \to P^{b}}_{y,j}$) from eq.
 \@ref(eq:get-phi-E-Pb-dot).
-Rather than assume that inter-annual variability in egg-to-parr survival beyond that explained by density-dependence is completely random across years, we allowed the model to account for serial autocorrelation in egg survival anomalies via a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \to P^{b}}_{j}$], wherein the white noise portion of the anomaly has covariance matrix $\Sigma_{\phi^{E \to P^{b}}}$:
+Rather than assume egg-to-parr survival anomalies (i.e., inter-annual variability in egg-to-parr survival beyond that explained by density-dependence) are completely random across years, a lag-1 autoregressive process [AR(1); coefficient denoted $\kappa^{E \to P^{b}}_{j}$] was used to account for serial autocorrelation:
 
@@
 
-Parr recruitment ($P^{b}_{y,j}$) to the end of summer was then the product of total egg production and egg-to-parr survival:
+Thus, the covariance matrix $\Sigma_{\phi^{E \to P^{b}}}$ captures variability in the white noise (i.e., non-correlated) portion of the survival anomaly.
+Total parr recruitment ($P^{b}_{y,j}$) was then the product of total egg production and egg-to-parr survival:
 
@@
 
-In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
-It is well known that juvenile survival is related to body size \todo{Insert references about survival being related to size} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
-We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a power function of egg density, which expressed on the logarithmic scale was:
+In addition to density-dependent egg-to-parr survival (eq.
+\@ref(eq:get-phi-E-Pb-dot)), there was reason to expect that parr growth/size is density-dependent, both from the literature on salmonid early life history [@grant-imre-2005; @copeland-venditti-2009; @walters-etal-2013; @myrvold-kennedy-2015; @grossman-simon-2020] and previous analyses on Grande Ronde Spring Chinook salmon populations [@cooney-etal-2017; @justice-etal-2023].
+Given the established relationships between size and survival  [@zabel-achord-2004; @hostetter-etal-2015], growth and density [e.g., @grant-imre-2005], and survival and density [@achord-etal-2003; @walters-etal-2013], it is possible that growth could be a useful mechanism to model density effects on post-recruitment juvenile survival.
+Expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) was modeled as a power function of egg density, which expressed on the logarithmic scale was:
 
@@
 
-Like many populations of stream-type spring Chinook salmon in the Columbia River basin \todo{Insert references about other CRB populations displaying the fall/spring migratory strategy}, there is life history diversity among the juveniles with respect to their migratory phenology and habitat types occupied for rearing overwinter.
-Some portion of the summer parr ($P^{b}_{y,j}$)  migrate out of the headwaters near where they were spawned in the fall and rear farther downstream (termed "fall migrants" and indexed by $i = \fall$) and the remaining portion migrate out the following spring (termed "spring migrants" and indexed by $i = \spring$).
-Due to this difference in migratory phenology, these two groups of fish are monitored separately \todo{Insert a reference to a recent ODFW screw trap monitoring report where it is stated (or implied) that migratory strategies are monitored separately.} depending on when they pass the rotary screw trap located in each tributary\todo{Create a map and include reference it here}.
-To enable building an observation model that could accommodate this feature of the populations in our model, we apportioned summer parr to each of these two strategies:
+Like many populations of stream-type spring Chinook salmon in the Columbia River basin, those in the Grande Ronde display life history diversity with respect to juvenile migratory phenology and overwinter rearing habitat use [copeland-etal-2014].
+Some portion of parr recruits ($P^{b}_{y,j}$)  migrate from the headwaters rearing areas in the fall and rear overwinter farther downstream (termed "fall migrants" and indexed by $i = \fall$) and the remaining portion migrate the following spring during the out-of-basin migration (termed "spring migrants" and indexed by $i = \spring$).
+Due to this difference in migratory phenology, these two groups of fish are monitored separately (`r highlight("REPORT CITATION NEEDED")`) depending on when they pass the rotary screw trap located in each tributary (`r highlight("FIGURE REFERENCE: map")`).
+Separate abundance and survival data in the observation model required that the process model track fish using these strategies separately, thus they were apportioned:
 
@@
 where $P^{a}_{y,i,j}$ is migratory strategy-specific parr abundance and $\pi_{y,i,j}$ is the proportion that take on each migratory strategy.
-We assumed the expected value of this proportion for fall migrants ($\dot{\pi}_{i = \fall,j}$) was time-constant and modeled the realized values as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \fall}}$:
+The expected value of the proportion of fall migrants ($\dot{\pi}_{i = \fall,j}$) was assumed to be time-constant and the realized values were modeled as having a multivariate logit-normal distribution with covariance matrix $\Sigma_{\pi_{i = \fall}}$:
 
@@
 
-Since there are only two migratory strategies, we obtained the proportion that are spring migrants as the complement ($\pi_{y,i = \spring,j} = 1 - \pi_{y,i = \fall,j}$).
+With only two migratory strategies, the proportion that were spring migrants was obtained as the complement: $\pi_{y,i = \spring,j} = 1 - \pi_{y,i = \fall,j}$.
 
@@
 
-We modeled expected survival from the parr (age-1) to in-basin smolt (age-2) stage (termed "overwinter" survival and denoted by $\dot{\phi}^{P^{a} \to M^{b}}_{y,i,j}$) as a logit-linear function of parr mean length:
+The model assumed that some inter-annual variability in overwinter survival (i.e., the transition from age-1 parr to age-2 smolt prior to out-migration) can be explained by parr mean length^[The assumption that parr length is related to overwinter survival can be relaxed by forcing $\gamma_{1,j}$ in eq.
+\@ref(eq:get-phi-Pa-Mb-dot) to zero rather than assigning it an uninformative prior distribution; in this case overwinter survival would be assumed to fluctuate around a time-constant expected value.].
+This was achieved by modeling expected overwinter survival (denoted by $\dot{\phi}^{P^{a} \to M^{b}}_{y,i,j}$) as a logit-linear function of parr mean length:
 
@@
 
-where $L^{*P^{b}}_{y,j}$ is parr mean length scaled and centered by subtracting the historical average observed parr mean length for population $j$ from $L^{P^{b}}_{y,j}$ and dividing by the historical observed standard deviation in mean length across years.
-Then, for each migratory strategy separately, overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \to M^{b}}}$ (assumed common among migratory strategies):
+where $L^{*P^{b}}_{y,j}$ is parr mean length centered and scaled based on the mean and standard deviation of observed mean lengths (denoted $\hat{L}^{P^{b}}_{y,j}$) across years for population $j$, respectively.
+Thus, $\gamma_{0,i,j}$ represents the expected log-odds of survival for type $i$ in population $j$ in a year with average parr mean length, and $\gamma_{1,j}$ represents the expected change in the log-odds for every additional standard deviation increase in parr mean length.
+Then, for each migratory strategy separately, realized overwinter survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{P^{a} \to M^{b}}}$ (assumed common among migratory strategies):
 
@@
 
-Since hatchery-origin smolts are released into the population in spring (see Section \@ref(hatchery-inputs)), we introduce the origin index ($o$) starting at the in-basin smolt stage prior to out-migration ($M^{b}_{y,i,o,j}$).
-The abundance of natural-origin (indexed by $o=\NOR$) smolt was then:
+The abundance of natural origin smolt (indexed by $o=\NOR$, hatchery-origin smolt releases described in Section \@ref(hatchery-inputs)) before out-migration was then:
 
@@
 
-We further wished to use the mean length of these surviving smolt ($L^{M^{b}}_{y,j}$) to later explain variability in survival along the migration out-of-basin.
-Because only spring migrants are measured for smolt mean length in the spring (as they pass the screw trap), we were forced to assume equal lengths for fall migrant smolt and we thus omit the $i$ subscript from these quantities related to smolt mean length.
-Preliminary analyses on the observed mean length data revealed that smolt mean length was positively related with parr mean length, but that the relationship was non-linear.
-To capture this non-linearity, we modeled the expected multiplicative change in mean length between the parr and smolt stage as a log-linear function of (standardized) parr mean length:
+Similar to the use of parr mean length to explain inter-annual variability in overwinter survival, smolt mean length ($L^{M^{b}}_{y,j}$) may be useful for explaining inter-annual variability in out-migration survival.
+Only spring migrant smolt have been measured for mean length (as they pass the screw trap), thus the $i$ subscript is omitted from quantities related to smolt mean length.
+Preliminary analyses revealed that smolt mean length was positively related to parr mean length, but that the relationship was non-linear.
+
+Preliminary analyses on the observed mean length data revealed that smolt mean length was positively related with parr mean length, but that the relationship was non-linear [@justice-etal-2023].
+This non-linearity was captured by modeling the expected multiplicative change in mean length from the parr to smolt stages as a log-linear function of (scaled and centered) parr mean length:
 
@@
 
-and obtained the realized multiplicative change in mean length as being multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \to L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \to L^{M^{b}}}}$:
+The realized multiplicative change in mean length was multivariate log-normally distributed around $\dot{\Delta}^{L^{P^{b}} \to L^{M^{b}}}_{y,j}$ with covariance matrix $\Sigma_{\Delta^{L^{P^{b}} \to L^{M^{b}}}}$:
 
@@
 
-For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error \todo{Insert reference to a document that gives info about these smolt releases}) were stored in the variable $M^{b}_{y,i=\spring,o=\HOR,j}$; we assumed no hatchery-origin parr were released the prior year, thus $M^{b}_{y,i=\fall,o=\HOR,j} = 0$.
-For all subsequent life stages, we tracked the abundance (and often survival) of hatchery-origin fish separately from natural-origin fish.
+For populations with hatchery supplementation (CAT, LOS, and UGR), hatchery-origin smolt releases (assumed known without error; `r highlight("REPORT CITATION NEEDED")`) were stored in the variable $M^{b}_{y,i=\spring,o=\HOR,j}$; the very rare occasions in which hatchery-origin parr were released the prior year were ignored, thus $M^{b}_{y,i=\fall,o=\HOR,j} = 0$ for all $y$ and $j$.
+Abundance (and often survival) of hatchery-origin fish was tracked separately from natural-origin fish for all subsequent life stages.
 
@@
 
-All in-basin smolt ($M^{b}_{y,i,o,j}$) migrate to the ocean in the spring of the year they become age-2 regardless of their migratory strategy ($i$).
-We divide mortality experienced during this migration into two stages: (_i_) from in-basin to Lower Granite Dam (LGR), the first in a series of eight dams\todo{Insert reference to a document describing dams} encountered in the downstream migration, and (_ii_) from LGR to the ocean.
-For parameter identifiability in mortality stage (_i_), we were required to assume that survival from in-basin to LGR was identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \to M^{a}}_{y,i=\fall,o=\NOR,j} = \phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}$, we thus omit the $i$ dimension when defining these quantities below), but we were able to model natural-origin survival separately from hatchery-origin because they are monitored separately (see Section \@ref(survival-data-sources)).
-
-We modeled expected out-of-basin migration survival for natural-origin smolt as a logit-linear function of smolt mean length:
+The model separates mortality sources experienced during seaward migration into two stages: (_i_) from the natal tributary to Lower Granite Dam (LGR), the first in a series of eight hydroelectric dams encountered during the downstream migration through the Snake and Columbia rivers, and (_ii_) from LGR to the ocean.
+Mortality source (_i_) was not identifiable when separated by migratory strategy, thus it was assumed identical between natural-origin fall and spring migrants (i.e., $\phi^{M^{b} \to M^{a}}_{y,i=\fall,o=\NOR,j} = \phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}$ for all $j$ and $y$); the $i$ dimension is thus omitted when defining these quantities below.
+Both mortality sources were separable by origin type (see Section \@ref(survival-data-sources))
+
+Expected out-of-basin migration survival for natural-origin smolt was a logit-linear function of smolt mean length:
 
@@
 
-where $L^{*M^{b}}_{y,j}$ has been scaled and centered by subtracting the historical average observed smolt mean length for population $j$ from $L^{M^{b}}_{y,j}$ and dividing by the historical observed standard deviation (just as for $L^{*P^{b}}_{y,j}$ for standardized parr mean length).
-For hatchery-origin smolt, we assumed this expected out-of-basin survival term was time-constant (i.e., all $\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\HOR,j}$ were equal within a population).
-For each origin separately, we modeled realized out-of-basin migration survival as a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \to M^{a}}}$ (assumed common across origin types):
+where $L^{*M^{b}}_{y,j}$ has been centered and scaled on the measured smolt mean length values ($\hat{L}^{M^{b}}_{y,j}$), just as for $L^{*P^{b}}_{y,j}$ in eqs.
+\@ref(eq:get-phi-Pa-Mb-dot) and \@ref(eq:get-Delta-L-Pb-L-Mb-dot).
+For hatchery-origin smolt, expected out-of-basin survival was assumed to be time-constant (i.e., all $\dot{\phi}^{M^{b} \to M^{a}}_{y,o=\HOR,j}$ were equal within a population).
+For each origin separately, realized out-of-basin migration survival was a multivariate logit-normal random variable around the expected value with covariance matrix $\Sigma_{\phi^{M^{b} \to M^{a}}}$ (assumed common across origin types):
 
@@
 
-We modeled survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \to O^{0}}_{y,o}$).
-We assumed these survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \to O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \to O^{0}}}$:
+Survival during the downstream migration through the hydrosystem on the Snake and Columbia rivers was modeled as a single survival rate, specific to each year and origin but shared among populations ($\phi^{M^{a} \to O^{0}}_{y,o}$).
+Realized survival rates were multivariate logit-normal random variables around a time-constant expected value ($\dot{\phi}^{M^{a} \to O^{0}}_{o}$) with covariance matrix $\Sigma_{\phi^{M^{a} \to O^{0}}}$:
 
@@
 
-Note the summation across migratory strategies ($i$) in eq.
-\@ref(eq:get-O0), which indicates that the fates of fish with these different strategies were assumed to be the result of identical processes following arrival to LGR.
+The summation across migration strategies ($i$) in eq.
+\@ref(eq:get-O0) indicates that the fates of fish with differing migratory strategies were not tracked separately after the $M^{a}_{y,i,o,j}$ stage.
 
@@
 
-The observation model components for the freshwater juvenile life stage were fitted to three primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary, \todo{Include reference to document describing methods of juvenile passage estimation}) in either the fall or spring, (_ii_) survival of juveniles from several PIT tagging events to LGR \todo{Include reference to document describing methods of juvenile survival estimation based on PIT tags}, and (_iii_) the mean length of sampled individuals during two of the PIT tagging events \todo{Include reference to document describing methods of juvenile mean length estimation}.
+The observation model components for the freshwater juvenile life stage were fitted to three primary data types: (_i_) abundance of juveniles passing rotary smolt traps (located in each tributary, `r highlight("REPORT CITATION NEEDED")`) in either the fall or spring, (_ii_) survival of juveniles from several PIT-tagging events to LGR (`r highlight("REPORT CITATION NEEDED")`), and (_iii_) the mean length of sampled individuals during two of the PIT-tagging events (`r highlight("REPORT CITATION NEEDED")`).
 For all types, the information supplied to the model were externally compiled estimates (e.g., survival from Cormack-Jolly-Seber models) and the estimated standard error was supplied to the model as a measure of observation error variability.
-A more fully integrated model would involve constructing the likelihood based on the frequency of PIT tag detection histories, however we thought unnecessary given the pre-compiled nature of currently available estimates and their uncertainty  \todo{Consider citing Staton et al.
-(2017) integrated vs.
-sequential SSSRA paper here}.
+
+An even more fully integrated model would involve constructing the join likelihood based on the frequency of PIT-tag detection histories.
+This was deemed unnecessary given (_a_) external estimates have been pre-compiled as well as their estimates of uncertainty (thus the model is consistent with published/established estimates), (_b_) much additional observational model complexity would be needed (e.g., detection probabilities), and (_c_) it would be unlikely to lead to greater parameter identifiability in the process model (e.g., allowing $\phi^{M^{b} \to M^{a}}_{y,i=\fall,o=\NOR,j} \ne \phi^{M^{b} \to M^{a}}_{y,i=\spring,o=\NOR,j}$).
+The practice of performing estimation based on raw data versus pre-compiled estimates that are treated as data is recommended to be avoided, especially if the uncertainty in pre-compiled estimates cannot be acknowledged [@brooks-deroba-2015].
+However, @staton-etal-2017a investigated this topic in the context of state-space (adult-to-adult age-structured spawner-recruit) models and found little difference in inferences between models that were integrated to varying degrees with respect to the extent of data pre-compilation, so long as uncertainty from the compilation step is accounted for.
 
@@
 Fish with the fall migratory strategy pass the screw trap in the fall as parr and fish with the spring migratory strategy pass the screw trap the following spring as smolt.
-The estimated passage during these time periods were used in log-normal likelihoods by assuming:
+The estimated passage abundances during these time periods were used in log-normal likelihoods by assuming:
 
@@
 
-Natural-origin juveniles have been PIT-tagged during four separate events in most years and populations: (_i_) at the end of summer prior to migratory strategy apportionment, (_ii_) as fall migrant parr pass the screw trap in the fall, (_iii_) at the start of winter in the headwaters (after fall migrants leave, so applies only to spring migrants; also not available for Minam River), and (_iv_) as spring migrant smolt pass the screw trap.
-Hatchery-origin smolt released in the spring have also been PIT-tagged.
+Natural-origin juveniles have been PIT-tagged during four separate events in most years and populations: (_i_) in summer prior to migratory strategy divergence, (_ii_) as fall migrant parr that pass the screw trap in the fall, (_iii_) in winter in the headwaters (after fall migrants leave, thus applies only to spring migrants; also not available for Minam River), and (_iv_) as spring migrant smolt pass the screw trap.
+Hatchery-origin smolt released in the spring were also PIT-tagged prior to release.
 All five of these tag groups have their survival estimated from the time of tagging to their arrival at LGR.
-These estimates (and their associated standard errors) were used in logit-normal likelihoods by assuming:
+These estimates (and their associated standard errors) were used in logit-normal likelihoods by assuming the following for each tag group.
+
+Summer tag group:
 
@@
 
-for the summer tagging group,
+Fall tag group:
 
@@
 
-for the fall tagging group,
+Winter tag group:
 
@@
 
-for the winter tagging group (where $\phi^{P^{b} \to P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\CAT, \LOS, \UGR]$),
+(where $\phi^{P^{b} \to P^{a}}_j$ is a time-constant model-estimated survival from summer tagging to winter tagging for parr that ultimately become spring migrants and $j \in [\CAT, \LOS, \UGR]$).
+
+Spring tag group:
 
@@
 
-for the spring tagging group, and
+Hatchery smolt tag group:
 
@@
 
-Much quantitative research has been devoted to studying the survival of Chinook salmon smolt migrating through the hydrosystem located on the Snake and Columbia rivers and we thought it best to utilize the findings from some of this research as input data to our modeling effort rather than attempt to have our model freely estimate survival along this migration.
-Using external estimates of survival here so would give us the flexibility to more freely estimate quantities which have received less directed research, namely ocean survival.
-We used the output from a recent Comparative Survival Study report [@mccann-etal-2020, Table A.1 on page A-20 therein] to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
+Much research has been devoted to studying the survival of Chinook salmon smolts migrating through the hydrosystem on the Snake and Columbia rivers. 
+In particular, the Comparative Survival Study has tracked the survival of a variety of tagging groups going back to the early 2000s; estimates from a recent report [@mccann-etal-2020, Table A.1 on page A-20 therein] were used to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
 Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\NOR}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\HOR}$ here).
-We treated these estimates as representative of the survival for each population, which implies an assumption that the different populations we model experience similar conditions during this migration and ignores any effect of barge-transporting fish.
-Similar to the other survival data sets, we assumed these estimates are made with logit-normal random error around the life cycle model estimate to build the likelihood:
+These estimates were treated as representative of the survival for each population, which implies an assumption that the different populations experienced similar conditions during this migration and attributes all variability to either random process or observation noise (i.e., no factors known to influence hydrosystem survival such as size, flood pulses, barging intensity were included).
+Similar to the other survival data sets, these estimates were assumed to have been made with logit-normal random error around the process model values to build the likelihood:
 
@@
 
-Upon capture for PIT tagging, individual fish lengths are measured.
-We calculated the mean length (and the associated standard errors) of all captured fish (tagged and untagged; only fish $\ge$ 55mm can receive a PIT tag) and used them in log-normal likelihoods by assuming:
+Individual fish lengths have been measured upon capture for PIT-tagging (`r highlight("REPORT CITATION NEEDED")`).
+The mean length (and the associated standard errors) of all captured fish (tagged and untagged; only fish $\ge$ 55mm can receive a PIT-tag) was used in log-normal likelihoods by assuming:
 
@@
 for mean length data for the smolt tagging group.
-Because the each population has approximately 1,000 fish tagged and measured during each tagging event, the standard errors on the mean length estimates were quite small.
+Because the each population had approximately 1,000 fish tagged and measured during each tagging event, the standard errors on the mean length estimates were quite small.
+
+Preliminary analyses revealed that parr mean length estimates had inter-annual variability attributable to the median sample date (capture method is active), so a standardization was devised and applied prior to model fitting [@justice-etal-2023, Figure 26 therein].
+All uses of $\hat{L}^{P^{b}}_{y,j}$ in this document refer to the standardized version.
+Although timing has varied for smolt mean length estimates ($\hat{L}^{M^{b}}_{y,j}$), it was caused by migratory timing not sample timing, thus should treated as process noise.
 
@@
 Spring Chinook salmon in the Grande Ronde basin migrate to sea as age-2 smolt and can return as either age-3, age-4, or age-5 adults.
-That is, ocean juveniles spend between 1 and 3 winters at sea and some fraction will make the return migration after each winter and before the following winter at sea.
-Thus, we divided ocean population dynamics into two types of demographic rates and their process noise: survival and maturation.
-Due to the confounding of these parameters\todo{Insert a reference to a paper that describes this ocean survival/maturation rate confounding?}, we were unable to freely estimate all rates and were instead required to make some simplifying assumptions and use more informative priors than in other parts of the model.
+That is, ocean juveniles spend between 1 and 3 winters at sea and some fraction make the return migration after each winter.
+Thus, ocean dynamics were divided into two types of demographic rates: survival and maturation.
+Attempting to freely estimate all desired parameters (i.e., time varying year-1, year-2, and year-3 survival rates and maturation rates after year-1 and year-2) revealed that these parameters were confounded given the available data, requiring more simplifying assumptions and stronger prior information than in other parts of the model.
 
@@
 
-We assumed first year natural-origin^[All $o=\NOR$ in eq.
-\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \to O^{1}}_{o=\NOR,j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \to O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion\todo{Include reference to papers that talk about ocean survival varying cyclically; e.g., Mantua et al.
-paper on PDO}:
+Year-1 natural-origin^[All $o=\NOR$ in eq.
+\@ref(eq:phi-O0-O1-random), omitted for brevity.] ocean survival was modeled as a multivariate logit-normal random variable around a time-constant expected value ($\dot{\phi}^{O^{0} \to O^{1}}_{o=\NOR,j}$) with covariance matrix $\Sigma_{\phi^{O^{0} \to O^{1}}}$, but included a lag-1 autoregressive process as a means to account for ocean conditions that may affect survival in a temporally non-independent fashion [e.g., @mantua-etal-1997]:
 
@@
 
-We assumed process variation was negligible in the second and third year ocean survival terms, thus we forced the year-specific values of $\phi^{O^{1} \to O^{2}}_{y,o=\NOR,j}$ and $\phi^{O^{2} \to O^{3}}_{y,o=\NOR,j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$, respectively).
-Because not all maturity and ocean survival terms were uniquely identifiable based on adult return abundance and age composition, we relied on reasonably strong priors to inform $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$ (Table \@ref(tab:param-table)).
-\todo{Are we using priors or fixed values? Include reference to reports where we can reference the specific values used.}
-To obtain hatchery-origin ocean survival each year, we adjusted the natural-origin survival by a log-odds ratio ($\delta_{j}$) that was common across all ocean years and brood years but varied by population:
+The first simplifying assumption surrounding ocean survival rates was that process variation was negligible in year-2 and year-3, thus we forced the brood year-specific values of $\phi^{O^{1} \to O^{2}}_{y,o=\NOR,j}$ and $\phi^{O^{2} \to O^{3}}_{y,o=\NOR,j}$ to take on the same value for all years (i.e., $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$, respectively).
+Further, it was discovered that reasonably strong priors would be needed to inform $\dot{\phi}^{O^{1} \to O^{2}}_{o=\NOR,j}$ and $\dot{\phi}^{O^{2} \to O^{3}}_{o=\NOR,j}$ to allow identifiability of the maturity parameters (Table \@ref(tab:param-table)); priors were used for ocean survival rather than maturity parameters because commonly assumed values were available for the former [@ctc-1988].
+The second simplifying assumption was that natural- and hatchery-origin ocean survival rates were perfectly correlated across years within populations, but offset by a time-constant log-odds ratio ($\delta_{j}$):
 
@@
 
-This $\delta_j$ parameter allows hatchery- and natural-origin to have different survival for each ocean year, but assumes the origin effect is equal for all brood years and ocean ages within a population, implying an assumption that ocean survival among origins is perfectly correlated.
-
 ### Maturation Rates {#maturity}
 
-We treated realized maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) as multivariate logit-normal random variables around time-constant expected values ($\dot{\psi}^{O^{w}}_{o,j}$; $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}}$ (assumed common across origins):
+Realized maturation rates (i.e., the proportion of fish from a given brood year alive and in the ocean at the beginning of a year that make the return migration that year) were modeled as multivariate logit-normal random variables around time-constant expected values ($\dot{\psi}^{O^{w}}_{o,j}$; $w$ is the number of winters spent in the ocean) with covariance matrix $\Sigma_{\psi^{O^{w}}}$ (assumed common across origins):
 
@@
 
-Since we assumed age-5 to be the last age of maturity, all fish alive and in the ocean after the third year at sea must mature and return that year (i.e., all $\psi^{O^{3}}_{y,o,j} = 1$).
+Since age-5 was the last modeled age of maturity, all fish alive and in the ocean after the third year at sea mature and return that year (i.e., all $\psi^{O^{3}}_{y,o,j} = 1$).
 
@@
 
-Now that we have defined the sources of process noise in the ocean demographic rates, we can define the process equations that result in transitioning ocean juveniles through the various ocean ages and ultimately at the mouth of the Columbia River for the upstream migration.
-We modeled ocean population dynamics as a sequence of survival, maturation of surviving fish, and survival of non-maturing fish:
+Based on the sources of process variation modeled in eqs.
+\@ref(eq:phi-O0-O1-random), \@ref(eq:get-phi-O-HOR), and \@ref(eq:psi-random) and the initial abundance of ocean juveniles ($O^{0}_{y,o,j}$, eq.
+\@ref(eq:get-O0)), the abundance of ocean juveniles after a given number of winters ($w$, superscripts in all $O^{w}$ symbols) was modeled as a sequence of survival, maturation of surviving fish, and survival of non-maturing fish:
 
@@
 
-The abundances of ocean juveniles ($O^{1}_{y,o,j}$, $O^{2}_{y,o,j}$, and $O^{3}_{y,o,j}$) are organized by brood year, however they will return in different years to spawn (and be observed) because they are of different ages.
-We placed returning mature fish into the correct year and age of return to the mouth of the Columbia River before the upstream migration ($R^{b}_{y,k,o,j}$) based on the following rule.
-Fish spawned in year $y$ will return as the $k^{\mathrm{th}}$ possible age of maturity in year $y + A_{\mathrm{min}} + k - 1$ (age-3 is the first possible total age of maturity, thus $A_{\mathrm{min}}$ = 3).
+The abundances of ocean juveniles ($O^{1}_{y,o,j}$, $O^{2}_{y,o,j}$, and $O^{3}_{y,o,j}$) from a given cohort were organized by brood year, however they returned in different years and ages to spawn.
+Returning mature fish were placed into the correct year and age of return to the mouth of the Columbia River before the upstream migration ($R^{b}_{y,k,o,j}$) based on the following rule: members of the cohort spawned in brood year $y$ returned at the $k^{\mathrm{th}}$ possible age of maturity to produce the cohort for brood year $y + A_{\mathrm{min}} + k - 1$.
 As an example, fish spawned in brood year $y$ = 2000 will return in 2003 as age-3 ($k$ = 1), in 2004 as age-4 ($k$ = 2), or in 2005 as age-5 ($k$ = 3) -- see Table \@ref(tab:year-table) for a visual of this example.
@@
 
-Note, however, that this leaves 12 age/year combinations per origin unpopulated with returning adults (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns; see Table \@ref(tab:year-table)).
-This is because no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
-Thus, to initialize the adult returns for natural-origin fish (and as a result, the rest of the life cycle), we estimated these 12 year/age return abundances as unknown parameters with fairly restrictive priors (Table \@ref(tab:param-table)) with boundaries loosely informed by the ranges of adult returns at age observed in the early years of the data time series.
-Initial abundance of hatchery-origin returns was handled by the "straying model" (see Section \@ref(processes-between-bon-and-lgr), below).
+This, however, leaves 12 ($\sum_{k}^{n_k} A_{\mathrm{min}} + k - 1$) age/year combinations per origin unpopulated with returning adults (the first 3 missing years for age-3 returns, first 4 missing years for age-4 returns, and first 5 missing years for age-5 returns; see Table \@ref(tab:year-table)).
+This occurs because no juvenile process model outcomes existed that would ultimately become these $R^{b}_{y,k,o,j}$ values in these early years.
+Thus, to initialize the adult returns for natural-origin fish, these 12 year/age return abundances were estimated as unknown parameters with fairly restrictive priors (Table \@ref(tab:param-table)) with boundaries loosely informed by the ranges of adult returns-at-age observed in the early years of the data time series.
+Initial abundances of age-specific hatchery-origin returns were handled by the "straying model" (see Section \@ref(processes-between-bon-and-lgr), below).
 
@@
 
-We attempted to partition several sources of mortality that occur between the upstream migration from the mouth of the Columbia River to the point of spawning in natal tributaries in Grande Ronde basin.
+There are a variety of mortality sources that occur along the upstream migration from the mouth of the Columbia River to the point of spawning in natal tributaries in Grande Ronde basin.
 For ease of presentation, we separate these processes into three categories depending on where they occur spatiotemporally: (_i_) downstream of Bonneville Dam (BON) at the beginning of the upstream migration, (_ii_) along the upstream migration in the mainstem Columbia and Snake rivers between BON and LGR, and (_iii_) after arrival to the natal tributaries and up until the point of spawning.
@@
 
-Prior to reaching BON, we subject returning adults to harvest mortality from fisheries (harvest rate denoted by $U_{y,k,o}$).\todo{Insert information about where harvest rate estimates came from.}
-We compiled the best available estimates but did not fit to them explicitly as part of the observation model (as we do with many other data sources) -- instead we passed them to the model as non-stochastic quantities that were assumed to be known without error (used in eq.
-\@ref(eq:get-Ra), below).
+Prior to reaching BON, returning adults are subjected to harvest mortality from fisheries (harvest rate denoted by $U_{y,k,o}$; `r highlight("REPORT CITATION NEEDED")`).
+These estimates were supplied to the model as known without error (i.e., non-stochastic; used in eq. \@ref(eq:get-Ra), below).
 
@@
 
-Once fish reach BON, however, their survival to LGR has been monitored (since 2000; $y=10$) via PIT tags and so we did fit to those data and estimate the survival rate between BON and LGR as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \to R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \to R^{a}}}$.
-In years without these PIT tag counts, however, the survival from BON to LGR is confounded with ocean survival, and so we assumed BON to LGR survival was equal to the expected value in these years for parameter identifiability purposes:
+Upon arrival to BON, survival to LGR has been monitored (since 2000; $y=10$) via PIT-tags with high (>0.95) detection probabilities, enabling estimation of survival along this portion of the migration.
+The survival rate between BON and LGR was assumed to vary by origin (but not by population) as multivariate logit-normal random variables around expected values ($\dot{\phi}^{R^{b} \to R^{a}}_{o}$) with covariance matrix $\Sigma_{\phi^{R^{b} \to R^{a}}}$.
+In years without these PIT-tag counts, however, the survival from BON to LGR was found to be confounded with ocean survival; this was resolved by using the expected value rather than estimating the value for these years:
 
@@
 
-Examination of the adult composition data indicated that hatchery-origin adults returned to Grande Ronde populations in years that could not be attributed to hatchery-origin smolt releases to these populations.
-Further, the Minam River population (which has no hatchery supplementation program) has had hatchery adults return in many of the years included in our model.
-Since there were non-zero observations of hatchery-origin adults in cases without a process model component to produce them, we required a process model mechanism to populate non-zero expected values for the observation model to remain valid based on the available data.
-We term this model component the "straying model", and applied it only in years/populations in which the presence of non-zero hatchery-origin returning adults could not otherwise be explained due to zero-valued hatchery-origin smolt releases.
-We denote the total number of strays that entered population $j$ in year $y$ as $G_{y,o,j}$; we forced all $G_{y,o=\NOR,j} = 0$ and forced all $G_{y,o=\HOR,j} = 0$ in years where non-zero hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
-We denote the age composition of these strays by $p^{G}_{k,j}$ (where $\sum_k^{n_k} p^{G}_{k,j} = 1$) and apportioned $G_{y,o,j}$ to age-specific values by $G_{y,k,o,j}=G_{y,o,j} \cdot p^{G}_{k,j}$.
-
-We can now define the abundance of adults arriving to their natal spawning tributaries by age and origin ($R^{a}_{y,k,o,j}$) as:
+Examination of the adult composition data indicated that hatchery-origin adults returned to Grande Ronde populations in early years that could not be attributed to hatchery-origin smolt releases to these populations.
+Further, the Minam River population (which has no hatchery supplementation program) has had hatchery adults found in carcass surveys in many of the years since monitoring began.
+Without a process model adjustment, the observation model would treat these unexpected non-zero hatchery-origin counts as impossible.
+This model component is referred to as the "straying model" (total abundance of entering strays denoted $G_{y,o,j}$), and it applied only in years/populations in which the presence of non-zero hatchery-origin returning adults could not otherwise be explained due to zero-valued hatchery-origin smolt releases.
+Thus, all $G_{y,o=\NOR,j} = 0$ and all $G_{y,o=\HOR,j} = 0$ in years where non-zero hatchery-origin smolt releases to population $j$ could have explained non-zero hatchery-origin adult returns in year $y$ at age $k$.
+The age composition of these strays was assumed to be time-constant ($p^{G}_{k,j}$; where $\sum_k^{n_k} p^{G}_{k,j} = 1$) and was used to apportion $G_{y,o,j}$.
+
+The abundance of adults arriving to natal spawning tributaries by age and origin ($R^{a}_{y,k,o,j}$) as:
 
@@
 Upon arrival to the natal tributary, populations with a weir and hatchery program (all populations except the Minam River, indexed by $j = \MIN$) have some number of adults removed each year for broodstock and as a means to minimize natural spawning of hatchery-origin fish.
-We supplied these weir removals (denoted by $B_{y,k,o,j}$) to the model as known without error and set all $B_{y,k,o,j=\MIN} = 0$.
-Similarly, fish are harvested in the natal tributaries prior to spawning, and we additionally supplied estimates of fish harvested ($H_{y,k,o,j}$).
-Thus, the abundance of adults that would have a chance to spawn each year was:
+These weir removals (denoted by $B_{y,k,o,j}$; all $B_{y,k,o,j=\MIN} = 0$) were supplied to the model as known without error, as were the number of fish estimated to have been in the natal tributaries prior to spawning.
+Thus, the abundance of potential spawners was:
 
@@
 The maximum constraint was used to ensure all $S^{b}_{y,k,o,j} > 0$.
-As a final step prior to spawning, these adults must survive the challenges of finding adequate spawning habitat and avoid succumbing to stress and mortality prior to spawning.
-We treated these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \to S^{a}}_{y,j}$, as having a time-constant value (i.e., all $\phi^{S^{b} \to S^{a}}_{y,j} = \dot{\phi}^{S^{b} \to S^{a}}_{j}$).
-We desired to allow for time-varying pre-spawn survival probabilities, but discovered that the observational data were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
-Thus, the abundance of successfully spawning individuals ($S^{a}_{y,k,o,j}$) was:
+
+It is well-known that some potential spawners die prior to spawning; these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \to S^{a}}_{y,j}$, were modeled as having time-constant values (i.e., all $\phi^{S^{b} \to S^{a}}_{y,j} = \dot{\phi}^{S^{b} \to S^{a}}_{j}$) for each population.
+The initial desire was to allow for time-varying pre-spawn survival probabilities, but it was discovered that the observational data (counts of spawned vs.
+gravid female carcasses, see eq.
+\@ref(eq:prespawn-surv-data)) were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
 
@@
 
-It is this $S^{a}_{y,k,o,j}$ value from which total egg production ($E_{y,j}$) is calculated in eq. \@ref(eq:get-E) to complete the life cycle.
+This $S^{a}_{y,k,o,j}$ value was used to calculate total egg production ($E_{y,j}$) in eq. \@ref(eq:get-E) to link the the spawner abundance to the parr recruitment abundance in the next generation.
 
@@
 
-The adult observation model relies on three primary data types: (_i_) total abundance of adult returns to the natal tributaries, (_ii_) information about survival on the upstream migration between LGR and BON as well as on the spawning grounds, and (_iii_) composition data to inform the relative abundance of adults of different ages and origins.
+The adult observation model relied on three primary data types: (_i_) total abundance of adult returns to the natal tributaries, (_ii_) information about survival on the upstream migration between LGR and BON as well as on the spawning grounds, and (_iii_) composition data to inform the relative abundance of adults of different ages and origins returning each year.
 
@@
 
-Total return abundance is estimated annually external to the model using a combination of weir counts, mark-recapture methods, and spawning ground surveys\todo{Insert reference about adult return monitoring methods}.
-For each population and year, these have been compiled into a point estimate ($\hat{R}^{a}_{y,j}$; note the lack of $o$ or $k$ indices -- this indicates the estimate is aggregated across these dimensions) and an estimate of observation uncertainty ($\hat{\sigma}_{R^{a}_{y,j}}$, expressed as a log-normal standard error).
-We assumed the point estimate is made with log-normal observation error around the model-predicted total returns to the tributary to build the likelihood for this component:
+Total tributary return abundance has been estimated annually external to the model using a combination of weir counts, mark-recapture methods, and spawning ground surveys (`r highlight("REPORT CITATION NEEDED")`).
+For each population and year, these have been compiled into a point estimate ($\hat{R}^{a}_{y,j}$; the lack of $o$ or $k$ indices indicates the estimate is aggregated across these dimensions) and an estimate of observation uncertainty ($\hat{\sigma}_{R^{a}_{y,j}}$, expressed as a log-normal standard error).
+The model assumed the point estimate is made with log-normal observation error around the model-predicted total returns to the tributary to build the likelihood for this component:
 
@@
 
-For the observation model component informing migration survival upstream from BON to LGR, we relied on counts of PIT tag detections of known Grande Ronde-origin fish passing BON ($\hat{x}^{\mathrm{BON}}_{y,o}$) and LGR ($\hat{x}^{\mathrm{LGR}}_{y,o}$)\todo{Insert reference to DART website where we obtained the BON to LGR PIT tag count data}.
-We assumed the latter was a binomial random variable to build the likelihood component for this data set:
+The model fitted to counts of PIT-tag detections of known Grande Ronde-origin fish passing BON ($\hat{x}^{\mathrm{BON}}_{y,o}$) and LGR ($\hat{x}^{\mathrm{LGR}}_{y,o}$) to inform the migratory survival rate between these two locations, queried using the DART Adult Return Conversion Rate tool^[https://www.cbr.washington.edu/dart/query/pitadult_conrate; exact query settings described at https://github.com/bstaton1/GR-sslcm/issues/93.].
+The latter was assumed to be a binomial random variable to build the likelihood component for this data set:
 
@@
 The other survival data set informing the freshwater adult observation model was for spawning success, i.e., pre-spawn survival.
-In annual spawning ground carcass surveys, surveyors record the counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$; \todo{Insert reference about carcass/spawning success data monitoring methods}).
-Only females are counted this way because it is too difficult to tell if a male has successfully spawned based on their gonads alone, thus we assumed that males and females experience the same pre-spawn survival.
-We assumed these counts were gathered using binomial sampling to build the likelihood:
+Surveyors in annual spawning ground carcass surveys have recorded counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$; `r highlight("REPORT CITATION NEEDED")`).
+These counts were treated as binomial random variables to build the likelihood:
 
@@
 
-Since the model is both age- and origin-structured, we required data to inform the relative abundance of adults returning according to these different classes.
-These took the form of two sources: (_i_) those collected at the weirs located within three of the four populations we model ($\hat{x}^{R^{a}}_{y,ko,j}$) and (_ii_) those collected during carcass surveys ($\hat{x}^{S^{a^{\prime}}}_{y,ko,j}$), given the Minam River population does not have a weir.
-We assumed the weir sampled fish representatively with respect to age and origin composition, however we discovered there was an age sampling bias for carcass surveys relative to the weir which required a correction factor (see eqs.
-\@ref(eq:z-random) -- \@ref(eq:get-pSa-prime), below).
-We fitted to these data assuming multinomial sampling in which there were $n_{ko} = 6$ possible outcomes: $n_k = 3$ ages of return by $n_o = 2$ origins.
-Further, we chose to use the observed sample size ($\sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}$) as the multinomial sample size rather than attempting to adjust it for non-independent sampling.
+Since the model is both age- and origin-structured, it required data to inform the relative abundance of adults returning according to these different classes.
+These data took the form of two sources: (_i_) those collected at weirs located within three of the four populations ($\hat{x}^{R^{a}}_{y,ko,j}$) and (_ii_) those collected during carcass surveys ($\hat{x}^{S^{a^{\prime}}}_{y,ko,j}$), given the Minam River population does not have a weir.
+The weir was assumed to have fish representatively with respect to age and origin composition and both data sources were fitted to by assuming multinomial sampling in which there were $n_{ko} = 6$ possible outcomes: $n_k = 3$ ages of return by $n_o = 2$ origins.
+Further,the observed sample size ($\sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}$) as the multinomial sample size rather than attempting to adjust it for non-independent sampling [@maunder-2011]; alternative sample size selections would likely be arbitrary, and past analyses have suggested that inferences are robust to rational alternatives [see Supplement A of @staton-etal-2021].
 The model-expected composition by age and origin ($p^{R^{a}}_{y,ko,j}$) was calculated from the return abundance by age and origin, reorganized such that age and origin fell along the same array dimension ($R^{a}_{y,ko,j}$) rather than along two dimensions as shown in the process model ($R^{a}_{y,k,o,j}$):
@@
 
-which we used as the multinomial expected frequency to build the likelihood:
+which was used as the multinomial expected frequency to build the likelihood:
 
@@
 
-Due to the age sampling bias of carcass surveys we discovered, we required a correction to ensure reliable fits to all data sets while still recovering unbiased true age composition data for the Minam River population, which had only carcass composition data (the other three populations had both weir and carcass composition data).
-For the three populations with paired composition data (i.e., $j \in [\CAT, \LOS, \UGR]$), we estimated correction factors in a hierarchical fashion:
+Preliminary analyses revealed an age sampling bias of carcass surveys relative to weir sampling, which required a correction to ensure reliable fits to all data sets while recovering unbiased true age composition data for the Minam River population, which had only carcass composition data.
+For the three populations with paired composition data (i.e., $j \in [\CAT, \LOS, \UGR]$), correction factors were estimated in a hierarchical fashion:
 
@@
 
-We used these correction factors to calculate the expected proportions by age and origin for carcass surveys ($p^{S^{a^{\prime}}}_{y,ko,j}$):
+These correction factors were used to calculate the expected proportions by age and origin for carcass surveys ($p^{S^{a^{\prime}}}_{y,ko,j}$):
 
@@
 
-which we used as the multinomial expected frequency to build the likelihood by assuming:
+which was used as the multinomial expected frequency to build the likelihood by assuming:
 
@@
   "5" = "Dirichlet Distribution: $\\\\mathcal{D}(\\\\mathrm{shape}_1$, $\\\\mathrm{shape}_2$, $\\\\mathrm{shape}_3)$",
-  "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see JAGS v4.3.0 user manual page 62 for details on this prior.
+  "6" = "Scaled Inverse-Wishart Distribution: $\\\\mathcal{SIW}$(\\\\textbf{S}, degrees of freedom); \\\\textbf{S} is a vector of scale parameters for scaled-Wishart; see \\\\cite{plummer-2017} page 62 for details on this prior.
 Briefly, the scale parameters of 0.10 - 0.30 places higher prior weight on small values of the component $\\\\sigma$ parameters, which was intentional because these represent variability on the log- or logit-scale.

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Initialize ms-content.Rmd

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

\rule{\textwidth}{1pt}

\vspace{-6pt}

::: {.Huge data-latex=""}
**Potential Manuscript Content**
:::

\vspace{-6pt}

::: {.Large data-latex=""}
**GR-sslcm**
:::

\vspace{-6pt}

\rule{\textwidth}{1pt}

\listoftables

\listoffigures

\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.pos = "H")
knitr::opts_knit$set(root.dir = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process")

# set up a chunk hook to calculate how long chunks took to run
# modified from https://bookdown.org/yihui/rmarkdown-cookbook/time-chunk.html#time-chunk

start_times = list()  # store the time for each chunk
end_times = list()  # store the time for each chunk
knitr::knit_hooks$set(time_it = local({
  function(before, options) {
    if (before) {
      start_times[[options$label]] <<- lubridate::now()
    } else {
      end_times[[options$label]] <<- lubridate::now()
    }
  }
}))
```

```{r load-post, time_it = TRUE}
source("C:/Users/bstaton/Desktop/source_rmd_chunk.R")
rmd_file = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process/output-plots.Rmd"
source_rmd_chunk(rmd_file, "setup")
source_rmd_chunk(rmd_file, "dimension-ids")
knitr::opts_chunk$set(out.width = "100%", dev = "cairo_pdf")
```

```{r load-packages}
source("../00-packages.R")
```

```{r plot-settings}
solid_col = "grey30"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3
```

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create capacity relationship figure

@@
 ```
+
+```{r captions}
+beta_caption = "
+  Estimated relationship between parr capacity and weighted usable habitat length.
+  Darker grey/thicker error bars represent 80% credible regions and lighter grey/thinner error bars represent 95% credible regions.
+"
+
+```
+
+```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE}
+# extract posterior summaries of the capacity parameters
+beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))
+
+# extract posterior samples of the slope parameter
+beta_per = post_subset(post, "lambda", TRUE)
+
+# create a sequence of WUL values to predict capacity at
+wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
+
+# obtain the regression line for each posterior sample
+pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
+
+# summarize posterior of regression line
+pred_beta_summ = apply(pred_beta, 2, function(x) c(mean = mean(x), quantile(x, c(0.025, 0.1, 0.5, 0.9, 0.975))))
+
+# empty plot with correct labeling/dimensions
+mypar(mfrow = c(1,1), col.axis = "black")
+plot(1,1, type = "n", xlim = range(wul_seq),
+     # ylim = c(0, max(beta_ests["97.5%",], pred_beta_summ["97.5%",])),
+     ylim = c(0, 3000) * 1000,
+     xlab = "",
+     ylab = "", yaxt = "n")
+
+# draw prettier y-axis
+at_y = c(0, 1000, 2000, 3000) * 1000
+axis(side = 2, at = at_y, labels = at_y/1000)
+usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+
+# draw the regression uncertainty
+polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["2.5%",], rev(pred_beta_summ["97.5%",])), border = NA, col = tranp_col)
+polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["10%",], rev(pred_beta_summ["90%",])), border = NA, col = tranp_col)
+
+# draw the posterior mean regression line
+lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)
+
+# draw the population-specific capacity estimates w/error bars and labels
+segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)
+
+# draw the population labels
+xoff = 0.015
+yoff = 0.03
+text(x = jags_data$wul      + xdiff * c(1.5,-1,1,1) * xoff,
+     y = beta_ests["mean",] + ydiff * c(1,-1,1,1) * yoff,
+     labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,2,2), font = 1, cex = 0.8)
+
+# add axis labels
+axis_labels("Weighted Usable Habitat Length (km)", "Parr Capacity (Thousands)")
+```

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create large relationships figure

@@
 
+relationship_caption = "
+  Estimated relationships showing density effects on recruitment (panels _a_ and _b_) and mean length (panel _c_), and length effects on future length (panel _d_) and survival (panels _e_ and _f_). 
+  Process model relationships are shown as the posterior mean (thick line) and 95% credible region (shaded); points show process model realizations (i.e., with process noise) by brood year.
+  Panels within the same row show the process model relationship for each of the four populations; _x_- and _y_-axis limits are identical for all panels within a row.
+"
+
 ```
@@
 ```
+
+\newpage
+
+```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE}
+solid_col = "grey30"
+tranp_col = alpha(solid_col, 0.25)
+pt_cex = 1.3
+
+##### EGG-TO-PARR SURVIVAL VS. EGG DENSITY #####
+
+phi_E_Pa_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of total egg production by brood year
+  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
+
+  # extract posterior summaries of egg to parr survival rates
+  phi_E_Pb = post_summ(post, sub_index("^phi_E_Pb[.+,pop]", pop = j))
+
+  # extract posterior samples of the BH parameters
+  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
+
+  # construct vector of egg abundances to predict at
+  E_pred = seq(0.1, max(E[1,]), length = 30)
+
+  # obtain predicted curves for each posterior sample
+  phi_E_Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) 1/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
+
+  # obtain posterior summary of predicted curve
+  colnames(phi_E_Pb_pred) = paste0("phi_E_Pb_pred[", 1:length(E_pred), "]")
+  phi_E_Pb_pred = post_convert(cbind(postpack:::id_mat(post), phi_E_Pb_pred))
+  phi_E_Pb_pred = post_summ(phi_E_Pb_pred, "phi_E_Pb_pred")
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = c(0, max(E[1,]))
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(0, phi_E_Pb["mean",], phi_E_Pb_pred["2.5%",], phi_E_Pb_pred["97.5%",])
+
+  # empty plot with correct dimensions
+  plot(phi_E_Pb["mean",] ~ E["mean",],
+       ylim = ylim,
+       xlim = xlim, type = "n",
+       xaxt = "n")
+
+  # panel label
+  panel_label(paste0("(", paste0("a", j), ")"), "topright", y_inp = 0.075)
+
+  # draw prettier x-axis
+  x_ticks = axisTicks(par("usr")[1:2], log = F)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+  # add credible region for predicted curve
+  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred["2.5%",], rev(phi_E_Pb_pred["97.5%",])), col = tranp_col, border = NA)
+
+  # add posterior mean predicted curve
+  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+
+  # add posterior mean of realized pairs
+  points(phi_E_Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### PARR RECRUITMENT VS. EGG PRODUCTION #####
+
+Pb_VS_E = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of total egg production by brood year
+  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
+
+  # extract posterior summaries of total parr production by brood year
+  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))
+
+  # extract posterior samples of the BH parameters
+  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
+
+  # construct vector of egg abundances to predict at
+  E_pred = seq(0.1, max(E[1,]), length = 30)
+
+  # obtain predicted curves for each posterior sample
+  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) E_pred/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
+
+  # obtain posterior summary of predicted curve
+  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
+  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
+  Pb_pred = post_summ(Pb_pred, "Pb_pred")
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = c(0, max(E[1,]))
+
+  # set yaxis limit
+  if (is.null(ylim)) ylim = c(0, max(Pb[1,]))
+
+  # empty plot with correct dimensions
+  plot(Pb["mean",] ~ E["mean",],
+       ylim = ylim,
+       xlim = xlim, type = "n",
+       xaxt = "n",
+       yaxt = "n")
+
+  # panel label
+  panel_label(paste0("(", paste0("b", j), ")"), "topright", y_inp = 0.075)
+
+  # draw prettier x-axis
+  x_ticks = axisTicks(par("usr")[1:2], log = F)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+  # draw prettier y-axis
+  y_ticks = axisTicks(par("usr")[3:4], log = F)
+  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
+
+  # add credible region for predicted curve
+  polygon(c(E_pred, rev(E_pred)), c(Pb_pred["2.5%",], rev(Pb_pred["97.5%",])), col = tranp_col, border = NA)
+
+  # add posterior mean predicted curve
+  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+
+  # add posterior mean of realized pairs
+  points(Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### PARR SIZE VS. EGG DENSITY #####
+
+L_Pb_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
+  # obtain posterior samples of total egg abundance scaled to WUL
+  E = post_subset(post, sub_index("^E[.+,pop]", pop = j), matrix = TRUE)
+  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
+  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
+  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
+
+  # summarize scaled egg abundance
+  E_scaled_mean = post_summ(post_E, "E_scaled")["mean",]
+
+  # create a vector of scaled egg abundances to predict at
+  E_scaled_seq = seq(min(E_scaled_mean), max(E_scaled_mean), length = 30)
+
+  # extract posteriors of coefficients
+  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
+  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[.+,pop]", pop = j))["mean",]
+
+  # function to create predicted survival curves for one posterior sample
+  pred_fn = function(i) {
+    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
+    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
+    pred_L_Pb
+  }
+
+  # calculate predicted length
+  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
+
+  # extract summarized predicted length
+  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
+  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
+  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]
+
+  E_scaled_seq = (E_scaled_seq * jags_data$wul[j] * jags_data$E_scale)/1e6
+  E_scaled_mean = (E_scaled_mean * jags_data$wul[j] * jags_data$E_scale)/1e6
+
+  # set xaxis limit
+  if (is.null(xlim)) xlim = range(0, E_scaled_seq)
+
+  # set yaxis limit
+  if (is.null(ylim)) ylim = range(L_Pb_mean, pred_L_Pb_lwr, pred_L_Pb_upr, na.rm = TRUE)
+
+  # empty plot with correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("c", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean predicted curve
+  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### OVERWINTER SURVIVAL VS. PARR SIZE #####
+
+phi_Pa_Mb_VS_L_Pb = function(j, i, xlim = NULL, ylim = NULL) {
+
+  pch = c(21, 23)
+  lty = c(1, 2)
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # obtain scaled/centered versions
+  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # summarize posterior of overwinter survival outcomes
+  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,LH_type,pop]", pop = j, LH_type = i))["mean",])[-1,i,j]
+
+  # create vector of lengths to predict at
+  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
+  L_Pb_star_seq = seq(min(L_Pb_star_mean), max(L_Pb_star_mean), length = 30)
+
+  # extract posteriors of coefficients
+  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
+    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
+    pred_phi_Pa_Mb
+  }
+
+  # calculate predicted survivals and add to posterior samples
+  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
+
+  # summarize predicted survival
+  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
+  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
+  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Pb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(0, pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_mean)
+
+  # empty plot with correct dimensions
+  if (i == 1) {
+    plot(1,1, type = "n", 
+         ylim = ylim,
+         xlim = xlim,
+         xlab = "", ylab = ""
+    )
+  }
+
+  # panel label
+  panel_label(paste0("(", paste0("d", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean predicted curve
+  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2, lty = lty[i])
+
+  # add posterior mean of realized pairs
+  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = pch[i], col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  legend_pop = 2
+  if (j == legend_pop & i == 1) {
+    legend("topleft", legend = c("Fall", "Spring"), title = "Mig. Type", pch = pch, pt.bg = tranp_col, col = solid_col, pt.cex = pt_cex, cex = 0.8, bty = "n")
+  }
+
+  # draw boundary box
+  box()
+}
+
+##### SMOLT SIZE VS PARR SIZE #####
+
+L_Mb_VS_L_Pb = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # create a vector of scaled summer lengths to predict at
+  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
+  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # extract posteriors of coefficients
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted curves for one posterior sample
+  pred_fn = function(i) {
+    pred_L_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq) * L_Pb_seq
+    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "1]")
+    pred_L_Mb
+  }
+
+  # calculate predicted growth values and add to posterior samples
+  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
+
+  # summarize predicted growth
+  pred_L_Mb_mean = post_summ(post_pred_L_Mb, ".")["mean",]
+  pred_L_Mb_lwr = post_summ(post_pred_L_Mb, ".")["2.5%",]
+  pred_L_Mb_upr = post_summ(post_pred_L_Mb, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Pb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_mean, na.rm = TRUE)
+
+  # empty plot with the correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim, 
+       xlab = "", ylab = ""
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("e", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean of predicted curve
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(L_Mb_mean ~ L_Pb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### SURVIVAL TO LGR VS. SMOLT SIZE #####
+
+phi_Mb_Ma_VS_L_Mb = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # obtain scaled/centered versions
+  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
+
+  # summarize posterior of migration to LGR survival outcomes
+  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]", pop = j, LH_type = 1, origin = 1))["mean",])[-1,1,1,j]
+
+  # create vectors to predict survival at: for credible regions and mean curve
+  L_Mb_seq = seq(min(L_Mb_mean), max(L_Mb_mean), length = 30)
+  L_Mb_star_seq = seq(min(L_Mb_star_mean), max(L_Mb_star_mean), length = 30)
+
+  # extract posteriors of coefficients
+  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
+  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
+    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
+    pred_phi_Mb_Ma
+  }
+
+  # calculate predicted survivals for each posterior sample
+  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
+
+  # summarize predicted survival
+  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
+  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
+  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Mb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_mean)
+
+  # empty plot with correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim,
+       xlab = "", ylab = ""
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("f", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean of predicted curve
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+}
+
+##### LARGE MULTI-PANEL PLOT #####
+
+make_layout = function(nrow, ncol, show = FALSE) {
+  m = NULL
+  for (r in 1:nrow) {
+    if (r == 1) {
+      f = 1
+    } else {
+      f = max(m) + 1
+    }
+    l = f+ncol-1
+    tmp = rbind(f:l, rep(l+1, ncol))
+    m = rbind(m, tmp)
+  }
+  layout(m, heights = rep(c(1, 0.25), nrow))
+  if (show) layout.show(max(m))
+}
+
+g = function(ylim = c(-3,3), xlim = c(-3,3)) {
+  x = rnorm(30)
+  y = rnorm(30)
+  plot(y ~ x, xlab = "", ylab = "", xlim = xlim, ylim = ylim)
+}
+
+yaxis_label = function(label_main, label_sub) {
+  mtext(side = 2, outer = FALSE, label_main, line = 2.25, cex = 0.9)
+  mtext(side = 2, outer = FALSE, label_sub, line = 1.25, cex = 0.75, font = 3)
+}
+
+xaxis_label = function(label) {
+  plot(1, 1, type = "n", xlim = c(0,1), ylim = c(0,1), axes = FALSE)
+  text(0.5, 0.3, label = label, cex = 1.25, xpd = TRUE)
+}
+
+make_layout(nrow = 6, ncol = 4, show = FALSE)
+
+par(mar = c(0.5,1.5,0,0), oma = c(0,2,1.5,1), tcl = 0, mgp = c(200,0.05,0),
+    lend = "square", ljoin = "mitre")
+
+# egg to parr survival vs. egg density
+# ylim = make_lim(post_summ(post, "^phi_E_Pb[")["mean",])
+ylim = c(0,0.4)
+xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  phi_E_Pa_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Egg \u2192 Parr Survival", "")
+  mtext(side = 3, outer = FALSE, line = 0, pops[j], font = 2)
+}); xaxis_label("Total Egg Production (Millions)")
+
+# parr recruitment vs. total egg production
+ylim = make_lim(post_summ(post, "^Pb[")["mean",]); ylim[1] = 0
+xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  Pb_VS_E(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr Recruitment", "Thousands")
+}); xaxis_label("Total Egg Production (Millions)")
+
+# parr size vs. egg production
+ylim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+xlim = make_lim(post_summ(post, "^E[")["mean",]/1e6); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  L_Pb_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr Mean Length", "mm")
+}); xaxis_label("Total Egg Production (Millions)")
+
+# overwinter survival vs. parr size
+ylim = make_lim(post_summ(post, "^phi_Pa_Mb[")["mean",])
+xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+junk = sapply(1:4, function(j) {
+  phi_Pa_Mb_VS_L_Pb(j, 1, xlim = xlim, ylim = ylim)
+  phi_Pa_Mb_VS_L_Pb(j, 2, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr \u2192 Smolt Survival", "")
+}); xaxis_label("Parr Mean Length (mm)")
+
+# smolt size vs. parr size
+xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+ylim = make_lim(post_summ(post, "^L_Mb[")["mean",])
+junk = sapply(1:4, function(j) {
+  L_Mb_VS_L_Pb(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Smolt Mean Length", "mm")
+}); xaxis_label("Parr Mean Length (mm)")
+
+# migration to LGR vs. smolt size
+xlim = make_lim(post_summ(post, "^L_Mb[")["mean",])
+ylim = make_lim(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = "1", origin = 1, pop = ".")))
+
+junk = sapply(1:4, function(j) {
+  phi_Mb_Ma_VS_L_Mb(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Smolt \u2192 LGR Survival", "")
+}); xaxis_label("Smolt Mean Length (mm)")
+
+```

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create the "no fall" figure

@@
 
+no_fall_caption = "
+  Ratios between the across-year mean (dark grey) and coefficient of variation (light grey) abundance of natural-origin smolt reaching Lower Granite Dam with (denominator) and without (numerator) the fall migrant life history strategy.
+  The 'without' scenario was calculated by assuming all parr recruits experienced freshwater survival rates of spring migrants.
+  Mean ratios <1 and CV ratios >1 indicate LGR smolt abundance would be lower and more variable, respectively, in the absence of the fall migrant strategy.
+  Values presented are posterior means and 95% credible regions.
+"
 ```
@@
 ```
+
+\newpage
+
+```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE}
+cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}
+
+##### STEP 1: EXTRACT POSTERIOR SAMPLES OF QUANTITIES NEEDED #####
+
+# total parr recruitment (regardless of LH type)
+Pb = post_subset(post, "^Pb[", matrix = TRUE)
+
+# total smolt at LGR (separated by LH type)
+Ma = post_subset(post, "^Ma[", matrix = TRUE)
+
+# overwinter survival (separated by LH type)
+phi_Pa_Mb = post_subset(post, "^phi_Pa_Mb[", matrix = TRUE)
+
+# migration survival (separated by LH type, but assumed constant)
+phi_Mb_Ma = post_subset(post, "^phi_Mb_Ma[", matrix = TRUE)
+
+##### STEP 2: DEFINE A FUNCTION TO CALCULATE THE DESIRED STATS FOR A GIVEN POSTERIOR SAMPLE #####
+f = function(i) {
+  # put the values from this draw into the format used in the model
+  Pb_i = array_format(Pb[i,])
+  Ma_i = array_format(Ma[i,])
+  phi_Pa_Mb_i = array_format(phi_Pa_Mb[i,])[,i_spring,]
+  phi_Mb_Ma_i = array_format(phi_Mb_Ma[i,])[,i_spring,o_nor,]
+
+  # calculate hypothetical NOR smolt reaching LGR if all parr were spring migrants
+  Ma_tot_hyp_i = Pb_i * phi_Pa_Mb_i * phi_Mb_Ma_i
+
+  # calculate actual NOR smolt reaching LGR
+  Ma_tot_real_i = Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]
+
+  # add columns storing the aggregate across populations
+  Ma_tot_hyp_i = cbind(Ma_tot_hyp_i, rowSums(Ma_tot_hyp_i))
+  Ma_tot_real_i = cbind(Ma_tot_real_i, rowSums(Ma_tot_real_i))
+
+  # calculate the ratios between the actual and hypothetical
+  mean_p_ratio = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
+  cv_ratio = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)
+
+  names(mean_p_ratio) = paste0("mean_p_ratio[", 1:5, "]")
+  names(cv_ratio) = paste0("cv_ratio[", 1:5, "]")
+  c(mean_p_ratio, cv_ratio)
+}
+
+##### STEP 3: APPLY FUNCTION TO ALL POSTERIOR SAMPLES, FORMAT, AND SUMMARIZE #####
+
+# apply
+ratio_out = t(sapply(1:nrow(Pb), f))
+
+# format
+ratio_post = post_convert(cbind(postpack:::id_mat(post), ratio_out))
+
+# summarize
+mean_summ = post_summ(ratio_post, "mean")
+cv_summ = post_summ(ratio_post, "cv")
+
+# format the summaries for barplotting
+mns = rbind(mean_summ["mean",], cv_summ["mean",])
+lwrs = rbind(mean_summ["2.5%",], cv_summ["2.5%",])
+uprs = rbind(mean_summ["97.5%",], cv_summ["97.5%",])
+
+# set the colors
+cols = c("grey50", "grey80")
+
+# make the plot
+mypar(mfrow = c(1,1), col.axis = "black")
+mp = barplot(mns, beside = TRUE, names.arg = c(pops, "TOTAL"),
+             ylim = c(0, 1.35), border = NA, col = cols)
+
+# draw error bars
+segments(mp, lwrs, mp, uprs)
+
+# draw x-axis
+segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
+axis_labels("Population", "Without:With Fall Migrant Strategy")
+
+# draw a reference line
+abline(h = 1, lty = 2)
+
+# draw a legend
+legend("topright", title = "LGR Smolt", legend = c("Mean", "CV"), pch = 15,
+       col = cols, pt.cex = 1.5, bty = "n", text.col = par("col.axis"), cex = 0.8)
+```
+
+  row_spec(0, bold = TRUE) %>%
+  column_spec(1, monospace = TRUE) %>%
+  row_spec(nrow(tab), bold = TRUE)
+```

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create the time elapsed table

@@
 
+\newpage
+
+```{r time-table}
+# calculate times elapsed for each chunk
+tab = data.frame(
+  Item = names(start_times),
+  Minutes = round(sapply(1:length(start_times), function(i) lubridate::int_length(lubridate::int_diff(c(start_times[[i]], end_times[[i]])))/60), 1)
+)
+
+# add a total time elapsed
+tab = rbind(tab, data.frame(Item = "Total", "Minutes" = sum(tab$Minutes)))
+
+# create the table
+kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") %>%
+  kable_styling(full_width = FALSE, latex_options = "HOLD_position") %>%
   row_spec(0, bold = TRUE) %>%

### 2023-07-06 01-functions/init-fns.R
Remove estimation of pre-spawn survival from SSM

@@ -74,7 +74,7 @@ get_E_obs = function(jags_data, fill_missing = FALSE, append_sim_yrs = FALSE) {
     harvest = do.call(abind, append(harvest, list(along = 3)))
     
     # get the pre-spawn survival
-    prespawn_surv = colSums(x_carcass_spawned, na.rm = TRUE)/colSums(x_carcass_total, na.rm = TRUE)
+    prespawn_surv = colMeans(phi_Sb_Sa, na.rm = TRUE)
     
     # get the age/origin compositon of the total adult return
     # assume 60% pHOS and 20%, 60%, 20% of age 3, 4, and 5

### 2023-07-06 02-model/fit-model.R

@@ -223,7 +223,7 @@ jags_params = c(
   
   # hyperparameters: central tendency
   "mu_pi", "mu_phi_Mb_Ma", "mu_phi_Ma_O0",
-  "mu_psi_O1", "mu_psi_O2", "mu_phi_Sb_Sa",
+  "mu_psi_O1", "mu_psi_O2",
   "mu_phi_O0_O1", "mu_phi_O1_O2", "mu_phi_O2_O3", "mu_phi_Rb_Ra",
   
   # "dot" parameters -- expected values after accounting for relationships (dot), AR(1) (dot2)
@@ -232,7 +232,7 @@ jags_params = c(
   
   # year-specific parameters
   "pi", "phi_Pa_Mb", "phi_Mb_Ma", "phi_Ma_O0", 
-  "psi_O1", "psi_O2", "phi_Sb_Sa",
+  "psi_O1", "psi_O2",
   "phi_O0_O1", "phi_O1_O2", "phi_O2_O3",
   "phi_Rb_Ra", "Delta_L_Pb_Mb",
   
@@ -270,7 +270,7 @@ jags_params = c(
   "x_Ra_obs_qresid", "x_Sa_prime_obs_qresid",
   "lPa_obs_qresid", "lMb_obs_qresid", "lRa_obs_qresid",
   "Lphi_obs_Pb_Ma_qresid", "Lphi_obs_Pa_Ma_qresid", "Lphi_obs_Mb_Ma_qresid",
-  "Lphi_obs_Ma_O0_qresid", "x_LGR_obs_qresid", "x_carcass_spawned_obs_qresid",
+  "Lphi_obs_Ma_O0_qresid", "x_LGR_obs_qresid",
   "lL_Pb_obs_qresid", "lL_Mb_obs_qresid",
   
   # AR(1) coefficients
@@ -291,7 +291,7 @@ pp_check_params = c(
 lppd_params = c(
   "x_Ra_lppd", "x_Sa_prime_lppd", "Pa_obs_lppd", "Mb_obs_lppd", "Ra_obs_lppd",
   "Lphi_obs_Pb_Ma_lppd", "Lphi_obs_Pa_Ma_lppd", "Lphi_obs_Mb_Ma_lppd",
-  "Lphi_obs_Ma_O0_lppd", "x_carcass_spawned_lppd", "x_LGR_lppd"
+  "Lphi_obs_Ma_O0_lppd", "x_LGR_lppd"
 )
 
 # nodes for monitoring potentially non-vague prior densities
[…]

### 2023-07-06 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Remove pre-spawn survival posterior output summary
* MCMC
* Fit to Data
* PP checks
* Noise terms

@@
 
-# Pre-spawn Survival
-L1 = "Pre-spawn Survival"
-L2 = c("Mean")
-match = c("mu_phi_Sb_Sa")
-tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
-tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
-diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
-summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
-
 # Carcass Correction

### 2023-07-06 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Remove pre-spawn survival posterior output summary
* MCMC
* Fit to Data
* PP checks
* Noise terms

@@
 
-#### Pre-spawn
-
-```{r pre-spawn-surv-resid, fig.width = p4_width, fig.height = p4_height}
-mypar()
-tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Return Year", "Count of Female Spawned-out Carcasses QResidual")
-obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
-```
-
 ### Length Data {.tabset .tabset-pills}

### 2023-07-06 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Whoops: squash with previous

@@
 obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
-obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
 obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
@@
 obs_error_ests$origin[stringr::str_detect(obs_error_ests$param, "Tagging")] = 1
-obs_error_ests$origin[obs_error_ests$param == "Pre-spawn"] = 3
 obs_error_ests$origin[obs_error_ests$param %in% c("Summer Parr", "Spring Smolt")] = 1
@@
 obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "->"), 2, obs_error_ests$type)
-obs_error_ests$type = ifelse(stringr::str_detect(obs_error_ests$param, "Pre-spawn"), 2, obs_error_ests$type)
 obs_error_ests$type = ifelse(obs_error_ests$param %in% c("Weir", "Carcass"), 3, obs_error_ests$type)
@@
 obs_error_ests$type = factor(obs_error_ests$type, levels = c("Abundance", "Survival", "Mean Length", "Composition"))
-obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Pre-spawn", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
+obs_error_ests$param = factor(obs_error_ests$param, levels = c("Fall Screw Trap", "Spring Screw Trap", "Adult Return", "Summer Tagging -> LGR", "Fall Tagging -> LGR", "Winter Tagging -> LGR", "Spring Tagging -> LGR", "Smolt Release -> LGR", "LGR Smolt -> Ocean", "BON Adults -> LGR", "Summer Parr", "Spring Smolt", "Weir", "Carcass"))
 obs_error_ests$origin = factor(obs_error_ests$origin, levels = c("NOR", "HOR", "Combined"))

### 2023-07-06 03-post-process/output-plots-children/14-known-values.Rmd
New section in output-plots: known values
See #204

---
editor_options: 
  chunk_output_type: console
---

# Assumed-Known Quantities {.tabset .tabset-dropdown}

This section displays values of quantities passed to the model as non-stochastic, i.e., as being assumed known without error.
These are quantities for which data exist to inform their inter-annual variability, but no process or observation model component exists to explain it.
Dashed lines show the average across all years with non-missing and non-zero values.

```{r known-plot-fn}
known_plot = function(y_val, label, ylim = NULL, y_scale = 1, is_empty = FALSE) {

  # control whether to make the plot an empty panel or not
  if (is_empty) {
    empty_plot()
  } else {
    # create a blank plot
    plot(y_val ~ all_yrs, type = "n", ylim = ylim,
         yaxt = "n", xaxt = "n")

    # add the time series as lines, broken if needed
    lines(y_val ~ all_yrs, col = main_cols["data"], lwd = 2)

    # add the time series as points, to show all years 
    points(y_val ~ all_yrs, col = "white", bg = "white", pch = 21, cex = pt_cex)
    points(y_val ~ all_yrs, col = main_cols["data"], bg = tran_cols["data"], pch = 21, cex = pt_cex)

    # add a horizontal line showing the time series average value
    mn = mean(y_val, na.rm = TRUE)
    segments(min(all_yrs[!is.na(y_val)]), mn, max(all_yrs[!is.na(y_val)]), mn,
             col = par("col.axis"), lty = 3, lwd = 2)

    # draw axes
    at_x = axisTicks(par("usr")[1:2], log = FALSE)
    at_y = axisTicks(par("usr")[3:4], log = FALSE)
    axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
    axis(side = 2, at = at_y, labels = at_y/y_scale)
  }

  # draw panel label
  panel_label(label)
}
```

## HOR Smolt Releases

```{r known-Mb-obs, fig.width = p4_width, fig.height = p4_height}
# function to make plot for one population
plot_f = function(j) {
  y_val = jags_data$Mb_obs[,i_spring,o_hor,j]
  y_val[y_val == 0] = NA
  ylim = c(0, max(jags_data$Mb_obs[,i_spring,o_hor,], na.rm = TRUE))
  known_plot(y_val, label = pops[j], is_empty = j == 3, ylim = ylim, y_scale = 1000)
}

# make plot for all populations
mypar()
junk = lapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "HOR Smolt Releases (1000s)")
```

## Harvest Rate Downstream of BON

```{r known-U, fig.width = p4_width, fig.height = p4_height}
# function to make plot for one age/origin combo
plot_f = function(ko) {
  U = cbind(jags_data$U[,,1], jags_data$U[,,2])
  y_val = U[,ko]
  y_val[y_val == 0] = NA
  oname = ifelse(ko %in% ko_origin$ko_nor, "NOR", "HOR")
  aname = ifelse(ko %in% ko_age$ko_3, "3", ifelse(ko %in% ko_age$ko_4, "4", "5"))

  ylim = c(0, max(jags_data$U, na.rm = TRUE))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), ylim = ylim)
}

# make plot for all ages/origin combos
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f)
axis_labels("Return Year", "Harvest Rate Downstream of BON")
```

## Tributary Harvest {.tabset .tabset-pills}

```{r known-H-fn, fig.width = p4_width, fig.height = p4_height}
# function to make plot for one age/origin combo for one population
plot_f = function(j, ko) {
  Hj = cbind(jags_data$H[,,o_nor,j], jags_data$H[,,o_hor,j])
  y_val = Hj[,ko]
  y_val[y_val == 0] = NA
  oname = ifelse(ko %in% ko_origin$ko_nor, "NOR", "HOR")
  aname = ifelse(ko %in% ko_age$ko_3, "3", ifelse(ko %in% ko_age$ko_4, "4", "5"))

  ylim = c(0, max(jags_data$H, na.rm = TRUE))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), ylim = ylim)
}
```

### CAT

```{r known-H-CAT, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_cat)
axis_labels("Return Year", "Harvest")
```

### LOS

```{r known-H-LOS, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_los)
axis_labels("Return Year", "Harvest")
```

### MIN

```{r known-H-MIN, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_min)
axis_labels("Return Year", "Harvest")
```

### UGR

```{r known-H-UGR, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_ugr)
axis_labels("Return Year", "Harvest")
```

## Weir Removals {.tabset .tabset-pills}

### Numbers of Fish {.tabset .tabset-pills}

```{r known-B-fn}
# function to make the plot for one age/origin combo for one population
plot_f = function(j, ko) {
  Bj = cbind(jags_data$B[,,o_nor,j], jags_data$B[,,o_hor,j])
  y_val = Bj[,ko]
  oname = ifelse(ko %in% ko_origin$ko_nor, "NOR", "HOR")
  aname = ifelse(ko %in% ko_age$ko_3, "3", ifelse(ko %in% ko_age$ko_4, "4", "5"))
  y_val[y_val == 0] = NA
  ylim = make_lim(c(0, max(y_val, na.rm = TRUE)))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), is_empty = j == 3, ylim = ylim)
}
```

#### CAT

```{r known-B-CAT, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_cat)
axis_labels("Return Year", "Removals at Weir")
```

#### LOS

```{r known-B-LOS, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_los)
axis_labels("Return Year", "Removals at Weir")
```

#### MIN

```{r known-B-MIN, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_min)
axis_labels("Return Year", "Removals at Weir")
```

#### UGR

```{r known-B-UGR, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_ugr)
axis_labels("Return Year", "Removals at Weir")
```

### Proportion of Return-to-River {.tabset .tabset-pills}

The fraction of the return estimated to have been removed at the weir based on the data alone, i.e., weir removals divided by the return-to-river estimate apportioned to age/origin by the proportional contribution observed at the weir that year.

```{r known-Bu-fn}
# function to make the plot for one age/origin combo for one population
plot_f = function(j, ko) {
  Bj = cbind(jags_data$B[,,o_nor,j], jags_data$B[,,o_hor,j])
  Ra = 
  p_Ra = jags_data$x_Ra[,ko,j]/jags_data$nx_Ra[,j]

  y_val = Bj[,ko]/(jags_data$Ra_obs[,j] * p_Ra)
  oname = ifelse(ko %in% ko_origin$ko_nor, "NOR", "HOR")
  aname = ifelse(ko %in% ko_age$ko_3, "3", ifelse(ko %in% ko_age$ko_4, "4", "5"))
  y_val[y_val == 0] = NA
  # y_val[y_val > 1] = 1
  # ylim = make_lim(c(0, max(y_val, na.rm = TRUE)))
  ylim = make_lim(c(0, 1.05))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), is_empty = j == 3, ylim = ylim)
}
```

#### CAT

```{r known-Bu-CAT, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_cat)
axis_labels("Return Year", "Removals at Weir")
```

#### LOS

```{r known-Bu-LOS, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_los)
axis_labels("Return Year", "Removals at Weir")
```

#### MIN

```{r known-Bu-MIN, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_min)
axis_labels("Return Year", "Removals at Weir")
```

#### UGR

```{r known-Bu-UGR, fig.width = p6_width, fig.height = p6_height}
mypar(mfrow = c(2,3))
junk = lapply(1:jags_data$nko, plot_f, j = j_ugr)
axis_labels("Return Year", "Removals at Weir")
```

## Fecundity {.tabset .tabset-pills}

Time- and population-varying fecundity estimates were derived from annual mean length-at-age data, and a length-fecundity relationship derived from hatchery spawned females.
Imputation of mean length-at-age data was needed; exploratory analyses revealed that LOS was much different in mean length than the other three populations, thus missing years in the former were imputed separately from the latter group, and populations in the latter group all share identical mean length (thus fecundity) time series.
Age-3 spawners were assumed to be 100% male, thus had assigned fecundity of zero in all years.

```{r known-f-fn}
# function to make the plot for one population/age
f = function(j, k) {
  y_val = jags_data$f[,k,j]
  aname = c(3,4,5)[k]
  y_val[y_val == 0] = NA
  ylim = make_lim(jags_data$f[,2:3,])
  known_plot(y_val, label = paste0("Age-", aname), ylim = ylim, y_scale = 1000)
}
```

### LOS

```{r known-f-LOS, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
junk = lapply(2:3, f, j = j_los)
axis_labels("Return Year", "Eggs Per Female (1000s)")
```

### CAT, MIN, UGR

```{r known-f-CAT-MIN-UGR, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2))
junk = lapply(2:3, f, j = j_cat)
axis_labels("Return Year", "Eggs Per Female (1000s)")
```

## Pre-Spawn Survival

These values are obtained as the model-predicted value from a GLMM fitted to counts of carcasses found with different spawn statuses.

<details>
  <summary>Show model details</summary>

```{r, eval = FALSE, echo = TRUE}
glmmTMB::glmmTMB(
  cbind(yes,no) ~ 1 + (1|year), 
  data = subset(data, population == one_pop), 
  family = binomial
)
```

Where `yes` and `no` are vectors storing as elements the number of female carcasses examined in a given return year (`year`) for one population (`one_pop`) that were and were not successful in spawning ("successful" spawning is assigned by the absence of >50% the potential total eggs carried by that female).
Values were bounded on the interval [0.4,1); several years for UGR suggested very low survival with low sample size.

</details>

```{r known-phi-Sb-Sa-fn}
# function to make the plot for one population
plot_f = function(j) {
  y_val = jags_data$phi_Sb_Sa[,j]
  y_val[y_val == 0] = NA
  ylim = make_lim(jags_data$phi_Sb_Sa)
  known_plot(y_val, label = pops[j], ylim = ylim)
}

# make the plot for all populations
mypar()
junk = lapply(1:jags_data$nj, plot_f)
axis_labels("Return Year", "Pre-Spawn Survival")
```

### 2023-07-06 03-post-process/output-plots.Rmd
New section in output-plots: known values
See #204

@@
     label: "Include Posterior vs. Prior Densities?"
+    value: TRUE
+  include_known:
+     label: "Include Non-Stochastic Quantities?"
      value: TRUE
@@
 
-```{r jags-info, child = "output-plots-children/14-jags-model-info.Rmd", eval = params$include_jags_info}
+```{r known-values, child = "output-plots-children/14-known-values.Rmd", eval = params$include_known}
 ```
+
+```{r jags-info, child = "output-plots-children/15-jags-model-info.Rmd", eval = params$include_jags_info}
+```

### 2023-07-06 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
New output in output-plots: eggs/spawner
New output in output-plots: eggs/female

@@
 
-## Total Eggs vs. Total Spawners
+## Total Eggs vs. Total Spawners {.tabset .tabset-pills}
+
+### Scatterplot
 
@@
 ```
+
+### Eggs per Spawner
+
+Calculated as total annual egg production divided by the sum of all spawners (regardless of age or sex).
+Dashed line shows the time series average for reference.
+
+```{r eggs-per-spawner, fig.width = p4_width, fig.height = p4_height}
+# function to create the plot for one population
+plot_f = function(j) {
+  est = post_summ(post, sub_index("^E_per_Sa[year,pop]$", year = ts_yrs, pop = j))
+  plot_tseries(est = est,
+               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000)
+
+  # add a time series mean
+  mn = mean(est["mean",])
+  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
+}
+
+# loop over populations
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Return Year", "Eggs per Spawner (1000s)")
+```
+
+### Eggs per Female
+
+Calculated as total annual egg production divided by the sum of half of all age-4 and age-5 spawners.
+Dashed line shows the time series average for reference.
+
+```{r eggs-per-female, fig.width = p4_width, fig.height = p4_height}
+# function to calculate eggs-per-female posterior samples
+f = function() {
+  # extract posterior samples of relevant quantities
+  Sa = post_subset(post, "^Sa[", matrix = TRUE)
+  E = post_subset(post, "^E[", matrix = TRUE)
+
+  # function to perform derived quantity calculation for each posterior sample
+  g = function(i) {
+
+    # format
+    Sa_i = array_format(Sa[i,])
+    E_i = array_format(E[i,])
+
+    # drop age-3
+    no_jacks = Sa_i[,-1,,]
+
+    # add hor and nor
+    no_jacks = no_jacks[,,1,] + no_jacks[,,2,]
+
+    # calculate females at age and sum
+    females = no_jacks[,1,] * jags_data$Omega[2] + no_jacks[,2,] * jags_data$Omega[3]
+
+    # calculate eggs per female
+    as.numeric(E_i/females)
+  }
+
+  # apply to each posterior sample
+  out = t(sapply(1:nrow(Sa), g))
+
+  # build element indices: the year
+  y_ind = rep(1:jags_data$ny, jags_data$nj)
+
+  # build element indices: the population
+  j_ind = rep(1:jags_data$nj, each = jags_data$ny)
+
+  # build element names
+  colnames(out) = paste0("E_per_Sa_female[", y_ind, ",", j_ind, "]")
+
+  # determine which should be dropped due to NA values
+  na_ind = which(!is.na(out[1,]))
+
+  # combine with remainder of posterior samples
+  post_bind(post, out[,na_ind])
+}
+
+# apply the function
+post = f()
+
+# function to create the plot for one population
+plot_f = function(j) {
+  est = post_summ(post, sub_index("^E_per_Sa_female[year,pop]$", year = ts_yrs, pop = j))
+  plot_tseries(est = est,
+               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000)
+
+  # add a time series mean
+  mn = mean(est["mean",])
+  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
+}
+
+# loop over populations
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Return Year", "Eggs per Female (1000s)")
+```

### 2023-07-06 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Updates to for sim years on output plots

@@
   lapply(sub_index, origin = o_hor) |>
-  lapply(sub_index, year = ts_yrs) |>
+  lapply(sub_index, year = observable) |>
   lapply(unique) |>

### 2023-07-06 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Updates to for sim years on output plots

@@
 
-plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
+plot_proc_qresid = function(qresid_param, year = observable, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {
 
@@
 mypar()
-tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
+tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
 axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")

### 2023-07-06 02-model/fit-model.R

@@ -464,7 +464,8 @@ if (args$rmd) {
   # render the output
   render(input = "output-plots.Rmd",
          output_file = rmd_out_file,
-         params = list(scenario = scenario),
+         params = list(scenario = scenario,
+                       include_sim_years = args$sim),
          quiet = TRUE
   )
   

### 2023-07-06 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Updates to new content
Misc. bugs, typos, optimizations missed previously

@@
   # add a time series mean
-  mn = mean(est["mean",])
+  mn = mean(est["mean",])/1000
   segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])

### 2023-07-06 03-post-process/output-plots-children/03-fit-to-data.Rmd

@@
 
-### Spawn Status Data
-
-```{r spawn-status-fits, fig.width = p6_width, fig.height = p6_height}
-plot_f = function(j) {
-  # top plot: pre-spawn survival time series
-  plot_tseries(est = post_summ(post, sub_index("^phi_Sb_Sa[year,pop]", pop = j, year = ts_yrs)),
-               obs = get_obs_ests_multinomial(cbind(jags_data$x_carcass_spawned[,j], jags_data$x_carcass_total[,j] - jags_data$x_carcass_spawned[,j])[observable,], 1),
-               label_text = pops[j], ylim = c(0,1), yrs = all_yrs[ts_yrs], pt_cex = pt_cex, label_loc = "bottomleft")
-
-  if (j == 1) mtext(side = 2, "Pre-Spawn Survival", line = 1, cex = 0.9)
-  # om = par("mar"); nm = om; nm[1] = 2; par(mar = nm); on.exit(par(mar = om))
-  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = make_lim(0, jags_data$x_carcass_total),
-               col = tran_cols["data"], border = main_cols["data"])
-  at_x = axisTicks(par("usr")[1:2], log = FALSE)
-  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$x_carcass_total[observable,j]), 3, 4)[at_x])
-  box(col = par("col.axis"))
-
-  if (j == 1) mtext(side = 2, "Carcasses Sampled", line = 1, cex = 0.9)
-}
-
-mypar(mfrow = c(1,1))
-layout(matrix(1:(jags_data$nj * 2), 2, jags_data$nj), heights = c(1, 0.65))
-junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Return Year")
-```
-
 ### Mean Length Data {.tabset .tabset-pills}

### 2023-07-06 03-post-process/output-plots-children/03a-pp-checks.Rmd

@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 ## Posterior Predictive Checks
@@
 
-# pre-spawn survival
-new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
-obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
-bp = array_format(colMeans(obs > new))
-dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
-x_carcass_spawned_bp = data.frame(
-  name = rep("Prespawn", 4), pop = pops,
-  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
-  summarize_bp(bp)
-)
-rownames(x_carcass_spawned_bp) = NULL
-
 # movement survival from BON to LGR
@@
   phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
-  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
+  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_LGR_bp
 )

### 2023-07-06 03-post-process/output-plots-children/12-param-summaries.Rmd

@@
 my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
-my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); ref_line(h = 0)
+my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "AR(1) Coef.", ylim = c(-1,1)); ref_line(h = 0)
 my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
@@
 ```
-
-## Pre-spawn Survival
-
-```{r prespawn-surv-bxp, fig.width = p4_width, fig.height = p4_height, out.width = "50%"}
-mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
-my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
-```

### 2023-07-06 03-post-process/output-plots-children/14-known-values.Rmd

@@
 
-  ylim = c(0, max(jags_data$U, na.rm = TRUE))
+  ylim = make_lim(c(0, max(jags_data$U, na.rm = TRUE)))
   known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), ylim = ylim)
@@
 
+It is possible for the raw data values to suggest >100% of the fish at a given age/origin combo were taken -- the SSM prevents this from happening.
+
 ```{r known-Bu-fn}
@@
 
-Where `yes` and `no` are vectors storing as elements the number of female carcasses examined in a given return year (`year`) for one population (`one_pop`) that were and were not successful in spawning ("successful" spawning is assigned by the absence of >50% the potential total eggs carried by that female).
+Where `yes` and `no` are vectors storing the number of female carcasses examined each return year (`year`) for one population (`one_pop`) that were and were not successful in spawning ("successful" spawning is assigned by the absence of >50% the potential total eggs carried by that female).
 Values were bounded on the interval [0.4,1); several years for UGR suggested very low survival with low sample size.
@@
 
-```{r known-phi-Sb-Sa-fn}
+```{r known-phi-Sb-Sa-fn, fig.width = p4_width, fig.height = p4_height}
 # function to make the plot for one population

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Enable toggling on/off ms-content analyses one at a time

@@
     input: numeric
-  include_sim_years:
-    label: "Include Simulated Years on Plots?"
-    value: FALSE
+  beta_fig:
+    value: TRUE
+  relationship_fig:
+    value: TRUE
+  no_fall_fig:
+    value: TRUE
 header-includes:
@@
 **GR-sslcm**
+:::
+
+\vspace{-6pt}
+
+::: {.normalsize data-latex=""}
+**Scenario:** ``r params$scenario``  
+**Kept MCMC Iterations:** `r paste0(params$thin_percent * 100, "\\%")`
 :::
@@
 
-```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE}
+```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE, eval = params$beta_fig}
 # extract posterior summaries of the capacity parameters
@@
 
-```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE}
+```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
 solid_col = "grey30"
@@
 
-```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE}
+```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE, eval = params$no_fall_fig}
 cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Add ms-content figure: comparison of survival rates

@@
   no_fall_fig:
+    value: TRUE
+  surv_compare_fig:
     value: TRUE
@@
   Values presented are posterior means and 95% credible regions.
+"
+
+surv_compare_caption = "
+  Survival probability parameters estimated by the state-space model, separated by stage transition and other demographic features (migratory type, origin, population) where applicable.
+  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
+  Information about mortality due to sources/stages not displayed here was either assumed known without error (e.g., prespawn mortality) or expressed as strong prior information with no inter-annual variability (i.e., mortality experienced in ocean-1 $\\to$ ocean-2 and ocean-2 $\\to$ ocean-3).
 "
@@
 
+```{r compare-fn, eval = params$surv_compare_fig | params$apportion_compare_fig}
+pch = c(21, 23)
+
+cex_main = 2.5
+cex_sub = 1.1
+
+solid_col = "grey40"
+tranp_col = alpha(solid_col, 0.25)
+
+f_horiz = function(ests1, ests2, lim, label) {
+  # prepare the first group of estimates
+  ests1 = ests1[-1,]; x1 = colMeans(ests1)
+
+  # figure out the correct axis labels
+  if (ncol(ests1) == 4) tick_labels = pops else tick_labels = c("NOR", "HOR")
+  jitter = runif(nrow(ests1), -0.25, 0.25)
+
+  if (is.null(ests2)) {
+    # empty barplot with correct dimensions
+    mp = barplot(x1, col = "white", border = "white", xlim = lim, ylim = c(ncol(ests1) + 0.5, 0.05), horiz = TRUE)
+
+    # figure out location of jittered points
+    mp_all = t(sapply(1:nrow(ests1), function(i) mp))
+    mp_all = apply(mp_all, 2, function(x) x + jitter)
+
+    # draw year-specific estimates
+    points(ests1, mp_all, col = solid_col, bg = tranp_col, pch = pch[1], cex = cex_sub)
+
+    # draw year averages
+    points(x1, mp, pch = pch[1], col = "white", bg = "black", cex = cex_main, lwd = 1.5)
+
+    # draw axis
+    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
+    par(mgp = nmgp)
+    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
+    axis(side = 2, at = mp, labels = tick_labels, las = 1)
+    par(mgp = omgp)
+
+  } else {
+    # prepare the second group of estimates if supplied
+    ests2 = ests2[-1,]; x2 = colMeans(ests2)
+
+    # empty barplot with correct dimensions
+    mp = barplot(rbind(x1, x2), beside = TRUE, space = c(0.25,1), col = "white", border = "white", xlim = lim, ylim = c(ncol(ests1) * 3 + 1, 0.15), horiz = TRUE)
+    mp1 = mp[1,]; mp2 = mp[2,]
+
+    # figure out location of jittered points
+    mp1_all = t(sapply(1:nrow(ests1), function(i) mp1))
+    mp1_all = apply(mp1_all, 2, function(x) x + jitter)
+    mp2_all = t(sapply(1:nrow(ests2), function(i) mp2))
+    mp2_all = apply(mp2_all, 2, function(x) x + jitter)
+
+    # draw year-specific estimates
+    points(ests1, mp1_all, col = solid_col, bg = tranp_col, pch = pch[1], cex = cex_sub)
+    points(ests2, mp2_all, col = solid_col, bg = tranp_col, pch = pch[2], cex = cex_sub)
+
+    # draw year averages
+    points(x1, mp1, pch = pch[1], cex = cex_main, bg = "black", col = "white", lwd = 1.5)
+    points(x2, mp2, pch = pch[2], cex = cex_main, bg = "black", col = "white", lwd = 1.5)
+
+    # draw axis
+    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
+    par(mgp = nmgp)
+    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
+    axis(side = 2, at = (mp1 + mp2)/2, labels = tick_labels, las = 1)
+    par(mpg = omgp)
+  }
+
+  # draw panel label
+  panel_label(label, y_inp = ifelse(ncol(ests1) == 4, 0.05, 0.1), cex = 1.2)
+}
+
+legend_f = function(title, grp1, grp2, loc = "topright") {
+  legend(loc, title = title, legend = c(grp1, grp2), pch = pch, pt.cex = 1.3, cex = 0.9, bty = "n",
+         text.col = par("col.axis"), col = "black", pt.bg = "black")
+}
+```
+
+```{r surv-compare-fig, fig.width = 3.4, fig.height = 8, fig.cap = msdown::prep_caption(surv_compare_caption), time_it = TRUE, eval = params$surv_compare_fig}
+
+# extract the posterior means to plot
+phi_E_Pb = array_format(post_summ(post, sub_index("^phi_E_Pb[year,pop]", year = observable, pop = ".+"))["mean",])
+phi_Pa_Mb_fall = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_fall))["mean",])[,i_fall,]
+phi_Pa_Mb_spring = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_spring))["mean",])[,i_spring,]
+phi_Mb_Ma_nor = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = observable, pop = ".+", LH_type = i_spring, origin = o_nor))["mean",])[,i_spring,o_nor,]
+phi_Mb_Ma_hor = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = observable, pop = ".+", LH_type = i_spring, origin = o_hor))["mean",])[,i_spring,o_hor,]
+phi_Ma_O0 = array_format(post_summ(post, sub_index("^phi_Ma_O0[year,origin]", year = observable, origin = ".+"))["mean",])
+phi_O0_O1_nor = array_format(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
+phi_O0_O1_hor = array_format(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]
+phi_Rb_Ra = array_format(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]", year = observable, origin = ".+"))["mean",])
+
+# set MIN to NA for HOR values
+phi_Mb_Ma_hor[,j_min] = NA
+phi_O0_O1_hor[,j_min] = NA
+
+mypar(mfrow = c(1,1), oma = c(1.5,1,0,1), col.axis = "black")
+layout(matrix(1:5, ncol = 1), height = c(1,1,1,0.5,1))
+f_horiz(ests1 = phi_E_Pb, ests2 = NULL, lim = c(0, 0.5), label = "(a) Egg \u2192 Parr")
+
+f_horiz(ests1 = phi_Pa_Mb_fall, ests2 = phi_Pa_Mb_spring, lim = c(0,1), label = "(b) Parr \u2192 Smolt")
+legend_f("Mig. Type", "Fall", "Spring")
+
+f_horiz(ests1 = phi_Mb_Ma_nor, ests2 = phi_Mb_Ma_hor, lim = c(0,1), label = "(c) Smolt \u2192 LGR")
+legend_f("Origin", "NOR", "HOR")
+
+f_horiz(ests1 = phi_Ma_O0, ests2 = phi_Rb_Ra, lim = c(0,1), label = "(d) Mainstem")
+legend_f("Direction", "LGR \u2192 BON", "BON \u2192 LGR", "bottomleft")
+
+f_horiz(ests1 = phi_O0_O1_nor, ests2 = phi_O0_O1_hor, lim = c(0,0.4), label = "(e) Ocean-0 \u2192 Ocean-1")
+legend_f("Origin", "NOR", "HOR", "bottomright")
+axis_labels("Survival Probability")
+```
+
 ```{r time-table}

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Add ms-content figure: comparison of transition rates
LH type apportionment and maturation rates

@@
 "
+
+apportion_compare_caption = "
+  Transition probability parameters (unrelated to survival) estimated by the state-space model, separated by life stage and origin where applicable.
+  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
+"
+
 ```
@@
 
+\newpage
+
+```{r apportion-compare-fig, fig.width = 3.4, fig.height = 8 * (3/4.5), fig.cap = msdown::prep_caption(apportion_compare_caption), time_it = TRUE, eval = params$apportion_compare_fig}
+
+# extract the posterior means to plot
+pi_fall = array_format(post_summ(post, sub_index("^pi[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_fall))["mean",])[,i_fall,]
+psi_O1_nor = array_format(post_summ(post, sub_index("^psi_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
+psi_O1_hor = array_format(post_summ(post, sub_index("^psi_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]
+psi_O2_nor = array_format(post_summ(post, sub_index("^psi_O2[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
+psi_O2_hor = array_format(post_summ(post, sub_index("^psi_O2[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]
+
+# set MIN to NA for HOR values
+psi_O1_hor[,j_min] = NA
+psi_O1_hor[,j_min] = NA
+
+mypar(mfrow = c(1,1), oma = c(1.5,1,0,1), col.axis = "black")
+layout(matrix(1:3, ncol = 1), height = c(1,1,1))
+f_horiz(ests1 = pi_fall, ests2 = NULL, lim = c(0, 0.6), label = "(a) Pr(Fall Migrant)")
+
+f_horiz(ests1 = psi_O1_nor, ests2 = psi_O1_hor, lim = c(0,0.4), label = "(b) Pr(Mature Age-3)")
+legend_f("Origin", "NOR", "HOR")
+
+f_horiz(ests1 = psi_O2_nor, ests2 = psi_O2_hor, lim = c(0,1), label = "(c) Pr(Mature Age-4)")
+legend_f("Origin", "NOR", "HOR", "bottomleft")
+
+axis_labels("Transition Probability (Non-Survival)")
+```
+
+\newpage
+
 ```{r time-table}

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Add ms-content figure: correlation comparions

@@
   surv_compare_fig:
+    value: TRUE
+  apportion_compare_fig:
+    value: TRUE
+  corr_compare_fig:
     value: TRUE
@@
 
+corr_compare_caption = "
+  Correlation terms of the covariance matrices controlling process variability.
+  Posterior means of population pair-specific correlations are displayed as points, and the posterior of the average of the 6 pairs is summarized in black (thin lines are 95% CRIs, thick lines 50% CRIs, and cross marks are means).
+  Survival processes are denoted by $x \\to y$, where as transition processes are denoted by $\\Pr(x)$.
+  The correlation in survival processes representing the migration downstream and upstream through the mainstem (LGR $\\to$ BON and BON $\\to$ LGR, respectively) represent among-origin correlation, hence the lack of points.
+"
 ```
@@
 
+```{r corr-compare-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(corr_compare_caption), eval = params$corr_compare_fig}
+
+# get posterior summaries of the mean correlation across all pop pairs
+# for each process separately
+rho_params1 = match_params(post, "rho", type = "base_only")
+rho_params2 = match_params(post, "rho_.+_pr", type = "base_only")
+rho_params = rho_params1[!(rho_params1 %in% rho_params2)]
+
+# function to extract posterior summaries of the rho parameters for a given process
+f = function(p) {
+  x = rowMeans(post_subset(post, paste0("^", p, "["), matrix = TRUE))
+  c(mean = mean(x), sd = sd(x), quantile(x, c(0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975)))
+}
+
+# apply it and order
+rho_mean_out = t(sapply(rho_params, f))
+rho_mean_out = rho_mean_out[order(rho_mean_out[,"mean"]),]
+
+# assign names to the different rho parameters
+rho_labels = c(
+  "rho_Lphi_E_Pb" = "Egg \u2192 Parr",
+  "rho_Lphi_O0_O1" = "Ocean-0 \u2192 Ocean-1",
+  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
+  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
+  "rho_lDelta_L_Pb_Mb" = "\u0394 Mean Length",
+  "rho_Lphi_Mb_Ma" = "Smolt \u2192 LGR",
+  "rho_lL_Pb" = "Mean Parr Length",
+  "rho_Lphi_Pa_Mb" = "Parr \u2192 Smolt",
+  "rho_Lphi_Rb_Ra" = "BON \u2192 LGR",
+  "rho_Lpi" = "Pr(Fall Migrant)",
+  "rho_Lphi_Ma_O0" = "LGR \u2192 BON"
+)
+
+# set up empty plotting region
+mypar(mar = c(2.5,6,1,0.75), yaxs = "i", mfrow = c(1,1), oma = c(0,0,0,0), mgp = c(2,0.1,0), col.axis = "black", cex.axis = 0.75)
+mp = barplot(rho_mean_out[,"mean"], 
+             horiz = TRUE, xlim = c(-1,1),
+             names.arg = rho_labels[rownames(rho_mean_out)],
+             las = 1, col = "white", border = "white")
+usr = par("usr")
+
+box_upr = mp - rbind(diff(mp)/2, NA)
+box_lwr = mp + rbind(diff(mp)/2, NA)
+box_upr[nrow(box_upr),] = box_upr[nrow(box_upr)-1,] + diff(box_upr[1:2])
+box_lwr[nrow(box_lwr),] = box_lwr[nrow(box_upr)-1,] + diff(box_lwr[1:2])
+
+pop_rhos = function(param, at_mp) {
+
+  # if the process is not one of the hydropower migration survival ones, do this
+  # those processes are correlated across origins, because all populations share the same values each year
+  if (!(param %in% c("rho_Lphi_Ma_O0", "rho_Lphi_Rb_Ra"))) {
+    x = post_summ(post, paste0(param, vcov_inds), probs = c(0.1, 0.25, 0.75, 0.9))
+    y = at_mp + runif(6, -0.3, 0.3)
+    points(y ~ x["mean",], pch = 21, col = solid_col, bg = tranp_col)
+  } 
+}
+abline(v = 0, lty = 1, lwd = 2, col = "grey")
+
+junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 7, col = "white")
+segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "white", lwd = 2)
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "white", lwd = 4)
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = "black")
+segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "black")
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "black", lwd = 3)
+
+abline(h = mp + rbind(diff(mp)/2, NA), xpd = FALSE, col = "grey", lty = 2)
+# par(tcl = -7)
+# axis(side = 2, at = mp + rbind(diff(mp)/2, NA), col = "grey", line = NA, labels = FALSE, lty = 2)
+box(col = par("col.axis"))
+axis_labels(xlab = "Process Noise Correlation", xline = 1.25, outer = FALSE)
+```
+
+\clearpage
+
 ```{r time-table}

### 2023-08-16 03-post-process/ms-content/ms-content.Rmd

@@
     input: numeric
+  include_sim_years:
+    value: FALSE
   beta_fig:
-    value: TRUE
+    value: FALSE
   relationship_fig:
@@
   corr_compare_fig:
+    value: TRUE
+  WUL_change_fig:
     value: TRUE
@@
 "
-```
-
-```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE, eval = params$beta_fig}
-# extract posterior summaries of the capacity parameters
-beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))
-
-# extract posterior samples of the slope parameter
-beta_per = post_subset(post, "lambda", TRUE)
-
-# create a sequence of WUL values to predict capacity at
-wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
-
-# obtain the regression line for each posterior sample
-pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
-
-# summarize posterior of regression line
-pred_beta_summ = apply(pred_beta, 2, function(x) c(mean = mean(x), quantile(x, c(0.025, 0.1, 0.5, 0.9, 0.975))))
-
-# empty plot with correct labeling/dimensions
-mypar(mfrow = c(1,1), col.axis = "black")
-plot(1,1, type = "n", xlim = range(wul_seq),
-     # ylim = c(0, max(beta_ests["97.5%",], pred_beta_summ["97.5%",])),
-     ylim = c(0, 3000) * 1000,
-     xlab = "",
-     ylab = "", yaxt = "n")
-
-# draw prettier y-axis
-at_y = c(0, 1000, 2000, 3000) * 1000
-axis(side = 2, at = at_y, labels = at_y/1000)
-usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
-
-# draw the regression uncertainty
-polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["2.5%",], rev(pred_beta_summ["97.5%",])), border = NA, col = tranp_col)
-polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["10%",], rev(pred_beta_summ["90%",])), border = NA, col = tranp_col)
-
-# draw the posterior mean regression line
-lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)
-
-# draw the population-specific capacity estimates w/error bars and labels
-segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)
-
-# draw the population labels
-xoff = 0.015
-yoff = 0.03
-text(x = jags_data$wul      + xdiff * c(1.5,-1,1,1) * xoff,
-     y = beta_ests["mean",] + ydiff * c(1,-1,1,1) * yoff,
-     labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,2,2), font = 1, cex = 0.8)
-
-# add axis labels
-axis_labels("Weighted Usable Habitat Length (km)", "Parr Capacity (Thousands)")
-```
-
-\newpage
-
-```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
-solid_col = "grey30"
-tranp_col = alpha(solid_col, 0.25)
-pt_cex = 1.3
-
-##### EGG-TO-PARR SURVIVAL VS. EGG DENSITY #####
-
-phi_E_Pa_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
-
-  # extract posterior summaries of egg to parr survival rates
-  phi_E_Pb = post_summ(post, sub_index("^phi_E_Pb[.+,pop]", pop = j))
-
-  # extract posterior samples of the BH parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # construct vector of egg abundances to predict at
-  E_pred = seq(0.1, max(E[1,]), length = 30)
-
-  # obtain predicted curves for each posterior sample
-  phi_E_Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) 1/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
-
-  # obtain posterior summary of predicted curve
-  colnames(phi_E_Pb_pred) = paste0("phi_E_Pb_pred[", 1:length(E_pred), "]")
-  phi_E_Pb_pred = post_convert(cbind(postpack:::id_mat(post), phi_E_Pb_pred))
-  phi_E_Pb_pred = post_summ(phi_E_Pb_pred, "phi_E_Pb_pred")
-
-  # set xaxis limits
-  if (is.null(xlim)) xlim = c(0, max(E[1,]))
-
-  # set yaxis limits
-  if (is.null(ylim)) ylim = range(0, phi_E_Pb["mean",], phi_E_Pb_pred["2.5%",], phi_E_Pb_pred["97.5%",])
-
-  # empty plot with correct dimensions
-  plot(phi_E_Pb["mean",] ~ E["mean",],
-       ylim = ylim,
-       xlim = xlim, type = "n",
-       xaxt = "n")
-
-  # panel label
-  panel_label(paste0("(", paste0("a", j), ")"), "topright", y_inp = 0.075)
-
-  # draw prettier x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  # add credible region for predicted curve
-  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred["2.5%",], rev(phi_E_Pb_pred["97.5%",])), col = tranp_col, border = NA)
-
-  # add posterior mean predicted curve
-  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
-
-  # add posterior mean of realized pairs
-  points(phi_E_Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
-
-  # draw boundary box
-  box()
-}
-
-##### PARR RECRUITMENT VS. EGG PRODUCTION #####
-
-Pb_VS_E = function(j, xlim = NULL, ylim = NULL) {
-
-  # extract posterior summaries of total egg production by brood year
-  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
-
-  # extract posterior summaries of total parr production by brood year
-  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))
-
-  # extract posterior samples of the BH parameters
-  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
-
-  # construct vector of egg abundances to predict at
-  E_pred = seq(0.1, max(E[1,]), length = 30)
-
-  # obtain predicted curves for each posterior sample
-  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) E_pred/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
-
-  # obtain posterior summary of predicted curve
-  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
-  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
-  Pb_pred = post_summ(Pb_pred, "Pb_pred")
-
-  # set xaxis limits
-  if (is.null(xlim)) xlim = c(0, max(E[1,]))
-
-  # set yaxis limit
-  if (is.null(ylim)) ylim = c(0, max(Pb[1,]))
-
-  # empty plot with correct dimensions
-  plot(Pb["mean",] ~ E["mean",],
-       ylim = ylim,
-       xlim = xlim, type = "n",
-       xaxt = "n",
-       yaxt = "n")
-
-  # panel label
-  panel_label(paste0("(", paste0("b", j), ")"), "topright", y_inp = 0.075)
-
-  # draw prettier x-axis
-  x_ticks = axisTicks(par("usr")[1:2], log = F)
-  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
-
-  # draw prettier y-axis
-  y_ticks = axisTicks(par("usr")[3:4], log = F)
-  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
-
-  # add credible region for predicted curve
-  polygon(c(E_pred, rev(E_pred)), c(Pb_pred["2.5%",], rev(Pb_pred["97.5%",])), col = tranp_col, border = NA)
-
-  # add posterior mean predicted curve
-  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
-
-  # add posterior mean of realized pairs
-  points(Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
-
-  # draw boundary box
-  box()
-}
-
-##### PARR SIZE VS. EGG DENSITY #####
-
-L_Pb_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
-  # obtain posterior samples of total egg abundance scaled to WUL
-  E = post_subset(post, sub_index("^E[.+,pop]", pop = j), matrix = TRUE)
-  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
-  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
-  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
-
-  # summarize scaled egg abundance
-  E_scaled_mean = post_summ(post_E, "E_scaled")["mean",]
-
-  # create a vector of scaled egg abundances to predict at
-  E_scaled_seq = seq(min(E_scaled_mean), max(E_scaled_mean), length = 30)
-
-  # extract posteriors of coefficients
-  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
-  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[.+,pop]", pop = j))["mean",]
-
-  # function to create predicted survival curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
-    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
-    pred_L_Pb
-  }
-
-  # calculate predicted length
-  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
-
-  # extract summarized predicted length
-  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
-  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
-  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]
-
-  E_scaled_seq = (E_scaled_seq * jags_data$wul[j] * jags_data$E_scale)/1e6
-  E_scaled_mean = (E_scaled_mean * jags_data$wul[j] * jags_data$E_scale)/1e6
-
-  # set xaxis limit
-  if (is.null(xlim)) xlim = range(0, E_scaled_seq)
-
-  # set yaxis limit
-  if (is.null(ylim)) ylim = range(L_Pb_mean, pred_L_Pb_lwr, pred_L_Pb_upr, na.rm = TRUE)
-
-  # empty plot with correct dimensions
-  plot(1,1, type = "n", 
-       ylim = ylim,
-       xlim = xlim
-  )
-
-  # panel label
-  panel_label(paste0("(", paste0("c", j), ")"), "topright", y_inp = 0.075)
-
-  # add credible region for predicted curve
-  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = tranp_col)
-
-  # add posterior mean predicted curve
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col, lwd = 2)
-
-  # add posterior mean of realized pairs
-  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
-
-  # draw boundary box
-  box()
-}
-
-##### OVERWINTER SURVIVAL VS. PARR SIZE #####
-
-phi_Pa_Mb_VS_L_Pb = function(j, i, xlim = NULL, ylim = NULL) {
-
-  pch = c(21, 23)
-  lty = c(1, 2)
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
-
-  # obtain scaled/centered versions
-  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # summarize posterior of overwinter survival outcomes
-  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,LH_type,pop]", pop = j, LH_type = i))["mean",])[-1,i,j]
-
-  # create vector of lengths to predict at
-  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
-  L_Pb_star_seq = seq(min(L_Pb_star_mean), max(L_Pb_star_mean), length = 30)
-
-  # extract posteriors of coefficients
-  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
-    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
-    pred_phi_Pa_Mb
-  }
-
-  # calculate predicted survivals and add to posterior samples
-  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
-
-  # summarize predicted survival
-  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
-  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
-  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]
-
-  # set xaxis limits
-  if (is.null(xlim)) xlim = range(L_Pb_seq)
-
-  # set yaxis limits
-  if (is.null(ylim)) ylim = range(0, pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_mean)
-
-  # empty plot with correct dimensions
-  if (i == 1) {
-    plot(1,1, type = "n", 
-         ylim = ylim,
-         xlim = xlim,
-         xlab = "", ylab = ""
-    )
-  }
-
-  # panel label
-  panel_label(paste0("(", paste0("d", j), ")"), "topright", y_inp = 0.075)
-
-  # add credible region for predicted curve
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = tranp_col)
-
-  # add posterior mean predicted curve
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2, lty = lty[i])
-
-  # add posterior mean of realized pairs
-  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = pch[i], col = solid_col, bg = tranp_col, cex = pt_cex)
-
-  legend_pop = 2
-  if (j == legend_pop & i == 1) {
-    legend("topleft", legend = c("Fall", "Spring"), title = "Mig. Type", pch = pch, pt.bg = tranp_col, col = solid_col, pt.cex = pt_cex, cex = 0.8, bty = "n")
-  }
-
-  # draw boundary box
-  box()
-}
-
-##### SMOLT SIZE VS PARR SIZE #####
-
-L_Mb_VS_L_Pb = function(j, xlim = NULL, ylim = NULL) {
-
-  # extract posterior summaries of summer length outcomes
-  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
-
-  # create a vector of scaled summer lengths to predict at
-  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
-  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
-
-  # extract posteriors of coefficients
-  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
-  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted curves for one posterior sample
-  pred_fn = function(i) {
-    pred_L_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq) * L_Pb_seq
-    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "1]")
-    pred_L_Mb
-  }
-
-  # calculate predicted growth values and add to posterior samples
-  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
-
-  # summarize predicted growth
-  pred_L_Mb_mean = post_summ(post_pred_L_Mb, ".")["mean",]
-  pred_L_Mb_lwr = post_summ(post_pred_L_Mb, ".")["2.5%",]
-  pred_L_Mb_upr = post_summ(post_pred_L_Mb, ".")["97.5%",]
-
-  # set xaxis limits
-  if (is.null(xlim)) xlim = range(L_Pb_seq)
-
-  # set yaxis limits
-  if (is.null(ylim)) ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_mean, na.rm = TRUE)
-
-  # empty plot with the correct dimensions
-  plot(1,1, type = "n", 
-       ylim = ylim,
-       xlim = xlim, 
-       xlab = "", ylab = ""
-  )
-
-  # panel label
-  panel_label(paste0("(", paste0("e", j), ")"), "topright", y_inp = 0.075)
-
-  # add credible region for predicted curve
-  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = tranp_col)
-
-  # add posterior mean of predicted curve
-  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2)
-
-  # add posterior mean of realized pairs
-  points(L_Mb_mean ~ L_Pb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
-
-  # draw boundary box
-  box()
-}
-
-##### SURVIVAL TO LGR VS. SMOLT SIZE #####
-
-phi_Mb_Ma_VS_L_Mb = function(j, xlim = NULL, ylim = NULL) {
-
-  # extract posterior summaries of spring length outcomes
-  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
-
-  # obtain scaled/centered versions
-  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
-
-  # summarize posterior of migration to LGR survival outcomes
-  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]", pop = j, LH_type = 1, origin = 1))["mean",])[-1,1,1,j]
-
-  # create vectors to predict survival at: for credible regions and mean curve
-  L_Mb_seq = seq(min(L_Mb_mean), max(L_Mb_mean), length = 30)
-  L_Mb_star_seq = seq(min(L_Mb_star_mean), max(L_Mb_star_mean), length = 30)
-
-  # extract posteriors of coefficients
-  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
-  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
-
-  # function to create predicted survival curve for one posterior sample
-  pred_fn = function(i) {
-    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
-    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
-    pred_phi_Mb_Ma
-  }
-
-  # calculate predicted survivals for each posterior sample
-  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
-  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
-
-  # summarize predicted survival
-  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
-  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
-  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
-
-  # set xaxis limits
-  if (is.null(xlim)) xlim = range(L_Mb_seq)
-
-  # set yaxis limits
-  if (is.null(ylim)) ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_mean)
-
-  # empty plot with correct dimensions
-  plot(1,1, type = "n", 
-       ylim = ylim,
-       xlim = xlim,
-       xlab = "", ylab = ""
-  )
-
-  # panel label
-  panel_label(paste0("(", paste0("f", j), ")"), "topright", y_inp = 0.075)
-
-  # add credible region for predicted curve
-  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tranp_col)
-
-  # add posterior mean of predicted curve
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col, lwd = 2)
-
-  # add posterior mean of realized pairs
-  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
-}
-
-##### LARGE MULTI-PANEL PLOT #####
-
-make_layout = function(nrow, ncol, show = FALSE) {
-  m = NULL
-  for (r in 1:nrow) {
-    if (r == 1) {
-      f = 1
-    } else {
-      f = max(m) + 1
-    }
-    l = f+ncol-1
-    tmp = rbind(f:l, rep(l+1, ncol))
-    m = rbind(m, tmp)
-  }
-  layout(m, heights = rep(c(1, 0.25), nrow))
-  if (show) layout.show(max(m))
-}
-
-g = function(ylim = c(-3,3), xlim = c(-3,3)) {
-  x = rnorm(30)
-  y = rnorm(30)
-  plot(y ~ x, xlab = "", ylab = "", xlim = xlim, ylim = ylim)
-}
-
-yaxis_label = function(label_main, label_sub) {
-  mtext(side = 2, outer = FALSE, label_main, line = 2.25, cex = 0.9)
-  mtext(side = 2, outer = FALSE, label_sub, line = 1.25, cex = 0.75, font = 3)
-}
-
-xaxis_label = function(label) {
-  plot(1, 1, type = "n", xlim = c(0,1), ylim = c(0,1), axes = FALSE)
-  text(0.5, 0.3, label = label, cex = 1.25, xpd = TRUE)
-}
-
-make_layout(nrow = 6, ncol = 4, show = FALSE)
-
-par(mar = c(0.5,1.5,0,0), oma = c(0,2,1.5,1), tcl = 0, mgp = c(200,0.05,0),
-    lend = "square", ljoin = "mitre")
-
-# egg to parr survival vs. egg density
-# ylim = make_lim(post_summ(post, "^phi_E_Pb[")["mean",])
-ylim = c(0,0.4)
-xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
-junk = sapply(1:4, function(j) {
-  phi_E_Pa_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Egg \u2192 Parr Survival", "")
-  mtext(side = 3, outer = FALSE, line = 0, pops[j], font = 2)
-}); xaxis_label("Total Egg Production (Millions)")
-
-# parr recruitment vs. total egg production
-ylim = make_lim(post_summ(post, "^Pb[")["mean",]); ylim[1] = 0
-xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
-junk = sapply(1:4, function(j) {
-  Pb_VS_E(j, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Parr Recruitment", "Thousands")
-}); xaxis_label("Total Egg Production (Millions)")
-
-# parr size vs. egg production
-ylim = make_lim(post_summ(post, "^L_Pb[")["mean",])
-xlim = make_lim(post_summ(post, "^E[")["mean",]/1e6); xlim[1] = 0
-junk = sapply(1:4, function(j) {
-  L_Pb_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Parr Mean Length", "mm")
-}); xaxis_label("Total Egg Production (Millions)")
-
-# overwinter survival vs. parr size
-ylim = make_lim(post_summ(post, "^phi_Pa_Mb[")["mean",])
-xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
-junk = sapply(1:4, function(j) {
-  phi_Pa_Mb_VS_L_Pb(j, 1, xlim = xlim, ylim = ylim)
-  phi_Pa_Mb_VS_L_Pb(j, 2, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Parr \u2192 Smolt Survival", "")
-}); xaxis_label("Parr Mean Length (mm)")
-
-# smolt size vs. parr size
-xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
-ylim = make_lim(post_summ(post, "^L_Mb[")["mean",])
-junk = sapply(1:4, function(j) {
-  L_Mb_VS_L_Pb(j, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Smolt Mean Length", "mm")
-}); xaxis_label("Parr Mean Length (mm)")
-
-# migration to LGR vs. smolt size
-xlim = make_lim(post_summ(post, "^L_Mb[")["mean",])
-ylim = make_lim(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = "1", origin = 1, pop = ".")))
-
-junk = sapply(1:4, function(j) {
-  phi_Mb_Ma_VS_L_Mb(j, xlim = xlim, ylim = ylim)
-  if (j == 1) yaxis_label("Smolt \u2192 LGR Survival", "")
-}); xaxis_label("Smolt Mean Length (mm)")
-
-```
-
-\newpage
-
-```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE, eval = params$no_fall_fig}
-cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}
-
-##### STEP 1: EXTRACT POSTERIOR SAMPLES OF QUANTITIES NEEDED #####
-
-# total parr recruitment (regardless of LH type)
-Pb = post_subset(post, "^Pb[", matrix = TRUE)
-
-# total smolt at LGR (separated by LH type)
-Ma = post_subset(post, "^Ma[", matrix = TRUE)
-
-# overwinter survival (separated by LH type)
-phi_Pa_Mb = post_subset(post, "^phi_Pa_Mb[", matrix = TRUE)
-
-# migration survival (separated by LH type, but assumed constant)
-phi_Mb_Ma = post_subset(post, "^phi_Mb_Ma[", matrix = TRUE)
-
-##### STEP 2: DEFINE A FUNCTION TO CALCULATE THE DESIRED STATS FOR A GIVEN POSTERIOR SAMPLE #####
-f = function(i) {
-  # put the values from this draw into the format used in the model
-  Pb_i = array_format(Pb[i,])
-  Ma_i = array_format(Ma[i,])
-  phi_Pa_Mb_i = array_format(phi_Pa_Mb[i,])[,i_spring,]
-  phi_Mb_Ma_i = array_format(phi_Mb_Ma[i,])[,i_spring,o_nor,]
-
-  # calculate hypothetical NOR smolt reaching LGR if all parr were spring migrants
-  Ma_tot_hyp_i = Pb_i * phi_Pa_Mb_i * phi_Mb_Ma_i
-
-  # calculate actual NOR smolt reaching LGR
-  Ma_tot_real_i = Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]
-
-  # add columns storing the aggregate across populations
-  Ma_tot_hyp_i = cbind(Ma_tot_hyp_i, rowSums(Ma_tot_hyp_i))
-  Ma_tot_real_i = cbind(Ma_tot_real_i, rowSums(Ma_tot_real_i))
-
-  # calculate the ratios between the actual and hypothetical
-  mean_p_ratio = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
-  cv_ratio = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)
-
-  names(mean_p_ratio) = paste0("mean_p_ratio[", 1:5, "]")
-  names(cv_ratio) = paste0("cv_ratio[", 1:5, "]")
-  c(mean_p_ratio, cv_ratio)
-}
-
-##### STEP 3: APPLY FUNCTION TO ALL POSTERIOR SAMPLES, FORMAT, AND SUMMARIZE #####
-
-# apply
-ratio_out = t(sapply(1:nrow(Pb), f))
-
-# format
-ratio_post = post_convert(cbind(postpack:::id_mat(post), ratio_out))
-
-# summarize
-mean_summ = post_summ(ratio_post, "mean")
-cv_summ = post_summ(ratio_post, "cv")
-
-# format the summaries for barplotting
-mns = rbind(mean_summ["mean",], cv_summ["mean",])
-lwrs = rbind(mean_summ["2.5%",], cv_summ["2.5%",])
-uprs = rbind(mean_summ["97.5%",], cv_summ["97.5%",])
-
-# set the colors
-cols = c("grey50", "grey80")
-
-# make the plot
-mypar(mfrow = c(1,1), col.axis = "black")
-mp = barplot(mns, beside = TRUE, names.arg = c(pops, "TOTAL"),
-             ylim = c(0, 1.35), border = NA, col = cols)
-
-# draw error bars
-segments(mp, lwrs, mp, uprs)
-
-# draw x-axis
-segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
-axis_labels("Population", "Without:With Fall Migrant Strategy")
-
-# draw a reference line
-abline(h = 1, lty = 2)
-
-# draw a legend
-legend("topright", title = "LGR Smolt", legend = c("Mean", "CV"), pch = 15,
-       col = cols, pt.cex = 1.5, bty = "n", text.col = par("col.axis"), cex = 0.8)
-```
-
-\newpage
+
+WUL_change_fig_caption = "
+  Density-dependent survival relationships from egg (panels a-d) and parr (panels e-f) to smolt arriving at Lower Granite Dam (LGR) under current (solid lines) and increased (dashed lines) weighted usable habitat (WUL).
+  Egg $\\to$ LGR survival includes density effects that are both direct (e.g., egg survival varies as a function of egg density) and indirect (parr size varies as a function of egg density, and survival varies with size), whereas parr $\\to$ LGR survival includes only the indirect density effects.
+"
+```
 
@@
 
-```{r corr-compare-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(corr_compare_caption), eval = params$corr_compare_fig}
+```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
+solid_col = "grey30"
+tranp_col = alpha(solid_col, 0.25)
+pt_cex = 1.3
+
+##### EGG-TO-PARR SURVIVAL VS. EGG DENSITY #####
+
+phi_E_Pa_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of total egg production by brood year
+  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
+
+  # extract posterior summaries of egg to parr survival rates
+  phi_E_Pb = post_summ(post, sub_index("^phi_E_Pb[.+,pop]", pop = j))
+
+  # extract posterior samples of the BH parameters
+  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
+
+  # construct vector of egg abundances to predict at
+  E_pred = seq(0.1, max(E[1,]), length = 30)
+
+  # obtain predicted curves for each posterior sample
+  phi_E_Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) 1/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
+
+  # obtain posterior summary of predicted curve
+  colnames(phi_E_Pb_pred) = paste0("phi_E_Pb_pred[", 1:length(E_pred), "]")
+  phi_E_Pb_pred = post_convert(cbind(postpack:::id_mat(post), phi_E_Pb_pred))
+  phi_E_Pb_pred = post_summ(phi_E_Pb_pred, "phi_E_Pb_pred")
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = c(0, max(E[1,]))
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(0, phi_E_Pb["mean",], phi_E_Pb_pred["2.5%",], phi_E_Pb_pred["97.5%",])
+
+  # empty plot with correct dimensions
+  plot(phi_E_Pb["mean",] ~ E["mean",],
+       ylim = ylim,
+       xlim = xlim, type = "n",
+       xaxt = "n")
+
+  # panel label
+  panel_label(paste0("(", paste0("a", j), ")"), "topright", y_inp = 0.075)
+
+  # draw prettier x-axis
+  x_ticks = axisTicks(par("usr")[1:2], log = F)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+  # add credible region for predicted curve
+  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred["2.5%",], rev(phi_E_Pb_pred["97.5%",])), col = tranp_col, border = NA)
+
+  # add posterior mean predicted curve
+  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+
+  # add posterior mean of realized pairs
+  points(phi_E_Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### PARR RECRUITMENT VS. EGG PRODUCTION #####
+
+Pb_VS_E = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of total egg production by brood year
+  E = post_summ(post, sub_index("^E[.+,pop]", pop = j))
+
+  # extract posterior summaries of total parr production by brood year
+  Pb = post_summ(post, sub_index("^Pb[.+,pop]", pop = j))
+
+  # extract posterior samples of the BH parameters
+  bh_params = post_subset(post, sub_index(c("alpha[pop]", "^beta[pop]$"), pop = j), matrix = TRUE)
+
+  # construct vector of egg abundances to predict at
+  E_pred = seq(0.1, max(E[1,]), length = 30)
+
+  # obtain predicted curves for each posterior sample
+  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) E_pred/((1/bh_params[i,1]) + E_pred/bh_params[i,2])))
+
+  # obtain posterior summary of predicted curve
+  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(E_pred), "]")
+  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
+  Pb_pred = post_summ(Pb_pred, "Pb_pred")
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = c(0, max(E[1,]))
+
+  # set yaxis limit
+  if (is.null(ylim)) ylim = c(0, max(Pb[1,]))
+
+  # empty plot with correct dimensions
+  plot(Pb["mean",] ~ E["mean",],
+       ylim = ylim,
+       xlim = xlim, type = "n",
+       xaxt = "n",
+       yaxt = "n")
+
+  # panel label
+  panel_label(paste0("(", paste0("b", j), ")"), "topright", y_inp = 0.075)
+
+  # draw prettier x-axis
+  x_ticks = axisTicks(par("usr")[1:2], log = F)
+  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
+
+  # draw prettier y-axis
+  y_ticks = axisTicks(par("usr")[3:4], log = F)
+  axis(side = 2, at = y_ticks, labels = y_ticks/1e3)
+
+  # add credible region for predicted curve
+  polygon(c(E_pred, rev(E_pred)), c(Pb_pred["2.5%",], rev(Pb_pred["97.5%",])), col = tranp_col, border = NA)
+
+  # add posterior mean predicted curve
+  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+
+  # add posterior mean of realized pairs
+  points(Pb["mean",] ~ E["mean",], pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### PARR SIZE VS. EGG DENSITY #####
+
+L_Pb_VS_E_per_WUL = function(j, xlim = NULL, ylim = NULL) {
+  # obtain posterior samples of total egg abundance scaled to WUL
+  E = post_subset(post, sub_index("^E[.+,pop]", pop = j), matrix = TRUE)
+  E_scaled = (E/jags_data$E_scale)/jags_data$wul[j]
+  colnames(E_scaled) = gsub("E", "E_scaled", x = colnames(E_scaled))
+  post_E = post_convert(cbind(postpack:::id_mat(post), E_scaled))
+
+  # summarize scaled egg abundance
+  E_scaled_mean = post_summ(post_E, "E_scaled")["mean",]
+
+  # create a vector of scaled egg abundances to predict at
+  E_scaled_seq = seq(min(E_scaled_mean), max(E_scaled_mean), length = 30)
+
+  # extract posteriors of coefficients
+  omega0 = post_subset(post, sub_index("omega0[pop]", pop = j), matrix = TRUE)
+  omega1 = post_subset(post, sub_index("omega1[pop]", pop = j), matrix = TRUE)
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[.+,pop]", pop = j))["mean",]
+
+  # function to create predicted survival curves for one posterior sample
+  pred_fn = function(i) {
+    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
+    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
+    pred_L_Pb
+  }
+
+  # calculate predicted length
+  pred_L_Pb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Pb = post_convert(cbind(postpack:::id_mat(post), pred_L_Pb))
+
+  # extract summarized predicted length
+  pred_L_Pb_mean = post_summ(post_pred_L_Pb, ".")["mean",]
+  pred_L_Pb_lwr = post_summ(post_pred_L_Pb, ".")["2.5%",]
+  pred_L_Pb_upr = post_summ(post_pred_L_Pb, ".")["97.5%",]
+
+  E_scaled_seq = (E_scaled_seq * jags_data$wul[j] * jags_data$E_scale)/1e6
+  E_scaled_mean = (E_scaled_mean * jags_data$wul[j] * jags_data$E_scale)/1e6
+
+  # set xaxis limit
+  if (is.null(xlim)) xlim = range(0, E_scaled_seq)
+
+  # set yaxis limit
+  if (is.null(ylim)) ylim = range(L_Pb_mean, pred_L_Pb_lwr, pred_L_Pb_upr, na.rm = TRUE)
+
+  # empty plot with correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("c", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean predicted curve
+  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(L_Pb_mean ~ E_scaled_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### OVERWINTER SURVIVAL VS. PARR SIZE #####
+
+phi_Pa_Mb_VS_L_Pb = function(j, i, xlim = NULL, ylim = NULL) {
+
+  pch = c(21, 23)
+  lty = c(1, 2)
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # obtain scaled/centered versions
+  L_Pb_star_mean = (L_Pb_mean - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # summarize posterior of overwinter survival outcomes
+  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[.+,LH_type,pop]", pop = j, LH_type = i))["mean",])[-1,i,j]
+
+  # create vector of lengths to predict at
+  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
+  L_Pb_star_seq = seq(min(L_Pb_star_mean), max(L_Pb_star_mean), length = 30)
+
+  # extract posteriors of coefficients
+  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
+    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
+    pred_phi_Pa_Mb
+  }
+
+  # calculate predicted survivals and add to posterior samples
+  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))
+
+  # summarize predicted survival
+  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
+  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
+  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Pb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(0, pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_mean)
+
+  # empty plot with correct dimensions
+  if (i == 1) {
+    plot(1,1, type = "n", 
+         ylim = ylim,
+         xlim = xlim,
+         xlab = "", ylab = ""
+    )
+  }
+
+  # panel label
+  panel_label(paste0("(", paste0("d", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean predicted curve
+  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2, lty = lty[i])
+
+  # add posterior mean of realized pairs
+  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = pch[i], col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  legend_pop = 2
+  if (j == legend_pop & i == 1) {
+    legend("topleft", legend = c("Fall", "Spring"), title = "Mig. Type", pch = pch, pt.bg = tranp_col, col = solid_col, pt.cex = pt_cex, cex = 0.8, bty = "n")
+  }
+
+  # draw boundary box
+  box()
+}
+
+##### SMOLT SIZE VS PARR SIZE #####
+
+L_Mb_VS_L_Pb = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of summer length outcomes
+  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # create a vector of scaled summer lengths to predict at
+  L_Pb_seq = seq(min(L_Pb_mean), max(L_Pb_mean), length = 30)
+  L_Pb_star_seq = (L_Pb_seq - jags_data$L_Pb_center[j])/jags_data$L_Pb_scale[j]
+
+  # extract posteriors of coefficients
+  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
+  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted curves for one posterior sample
+  pred_fn = function(i) {
+    pred_L_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq) * L_Pb_seq
+    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "1]")
+    pred_L_Mb
+  }
+
+  # calculate predicted growth values and add to posterior samples
+  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))
+
+  # summarize predicted growth
+  pred_L_Mb_mean = post_summ(post_pred_L_Mb, ".")["mean",]
+  pred_L_Mb_lwr = post_summ(post_pred_L_Mb, ".")["2.5%",]
+  pred_L_Mb_upr = post_summ(post_pred_L_Mb, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Pb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_mean, na.rm = TRUE)
+
+  # empty plot with the correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim, 
+       xlab = "", ylab = ""
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("e", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean of predicted curve
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(L_Mb_mean ~ L_Pb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+
+  # draw boundary box
+  box()
+}
+
+##### SURVIVAL TO LGR VS. SMOLT SIZE #####
+
+phi_Mb_Ma_VS_L_Mb = function(j, xlim = NULL, ylim = NULL) {
+
+  # extract posterior summaries of spring length outcomes
+  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ".+", pop = j))["mean",]
+
+  # obtain scaled/centered versions
+  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
+
+  # summarize posterior of migration to LGR survival outcomes
+  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[.+,LH_type,origin,pop]", pop = j, LH_type = 1, origin = 1))["mean",])[-1,1,1,j]
+
+  # create vectors to predict survival at: for credible regions and mean curve
+  L_Mb_seq = seq(min(L_Mb_mean), max(L_Mb_mean), length = 30)
+  L_Mb_star_seq = seq(min(L_Mb_star_mean), max(L_Mb_star_mean), length = 30)
+
+  # extract posteriors of coefficients
+  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
+  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)
+
+  # function to create predicted survival curve for one posterior sample
+  pred_fn = function(i) {
+    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
+    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
+    pred_phi_Mb_Ma
+  }
+
+  # calculate predicted survivals for each posterior sample
+  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
+  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))
+
+  # summarize predicted survival
+  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
+  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
+  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]
+
+  # set xaxis limits
+  if (is.null(xlim)) xlim = range(L_Mb_seq)
+
+  # set yaxis limits
+  if (is.null(ylim)) ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_mean)
+
+  # empty plot with correct dimensions
+  plot(1,1, type = "n", 
+       ylim = ylim,
+       xlim = xlim,
+       xlab = "", ylab = ""
+  )
+
+  # panel label
+  panel_label(paste0("(", paste0("f", j), ")"), "topright", y_inp = 0.075)
+
+  # add credible region for predicted curve
+  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tranp_col)
+
+  # add posterior mean of predicted curve
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col, lwd = 2)
+
+  # add posterior mean of realized pairs
+  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 21, col = solid_col, bg = tranp_col, cex = pt_cex)
+}
+
+##### LARGE MULTI-PANEL PLOT #####
+
+make_layout = function(nrow, ncol, show = FALSE) {
+  m = NULL
+  for (r in 1:nrow) {
+    if (r == 1) {
+      f = 1
+    } else {
+      f = max(m) + 1
+    }
+    l = f+ncol-1
+    tmp = rbind(f:l, rep(l+1, ncol))
+    m = rbind(m, tmp)
+  }
+  layout(m, heights = rep(c(1, 0.25), nrow))
+  if (show) layout.show(max(m))
+}
+
+g = function(ylim = c(-3,3), xlim = c(-3,3)) {
+  x = rnorm(30)
+  y = rnorm(30)
+  plot(y ~ x, xlab = "", ylab = "", xlim = xlim, ylim = ylim)
+}
+
+yaxis_label = function(label_main, label_sub) {
+  mtext(side = 2, outer = FALSE, label_main, line = 2.25, cex = 0.9)
+  mtext(side = 2, outer = FALSE, label_sub, line = 1.25, cex = 0.75, font = 3)
+}
+
+xaxis_label = function(label) {
+  plot(1, 1, type = "n", xlim = c(0,1), ylim = c(0,1), axes = FALSE)
+  text(0.5, 0.3, label = label, cex = 1.25, xpd = TRUE)
+}
+
+make_layout(nrow = 6, ncol = 4, show = FALSE)
+
+par(mar = c(0.5,1.5,0,0), oma = c(0,2,1.5,1), tcl = 0, mgp = c(200,0.05,0),
+    lend = "square", ljoin = "mitre")
+
+# egg to parr survival vs. egg density
+# ylim = make_lim(post_summ(post, "^phi_E_Pb[")["mean",])
+ylim = c(0,0.4)
+xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  phi_E_Pa_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Egg \u2192 Parr Survival", "")
+  mtext(side = 3, outer = FALSE, line = 0, pops[j], font = 2)
+}); xaxis_label("Total Egg Production (Millions)")
+
+# parr recruitment vs. total egg production
+ylim = make_lim(post_summ(post, "^Pb[")["mean",]); ylim[1] = 0
+xlim = make_lim(post_summ(post, "^E[")["mean",]); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  Pb_VS_E(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr Recruitment", "Thousands")
+}); xaxis_label("Total Egg Production (Millions)")
+
+# parr size vs. egg production
+ylim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+xlim = make_lim(post_summ(post, "^E[")["mean",]/1e6); xlim[1] = 0
+junk = sapply(1:4, function(j) {
+  L_Pb_VS_E_per_WUL(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr Mean Length", "mm")
+}); xaxis_label("Total Egg Production (Millions)")
+
+# overwinter survival vs. parr size
+ylim = make_lim(post_summ(post, "^phi_Pa_Mb[")["mean",])
+xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+junk = sapply(1:4, function(j) {
+  phi_Pa_Mb_VS_L_Pb(j, 1, xlim = xlim, ylim = ylim)
+  phi_Pa_Mb_VS_L_Pb(j, 2, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Parr \u2192 Smolt Survival", "")
+}); xaxis_label("Parr Mean Length (mm)")
+
+# smolt size vs. parr size
+xlim = make_lim(post_summ(post, "^L_Pb[")["mean",])
+ylim = make_lim(post_summ(post, "^L_Mb[")["mean",])
+junk = sapply(1:4, function(j) {
+  L_Mb_VS_L_Pb(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Smolt Mean Length", "mm")
+}); xaxis_label("Parr Mean Length (mm)")
+
+# migration to LGR vs. smolt size
+xlim = make_lim(post_summ(post, "^L_Mb[")["mean",])
+ylim = make_lim(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = "1", origin = 1, pop = ".")))
+
+junk = sapply(1:4, function(j) {
+  phi_Mb_Ma_VS_L_Mb(j, xlim = xlim, ylim = ylim)
+  if (j == 1) yaxis_label("Smolt \u2192 LGR Survival", "")
+}); xaxis_label("Smolt Mean Length (mm)")
+
+```
+
+\newpage
+
+```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE, eval = params$beta_fig}
+# extract posterior summaries of the capacity parameters
+beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))
+
+# extract posterior samples of the slope parameter
+beta_per = post_subset(post, "lambda", TRUE)
+
+# create a sequence of WUL values to predict capacity at
+wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)
+
+# obtain the regression line for each posterior sample
+pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))
+
+# summarize posterior of regression line
+pred_beta_summ = apply(pred_beta, 2, function(x) c(mean = mean(x), quantile(x, c(0.025, 0.1, 0.5, 0.9, 0.975))))
+
+# empty plot with correct labeling/dimensions
+mypar(mfrow = c(1,1), col.axis = "black")
+plot(1,1, type = "n", xlim = range(wul_seq),
+     # ylim = c(0, max(beta_ests["97.5%",], pred_beta_summ["97.5%",])),
+     ylim = c(0, 3000) * 1000,
+     xlab = "",
+     ylab = "", yaxt = "n")
+
+# draw prettier y-axis
+at_y = c(0, 1000, 2000, 3000) * 1000
+axis(side = 2, at = at_y, labels = at_y/1000)
+usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
+
+# draw the regression uncertainty
+polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["2.5%",], rev(pred_beta_summ["97.5%",])), border = NA, col = tranp_col)
+polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["10%",], rev(pred_beta_summ["90%",])), border = NA, col = tranp_col)
+
+# draw the posterior mean regression line
+lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)
+
+# draw the population-specific capacity estimates w/error bars and labels
+segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)
+
+# draw the population labels
+xoff = 0.015
+yoff = 0.03
+text(x = jags_data$wul      + xdiff * c(1.5,-1,1,1) * xoff,
+     y = beta_ests["mean",] + ydiff * c(1,-1,1,1) * yoff,
+     labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,2,2), font = 1, cex = 0.8)
+
+# add axis labels
+axis_labels("Weighted Usable Habitat Length (km)", "Parr Capacity (Thousands)")
+```
+
+\newpage
+
+```{r corr-compare-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(corr_compare_caption), eval = params$corr_compare_fig, time_it = TRUE}
 
@@
 
+\newpage
+
+```{r WUL-change-fig, fig.width = 7.2, fig.height = 4.5, eval = params$WUL_change_fig, fig.cap = WUL_change_fig_caption, time_it = TRUE}
+
+prep_samples = function(j) {
+
+  # the parameters needed to calucate process model expected values
+  the_params = c("alpha[pop]", "beta[pop]", "^lambda$",
+                 "omega0[pop]", "omega1[pop]", "mu_pi[1,pop]",
+                 "gamma0[1,pop]", "gamma1[1,pop]",
+                 "gamma0[2,pop]", "gamma1[2,pop]",
+                 "theta0[pop]", "theta1[pop]",
+                 "tau0[pop]", "tau1[pop]"
+  )
+
+  # extract the posterior samples for all of these parameters for this population
+  the_samps = post_subset(post, sub_index(the_params, pop = j), matrix = TRUE)
+
+  # handle the names
+  the_names = postpack:::drop_index(names(the_samps[1,]))
+  the_names[which(the_names == "gamma0")] = paste0("gamma0", c("_fall", "_spring"))
+  the_names[which(the_names == "gamma1")] = paste0("gamma1", c("_fall", "_spring"))
+  colnames(the_samps) = the_names
+
+  return(the_samps)
+}
+
+prep_sample = function(the_samps, i, j) {
+  c(the_samps[i,],
+    WUL = unname(jags_data$wul[j]),
+    E_scale = unname(jags_data$E_scale),
+    L_Pb_scale = unname(jags_data$L_Pb_scale[j]),
+    L_Pb_center = unname(jags_data$L_Pb_center[j]),
+    L_Mb_scale = unname(jags_data$L_Mb_scale[j]),
+    L_Mb_center = unname(jags_data$L_Mb_center[j])
+    )
+}
+
+get_phi_hat = function(x, E, WUL_change = 0, start = "E") {
+  with(as.list(c(x, E = E, WUL_change = WUL_change)), {
+    beta_hat = lambda * WUL
+
+    WUL_new = WUL * (1 + WUL_change)
+    beta_hat_new = lambda * WUL_new
+    beta_new = beta_hat_new * (beta/beta_hat)
+
+    phi_E_Pb = 1/(1/alpha + E/beta_new)
+    Pb = E * phi_E_Pb
+
+    L_Pb = exp(omega0 + omega1 * log((E/E_scale)/WUL_new))
+    L_Pb_star = (L_Pb - L_Pb_center)/L_Pb_scale
+
+    Pa_fall = Pb * mu_pi
+    Pa_spring = Pb * (1 - mu_pi)
+
+    phi_Pa_Mb_fall = plogis(gamma0_fall + gamma1_fall * L_Pb_star)
+    phi_Pa_Mb_spring = plogis(gamma0_spring + gamma1_spring * L_Pb_star)
+
+    Mb_fall = Pa_fall * phi_Pa_Mb_fall
+    Mb_spring = Pa_spring * phi_Pa_Mb_spring
+
+    Delta = exp(theta0 + theta1 * L_Pb_star)
+
+    L_Mb = L_Pb * Delta
+    L_Mb_star = (L_Mb - L_Mb_center)/L_Mb_scale
+
+    phi_Mb_Ma = plogis(tau0 + tau1 * L_Mb_star)
+
+    Ma_fall = Mb_fall * phi_Mb_Ma
+    Ma_spring = Mb_spring * phi_Mb_Ma
+    Ma = Ma_fall + Ma_spring
+
+    if (start == "E") out = Ma/E
+    if (start == "Pb") out = Pb/E
+    return(out)
+  })
+}
+
+get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E") {
+
+  the_samps = prep_samples(j = j)
+
+  out = sapply(1:nrow(the_samps), function(i) {
+    x = prep_sample(the_samps, i = i, j = j)
+    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start))
+  })
+
+  out = t(out)
+  colnames(out) = paste0("var", 1:ncol(out))
+
+  postpack::post_convert(cbind(postpack:::id_mat(post), out))
+}
+
+get_phi_real_post = function(j, start = "E") {
+
+  if (start == "E") start_param = "^E[.+,pop]"
+  if (start == "Pb") start_param = "^Pb[.+,pop]"
+
+  Ma_fall = post_subset(post, sub_index("^Ma[.+,1,1,pop]", pop = j), matrix = TRUE)
+  Ma_spring = post_subset(post, sub_index("^Ma[.+,2,1,pop]", pop = j), matrix = TRUE)
+  start_out = post_subset(post, sub_index(start_param, pop = j), matrix = TRUE)
+
+  phi = (Ma_fall + Ma_spring)/start_out
+
+  colnames(phi) = paste0("var", 1:ncol(phi))
+  postpack::post_convert(cbind(postpack:::id_mat(post), phi))
+}
+
+plot_f = function(j, start, WUL_change) {
+  phi_real_post = get_phi_real_post(j = j, start = start)
+  phi_real = post_summ(phi_real_post, ".")
+  E_real = post_summ(post, sub_index("^E[.+,pop]", pop = j))
+  E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)
+
+  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start)
+  phi_hat = post_summ(phi_hat_post, ".")
+  phi_hat_new_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_change, start = start)
+  phi_hat_new = post_summ(phi_hat_new_post, ".")
+
+  plot(phi_real["mean",] ~ E_real["mean",], type = "n",
+       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),],
+                phi_hat_new[c("2.5%","97.5%"),]),
+                # phi_real["mean",]),
+       # ylim = make_lim(0, ifelse(start == "E", 0.075, 0.3)),
+       xlim = c(0, max(E_real["mean",], E_pred)),
+       xaxt = "n")
+
+  # points(phi_real["mean",] ~ E_real["mean",], pch = 21, 
+  #        col = "black", bg = scales::alpha("grey25", 0.25), cex = 0.8)
+
+  polygon(x = c(E_pred, rev(E_pred)), 
+          y = c(phi_hat["2.5%",], rev(phi_hat["97.5%",])),
+          col = tranp_col, border = NA)
+  lines(phi_hat["mean",] ~ E_pred, lwd = 2)
+  lines(phi_hat["2.5%",] ~ E_pred)
+  lines(phi_hat["97.5%",] ~ E_pred)
+
+  polygon(x = c(E_pred, rev(E_pred)), 
+          y = c(phi_hat_new["2.5%",], rev(phi_hat_new["97.5%",])),
+          col = tranp_col, border = NA)
+  lines(phi_hat_new["mean",] ~ E_pred, lwd = 2, lty = 2)
+  lines(phi_hat_new["2.5%",] ~ E_pred,  lty = 2)
+  lines(phi_hat_new["97.5%",] ~ E_pred, lty = 2)
+  at_x = axisTicks(par("usr")[1:2], log = FALSE)
+  axis(side = 1, at = at_x, labels = at_x/1e6)
+  panel_label(paste0("(", letters[ifelse(start == "E", 0, 3) + j], ") ", pops[j]))
+
+  if (j == 1) {
+    if (start == "E") {
+      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 1)
+      legend("topright", title = "WUL", legend = c("Current", paste0("\u2191", WUL_change * 100, "%")), lty = c(1,2), seg.len = 1.5, bty = "n", cex = 0.8)
+    } 
+    if (start == "Pb") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 1)
+  }
+
+}
+
+mypar(mfrow = c(2,4), col.axis = "black")
+junk = sapply(1:4, function(j) plot_f(j, "E", 1))
+junk = sapply(1:4, function(j) plot_f(j, "Pb", 1))
+axis_labels(xlab = "Egg Production (Millions)")
+```
+
+\newpage
+
+```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE, eval = params$no_fall_fig}
+cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}
+
+##### STEP 1: EXTRACT POSTERIOR SAMPLES OF QUANTITIES NEEDED #####
+
+# total parr recruitment (regardless of LH type)
+Pb = post_subset(post, "^Pb[", matrix = TRUE)
+
+# total smolt at LGR (separated by LH type)
+Ma = post_subset(post, "^Ma[", matrix = TRUE)
+
+# overwinter survival (separated by LH type)
+phi_Pa_Mb = post_subset(post, "^phi_Pa_Mb[", matrix = TRUE)
+
+# migration survival (separated by LH type, but assumed constant)
+phi_Mb_Ma = post_subset(post, "^phi_Mb_Ma[", matrix = TRUE)
+
+##### STEP 2: DEFINE A FUNCTION TO CALCULATE THE DESIRED STATS FOR A GIVEN POSTERIOR SAMPLE #####
+f = function(i) {
+  # put the values from this draw into the format used in the model
+  Pb_i = array_format(Pb[i,])
+  Ma_i = array_format(Ma[i,])
+  phi_Pa_Mb_i = array_format(phi_Pa_Mb[i,])[,i_spring,]
+  phi_Mb_Ma_i = array_format(phi_Mb_Ma[i,])[,i_spring,o_nor,]
+
+  # calculate hypothetical NOR smolt reaching LGR if all parr were spring migrants
+  Ma_tot_hyp_i = Pb_i * phi_Pa_Mb_i * phi_Mb_Ma_i
+
+  # calculate actual NOR smolt reaching LGR
+  Ma_tot_real_i = Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]
+
+  # add columns storing the aggregate across populations
+  Ma_tot_hyp_i = cbind(Ma_tot_hyp_i, rowSums(Ma_tot_hyp_i))
+  Ma_tot_real_i = cbind(Ma_tot_real_i, rowSums(Ma_tot_real_i))
+
+  # calculate the ratios between the actual and hypothetical
+  mean_p_ratio = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
+  cv_ratio = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)
+
+  names(mean_p_ratio) = paste0("mean_p_ratio[", 1:5, "]")
+  names(cv_ratio) = paste0("cv_ratio[", 1:5, "]")
+  c(mean_p_ratio, cv_ratio)
+}
+
+##### STEP 3: APPLY FUNCTION TO ALL POSTERIOR SAMPLES, FORMAT, AND SUMMARIZE #####
+
+# apply
+ratio_out = t(sapply(1:nrow(Pb), f))
+
+# format
+ratio_post = post_convert(cbind(postpack:::id_mat(post), ratio_out))
+
+# summarize
+mean_summ = post_summ(ratio_post, "mean")
+cv_summ = post_summ(ratio_post, "cv")
+
+# format the summaries for barplotting
+mns = rbind(mean_summ["mean",], cv_summ["mean",])
+lwrs = rbind(mean_summ["2.5%",], cv_summ["2.5%",])
+uprs = rbind(mean_summ["97.5%",], cv_summ["97.5%",])
+
+# set the colors
+cols = c("grey50", "grey80")
+
+# make the plot
+mypar(mfrow = c(1,1), col.axis = "black")
+mp = barplot(mns, beside = TRUE, names.arg = c(pops, "TOTAL"),
+             ylim = c(0, 1.35), border = NA, col = cols)
+
+# draw error bars
+segments(mp, lwrs, mp, uprs)
+
+# draw x-axis
+segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
+axis_labels("Population", "Without:With Fall Migrant Strategy")
+
+# draw a reference line
+abline(h = 1, lty = 2)
+
+# draw a legend
+legend("topright", title = "LGR Smolt", legend = c("Mean", "CV"), pch = 15,
+       col = cols, pt.cex = 1.5, bty = "n", text.col = par("col.axis"), cex = 0.8)
+```
+
 \clearpage

### 2023-08-16 100-math-description/GR-sslcm-math-description.Rmd
Revise text for updated PS survival handling

@@
 
-It is well-known that some potential spawners die prior to spawning; these "pre-spawn survival" outcomes, denoted by $\phi^{S^{b} \to S^{a}}_{y,j}$, were modeled as having time-constant values (i.e., all $\phi^{S^{b} \to S^{a}}_{y,j} = \dot{\phi}^{S^{b} \to S^{a}}_{j}$) for each population.
-The initial desire was to allow for time-varying pre-spawn survival probabilities, but it was discovered that the observational data (counts of spawned vs.
-gravid female carcasses, see eq.
-\@ref(eq:prespawn-surv-data)) were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
+It is well-known that some potential spawners die prior to spawning [e.g., @bowerman-etal-2021]; these "pre-spawn survival" outcomes are denoted by $\phi^{S^{b} \to S^{a}}_{y,j}$.
+The initial desire was to allow for the model to internally estimate time-varying pre-spawn survival probabilities, but it was discovered that the observational data (counts of spawned vs.
+gravid female carcasses) were not informative enough for all populations to prevent parameter confounding with egg-to-parr survival.
+As alternative, binary logistic regression models were fitted that included year-specific random effects around a time-constant expected value (one per population; success represented by year-specific counts of spawned female carcasses, trials represented by total female carcasses examined) and the resulting time- and population-varying estimates were supplied to the model as known without error.
+The abundance of adults spawning successfully was then:
 
@@
 
-The adult observation model relied on three primary data types: (_i_) total abundance of adult returns to the natal tributaries, (_ii_) information about survival on the upstream migration between LGR and BON as well as on the spawning grounds, and (_iii_) composition data to inform the relative abundance of adults of different ages and origins returning each year.
+The adult observation model relied on three primary data types: (_i_) total abundance of adult returns to the natal tributaries, (_ii_) information about survival on the upstream migration between LGR and BON, and (_iii_) composition data to inform the relative abundance of adults of different ages and origins returning each year.
 
@@
 (\#eq:upstream-surv-data)
-\end{equation}
-
-The other survival data set informing the freshwater adult observation model was for spawning success, i.e., pre-spawn survival.
-Surveyors in annual spawning ground carcass surveys have recorded counts of total females encountered ($\hat{x}^{\mathrm{carcass,total}}_{y,j}$) and counts of those found to have successfully spawned ($\hat{x}^{\mathrm{carcass,spawned}}_{y,j}$; `r highlight("REPORT CITATION NEEDED")`).
-These counts were treated as binomial random variables to build the likelihood:
-
-\begin{equation}
-\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \Bdist\left(\phi^{S^{b} \to S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
-(\#eq:prespawn-surv-data)
 \end{equation}

### 2023-08-16 100-math-description/GR-sslcm-math-description.Rmd

@@
 
-Much research has been devoted to studying the survival of Chinook salmon smolts migrating through the hydrosystem on the Snake and Columbia rivers. 
-In particular, the Comparative Survival Study has tracked the survival of a variety of tagging groups going back to the early 2000s; estimates from a recent report [@mccann-etal-2020, Table A.1 on page A-20 therein] were used to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
-Provided by @mccann-etal-2020 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\NOR}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\HOR}$ here).
+Much research has been devoted to studying the survival of Chinook salmon smolt migrating through the hydrosystem on the Snake and Columbia rivers. 
+In particular, the Comparative Survival Study has tracked the survival of a variety of tagging groups going back to the early 2000s; estimates from a recent report [@mccann-etal-2022, Table A.1] were used to serve as empirical observations (with estimates of uncertainty) with which to inform this component of our model.
+Provided by @mccann-etal-2022 are annual estimates of in-stream survival along the migration from LGR through Bonneville Dam (BON); separate time series are available for natural-origin (we used the "Aggregate Wild Chinook" estimates as none were available for Grande Ronde populations only, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\NOR}$ here) and for hatchery-origin (we used the "Catherine Creek AP" estimates, denoted $\hat{\phi}^{M^{a} \to O^{0}}_{y,o=\HOR}$ here).
 These estimates were treated as representative of the survival for each population, which implies an assumption that the different populations experienced similar conditions during this migration and attributes all variability to either random process or observation noise (i.e., no factors known to influence hydrosystem survival such as size, flood pulses, barging intensity were included).

### 2023-08-17 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Improve MCMC diagnostics Rmd section
* Better text
* Ditched %>% for |>
* Plot consistencies

@@
 Values in cells represent the percentage of parameters of a given type that fail a diagnostic check.
-E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05.
+E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had Rhat values greater than 1.05.
 Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.
 
-* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution.
-Values close to 1 are ideal but values greater than 1.2 should be considered not well-converged (general rules of thumb).
+All convergence diagnostics were calculated using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which implements updated versions (based on rank-normalization) of the classical convergence diagnostics (presented in Vehtari et al.
+[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
+
+* **Rhat** measures convergence of multiple chains to a common target distribution. Values close to 1 are better -- we've chosen these approximate categories for ease of interpretation: 
+  * _Ideal_: [1,1.01] 
+  * _No Issue_: (1.01,1.05]
+  * _Acceptable_: (1.05,1.1]
+  * _Potential Concern_: (1.1,1.2]
+  * _Definite Concern_: (1.2,100)
 * **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
 Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggests 400 as a good rule of thumb.
+([2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)) suggests 400 as a good rule of thumb.
 * **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI.
-Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has deemed an acceptable level of imprecision.
-
-The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
+Percentages shown represent the fraction of parameters that have greater than 5% MCCV, which we have deemed an acceptable level of imprecision.
 
@@
 # produce the kable
-kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
-  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
-  column_spec(2:3, width = "150px") %>%
-  column_spec(c(4,8,11), border_right = TRUE) %>%
-  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
-  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
-  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
-  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
-  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
-  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
-  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
-  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
-  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
-  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
+kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) |>
+  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) |>
+  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) |>
+  column_spec(2:3, width = "150px") |>
+  column_spec(c(4,8,11), border_right = TRUE) |>
+  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) |>
+  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) |>
+  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) |>
+  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) |>
+  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) |>
+  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) |>
+  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) |>
+  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) |>
+  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) |>
+  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) |>
   collapse_rows(columns = 1:2)
@@
 
-## Figures {.tabset .tabset-pills}
+## Figures {.tabset .tabset-dropdown}
 
@@
 rhat_hist = function(rhat) {
-  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
+  # par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
+  mypar(xaxs = "i", yaxs = "i", mfrow = c(1,1))
   breaks = seq(min(rhat), max(rhat), length = 20)
   max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
-  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
+  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, main = "")
+  axis_labels(xlab = TeX("$\\hat{R}$"), ylab = "Frequency")
   usr = par("usr")
-  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
-  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
+  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE, col = par("col.axis"))
+  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
 }
@@
 
-There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
+There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with Rhat in this group. Here is their distribution:
 
@@
 
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest Rhat values in this group are shown.
 
@@
 
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest Rhat values in this group are shown.
 
@@
 
-Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.
+Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest Rhat values in this group are shown.
 

### 2023-08-17 03-post-process/output-plots-children/03-fit-to-data.Rmd
Improve fit to data Rmd section

@@
 
-# Fit to Data {.tabset .tabset-pills}
-
-## Figures {.tabset .tabset-dropdown}
+# Fit to Data {.tabset .tabset-dropdown}
 
@@
 
-### Abundance Data {.tabset .tabset-pills}
+## Abundance Data {.tabset .tabset-dropdown}
 
-#### Fall Parr Abundance
+### Fall Parr Abundance
 
@@
 
-#### Spring Smolt Abundance
+### Spring Smolt Abundance
 
@@
 
-#### Adult Return Abundance
+### Adult Return Abundance
 
@@
 
-### Survival Data {.tabset .tabset-dropdown}
+## Survival Data {.tabset .tabset-dropdown}
 
-#### Summer Parr $\rightarrow$ LGR
+### Summer Parr $\rightarrow$ LGR
 
@@
 
-#### Fall Parr $\rightarrow$ LGR
+### Fall Parr $\rightarrow$ LGR
 
@@
 
-#### Winter Parr $\rightarrow$ LGR
+### Winter Parr $\rightarrow$ LGR
 
@@
 
-#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
+### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}
 
-##### NOR
+#### NOR {-}
 
@@
 
-##### HOR
+#### HOR {-}
 
@@
 
-#### LGR Smolt $\rightarrow$ BON
+### LGR Smolt $\rightarrow$ BON
 
@@
 
-#### BON Adults $\rightarrow$ LGR
+### BON Adults $\rightarrow$ LGR
 
@@
 
-### Composition Data {.tabset .tabset-pills}
+## Composition Data {.tabset .tabset-pills}
 
@@
 
-#### Weir Sampling {.tabset .tabset-dropdown}
+### Weir Sampling {.tabset .tabset-dropdown}
 
@@
 
-##### By Age/Origin {.tabset .tabset-pills}
+#### By Age/Origin {.tabset .tabset-pills}
 
@@
 
-###### CAT
+##### CAT {-}
 
@@
 
-###### LOS
+##### LOS {-}
 
@@
 
-###### MIN
+##### MIN {-}
 
@@
 
-###### UGR
+##### UGR {-}
 
@@
 
-##### By Age {.tabset .tabset-pills}
+#### By Age {.tabset .tabset-pills}
 
@@
 
-##### By Origin {.tabset .tabset-pills}
+#### By Origin {.tabset .tabset-pills}
 
@@
 
-##### Total Sample Size {.tabset .tabset-pills}
+#### Total Sample Size {.tabset .tabset-pills}
 
@@
 
-#### Carcass Sampling {.tabset .tabset-dropdown}
+### Carcass Sampling {.tabset .tabset-dropdown}
 
@@
 
-### Mean Length Data {.tabset .tabset-pills}
+## Mean Length Data {.tabset .tabset-pills}
 
-#### Summer Parr
+### Summer Parr
 
@@
 
-#### Spring Smolt
+### Spring Smolt
 
@@
 ```
-
-```{r pp-check-output, child = "output-plots-children/03a-pp-checks.Rmd", eval = model_info$do_pp_check}
-```
-
-```{r waic-output, child = "output-plots-children/03b-waic.Rmd", eval = model_info$do_lppd}
-```

### 2023-08-17 03-post-process/output-plots.Rmd
Rename Rmd file
Rename parr recruitment Rmd section

@@
     value: TRUE
-  include_egg_to_parr_surv:
-    label: "Include Egg-to-Parr Survival Output?"
     value: TRUE
+  include_parr_recruitment:
+    label: "Include Parr Recruitment Output?"
   include_mean_length:
@@
 
-```{r model-info, child = "output-plots-children/01-model-info.Rmd"}
+```{r model-info, child = "output-plots-children/01-mcmc-dims-runtime.Rmd"}
 ```
@@
 
-```{r egg-to-parr-surv, child = "output-plots-children/04-egg-to-parr-surv.Rmd", eval = params$include_egg_to_parr_surv}
+```{r egg-to-parr-surv, child = "output-plots-children/04-parr-recruitment.Rmd", eval = params$include_parr_recruitment}
 ```

### 2023-08-17 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Improve capacity vs. WUL Rmd section

@@
 
-# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}
+# Parr Capacity vs. Habitat Relationship
 
-## Scatterplot
-
-Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.
+Error bars represent the central 80% of the posterior; grey lines are individual posterior draws of the expected relationship.
 
@@
 
-## Slope Parameter
-
 ```{r beta-v-habitat-slope}
@@
 est = post_summ(post, "^lambda$")
-colnames(est) = "slope"
+colnames(est) = "Slope"
 

### 2023-08-17 03-post-process/output-plots-children/09-equiv-rates.Rmd
Improvements to equivalency rates Rmd section

@@
 
-# Equivilency Rates {.tabset .tabset-pills}
+# Composite Rates {.tabset .tabset-dropdown}
 
-## Smolt-to-Adult Rates {.tabset .tabset-pills}
+The values reported in this section are not directly estimated quantities (i.e., do not have a prior distribution assigned), but rather composite rates that stem from combining multiple life stages together.
+In all cases, the rates were calculated by dividing the number of fish produced by the process by the number of fish that initiated the process.
 
-### LGR to LGR
+These rates are calculated through only brood year `r max(all_yrs[sar_yrs])`, since this is the last brood with of all adult ages (3, 4, and 5) accounted for in the model.
 
-This is survival from $M^{a}$ (smolt at the top of LGR by origin, NOR fish aggregated across migratory strategy type) to $R^{a}$ (adults arriving to LGR).
+## Smolt $\to$ Adult Rates {.tabset .tabset-pills}
 
-The adult portion is calculated across return years, by summing the number of adults of each age that return in the appropriate years.
-For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996.
-The calculation is done for hatchery and natural origin fish separately.
-Only SARs through brood year `r max(all_yrs[sar_yrs])` are calculated, since this is the last brood with of all adult ages (3, 4, and 5) accounted for in the model.
+### BON $\to$ BON
 
-```{r adults-per-smolt, fig.width = p4_width, fig.height = p4_height}
-j = 1
-
-plot_fn = function(j) {
-  # which years had zero hatchery smolt released
-  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
-
-  # summarize rates
-  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
-  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
-
-  # make hatchery values NA in year with no smolt
-  Ra_per_Ma_hor[,zero_hor_smolt] = NA
-
-  # plot natural origin time series
-  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 0.1))
-
-  # add hatchery origin time series
-  add_tseries(est = Ra_per_Ma_hor, yrs = all_yrs[sar_yrs])
-
-  if (j == 2) {
-    legend("topright", legend = origins, title = "Origin",
-           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
-  }
-}
-mypar()
-junk = sapply(1:jags_data$nj, plot_fn)
-axis_labels("Brood Year", "Smolt \u2192 Adult Survival Rate")
-```
-
-### BON to BON
-
-```{r bon-to-bon, fig.width = p4_width, fig.height = p4_height}
+```{r SAR-bon-to-bon, fig.width = p4_width, fig.height = p4_height}
 plot_fn = function(j) {
@@
 
+### LGR $\to$ LGR
+
+```{r SAR-LGR-to-LGR, fig.width = p4_width, fig.height = p4_height}
+plot_fn = function(j) {
+  # which years had zero hatchery smolt released
+  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0
+
+  # summarize rates
+  Ra_per_Ma_nor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_nor, pop = j))
+  Ra_per_Ma_hor = post_summ(post, sub_index("Ra_per_Ma[year,origin,pop]", year = sar_yrs, origin = o_hor, pop = j))
+
+  # make hatchery values NA in year with no smolt
+  Ra_per_Ma_hor[,zero_hor_smolt] = NA
+
+  # plot natural origin time series
+  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 0.1))
+
+  # add hatchery origin time series
+  add_tseries(est = Ra_per_Ma_hor, yrs = all_yrs[sar_yrs])
+
+  if (j == 2) {
+    legend("topright", legend = origins, title = "Origin",
+           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
+  }
+}
+mypar()
+junk = sapply(1:jags_data$nj, plot_fn)
+axis_labels("Brood Year", "Smolt \u2192 Adult Survival Rate")
+```
+
 ## Parr per Spawner
 
-"Spawner" means total spawners that survive pre-spawn mortality.
+"Spawner" means total adults reaching the spawning grounds that survive pre-spawn mortality.
 
@@
 
-"Smolt" means total NOR smolt that survive their second winter, immediately prior to migration out of basin.
+"Smolt" means total NOR smolt immediately prior to migration out of basin.
 
@@
 
-This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adult recruits returning across multiple ages/years).
-"Brood year" refers to the year the returning production was spawned.
+This is the sum of all spawners that were produced by the spawners in a given brood year (i.e., accounts for adults from a cohort returning across multiple ages/years).
+"Brood year" refers to the year the returning cohort was spawned.
 
@@
 ```
+
+## Spawners per Adult Return {.tabset .tabset-pills}
+
+Unlike the previous figures, this figure shows the proportion of the adults that returned to the Columbia River each year (prior to any mortality on upstream migration) that ultimately spawned successfully.
+
+### Time Series {.tabset .tabset-pills}
+
+```{r spawners-per-return-fn}
+# function to calculate the survival term for a given origin, population, and combo of ages
+f = function(o, j, include_age3) {
+  # spawning adult abundance
+  Sa = post_subset(post, sub_index("^Sa[year,age,origin,pop]", year = ".+", age = ".+", origin = o, pop = j), matrix = TRUE)
+
+  # adults at estuary
+  Rb = post_subset(post, sub_index("^Rb[year,age,origin,pop]", year = 2:33, age = ".+", origin = o, pop = j), matrix = TRUE)
+
+  # function to calculate for a given MCMC iteration
+  g = function(i, include_age3) {
+    # put the values from this draw into the format used in the model
+    Sa_i = array_format(Sa[i,])[,,o,j]
+    Rb_i = array_format(Rb[i,])[,,o,j]
+
+    # choose which columns to include in sum over ages
+    if (include_age3) keep_cols = 1:3 else keep_cols = 2:3
+
+    # calculate the composite survival
+    phi_Rb_Sa_i = rowSums(Sa_i[,keep_cols], na.rm = TRUE)/rowSums(Rb_i[,keep_cols], na.rm = TRUE)
+
+    # Inf comes from dividing by zero (i.e., the stray years)
+    # NaN comes from a dividing zero by zero (i.e., the first year)
+    phi_Rb_Sa_i[phi_Rb_Sa_i == Inf | phi_Rb_Sa_i == "NaN"] = NA
+
+    # in some rare cases, the max() constraint produces fish
+    phi_Rb_Sa_i[phi_Rb_Sa_i > 1] = 0.99
+    as.numeric(phi_Rb_Sa_i)
+  }
+
+  # apply to each posterior sample
+  out = t(sapply(1:nrow(Sa), g, include_age3 = include_age3))
+
+  # set index names
+  y_ind = 1:ncol(out)
+  base_name = ifelse(include_age3, "phi_Rb_Sa", "phi_Rb_Sa_45")
+  colnames(out) = sub_index(paste0(base_name, "[year,origin,pop]"), year = y_ind, origin = o, pop = j)
+
+  # remove NA values
+  na_ind = which(!is.na(out[1,]))
+  out[,na_ind]
+}
+
+# apply the function to all populations and ages
+out = do.call(cbind, lapply(1:jags_data$nj, function(j) {
+  cbind(f(o = o_nor, j = j, include_age3 = TRUE),
+        f(o = o_hor, j = j, include_age3 = TRUE),
+        f(o = o_nor, j = j, include_age3 = FALSE),
+        f(o = o_hor, j = j, include_age3 = FALSE)
+  )
+}))
+
+# combine with other posterior samples
+post = post_bind(post, out)
+
+# function to create the plot for one population
+plot_f = function(j, include_age3) {
+
+  param = paste0(ifelse(include_age3, "phi_Rb_Sa", "phi_Rb_Sa_45"), "[year,origin,pop]")
+  est_nor = post_summ(post, sub_index(param, year = ".+", origin = o_nor, pop = j))
+
+  if (j != j_min) {
+    est_hor = post_summ(post, sub_index(param, year = ".+", origin = o_hor, pop = j))
+    hor_yrs = stringr::str_extract(colnames(est_hor), "\\[[0-9]+") |> stringr::str_remove("\\[") |> as.numeric()
+    missing_hor_yrs = ts_yrs[!(ts_yrs %in% hor_yrs)]
+
+    if (length(missing_hor_yrs) > 0) {
+      est_empty = replicate(n = length(missing_hor_yrs), expr = rep(NA, 5))
+      rownames(est_empty) = rownames(est_hor)
+      est_hor = cbind(est_empty, est_hor)
+    }
+  }
+
+  plot_tseries(est = est_nor, label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = c(0,1))
+  if (j != j_min) add_tseries(est = est_hor, yrs = all_yrs[ts_yrs])
+
+  if (j == 1) {
+    legend("topright", legend = origins, title = "Origin",
+           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2,
+           pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
+  }
+}
+```
+
+#### All Ages {-}
+
+```{r spawners-per-return-all-ages, fig.width = p4_width, fig.height = p4_height}
+
+# loop over populations
+# includes all ages
+mypar()
+junk = sapply(1:jags_data$nj, plot_f, include_age3 = TRUE)
+axis_labels("Return Year", "Spawners per Returning Adult (All Ages)")
+```
+
+### Ages 4&5 {-}
+
+```{r spawners-per-return-old-ages, fig.width = p4_width, fig.height = p4_height}
+
+# loop over populations
+# includes only ages 4 and 5
+mypar()
+junk = sapply(1:jags_data$nj, plot_f, include_age3 = FALSE)
+axis_labels("Brood Year", "Spawners per Returning Adult (Ages 4&5)")
+```
+
+### Tables {.tabset .tabset-pills}
+
+These tables summarize the time series shown.
+The summary statistic across years was calculated for each posterior sample and the posterior means are reported.
+
+```{r spawners-per-return-table-fns}
+# function reporting across year summary stat
+# for a given origin, population, and age grouping
+f = function(o, j, include_age3, FUN, ...) {
+  if (o == o_hor & j == j_min) {
+    return(NA)
+  } else {
+    # create the parameter name to subset
+    param = paste0(ifelse(include_age3, "phi_Rb_Sa", "phi_Rb_Sa_45"), "[.+,origin,pop]")
+
+    # extract posterior samples for this origin and population
+    samps = post_subset(post, sub_index(param, origin = o, pop = j), matrix = TRUE)
+
+    # obtain posterior samples of the inter-annual summary statistic returned by FUN
+    stat = apply(samps, 1, FUN, ...)
+
+    # return the posterior mean of the summary statistic returned by FUN
+    mean(stat)
+  }
+}
+
+# wrapper for f()
+# performs task for all populations, origins, and age groupings
+g = function(FUN, digits = 2, ...) {
+
+  # summarize the posteriors
+  x = rbind(
+    sapply(1:jags_data$nj, function(j) f(o = o_nor, j = j, include_age3 = TRUE, FUN = FUN, ...)),
+    sapply(1:jags_data$nj, function(j) f(o = o_hor, j = j, include_age3 = TRUE, FUN = FUN, ...)),
+    sapply(1:jags_data$nj, function(j) f(o = o_nor, j = j, include_age3 = FALSE, FUN = FUN, ...)),
+    sapply(1:jags_data$nj, function(j) f(o = o_hor, j = j, include_age3 = FALSE, FUN = FUN, ...))
+  ) |> as.data.frame()
+  colnames(x) = pops
+
+  # add identifiers
+  tab = cbind(
+    age_type = rep(c("All Ages", "Ages 4&5"), each = 2),
+    origin_type = rep(c("NOR", "HOR"), 2),
+    round(x, digits = digits)
+  )
+
+  # make NA values empty
+  tab[is.na(tab)] = " "
+
+  # return the table, ready to be passed to kable
+  return(tab)
+}
+
+kable_f = function(tab) {
+  tab |>
+    kbl(format = "html", col.names = c(" ", "Origin", pops)) |>
+    kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped")) |> 
+    column_spec(1:2, bold = TRUE) |>
+    collapse_rows(1)
+}
+```
+
+#### Inter-Annual Mean {-}
+
+```{r, spawners-per-return-table-mean}
+# posterior means of the inter-annual mean survival rate
+g(FUN = mean) |>
+  kable_f()
+```
+
+#### Inter-Annual q10 {-}
+
+```{r, spawners-per-return-table-q10}
+# posterior means of the survival value that 10% of years fall below
+g(FUN = quantile, probs = 0.1) |>
+  kable_f()
+```
+
+#### Inter-Annual q90 {-}
+
+```{r, spawners-per-return-table-mean-q90}
+# posterior means of the survival value that 90% of years fall below
+g(FUN = quantile, probs = 0.9) |>
+  kable_f()
+```

### 2023-08-17 03-post-process/output-plots.Rmd
Rename equiv to composite Rmd

@@
     value: TRUE
-  include_equiv_rates:
-    label: "Include Equivilency Rate Output?"
+  include_composite_rates:
+    label: "Include Composite Rate Output?"
     value: TRUE
@@
 
-```{r equiv-rates, child = "output-plots-children/09-equiv-rates.Rmd", eval = params$include_equiv_rates}
+```{r equiv-rates, child = "output-plots-children/09-composite-rates.Rmd", eval = params$include_composite_rates}
 ```

### 2023-08-17 03-post-process/output-plots-children/10-rho-params.Rmd
Improve Rho parameter Rmd section

@@
 rho_labels = c(
-  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
+  "rho_Lphi_E_Pb" = "Egg \u2192 Parr Survival",
   "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
@@
   "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
-  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
+  "rho_Lphi_Mb_Ma" = "Smolt \u2192 LGR Survival",
   "rho_lL_Pb" = "Mean Parr Length",
   "rho_Lphi_Pa_Mb" = "Overwinter Survival",
-  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
+  "rho_Lphi_Rb_Ra" = "BON \u2192 LGR Survival",
   "rho_Lpi" = "Pr(Fall Migrant)",
-  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
+  "rho_Lphi_Ma_O0" = "LGR \u2192 Ocean Survival"
 )
@@
 * Dots: Posterior mean correlation of individual population pairs
-<!-- * Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness) -->
 
@@
 
-### Egg-to-Parr Survival
+### Egg $\to$ Parr Survival
 
@@
 
-### Trib. to LGR Survival
+### Smolt $\to$ LGR Survival
 
@@
 
-### LGR to Ocean Survival
+### LGR $\to$ BON Survival
 
@@
 
-#### Pr(Age-3)
+#### Pr(Age-3) {-}
 
@@
 
-#### Pr(Age-4)
+#### Pr(Age-4) {-}
 
@@
 
-### BON to LGR Survival
+### BON $\to$ LGR Survival
 

### 2023-08-18 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Improve the noise term diagnostics Rmd section

@@
 
-# Random Noise Diagnostics {.tabset .tabset-pills}
+# Residual Diagnostics {.tabset .tabset-pills}
 
@@
 
-This section is devoted to evaluating how consistent the estimated noise terms are with the assumptions of the random processes they are assumed to be generated by.
-Diagnostics are separate by process model and observation model and the time series of noise terms is displayed to visually detect issues.
-Each model component (process or observation) includes summary tables that quantitatively summarize the results displayed on the time series figures.
-
-#### Why Does this Matter?
+This section is devoted to evaluating how consistent the estimated process and observation noise terms (i.e., residuals) are with the assumptions of the random processes they are assumed to be generated by.
+Diagnostics are separated by process model and observation model and the time series of noise terms is displayed to visually detect issues.
+Each model component (process or observation) includes summary tables that summarize the results displayed on the time series figures.
+
+#### Why Does this Matter? {-}
 
@@
 
-#### What was Calculated?
+#### What was Calculated? {-}
 
@@
 
-##### JAGS Code Example
+##### JAGS Code Example {-}
 
@@
 mu_phi ~ dbeta(1,1)
-sigma_Lphi ~ dunif(0,5)
+sigma_Lphi ~ dunif(0,2)
 &nbsp;
@@
 
-#### What is Shown?
+#### What is Shown? {-}
 
@@
 
-## Process Model Noise Terms {.tabset .tabset-pills}
+## Process Model Noise Terms {.tabset .tabset-dropdown}
 
@@
 
-### FW Juvenile {.tabset .tabset-pills}
+### FW Juvenile {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Egg \u2192 Parr Survival) QResidual")
+axis_labels("Brood Year", "Egg \u2192 Parr Survival QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,LH_type,pop]", pop = j, main = pops[j], LH_type = i_fall))
-axis_labels("Brood Year", "logit(Proportion Fall Migrants) QResidual")
+axis_labels("Brood Year", "Proportion Fall Migrants QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-##### Fall Migrants
+##### Fall Migrants {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
-axis_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### Spring Migrants
+axis_labels("Brood Year", "Over-winter Survival (Fall Migrants) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### Spring Migrants {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
-axis_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) QResidual")
+axis_labels("Brood Year", "Over-winter Survival (Spring Migrants) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Brood Year", "log(Parr \u2192 Smolt 'Growth' Factor) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-#### Trib $\to$ LGR {.tabset .tabset-pills}
-
-##### NOR
+axis_labels("Brood Year", "Parr \u2192 Smolt 'Growth' Factor QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+#### Smolt $\to$ LGR {.tabset .tabset-pills}
+
+##### NOR {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 1, LH_type = 2, main = pops[j]))
-axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [NOR]) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
+axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,LH_type,origin,pop]", pop = j, origin = 2, LH_type = 2, main = pops[j]))
-axis_labels("Brood Year", "logit(Trib \u2192 LGR Survival [HOR]) QResidual")
+axis_labels("Brood Year", "Smolt \u2192 LGR Survival (HOR) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### SW Juvenile {.tabset .tabset-pills}
+axis_labels("Brood Year", "LGR \u2192 BON Survival QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### SW Juvenile {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Yr1 Ocean Survival) QResidual")
+axis_labels("Brood Year", "Yr1 Ocean Survival QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-##### NOR
+##### NOR {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Mature at Age-3 [NOR]) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
+axis_labels("Brood Year", "Pr(Mature at Age-3|NOR) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Mature at Age-3 [HOR]) QResidual")
+axis_labels("Brood Year", "Pr(Mature at Age-3|HOR) QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Mature at Age-4 [NOR]) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-##### HOR
+axis_labels("Brood Year", "Pr(Mature at Age-4|NOR) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+##### HOR {-}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Mature at Age-4 [HOR]) QResidual")
-proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
-```
-
-### FW Adult {.tabset .tabset-pills}
+axis_labels("Brood Year", "Pr(Mature at Age-4|HOR) QResidual")
+proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
+```
+
+### FW Adult {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
-axis_labels("Return Year", "logit(BON \u2192 LGR Survival) QResidual")
+axis_labels("Return Year", "BON \u2192 LGR Survival QResidual")
 proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
@@
 
-## Observation Model Noise Terms {.tabset .tabset-pills}
+## Observation Model Noise Terms {.tabset .tabset-dropdown}
 
@@
 
-### Abundance Data {.tabset .tabset-pills}
+### Abundance Data {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "log(Fall Parr Abundance) QResidual")
+axis_labels("Brood Year", "Fall Parr Abundance QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "log(Spring Trap Count) QResidual")
+axis_labels("Brood Year", "Spring Smolt Abundance QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Return Year", "log(Total Adult Count) QResidual")
+axis_labels("Return Year", "Total Adult Return QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-### Survival Data {.tabset .tabset-pills}
+### Survival Data {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Summer Parr \u2192 LGR Survival) QResidual")
+axis_labels("Brood Year", "Summer Parr \u2192 LGR Survival QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
-axis_labels("Brood Year", "logit(Fall Parr \u2192 LGR Survival) QResidual")
+axis_labels("Brood Year", "Fall Parr \u2192 LGR Survival QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 })
-axis_labels("Brood Year", "logit(Winter Parr \u2192 LGR Survival) QResidual")
+axis_labels("Brood Year", "Winter Parr \u2192 LGR Survival QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
-axis_labels("Brood Year", "logit(NOR Smolt \u2192 LGR Survival) QResidual")
+axis_labels("Brood Year", "Smolt \u2192 LGR Survival (NOR) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-##### HOR
+##### HOR {-}
 
@@
 })
-axis_labels("Brood Year", "logit(HOR Smolt \u2192 LGR Survival) QResidual")
+axis_labels("Brood Year", "Smolt \u2192 LGR (NOR) Survival) QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
-axis_labels("Brood Year", "logit(LGR \u2192 BON Survival) QResidual")
+axis_labels("Brood Year", "LGR \u2192 BON Survival QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-### Length Data {.tabset .tabset-pills}
+### Length Data {.tabset .tabset-dropdown}
 
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Brood Year", "log(Parr Mean Length) QResidual")
+axis_labels("Brood Year", "Parr Mean Length QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
-axis_labels("Brood Year", "log(Smolt Mean Length) QResidual")
+axis_labels("Brood Year", "Smolt Mean Length QResidual")
 obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
@@
 
-### Composition Data {.tabset .tabset-pills}
+### Composition Data {.tabset .tabset-dropdown}
 
@@
 
-##### CAT
+##### CAT {-}
 
@@
 
-##### LOS
+##### LOS {-}
 
@@
 
-##### MIN
+##### MIN {-}
 
@@
 
-##### UGR
+##### UGR {-}
 
@@
 
-#### Carcass Sampling {.tabset .tabset-pills}
+#### Carcass Sampling {.tabset .tabset-dropdown}
 

### 2023-08-18 03-post-process/output-plots-children/12-pp-checks.Rmd
Rename resid and pp-check diag Rmd sections

--- 2023-07-06 03-post-process/output-plots-children/03a-pp-checks.Rmd
@@
 
-## Posterior Predictive Checks
+# Posterior Predictive Checks
 
-This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
+This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model, similar to the residual diagnostic section.
 For each observed data point and MCMC iteration, a value was simulated from the model.
@@
 This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
-* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities by performing calculations on the square root of observed and expected counts..
-This applies to all composition data, the survival from BON to LGR data, and the spawn status data.
+* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities by performing calculations on the square root of observed and expected counts.
+This applies to all composition data and the survival from BON to LGR data.
 

### 2023-08-18 03-post-process/output-plots.Rmd
Rename resid and pp-check diag Rmd sections

@@
     label: "Include Process Model Correlation Output?"
-    value: TRUE
-  include_noise_term_diags:
-    label: "Include Noise Term Diagnostic Output?"
+    value: FALSE
+  include_residual_diags:
+    label: "Include Residual Diagnostic Output?"
+    value: FALSE
+  include_pp_check:
+    label: "Include Posterior Predictive Check Output?"
     value: TRUE
@@
 
-```{r noise-term-diags, child = "output-plots-children/11-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
+```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_resid_diags}
+```
+
+```{r pp-check, child = "output-plots-children/12-pp-checks.Rmd", eval = params$include_pp_check & model_info$do_pp_check}
 ```

### 2023-08-18 03-post-process/output-plots.Rmd
Rename param summaries Rmd section
& Improve it some
Rename post-vs-prior Rmd section
& Improve some

@@
 
-```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_resid_diags}
+```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_residual_diags}
 ```
@@
 
-```{r param-summaries, child = "output-plots-children/12-param-summaries.Rmd", eval = params$include_param_summaries}
+```{r param-summaries, child = "output-plots-children/13-param-summaries.Rmd", eval = params$include_param_summaries}
 ```
 
-```{r post-v-prior, child = "output-plots-children/13-post-vs-prior.Rmd", eval = params$include_post_v_prior}
+```{r post-v-prior, child = "output-plots-children/14-post-vs-prior.Rmd", eval = params$include_post_v_prior}
 ```

### 2023-08-18 03-post-process/output-plots.Rmd
Rename/reorder JAGS info & WAIC Rmd sections

@@
     value: TRUE
+  include_waic:
+    labels: "Include WAIC Output"
+    value: FALSE
 editor_options: 
@@
 
-```{r known-values, child = "output-plots-children/14-known-values.Rmd", eval = params$include_known}
+```{r known-values, child = "output-plots-children/15-known-values.Rmd", eval = params$include_known}
 ```
 
-```{r jags-info, child = "output-plots-children/15-jags-model-info.Rmd", eval = params$include_jags_info}
+```{r jags-info, child = "output-plots-children/16-jags-model-info.Rmd", eval = params$include_jags_info}
 ```
+
+```{r waic-output, child = "output-plots-children/99-waic.Rmd", eval = params$include_waic & model_info$do_lppd}
+```

### 2023-08-18 03-post-process/output-plots.Rmd
Use html_document2 and numbered sections

@@
 output: 
-  html_document:
+  bookdown::html_document2:
     toc: true
     toc_float: true
+    number_sections: true
 params:
@@
     value: TRUE
-    value: TRUE
   include_parr_recruitment:
     label: "Include Parr Recruitment Output?"
+    value: TRUE
   include_mean_length:
@@
     label: "Include Process Model Correlation Output?"
-    value: FALSE
+    value: TRUE
   include_residual_diags:
     label: "Include Residual Diagnostic Output?"
-    value: FALSE
+    value: TRUE
   include_pp_check:

### 2023-09-08 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Update text in capacity vs habitat Rmd section

@@
 
-Error bars represent the central 80% of the posterior; grey lines are individual posterior draws of the expected relationship.
+Error bars represent the central 80% of the posterior for population-specific parr capacity; thin lines are individual posterior draws of the expected relationship, thick line is the posterior mean relationship.
 

### 2023-09-08 03-post-process/ms-content/ms-content.Rmd
ms-content: force captions at top of figures

@@
   - \renewcommand{\rmdefault}{\sfdefault}
-  - \usepackage{float}
   - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
   - \captionsetup{width=\textwidth}
+  - \usepackage{floatrow}
+  - \floatsetup[figure]{style=plaintop}
+  - \floatsetup[table]{style=plaintop}
 editor_options: 

### 2023-09-08 03-post-process/ms-content/ms-content.Rmd
ms-content: include a no-fall table
Co-author comments suggested figure was confusing. Now table shows raw values, not expressed as ratios

@@
 
-no_fall_caption = "
+no_fall_fig_caption = "
   Ratios between the across-year mean (dark grey) and coefficient of variation (light grey) abundance of natural-origin smolt reaching Lower Granite Dam with (denominator) and without (numerator) the fall migrant life history strategy.
@@
   Values presented are posterior means and 95% credible regions.
+"
+
+no_fall_table_caption = "
+  Inter-annual mean and coefficient of variation (\\%CV) of natural-origin smolt reaching Lower Granite Dam in the presence and (hypothetical) absence of the fall migrant life history type.
+  Findings indicate that smolt abundance would be lower on average and more variable across years if the fall migrant strategy did not exist.
 "
@@
 
-```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE, eval = params$no_fall_fig}
+```{r no-fall-analysis, time_it = TRUE, eval = params$no_fall_fig | params$no_fall_tab}
 cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}
@@
   # calculate the ratios between the actual and hypothetical
-  mean_p_ratio = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
-  cv_ratio = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)
-
-  names(mean_p_ratio) = paste0("mean_p_ratio[", 1:5, "]")
-  names(cv_ratio) = paste0("cv_ratio[", 1:5, "]")
-  c(mean_p_ratio, cv_ratio)
-}
-
-##### STEP 3: APPLY FUNCTION TO ALL POSTERIOR SAMPLES, FORMAT, AND SUMMARIZE #####
-
-# apply
-ratio_out = t(sapply(1:nrow(Pb), f))
-
-# format
-ratio_post = post_convert(cbind(postpack:::id_mat(post), ratio_out))
-
+  mean_p_ratio_i = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
+  cv_ratio_i = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)
+
+  # calculate interannual cv by population and scenario
+  Ma_cv_hyp_i = apply(Ma_tot_hyp_i, 2, cv)
+  Ma_cv_real_i = apply(Ma_tot_real_i, 2, cv)
+
+  # calculate interannual mean by population and scenario
+  Ma_mean_hyp_i = colMeans(Ma_tot_hyp_i, na.rm = TRUE)
+  Ma_mean_real_i = colMeans(Ma_tot_real_i, na.rm = TRUE)
+
+  # calculate percent changes
+  Ma_mean_change_i = (Ma_mean_hyp_i - Ma_mean_real_i)/Ma_mean_real_i
+  Ma_cv_change_i = (Ma_cv_hyp_i - Ma_cv_real_i)/Ma_cv_real_i
+
+  # add names
+  names(Ma_mean_hyp_i) = paste0("Ma_mean_hyp[", 1:5, "]")
+  names(Ma_mean_real_i) = paste0("Ma_mean_real[", 1:5, "]")
+  names(Ma_cv_hyp_i) = paste0("Ma_cv_hyp[", 1:5, "]")
+  names(Ma_cv_real_i) = paste0("Ma_cv_real[", 1:5, "]")
+  names(Ma_mean_change_i) = paste0("Ma_mean_change[", 1:5, "]")
+  names(Ma_cv_change_i) = paste0("Ma_cv_change[", 1:5, "]")
+
+  names(mean_p_ratio_i) = paste0("mean_p_ratio[", 1:5, "]")
+  names(cv_ratio_i) = paste0("cv_ratio[", 1:5, "]")
+  c(mean_p_ratio_i, cv_ratio_i, Ma_mean_hyp_i, Ma_mean_real_i, Ma_cv_hyp_i, Ma_cv_real_i, Ma_mean_change_i, Ma_cv_change_i)
+}
+
+# apply to each posterior sample
+out = t(sapply(1:nrow(Pb), f))
+out = post_convert(cbind(postpack:::id_mat(post), out))
+
+```
+
+```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_fig_caption), eval = params$no_fall_fig}
 # summarize
-mean_summ = post_summ(ratio_post, "mean")
-cv_summ = post_summ(ratio_post, "cv")
+mean_summ = post_summ(out, "mean_p_ratio")
+cv_summ = post_summ(out, "cv_ratio")
 
@@
 ```
+
+`r ifelse(params$no_fall_fig & params$no_fall_tab, "_**Alternatively**, as a table, showing the actual numbers and a percent change, rather than as ratios._", "")`
+
+```{r no-fall-tab, eval = params$no_fall_tab}
+f = function(x, is_percent) {
+  g = function(x, is_percent) {
+    if (!is_percent) {
+      prettyNum(round(x, 1), big.mark = ",", scientific = FALSE)
+    } else {
+      paste0(round(x, 2) * 100, "\\%")
+    }
+  }
+  paste0(g(x["mean",], is_percent), " (", g(x["sd",], is_percent), ")")
+}
+
+tab = cbind(
+  pop = c("CAT", "LOS", "MIN", "UGR", "Total"),
+  f(post_summ(out, "Ma_mean_real")/1000, FALSE),
+  f(post_summ(out, "Ma_mean_hyp")/1000, FALSE),
+  f(post_summ(out, "Ma_mean_change"), TRUE),
+  f(post_summ(out, "Ma_cv_real"), TRUE),
+  f(post_summ(out, "Ma_cv_hyp"), TRUE)
+)
+
+kbl(tab, "latex", booktabs = TRUE, 
+    col.names = c(
+      " ", "Real\\textsuperscript{1,3}", "All Spring\\textsuperscript{2,3}", "\\%$\\Delta$",
+      "Real\\textsuperscript{1}", "All Spring\\textsuperscript{2}"), escape = FALSE,
+    caption = msdown::prep_caption(no_fall_table_caption)) |>
+  kable_styling(full_width = FALSE, latex_options = "HOLD") |>
+  add_header_above(c(" " = 1, "Inter-Annual Mean" = 3, "Inter-Annual \\\\%CV" = 2), bold = TRUE, escape = FALSE) |>
+  column_spec(1, bold = TRUE) |>
+  row_spec(0, bold = TRUE) |>
+  footnote(general_title = "",
+           general = c(
+             "\\\\textit{Posterior summaries represented as mean (standard deviation).}"
+           ),
+           number =  c(
+             "Based on the observed time series, in which both spring and fall migrants were present.",
+             "Based on the hypothetical case where no parr recruits were fall migrants -- calculated after model fitting by assuming all parr recruits experience the higher mortality rates of the spring migrant life history type.",
+             "Abundance expressed as thousands of natural-origin smolt reaching Lower Granite Dam."
+           ), threeparttable = TRUE, escape = FALSE)
+
+```
+
+\clearpage
 

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: update WUL-change figure
Based on reviewer comments:
* show three levels of WUL change: 50%, 100%, and 200%
* only show uncertainty for the "current scenario"
* use approx spawners instead of eggs
* include new row of plots showing resulting relationship between spawners and smolt at LGR

@@
 WUL_change_fig_caption = "
-  Density-dependent survival relationships from egg (panels a-d) and parr (panels e-f) to smolt arriving at Lower Granite Dam (LGR) under current (solid lines) and increased (dashed lines) weighted usable habitat (WUL).
-  Egg $\\to$ LGR survival includes density effects that are both direct (e.g., egg survival varies as a function of egg density) and indirect (parr size varies as a function of egg density, and survival varies with size), whereas parr $\\to$ LGR survival includes only the indirect density effects.
+  Freshwater juvenile density-dependent relationships under current (solid lines) and increased (dashed lines) weighted usable habitat.
+  Panels (_a_-_d_): composite survival from egg to smolt at Lower Granite Dam (LGR) including both direct (i.e., egg density affects egg survival via Beverton-Holt dynamics) and indirect (i.e., egg density affects growth rates, size affects parr and smolt survival) density effects; panels (_e_-_h_): composite survival from parr to smolt at LGR which includes only indirect effects; panels (_i_-_l_): smolt reaching LGR.
+  Calculations operate based on density of juveniles -- _x_-axis converted to approximate spawner abundance (all ages, origins, and sexes) for ease of interpretation.
+Grey bands show the 95% credible region for the current relationship only; lines show posterior means.
+"
+
+obs_vs_fit_fig_caption = "
+  Consistency between model fitted values (posterior means) and nearly all data sources with an explicit likelihood function; only parr and smolt mean length data have been omitted here for space.
+  Each data point is one year for one population, with the exceptions of panels _g_, _h_, and _i_, which display values for both natural- and hatchery-origin survival rates, and in the cases of _h_ and _i_, these rates apply equally to all populations.
+  More detailed visualizations of model fit are shown in Supplement B (Section 3: model fits as time series with magnitude of observation uncertainty shown; Section 11: diagnostics based on quantile-standardized residuals; Section 12: posterior predictive checks).
 "
@@
 
-```{r WUL-change-fig, fig.width = 7.2, fig.height = 4.5, eval = params$WUL_change_fig, fig.cap = WUL_change_fig_caption, time_it = TRUE}
+```{r WUL-change-fig, fig.width = 7.2, fig.height = 6, eval = params$WUL_change_fig, fig.cap = msdown::prep_caption(WUL_change_fig_caption), time_it = TRUE}
 
@@
 
-  # the parameters needed to calucate process model expected values
+  # the parameters needed to calculate process model expected values
   the_params = c("alpha[pop]", "beta[pop]", "^lambda$",
@@
 
-get_phi_hat = function(x, E, WUL_change = 0, start = "E") {
+get_phi_hat = function(x, E, WUL_change = 0, start = "E", out_type = "phi") {
   with(as.list(c(x, E = E, WUL_change = WUL_change)), {
@@
     if (start == "Pb") out = Pb/E
-    return(out)
+
+    if (out_type == "phi") return(out)
+    if (out_type == "Ma") return(Ma)
   })
@@
 
-get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E") {
+get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E", out_type = "phi") {
 
@@
     x = prep_sample(the_samps, i = i, j = j)
-    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start))
+    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start, out_type = out_type))
   })
@@
 
-plot_f = function(j, start, WUL_change) {
+plot_f = function(j, start, out_type) {
+
+  WUL_changes = c(0.5, 1, 2)
+  lwd = 1.5
+
+  eps = mean(post_summ(post, sub_index("E_per_Sa[year,pop]", year = ".+", pop = j))["mean",])
   phi_real_post = get_phi_real_post(j = j, start = start)
@@
   E_real = post_summ(post, sub_index("^E[.+,pop]", pop = j))
-  E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)
-
-  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start)
+  # E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)
+  E_pred = seq(eps * 100, max(E_real["mean",]), length = 30)
+  keep_yrs = stringr::str_extract(colnames(E_real), "[:digit:]+,") |> 
+    stringr::str_remove(",")
+
+  S_pred = E_pred/eps
+  S_real = post_summ(post, sub_index("^Sa_tot[year,pop]", year = keep_yrs, pop = j))
+
+  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start, out_type = out_type)
   phi_hat = post_summ(phi_hat_post, ".")
-  phi_hat_new_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_change, start = start)
-  phi_hat_new = post_summ(phi_hat_new_post, ".")
-
-  plot(phi_real["mean",] ~ E_real["mean",], type = "n",
-       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),],
-                phi_hat_new[c("2.5%","97.5%"),]),
+
+  phi_hat_new1_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[1], start = start, out_type = out_type)
+  phi_hat_new1 = post_summ(phi_hat_new1_post, ".")
+  phi_hat_new2_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[2], start = start, out_type = out_type)
+  phi_hat_new2 = post_summ(phi_hat_new2_post, ".")
+  phi_hat_new3_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[3], start = start, out_type = out_type)
+  phi_hat_new3 = post_summ(phi_hat_new3_post, ".")
+
+  plot(phi_real["mean",] ~ S_real["mean",], type = "n",
+       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),], phi_hat_new3["mean",]),
        # phi_real["mean",]),
        # ylim = make_lim(0, ifelse(start == "E", 0.075, 0.3)),
-       xlim = c(0, max(E_real["mean",], E_pred)),
-       xaxt = "n")
-
-  # points(phi_real["mean",] ~ E_real["mean",], pch = 21, 
+       xlim = c(0, max(S_real["mean",], S_pred)),
+       xaxt = "n", yaxt = "n")
+
+  # points(phi_real["mean",] ~ S_real["mean",], pch = 21,
   #        col = "black", bg = scales::alpha("grey25", 0.25), cex = 0.8)
 
-  polygon(x = c(E_pred, rev(E_pred)), 
+  polygon(x = c(S_pred, rev(S_pred)), 
           y = c(phi_hat["2.5%",], rev(phi_hat["97.5%",])),
           col = tranp_col, border = NA)
-  lines(phi_hat["mean",] ~ E_pred, lwd = 2)
-  lines(phi_hat["2.5%",] ~ E_pred)
-  lines(phi_hat["97.5%",] ~ E_pred)
-
-  polygon(x = c(E_pred, rev(E_pred)), 
-          y = c(phi_hat_new["2.5%",], rev(phi_hat_new["97.5%",])),
-          col = tranp_col, border = NA)
-  lines(phi_hat_new["mean",] ~ E_pred, lwd = 2, lty = 2)
-  lines(phi_hat_new["2.5%",] ~ E_pred,  lty = 2)
-  lines(phi_hat_new["97.5%",] ~ E_pred, lty = 2)
+
+  lines(phi_hat["mean",] ~ S_pred, lwd = lwd)
+  lines(phi_hat_new1["mean",] ~ S_pred, lty = 3, lwd = lwd)
+  lines(phi_hat_new2["mean",] ~ S_pred, lty = 2, lwd = lwd)
+  lines(phi_hat_new3["mean",] ~ S_pred, lty = 5, lwd = lwd)
+
   at_x = axisTicks(par("usr")[1:2], log = FALSE)
-  axis(side = 1, at = at_x, labels = at_x/1e6)
-  panel_label(paste0("(", letters[ifelse(start == "E", 0, 3) + j], ") ", pops[j]))
+  axis(side = 1, at = at_x, labels = at_x/1000)
+
+  at_y = axisTicks(par("usr")[3:4], log = FALSE)
+  axis(side = 2, at = at_y, labels = at_y/ifelse(out_type == "Ma", 1000, 1))
+
+  base = ifelse(start == "E", 0, 4)
+  base = ifelse(out_type == "Ma", 8, base)
+  panel_label(paste0("(", letters[base + j], ") "))
 
   if (j == 1) {
-    if (start == "E") {
-      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 1)
-      legend("topright", title = "WUL", legend = c("Current", paste0("\u2191", WUL_change * 100, "%")), lty = c(1,2), seg.len = 1.5, bty = "n", cex = 0.8)
-    } 
-    if (start == "Pb") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 1)
-  }
-
-}
-
-mypar(mfrow = c(2,4), col.axis = "black")
-junk = sapply(1:4, function(j) plot_f(j, "E", 1))
-junk = sapply(1:4, function(j) plot_f(j, "Pb", 1))
-axis_labels(xlab = "Egg Production (Millions)")
+    if (start == "E" & out_type == "phi") {
+      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 2)
+      legend("topright", title = "Weighted Habitat", legend = c("Current", paste0("\u2191", WUL_changes * 100, "%")), lty = c(1,3,2,5), seg.len = 2.7, bty = "n", lwd = lwd, cex = 0.9)
+    } 
+    if (start == "Pb" & out_type == "phi") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 2)
+    if (out_type == "Ma") {
+      axis_labels(ylab = "LGR Smolt", outer = FALSE, yline = 2)
+      axis_labels(ylab = "Thousands", outer = FALSE, yline = 1, cex = 0.8, font = 3)
+    } 
+  }
+
+  if (start == "E" & out_type == "phi") {
+    mtext(side = 3, line = 0.15, font = 2, text = pops[j], cex = 1)
+  }
+}
+
+mypar(mfrow = c(3,4), oma = c(2.5,2.5,1,0), col.axis = "black")
+junk = sapply(1:4, function(j) plot_f(j, "E", "phi"))
+junk = sapply(1:4, function(j) plot_f(j, "Pb", "phi"))
+junk = sapply(1:4, function(j) plot_f(j, "Pb", "Ma"))
+axis_labels(xlab = "Spawner Abundance")
+axis_labels(xlab = "Thousands", outer = TRUE, xline = 1.5, cex = 0.8, font = 3)
 ```

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: include a figure showing fit to data

@@
 
+```{r obs-vs-fit-fig, fig.width = 7.2, fig.height = 7, eval = params$obs_vs_fit_fig, fig.cap = msdown::prep_caption(obs_vs_fit_fig_caption)}
+# initialize an empty list
+plot_dat = list()
+
+# prep values to plot: fall trap passage
+plot_dat$Pa_fall = list(
+  obs = jags_data$Pa_obs[,i_fall,],
+  fitted = {
+    tmp = post_summ(post, sub_index("^Pa[.+,LH_type,.]", LH_type = i_fall))
+    list(
+      mn = array_format(tmp["mean",])[,i_fall,],
+      lwr = array_format(tmp["2.5%",])[,i_fall,],
+      upr = array_format(tmp["97.5%",])[,i_fall,]
+    )
+  }
+)
+
+# prep values to plot: spring trap passage
+plot_dat$Mb_spring = list(
+  obs = jags_data$Mb_obs[,i_spring,o_nor,],
+  fitted = {
+    tmp = post_summ(post, sub_index("^Mb[.+,LH_type,origin,.]", LH_type = i_spring, origin = o_nor))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: adult return to river
+plot_dat$Ra_tot = list(
+  obs = jags_data$Ra_obs,
+  fitted = {
+    tmp = post_summ(post, "^Ra_tot[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: summer to LGR survival
+plot_dat$phi_Pb_Ma = list(
+  obs = plogis(jags_data$Lphi_obs_Pb_Ma),
+  fitted = {
+    tmp = post_summ(post, "^phi_Pb_Ma[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: fall to LGR survival
+plot_dat$phi_Pa_Ma_fall = list(
+  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_fall,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_fall, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_fall,],
+      lwr = array_format(tmp["2.5%",])[,i_fall,],
+      upr = array_format(tmp["97.5%",])[,i_fall,]
+    )
+  }
+)
+
+# prep values to plot: winter to LGR survival
+plot_dat$phi_Pa_Ma_winter = list(
+  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_spring,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_spring, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,],
+      upr = array_format(tmp["97.5%",])[,i_spring,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (NOR)
+plot_dat$phi_Mb_Ma_nor = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_nor,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_nor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (HOR)
+plot_dat$phi_Mb_Ma_hor = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_hor,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_hor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_hor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_hor,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (NOR & HOR both)
+plot_dat$phi_Mb_Ma = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,.,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,,],
+      upr = array_format(tmp["97.5%",])[,i_spring,,]
+    )
+  }
+)
+
+# prep values to plot: LGR to BON (NOR & HOR both)
+plot_dat$phi_Ma_O0 = list(
+  obs = plogis(jags_data$Lphi_obs_Ma_O0),
+  fitted = {
+    tmp = post_summ(post, "^phi_Ma_O0[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: BON to LGR (NOR & HOR both)
+plot_dat$phi_Rb_Ra = list(
+  obs = jags_data$x_LGR/jags_data$x_BON,
+  fitted = {
+    tmp = post_summ(post, "^phi_Rb_Ra[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# add aggregate age/origin compositions
+source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-model")
+source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-data")
+
+# prep values to plot: weir compositon age-3
+plot_dat$p_Ra_age3 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_3,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_3,],
+      lwr = array_format(tmp["2.5%",])[,k_3,],
+      upr = array_format(tmp["97.5%",])[,k_3,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-4
+plot_dat$p_Ra_age4 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_4,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,2,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_4,],
+      lwr = array_format(tmp["2.5%",])[,k_4,],
+      upr = array_format(tmp["97.5%",])[,k_4,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-5
+plot_dat$p_Ra_age5 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_5,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,3,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_5,],
+      lwr = array_format(tmp["2.5%",])[,k_5,],
+      upr = array_format(tmp["97.5%",])[,k_5,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon origin
+plot_dat$p_Ra_nor = list(
+  obs = x_Ra_new_obs$x_Ra_origin_obs[,o_nor,]/apply(x_Ra_new_obs$x_Ra_origin_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_origin[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,o_nor,],
+      upr = array_format(tmp["97.5%",])[,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: carcass compositon age-3
+plot_dat$p_Sa_prime_age3 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_3,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_3,],
+      lwr = array_format(tmp["2.5%",])[,k_3,],
+      upr = array_format(tmp["97.5%",])[,k_3,]
+    )
+  }
+)
+
+# prep values to plot: carcass compositon age-4
+plot_dat$p_Sa_prime_age4 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_4,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_4,],
+      lwr = array_format(tmp["2.5%",])[,k_4,],
+      upr = array_format(tmp["97.5%",])[,k_4,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-5
+plot_dat$p_Sa_prime_age5 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_5,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_5,],
+      lwr = array_format(tmp["2.5%",])[,k_5,],
+      upr = array_format(tmp["97.5%",])[,k_5,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon origin
+plot_dat$p_Sa_prime_nor = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_origin_obs[,o_nor,]/apply(x_Sa_prime_new_obs$x_Sa_prime_origin_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,o_nor,],
+      upr = array_format(tmp["97.5%",])[,o_nor,]
+    )
+  }
+)
+
+# function to create plot for one data type
+plot_f = function(dat_list, f, label = "", adj_label = FALSE) {
+
+  with(dat_list, {
+
+    # handle outlying values
+    # obs[obs == 0] = NA
+    # obs[obs == 1] = NA
+    obs[obs == "NaN"] = NA
+
+    # apply transformations
+    obs = f(obs)
+    mn = f(fitted$mn)
+    lwr = f(fitted$lwr)
+    upr = f(fitted$upr)
+
+    # set fitted value to NA if no data value
+    mn[is.na(obs)] = NA
+    lwr[is.na(obs)] = NA
+    upr[is.na(obs)] = NA
+
+    # obtain axis limits
+    lim = range(mn, lwr, upr, obs, na.rm = TRUE)
+
+    # create the plot
+    plot(mn ~ obs, xlim = lim, ylim = lim, pch = 21, col = solid_col, bg = tranp_col, cex = 1.5)
+
+    # draw fitted value CRIs
+    # segments(obs, lwr, obs, upr)
+
+    # draw 1:1 line
+    abline(0,1, lty = 2)
+
+    # add text
+    panel_label(label, x_inp = ifelse(adj_label, 0.05, 0.015), cex = 0.95)
+  })
+}
+
+# identity function
+ifun = function(x) x
+
+# png("fig.png", h = 7 * ppi, w = 7.2 * ppi, res = ppi)
+mypar(mfrow = c(1,1), oma = c(1.5,1.5,0,1.5), col.axis = "black", mar = c(1,0.75,0.5,0.25))
+# r1 = rep(1:3, each = 4); r2 = rep(4:7, each = 3); r3 = rep(8:11, each = 3); r4 = rep(12:15, each = 3)
+r1 = rep(1:3, each = 4); r2 = rep(4:9, each = 2); r3 = rep(10:13, each = 3); r4 = rep(14:17, each = 3)
+layout(rbind(r1, r2, r3, r4))
+# layout.show(17); dev.off()
+
+# abundance plots
+plot_f(plot_dat[["Pa_fall"]], ifun, "(a) Fall Trap Passage")
+plot_f(plot_dat[["Mb_spring"]], ifun, "(b) Spring Trap Passage")
+plot_f(plot_dat[["Ra_tot"]], ifun, "(c) Adult Return to River"); mtext(side = 4, text = "Abundance", outer = FALSE, line = 0.55)
+
+# survival plots
+plot_f(plot_dat[["phi_Pb_Ma"]], ifun, "(d) Summer \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Pa_Ma_fall"]], ifun, "(e) Fall \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Pa_Ma_winter"]], ifun, "(f) Winter \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Mb_Ma"]], ifun, "(g) Spring \u2192 LGR", TRUE)#; mtext(side = 4, text = "Survival", outer = FALSE, line = 0.75)
+plot_f(plot_dat[["phi_Ma_O0"]], ifun, "(h) LGR \u2192 BON", TRUE)
+plot_f(plot_dat[["phi_Rb_Ra"]], ifun, "(i) BON \u2192 LGR", TRUE); mtext(side = 4, text = "Survival", outer = FALSE, line = 0.55)
+
+# composition plots
+plot_f(plot_dat[["p_Ra_age3"]], ifun, "(j) Proportion Age-3")
+plot_f(plot_dat[["p_Ra_age4"]], ifun, "(k) Proportion Age-4")
+plot_f(plot_dat[["p_Ra_age5"]], ifun, "(l) Proportion Age-5")
+plot_f(plot_dat[["p_Ra_nor"]], ifun, "(m) Proportion NOR"); mtext(side = 4, text = "Weir Composition", outer = FALSE, line = 0.55)
+
+# composition plots
+plot_f(plot_dat[["p_Sa_prime_age3"]], ifun, "(n) Proportion Age-3")
+plot_f(plot_dat[["p_Sa_prime_age4"]], ifun, "(o) Proportion Age-4")
+plot_f(plot_dat[["p_Sa_prime_age5"]], ifun, "(p) Proportion Age-5")
+plot_f(plot_dat[["p_Sa_prime_nor"]], ifun, "(q) Proportion NOR"); mtext(side = 4, text = "Carcass Composition", outer = FALSE, line = 0.55)
+
+# axis labels
+axis_labels("Observed Value", "Fitted Value", yline = 0.25)
+
+# dev.off(); file.show("fig.png")
+```
+
 \clearpage

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: update color aesthetics

@@
     axis(side = 2, at = (mp1 + mp2)/2, labels = tick_labels, las = 1)
-    par(mpg = omgp)
+    par(mgp = omgp)
   }
@@
 solid_col = "grey30"
+solid_col2 = "black"
 tranp_col = alpha(solid_col, 0.25)
@@
   # add posterior mean predicted curve
-  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col2)
 
@@
   # add posterior mean predicted curve
-  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)
+  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col2)
 
@@
   # add posterior mean predicted curve
-  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col, lwd = 2)
+  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col2, lwd = 2)
 
@@
   # add posterior mean predicted curve
-  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2, lty = lty[i])
+  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col2, lwd = 2, lty = lty[i])
 
@@
   # add posterior mean of predicted curve
-  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2)
+  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col2, lwd = 2)
 
@@
   # add posterior mean of predicted curve
-  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col, lwd = 2)
+  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col2, lwd = 2)
 
@@
 # draw the posterior mean regression line
-lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)
+lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col2)
 
 # draw the population-specific capacity estimates w/error bars and labels
-segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
-segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
-points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)
+segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col2)
+segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col2, lwd = 3)
+points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col2, bg = solid_col2)
 
@@
 junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
-segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 7, col = "white")
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 5, col = "white")
 segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "white", lwd = 2)
-points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "white", lwd = 4)
-segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = "black")
-segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "black")
-points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "black", lwd = 3)
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "white", lwd = 3)
+
+segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 4, col = "black")
+segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "black", lwd = 1)
+points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "black", lwd = 2)
 

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: include toggles for new content

@@
   beta_fig:
-    value: FALSE
+    value: TRUE
   relationship_fig:
@@
   no_fall_fig:
+    value: TRUE
+  no_fall_tab:
     value: TRUE
@@
   WUL_change_fig:
+    value: TRUE
+  obs_vs_fit_fig:
+    value: TRUE
+  time_table:
     value: TRUE
@@
 
-```{r time-table}
+```{r time-table, eval = params$time_table}
 # calculate times elapsed for each chunk

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
Update scenario name

@@
     label: "Scenario"
-    value: "base_vlong"
+    value: "new-wul_vlong"
     input: text

### 2023-09-11 03-post-process/output-plots.Rmd
Update scenario name

@@
 
-```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_residual_diags}
+```{r noise-term-diags, child = "output-plots-children/11-residual-diags.Rmd", eval = params$include_residual_diags}
 ```

### 2023-10-19 03-post-process/ms-content/ms-content.Rmd
Update manuscript content figures
* Include placeholder for map
* Add a model fit summary figure
* Include a table that may better present the "no fall migrants" analysis
* Include some minor aesthetic changes

--- 2023-09-11 03-post-process/ms-content/ms-content.Rmd
@@
     value: FALSE
+  map_fig:
+    value: TRUE
+  diagram_fig:
+    value: TRUE
   beta_fig:
@@
   time_table:
-    value: TRUE
+    value: FALSE
 header-includes:
@@
 ```{r captions}
+map_caption = "
+  Placeholder for a map figure. The map should show at least: Grande Ronde basin with relevant tributaries, locations of weirs and screw traps, inset map showing region of US covered.
+"
+
+diagram_caption = "
+  Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.
+"
+
 beta_caption = "
@@
 ```
+
+```{r map-fig, fig.width = 7.2, fig.height = 5, fig.cap = msdown::prep_caption(map_caption), eval = params$map_fig}
+par(mar = rep(0.25, 4), ljoin = "mitre")
+plot(1,1, xlim = c(0,1), ylim = c(0,1), type = "n", axes = FALSE, ann = FALSE)
+text(x = 0.5, y = 0.5, "MAP\nPLACEHOLDER", font = 2, cex = 3)
+box(lwd = 4)
+```
+
+\newpage
+
+\begin{figure}[H]
+{\centering \includegraphics[width=1\linewidth,]{../../100-math-description/GR-sslcm-diagram.pdf}}
+\caption{Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.}
+\label{fig:diagram}
+\end{figure}
+
+\newpage
+
+```{r obs-vs-fit-fig, fig.width = 7.2, fig.height = 7, eval = params$obs_vs_fit_fig, fig.cap = msdown::prep_caption(obs_vs_fit_fig_caption)}
+# initialize an empty list
+plot_dat = list()
+
+# prep values to plot: fall trap passage
+plot_dat$Pa_fall = list(
+  obs = jags_data$Pa_obs[,i_fall,],
+  fitted = {
+    tmp = post_summ(post, sub_index("^Pa[.+,LH_type,.]", LH_type = i_fall))
+    list(
+      mn = array_format(tmp["mean",])[,i_fall,],
+      lwr = array_format(tmp["2.5%",])[,i_fall,],
+      upr = array_format(tmp["97.5%",])[,i_fall,]
+    )
+  }
+)
+
+# prep values to plot: spring trap passage
+plot_dat$Mb_spring = list(
+  obs = jags_data$Mb_obs[,i_spring,o_nor,],
+  fitted = {
+    tmp = post_summ(post, sub_index("^Mb[.+,LH_type,origin,.]", LH_type = i_spring, origin = o_nor))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: adult return to river
+plot_dat$Ra_tot = list(
+  obs = jags_data$Ra_obs,
+  fitted = {
+    tmp = post_summ(post, "^Ra_tot[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: summer to LGR survival
+plot_dat$phi_Pb_Ma = list(
+  obs = plogis(jags_data$Lphi_obs_Pb_Ma),
+  fitted = {
+    tmp = post_summ(post, "^phi_Pb_Ma[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: fall to LGR survival
+plot_dat$phi_Pa_Ma_fall = list(
+  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_fall,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_fall, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_fall,],
+      lwr = array_format(tmp["2.5%",])[,i_fall,],
+      upr = array_format(tmp["97.5%",])[,i_fall,]
+    )
+  }
+)
+
+# prep values to plot: winter to LGR survival
+plot_dat$phi_Pa_Ma_winter = list(
+  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_spring,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_spring, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,],
+      upr = array_format(tmp["97.5%",])[,i_spring,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (NOR)
+plot_dat$phi_Mb_Ma_nor = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_nor,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_nor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (HOR)
+plot_dat$phi_Mb_Ma_hor = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_hor,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,o_hor,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,o_hor,],
+      upr = array_format(tmp["97.5%",])[,i_spring,o_hor,]
+    )
+  }
+)
+
+# prep values to plot: spring to LGR survival (NOR & HOR both)
+plot_dat$phi_Mb_Ma = list(
+  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,,]),
+  fitted = {
+    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,.,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,i_spring,,],
+      lwr = array_format(tmp["2.5%",])[,i_spring,,],
+      upr = array_format(tmp["97.5%",])[,i_spring,,]
+    )
+  }
+)
+
+# prep values to plot: LGR to BON (NOR & HOR both)
+plot_dat$phi_Ma_O0 = list(
+  obs = plogis(jags_data$Lphi_obs_Ma_O0),
+  fitted = {
+    tmp = post_summ(post, "^phi_Ma_O0[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# prep values to plot: BON to LGR (NOR & HOR both)
+plot_dat$phi_Rb_Ra = list(
+  obs = jags_data$x_LGR/jags_data$x_BON,
+  fitted = {
+    tmp = post_summ(post, "^phi_Rb_Ra[")
+    list(
+      mn = array_format(tmp["mean",]),
+      lwr = array_format(tmp["2.5%",]),
+      upr = array_format(tmp["97.5%",])
+    )
+  }
+)
+
+# add aggregate age/origin compositions
+source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-model")
+source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-data")
+
+# prep values to plot: weir compositon age-3
+plot_dat$p_Ra_age3 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_3,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_3,],
+      lwr = array_format(tmp["2.5%",])[,k_3,],
+      upr = array_format(tmp["97.5%",])[,k_3,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-4
+plot_dat$p_Ra_age4 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_4,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,2,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_4,],
+      lwr = array_format(tmp["2.5%",])[,k_4,],
+      upr = array_format(tmp["97.5%",])[,k_4,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-5
+plot_dat$p_Ra_age5 = list(
+  obs = x_Ra_new_obs$x_Ra_age_obs[,k_5,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_age[year,3,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_5,],
+      lwr = array_format(tmp["2.5%",])[,k_5,],
+      upr = array_format(tmp["97.5%",])[,k_5,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon origin
+plot_dat$p_Ra_nor = list(
+  obs = x_Ra_new_obs$x_Ra_origin_obs[,o_nor,]/apply(x_Ra_new_obs$x_Ra_origin_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Ra_origin[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,o_nor,],
+      upr = array_format(tmp["97.5%",])[,o_nor,]
+    )
+  }
+)
+
+# prep values to plot: carcass compositon age-3
+plot_dat$p_Sa_prime_age3 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_3,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_3,],
+      lwr = array_format(tmp["2.5%",])[,k_3,],
+      upr = array_format(tmp["97.5%",])[,k_3,]
+    )
+  }
+)
+
+# prep values to plot: carcass compositon age-4
+plot_dat$p_Sa_prime_age4 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_4,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_4,],
+      lwr = array_format(tmp["2.5%",])[,k_4,],
+      upr = array_format(tmp["97.5%",])[,k_4,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon age-5
+plot_dat$p_Sa_prime_age5 = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_5,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,k_5,],
+      lwr = array_format(tmp["2.5%",])[,k_5,],
+      upr = array_format(tmp["97.5%",])[,k_5,]
+    )
+  }
+)
+
+# prep values to plot: weir compositon origin
+plot_dat$p_Sa_prime_nor = list(
+  obs = x_Sa_prime_new_obs$x_Sa_prime_origin_obs[,o_nor,]/apply(x_Sa_prime_new_obs$x_Sa_prime_origin_obs, 3, rowSums),
+  fitted = {
+    tmp = post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]", year = ".+", pop = ".+"))
+    list(
+      mn = array_format(tmp["mean",])[,o_nor,],
+      lwr = array_format(tmp["2.5%",])[,o_nor,],
+      upr = array_format(tmp["97.5%",])[,o_nor,]
+    )
+  }
+)
+
+# function to create plot for one data type
+plot_f = function(dat_list, f, label = "", adj_label = FALSE) {
+
+  with(dat_list, {
+
+    # handle outlying values
+    # obs[obs == 0] = NA
+    # obs[obs == 1] = NA
+    obs[obs == "NaN"] = NA
+
+    # apply transformations
+    obs = f(obs)
+    mn = f(fitted$mn)
+    lwr = f(fitted$lwr)
+    upr = f(fitted$upr)
+
+    # set fitted value to NA if no data value
+    mn[is.na(obs)] = NA
+    lwr[is.na(obs)] = NA
+    upr[is.na(obs)] = NA
+
+    # obtain axis limits
+    lim = range(mn, lwr, upr, obs, na.rm = TRUE)
+
+    # create the plot
+    plot(mn ~ obs, xlim = lim, ylim = lim, pch = 21, col = solid_col, bg = tranp_col, cex = 1.5)
+
+    # draw fitted value CRIs
+    # segments(obs, lwr, obs, upr)
+
+    # draw 1:1 line
+    abline(0,1, lty = 2)
+
+    # add text
+    panel_label(label, x_inp = ifelse(adj_label, 0.05, 0.015), cex = 0.95)
+  })
+}
+
+# identity function
+ifun = function(x) x
+
+# png("fig.png", h = 7 * ppi, w = 7.2 * ppi, res = ppi)
+mypar(mfrow = c(1,1), oma = c(1.5,1.5,0,1.5), col.axis = "black", mar = c(1,0.75,0.5,0.25))
+# r1 = rep(1:3, each = 4); r2 = rep(4:7, each = 3); r3 = rep(8:11, each = 3); r4 = rep(12:15, each = 3)
+r1 = rep(1:3, each = 4); r2 = rep(4:9, each = 2); r3 = rep(10:13, each = 3); r4 = rep(14:17, each = 3)
+layout(rbind(r1, r2, r3, r4))
+# layout.show(17); dev.off()
+
+# abundance plots
+plot_f(plot_dat[["Pa_fall"]], ifun, "(a) Fall Trap Passage")
+plot_f(plot_dat[["Mb_spring"]], ifun, "(b) Spring Trap Passage")
+plot_f(plot_dat[["Ra_tot"]], ifun, "(c) Adult Return to River"); mtext(side = 4, text = "Abundance", outer = FALSE, line = 0.55)
+
+# survival plots
+plot_f(plot_dat[["phi_Pb_Ma"]], ifun, "(d) Summer \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Pa_Ma_fall"]], ifun, "(e) Fall \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Pa_Ma_winter"]], ifun, "(f) Winter \u2192 LGR", TRUE)
+plot_f(plot_dat[["phi_Mb_Ma"]], ifun, "(g) Spring \u2192 LGR", TRUE)#; mtext(side = 4, text = "Survival", outer = FALSE, line = 0.75)
+plot_f(plot_dat[["phi_Ma_O0"]], ifun, "(h) LGR \u2192 BON", TRUE)
+plot_f(plot_dat[["phi_Rb_Ra"]], ifun, "(i) BON \u2192 LGR", TRUE); mtext(side = 4, text = "Survival", outer = FALSE, line = 0.55)
+
+# composition plots
+plot_f(plot_dat[["p_Ra_age3"]], ifun, "(j) Proportion Age-3")
+plot_f(plot_dat[["p_Ra_age4"]], ifun, "(k) Proportion Age-4")
+plot_f(plot_dat[["p_Ra_age5"]], ifun, "(l) Proportion Age-5")
+plot_f(plot_dat[["p_Ra_nor"]], ifun, "(m) Proportion NOR"); mtext(side = 4, text = "Weir Composition", outer = FALSE, line = 0.55)
+
+# composition plots
+plot_f(plot_dat[["p_Sa_prime_age3"]], ifun, "(n) Proportion Age-3")
+plot_f(plot_dat[["p_Sa_prime_age4"]], ifun, "(o) Proportion Age-4")
+plot_f(plot_dat[["p_Sa_prime_age5"]], ifun, "(p) Proportion Age-5")
+plot_f(plot_dat[["p_Sa_prime_nor"]], ifun, "(q) Proportion NOR"); mtext(side = 4, text = "Carcass Composition", outer = FALSE, line = 0.55)
+
+# axis labels
+axis_labels("Observed Value", "Fitted Value", yline = 0.25)
+
+# dev.off(); file.show("fig.png")
+```
+
+\newpage
 
@@
 ```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
-solid_col = "grey30"
-solid_col2 = "black"
-tranp_col = alpha(solid_col, 0.25)
-pt_cex = 1.3
 
@@
 
-\clearpage
-
-```{r obs-vs-fit-fig, fig.width = 7.2, fig.height = 7, eval = params$obs_vs_fit_fig, fig.cap = msdown::prep_caption(obs_vs_fit_fig_caption)}
-# initialize an empty list
-plot_dat = list()
-
-# prep values to plot: fall trap passage
-plot_dat$Pa_fall = list(
-  obs = jags_data$Pa_obs[,i_fall,],
-  fitted = {
-    tmp = post_summ(post, sub_index("^Pa[.+,LH_type,.]", LH_type = i_fall))
-    list(
-      mn = array_format(tmp["mean",])[,i_fall,],
-      lwr = array_format(tmp["2.5%",])[,i_fall,],
-      upr = array_format(tmp["97.5%",])[,i_fall,]
-    )
-  }
-)
-
-# prep values to plot: spring trap passage
-plot_dat$Mb_spring = list(
-  obs = jags_data$Mb_obs[,i_spring,o_nor,],
-  fitted = {
-    tmp = post_summ(post, sub_index("^Mb[.+,LH_type,origin,.]", LH_type = i_spring, origin = o_nor))
-    list(
-      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
-      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
-      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
-    )
-  }
-)
-
-# prep values to plot: adult return to river
-plot_dat$Ra_tot = list(
-  obs = jags_data$Ra_obs,
-  fitted = {
-    tmp = post_summ(post, "^Ra_tot[")
-    list(
-      mn = array_format(tmp["mean",]),
-      lwr = array_format(tmp["2.5%",]),
-      upr = array_format(tmp["97.5%",])
-    )
-  }
-)
-
-# prep values to plot: summer to LGR survival
-plot_dat$phi_Pb_Ma = list(
-  obs = plogis(jags_data$Lphi_obs_Pb_Ma),
-  fitted = {
-    tmp = post_summ(post, "^phi_Pb_Ma[")
-    list(
-      mn = array_format(tmp["mean",]),
-      lwr = array_format(tmp["2.5%",]),
-      upr = array_format(tmp["97.5%",])
-    )
-  }
-)
-
-# prep values to plot: fall to LGR survival
-plot_dat$phi_Pa_Ma_fall = list(
-  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_fall,]),
-  fitted = {
-    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_fall, pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,i_fall,],
-      lwr = array_format(tmp["2.5%",])[,i_fall,],
-      upr = array_format(tmp["97.5%",])[,i_fall,]
-    )
-  }
-)
-
-# prep values to plot: winter to LGR survival
-plot_dat$phi_Pa_Ma_winter = list(
-  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_spring,]),
-  fitted = {
-    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_spring, pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,i_spring,],
-      lwr = array_format(tmp["2.5%",])[,i_spring,],
-      upr = array_format(tmp["97.5%",])[,i_spring,]
-    )
-  }
-)
-
-# prep values to plot: spring to LGR survival (NOR)
-plot_dat$phi_Mb_Ma_nor = list(
-  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_nor,]),
-  fitted = {
-    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_nor, pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
-      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
-      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
-    )
-  }
-)
-
-# prep values to plot: spring to LGR survival (HOR)
-plot_dat$phi_Mb_Ma_hor = list(
-  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_hor,]),
-  fitted = {
-    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,i_spring,o_hor,],
-      lwr = array_format(tmp["2.5%",])[,i_spring,o_hor,],
-      upr = array_format(tmp["97.5%",])[,i_spring,o_hor,]
-    )
-  }
-)
-
-# prep values to plot: spring to LGR survival (NOR & HOR both)
-plot_dat$phi_Mb_Ma = list(
-  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,,]),
-  fitted = {
-    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,.,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,i_spring,,],
-      lwr = array_format(tmp["2.5%",])[,i_spring,,],
-      upr = array_format(tmp["97.5%",])[,i_spring,,]
-    )
-  }
-)
-
-# prep values to plot: LGR to BON (NOR & HOR both)
-plot_dat$phi_Ma_O0 = list(
-  obs = plogis(jags_data$Lphi_obs_Ma_O0),
-  fitted = {
-    tmp = post_summ(post, "^phi_Ma_O0[")
-    list(
-      mn = array_format(tmp["mean",]),
-      lwr = array_format(tmp["2.5%",]),
-      upr = array_format(tmp["97.5%",])
-    )
-  }
-)
-
-# prep values to plot: BON to LGR (NOR & HOR both)
-plot_dat$phi_Rb_Ra = list(
-  obs = jags_data$x_LGR/jags_data$x_BON,
-  fitted = {
-    tmp = post_summ(post, "^phi_Rb_Ra[")
-    list(
-      mn = array_format(tmp["mean",]),
-      lwr = array_format(tmp["2.5%",]),
-      upr = array_format(tmp["97.5%",])
-    )
-  }
-)
-
-# add aggregate age/origin compositions
-source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-model")
-source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-data")
-
-# prep values to plot: weir compositon age-3
-plot_dat$p_Ra_age3 = list(
-  obs = x_Ra_new_obs$x_Ra_age_obs[,k_3,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Ra_age[year,1,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_3,],
-      lwr = array_format(tmp["2.5%",])[,k_3,],
-      upr = array_format(tmp["97.5%",])[,k_3,]
-    )
-  }
-)
-
-# prep values to plot: weir compositon age-4
-plot_dat$p_Ra_age4 = list(
-  obs = x_Ra_new_obs$x_Ra_age_obs[,k_4,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Ra_age[year,2,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_4,],
-      lwr = array_format(tmp["2.5%",])[,k_4,],
-      upr = array_format(tmp["97.5%",])[,k_4,]
-    )
-  }
-)
-
-# prep values to plot: weir compositon age-5
-plot_dat$p_Ra_age5 = list(
-  obs = x_Ra_new_obs$x_Ra_age_obs[,k_5,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Ra_age[year,3,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_5,],
-      lwr = array_format(tmp["2.5%",])[,k_5,],
-      upr = array_format(tmp["97.5%",])[,k_5,]
-    )
-  }
-)
-
-# prep values to plot: weir compositon origin
-plot_dat$p_Ra_nor = list(
-  obs = x_Ra_new_obs$x_Ra_origin_obs[,o_nor,]/apply(x_Ra_new_obs$x_Ra_origin_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Ra_origin[year,1,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,o_nor,],
-      lwr = array_format(tmp["2.5%",])[,o_nor,],
-      upr = array_format(tmp["97.5%",])[,o_nor,]
-    )
-  }
-)
-
-# prep values to plot: carcass compositon age-3
-plot_dat$p_Sa_prime_age3 = list(
-  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_3,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_3,],
-      lwr = array_format(tmp["2.5%",])[,k_3,],
-      upr = array_format(tmp["97.5%",])[,k_3,]
-    )
-  }
-)
-
-# prep values to plot: carcass compositon age-4
-plot_dat$p_Sa_prime_age4 = list(
-  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_4,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_4,],
-      lwr = array_format(tmp["2.5%",])[,k_4,],
-      upr = array_format(tmp["97.5%",])[,k_4,]
-    )
-  }
-)
-
-# prep values to plot: weir compositon age-5
-plot_dat$p_Sa_prime_age5 = list(
-  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_5,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,k_5,],
-      lwr = array_format(tmp["2.5%",])[,k_5,],
-      upr = array_format(tmp["97.5%",])[,k_5,]
-    )
-  }
-)
-
-# prep values to plot: weir compositon origin
-plot_dat$p_Sa_prime_nor = list(
-  obs = x_Sa_prime_new_obs$x_Sa_prime_origin_obs[,o_nor,]/apply(x_Sa_prime_new_obs$x_Sa_prime_origin_obs, 3, rowSums),
-  fitted = {
-    tmp = post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]", year = ".+", pop = ".+"))
-    list(
-      mn = array_format(tmp["mean",])[,o_nor,],
-      lwr = array_format(tmp["2.5%",])[,o_nor,],
-      upr = array_format(tmp["97.5%",])[,o_nor,]
-    )
-  }
-)
-
-# function to create plot for one data type
-plot_f = function(dat_list, f, label = "", adj_label = FALSE) {
-
-  with(dat_list, {
-
-    # handle outlying values
-    # obs[obs == 0] = NA
-    # obs[obs == 1] = NA
-    obs[obs == "NaN"] = NA
-
-    # apply transformations
-    obs = f(obs)
-    mn = f(fitted$mn)
-    lwr = f(fitted$lwr)
-    upr = f(fitted$upr)
-
-    # set fitted value to NA if no data value
-    mn[is.na(obs)] = NA
-    lwr[is.na(obs)] = NA
-    upr[is.na(obs)] = NA
-
-    # obtain axis limits
-    lim = range(mn, lwr, upr, obs, na.rm = TRUE)
-
-    # create the plot
-    plot(mn ~ obs, xlim = lim, ylim = lim, pch = 21, col = solid_col, bg = tranp_col, cex = 1.5)
-
-    # draw fitted value CRIs
-    # segments(obs, lwr, obs, upr)
-
-    # draw 1:1 line
-    abline(0,1, lty = 2)
-
-    # add text
-    panel_label(label, x_inp = ifelse(adj_label, 0.05, 0.015), cex = 0.95)
-  })
-}
-
-# identity function
-ifun = function(x) x
-
-# png("fig.png", h = 7 * ppi, w = 7.2 * ppi, res = ppi)
-mypar(mfrow = c(1,1), oma = c(1.5,1.5,0,1.5), col.axis = "black", mar = c(1,0.75,0.5,0.25))
-# r1 = rep(1:3, each = 4); r2 = rep(4:7, each = 3); r3 = rep(8:11, each = 3); r4 = rep(12:15, each = 3)
-r1 = rep(1:3, each = 4); r2 = rep(4:9, each = 2); r3 = rep(10:13, each = 3); r4 = rep(14:17, each = 3)
-layout(rbind(r1, r2, r3, r4))
-# layout.show(17); dev.off()
-
-# abundance plots
-plot_f(plot_dat[["Pa_fall"]], ifun, "(a) Fall Trap Passage")
-plot_f(plot_dat[["Mb_spring"]], ifun, "(b) Spring Trap Passage")
-plot_f(plot_dat[["Ra_tot"]], ifun, "(c) Adult Return to River"); mtext(side = 4, text = "Abundance", outer = FALSE, line = 0.55)
-
-# survival plots
-plot_f(plot_dat[["phi_Pb_Ma"]], ifun, "(d) Summer \u2192 LGR", TRUE)
-plot_f(plot_dat[["phi_Pa_Ma_fall"]], ifun, "(e) Fall \u2192 LGR", TRUE)
-plot_f(plot_dat[["phi_Pa_Ma_winter"]], ifun, "(f) Winter \u2192 LGR", TRUE)
-plot_f(plot_dat[["phi_Mb_Ma"]], ifun, "(g) Spring \u2192 LGR", TRUE)#; mtext(side = 4, text = "Survival", outer = FALSE, line = 0.75)
-plot_f(plot_dat[["phi_Ma_O0"]], ifun, "(h) LGR \u2192 BON", TRUE)
-plot_f(plot_dat[["phi_Rb_Ra"]], ifun, "(i) BON \u2192 LGR", TRUE); mtext(side = 4, text = "Survival", outer = FALSE, line = 0.55)
-
-# composition plots
-plot_f(plot_dat[["p_Ra_age3"]], ifun, "(j) Proportion Age-3")
-plot_f(plot_dat[["p_Ra_age4"]], ifun, "(k) Proportion Age-4")
-plot_f(plot_dat[["p_Ra_age5"]], ifun, "(l) Proportion Age-5")
-plot_f(plot_dat[["p_Ra_nor"]], ifun, "(m) Proportion NOR"); mtext(side = 4, text = "Weir Composition", outer = FALSE, line = 0.55)
-
-# composition plots
-plot_f(plot_dat[["p_Sa_prime_age3"]], ifun, "(n) Proportion Age-3")
-plot_f(plot_dat[["p_Sa_prime_age4"]], ifun, "(o) Proportion Age-4")
-plot_f(plot_dat[["p_Sa_prime_age5"]], ifun, "(p) Proportion Age-5")
-plot_f(plot_dat[["p_Sa_prime_nor"]], ifun, "(q) Proportion NOR"); mtext(side = 4, text = "Carcass Composition", outer = FALSE, line = 0.55)
-
-# axis labels
-axis_labels("Observed Value", "Fitted Value", yline = 0.25)
-
-# dev.off(); file.show("fig.png")
-```
-
-\clearpage
+\newpage
 

### 2023-10-19 03-post-process/compare-sim-to-obs.Rmd
Replace all instances of %>% with |>
Native pipe operator

@@
 
-  kable(table_x, "html", digits = 2, row.names = FALSE, align = "llllccccc") %>%
-    kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    column_spec(5, background = assign_color(x[,5])) %>%
-    column_spec(6, background = assign_color(x[,6])) %>%
-    column_spec(7, background = assign_color(x[,7])) %>%
-    column_spec(8, background = assign_color(x[,8])) %>%
-    column_spec(9, background = assign_color(x[,9])) %>%
+  kable(table_x, "html", digits = 2, row.names = FALSE, align = "llllccccc") |> 
+    kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
+    column_spec(5, background = assign_color(x[,5])) |> 
+    column_spec(6, background = assign_color(x[,6])) |> 
+    column_spec(7, background = assign_color(x[,7])) |> 
+    column_spec(8, background = assign_color(x[,8])) |> 
+    column_spec(9, background = assign_color(x[,9])) |> 
     collapse_rows(1:4)

### 2023-10-19 03-post-process/ms-content/ms-content.Rmd
Replace all instances of %>% with |>
Native pipe operator

@@
 # create the table
-kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") %>%
-  kable_styling(full_width = FALSE, latex_options = "HOLD_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  column_spec(1, monospace = TRUE) %>%
+kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") |> 
+  kable_styling(full_width = FALSE, latex_options = "HOLD_position") |> 
+  row_spec(0, bold = TRUE) |> 
+  column_spec(1, monospace = TRUE) |> 
   row_spec(nrow(tab), bold = TRUE)

### 2023-10-19 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Replace all instances of %>% with |>
Native pipe operator

@@
 # print a table 
-kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
+kable(t(est), digits = 0, format.args = list(big.mark = ",")) |> 
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))

### 2023-10-19 03-post-process/output-plots-children/11-residual-diags.Rmd
Replace all instances of %>% with |>
Native pipe operator

--- 2023-08-18 03-post-process/output-plots-children/11-noise-term-diags.Rmd
@@
   # make the table
-  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    column_spec(5, background = out_colors[,5]) %>%
-    column_spec(6, background = out_colors[,6]) %>%
-    column_spec(7, background = out_colors[,7]) %>%
-    column_spec(8, background = out_colors[,8]) %>%
-    column_spec(9, background = out_colors[,9]) %>%
+  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") |>
+    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
+    column_spec(5, background = out_colors[,5]) |> 
+    column_spec(6, background = out_colors[,6]) |> 
+    column_spec(7, background = out_colors[,7]) |> 
+    column_spec(8, background = out_colors[,8]) |> 
+    column_spec(9, background = out_colors[,9]) |> 
     collapse_rows(columns = 1:4)
@@
 
-  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
-    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-    column_spec(6, background = out_colors[,6]) %>%
-    column_spec(7, background = out_colors[,7]) %>%
-    column_spec(8, background = out_colors[,8]) %>%
-    column_spec(9, background = out_colors[,9]) %>%
-    column_spec(10, background = out_colors[,10]) %>%
+  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") |> 
+    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
+    column_spec(6, background = out_colors[,6]) |> 
+    column_spec(7, background = out_colors[,7]) |> 
+    column_spec(8, background = out_colors[,8]) |> 
+    column_spec(9, background = out_colors[,9]) |> 
+    column_spec(10, background = out_colors[,10]) |> 
     collapse_rows(columns = 1:5)

### 2023-10-19 03-post-process/output-plots-children/99-waic.Rmd
Replace all instances of %>% with |>
Native pipe operator

--- 2022-04-28 03-post-process/output-plots-children/03b-waic.Rmd
@@
+---
+editor_options: 
+  chunk_output_type: console
+---
+
 ## WAIC
@@
 waic_out = as.data.frame(as.list(waic_out))
-waic_out %>%
-  kbl(format.args = list(big.mark = ",")) %>%
+waic_out |> 
+  kbl(format.args = list(big.mark = ",")) |> 
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))

### 2023-10-19 02-model/fit-model.R

@@ -43,19 +43,19 @@ default_args = list(
 parser = arg_parser("Fit the GR-sslcm to Data", hide.opts = TRUE) |>
   
   add_argument("scenario", "Name of model run",
-               type = "character", default = default_args$scenario) %>%
+               type = "character", default = default_args$scenario) |> 
   
   add_argument("--mcmc", paste0("Overall run length, ranging from ~5mins to ~24hrs. Accepted options are: ", knitr::combine_words(accepted_mcmc, before = "'", and = " or ")),
-               type = "character", default = default_args$mcmc) %>%
+               type = "character", default = default_args$mcmc) |> 
   
   add_argument("--sim", "Perform simulation as a validation?",
-               type = "logical", default = default_args$sim, short = "sim") %>%
+               type = "logical", default = default_args$sim, short = "sim") |> 
   
   add_argument("--rmd", "Render Rmarkdown output?",
-               type = "logical", default = default_args$rmd, short = "rmd") %>%
+               type = "logical", default = default_args$rmd, short = "rmd") |> 
   
   add_argument("--pp_check", "Include posterior predictive check calculations?",
-               type = "logical", default = default_args$pp_check, short = "pp_check") %>%
+               type = "logical", default = default_args$pp_check, short = "pp_check") |> 
   
   add_argument("--lppd", "Include log posterior predictive density calculations (for WAIC)?",
                type = "logical", default = default_args$lppd, short = "lppd") 

### 2023-10-19 03-post-process/ms-content/ms-content.Rmd
Update scenario name

@@
     label: "Scenario"
-    value: "new-wul_vlong"
+    value: "base_vlong"
     input: text

### 2023-12-05 03-post-process/output-plots-children/09-composite-rates.Rmd
Fix tiny bugs in Rmd output
Fix years in phi_Rb_Sa composite rates
Old version broken for simulation case

--- 2023-08-17 03-post-process/output-plots-children/09-equiv-rates.Rmd
@@
   # spawning adult abundance
-  Sa = post_subset(post, sub_index("^Sa[year,age,origin,pop]", year = ".+", age = ".+", origin = o, pop = j), matrix = TRUE)
+  Sa = post_subset(post, sub_index("^Sa[year,age,origin,pop]", year = ts_yrs, age = ".+", origin = o, pop = j), matrix = TRUE)
 
   # adults at estuary
-  Rb = post_subset(post, sub_index("^Rb[year,age,origin,pop]", year = 2:33, age = ".+", origin = o, pop = j), matrix = TRUE)
+  Rb = post_subset(post, sub_index("^Rb[year,age,origin,pop]", year = ts_yrs, age = ".+", origin = o, pop = j), matrix = TRUE)
 
@@
 ```{r spawners-per-return-all-ages, fig.width = p4_width, fig.height = p4_height}
-
 # loop over populations
@@
 
-### Ages 4&5 {-}
+#### Ages 4&5 {-}
 
 ```{r spawners-per-return-old-ages, fig.width = p4_width, fig.height = p4_height}
-
 # loop over populations

### 2023-12-06 03-post-process/output-plots-children/01-mcmc-dims-runtime.Rmd

---
editor_options: 
  chunk_output_type: console
---

# MCMC Dimensions & Run Time

```{r mcmc-dims-and-runtime}

## MCMC dimensions ##

# query the dimensions of the posterior samples: the full samples even if thin_percent not equal to 1
dims = post_dim(model_info$post)

# build a data frame for printing this information
df_dims = data.frame(
  Quantity = c("Burn-in + Adapt Samples", "Post Burn-in Samples", "Thinning Interval", "Chains", "Saved Samples", "Monitored Quantities", "% of Saved Samples used Here", "Chains Ran in Parallel?"),
  Value = c(unname(dims), NA, NA)
)
df_dims$Value = prettyNum(df_dims$Value, big.mark = ",", scientific = FALSE)
df_dims$Value[df_dims$Quantity == "Chains Ran in Parallel?"] = ifelse(model_info$jags_dims$parallel, "Yes", "No")
df_dims$Value[df_dims$Quantity == "% of Saved Samples used Here"] = paste0(params$thin_percent * 100, "%")

## MCMC Runtime ##

# Calculate hours per 10,000 iterations
hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
  # calculation of total iters differs if parallel or not
  if (parallel) {
    total_iters = n_adapt + n_post + n_burn
  } else {
    total_iters = (n_adapt + n_post + n_burn) * n_chains
  }
  ten_thousands_of_total_iters = total_iters/10000

  # calculate hours elapsed
  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
  time_number = as.numeric(time_diff)
  time_units = attributes(time_diff)$units
  hour_convert = switch(time_units,
                        "secs" = 3600,
                        "mins" = 60,
                        "hours" = 1,
                        "days" = 1/24)
  hours_diff = time_number/hour_convert

  # calculate/round rate
  round(hours_diff/ten_thousands_of_total_iters, 2)
})

# combine relevant info into a data frame
df_time = data.frame(
  Quantity = c("Time Started", "Time Ended", "Time Elapsed", "Hours Per 10,000 Iterations"),
  Value = c(model_info$jags_time, hrs_per_ten_thousand_iters)
)

# combine the dimensions and run time dfs into one
df = rbind(df_dims, df_time)
groups = c(rep(1, nrow(df_dims)), rep(2, nrow(df_time)))
rownames(df) = NULL

# render the table
kable(df, format.args = list(big.mark = ","), caption = "MCMC sampling dimensions and run time.", col.names = c(" ", " "), escape = FALSE) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "condensed")) |>
  group_rows("Dimensions", start_row = min(which(groups == 1)), end_row = max(which(groups == 1))) |>
  group_rows("Per Chain", start_row = 1, end_row = 3, escape = FALSE) |>
  group_rows("Overall", start_row = 4, end_row = max(which(groups == 1))) |>
  group_rows("Run Time", start_row = min(which(groups == 2)), end_row = max(which(groups == 2)))
```

### 2023-12-06 03-post-process/output-plots-children/02-mcmc-diags.Rmd

@@
 
-All convergence diagnostics were calculated using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which implements updated versions (based on rank-normalization) of the classical convergence diagnostics (presented in Vehtari et al.
-[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).
+<details>
+<summary>Click to View Diagnostic Descriptions</summary>
 
-* **Rhat** measures convergence of multiple chains to a common target distribution. Values close to 1 are better -- we've chosen these approximate categories for ease of interpretation: 
+* **Rhat** measures convergence of multiple chains to a common target distribution. Values close to 1 are better -- we've chosen these categories for ease of interpretation: 
   * _Ideal_: [1,1.01] 
@@
 Percentages shown represent the fraction of parameters that have greater than 5% MCCV, which we have deemed an acceptable level of imprecision.
+
+_All convergence diagnostics were calculated using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which implements updated versions (based on rank-normalization) of the classical convergence diagnostics (presented in Vehtari et al.
+[2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full))._
+
+</details>
 
@@
 rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
-rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable
+rhat_3_params = subset(diags_out, rhat >= 1.1)$variable
 
@@
 post_sub_2 = post_subset(post, rhat_2_params_draw)
-post_sub_3 = post_subset(post, rhat_3_params_draw)
+
+if (length(rhat_3_params) > 0) post_sub_3 = post_subset(post, rhat_3_params_draw)
 
@@
   hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, main = "")
-  axis_labels(xlab = TeX("$\\hat{R}$"), ylab = "Frequency")
+  axis_labels(xlab = "Rhat", ylab = "Frequency")
   usr = par("usr")
@@
 
-### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}
+### Ideal/No Issue {.tabset .tabset-pills}
 
@@
 
-### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}
+### Acceptable {.tabset .tabset-pills}
 
@@
 
-### $\hat{R} > 1.1$ {.tabset .tabset-pills}
+### Concerning {.tabset .tabset-pills}
 
@@
 
-There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
+There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. `r ifelse(nrow(rhat_3_params) > 0, "Here is their distribution:", "")`
 
-```{r rhat-hist-3, fig.width = 6, fig.height = 4}
+```{r rhat-hist-3, fig.width = 6, fig.height = 4, eval = length(rhat_3_params) > 0}
 rhat_hist(rhat_3)
@@
 
-```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
+```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5, eval = length(rhat_3_params) > 0}
 diag_plots(post_sub_3, ".", show_diags = "never")

### 2023-12-06 03-post-process/output-plots-children/10-rho-params.Rmd

@@
 est = post_summ(post, "rho_Lphi_Ma_O0[2,1]")
-kable(t(est), digits = 3, row.names = FALSE) %>%
+kable(t(est), digits = 3, row.names = FALSE) |> 
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
@@
 est = post_summ(post, "rho_Lphi_Rb_Ra[2,1]")
-kable(t(est), digits = 3, row.names = FALSE) %>%
+kable(t(est), digits = 3, row.names = FALSE) |> 
   kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))

### 2023-12-06 03-post-process/output-plots-children/12-pp-checks.Rmd

@@
 # produce the kable
-bp_tab %>%
+bp_tab |> 
   kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
-      align = c("lllllcccccc")) %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
-  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
-  column_spec(7, background = assign_color(bp_tab[,7])) %>%
-  column_spec(8, background = assign_color(bp_tab[,8])) %>%
-  column_spec(9, background = assign_color(bp_tab[,9])) %>%
+      align = c("lllllcccccc")) |> 
+  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
+  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) |> 
+  column_spec(7, background = assign_color(bp_tab[,7])) |> 
+  column_spec(8, background = assign_color(bp_tab[,8])) |> 
+  column_spec(9, background = assign_color(bp_tab[,9])) |> 
   collapse_rows(1:5) 

### 2023-12-06 100-math-description/GR-sslcm-math-description.Rmd

@@
 The model tracks the cohort-specific abundance of fish through various life stages and links these "state variables" over time across cohorts via production relationships (e.g., spawners produce eggs) or within cohorts via transition probabilities (e.g., parr become smolt after surviving overwinter).
-The model integrates many different data sources and fits to them simultaneously in a single joint likelihood; these data sources include rotary screw trap passage estimates, a variety of PIT tag-derived survival estimates, mean length data, hatchery smolt releases, adult return abundance, and the composition of adult returns by age and origin; other data sources that are used but are not fitted to include hatchery smolt release abundances, harvest information, fecundity estiamtes, and numbers of returning adults removed for hatchery operations.
+The model integrates many different data sources and fits to them simultaneously in a single joint likelihood; these data sources include rotary screw trap passage estimates, a variety of PIT tag-derived survival estimates, mean length data, hatchery smolt releases, adult return abundance, and the composition of adult returns by age and origin; other data sources that are used but are not fitted to include hatchery smolt release abundances, harvest information, fecundity estimates, and numbers of returning adults removed for hatchery operations.
 Four spawning populations within the Grande Ronde basin are simultaneously analyzed: Catherine Creek (CAT), Lostine River (LOS), Minam River (MIN) and the upper Grande Ronde River (UGR; `r highlight("FIGURE REFERENCE: map")`), and where relevant, the model stratifies life stages by juvenile migratory strategy (fall vs.
@@
 # build the table
-my_kable(x = tab[,1:3], caption = index_tab_cap) %>%
-  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
-  row_spec(0, bold = TRUE) %>%
-  column_spec(1, width = "50px") %>%
-  column_spec(2, width = "50px") %>%
-  column_spec(3, width = "332px") %>%
-  collapse_rows(1, valign = "bottom", latex_hline = "major") %>%
+my_kable(x = tab[,1:3], caption = index_tab_cap) |> 
+  kable_styling(full_width = FALSE, latex_options = c("HOLD")) |> 
+  row_spec(0, bold = TRUE) |> 
+  column_spec(1, width = "50px") |> 
+  column_spec(2, width = "50px") |> 
+  column_spec(3, width = "332px") |> 
+  collapse_rows(1, valign = "bottom", latex_hline = "major") |> 
   footnote(number = footnote_key, threeparttable = TRUE, escape = FALSE)
@@
 
-my_kable(x = tab[,2:5], caption = symbol_tab_cap, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = symbol_tab_cap, longtable = TRUE) |> 
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                 # repeat_header_continued = "\\textit{(Continued on next page...)}"
-                ) %>%
-  row_spec(0, bold = TRUE) %>%
-  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
-  column_spec(1, width = "25px") %>%
-  column_spec(2, width = "50px") %>%
-  column_spec(3, width = "50px") %>%
-  column_spec(4, width = "300px") %>%
+                ) |> 
+  row_spec(0, bold = TRUE) |> 
+  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) |> 
+  column_spec(1, width = "25px") |> 
+  column_spec(2, width = "50px") |> 
+  column_spec(3, width = "50px") |> 
+  column_spec(4, width = "300px") |> 
   collapse_rows(1, valign = "bottom", latex_hline = "full")
@@
 
-my_kable(x = tab[,2:5], caption = param_tab_cap, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = param_tab_cap, longtable = TRUE) |> 
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                 # repeat_header_continued = "\\textit{(Continued on next page...)}"
-                ) %>%
-  row_spec(0, bold = TRUE) %>%
-  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
-  column_spec(1, width = "50px") %>%
-  column_spec(2, width = "65px") %>%
-  column_spec(3, width = "20px") %>%
-  column_spec(4, width = "290px") %>%
-  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
+                ) |> 
+  row_spec(0, bold = TRUE) |> 
+  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) |> 
+  column_spec(1, width = "50px") |> 
+  column_spec(2, width = "65px") |> 
+  column_spec(3, width = "20px") |> 
+  column_spec(4, width = "290px") |> 
+  row_spec(1:(nrow(tab)-1), hline_after = TRUE) |> 
   footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
@@
 
-my_kable(x = tab[,2:5], caption = data_tab_cap, longtable = TRUE) %>%
+my_kable(x = tab[,2:5], caption = data_tab_cap, longtable = TRUE) |> 
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                 # repeat_header_continued = "\\textit{(Continued on next page...)}"
-                ) %>%
-  row_spec(0, bold = TRUE) %>%
-  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
-  column_spec(1, width = "50px") %>%
-  column_spec(2, width = "70px") %>%
-  column_spec(3, width = "20px") %>%
-  column_spec(4, width = "295px") %>%
+                ) |> 
+  row_spec(0, bold = TRUE) |> 
+  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) |> 
+  column_spec(1, width = "50px") |> 
+  column_spec(2, width = "70px") |> 
+  column_spec(3, width = "20px") |> 
+  column_spec(4, width = "295px") |> 
   collapse_rows(1, valign = "bottom", latex_hline = "full")
@@
 
-my_kable(x = tab[,2:4], caption = equation_tab_cap, longtable = TRUE, align = "lrl") %>%
+my_kable(x = tab[,2:4], caption = equation_tab_cap, longtable = TRUE, align = "lrl") |> 
   kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                 # repeat_header_continued = "\\textit{(Continued on next page...)}"
-                ) %>%
-  row_spec(0, bold = TRUE) %>%
-  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
-  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
-  column_spec(1, width = "55px") %>%
-  column_spec(2, width = "15px") %>%
-  column_spec(3, width = "365px") %>%
+                ) |> 
+  row_spec(0, bold = TRUE) |> 
+  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) |> 
+  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) |> 
+  column_spec(1, width = "55px") |> 
+  column_spec(2, width = "15px") |> 
+  column_spec(3, width = "365px") |> 
   collapse_rows(1, valign = "bottom", latex_hline = "major")
@@
 my_kable(x = tab, align = "cccc", col.names = c("Return Year", "Age-3", "Age-4", "Age-5"), 
-         caption = year_tab_caption, row.names = FALSE) %>%
-  kable_styling(full_width = FALSE) %>%
-  add_header_above(c(" " = 1, "Brood Year of Returning Adults by Age" = 3), bold = TRUE) %>%
-  row_spec(0, bold = TRUE) %>%
-  column_spec(1, bold = TRUE) %>%
+         caption = year_tab_caption, row.names = FALSE) |> 
+  kable_styling(full_width = FALSE) |> 
+  add_header_above(c(" " = 1, "Brood Year of Returning Adults by Age" = 3), bold = TRUE) |> 
+  row_spec(0, bold = TRUE) |> 
+  column_spec(1, bold = TRUE) |> 
   column_spec(2:4, width = "50px")

### 2025-05-01 03-post-process/output-plots-children/08-misc-processes.Rmd
Improve misc processes Rmd section
Minor aesthetic/organizational changes to output plots

@@
 
-# Miscellaneous Processes {.tabset .tabset-pills}
+# Miscellaneous Processes {.tabset .tabset-dropdown}
 
@@
 
-## Ocean Survival {.tabset .tabset-pills}
+## Ocean Survival {.tabset .tabset-dropdown}
 
-### Yr1 {.tabset .tabset-pills}
+### Year-1 {.tabset .tabset-pills}
 
-#### NOR {.tabset .tabset-pills}
-
-##### Realized Alone
+#### Realized Alone {.tabset .tabset-pills}
 
 The `r colorize("realized time series", main_cols["model"])`.
+
+##### (a) NOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
+axis_labels("Brood Year", "Year-1 Ocean Survival (NOR)")
 ```
 
-##### Realized & [Expected + AR(1)]
-
-The `r colorize("realized time series", main_cols["model"])` and the `r colorize("expected time series including the carry-over residual", main_cols["model2"])`.
-
-```{r phi-O0-O1-plots2, fig.width = p4_width, fig.height = p4_height}
-plot_f = function(j) {
-  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
-  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
-
-  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
-  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
-}
-
-mypar()
-junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
-```
-
-#### HOR {.tabset .tabset-pills}
-
-##### Realized Alone
-
-The `r colorize("realized time series", main_cols["model"])`.
+##### (b) HOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr1 Ocean Survival (HOR)")
+axis_labels("Brood Year", "Year-1 Ocean Survival (HOR)")
 ```
 
-### Yr2 {.tabset .tabset-pills}
+#### Realized & [Expected + AR(1)] {.tabset .tabset-pills}
 
-#### NOR
+The `r colorize("realized time series", main_cols["model"])` and the `r colorize("expected time series including the carry-over residual", main_cols["model2"])`.
+
+##### (a) NOR {-}
+
+```{r phi-O0-O1-plots2, fig.width = p4_width, fig.height = p4_height}
+plot_f = function(j) {
+  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
+
+  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
+  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
+}
+
+mypar()
+junk = sapply(1:jags_data$nj, plot_f)
+axis_labels("Brood Year", "Year-1 Ocean Survival (NOR)")
+```
+
+### Year-2 {.tabset .tabset-pills}
+
+#### (a) NOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr2 Ocean Survival (NOR)")
+axis_labels("Brood Year", "Year-2 Ocean Survival (NOR)")
 ```
 
-#### HOR
+#### (b) HOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr2 Ocean Survival (HOR)")
+axis_labels("Brood Year", "Year-2 Ocean Survival (HOR)")
 ```
 
-### Yr3 {.tabset .tabset-pills}
+### Year-3 {.tabset .tabset-pills}
 
-#### NOR
+#### (a) NOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr3 Ocean Survival (NOR)")
+axis_labels("Brood Year", "Year-3 Ocean Survival (NOR)")
 ```
 
-#### HOR
+#### (b) HOR {-}
 
@@
 junk = sapply(1:jags_data$nj, plot_f)
-axis_labels("Brood Year", "Yr3 Ocean Survival (HOR)")
+axis_labels("Brood Year", "Year-3 Ocean Survival (HOR)")
 ```
@@
 
-#### NOR
+#### (a) NOR {-}
 
@@
 
-#### HOR
+#### (b) HOR {-}
 

### 2025-05-05 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Minor Rmd updates after testing smallest MCMC settings

@@
   mypar(xaxs = "i", yaxs = "i", mfrow = c(1,1))
-  breaks = seq(min(rhat), max(rhat), length = 20)
+  breaks = seq(min(rhat[rhat != Inf]), max(rhat[rhat != Inf]), length = 20)
   max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)

### 2025-05-05 02-model/fit-model.R
Update model run defaults to the MS settings

@@ -30,8 +30,8 @@ accepted_mcmc = c("vshort", "short", "medium", "long", "vlong")
 
 # set defaults: if running interactively, adjust settings here
 default_args = list(
-  scenario    = "test",
-  mcmc        = "vshort",
+  scenario    = "final",
+  mcmc        = "vlong",
   rmd         = TRUE,
   sim         = FALSE,
   pp_check    = TRUE,
@@ -42,10 +42,10 @@ default_args = list(
 # provides defaults and instructions
 parser = arg_parser("Fit the GR-sslcm to Data", hide.opts = TRUE) |>
   
-  add_argument("scenario", "Name of model run",
+  add_argument("--scenario", "Name of model run, anything you like",
                type = "character", default = default_args$scenario) |> 
   
-  add_argument("--mcmc", paste0("Overall run length, ranging from ~5mins to ~24hrs. Accepted options are: ", knitr::combine_words(accepted_mcmc, before = "'", and = " or ")),
+  add_argument("--mcmc", paste0("Overall run length, ranging from ~5mins to ~18hrs. Accepted options are: ", knitr::combine_words(accepted_mcmc, before = "'", and = " or ")),
                type = "character", default = default_args$mcmc) |> 
   
   add_argument("--sim", "Perform simulation as a validation?",

### 2025-05-14 README.rmd
Update main README Rmd & render

---
title: ""
output: 
  github_document:
    pandoc_args: ["--wrap=preserve"]
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

> This repository stores the code code used to fit the model and compile the output presented in the manuscript _A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_ by B.A. Staton, P.P. Gibson, M. Liermann, C. Justice, M.J. Kaylor, R. Sharma, and S.M. White, which is currently undergoing peer review.

[![ArticleDOI](https://img.shields.io/badge/Article-PLACEHOLDER-blue?logo=doi&logoColor=f5f5f5)]()  
[![GitHub Repo Archive DOI](https://img.shields.io/badge/GitHub%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()

## Repo Organization

```{r subdir-table}
tab = matrix(c(
  "`00-data/`",          "Scripts for compiling the data files from their raw format in the [GR-sslcm-data](https://github.com/gibsonpp/GR-sslcm-data) repository for model fitting.",
  "`01-functions/`",     "Scripts housing functions used by scripts throughout the repository, organized by those for data preparation, plotting, MCMC initialization, and miscellaneous utility tasks.",
  "`02-model/`",         "Scripts to fit the model as well as the JAGS model code. MCMC samples are saved here after model fitting.",
  "`03-post-process.`",  "Scripts to analyze the model output, including those to produce Rmarkdown files and the figures/tables presented in the manuscript.",
  "`99-admin/`",         "Notes from various meetings discussing model development and preliminary results."
), ncol = 2, byrow = TRUE)

knitr::kable(tab, "markdown", col.names = c("Subdirectory", "Description"))

```

The additional script include `00-packages.R` loads most packages used by other scripts in this repository.

## Reproducibility

The output file from running the model is too large to track in a git repo, so this code will need to be executed locally to reproduce the output presented in the manuscript and supplement.

First, download the contents of this repository and the data repository ([GR-sslcm-data](https://github.com/gibsonpp/GR-sslcm-data)), and unzip them such that they are in the same parent directory (called whatever you like), as follows:

```bash
├── parent
    ├── GR-sslcm
    ├── GR-sslcm-data
```

Then, navigate to the `GR-sslcm` directory and from the command line, execute:

```bash
Rscript 02-model/fit.model.R
```

To see the help documentation regarding the various arguments and their settings, execute:

```bash
Rscript 02-model/fit.model.R --help
```

If you do not have access to a command line, the model can still be executed from within [RStudio](https://posit.co/download/rstudio-desktop/). Open the `GR-sslcm.Rproj` and execute:

```R
source("02-model/fit-model.R")
```

Either option will fit the state-space model, build the output summary file, and the manuscript figures and tables using the same configurations as presented in the manuscript. The supplement will be a `.html` file in the `03-post-process` subdirectory, and the figures/tables will be saved in the `03-post-process/ms-content` subdirectory.

>_The default is to use 4 CPU cores to run 150,000 MCMC iterations per each of the 4 chains. 
>This takes approximately 18 hours for MCMC and an additional several hours for post-processing on a modern laptop computer (RAM: 64GB; Processor: 20 threads, 5.40 GHz Max Turbo, 24 MB Cache).
>Similar results to those we present can be obtained with fewer MCMC iterations but lower convergence, for example:_
>```bash
>Rscript 02-model/fit-model.R --mcmc medium
>```
>_This should take approximately a third of the time, other options would be_:
>```bash
>Rscript 02-model/fit-model.R --mcmc short
>```
>_or even_:
>```bash
>Rscript 02-model/fit-model.R --mcmc vshort
>```
>_The last option should take only several minutes for MCMC and render the output in under an hour, however, because the chains will be far from converged, **it is intended for testing the code only**._

## Dependencies: JAGS and R

Program JAGS was used to run the MCMC for fitting the state-space model (v4.3.1 at the time of manuscript publication). It can be downloaded [here](https://sourceforge.net/projects/mcmc-jags/files/JAGS/4.x/) and use all defaults for installation.

Program R was used to perform all analyses (v.4.4.1 at the time of manuscript publication). It can be downloaded [here](https://www.r-project.org/) and use all defaults for installation.

The table below shows all R packages (and their versions at time of publication) that are specifically called (typically with `pkg::fn()`) or loaded (using `library(pkg)`).

```{r pkg-table}

# detect all packages called specifically
used_pkgs = renv::dependencies(quiet = TRUE)$Package |> 
  unique() |> 
  sort()

# exclude any packages you don't wish to include in the table here
# e.g., anything used solely in building this Rmd
used_pkgs = used_pkgs[!used_pkgs %in% c("renv", "sessioninfo")]

# get the version of each package
versions = sapply(used_pkgs, function(pkg) paste(packageVersion(pkg), collapse = "."))

# get the description (i.e., title field of DESCRIPTION file) of each package
desc = sapply(used_pkgs, function(pkg) paste(packageDescription(pkg)$Title, collapse = ".")) |> 
  stringr::str_replace_all("\\n", " ")

# build a matrix
tab = cbind(pkg = used_pkgs, version = versions, desc = desc)
rownames(tab) = NULL

# build package name as a markdown link, with a URL placeholder
tab[,"pkg"] = paste0("[`", tab[,"pkg"], "`](URL)")

# function to get the URL that will replace the placeholder
get_url = function(pkg) {
  paste0("https://CRAN.R-project.org/package=", pkg)
}

# get the URLs for each package and perform the replacement
tab[,"pkg"] = stringr::str_replace(tab[,"pkg"], "URL", sapply(used_pkgs, get_url))

# return the kable
kableExtra::kbl(tab, "markdown", col.names = c("Package", "Version", "Description"), align = "lrl")
```

Running the code below will display the packages not already installed on your machine:

```{r, eval = TRUE, echo = FALSE}
check_code = paste0("```R\npkgs <- c(", knitr::combine_words(used_pkgs, before = '"', and = "", sep = ', '), ")\npkgs[!pkgs %in% rownames(installed.packages())]\n```")
```

`r check_code`

## Session Info

<details>
<summary><b>Click to Expand/Hide Session Info</b></summary>

```{r message = FALSE, warning = FALSE}
junk = suppressPackageStartupMessages({
  sapply(used_pkgs, library, character.only = TRUE)
})
```

```{r}
sessioninfo::session_info()
```

</details>

### 2025-05-14 README.rmd
Update main README Rmd & render

@@
 >_The last option should take only several minutes for MCMC and render the output in under an hour, however, because the chains will be far from converged, **it is intended for testing the code only**._
+>
+>_If using the RStudio and `source(02-model/fit-model.R)` approach, these defaults can be changed by altering the `default_args` object found near the top of the script._
 

### 2025-05-14 03-post-process/output-plots-children/01-mcmc-dims-runtime.Rmd

@@
 # MCMC Dimensions & Run Time
+
+**Model Scenario Name**: ``r params$scenario``
+
+The table below displays MCMC sampling dimensions and run time.
 
@@
 # render the table
-kable(df, format.args = list(big.mark = ","), caption = "MCMC sampling dimensions and run time.", col.names = c(" ", " "), escape = FALSE) |>
+kable(df, format.args = list(big.mark = ","), col.names = c(" ", " "), escape = FALSE) |>
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "condensed")) |>

### 2025-05-14 03-post-process/output-plots-children/11-residual-diags.Rmd

@@
 
-#### Why Does this Matter? {-}
+<details>
+  <summary>
+    <p style="font-size:20px; display:inline">Why Does this Matter?</p>
+  </summary>
 
@@
 
-#### What was Calculated? {-}
+</details>
+
+<details>
+  <summary>
+    <p style="font-size:20px; display:inline">What was Calculated?</p>
+  </summary>
 
@@
 
-##### JAGS Code Example {-}
+</details>
+
+<details>
+  <summary>
+    <p style="font-size:20px; display:inline">Example with JAGS Code</p>
+  </summary>
 
@@
 
-<details>
-<summary>Click to Show Example Code</summary>
 <pre>
@@
 } </pre>
+
 </details>
 
-#### What is Shown? {-}
+<details>
+  <summary>
+    <p style="font-size:20px; display:inline">What is Shown?</p>
+  </summary>
 
@@
 They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
-`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
+
+</details>
 
@@
 
+`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`
+
 ```{r proc-error-table-prep}

### 2025-05-14 03-post-process/output-plots-children/13-param-summaries.Rmd
Rename param summaries Rmd section
& Improve it some

--- 2023-07-06 03-post-process/output-plots-children/12-param-summaries.Rmd
@@
 # Parameter Summaries {.tabset .tabset-dropdown}
+
+Boxplots display the posterior median as the heavy line, central 50% CRL as the box boundaries, and central 95% CRL as the whisker boundaries.
 
@@
   panel_label(label_text, "topleft")
+  box(col = par("col.axis"))
 }
@@
 
-### Year 1 {.tabset .tabset-pills}
+### Year-1 {.tabset .tabset-pills}
 
@@
 
-### Year 2 {.tabset .tabset-pills}
+### Year-2 {.tabset .tabset-pills}
 
@@
 
-### Year 3 {.tabset .tabset-pills}
+### Year-3 {.tabset .tabset-pills}
 

### 2025-05-14 03-post-process/output-plots.Rmd

@@
 ---
-title: "Output Summary"
-subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
-date: "`r paste0('Date Rendered: ', Sys.Date())`"
+title: '<span style="font-variant: small-caps;"><b><big>Supplement B</big></b></span>'
+subtitle: "<small>_A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_</small>"
+author: |
+  | <small>**Authors**: B.A.
+Staton <a href="https://orcid.org/0000-0002-2342-3482"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, P.P.
+Gibson <a href="https://orcid.org/0000-0002-9751-7895"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M.
+Liermann <a href="https://orcid.org/0009-0004-5019-1471"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, C.
+Justice <a href="https://orcid.org/0000-0003-0663-5536"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M.J.
+Kaylor <a href="https://orcid.org/0000-0001-5331-9830"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, R.
+Sharma <a href="https://orcid.org/0000-0002-3818-9393"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, and S.M.
+White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
 output: 
@@
     label: "Scenario"
-    value: "new-wul_vlong"
+    value: "final_vlong"
     input: text
@@
 ---
+
+```{css, echo = FALSE}
+h1 {
+  color: black;
+  background-color: lightgrey;
+  font-size: 2.75em;
+  font-variant: small-caps;
+  font-weight: 700;
+  text-decoration: underline;
+  border-radius: 5px;
+  border-color: darkslategrey;
+  padding-left: 10px;
+  padding-right: 10px;
+  padding-bottom: 5px;
+  padding-top: 5px;
+}
+```
 

### 2025-08-05 03-post-process/output-plots.Rmd
Include DOIs/placeholders in supplemental plots

@@
 White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
+  | [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)    
+  | [![CodeDOI](https://img.shields.io/badge/Code%20Archive-PLACEHOLDER-blue?logo=github&logoColor=f5f5f5)](https://doi.org/PLACEHOLDER)  
+  | [![CodeDOI](https://img.shields.io/badge/Data%20Archive-PLACEHOLDER-blue?logo=github&logoColor=f5f5f5)](https://doi.org/PLACEHOLDER)  
 output: 

### 2025-08-05 README.rmd
Include DOIs/placeholders in repo README

@@
 
-> This repository stores the code code used to fit the model and compile the output presented in the manuscript _A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_ by B.A.
+> This repository stores the code used to fit the model and compile the output presented in the manuscript _A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_ by B.A.
 Staton, P.P.
@@
 Sharma, and S.M.
-White, which is currently undergoing peer review.
+White, which has been accepted for publication in the journal _Ecological Modelling_.
 
-[![ArticleDOI](https://img.shields.io/badge/Article-PLACEHOLDER-blue?logo=doi&logoColor=f5f5f5)]()  
-[![GitHub Repo Archive DOI](https://img.shields.io/badge/GitHub%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()
+[![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)  
+[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()  
+[![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()
 

### 2025-08-05 03-post-process/output-plots.Rmd
Include code repo DOI in supplement A and README

--- 2025-05-14 03-post-process/output-plots.Rmd
@@
 White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
+  | [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)    
+  | [![CodeDOI](https://img.shields.io/badge/Code%20Archive-10.5281/zenodo.16748911-blue?logo=github&logoColor=f5f5f5)](https://doi.org/10.5281/zenodo.16748911)  
+  | [![CodeDOI](https://img.shields.io/badge/Data%20Archive-PLACEHOLDER-blue?logo=github&logoColor=f5f5f5)](https://doi.org/PLACEHOLDER)  
 output: 

### 2025-08-05 README.rmd
Include code repo DOI in supplement A and README

@@
 [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)  
-[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()  
+[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-10.5281/zenodo.16748911-blue?logo=github)](https://doi.org/10.5281/zenodo.16748911)  
 [![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()

### 2025-08-07 03-post-process/output-plots.Rmd
Include code repo DOIs in supplement A and README
Actually supplement B, here and in previous commits. SupplA is the math description

--- 2025-05-14 03-post-process/output-plots.Rmd
@@
 White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
+  | [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)    
+  | [![CodeDOI](https://img.shields.io/badge/Code%20Archive-10.5281/zenodo.16748911-blue?logo=github&logoColor=f5f5f5)](https://doi.org/10.5281/zenodo.16748911)  
+  | [![CodeDOI](https://img.shields.io/badge/Data%20Archive-10.5281/zenodo.16756167-blue?logo=github&logoColor=f5f5f5)](https://doi.org/10.5281/zenodo.16756167)  
 output: 

### 2025-08-07 README.rmd
Include code repo DOIs in supplement A and README
Actually supplement B, here and in previous commits. SupplA is the math description

--- 2025-08-05 README.rmd
@@
 [![ArticleDOI](https://img.shields.io/badge/Article-10.1016/j.ecolmodel.2025.111289-blue?logo=doi&logoColor=f5f5f5)](https://www.doi.org/10.1016/j.ecolmodel.2025.111289)  
-[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()  
-[![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-PLACEHOLDER-blue?logo=github)]()
+[![GitHub Code Repo Archive DOI](https://img.shields.io/badge/GitHub%20Code%20Repo%20Archive-10.5281/zenodo.16748911-blue?logo=github)](https://doi.org/10.5281/zenodo.16748911)  
+[![GitHub Data Repo Archive DOI](https://img.shields.io/badge/GitHub%20Data%20Repo%20Archive-10.5281/zenodo.16756167-blue?logo=github)](https://doi.org/10.5281/zenodo.16756167)
 
